### 2023-02-09 conclusion.Rmd
Adding first cut of thesis

---
title: ''
output: pdf_document

---

\addcontentsline{toc}{section}{Conclusion}
\section*{Conclusion}

Thank you for following this tutorial!

I hope you'll find it useful to write a very professional dissertation.

\cite{ngTracingPathChikungunya2010}

### 2023-02-09 frontmatter.Rmd
Adding first cut of thesis

---
title: ''
output: pdf_document
indent: true
---

\addcontentsline{toc}{section}{Acknowledgements}

\section*{Acknowledgements}

<!-- Thank you to: -->

<!-- Stéphane Verguet -->
<!-- Margaret McConnell -->
<!-- Jessica Cohen -->

<!-- Feedback from: -->

<!-- <!-- Sebastian Bauhoff (early ideas) -->
<!-- <!-- Kevin Croke (early ideas) --> 
<!-- <!-- Harvard Center for Population and Development Studies  --> 
<!-- <!-- David Canning (teaching and econometrics) -->

<!-- Support from: -->

<!-- Jarvis Chen -->
<!-- Bruce Villineau -->
<!-- Matthew Boccuzzi -->
<!-- Claudette Agustin -->

<!-- Allison Conary -->
<!-- Barbara Heil -->

<!-- Friends at HSPH: -->
<!-- ... -->
<!-- Family: -->
<!-- Partner: -->

\newpage

\hspace{0pt}

\vfill

\begin{raggedright}

\emph{Dedicated to ....}

\end{raggedright}

\vfill

\hspace{0pt}

### 2023-02-09 intro.Rmd
Adding first cut of thesis

---
title: ''
output: pdf_document
indent: yes
---
\section*{Introduction}

\addcontentsline{toc}{section}{Introduction}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Lacinia quis vel eros donec ac odio tempor. Urna nec tincidunt praesent semper feugiat nibh. Tortor aliquam nulla facilisi cras fermentum odio eu feugiat. Magna ac placerat vestibulum lectus mauris ultrices eros. Pulvinar proin gravida hendrerit lectus. Nisi scelerisque eu ultrices vitae auctor eu. Quis hendrerit dolor magna eget est lorem ipsum. At consectetur lorem donec massa sapien faucibus et molestie. Feugiat in fermentum posuere urna nec tincidunt praesent. Facilisis gravida neque convallis a cras. Massa id neque aliquam vestibulum morbi blandit. Faucibus purus in massa tempor nec feugiat nisl pretium fusce. Amet facilisis magna etiam tempor orci eu lobortis. Odio tempor orci dapibus ultrices in iaculis nunc sed augue. Nulla aliquet porttitor lacus luctus accumsan tortor posuere ac ut. Sit amet aliquam id diam maecenas. Rhoncus aenean vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant. Urna nunc id cursus metus aliquam.

Arcu odio ut sem nulla pharetra diam sit. Adipiscing bibendum est ultricies integer. Accumsan lacus vel facilisis volutpat est. Turpis egestas sed tempus urna et pharetra pharetra. Est placerat in egestas erat imperdiet. Blandit aliquam etiam erat velit scelerisque in dictum non. Semper eget duis at tellus at urna condimentum. Tellus cras adipiscing enim eu turpis egestas. Vitae ultricies leo integer malesuada nunc vel. Sapien pellentesque habitant morbi tristique senectus et.

Diam maecenas ultricies mi eget mauris pharetra. In arcu cursus euismod quis viverra nibh. Erat imperdiet sed euismod nisi porta. Ultricies mi eget mauris pharetra. Donec et odio pellentesque diam volutpat commodo. Vulputate sapien nec sagittis aliquam malesuada bibendum arcu. In eu mi bibendum neque egestas congue quisque egestas diam. Tortor dignissim convallis aenean et. Aliquam ut porttitor leo a diam sollicitudin. Cursus turpis massa tincidunt dui ut ornare lectus. Rhoncus mattis rhoncus urna neque. Enim blandit volutpat maecenas volutpat blandit. Egestas tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla. Adipiscing commodo elit at imperdiet dui accumsan sit amet. Pharetra massa massa ultricies mi quis. Quam pellentesque nec nam aliquam.

At tempor commodo ullamcorper a. Commodo viverra maecenas accumsan lacus vel facilisis volutpat est. Sed arcu non odio euismod lacinia at. Turpis nunc eget lorem dolor sed viverra ipsum. Malesuada fames ac turpis egestas. Et ultrices neque ornare aenean euismod elementum. Quisque egestas diam in arcu cursus euismod quis viverra nibh. Semper eget duis at tellus. Id diam maecenas ultricies mi eget mauris pharetra. Eget nunc scelerisque viverra mauris in aliquam sem fringilla. Sit amet massa vitae tortor condimentum lacinia quis vel. Ut faucibus pulvinar elementum integer enim neque. Amet justo donec enim diam vulputate. Cursus eget nunc scelerisque viverra. Gravida dictum fusce ut placerat orci nulla pellentesque. Purus semper eget duis at tellus at urna condimentum mattis. Ante in nibh mauris cursus mattis molestie a iaculis. Tincidunt augue interdum velit euismod. Urna nec tincidunt praesent semper feugiat nibh sed pulvinar. Tellus integer feugiat scelerisque varius morbi enim nunc.

Felis eget velit aliquet sagittis id. Lacus laoreet non curabitur gravida arcu ac. Id diam vel quam elementum. Lacinia at quis risus sed vulputate odio ut enim blandit. Platea dictumst vestibulum rhoncus est pellentesque elit ullamcorper. Nunc aliquet bibendum enim facilisis. Viverra mauris in aliquam sem fringilla ut morbi. Eu lobortis elementum nibh tellus molestie nunc non blandit. Ut enim blandit volutpat maecenas volutpat blandit aliquam. Non odio euismod lacinia at quis risus sed vulputate.

Libero id faucibus nisl tincidunt eget. Odio aenean sed adipiscing diam donec. Porta nibh venenatis cras sed felis eget velit aliquet. Enim nunc faucibus a pellentesque sit amet porttitor. Elementum nisi quis eleifend quam adipiscing vitae proin. Eget sit amet tellus cras adipiscing enim. In ante metus dictum at tempor commodo ullamcorper. Feugiat in fermentum posuere urna nec tincidunt praesent. Amet justo donec enim diam. In massa tempor nec feugiat. Mattis rhoncus urna neque viverra justo nec ultrices dui sapien. Tellus cras adipiscing enim eu turpis. Scelerisque eu ultrices vitae auctor. Viverra maecenas accumsan lacus vel facilisis. Donec et odio pellentesque diam volutpat commodo. Congue nisi vitae suscipit tellus mauris a. A scelerisque purus semper eget duis at tellus at urna.

Mauris augue neque gravida in fermentum et sollicitudin ac orci. Rutrum quisque non tellus orci ac. Diam ut venenatis tellus in metus vulputate eu. Amet nisl suscipit adipiscing bibendum est ultricies integer quis. Velit euismod in pellentesque massa placerat duis ultricies lacus sed. Suspendisse potenti nullam ac tortor. Porttitor rhoncus dolor purus non enim praesent. Tortor consequat id porta nibh venenatis cras sed felis. Mattis rhoncus urna neque viverra justo nec ultrices dui. Eget lorem dolor sed viverra ipsum nunc aliquet.

Sed ullamcorper morbi tincidunt ornare. Gravida rutrum quisque non tellus. Metus aliquam eleifend mi in. Sollicitudin aliquam ultrices sagittis orci a scelerisque. Ullamcorper velit sed ullamcorper morbi. Cras sed felis eget velit aliquet. Libero enim sed faucibus turpis in. Molestie ac feugiat sed lectus vestibulum mattis ullamcorper velit. Viverra orci sagittis eu volutpat odio facilisis mauris sit amet. Dignissim sodales ut eu sem integer vitae.

Posuere urna nec tincidunt praesent. Et tortor consequat id porta nibh. Elit duis tristique sollicitudin nibh sit amet commodo nulla. Iaculis nunc sed augue lacus. Pulvinar pellentesque habitant morbi tristique senectus et. Integer quis auctor elit sed vulputate mi. Interdum posuere lorem ipsum dolor sit amet consectetur adipiscing elit. Ultricies tristique nulla aliquet enim tortor. Vivamus arcu felis bibendum ut tristique et egestas quis ipsum. Id eu nisl nunc mi. Eget nullam non nisi est sit amet facilisis magna. Quis ipsum suspendisse ultrices gravida. Blandit turpis cursus in hac habitasse platea dictumst quisque. Vulputate mi sit amet mauris commodo quis imperdiet. Pretium fusce id velit ut. Libero enim sed faucibus turpis. Massa eget egestas purus viverra accumsan.

Quis imperdiet massa tincidunt nunc pulvinar sapien et ligula ullamcorper. Diam phasellus vestibulum lorem sed risus ultricies tristique. Orci eu lobortis elementum nibh tellus molestie. Ornare aenean euismod elementum nisi. Rhoncus urna neque viverra justo. Dignissim cras tincidunt lobortis feugiat vivamus. Fusce id velit ut tortor pretium viverra. Quis vel eros donec ac odio. Tellus id interdum velit laoreet. Maecenas accumsan lacus vel facilisis. Cursus mattis molestie a iaculis at erat. Nibh mauris cursus mattis molestie. Pellentesque diam volutpat commodo sed egestas. Et netus et malesuada fames ac turpis egestas integer eget.

Consequat interdum varius sit amet mattis vulputate enim nulla aliquet. Aliquam id diam maecenas ultricies mi eget mauris pharetra. Porttitor eget dolor morbi non arcu. Eleifend donec pretium vulputate sapien nec sagittis aliquam malesuada. Viverra ipsum nunc aliquet bibendum enim. Egestas purus viverra accumsan in nisl nisi. Quam elementum pulvinar etiam non quam lacus. Non enim praesent elementum facilisis leo. Eget velit aliquet sagittis id consectetur. Leo integer malesuada nunc vel risus commodo viverra. Nulla facilisi etiam dignissim diam. Id diam maecenas ultricies mi eget. Arcu felis bibendum ut tristique et. Nunc lobortis mattis aliquam faucibus purus. Semper auctor neque vitae tempus.

Est ultricies integer quis auctor elit sed vulputate mi. Bibendum at varius vel pharetra vel turpis. Risus viverra adipiscing at in tellus. Volutpat maecenas volutpat blandit aliquam etiam erat. Cras sed felis eget velit aliquet sagittis id consectetur purus. Dignissim diam quis enim lobortis scelerisque fermentum dui faucibus in. Vivamus arcu felis bibendum ut tristique et egestas. Porttitor eget dolor morbi non. Ut pharetra sit amet aliquam id diam maecenas ultricies. Viverra nam libero justo laoreet sit amet. Egestas diam in arcu cursus euismod quis viverra nibh cras. Non nisi est sit amet facilisis. Dictumst vestibulum rhoncus est pellentesque elit. Ipsum consequat nisl vel pretium lectus. Nunc sed velit dignissim sodales ut eu. Ipsum suspendisse ultrices gravida dictum. Orci sagittis eu volutpat odio facilisis. Lobortis feugiat vivamus at augue eget arcu dictum varius. Bibendum ut tristique et egestas. Tincidunt ornare massa eget egestas purus viverra accumsan in.

Arcu odio ut sem nulla. Porttitor massa id neque aliquam. Sed felis eget velit aliquet sagittis id consectetur purus. Lacus vestibulum sed arcu non odio euismod lacinia at. Varius sit amet mattis vulputate enim nulla aliquet. Scelerisque mauris pellentesque pulvinar pellentesque habitant morbi tristique. Morbi enim nunc faucibus a pellentesque sit amet. Varius quam quisque id diam vel quam elementum. Commodo nulla facilisi nullam vehicula ipsum a arcu cursus. Diam donec adipiscing tristique risus nec feugiat in fermentum. Blandit turpis cursus in hac habitasse platea dictumst. Ante in nibh mauris cursus mattis molestie. Sed adipiscing diam donec adipiscing tristique risus nec.

Amet facilisis magna etiam tempor orci eu lobortis elementum nibh. Eget dolor morbi non arcu risus quis varius quam. Consequat id porta nibh venenatis cras sed. Pretium nibh ipsum consequat nisl vel. Feugiat nibh sed pulvinar proin gravida hendrerit. Risus sed vulputate odio ut enim blandit volutpat. Sem integer vitae justo eget magna fermentum iaculis. Consequat semper viverra nam libero justo laoreet sit amet. Arcu felis bibendum ut tristique et egestas. Proin fermentum leo vel orci porta. Aliquam malesuada bibendum arcu vitae elementum. Consectetur adipiscing elit duis tristique sollicitudin nibh. Non quam lacus suspendisse faucibus interdum posuere lorem ipsum. Ullamcorper velit sed ullamcorper morbi tincidunt ornare massa. Risus commodo viverra maecenas accumsan lacus vel facilisis volutpat. Ut etiam sit amet nisl. Urna condimentum mattis pellentesque id nibh tortor id aliquet lectus. Ornare massa eget egestas purus viverra accumsan.

Auctor augue mauris augue neque gravida in fermentum et. Lectus mauris ultrices eros in cursus turpis. Commodo elit at imperdiet dui accumsan sit. Eget nulla facilisi etiam dignissim diam quis enim lobortis scelerisque. Volutpat est velit egestas dui id. Nunc eget lorem dolor sed viverra ipsum. Nullam ac tortor vitae purus faucibus ornare suspendisse sed nisi. Justo donec enim diam vulputate ut. Sodales ut etiam sit amet nisl purus. Congue nisi vitae suscipit tellus. Mauris cursus mattis molestie a. Pellentesque id nibh tortor id aliquet. Porta non pulvinar neque laoreet suspendisse interdum consectetur libero id. Diam vulputate ut pharetra sit. Placerat vestibulum lectus mauris ultrices eros in cursus. A arcu cursus vitae congue mauris rhoncus aenean.

Nisi vitae suscipit tellus mauris a diam. Aenean et tortor at risus viverra adipiscing at. Ultrices eros in cursus turpis massa tincidunt. Euismod lacinia at quis risus sed. Egestas diam in arcu cursus euismod quis. Eu lobortis elementum nibh tellus molestie nunc non. Ornare arcu odio ut sem nulla pharetra diam. Senectus et netus et malesuada fames. Condimentum vitae sapien pellentesque habitant morbi. Diam sit amet nisl suscipit. Porta lorem mollis aliquam ut porttitor leo a. Sed risus pretium quam vulputate dignissim suspendisse in est ante. Risus pretium quam vulputate dignissim suspendisse in est. Pellentesque eu tincidunt tortor aliquam. Amet consectetur adipiscing elit pellentesque habitant. Mattis pellentesque id nibh tortor. Purus faucibus ornare suspendisse sed. Id venenatis a condimentum vitae. Ipsum a arcu cursus vitae. Pretium fusce id velit ut.

Feugiat scelerisque varius morbi enim nunc. Mattis vulputate enim nulla aliquet porttitor lacus. Est ante in nibh mauris cursus mattis molestie. Egestas tellus rutrum tellus pellentesque eu tincidunt tortor. Hendrerit gravida rutrum quisque non tellus orci. Platea dictumst vestibulum rhoncus est pellentesque. Amet nisl purus in mollis nunc sed. Vestibulum morbi blandit cursus risus at ultrices mi tempus imperdiet. Enim neque volutpat ac tincidunt vitae semper quis lectus nulla. Praesent elementum facilisis leo vel fringilla est ullamcorper. Consectetur adipiscing elit ut aliquam purus sit amet. Risus commodo viverra maecenas accumsan lacus. Tristique nulla aliquet enim tortor at auctor urna nunc. A scelerisque purus semper eget duis at tellus at.

Felis imperdiet proin fermentum leo vel orci porta non. Egestas egestas fringilla phasellus faucibus scelerisque. Lectus magna fringilla urna porttitor. Dignissim convallis aenean et tortor at. Laoreet id donec ultrices tincidunt arcu. Magna fringilla urna porttitor rhoncus dolor purus. Felis bibendum ut tristique et egestas quis ipsum. Ultrices vitae auctor eu augue ut lectus arcu bibendum at. Scelerisque eu ultrices vitae auctor eu augue ut lectus arcu. Fringilla est ullamcorper eget nulla facilisi etiam dignissim. Neque viverra justo nec ultrices dui sapien eget mi. Aliquet bibendum enim facilisis gravida neque convallis. Est placerat in egestas erat imperdiet sed. Arcu felis bibendum ut tristique et egestas quis ipsum suspendisse. Id donec ultrices tincidunt arcu non sodales. Senectus et netus et malesuada fames ac.

Feugiat nibh sed pulvinar proin gravida hendrerit. Ullamcorper dignissim cras tincidunt lobortis feugiat vivamus at. Ultrices dui sapien eget mi proin sed libero enim sed. In metus vulputate eu scelerisque. A arcu cursus vitae congue mauris rhoncus aenean vel elit. Pellentesque id nibh tortor id aliquet lectus proin nibh nisl. Diam donec adipiscing tristique risus nec feugiat in fermentum posuere. Suspendisse faucibus interdum posuere lorem ipsum. In metus vulputate eu scelerisque felis imperdiet. Porttitor leo a diam sollicitudin tempor id. Elit duis tristique sollicitudin nibh sit amet. Imperdiet proin fermentum leo vel. Eu sem integer vitae justo eget. Diam volutpat commodo sed egestas egestas. Sagittis aliquam malesuada bibendum arcu vitae elementum curabitur vitae nunc. Quam pellentesque nec nam aliquam. Tellus in metus vulputate eu scelerisque felis imperdiet proin fermentum.

Libero justo laoreet sit amet cursus sit amet. Scelerisque eu ultrices vitae auctor eu augue. Ultrices eros in cursus turpis massa tincidunt dui. Convallis tellus id interdum velit laoreet id donec. Cras adipiscing enim eu turpis. Blandit cursus risus at ultrices. Ut etiam sit amet nisl. Vel fringilla est ullamcorper eget nulla. Consequat id porta nibh venenatis cras sed felis eget. At consectetur lorem donec massa sapien. Auctor elit sed vulputate mi. Vitae suscipit tellus mauris a diam maecenas. Rhoncus urna neque viverra justo nec ultrices dui sapien. Vulputate dignissim suspendisse in est. Ac turpis egestas maecenas pharetra. Gravida dictum fusce ut placerat orci nulla pellentesque. Diam vel quam elementum pulvinar etiam.

Congue nisi vitae suscipit tellus mauris. Rhoncus mattis rhoncus urna neque viverra justo. At augue eget arcu dictum varius. Vitae turpis massa sed elementum tempus. Sed risus pretium quam vulputate dignissim. Consectetur adipiscing elit ut aliquam purus. Ligula ullamcorper malesuada proin libero nunc. Tincidunt tortor aliquam nulla facilisi. Phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor. Etiam erat velit scelerisque in dictum non consectetur a. Placerat duis ultricies lacus sed turpis. Diam vulputate ut pharetra sit amet aliquam id. Faucibus in ornare quam viverra. Elementum nibh tellus molestie nunc non blandit massa. Nunc vel risus commodo viverra maecenas accumsan lacus vel. Sagittis orci a scelerisque purus semper eget duis at tellus.

Quam nulla porttitor massa id neque aliquam. Et netus et malesuada fames ac turpis egestas sed tempus. Tellus integer feugiat scelerisque varius morbi enim nunc faucibus. Mattis ullamcorper velit sed ullamcorper. Ornare arcu odio ut sem nulla pharetra diam sit. Sed vulputate odio ut enim. Ut tristique et egestas quis ipsum. Dui sapien eget mi proin sed. Eget nulla facilisi etiam dignissim diam quis enim. Venenatis lectus magna fringilla urna porttitor rhoncus dolor purus. Auctor urna nunc id cursus metus aliquam. Ornare aenean euismod elementum nisi quis. Et leo duis ut diam quam nulla. Dictum sit amet justo donec enim. Quis auctor elit sed vulputate mi sit. Diam sollicitudin tempor id eu.

Venenatis tellus in metus vulputate eu scelerisque felis imperdiet proin. Quis vel eros donec ac. Sit amet cursus sit amet. Et magnis dis parturient montes nascetur ridiculus mus. Purus sit amet luctus venenatis lectus magna fringilla. Amet consectetur adipiscing elit duis tristique. Aliquet bibendum enim facilisis gravida. Neque laoreet suspendisse interdum consectetur. Etiam dignissim diam quis enim lobortis scelerisque fermentum. Id consectetur purus ut faucibus pulvinar. Parturient montes nascetur ridiculus mus mauris vitae ultricies leo integer. Enim neque volutpat ac tincidunt. Aliquam malesuada bibendum arcu vitae elementum curabitur. At imperdiet dui accumsan sit amet nulla facilisi morbi. Hac habitasse platea dictumst vestibulum rhoncus est. Accumsan lacus vel facilisis volutpat est velit. Commodo quis imperdiet massa tincidunt. Faucibus purus in massa tempor nec feugiat nisl.

Amet nulla facilisi morbi tempus iaculis urna id. Et malesuada fames ac turpis egestas sed tempus urna et. Nam aliquam sem et tortor consequat id porta. Suspendisse potenti nullam ac tortor. Quis enim lobortis scelerisque fermentum. Sed velit dignissim sodales ut eu sem integer vitae justo. In est ante in nibh mauris cursus mattis. Sollicitudin nibh sit amet commodo nulla facilisi nullam vehicula ipsum. Vitae tortor condimentum lacinia quis vel eros. Etiam non quam lacus suspendisse faucibus interdum posuere. Magna ac placerat vestibulum lectus mauris ultrices. Auctor eu augue ut lectus arcu. Mi eget mauris pharetra et ultrices neque ornare aenean euismod. Mattis ullamcorper velit sed ullamcorper morbi tincidunt ornare massa eget. Elementum sagittis vitae et leo duis ut diam quam nulla.

At lectus urna duis convallis. Fames ac turpis egestas integer eget. Sapien eget mi proin sed. Id ornare arcu odio ut sem nulla pharetra diam. Ac tincidunt vitae semper quis lectus. Varius vel pharetra vel turpis nunc eget lorem dolor sed. Tortor at risus viverra adipiscing at in tellus. Venenatis a condimentum vitae sapien pellentesque habitant. Convallis posuere morbi leo urna molestie at. Dignissim sodales ut eu sem integer. Maecenas sed enim ut sem viverra aliquet eget sit amet. Id cursus metus aliquam eleifend mi in nulla.

Facilisi morbi tempus iaculis urna id. Quis eleifend quam adipiscing vitae. Viverra accumsan in nisl nisi scelerisque eu ultrices vitae auctor. Imperdiet nulla malesuada pellentesque elit eget gravida cum sociis natoque. Turpis in eu mi bibendum neque egestas congue quisque. Urna neque viverra justo nec ultrices dui. Proin sagittis nisl rhoncus mattis rhoncus urna. Eros donec ac odio tempor orci dapibus ultrices in iaculis. Ornare arcu dui vivamus arcu felis bibendum ut. Tincidunt nunc pulvinar sapien et ligula. In dictum non consectetur a. Bibendum arcu vitae elementum curabitur vitae nunc sed velit. Ut consequat semper viverra nam libero justo. Commodo viverra maecenas accumsan lacus vel. Vitae tortor condimentum lacinia quis vel eros donec. Iaculis urna id volutpat lacus laoreet non. Nec ultrices dui sapien eget mi. Suspendisse potenti nullam ac tortor vitae purus faucibus. Scelerisque felis imperdiet proin fermentum.

Nunc mi ipsum faucibus vitae aliquet nec ullamcorper sit. Id aliquet lectus proin nibh nisl condimentum. Feugiat in fermentum posuere urna nec tincidunt. Nunc sed id semper risus in hendrerit gravida rutrum. Vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant morbi. Id aliquet lectus proin nibh nisl condimentum id venenatis. Quis eleifend quam adipiscing vitae. Commodo ullamcorper a lacus vestibulum sed arcu non odio euismod. Tellus pellentesque eu tincidunt tortor aliquam nulla. Nunc mi ipsum faucibus vitae. A scelerisque purus semper eget duis at tellus at urna. Faucibus ornare suspendisse sed nisi lacus sed viverra tellus. Tortor pretium viverra suspendisse potenti nullam.

Habitant morbi tristique senectus et netus et malesuada fames. Nisl nunc mi ipsum faucibus vitae aliquet nec. Sapien nec sagittis aliquam malesuada. Purus faucibus ornare suspendisse sed nisi lacus sed. Venenatis lectus magna fringilla urna porttitor rhoncus dolor. Adipiscing elit pellentesque habitant morbi tristique senectus et. In tellus integer feugiat scelerisque. Amet nisl purus in mollis nunc. Mauris augue neque gravida in fermentum et. Augue ut lectus arcu bibendum at.

Pharetra sit amet aliquam id diam maecenas ultricies mi. Sociis natoque penatibus et magnis dis parturient. Fringilla phasellus faucibus scelerisque eleifend. Ultrices tincidunt arcu non sodales neque sodales ut. Sed egestas egestas fringilla phasellus faucibus scelerisque eleifend donec. Eget nulla facilisi etiam dignissim diam quis enim. Cras ornare arcu dui vivamus arcu felis bibendum ut. Ultricies lacus sed turpis tincidunt id. Volutpat est velit egestas dui id ornare arcu. Tristique senectus et netus et malesuada fames. Id volutpat lacus laoreet non curabitur. Massa sed elementum tempus egestas sed sed risus pretium. Mollis aliquam ut porttitor leo. Leo urna molestie at elementum eu facilisis sed odio morbi. Netus et malesuada fames ac turpis egestas integer. Magnis dis parturient montes nascetur ridiculus mus.

Urna neque viverra justo nec ultrices dui sapien. Et odio pellentesque diam volutpat. Nunc lobortis mattis aliquam faucibus purus in massa tempor nec. Ac turpis egestas maecenas pharetra convallis posuere morbi. Amet nisl suscipit adipiscing bibendum. Ultricies mi quis hendrerit dolor magna. Morbi quis commodo odio aenean. Dolor magna eget est lorem ipsum dolor sit amet. Nulla aliquet enim tortor at auctor urna. Pellentesque dignissim enim sit amet venenatis urna cursus eget nunc. Nunc lobortis mattis aliquam faucibus purus. Amet est placerat in egestas erat imperdiet. Turpis in eu mi bibendum neque egestas congue quisque.

Et egestas quis ipsum suspendisse ultrices gravida dictum fusce ut. Risus sed vulputate odio ut enim blandit volutpat maecenas. Tristique senectus et netus et. Aenean euismod elementum nisi quis eleifend quam adipiscing vitae proin. Ac placerat vestibulum lectus mauris. Mauris ultrices eros in cursus turpis. Ipsum consequat nisl vel pretium lectus quam id leo in. Eu sem integer vitae justo eget magna. Mi sit amet mauris commodo quis imperdiet massa. Venenatis urna cursus eget nunc scelerisque. Fermentum leo vel orci porta non pulvinar. Diam donec adipiscing tristique risus nec feugiat in fermentum posuere. Nibh tellus molestie nunc non blandit.

Vel eros donec ac odio tempor orci. Nibh cras pulvinar mattis nunc. Et magnis dis parturient montes nascetur ridiculus. Blandit turpis cursus in hac habitasse platea dictumst quisque. Blandit libero volutpat sed cras ornare arcu. Est pellentesque elit ullamcorper dignissim cras tincidunt lobortis. Dictumst vestibulum rhoncus est pellentesque. Sagittis orci a scelerisque purus semper eget duis. Nisi quis eleifend quam adipiscing vitae. Vehicula ipsum a arcu cursus vitae congue mauris rhoncus aenean.

Curabitur gravida arcu ac tortor dignissim convallis aenean et. Senectus et netus et malesuada fames ac turpis egestas sed. Magna eget est lorem ipsum dolor sit amet consectetur. Congue mauris rhoncus aenean vel elit scelerisque. Erat nam at lectus urna duis convallis convallis tellus. Mauris sit amet massa vitae tortor condimentum lacinia. Egestas fringilla phasellus faucibus scelerisque eleifend donec pretium. Netus et malesuada fames ac turpis egestas maecenas pharetra convallis. Viverra accumsan in nisl nisi scelerisque eu ultrices. Proin sed libero enim sed faucibus turpis in eu mi. Id neque aliquam vestibulum morbi blandit. Laoreet non curabitur gravida arcu ac tortor dignissim. Iaculis nunc sed augue lacus viverra vitae congue eu consequat. Ut tortor pretium viverra suspendisse. Quisque sagittis purus sit amet volutpat consequat mauris nunc. Amet nulla facilisi morbi tempus iaculis. Amet cursus sit amet dictum sit amet justo donec.

Diam maecenas sed enim ut sem viverra aliquet. Odio tempor orci dapibus ultrices. Natoque penatibus et magnis dis parturient montes nascetur ridiculus mus. Nisi lacus sed viverra tellus in hac habitasse platea dictumst. Id diam vel quam elementum. Nulla posuere sollicitudin aliquam ultrices sagittis orci a scelerisque purus. Facilisi nullam vehicula ipsum a arcu cursus vitae. Non nisi est sit amet facilisis magna. Molestie ac feugiat sed lectus vestibulum mattis ullamcorper velit sed. Odio pellentesque diam volutpat commodo sed egestas egestas fringilla. Pellentesque id nibh tortor id aliquet lectus proin. Quis eleifend quam adipiscing vitae proin sagittis. Risus sed vulputate odio ut enim blandit volutpat. Pellentesque id nibh tortor id aliquet lectus proin nibh. Ullamcorper a lacus vestibulum sed arcu non odio euismod.

Ut tortor pretium viverra suspendisse potenti nullam ac tortor vitae. Aliquet nibh praesent tristique magna sit amet. Arcu cursus euismod quis viverra nibh cras pulvinar. Magnis dis parturient montes nascetur ridiculus mus mauris vitae. Diam sit amet nisl suscipit adipiscing. Consequat ac felis donec et odio pellentesque diam volutpat. Pellentesque pulvinar pellentesque habitant morbi tristique senectus et netus. Magna sit amet purus gravida quis blandit turpis cursus. Maecenas sed enim ut sem viverra aliquet eget sit. Consectetur adipiscing elit ut aliquam purus. Ut morbi tincidunt augue interdum velit euismod in pellentesque massa.

Nunc pulvinar sapien et ligula ullamcorper malesuada proin. Faucibus a pellentesque sit amet porttitor eget. Quam adipiscing vitae proin sagittis nisl rhoncus. Quis blandit turpis cursus in hac habitasse platea dictumst. Feugiat vivamus at augue eget arcu. Duis convallis convallis tellus id interdum velit laoreet id donec. Ornare quam viverra orci sagittis eu volutpat odio. Netus et malesuada fames ac turpis egestas maecenas. Faucibus turpis in eu mi bibendum neque egestas. Sed velit dignissim sodales ut. Dolor sed viverra ipsum nunc aliquet bibendum enim facilisis gravida.

Interdum varius sit amet mattis vulputate. Dui id ornare arcu odio ut sem nulla pharetra diam. Neque gravida in fermentum et sollicitudin ac orci. Nibh ipsum consequat nisl vel pretium lectus quam id leo. Mauris pellentesque pulvinar pellentesque habitant morbi tristique senectus et netus. Massa tempor nec feugiat nisl pretium fusce id velit ut. Vivamus at augue eget arcu dictum varius duis at consectetur. Odio ut enim blandit volutpat maecenas volutpat blandit aliquam etiam. Mauris ultrices eros in cursus. Tristique senectus et netus et malesuada.

Imperdiet sed euismod nisi porta lorem mollis aliquam. Eget lorem dolor sed viverra ipsum nunc aliquet bibendum enim. Eget lorem dolor sed viverra. Vitae proin sagittis nisl rhoncus mattis. Mi sit amet mauris commodo quis imperdiet massa tincidunt. Quis auctor elit sed vulputate mi. Augue eget arcu dictum varius duis at consectetur lorem. Commodo elit at imperdiet dui accumsan sit amet. Consequat semper viverra nam libero justo laoreet sit. Quis hendrerit dolor magna eget est lorem ipsum. Eget arcu dictum varius duis at consectetur lorem. Fermentum posuere urna nec tincidunt praesent semper feugiat. Integer quis auctor elit sed vulputate mi sit amet. Ultricies integer quis auctor elit. Metus vulputate eu scelerisque felis imperdiet proin fermentum. Ut porttitor leo a diam sollicitudin tempor id eu nisl. Cras adipiscing enim eu turpis egestas. Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.

Augue eget arcu dictum varius duis at. Tempor orci eu lobortis elementum nibh. Nibh sit amet commodo nulla. At varius vel pharetra vel. In metus vulputate eu scelerisque felis imperdiet. Venenatis tellus in metus vulputate eu. Aliquam sem fringilla ut morbi tincidunt augue. Risus feugiat in ante metus dictum at tempor commodo ullamcorper. In dictum non consectetur a erat nam. Ut sem viverra aliquet eget sit. Eleifend donec pretium vulputate sapien nec sagittis aliquam. Neque viverra justo nec ultrices dui. Turpis in eu mi bibendum neque egestas. Tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla facilisi.

Semper eget duis at tellus at urna condimentum. Viverra justo nec ultrices dui sapien eget. Etiam dignissim diam quis enim lobortis scelerisque fermentum dui. Sapien nec sagittis aliquam malesuada. Ac auctor augue mauris augue neque. Enim sed faucibus turpis in eu mi bibendum neque. Proin sagittis nisl rhoncus mattis rhoncus. Vel elit scelerisque mauris pellentesque pulvinar. Aliquam etiam erat velit scelerisque in dictum. Dictum varius duis at consectetur lorem donec massa sapien. Risus at ultrices mi tempus imperdiet nulla malesuada pellentesque. Faucibus purus in massa tempor nec feugiat nisl pretium fusce.

Arcu odio ut sem nulla pharetra diam sit amet. Lorem ipsum dolor sit amet consectetur. Vitae aliquet nec ullamcorper sit amet risus nullam eget. Condimentum lacinia quis vel eros donec ac odio. Nulla posuere sollicitudin aliquam ultrices sagittis. Quis blandit turpis cursus in hac habitasse platea dictumst quisque. Amet risus nullam eget felis. Nec sagittis aliquam malesuada bibendum arcu vitae. In vitae turpis massa sed elementum tempus egestas sed sed. Netus et malesuada fames ac turpis egestas integer. Turpis tincidunt id aliquet risus feugiat. Lorem ipsum dolor sit amet consectetur adipiscing elit ut aliquam. Pretium vulputate sapien nec sagittis aliquam malesuada bibendum arcu vitae. Lectus nulla at volutpat diam ut venenatis tellus.

Lorem mollis aliquam ut porttitor leo a. Commodo elit at imperdiet dui accumsan sit amet nulla facilisi. Nec tincidunt praesent semper feugiat nibh sed. Tellus integer feugiat scelerisque varius morbi enim nunc. Euismod quis viverra nibh cras. Ipsum nunc aliquet bibendum enim facilisis gravida. Tincidunt lobortis feugiat vivamus at augue eget arcu dictum. Sodales neque sodales ut etiam sit amet nisl. Sollicitudin nibh sit amet commodo nulla facilisi. Elit ut aliquam purus sit amet luctus venenatis lectus magna. Auctor elit sed vulputate mi sit amet mauris commodo. Varius morbi enim nunc faucibus a.

Malesuada bibendum arcu vitae elementum curabitur vitae nunc sed velit. Sed sed risus pretium quam vulputate dignissim. Ipsum a arcu cursus vitae. Et magnis dis parturient montes nascetur. Arcu cursus euismod quis viverra nibh cras pulvinar mattis. Quam lacus suspendisse faucibus interdum posuere lorem ipsum dolor. Adipiscing bibendum est ultricies integer quis auctor elit sed vulputate. Odio tempor orci dapibus ultrices in iaculis. Quis imperdiet massa tincidunt nunc pulvinar sapien et. Viverra adipiscing at in tellus integer feugiat scelerisque varius morbi. Urna nec tincidunt praesent semper feugiat nibh sed. Sit amet tellus cras adipiscing enim eu turpis egestas pretium. Ut venenatis tellus in metus vulputate eu scelerisque felis. Tempus quam pellentesque nec nam. Ac placerat vestibulum lectus mauris ultrices eros in. In vitae turpis massa sed elementum tempus egestas.

Cursus in hac habitasse platea dictumst. Turpis egestas pretium aenean pharetra. Et odio pellentesque diam volutpat commodo sed egestas egestas. Dictumst quisque sagittis purus sit amet volutpat. Tortor posuere ac ut consequat semper viverra nam. Ornare arcu odio ut sem nulla pharetra diam sit amet. Sed enim ut sem viverra aliquet eget sit amet. Nam at lectus urna duis convallis convallis tellus id. Dui vivamus arcu felis bibendum ut tristique et egestas. Pretium viverra suspendisse potenti nullam ac tortor vitae purus faucibus. Quam id leo in vitae turpis massa sed elementum. Ornare arcu dui vivamus arcu felis bibendum ut tristique. Arcu non odio euismod lacinia at quis risus sed vulputate. Convallis posuere morbi leo urna molestie. Eget mi proin sed libero enim sed faucibus. Id consectetur purus ut faucibus pulvinar elementum integer enim neque. Tincidunt ornare massa eget egestas purus viverra accumsan in. Commodo quis imperdiet massa tincidunt nunc pulvinar sapien et. Risus quis varius quam quisque id diam vel. Velit ut tortor pretium viverra.

Rutrum quisque non tellus orci. Eu mi bibendum neque egestas congue quisque egestas. Massa tincidunt nunc pulvinar sapien. Ac ut consequat semper viverra nam libero justo laoreet sit. Eget gravida cum sociis natoque penatibus et. Maecenas pharetra convallis posuere morbi leo urna molestie at. Vitae tempus quam pellentesque nec nam aliquam sem et. Consectetur adipiscing elit ut aliquam purus sit amet luctus venenatis. Aliquam vestibulum morbi blandit cursus risus at ultrices mi. At in tellus integer feugiat scelerisque varius morbi enim. In tellus integer feugiat scelerisque varius. Morbi non arcu risus quis varius. Rutrum quisque non tellus orci ac auctor augue mauris augue. Dolor purus non enim praesent elementum facilisis. Ornare aenean euismod elementum nisi. Venenatis tellus in metus vulputate eu scelerisque felis imperdiet proin. Scelerisque eleifend donec pretium vulputate sapien nec sagittis aliquam malesuada. Elementum tempus egestas sed sed risus. Velit sed ullamcorper morbi tincidunt ornare massa eget. Non consectetur a erat nam.

Vel fringilla est ullamcorper eget nulla facilisi etiam dignissim. Sodales ut eu sem integer vitae justo eget. Leo urna molestie at elementum eu facilisis sed. Venenatis tellus in metus vulputate eu. Dictum fusce ut placerat orci nulla pellentesque dignissim. Ornare quam viverra orci sagittis eu volutpat odio facilisis. Feugiat nisl pretium fusce id velit ut. Sed nisi lacus sed viverra. Blandit turpis cursus in hac habitasse platea dictumst. Ut venenatis tellus in metus vulputate eu scelerisque. Neque viverra justo nec ultrices dui sapien eget mi. Hac habitasse platea dictumst quisque sagittis purus. Lorem ipsum dolor sit amet consectetur adipiscing. Venenatis lectus magna fringilla urna porttitor.

Sit amet aliquam id diam maecenas. Turpis in eu mi bibendum neque egestas. Eu consequat ac felis donec. Sit amet mattis vulputate enim nulla aliquet porttitor. Rutrum quisque non tellus orci ac auctor augue mauris augue. Turpis tincidunt id aliquet risus feugiat in ante. Massa eget egestas purus viverra accumsan. Integer vitae justo eget magna fermentum iaculis. Fringilla phasellus faucibus scelerisque eleifend donec pretium vulputate. Neque convallis a cras semper auctor neque vitae tempus. Fames ac turpis egestas sed tempus. Id consectetur purus ut faucibus. Praesent elementum facilisis leo vel fringilla est. Senectus et netus et malesuada fames. Imperdiet massa tincidunt nunc pulvinar. Egestas integer eget aliquet nibh praesent tristique magna sit. Facilisi etiam dignissim diam quis enim.

Maecenas volutpat blandit aliquam etiam erat velit scelerisque in. Consectetur adipiscing elit duis tristique sollicitudin nibh. Mattis aliquam faucibus purus in massa. Arcu cursus euismod quis viverra nibh cras pulvinar. Egestas purus viverra accumsan in. Enim sed faucibus turpis in eu. Quis varius quam quisque id diam vel. Viverra adipiscing at in tellus integer feugiat scelerisque varius. Donec ac odio tempor orci dapibus. Elit eget gravida cum sociis. Massa sapien faucibus et molestie ac feugiat sed lectus vestibulum.

Amet volutpat consequat mauris nunc congue nisi. Donec adipiscing tristique risus nec feugiat in fermentum posuere. Ipsum dolor sit amet consectetur adipiscing elit. Ullamcorper eget nulla facilisi etiam dignissim diam quis. Ut lectus arcu bibendum at varius vel pharetra. Nulla posuere sollicitudin aliquam ultrices sagittis orci a scelerisque. Enim nulla aliquet porttitor lacus luctus accumsan tortor posuere. Tempor orci eu lobortis elementum nibh tellus molestie. Donec massa sapien faucibus et molestie ac feugiat sed. Morbi tristique senectus et netus et malesuada fames. Interdum velit laoreet id donec ultrices.

Iaculis nunc sed augue lacus viverra vitae congue eu consequat. Sodales ut eu sem integer vitae. Pulvinar mattis nunc sed blandit libero volutpat sed cras. Maecenas volutpat blandit aliquam etiam erat velit scelerisque in dictum. Ultricies integer quis auctor elit sed vulputate mi. Ornare suspendisse sed nisi lacus sed viverra tellus in. Quis commodo odio aenean sed adipiscing diam donec. Platea dictumst vestibulum rhoncus est pellentesque elit. Commodo nulla facilisi nullam vehicula ipsum a arcu cursus. Ut faucibus pulvinar elementum integer enim neque volutpat. Diam quis enim lobortis scelerisque fermentum dui.

### 2023-02-09 paper1.Rmd
Adding first cut of thesis

---
title: ''
output: pdf_document
header-includes:
  - \usepackage{float}

---

# Chapter 1: Quantifying the global burden of mental disorders and their economic value

\begin{raggedright}

{\bf Background:} Epidemiological and economic estimates suggest that the global burden of mental disorders is considerable, both in its impacts on human health and losses to societal welfare. The availability of additional data and the emergence of new approaches present an opportunity to examine these estimates, which form a critical part in making the investment case for global mental health.

{\bf Methods:} This study reviews, develops, and incorporates new estimates and methods in quantifying the global burden of mental illness. Using a composite estimation approach that accounts for premature mortality due to mental disorders and additional sources of morbidity and applying a value of a statistical life approach to economic valuation, we determine global and regional estimates of the economic cost that can be associated with mental disorders, building on data from the 2019 Global Burden of Disease study.

{\bf Findings:} We estimate that 418 million disability-adjusted life years (DALYs) could be attributable to mental disorders in 2019 (16\% of global DALYs)—a more than three-fold increase compared to conventional estimates. The economic value associated with this burden is estimated at about USD 5 trillion. At a regional level, the losses could account for between 4\% of gross domestic product in Eastern sub-Saharan Africa and 8\% in High-income North America.

{\bf Interpretation:} The burden of mental illness in terms of both health and economic losses may be much higher than previously assessed.

{\bf Funding:} None.

\vspace{24pt}

\emph{Keywords: mental health, disease burden, premature mortality, economic burden.}

\end{raggedright}

\newpage

## Introduction

Mental health is an essential part of human flourishing. As defined by the World Health Organization (WHO), it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community.[@worldhealthorganizationComprehensiveMentalHealth2013]” For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are both leading causes of disability and significant risk factors for premature mortality.[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] At all levels of sociodemographic development, this burden of morbidity and mortality is rising.[@patelLancetCommissionGlobal2018] Furthermore, as the COVID-19 pandemic continues, there is growing and alarming evidence of its detrimental psychological and psychiatric effects—for patients, health care workers, and the public overall.[@vindegaardCOVID19PandemicMental2020]

The magnitude of disability caused by mental disorders has galvanized a global movement and a call to action for greater investment and prioritization for mental health.[@patelRenewedAgendaGlobal2011] This movement has emphasized the importance of investing in mental health as a means of promoting sustainable development, human rights, and social inclusion.[@patelLancetCommissionGlobal2018]

A critical link between mental health and development arises from the economic consequences of mental disorders. A growing body of literature suggests that mental disorders are costly, both in the direct medical costs of care, outpatient visits, and hospitalizations, and in indirect costs, such as losses in income and productivity due to disability, which may cause absenteeism and presenteeism.[@trautmannEconomicCostsMental2016] These costs further worsen conditions of poverty[@patelPovertyCommonMental2003]—a vulnerability that, in turn, worsens mental health, feeding a vicious cycle of poverty and illness.[@lundPovertyCommonMental2010] At the national level, mental disorders deplete the supply of labor and capital, resulting in poorer economic output.[@canavanPsychologicalDistressGhana2013] Among households and nations alike, the burden of mental illness thus has considerable economic consequences and poses a challenge to both health and wealth.

Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This study used three distinct approaches to quantify the economic burden of non-communicable diseases (NCDs), including mental illnesses.[@bloomGlobalEconomicBurden2011] The first is a cost-of-illness (COI) analysis, which includes the direct costs of illness as well as the indirect costs (e.g., lost productivity). The second is a value of lost output approach, which estimates the effects of illness on gross domestic product (GDP) due to the depletion of labor and capital. The third builds from value of a statistical life (VSL) approaches and attempts to capture a population’s willingness to pay to reduce morbidity and mortality associated with illness. This expands on the COI and value of lost output approaches, as it puts an economic value on the loss of health itself.

With a third of disability-adjusted life years (DALYs) due to NCDs arising from mental disorders, this landmark paper estimated that the value of losses due to mental disorders was roughly 1·3 trillion USD in 2010 (1·6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2·5 trillion USD 2010 (or approximately 3·0 trillion USD in 2019) by 2030. (See Supplementary appendix Tables S1 and S2 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]

While the estimates presented from this paper remain staggering and salient, new studies estimating the morbidity and mortality associated with mental illness have since become available.[@gbd2019mentaldisorderscollaboratorsGlobalRegionalNational2022; @vigoEstimatingTrueGlobal2016; @walkerMortalityMentalDisorders2015] These studies suggest that previous (and current) estimates of the global burden of mental disorders may be considerably underestimated, which, in turn, has implications for estimating the true economic burden of mental illness.

The most recent estimates of morbidity and mortality due to mental disorders come from the Global Burden of Disease (GBD) 2019 study.[@vosGlobalBurden3692020a] The GBD study provides disease burden estimates using DALYs, years of life lost (YLLs), and years lived with disability (YLDs), which are then aggregated within a hierarchical grouping scheme that classifies causes of disability and death at different levels of mutually exclusive and completely exhaustive categories. (Mental disorders are a Level 2 condition, nested under NCDs; see Table S3.)

While GBD remains the gold standard for global epidemiologic estimation, the nature of the GBD scheme—in particular, the rationale for grouping certain conditions under mental disorders or not—has been the subject of debate in the literature.[@atunChallengesEstimatingTrue2016; @vigoEstimatingTrueGlobal2016; @whitefordChallengesEstimatingTrue2016] In particular, work by Vigo et al. (2016) published in The Lancet Psychiatry argues for an expanded classification of mental disorders under the GBD classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders. Using data from the 2013 GBD study, Vigo and colleagues re-allocated the entire burden of dementias, epilepsy, migraine, tension-type headache, and self-harm to mental disorders. In addition, a third of the burden of musculoskeletal disorders without anatomical correlate (i.e., somatoform disorders with prominent pain) was attributed to mental disorders.[@vigoEstimatingTrueGlobal2016] This reallocation attributed 13% of DALYs to mental disorders, a 6 percentage point increase from the GBD estimate of 7%.

In this paper, we attempt to revisit the estimation of the global burden of mental disorders and of its associated economic value. Our aim is to characterize potential underestimation of the burden of mental disorders and to quantify the economic value of this burden under different estimation approaches. Specifically, we expand on Vigo et al.[@vigoEstimatingTrueGlobal2016] by capturing premature mortality due to mental disorders using pooled risk ratios of mortality from a systematic review of mental disorders[@walkerMortalityMentalDisorders2015] to determine the population attributable fraction (PAF) of premature mortality. Inclusion of premature mortality through the PAF presents a novel composite approach that can more broadly capture attributable morbidity and mortality. Using this approach on GBD 2019 estimates, we then apply monetary values to DALYs to reach estimates of the global economic value of the mental burden of disease using a VSL approach. The VSL approach—in contrast to COI and VLO approaches—includes an economic valuation of mortality risk reductions in monetary terms, and thus enables comparison across sectors (beyond the sole health sector) which can motivate decision-making toward ameliorating welfare and societal mental health. Our findings suggest that both the epidemiological and economic burden of mental disorders could be larger than previously estimated, and that underestimation would be larger among regions where premature mortality due to mental disorders is greater.

## Methods

To estimate the economic burden of mental disorders, we first estimate the attributable mental burden of DALYs under various estimation approaches using data from the 2019 GBD study (available from the Global Health Data Exchange at https://ghdx.healthdata.org/gbd-2019). Second, we apply a monetary value to a DALY to yield an economic assessment associated with these burden estimates.

### Burden of mental disorders

In our analysis, we replicate the approach of Vigo et al. (2016) using GBD 2019 estimates, applying a similar re-allocation formula to YLLs, YLDs, DALYs, and deaths. Our approach, however, differs in some key respects.

First, we agree with Whiteford and colleagues in viewing the assigning of the entire burden of suicide and self-harm to mental disorders as an overestimate, and consequently do not reallocate all DALYs due to suicide towards the mental health burden.[@whitefordChallengesEstimatingTrue2016] While it is empirically clear that mental disorders elevate the risk of death by suicide and that the majority of suicides appear to be due to mental disorders,[@bertoloteSuicidePsychiatricDiagnosis2002] we view assigning the entirety of this burden to mental disorders as overinclusive, which we avoid to favor a conservative estimation strategy.

Second, we attempt to capture premature mortality attributable to mental disorders, recognizing that persons with mental disorders are at elevated risk of all-cause mortality,[@walkerMortalityMentalDisorders2015] unnatural death,[@crumpMentalDisordersRisk2013] and deaths due to natural causes.[@coltonCongruenciesIncreasedMortality2006] Not capturing this share of mortality is likely to be a prominent cause of underestimating the burden of mental illness, particularly in countries where the dominant share of the DALY burden is mortality (rather than morbidity).

Following Vigo and colleagues, we replicate reallocations in neurological and musculoskeletal conditions, and further include alcohol and mental use disorders, as these were previously classified under mental disorders within the GBD classification.

This provides estimates of YLDs due to mental disorders. We then estimate the PAF of mortality due to mental disorders, using GBD prevalence estimates and relative risk estimates for natural-cause and unnatural-cause mortality generated from a systematic review and meta-analysis by Walker et al.[@walkerMortalityMentalDisorders2015] A comparison of our allocation approach with those of Vigo et al. and the original GBD hierarchical allocation is shown in Table 1.

Our approach to capturing premature mortality relies on a pooled relative risk estimate for mortality by natural and unnatural causes, drawn from 148 studies identified by Walker et al.[@walkerMortalityMentalDisorders2015] These studies collectively reflect over 338,000 deaths across 29 countries and 6 continents. The majority of deaths (67%) recorded in studies with disaggregated data arose from acute and chronic illnesses, while unnatural causes such as injury and suicide represented 18% of deaths (the rest being unallocated). Overall, the pooled risk of all-cause mortality was 2·2 times higher (95% confidence interval (CI): 2·1-2·3) among people with mental disorders compared to those without. Using this relative risk estimate, Walker and colleagues calculated a PAF to estimate that 8 million deaths were due to mental disorders in 2012.

While Walker and colleagues used a global estimate of the worldwide prevalence of mental disorders in their study to calculate the PAF, we use GBD estimates of prevalence to derive both global- and country-level results. The PAF for a given disorder d and country c is given by:
\[ PAF_{(d,c)}= \frac{p_{(d,c)}\ (RR_d-1)}{1+p_{(d,c)}\ (RR_d-1)}\ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (1)\]

where $p_{d,c}$ is the prevalence of a given disorder in a country and $RR_d$ is the relative risk of mortality estimated by Walker et al.[@walkerMortalityMentalDisorders2015]

We separately estimate the PAF for natural and unnatural causes of mortality. Using the calculated PAF estimates, we estimate YLLs attributable to mental disorders by multiplying the PAF by the national burden of mortality. For natural causes of death, we conservatively apply the PAF against YLLs attributable to NCDs. For unnatural causes of death, we apply the PAF against YLLs due to self-harm and injuries. These YLLs are then combined with the YLDs calculated previously to provide DALYs.

### Economic burden of disease

To estimate the economic cost associated with premature mortality and morbidity tied to mental illnesses, we assigned a monetary value to attributable DALYs. VSL approaches assign a monetary value to small reductions in mortality risks.[@robinsonValuingMortalityRisk2019] Drawing from these approaches, Jamison and colleagues have estimated monetary values of statistical life years,[@jamisonGlobalHealth20352013] which Khadka and colleagues recently adapted to quantify the economic value of changing mortality risk by cause of death in low- and middle-income countries (LMICs).[@khadkaEconomicValueChanging2021] While VSL approaches are not meant to assign monetary values to full life years or years lived with illness or disability,[@robinsonValuingMortalityRisk2019] the Copenhagen Consensus has previously implemented the use of GDP per capita as a proxy for the monetary value of a DALY as a standard estimate.[@copenhagenconsensuscenterMethodology] Values of one and three times GDP per capita have been suggested as proxies for the value of a DALY.[@bertramCostEffectivenessThresholds2016; @commissiononmacroeconomicsandhealthMacroeconomicsHealthInvesting2001] Estimates of $1,000 and $5,000 per DALY have been used, with the justification that these would be reasonable and convenient lower and upper values, particularly for low-income and lower-middle income countries.[@jamisonInfectiousDiseaseInjury2013; @jhaBenefitsCostsHealth2018]

Consistent with previous approaches, we use GDP per capita (USD 2019) for our base-case value of a DALY. GDP inputs are reported in 2019 USD and obtained from the World Bank’s World Development Indicators; for consistency with our epidemiological inputs, we convert to per capita values using GBD population estimates.

### Sensitivity analyses

The primary focus of this paper concerns structural uncertainty in determining the burden of mental illness, resulting in the evaluation of three different estimation approaches. To address parameter uncertainty within each approach, we apply a three-way sensitivity analysis. First, following a simple intuitive approach, we incorporate the upper and lower uncertainty intervals (UIs) provided by GBD 2019 for YLLs, YLDs, and DALYs to account for parameter uncertainty. Second, we use the upper and lower values of prevalence estimates and of the 95% confidence intervals (CIs) of the pooled relative risk of all-cause mortality from Walker and colleagues in our composite approach.[@walkerMortalityMentalDisorders2015] Third, our lower bound estimates are set to reallocate one sixth of the burden of musculoskeletal disorders proposed by Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] while our upper bound estimates are set to reallocate one half of this burden.

In addition to our base-case economic valuation, we further report our VSL estimates using three times GDP per capita as the value of a DALY. (Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S5 and S6 of the Supplementary appendix.)

### Statistical analysis

All computations were conducted using R software (version 3·6·2).

### Ethics statement

The research draws exclusively on secondary country-level data reported at the national or subnational level. As such, it does not involve data collection, experimentation, or investigation concerning human subjects. The Institutional Review Board (IRB) of the Harvard T.H. Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol # IRB20-1946, determined on November 13, 2020).

### Role of funding source

This study received no funding. All authors (DA, SV, and SS) had access to the data and shared in the decision to submit this article for publication.

## Results

Under GBD 2019, over 125 million DALYs were attributed to mental disorders, or roughly 5% of the global burden. After including alcohol and drug use, neurological disorders, chronic pain, suicide, and self-harm, the share due to mental disorders rose to 12% of global DALYs (approximately 321 million DALYs). Under the composite approach, an additional 97 million DALYs were attributed to mental disorders, encompassing, in total, over 16% of global DALYs. Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising over twice the burden of disease in high-income countries compared to low-income countries.

Rates of DALYs and deaths attributable to mental disorders under the different estimation approaches are presented by GBD region (Figure 1). Geographically, the composite approach allocated a large portion of DALYs (to mental disorders) in Eastern Europe, North and Latin America, and sub-Saharan Africa. This is largely driven by the inclusion of premature mortality in the composite approach. Estimates of DALYs by country income group and GBD region are reported in Table 2. (Estimates of deaths are reported in Table S4-6.)

Under the three approaches, we calculated the economic value of mental disorder losses (Table 3). Using GDP per capita as a proxy for the value per DALY, economic losses due to mental disorders were estimated at 4·7 trillion USD using our composite approach. This estimate is 1·1 trillion USD larger than that reached using the 2016 reallocation approach and over 3·3 trillion USD larger than that reached from the unadjusted GBD 2019 estimates. Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7·2 trillion international dollars in 2019 (Table S7).

Although economic losses do not represent an actual loss to GDP, a sense of the scale can be gained by expressing the economic consequences with respect to GDP. Figure 2 displays the economic burden of disease due to mental disorders under the three estimation approaches by GBD region, as a percent of regional GDP. (Estimates by absolute values per DALY are provided in the Supplementary appendix, along with mapped data visualizing estimates across all values per DALY.) Across approaches, the greatest change in estimated burden occurs in Eastern Europe, Latin America, North America, and Southern sub-Saharan Africa. Under the relative GDP-per-capita values the economic burden would account for between 4% of GDP in Eastern Sub-Saharan Africa and 8% in High-income North America under our composite approach.

## Discussion

This study explores possible alternative approaches to estimating the global burden of mental illness and the economic losses thereof. In particular, we propose a composite approach to address contention in the classification of mental disorders. This approach suggests that the global DALYs attributable to mental disorders could exceed 400 million per year, or 16% of the total burden.

When applied against an economic value per DALY of one times GDP per capita, this approach further suggests that the per year losses associated with this burden could exceed 4·7 trillion USD in 2019. When adjusting for the uncertainty in estimates of the attributable burden of disease, the losses could range from 3·1 trillion to more than 6·9 trillion USD. Adjusting for purchasing power parity would increase the magnitude of these estimates, with ranges from 4·8 to 10·6 trillion international dollars at the global scale.

Put in context of the existing literature, our epidemiological and economic estimates provide two important contributions. First, our findings echo in magnitude those of Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] which have highlighted that suicide and premature mortality due to mental disorders are potentially large sources of underestimation in the current GBD classification. Second, when including these sources of attributable mortality, the economic findings suggest staggering loses. We estimate that in 2019, the losses would already be over 1·8 trillion USD greater than Bloom and colleagues’ global losses projections for 2030 (2·9 trillion 2019 USD, using the same value per DALY approach).[@bloomGlobalEconomicBurden2011]

Our findings add to a growing literature concerning the classification of mental disorders, in particular related to underscoring the importance of including premature mortality attributable to mental disorders in burden conceptualizations.[@vigoBurdenMentalNeurological2020; @vigoEstimatingTrueGlobal2016; @vigoTrueGlobalDisease2022; @whitefordChallengesEstimatingTrue2016] These calls have most recently been emphasized by GBD collaborators who have urged that “the differential mortality gap for individuals with mental disorders needs to be reflected within the GBD framework.”[@gbd2019mentaldisorderscollaboratorsGlobalRegionalNational2022] Our composite approach to assigning attributable mortality presents one potential attempt for acknowledging this differential mortality gap. Our economic analysis further provides updated monetary estimates of the burden of mental illness; to our knowledge, this is the first such analysis of the global economic burden of mental disorders in over a decade.

Our results should, however, be interpreted with several limitations in mind. First, our estimation approaches themselves all draw upon modeled data (i.e., GBD estimates). While GBD generates descriptions of morbidity and mortality at fine demographic and geographic levels, it is important to emphasize that the sophisticated modeling approaches implemented often draw on (potentially little) available underlying empirical data.[@tichenorMetricPartnershipsGlobal2020] These inputs can be extremely limited for particular diseases and geographical locations, especially so for mental disorders. By way of example, the GBD 2019 Data Input Sources Tool retrieves 3,084 separate data sources for mental disorders. Of these, only 60 pertain to sub-Saharan Africa (1·9%) and 58 to South Asia (1·8%).[@instituteforhealthmetricsandevaluationihmeGlobalBurdenDisease] By comparison, of the 6,064 records pertaining to maternal and neonatal disorders, 631 are for sub-Saharan Africa (10·4%) and 270 for South Asia (4·5%). These severely limited inputs reflect a dearth of global mental health data; as of 2017, the World Mental Health survey initiative had conducted interviews in just 26 countries, only 13 of which were classified as low- or middle-income.[@steinCrossnationalEpidemiologySocial2017]

Relatedly, our composite approach relies on pooled estimates of the relative risk of mortality from a systematic review and meta-analysis that itself is limited by the available data it draws upon[@walkerMortalityMentalDisorders2015]. The review identified 203 studies for inclusion, of which only two were located in Africa, 16 in Asia, and one in South America. While the authors found that the estimates of mortality risk did not vary by region, the limited representation of studies from the world’s most populous and epidemiologically diverse continents is a considerable shortcoming. It is possible, for instance, that the relative risk of all-cause mortality associated with mental disorders is lower where the burden of mortality is more heavily concentrated among child, maternal, and infectious diseases, and is higher where the burden is dominated by NCDs. Therefore, to reach a conservative estimate of attributable mortality, we separately estimated population attributable fractions for natural and unnatural causes of death and restricted our allocation of YLLs from natural causes to NCDs—meaning no deaths from maternal or infectious diseases were attributed to mental disorders under the composite approach.

Furthermore, our composite approach allocates mortality due to mental disorders by calculating population attributable fractions using the conventional formula, which may be biased in the presence of confounding or effect heterogeneity.[@darrowConfoundingBiasAttributable2011] In particular, the use of adjusted risk ratios (as in the current analysis) may result in anticonservative bias if the crude risk ratios are lower than the adjusted ones. To mitigate the potential for bias, our sensitivity analysis presents results under conservative assumptions for risk ratios and estimates of prevalence and mortality.

Despite these limitations, our findings underscore both that the true burden of mental disorders may only partially be captured by current estimation approaches, and that, consequently, the associated economic losses may be much higher than previously estimated. We note that our findings may themselves be an underestimate, as our composite approach excludes deaths due to neonatal, maternal, and infectious diseases attributable to mental disorders. However, we observe that conventional estimation approaches may fail to capture large shares of premature mortality attributable to mental health causes, both from self-inflicted and unnatural causes of death and mortality from NCDs. Capturing this share of the burden emphasizes that mental health is a critical risk factor for premature mortality, as well as a direct source of morbidity.

The magnitude of economic costs associated with mental disorders raises the need for health economics research, particularly on returns on investment and costing for effective prevention and treatment strategies.[@patelAddressingBurdenMental2016] Further work is also needed to strengthen the measurement of the global burden of mental illness, not only for more fully capturing the morbidity and mortality of mental disorders, but also for incorporating the impacts of new and evolving threats—such as pandemics, conflicts and climate change—to population mental health.

Our study highlights that mental health—far from being an issue solely concentrated in high-income regions alone— is a major global issue, one that imposes a significant toll to health and welfare. The large magnitude of these twin burdens highlights the urgency for global action to support mental health financing and to bolster its prioritization.

## Acknowledgements

We thank David Bloom, Goodarz Danaei, and Daniel Vicente Vigo for their feedback on an earlier version of the paper, as well as five anonymous reviewers for their valuable and constructive comments on our manuscript. This study received no funding.

### Author conntributors

All authors contributed to study conception, methodology, and interpretation. DA oversaw data acquisition, programming, formal analysis, visualization, the first draft of the manuscript. All authors contributed to critical revision of the manuscript, with responses to reviewers and subsequent revisions led by DA. All authors had access to and verified all the data and accept responsibility for the decision to submit for publication.

### Declaration of interests

We declare no competing interests.

### Data sharing statement

GBD estimates are available for download from the Global Health Data Exchange and are available freely for non-commercial users under the Open Data Commons Attribution License (https://ghdx.healthdata.org/gbd-2019). All codes used for the analysis in this article are available on GitHub (https://github.com/darias5/gmh_econ).

### 2023-02-09 thesis.Rmd
Adding first cut of thesis

--- 2023-02-09 intro.Rmd
@@
 ---
-title: ''
-output: pdf_document
-indent: yes
+title: " "
+output:
+    pdf_document:
+        number_sections: TRUE
+
+geometry: margin=1in
+fontsize: 12pt
+indent: true
+header-includes:
+  - \usepackage{float}
+  - \usepackage{sectsty}
+  - \usepackage{setspace}\spacing{2}
+  - \usepackage{fancyhdr}
+  - \usepackage{lastpage}
+  - \usepackage{dcolumn}
+  # - \usepackage{natbib}\bibliographystyle{agsm}
+  # - \usepackage[nottoc]{tocbibind}
+
+bibliography: bibliography.bib
+
 ---
-\section*{Introduction}
 
-\addcontentsline{toc}{section}{Introduction}
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Lacinia quis vel eros donec ac odio tempor.
-Urna nec tincidunt praesent semper feugiat nibh.
-Tortor aliquam nulla facilisi cras fermentum odio eu feugiat.
-Magna ac placerat vestibulum lectus mauris ultrices eros.
-Pulvinar proin gravida hendrerit lectus.
-Nisi scelerisque eu ultrices vitae auctor eu.
-Quis hendrerit dolor magna eget est lorem ipsum.
-At consectetur lorem donec massa sapien faucibus et molestie.
-Feugiat in fermentum posuere urna nec tincidunt praesent.
-Facilisis gravida neque convallis a cras.
-Massa id neque aliquam vestibulum morbi blandit.
-Faucibus purus in massa tempor nec feugiat nisl pretium fusce.
-Amet facilisis magna etiam tempor orci eu lobortis.
-Odio tempor orci dapibus ultrices in iaculis nunc sed augue.
-Nulla aliquet porttitor lacus luctus accumsan tortor posuere ac ut.
-Sit amet aliquam id diam maecenas.
-Rhoncus aenean vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant.
-Urna nunc id cursus metus aliquam.
+```
 
-Arcu odio ut sem nulla pharetra diam sit.
-Adipiscing bibendum est ultricies integer.
-Accumsan lacus vel facilisis volutpat est.
-Turpis egestas sed tempus urna et pharetra pharetra.
-Est placerat in egestas erat imperdiet.
-Blandit aliquam etiam erat velit scelerisque in dictum non.
-Semper eget duis at tellus at urna condimentum.
-Tellus cras adipiscing enim eu turpis egestas.
-Vitae ultricies leo integer malesuada nunc vel.
-Sapien pellentesque habitant morbi tristique senectus et.
+\allsectionsfont{\centering\normalsize}
+\subsectionfont{\raggedright}
+\subsubsectionfont{\raggedright}
+\pagenumbering{roman}
+\pagestyle{empty}
 
-Diam maecenas ultricies mi eget mauris pharetra.
-In arcu cursus euismod quis viverra nibh.
-Erat imperdiet sed euismod nisi porta.
-Ultricies mi eget mauris pharetra.
-Donec et odio pellentesque diam volutpat commodo.
-Vulputate sapien nec sagittis aliquam malesuada bibendum arcu.
-In eu mi bibendum neque egestas congue quisque egestas diam.
-Tortor dignissim convallis aenean et.
-Aliquam ut porttitor leo a diam sollicitudin.
-Cursus turpis massa tincidunt dui ut ornare lectus.
-Rhoncus mattis rhoncus urna neque.
-Enim blandit volutpat maecenas volutpat blandit.
-Egestas tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla.
-Adipiscing commodo elit at imperdiet dui accumsan sit amet.
-Pharetra massa massa ultricies mi quis.
-Quam pellentesque nec nam aliquam.
+\begin{centering}
 
-At tempor commodo ullamcorper a.
-Commodo viverra maecenas accumsan lacus vel facilisis volutpat est.
-Sed arcu non odio euismod lacinia at.
-Turpis nunc eget lorem dolor sed viverra ipsum.
-Malesuada fames ac turpis egestas.
-Et ultrices neque ornare aenean euismod elementum.
-Quisque egestas diam in arcu cursus euismod quis viverra nibh.
-Semper eget duis at tellus.
-Id diam maecenas ultricies mi eget mauris pharetra.
-Eget nunc scelerisque viverra mauris in aliquam sem fringilla.
-Sit amet massa vitae tortor condimentum lacinia quis vel.
-Ut faucibus pulvinar elementum integer enim neque.
-Amet justo donec enim diam vulputate.
-Cursus eget nunc scelerisque viverra.
-Gravida dictum fusce ut placerat orci nulla pellentesque.
-Purus semper eget duis at tellus at urna condimentum mattis.
-Ante in nibh mauris cursus mattis molestie a iaculis.
-Tincidunt augue interdum velit euismod.
-Urna nec tincidunt praesent semper feugiat nibh sed pulvinar.
-Tellus integer feugiat scelerisque varius morbi enim nunc.
+\vspace*{24pt}
 
-Felis eget velit aliquet sagittis id.
-Lacus laoreet non curabitur gravida arcu ac.
-Id diam vel quam elementum.
-Lacinia at quis risus sed vulputate odio ut enim blandit.
-Platea dictumst vestibulum rhoncus est pellentesque elit ullamcorper.
-Nunc aliquet bibendum enim facilisis.
-Viverra mauris in aliquam sem fringilla ut morbi.
-Eu lobortis elementum nibh tellus molestie nunc non blandit.
-Ut enim blandit volutpat maecenas volutpat blandit aliquam.
-Non odio euismod lacinia at quis risus sed vulputate.
+\large
 
-Libero id faucibus nisl tincidunt eget.
-Odio aenean sed adipiscing diam donec.
-Porta nibh venenatis cras sed felis eget velit aliquet.
-Enim nunc faucibus a pellentesque sit amet porttitor.
-Elementum nisi quis eleifend quam adipiscing vitae proin.
-Eget sit amet tellus cras adipiscing enim.
-In ante metus dictum at tempor commodo ullamcorper.
-Feugiat in fermentum posuere urna nec tincidunt praesent.
-Amet justo donec enim diam.
-In massa tempor nec feugiat.
-Mattis rhoncus urna neque viverra justo nec ultrices dui sapien.
-Tellus cras adipiscing enim eu turpis.
-Scelerisque eu ultrices vitae auctor.
-Viverra maecenas accumsan lacus vel facilisis.
-Donec et odio pellentesque diam volutpat commodo.
-Congue nisi vitae suscipit tellus mauris a.
-A scelerisque purus semper eget duis at tellus at urna.
+{\bf `r toupper("Quantitative Approaches Towards Evaluating the Global Burden of Mental Illness")`}
 
-Mauris augue neque gravida in fermentum et sollicitudin ac orci.
-Rutrum quisque non tellus orci ac.
-Diam ut venenatis tellus in metus vulputate eu.
-Amet nisl suscipit adipiscing bibendum est ultricies integer quis.
-Velit euismod in pellentesque massa placerat duis ultricies lacus sed.
-Suspendisse potenti nullam ac tortor.
-Porttitor rhoncus dolor purus non enim praesent.
-Tortor consequat id porta nibh venenatis cras sed felis.
-Mattis rhoncus urna neque viverra justo nec ultrices dui.
-Eget lorem dolor sed viverra ipsum nunc aliquet.
+\vspace{12pt}
 
-Sed ullamcorper morbi tincidunt ornare.
-Gravida rutrum quisque non tellus.
-Metus aliquam eleifend mi in.
-Sollicitudin aliquam ultrices sagittis orci a scelerisque.
-Ullamcorper velit sed ullamcorper morbi.
-Cras sed felis eget velit aliquet.
-Libero enim sed faucibus turpis in.
-Molestie ac feugiat sed lectus vestibulum mattis ullamcorper velit.
-Viverra orci sagittis eu volutpat odio facilisis mauris sit amet.
-Dignissim sodales ut eu sem integer vitae.
+\normalsize
 
-Posuere urna nec tincidunt praesent.
-Et tortor consequat id porta nibh.
-Elit duis tristique sollicitudin nibh sit amet commodo nulla.
-Iaculis nunc sed augue lacus.
-Pulvinar pellentesque habitant morbi tristique senectus et.
-Integer quis auctor elit sed vulputate mi.
-Interdum posuere lorem ipsum dolor sit amet consectetur adipiscing elit.
-Ultricies tristique nulla aliquet enim tortor.
-Vivamus arcu felis bibendum ut tristique et egestas quis ipsum.
-Id eu nisl nunc mi.
-Eget nullam non nisi est sit amet facilisis magna.
-Quis ipsum suspendisse ultrices gravida.
-Blandit turpis cursus in hac habitasse platea dictumst quisque.
-Vulputate mi sit amet mauris commodo quis imperdiet.
-Pretium fusce id velit ut.
-Libero enim sed faucibus turpis.
-Massa eget egestas purus viverra accumsan.
+by
 
-Quis imperdiet massa tincidunt nunc pulvinar sapien et ligula ullamcorper.
-Diam phasellus vestibulum lorem sed risus ultricies tristique.
-Orci eu lobortis elementum nibh tellus molestie.
-Ornare aenean euismod elementum nisi.
-Rhoncus urna neque viverra justo.
-Dignissim cras tincidunt lobortis feugiat vivamus.
-Fusce id velit ut tortor pretium viverra.
-Quis vel eros donec ac odio.
-Tellus id interdum velit laoreet.
-Maecenas accumsan lacus vel facilisis.
-Cursus mattis molestie a iaculis at erat.
-Nibh mauris cursus mattis molestie.
-Pellentesque diam volutpat commodo sed egestas.
-Et netus et malesuada fames ac turpis egestas integer eget.
+\vspace{12pt}
 
-Consequat interdum varius sit amet mattis vulputate enim nulla aliquet.
-Aliquam id diam maecenas ultricies mi eget mauris pharetra.
-Porttitor eget dolor morbi non arcu.
-Eleifend donec pretium vulputate sapien nec sagittis aliquam malesuada.
-Viverra ipsum nunc aliquet bibendum enim.
-Egestas purus viverra accumsan in nisl nisi.
-Quam elementum pulvinar etiam non quam lacus.
-Non enim praesent elementum facilisis leo.
-Eget velit aliquet sagittis id consectetur.
-Leo integer malesuada nunc vel risus commodo viverra.
-Nulla facilisi etiam dignissim diam.
-Id diam maecenas ultricies mi eget.
-Arcu felis bibendum ut tristique et.
-Nunc lobortis mattis aliquam faucibus purus.
-Semper auctor neque vitae tempus.
+{\ Daniel Arias}
 
-Est ultricies integer quis auctor elit sed vulputate mi.
-Bibendum at varius vel pharetra vel turpis.
-Risus viverra adipiscing at in tellus.
-Volutpat maecenas volutpat blandit aliquam etiam erat.
-Cras sed felis eget velit aliquet sagittis id consectetur purus.
-Dignissim diam quis enim lobortis scelerisque fermentum dui faucibus in.
-Vivamus arcu felis bibendum ut tristique et egestas.
-Porttitor eget dolor morbi non.
-Ut pharetra sit amet aliquam id diam maecenas ultricies.
-Viverra nam libero justo laoreet sit amet.
-Egestas diam in arcu cursus euismod quis viverra nibh cras.
-Non nisi est sit amet facilisis.
-Dictumst vestibulum rhoncus est pellentesque elit.
-Ipsum consequat nisl vel pretium lectus.
-Nunc sed velit dignissim sodales ut eu.
-Ipsum suspendisse ultrices gravida dictum.
-Orci sagittis eu volutpat odio facilisis.
-Lobortis feugiat vivamus at augue eget arcu dictum varius.
-Bibendum ut tristique et egestas.
-Tincidunt ornare massa eget egestas purus viverra accumsan in.
+\vspace{24pt}
 
-Arcu odio ut sem nulla.
-Porttitor massa id neque aliquam.
-Sed felis eget velit aliquet sagittis id consectetur purus.
-Lacus vestibulum sed arcu non odio euismod lacinia at.
-Varius sit amet mattis vulputate enim nulla aliquet.
-Scelerisque mauris pellentesque pulvinar pellentesque habitant morbi tristique.
-Morbi enim nunc faucibus a pellentesque sit amet.
-Varius quam quisque id diam vel quam elementum.
-Commodo nulla facilisi nullam vehicula ipsum a arcu cursus.
-Diam donec adipiscing tristique risus nec feugiat in fermentum.
-Blandit turpis cursus in hac habitasse platea dictumst.
-Ante in nibh mauris cursus mattis molestie.
-Sed adipiscing diam donec adipiscing tristique risus nec.
+A dissertation submitted to the faculty of \\
+the Harvard T.H. Chan School of Public Health\\
+in partial fulfillment of the requirements\\
+for the degree of \emph{Doctor of Philosophy}\\
+in the Department of Global Health and Population
 
-Amet facilisis magna etiam tempor orci eu lobortis elementum nibh.
-Eget dolor morbi non arcu risus quis varius quam.
-Consequat id porta nibh venenatis cras sed.
-Pretium nibh ipsum consequat nisl vel.
-Feugiat nibh sed pulvinar proin gravida hendrerit.
-Risus sed vulputate odio ut enim blandit volutpat.
-Sem integer vitae justo eget magna fermentum iaculis.
-Consequat semper viverra nam libero justo laoreet sit amet.
-Arcu felis bibendum ut tristique et egestas.
-Proin fermentum leo vel orci porta.
-Aliquam malesuada bibendum arcu vitae elementum.
-Consectetur adipiscing elit duis tristique sollicitudin nibh.
-Non quam lacus suspendisse faucibus interdum posuere lorem ipsum.
-Ullamcorper velit sed ullamcorper morbi tincidunt ornare massa.
-Risus commodo viverra maecenas accumsan lacus vel facilisis volutpat.
-Ut etiam sit amet nisl.
-Urna condimentum mattis pellentesque id nibh tortor id aliquet lectus.
-Ornare massa eget egestas purus viverra accumsan.
+\vspace{36pt}
 
-Auctor augue mauris augue neque gravida in fermentum et.
-Lectus mauris ultrices eros in cursus turpis.
-Commodo elit at imperdiet dui accumsan sit.
-Eget nulla facilisi etiam dignissim diam quis enim lobortis scelerisque.
-Volutpat est velit egestas dui id.
-Nunc eget lorem dolor sed viverra ipsum.
-Nullam ac tortor vitae purus faucibus ornare suspendisse sed nisi.
-Justo donec enim diam vulputate ut.
-Sodales ut etiam sit amet nisl purus.
-Congue nisi vitae suscipit tellus.
-Mauris cursus mattis molestie a.
-Pellentesque id nibh tortor id aliquet.
-Porta non pulvinar neque laoreet suspendisse interdum consectetur libero id.
-Diam vulputate ut pharetra sit.
-Placerat vestibulum lectus mauris ultrices eros in cursus.
-A arcu cursus vitae congue mauris rhoncus aenean.
+Harvard University \\
+Boston, Massachusetts
 
-Nisi vitae suscipit tellus mauris a diam.
-Aenean et tortor at risus viverra adipiscing at.
-Ultrices eros in cursus turpis massa tincidunt.
-Euismod lacinia at quis risus sed.
-Egestas diam in arcu cursus euismod quis.
-Eu lobortis elementum nibh tellus molestie nunc non.
-Ornare arcu odio ut sem nulla pharetra diam.
-Senectus et netus et malesuada fames.
-Condimentum vitae sapien pellentesque habitant morbi.
-Diam sit amet nisl suscipit.
-Porta lorem mollis aliquam ut porttitor leo a.
-Sed risus pretium quam vulputate dignissim suspendisse in est ante.
-Risus pretium quam vulputate dignissim suspendisse in est.
-Pellentesque eu tincidunt tortor aliquam.
-Amet consectetur adipiscing elit pellentesque habitant.
-Mattis pellentesque id nibh tortor.
-Purus faucibus ornare suspendisse sed.
-Id venenatis a condimentum vitae.
-Ipsum a arcu cursus vitae.
-Pretium fusce id velit ut.
+\vspace{36pt}
 
-Feugiat scelerisque varius morbi enim nunc.
-Mattis vulputate enim nulla aliquet porttitor lacus.
-Est ante in nibh mauris cursus mattis molestie.
-Egestas tellus rutrum tellus pellentesque eu tincidunt tortor.
-Hendrerit gravida rutrum quisque non tellus orci.
-Platea dictumst vestibulum rhoncus est pellentesque.
-Amet nisl purus in mollis nunc sed.
-Vestibulum morbi blandit cursus risus at ultrices mi tempus imperdiet.
-Enim neque volutpat ac tincidunt vitae semper quis lectus nulla.
-Praesent elementum facilisis leo vel fringilla est ullamcorper.
-Consectetur adipiscing elit ut aliquam purus sit amet.
-Risus commodo viverra maecenas accumsan lacus.
-Tristique nulla aliquet enim tortor at auctor urna nunc.
-A scelerisque purus semper eget duis at tellus at.
+`r format(Sys.time(), '%B %Y')`
 
-Felis imperdiet proin fermentum leo vel orci porta non.
-Egestas egestas fringilla phasellus faucibus scelerisque.
-Lectus magna fringilla urna porttitor.
-Dignissim convallis aenean et tortor at.
-Laoreet id donec ultrices tincidunt arcu.
-Magna fringilla urna porttitor rhoncus dolor purus.
-Felis bibendum ut tristique et egestas quis ipsum.
-Ultrices vitae auctor eu augue ut lectus arcu bibendum at.
-Scelerisque eu ultrices vitae auctor eu augue ut lectus arcu.
-Fringilla est ullamcorper eget nulla facilisi etiam dignissim.
-Neque viverra justo nec ultrices dui sapien eget mi.
-Aliquet bibendum enim facilisis gravida neque convallis.
-Est placerat in egestas erat imperdiet sed.
-Arcu felis bibendum ut tristique et egestas quis ipsum suspendisse.
-Id donec ultrices tincidunt arcu non sodales.
-Senectus et netus et malesuada fames ac.
+\end{centering}
 
-Feugiat nibh sed pulvinar proin gravida hendrerit.
-Ullamcorper dignissim cras tincidunt lobortis feugiat vivamus at.
-Ultrices dui sapien eget mi proin sed libero enim sed.
-In metus vulputate eu scelerisque.
-A arcu cursus vitae congue mauris rhoncus aenean vel elit.
-Pellentesque id nibh tortor id aliquet lectus proin nibh nisl.
-Diam donec adipiscing tristique risus nec feugiat in fermentum posuere.
-Suspendisse faucibus interdum posuere lorem ipsum.
-In metus vulputate eu scelerisque felis imperdiet.
-Porttitor leo a diam sollicitudin tempor id.
-Elit duis tristique sollicitudin nibh sit amet.
-Imperdiet proin fermentum leo vel.
-Eu sem integer vitae justo eget.
-Diam volutpat commodo sed egestas egestas.
-Sagittis aliquam malesuada bibendum arcu vitae elementum curabitur vitae nunc.
-Quam pellentesque nec nam aliquam.
-Tellus in metus vulputate eu scelerisque felis imperdiet proin fermentum.
+\newpage
 
-Libero justo laoreet sit amet cursus sit amet.
-Scelerisque eu ultrices vitae auctor eu augue.
-Ultrices eros in cursus turpis massa tincidunt dui.
-Convallis tellus id interdum velit laoreet id donec.
-Cras adipiscing enim eu turpis.
-Blandit cursus risus at ultrices.
-Ut etiam sit amet nisl.
-Vel fringilla est ullamcorper eget nulla.
-Consequat id porta nibh venenatis cras sed felis eget.
-At consectetur lorem donec massa sapien.
-Auctor elit sed vulputate mi.
-Vitae suscipit tellus mauris a diam maecenas.
-Rhoncus urna neque viverra justo nec ultrices dui sapien.
-Vulputate dignissim suspendisse in est.
-Ac turpis egestas maecenas pharetra.
-Gravida dictum fusce ut placerat orci nulla pellentesque.
-Diam vel quam elementum pulvinar etiam.
+\vspace*{\fill}
+© `r format(Sys.time(), '%Y')` Daniel Arias. All rights reserved.
 
-Congue nisi vitae suscipit tellus mauris.
-Rhoncus mattis rhoncus urna neque viverra justo.
-At augue eget arcu dictum varius.
-Vitae turpis massa sed elementum tempus.
-Sed risus pretium quam vulputate dignissim.
-Consectetur adipiscing elit ut aliquam purus.
-Ligula ullamcorper malesuada proin libero nunc.
-Tincidunt tortor aliquam nulla facilisi.
-Phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor.
-Etiam erat velit scelerisque in dictum non consectetur a.
-Placerat duis ultricies lacus sed turpis.
-Diam vulputate ut pharetra sit amet aliquam id.
-Faucibus in ornare quam viverra.
-Elementum nibh tellus molestie nunc non blandit massa.
-Nunc vel risus commodo viverra maecenas accumsan lacus vel.
-Sagittis orci a scelerisque purus semper eget duis at tellus.
+\newpage
 
-Quam nulla porttitor massa id neque aliquam.
-Et netus et malesuada fames ac turpis egestas sed tempus.
-Tellus integer feugiat scelerisque varius morbi enim nunc faucibus.
-Mattis ullamcorper velit sed ullamcorper.
-Ornare arcu odio ut sem nulla pharetra diam sit.
-Sed vulputate odio ut enim.
-Ut tristique et egestas quis ipsum.
-Dui sapien eget mi proin sed.
-Eget nulla facilisi etiam dignissim diam quis enim.
-Venenatis lectus magna fringilla urna porttitor rhoncus dolor purus.
-Auctor urna nunc id cursus metus aliquam.
-Ornare aenean euismod elementum nisi quis.
-Et leo duis ut diam quam nulla.
-Dictum sit amet justo donec enim.
-Quis auctor elit sed vulputate mi sit.
-Diam sollicitudin tempor id eu.
+\pagestyle{plain}
 
-Venenatis tellus in metus vulputate eu scelerisque felis imperdiet proin.
-Quis vel eros donec ac.
-Sit amet cursus sit amet.
-Et magnis dis parturient montes nascetur ridiculus mus.
-Purus sit amet luctus venenatis lectus magna fringilla.
-Amet consectetur adipiscing elit duis tristique.
-Aliquet bibendum enim facilisis gravida.
-Neque laoreet suspendisse interdum consectetur.
-Etiam dignissim diam quis enim lobortis scelerisque fermentum.
-Id consectetur purus ut faucibus pulvinar.
-Parturient montes nascetur ridiculus mus mauris vitae ultricies leo integer.
-Enim neque volutpat ac tincidunt.
-Aliquam malesuada bibendum arcu vitae elementum curabitur.
-At imperdiet dui accumsan sit amet nulla facilisi morbi.
-Hac habitasse platea dictumst vestibulum rhoncus est.
-Accumsan lacus vel facilisis volutpat est velit.
-Commodo quis imperdiet massa tincidunt.
-Faucibus purus in massa tempor nec feugiat nisl.
+\normalsize
 
-Amet nulla facilisi morbi tempus iaculis urna id.
-Et malesuada fames ac turpis egestas sed tempus urna et.
-Nam aliquam sem et tortor consequat id porta.
-Suspendisse potenti nullam ac tortor.
-Quis enim lobortis scelerisque fermentum.
-Sed velit dignissim sodales ut eu sem integer vitae justo.
-In est ante in nibh mauris cursus mattis.
-Sollicitudin nibh sit amet commodo nulla facilisi nullam vehicula ipsum.
-Vitae tortor condimentum lacinia quis vel eros.
-Etiam non quam lacus suspendisse faucibus interdum posuere.
-Magna ac placerat vestibulum lectus mauris ultrices.
-Auctor eu augue ut lectus arcu.
-Mi eget mauris pharetra et ultrices neque ornare aenean euismod.
-Mattis ullamcorper velit sed ullamcorper morbi tincidunt ornare massa eget.
-Elementum sagittis vitae et leo duis ut diam quam nulla.
+\begin{centering}
 
-At lectus urna duis convallis.
-Fames ac turpis egestas integer eget.
-Sapien eget mi proin sed.
-Id ornare arcu odio ut sem nulla pharetra diam.
-Ac tincidunt vitae semper quis lectus.
-Varius vel pharetra vel turpis nunc eget lorem dolor sed.
-Tortor at risus viverra adipiscing at in tellus.
-Venenatis a condimentum vitae sapien pellentesque habitant.
-Convallis posuere morbi leo urna molestie at.
-Dignissim sodales ut eu sem integer.
-Maecenas sed enim ut sem viverra aliquet eget sit amet.
-Id cursus metus aliquam eleifend mi in nulla.
+Dissertation Advisor: Stéphane Verguet \hfill Daniel Arias
 
-Facilisi morbi tempus iaculis urna id.
-Quis eleifend quam adipiscing vitae.
-Viverra accumsan in nisl nisi scelerisque eu ultrices vitae auctor.
-Imperdiet nulla malesuada pellentesque elit eget gravida cum sociis natoque.
-Turpis in eu mi bibendum neque egestas congue quisque.
-Urna neque viverra justo nec ultrices dui.
-Proin sagittis nisl rhoncus mattis rhoncus urna.
-Eros donec ac odio tempor orci dapibus ultrices in iaculis.
-Ornare arcu dui vivamus arcu felis bibendum ut.
-Tincidunt nunc pulvinar sapien et ligula.
-In dictum non consectetur a.
-Bibendum arcu vitae elementum curabitur vitae nunc sed velit.
-Ut consequat semper viverra nam libero justo.
-Commodo viverra maecenas accumsan lacus vel.
-Vitae tortor condimentum lacinia quis vel eros donec.
-Iaculis urna id volutpat lacus laoreet non.
-Nec ultrices dui sapien eget mi.
-Suspendisse potenti nullam ac tortor vitae purus faucibus.
-Scelerisque felis imperdiet proin fermentum.
+\vspace{24 pt}
 
-Nunc mi ipsum faucibus vitae aliquet nec ullamcorper sit.
-Id aliquet lectus proin nibh nisl condimentum.
-Feugiat in fermentum posuere urna nec tincidunt.
-Nunc sed id semper risus in hendrerit gravida rutrum.
-Vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant morbi.
-Id aliquet lectus proin nibh nisl condimentum id venenatis.
-Quis eleifend quam adipiscing vitae.
-Commodo ullamcorper a lacus vestibulum sed arcu non odio euismod.
-Tellus pellentesque eu tincidunt tortor aliquam nulla.
-Nunc mi ipsum faucibus vitae.
-A scelerisque purus semper eget duis at tellus at urna.
-Faucibus ornare suspendisse sed nisi lacus sed viverra tellus.
-Tortor pretium viverra suspendisse potenti nullam.
+{\bf `r toupper("Quantitative Approaches Towards Evaluating the Global Burden of Mental Illness")`}
 
-Habitant morbi tristique senectus et netus et malesuada fames.
-Nisl nunc mi ipsum faucibus vitae aliquet nec.
-Sapien nec sagittis aliquam malesuada.
-Purus faucibus ornare suspendisse sed nisi lacus sed.
-Venenatis lectus magna fringilla urna porttitor rhoncus dolor.
-Adipiscing elit pellentesque habitant morbi tristique senectus et.
-In tellus integer feugiat scelerisque.
-Amet nisl purus in mollis nunc.
-Mauris augue neque gravida in fermentum et.
-Augue ut lectus arcu bibendum at.
+\vspace{12pt}
 
-Pharetra sit amet aliquam id diam maecenas ultricies mi.
-Sociis natoque penatibus et magnis dis parturient.
-Fringilla phasellus faucibus scelerisque eleifend.
-Ultrices tincidunt arcu non sodales neque sodales ut.
-Sed egestas egestas fringilla phasellus faucibus scelerisque eleifend donec.
-Eget nulla facilisi etiam dignissim diam quis enim.
-Cras ornare arcu dui vivamus arcu felis bibendum ut.
-Ultricies lacus sed turpis tincidunt id.
-Volutpat est velit egestas dui id ornare arcu.
-Tristique senectus et netus et malesuada fames.
-Id volutpat lacus laoreet non curabitur.
-Massa sed elementum tempus egestas sed sed risus pretium.
-Mollis aliquam ut porttitor leo.
-Leo urna molestie at elementum eu facilisis sed odio morbi.
-Netus et malesuada fames ac turpis egestas integer.
-Magnis dis parturient montes nascetur ridiculus mus.
+\section*{Abstract}
 
-Urna neque viverra justo nec ultrices dui sapien.
-Et odio pellentesque diam volutpat.
-Nunc lobortis mattis aliquam faucibus purus in massa tempor nec.
-Ac turpis egestas maecenas pharetra convallis posuere morbi.
-Amet nisl suscipit adipiscing bibendum.
-Ultricies mi quis hendrerit dolor magna.
-Morbi quis commodo odio aenean.
-Dolor magna eget est lorem ipsum dolor sit amet.
-Nulla aliquet enim tortor at auctor urna.
-Pellentesque dignissim enim sit amet venenatis urna cursus eget nunc.
-Nunc lobortis mattis aliquam faucibus purus.
-Amet est placerat in egestas erat imperdiet.
-Turpis in eu mi bibendum neque egestas congue quisque.
+\addcontentsline{toc}{section}{Abstract}
 
-Et egestas quis ipsum suspendisse ultrices gravida dictum fusce ut.
-Risus sed vulputate odio ut enim blandit volutpat maecenas.
-Tristique senectus et netus et.
-Aenean euismod elementum nisi quis eleifend quam adipiscing vitae proin.
-Ac placerat vestibulum lectus mauris.
-Mauris ultrices eros in cursus turpis.
-Ipsum consequat nisl vel pretium lectus quam id leo in.
-Eu sem integer vitae justo eget magna.
-Mi sit amet mauris commodo quis imperdiet massa.
-Venenatis urna cursus eget nunc scelerisque.
-Fermentum leo vel orci porta non pulvinar.
-Diam donec adipiscing tristique risus nec feugiat in fermentum posuere.
-Nibh tellus molestie nunc non blandit.
+\end{centering}
 
-Vel eros donec ac odio tempor orci.
-Nibh cras pulvinar mattis nunc.
-Et magnis dis parturient montes nascetur ridiculus.
-Blandit turpis cursus in hac habitasse platea dictumst quisque.
-Blandit libero volutpat sed cras ornare arcu.
-Est pellentesque elit ullamcorper dignissim cras tincidunt lobortis.
-Dictumst vestibulum rhoncus est pellentesque.
-Sagittis orci a scelerisque purus semper eget duis.
-Nisi quis eleifend quam adipiscing vitae.
-Vehicula ipsum a arcu cursus vitae congue mauris rhoncus aenean.
+testsets
 
-Curabitur gravida arcu ac tortor dignissim convallis aenean et.
-Senectus et netus et malesuada fames ac turpis egestas sed.
-Magna eget est lorem ipsum dolor sit amet consectetur.
-Congue mauris rhoncus aenean vel elit scelerisque.
-Erat nam at lectus urna duis convallis convallis tellus.
-Mauris sit amet massa vitae tortor condimentum lacinia.
-Egestas fringilla phasellus faucibus scelerisque eleifend donec pretium.
-Netus et malesuada fames ac turpis egestas maecenas pharetra convallis.
-Viverra accumsan in nisl nisi scelerisque eu ultrices.
-Proin sed libero enim sed faucibus turpis in eu mi.
-Id neque aliquam vestibulum morbi blandit.
-Laoreet non curabitur gravida arcu ac tortor dignissim.
-Iaculis nunc sed augue lacus viverra vitae congue eu consequat.
-Ut tortor pretium viverra suspendisse.
-Quisque sagittis purus sit amet volutpat consequat mauris nunc.
-Amet nulla facilisi morbi tempus iaculis.
-Amet cursus sit amet dictum sit amet justo donec.
+etstestsetest . estsetset
 
-Diam maecenas sed enim ut sem viverra aliquet.
-Odio tempor orci dapibus ultrices.
-Natoque penatibus et magnis dis parturient montes nascetur ridiculus mus.
-Nisi lacus sed viverra tellus in hac habitasse platea dictumst.
-Id diam vel quam elementum.
-Nulla posuere sollicitudin aliquam ultrices sagittis orci a scelerisque purus.
-Facilisi nullam vehicula ipsum a arcu cursus vitae.
-Non nisi est sit amet facilisis magna.
-Molestie ac feugiat sed lectus vestibulum mattis ullamcorper velit sed.
-Odio pellentesque diam volutpat commodo sed egestas egestas fringilla.
-Pellentesque id nibh tortor id aliquet lectus proin.
-Quis eleifend quam adipiscing vitae proin sagittis.
-Risus sed vulputate odio ut enim blandit volutpat.
-Pellentesque id nibh tortor id aliquet lectus proin nibh.
-Ullamcorper a lacus vestibulum sed arcu non odio euismod.
-
-Ut tortor pretium viverra suspendisse potenti nullam ac tortor vitae.
-Aliquet nibh praesent tristique magna sit amet.
-Arcu cursus euismod quis viverra nibh cras pulvinar.
-Magnis dis parturient montes nascetur ridiculus mus mauris vitae.
-Diam sit amet nisl suscipit adipiscing.
-Consequat ac felis donec et odio pellentesque diam volutpat.
-Pellentesque pulvinar pellentesque habitant morbi tristique senectus et netus.
-Magna sit amet purus gravida quis blandit turpis cursus.
-Maecenas sed enim ut sem viverra aliquet eget sit.
-Consectetur adipiscing elit ut aliquam purus.
-Ut morbi tincidunt augue interdum velit euismod in pellentesque massa.
-
-Nunc pulvinar sapien et ligula ullamcorper malesuada proin.
+Lorem ipsum dolor sit amet, nunc pulvinar sapien et ligula ullamcorper malesuada proin.
 Faucibus a pellentesque sit amet porttitor eget.
@@
 
-Lorem mollis aliquam ut porttitor leo a.
-Commodo elit at imperdiet dui accumsan sit amet nulla facilisi.
-Nec tincidunt praesent semper feugiat nibh sed.
-Tellus integer feugiat scelerisque varius morbi enim nunc.
-Euismod quis viverra nibh cras.
-Ipsum nunc aliquet bibendum enim facilisis gravida.
-Tincidunt lobortis feugiat vivamus at augue eget arcu dictum.
-Sodales neque sodales ut etiam sit amet nisl.
-Sollicitudin nibh sit amet commodo nulla facilisi.
-Elit ut aliquam purus sit amet luctus venenatis lectus magna.
-Auctor elit sed vulputate mi sit amet mauris commodo.
-Varius morbi enim nunc faucibus a.
+\newpage
 
-Malesuada bibendum arcu vitae elementum curabitur vitae nunc sed velit.
-Sed sed risus pretium quam vulputate dignissim.
-Ipsum a arcu cursus vitae.
-Et magnis dis parturient montes nascetur.
-Arcu cursus euismod quis viverra nibh cras pulvinar mattis.
-Quam lacus suspendisse faucibus interdum posuere lorem ipsum dolor.
-Adipiscing bibendum est ultricies integer quis auctor elit sed vulputate.
-Odio tempor orci dapibus ultrices in iaculis.
-Quis imperdiet massa tincidunt nunc pulvinar sapien et.
-Viverra adipiscing at in tellus integer feugiat scelerisque varius morbi.
-Urna nec tincidunt praesent semper feugiat nibh sed.
-Sit amet tellus cras adipiscing enim eu turpis egestas pretium.
-Ut venenatis tellus in metus vulputate eu scelerisque felis.
-Tempus quam pellentesque nec nam.
-Ac placerat vestibulum lectus mauris ultrices eros in.
-In vitae turpis massa sed elementum tempus egestas.
+\begin{spacing}{1}
 
-Cursus in hac habitasse platea dictumst.
-Turpis egestas pretium aenean pharetra.
-Et odio pellentesque diam volutpat commodo sed egestas egestas.
-Dictumst quisque sagittis purus sit amet volutpat.
-Tortor posuere ac ut consequat semper viverra nam.
-Ornare arcu odio ut sem nulla pharetra diam sit amet.
-Sed enim ut sem viverra aliquet eget sit amet.
-Nam at lectus urna duis convallis convallis tellus id.
-Dui vivamus arcu felis bibendum ut tristique et egestas.
-Pretium viverra suspendisse potenti nullam ac tortor vitae purus faucibus.
-Quam id leo in vitae turpis massa sed elementum.
-Ornare arcu dui vivamus arcu felis bibendum ut tristique.
-Arcu non odio euismod lacinia at quis risus sed vulputate.
-Convallis posuere morbi leo urna molestie.
-Eget mi proin sed libero enim sed faucibus.
-Id consectetur purus ut faucibus pulvinar elementum integer enim neque.
-Tincidunt ornare massa eget egestas purus viverra accumsan in.
-Commodo quis imperdiet massa tincidunt nunc pulvinar sapien et.
-Risus quis varius quam quisque id diam vel.
-Velit ut tortor pretium viverra.
+\renewcommand*\contentsname{Table of Contents}
 
-Rutrum quisque non tellus orci.
-Eu mi bibendum neque egestas congue quisque egestas.
-Massa tincidunt nunc pulvinar sapien.
-Ac ut consequat semper viverra nam libero justo laoreet sit.
-Eget gravida cum sociis natoque penatibus et.
-Maecenas pharetra convallis posuere morbi leo urna molestie at.
-Vitae tempus quam pellentesque nec nam aliquam sem et.
-Consectetur adipiscing elit ut aliquam purus sit amet luctus venenatis.
-Aliquam vestibulum morbi blandit cursus risus at ultrices mi.
-At in tellus integer feugiat scelerisque varius morbi enim.
-In tellus integer feugiat scelerisque varius.
-Morbi non arcu risus quis varius.
-Rutrum quisque non tellus orci ac auctor augue mauris augue.
-Dolor purus non enim praesent elementum facilisis.
-Ornare aenean euismod elementum nisi.
-Venenatis tellus in metus vulputate eu scelerisque felis imperdiet proin.
-Scelerisque eleifend donec pretium vulputate sapien nec sagittis aliquam malesuada.
-Elementum tempus egestas sed sed risus.
-Velit sed ullamcorper morbi tincidunt ornare massa eget.
-Non consectetur a erat nam.
+\tableofcontents
 
-Vel fringilla est ullamcorper eget nulla facilisi etiam dignissim.
-Sodales ut eu sem integer vitae justo eget.
-Leo urna molestie at elementum eu facilisis sed.
-Venenatis tellus in metus vulputate eu.
-Dictum fusce ut placerat orci nulla pellentesque dignissim.
-Ornare quam viverra orci sagittis eu volutpat odio facilisis.
-Feugiat nisl pretium fusce id velit ut.
-Sed nisi lacus sed viverra.
-Blandit turpis cursus in hac habitasse platea dictumst.
-Ut venenatis tellus in metus vulputate eu scelerisque.
-Neque viverra justo nec ultrices dui sapien eget mi.
-Hac habitasse platea dictumst quisque sagittis purus.
-Lorem ipsum dolor sit amet consectetur adipiscing.
-Venenatis lectus magna fringilla urna porttitor.
+\addcontentsline{toc}{section}{Table of Contents}
 
-Sit amet aliquam id diam maecenas.
-Turpis in eu mi bibendum neque egestas.
-Eu consequat ac felis donec.
-Sit amet mattis vulputate enim nulla aliquet porttitor.
-Rutrum quisque non tellus orci ac auctor augue mauris augue.
-Turpis tincidunt id aliquet risus feugiat in ante.
-Massa eget egestas purus viverra accumsan.
-Integer vitae justo eget magna fermentum iaculis.
-Fringilla phasellus faucibus scelerisque eleifend donec pretium vulputate.
-Neque convallis a cras semper auctor neque vitae tempus.
-Fames ac turpis egestas sed tempus.
-Id consectetur purus ut faucibus.
-Praesent elementum facilisis leo vel fringilla est.
-Senectus et netus et malesuada fames.
-Imperdiet massa tincidunt nunc pulvinar.
-Egestas integer eget aliquet nibh praesent tristique magna sit.
-Facilisi etiam dignissim diam quis enim.
+\newpage
 
-Maecenas volutpat blandit aliquam etiam erat velit scelerisque in.
-Consectetur adipiscing elit duis tristique sollicitudin nibh.
-Mattis aliquam faucibus purus in massa.
-Arcu cursus euismod quis viverra nibh cras pulvinar.
-Egestas purus viverra accumsan in.
-Enim sed faucibus turpis in eu.
-Quis varius quam quisque id diam vel.
-Viverra adipiscing at in tellus integer feugiat scelerisque varius.
-Donec ac odio tempor orci dapibus.
-Elit eget gravida cum sociis.
-Massa sapien faucibus et molestie ac feugiat sed lectus vestibulum.
+\listoffigures
 
-Amet volutpat consequat mauris nunc congue nisi.
-Donec adipiscing tristique risus nec feugiat in fermentum posuere.
-Ipsum dolor sit amet consectetur adipiscing elit.
-Ullamcorper eget nulla facilisi etiam dignissim diam quis.
-Ut lectus arcu bibendum at varius vel pharetra.
-Nulla posuere sollicitudin aliquam ultrices sagittis orci a scelerisque.
-Enim nulla aliquet porttitor lacus luctus accumsan tortor posuere.
-Tempor orci eu lobortis elementum nibh tellus molestie.
-Donec massa sapien faucibus et molestie ac feugiat sed.
-Morbi tristique senectus et netus et malesuada fames.
-Interdum velit laoreet id donec ultrices.
+\newpage
 
-Iaculis nunc sed augue lacus viverra vitae congue eu consequat.
-Sodales ut eu sem integer vitae.
-Pulvinar mattis nunc sed blandit libero volutpat sed cras.
-Maecenas volutpat blandit aliquam etiam erat velit scelerisque in dictum.
-Ultricies integer quis auctor elit sed vulputate mi.
-Ornare suspendisse sed nisi lacus sed viverra tellus in.
-Quis commodo odio aenean sed adipiscing diam donec.
-Platea dictumst vestibulum rhoncus est pellentesque elit.
-Commodo nulla facilisi nullam vehicula ipsum a arcu cursus.
-Ut faucibus pulvinar elementum integer enim neque volutpat.
-Diam quis enim lobortis scelerisque fermentum dui.
+\listoftables
+
+\newpage
+
+\end{spacing}
+
+```{r frontmatter, child='frontmatter.Rmd'}
+```
+
+\newpage
+
+\pagenumbering{arabic}
+
+```{r intro, child='intro.Rmd'}
+```
+
+\newpage
+
+```{r paper1, child='paper1.Rmd'}
+```
+
+\newpage
+
+```{r paper2, child='paper2.Rmd'}
+```
+
+\newpage
+
+```{r paper3, child='paper3.Rmd'}
+```
+
+\newpage
+
+```{r conclusion, child='conclusion.Rmd'}
+```
+
+\newpage

### 2023-02-10 conclusion.Rmd
Clean up of formatting and typesetting throughout.

@@
----
-title: ''
-output: pdf_document
-
----
+\section*{Conclusion}
 
 \addcontentsline{toc}{section}{Conclusion}
-\section*{Conclusion}
 
-Thank you for following this tutorial!
+Iaculis nunc sed augue lacus viverra vitae congue eu consequat.
+Sodales ut eu sem integer vitae.
+Pulvinar mattis nunc sed blandit libero volutpat sed cras.
+Maecenas volutpat blandit aliquam etiam erat velit scelerisque in dictum.
+Ultricies integer quis auctor elit sed vulputate mi.
+Ornare suspendisse sed nisi lacus sed viverra tellus in.
+Quis commodo odio aenean sed adipiscing diam donec.
+Platea dictumst vestibulum rhoncus est pellentesque elit.
+Commodo nulla facilisi nullam vehicula ipsum a arcu cursus.
+Ut faucibus pulvinar elementum integer enim neque volutpat.
+Diam quis enim lobortis scelerisque fermentum dui.
 
-I hope you'll find it useful to write a very professional dissertation.
+...
 
-\cite{ngTracingPathChikungunya2010}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Lacinia quis vel eros donec ac odio tempor.
+Urna nec tincidunt praesent semper feugiat nibh.
+Tortor aliquam nulla facilisi cras fermentum odio eu feugiat.
+Magna ac placerat vestibulum lectus mauris ultrices eros.
+Pulvinar proin gravida hendrerit lectus.
+Nisi scelerisque eu ultrices vitae auctor eu.
+Quis hendrerit dolor magna eget est lorem ipsum.
+At consectetur lorem donec massa sapien faucibus et molestie.
+Feugiat in fermentum posuere urna nec tincidunt praesent.
+Facilisis gravida neque convallis a cras.
+Massa id neque aliquam vestibulum morbi blandit.
+Faucibus purus in massa tempor nec feugiat nisl pretium fusce.
+Amet facilisis magna etiam tempor orci eu lobortis.
+Odio tempor orci dapibus ultrices in iaculis nunc sed augue.
+Nulla aliquet porttitor lacus luctus accumsan tortor posuere ac ut.
+Sit amet aliquam id diam maecenas.
+Rhoncus aenean vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant.
+Urna nunc id cursus metus aliquam.

### 2023-02-10 frontmatter.Rmd
Clean up of formatting and typesetting throughout.

@@
 \section*{Acknowledgements}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
+Lacinia quis vel eros donec ac odio tempor.
+Urna nec tincidunt praesent semper feugiat nibh.
+
+Tortor aliquam nulla facilisi cras fermentum odio eu feugiat.
+Magna ac placerat vestibulum lectus mauris ultrices eros.
+Pulvinar proin gravida hendrerit lectus.
+Nisi scelerisque eu ultrices vitae auctor eu.
+Quis hendrerit dolor magna eget est lorem ipsum.
+At consectetur lorem donec massa sapien faucibus et molestie.
+Feugiat in fermentum posuere urna nec tincidunt praesent.
+
+Facilisis gravida neque convallis a cras.
+Massa id neque aliquam vestibulum morbi blandit.
+Faucibus purus in massa tempor nec feugiat nisl pretium fusce.
+Amet facilisis magna etiam tempor orci eu lobortis.
+Odio tempor orci dapibus ultrices in iaculis nunc sed augue.
+Nulla aliquet porttitor lacus luctus accumsan tortor posuere ac ut.
+Sit amet aliquam id diam maecenas.
+Rhoncus aenean vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant.
+Urna nunc id cursus metus aliquam.
 
@@
 
-\emph{Dedicated to ....}
+\emph{Dedicated to lorem ipsum...}
 

### 2023-02-10 intro.Rmd
Clean up of formatting and typesetting throughout.

@@
----
-title: ''
-output: pdf_document
-indent: yes
----
 \section*{Introduction}
@@
 
-Arcu odio ut sem nulla pharetra diam sit.
-Adipiscing bibendum est ultricies integer.
-Accumsan lacus vel facilisis volutpat est.
-Turpis egestas sed tempus urna et pharetra pharetra.
-Est placerat in egestas erat imperdiet.
-Blandit aliquam etiam erat velit scelerisque in dictum non.
-Semper eget duis at tellus at urna condimentum.
-Tellus cras adipiscing enim eu turpis egestas.
-Vitae ultricies leo integer malesuada nunc vel.
-Sapien pellentesque habitant morbi tristique senectus et.
-
-Diam maecenas ultricies mi eget mauris pharetra.
-In arcu cursus euismod quis viverra nibh.
-Erat imperdiet sed euismod nisi porta.
-Ultricies mi eget mauris pharetra.
-Donec et odio pellentesque diam volutpat commodo.
-Vulputate sapien nec sagittis aliquam malesuada bibendum arcu.
-In eu mi bibendum neque egestas congue quisque egestas diam.
-Tortor dignissim convallis aenean et.
-Aliquam ut porttitor leo a diam sollicitudin.
-Cursus turpis massa tincidunt dui ut ornare lectus.
-Rhoncus mattis rhoncus urna neque.
-Enim blandit volutpat maecenas volutpat blandit.
-Egestas tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla.
-Adipiscing commodo elit at imperdiet dui accumsan sit amet.
-Pharetra massa massa ultricies mi quis.
-Quam pellentesque nec nam aliquam.
-
-At tempor commodo ullamcorper a.
-Commodo viverra maecenas accumsan lacus vel facilisis volutpat est.
-Sed arcu non odio euismod lacinia at.
-Turpis nunc eget lorem dolor sed viverra ipsum.
-Malesuada fames ac turpis egestas.
-Et ultrices neque ornare aenean euismod elementum.
-Quisque egestas diam in arcu cursus euismod quis viverra nibh.
-Semper eget duis at tellus.
-Id diam maecenas ultricies mi eget mauris pharetra.
-Eget nunc scelerisque viverra mauris in aliquam sem fringilla.
-Sit amet massa vitae tortor condimentum lacinia quis vel.
-Ut faucibus pulvinar elementum integer enim neque.
-Amet justo donec enim diam vulputate.
-Cursus eget nunc scelerisque viverra.
-Gravida dictum fusce ut placerat orci nulla pellentesque.
-Purus semper eget duis at tellus at urna condimentum mattis.
-Ante in nibh mauris cursus mattis molestie a iaculis.
-Tincidunt augue interdum velit euismod.
-Urna nec tincidunt praesent semper feugiat nibh sed pulvinar.
-Tellus integer feugiat scelerisque varius morbi enim nunc.
-
-Felis eget velit aliquet sagittis id.
-Lacus laoreet non curabitur gravida arcu ac.
-Id diam vel quam elementum.
-Lacinia at quis risus sed vulputate odio ut enim blandit.
-Platea dictumst vestibulum rhoncus est pellentesque elit ullamcorper.
-Nunc aliquet bibendum enim facilisis.
-Viverra mauris in aliquam sem fringilla ut morbi.
-Eu lobortis elementum nibh tellus molestie nunc non blandit.
-Ut enim blandit volutpat maecenas volutpat blandit aliquam.
-Non odio euismod lacinia at quis risus sed vulputate.
-
-Libero id faucibus nisl tincidunt eget.
-Odio aenean sed adipiscing diam donec.
-Porta nibh venenatis cras sed felis eget velit aliquet.
-Enim nunc faucibus a pellentesque sit amet porttitor.
-Elementum nisi quis eleifend quam adipiscing vitae proin.
-Eget sit amet tellus cras adipiscing enim.
-In ante metus dictum at tempor commodo ullamcorper.
-Feugiat in fermentum posuere urna nec tincidunt praesent.
-Amet justo donec enim diam.
-In massa tempor nec feugiat.
-Mattis rhoncus urna neque viverra justo nec ultrices dui sapien.
-Tellus cras adipiscing enim eu turpis.
-Scelerisque eu ultrices vitae auctor.
-Viverra maecenas accumsan lacus vel facilisis.
-Donec et odio pellentesque diam volutpat commodo.
-Congue nisi vitae suscipit tellus mauris a.
-A scelerisque purus semper eget duis at tellus at urna.
-
-Mauris augue neque gravida in fermentum et sollicitudin ac orci.
-Rutrum quisque non tellus orci ac.
-Diam ut venenatis tellus in metus vulputate eu.
-Amet nisl suscipit adipiscing bibendum est ultricies integer quis.
-Velit euismod in pellentesque massa placerat duis ultricies lacus sed.
-Suspendisse potenti nullam ac tortor.
-Porttitor rhoncus dolor purus non enim praesent.
-Tortor consequat id porta nibh venenatis cras sed felis.
-Mattis rhoncus urna neque viverra justo nec ultrices dui.
-Eget lorem dolor sed viverra ipsum nunc aliquet.
-
-Sed ullamcorper morbi tincidunt ornare.
-Gravida rutrum quisque non tellus.
-Metus aliquam eleifend mi in.
-Sollicitudin aliquam ultrices sagittis orci a scelerisque.
-Ullamcorper velit sed ullamcorper morbi.
-Cras sed felis eget velit aliquet.
-Libero enim sed faucibus turpis in.
-Molestie ac feugiat sed lectus vestibulum mattis ullamcorper velit.
-Viverra orci sagittis eu volutpat odio facilisis mauris sit amet.
-Dignissim sodales ut eu sem integer vitae.
-
-Posuere urna nec tincidunt praesent.
-Et tortor consequat id porta nibh.
-Elit duis tristique sollicitudin nibh sit amet commodo nulla.
-Iaculis nunc sed augue lacus.
-Pulvinar pellentesque habitant morbi tristique senectus et.
-Integer quis auctor elit sed vulputate mi.
-Interdum posuere lorem ipsum dolor sit amet consectetur adipiscing elit.
-Ultricies tristique nulla aliquet enim tortor.
-Vivamus arcu felis bibendum ut tristique et egestas quis ipsum.
-Id eu nisl nunc mi.
-Eget nullam non nisi est sit amet facilisis magna.
-Quis ipsum suspendisse ultrices gravida.
-Blandit turpis cursus in hac habitasse platea dictumst quisque.
-Vulputate mi sit amet mauris commodo quis imperdiet.
-Pretium fusce id velit ut.
-Libero enim sed faucibus turpis.
-Massa eget egestas purus viverra accumsan.
-
-Quis imperdiet massa tincidunt nunc pulvinar sapien et ligula ullamcorper.
-Diam phasellus vestibulum lorem sed risus ultricies tristique.
-Orci eu lobortis elementum nibh tellus molestie.
-Ornare aenean euismod elementum nisi.
-Rhoncus urna neque viverra justo.
-Dignissim cras tincidunt lobortis feugiat vivamus.
-Fusce id velit ut tortor pretium viverra.
-Quis vel eros donec ac odio.
-Tellus id interdum velit laoreet.
-Maecenas accumsan lacus vel facilisis.
-Cursus mattis molestie a iaculis at erat.
-Nibh mauris cursus mattis molestie.
-Pellentesque diam volutpat commodo sed egestas.
-Et netus et malesuada fames ac turpis egestas integer eget.
-
-Consequat interdum varius sit amet mattis vulputate enim nulla aliquet.
-Aliquam id diam maecenas ultricies mi eget mauris pharetra.
-Porttitor eget dolor morbi non arcu.
-Eleifend donec pretium vulputate sapien nec sagittis aliquam malesuada.
-Viverra ipsum nunc aliquet bibendum enim.
-Egestas purus viverra accumsan in nisl nisi.
-Quam elementum pulvinar etiam non quam lacus.
-Non enim praesent elementum facilisis leo.
-Eget velit aliquet sagittis id consectetur.
-Leo integer malesuada nunc vel risus commodo viverra.
-Nulla facilisi etiam dignissim diam.
-Id diam maecenas ultricies mi eget.
-Arcu felis bibendum ut tristique et.
-Nunc lobortis mattis aliquam faucibus purus.
-Semper auctor neque vitae tempus.
-
-Est ultricies integer quis auctor elit sed vulputate mi.
-Bibendum at varius vel pharetra vel turpis.
-Risus viverra adipiscing at in tellus.
-Volutpat maecenas volutpat blandit aliquam etiam erat.
-Cras sed felis eget velit aliquet sagittis id consectetur purus.
-Dignissim diam quis enim lobortis scelerisque fermentum dui faucibus in.
-Vivamus arcu felis bibendum ut tristique et egestas.
-Porttitor eget dolor morbi non.
-Ut pharetra sit amet aliquam id diam maecenas ultricies.
-Viverra nam libero justo laoreet sit amet.
-Egestas diam in arcu cursus euismod quis viverra nibh cras.
-Non nisi est sit amet facilisis.
-Dictumst vestibulum rhoncus est pellentesque elit.
-Ipsum consequat nisl vel pretium lectus.
-Nunc sed velit dignissim sodales ut eu.
-Ipsum suspendisse ultrices gravida dictum.
-Orci sagittis eu volutpat odio facilisis.
-Lobortis feugiat vivamus at augue eget arcu dictum varius.
-Bibendum ut tristique et egestas.
-Tincidunt ornare massa eget egestas purus viverra accumsan in.
-
-Arcu odio ut sem nulla.
-Porttitor massa id neque aliquam.
-Sed felis eget velit aliquet sagittis id consectetur purus.
-Lacus vestibulum sed arcu non odio euismod lacinia at.
-Varius sit amet mattis vulputate enim nulla aliquet.
-Scelerisque mauris pellentesque pulvinar pellentesque habitant morbi tristique.
-Morbi enim nunc faucibus a pellentesque sit amet.
-Varius quam quisque id diam vel quam elementum.
-Commodo nulla facilisi nullam vehicula ipsum a arcu cursus.
-Diam donec adipiscing tristique risus nec feugiat in fermentum.
-Blandit turpis cursus in hac habitasse platea dictumst.
-Ante in nibh mauris cursus mattis molestie.
-Sed adipiscing diam donec adipiscing tristique risus nec.
-
-Amet facilisis magna etiam tempor orci eu lobortis elementum nibh.
-Eget dolor morbi non arcu risus quis varius quam.
-Consequat id porta nibh venenatis cras sed.
-Pretium nibh ipsum consequat nisl vel.
-Feugiat nibh sed pulvinar proin gravida hendrerit.
-Risus sed vulputate odio ut enim blandit volutpat.
-Sem integer vitae justo eget magna fermentum iaculis.
-Consequat semper viverra nam libero justo laoreet sit amet.
-Arcu felis bibendum ut tristique et egestas.
-Proin fermentum leo vel orci porta.
-Aliquam malesuada bibendum arcu vitae elementum.
-Consectetur adipiscing elit duis tristique sollicitudin nibh.
-Non quam lacus suspendisse faucibus interdum posuere lorem ipsum.
-Ullamcorper velit sed ullamcorper morbi tincidunt ornare massa.
-Risus commodo viverra maecenas accumsan lacus vel facilisis volutpat.
-Ut etiam sit amet nisl.
-Urna condimentum mattis pellentesque id nibh tortor id aliquet lectus.
-Ornare massa eget egestas purus viverra accumsan.
-
-Auctor augue mauris augue neque gravida in fermentum et.
-Lectus mauris ultrices eros in cursus turpis.
-Commodo elit at imperdiet dui accumsan sit.
-Eget nulla facilisi etiam dignissim diam quis enim lobortis scelerisque.
-Volutpat est velit egestas dui id.
-Nunc eget lorem dolor sed viverra ipsum.
-Nullam ac tortor vitae purus faucibus ornare suspendisse sed nisi.
-Justo donec enim diam vulputate ut.
-Sodales ut etiam sit amet nisl purus.
-Congue nisi vitae suscipit tellus.
-Mauris cursus mattis molestie a.
-Pellentesque id nibh tortor id aliquet.
-Porta non pulvinar neque laoreet suspendisse interdum consectetur libero id.
-Diam vulputate ut pharetra sit.
-Placerat vestibulum lectus mauris ultrices eros in cursus.
-A arcu cursus vitae congue mauris rhoncus aenean.
-
-Nisi vitae suscipit tellus mauris a diam.
-Aenean et tortor at risus viverra adipiscing at.
-Ultrices eros in cursus turpis massa tincidunt.
-Euismod lacinia at quis risus sed.
-Egestas diam in arcu cursus euismod quis.
-Eu lobortis elementum nibh tellus molestie nunc non.
-Ornare arcu odio ut sem nulla pharetra diam.
-Senectus et netus et malesuada fames.
-Condimentum vitae sapien pellentesque habitant morbi.
-Diam sit amet nisl suscipit.
-Porta lorem mollis aliquam ut porttitor leo a.
-Sed risus pretium quam vulputate dignissim suspendisse in est ante.
-Risus pretium quam vulputate dignissim suspendisse in est.
-Pellentesque eu tincidunt tortor aliquam.
-Amet consectetur adipiscing elit pellentesque habitant.
-Mattis pellentesque id nibh tortor.
-Purus faucibus ornare suspendisse sed.
-Id venenatis a condimentum vitae.
-Ipsum a arcu cursus vitae.
-Pretium fusce id velit ut.
-
-Feugiat scelerisque varius morbi enim nunc.
-Mattis vulputate enim nulla aliquet porttitor lacus.
-Est ante in nibh mauris cursus mattis molestie.
-Egestas tellus rutrum tellus pellentesque eu tincidunt tortor.
-Hendrerit gravida rutrum quisque non tellus orci.
-Platea dictumst vestibulum rhoncus est pellentesque.
-Amet nisl purus in mollis nunc sed.
-Vestibulum morbi blandit cursus risus at ultrices mi tempus imperdiet.
-Enim neque volutpat ac tincidunt vitae semper quis lectus nulla.
-Praesent elementum facilisis leo vel fringilla est ullamcorper.
-Consectetur adipiscing elit ut aliquam purus sit amet.
-Risus commodo viverra maecenas accumsan lacus.
-Tristique nulla aliquet enim tortor at auctor urna nunc.
-A scelerisque purus semper eget duis at tellus at.
-
-Felis imperdiet proin fermentum leo vel orci porta non.
-Egestas egestas fringilla phasellus faucibus scelerisque.
-Lectus magna fringilla urna porttitor.
-Dignissim convallis aenean et tortor at.
-Laoreet id donec ultrices tincidunt arcu.
-Magna fringilla urna porttitor rhoncus dolor purus.
-Felis bibendum ut tristique et egestas quis ipsum.
-Ultrices vitae auctor eu augue ut lectus arcu bibendum at.
-Scelerisque eu ultrices vitae auctor eu augue ut lectus arcu.
-Fringilla est ullamcorper eget nulla facilisi etiam dignissim.
-Neque viverra justo nec ultrices dui sapien eget mi.
-Aliquet bibendum enim facilisis gravida neque convallis.
-Est placerat in egestas erat imperdiet sed.
-Arcu felis bibendum ut tristique et egestas quis ipsum suspendisse.
-Id donec ultrices tincidunt arcu non sodales.
-Senectus et netus et malesuada fames ac.
-
-Feugiat nibh sed pulvinar proin gravida hendrerit.
-Ullamcorper dignissim cras tincidunt lobortis feugiat vivamus at.
-Ultrices dui sapien eget mi proin sed libero enim sed.
-In metus vulputate eu scelerisque.
-A arcu cursus vitae congue mauris rhoncus aenean vel elit.
-Pellentesque id nibh tortor id aliquet lectus proin nibh nisl.
-Diam donec adipiscing tristique risus nec feugiat in fermentum posuere.
-Suspendisse faucibus interdum posuere lorem ipsum.
-In metus vulputate eu scelerisque felis imperdiet.
-Porttitor leo a diam sollicitudin tempor id.
-Elit duis tristique sollicitudin nibh sit amet.
-Imperdiet proin fermentum leo vel.
-Eu sem integer vitae justo eget.
-Diam volutpat commodo sed egestas egestas.
-Sagittis aliquam malesuada bibendum arcu vitae elementum curabitur vitae nunc.
-Quam pellentesque nec nam aliquam.
-Tellus in metus vulputate eu scelerisque felis imperdiet proin fermentum.
-
-Libero justo laoreet sit amet cursus sit amet.
-Scelerisque eu ultrices vitae auctor eu augue.
-Ultrices eros in cursus turpis massa tincidunt dui.
-Convallis tellus id interdum velit laoreet id donec.
-Cras adipiscing enim eu turpis.
-Blandit cursus risus at ultrices.
-Ut etiam sit amet nisl.
-Vel fringilla est ullamcorper eget nulla.
-Consequat id porta nibh venenatis cras sed felis eget.
-At consectetur lorem donec massa sapien.
-Auctor elit sed vulputate mi.
-Vitae suscipit tellus mauris a diam maecenas.
-Rhoncus urna neque viverra justo nec ultrices dui sapien.
-Vulputate dignissim suspendisse in est.
-Ac turpis egestas maecenas pharetra.
-Gravida dictum fusce ut placerat orci nulla pellentesque.
-Diam vel quam elementum pulvinar etiam.
-
-Congue nisi vitae suscipit tellus mauris.
-Rhoncus mattis rhoncus urna neque viverra justo.
-At augue eget arcu dictum varius.
-Vitae turpis massa sed elementum tempus.
-Sed risus pretium quam vulputate dignissim.
-Consectetur adipiscing elit ut aliquam purus.
-Ligula ullamcorper malesuada proin libero nunc.
-Tincidunt tortor aliquam nulla facilisi.
-Phasellus egestas tellus rutrum tellus pellentesque eu tincidunt tortor.
-Etiam erat velit scelerisque in dictum non consectetur a.
-Placerat duis ultricies lacus sed turpis.
-Diam vulputate ut pharetra sit amet aliquam id.
-Faucibus in ornare quam viverra.
-Elementum nibh tellus molestie nunc non blandit massa.
-Nunc vel risus commodo viverra maecenas accumsan lacus vel.
-Sagittis orci a scelerisque purus semper eget duis at tellus.
-
-Quam nulla porttitor massa id neque aliquam.
-Et netus et malesuada fames ac turpis egestas sed tempus.
-Tellus integer feugiat scelerisque varius morbi enim nunc faucibus.
-Mattis ullamcorper velit sed ullamcorper.
-Ornare arcu odio ut sem nulla pharetra diam sit.
-Sed vulputate odio ut enim.
-Ut tristique et egestas quis ipsum.
-Dui sapien eget mi proin sed.
-Eget nulla facilisi etiam dignissim diam quis enim.
-Venenatis lectus magna fringilla urna porttitor rhoncus dolor purus.
-Auctor urna nunc id cursus metus aliquam.
-Ornare aenean euismod elementum nisi quis.
-Et leo duis ut diam quam nulla.
-Dictum sit amet justo donec enim.
-Quis auctor elit sed vulputate mi sit.
-Diam sollicitudin tempor id eu.
-
-Venenatis tellus in metus vulputate eu scelerisque felis imperdiet proin.
-Quis vel eros donec ac.
-Sit amet cursus sit amet.
-Et magnis dis parturient montes nascetur ridiculus mus.
-Purus sit amet luctus venenatis lectus magna fringilla.
-Amet consectetur adipiscing elit duis tristique.
-Aliquet bibendum enim facilisis gravida.
-Neque laoreet suspendisse interdum consectetur.
-Etiam dignissim diam quis enim lobortis scelerisque fermentum.
-Id consectetur purus ut faucibus pulvinar.
-Parturient montes nascetur ridiculus mus mauris vitae ultricies leo integer.
-Enim neque volutpat ac tincidunt.
-Aliquam malesuada bibendum arcu vitae elementum curabitur.
-At imperdiet dui accumsan sit amet nulla facilisi morbi.
-Hac habitasse platea dictumst vestibulum rhoncus est.
-Accumsan lacus vel facilisis volutpat est velit.
-Commodo quis imperdiet massa tincidunt.
-Faucibus purus in massa tempor nec feugiat nisl.
-
-Amet nulla facilisi morbi tempus iaculis urna id.
-Et malesuada fames ac turpis egestas sed tempus urna et.
-Nam aliquam sem et tortor consequat id porta.
-Suspendisse potenti nullam ac tortor.
-Quis enim lobortis scelerisque fermentum.
-Sed velit dignissim sodales ut eu sem integer vitae justo.
-In est ante in nibh mauris cursus mattis.
-Sollicitudin nibh sit amet commodo nulla facilisi nullam vehicula ipsum.
-Vitae tortor condimentum lacinia quis vel eros.
-Etiam non quam lacus suspendisse faucibus interdum posuere.
-Magna ac placerat vestibulum lectus mauris ultrices.
-Auctor eu augue ut lectus arcu.
-Mi eget mauris pharetra et ultrices neque ornare aenean euismod.
-Mattis ullamcorper velit sed ullamcorper morbi tincidunt ornare massa eget.
-Elementum sagittis vitae et leo duis ut diam quam nulla.
-
-At lectus urna duis convallis.
-Fames ac turpis egestas integer eget.
-Sapien eget mi proin sed.
-Id ornare arcu odio ut sem nulla pharetra diam.
-Ac tincidunt vitae semper quis lectus.
-Varius vel pharetra vel turpis nunc eget lorem dolor sed.
-Tortor at risus viverra adipiscing at in tellus.
-Venenatis a condimentum vitae sapien pellentesque habitant.
-Convallis posuere morbi leo urna molestie at.
-Dignissim sodales ut eu sem integer.
-Maecenas sed enim ut sem viverra aliquet eget sit amet.
-Id cursus metus aliquam eleifend mi in nulla.
-
-Facilisi morbi tempus iaculis urna id.
-Quis eleifend quam adipiscing vitae.
-Viverra accumsan in nisl nisi scelerisque eu ultrices vitae auctor.
-Imperdiet nulla malesuada pellentesque elit eget gravida cum sociis natoque.
-Turpis in eu mi bibendum neque egestas congue quisque.
-Urna neque viverra justo nec ultrices dui.
-Proin sagittis nisl rhoncus mattis rhoncus urna.
-Eros donec ac odio tempor orci dapibus ultrices in iaculis.
-Ornare arcu dui vivamus arcu felis bibendum ut.
-Tincidunt nunc pulvinar sapien et ligula.
-In dictum non consectetur a.
-Bibendum arcu vitae elementum curabitur vitae nunc sed velit.
-Ut consequat semper viverra nam libero justo.
-Commodo viverra maecenas accumsan lacus vel.
-Vitae tortor condimentum lacinia quis vel eros donec.
-Iaculis urna id volutpat lacus laoreet non.
-Nec ultrices dui sapien eget mi.
-Suspendisse potenti nullam ac tortor vitae purus faucibus.
-Scelerisque felis imperdiet proin fermentum.
-
-Nunc mi ipsum faucibus vitae aliquet nec ullamcorper sit.
-Id aliquet lectus proin nibh nisl condimentum.
-Feugiat in fermentum posuere urna nec tincidunt.
-Nunc sed id semper risus in hendrerit gravida rutrum.
-Vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant morbi.
-Id aliquet lectus proin nibh nisl condimentum id venenatis.
-Quis eleifend quam adipiscing vitae.
-Commodo ullamcorper a lacus vestibulum sed arcu non odio euismod.
-Tellus pellentesque eu tincidunt tortor aliquam nulla.
-Nunc mi ipsum faucibus vitae.
-A scelerisque purus semper eget duis at tellus at urna.
-Faucibus ornare suspendisse sed nisi lacus sed viverra tellus.
-Tortor pretium viverra suspendisse potenti nullam.
-
-Habitant morbi tristique senectus et netus et malesuada fames.
-Nisl nunc mi ipsum faucibus vitae aliquet nec.
-Sapien nec sagittis aliquam malesuada.
-Purus faucibus ornare suspendisse sed nisi lacus sed.
-Venenatis lectus magna fringilla urna porttitor rhoncus dolor.
-Adipiscing elit pellentesque habitant morbi tristique senectus et.
-In tellus integer feugiat scelerisque.
-Amet nisl purus in mollis nunc.
-Mauris augue neque gravida in fermentum et.
-Augue ut lectus arcu bibendum at.
-
-Pharetra sit amet aliquam id diam maecenas ultricies mi.
-Sociis natoque penatibus et magnis dis parturient.
-Fringilla phasellus faucibus scelerisque eleifend.
-Ultrices tincidunt arcu non sodales neque sodales ut.
-Sed egestas egestas fringilla phasellus faucibus scelerisque eleifend donec.
-Eget nulla facilisi etiam dignissim diam quis enim.
-Cras ornare arcu dui vivamus arcu felis bibendum ut.
-Ultricies lacus sed turpis tincidunt id.
-Volutpat est velit egestas dui id ornare arcu.
-Tristique senectus et netus et malesuada fames.
-Id volutpat lacus laoreet non curabitur.
-Massa sed elementum tempus egestas sed sed risus pretium.
-Mollis aliquam ut porttitor leo.
-Leo urna molestie at elementum eu facilisis sed odio morbi.
-Netus et malesuada fames ac turpis egestas integer.
-Magnis dis parturient montes nascetur ridiculus mus.
-
-Urna neque viverra justo nec ultrices dui sapien.
-Et odio pellentesque diam volutpat.
-Nunc lobortis mattis aliquam faucibus purus in massa tempor nec.
-Ac turpis egestas maecenas pharetra convallis posuere morbi.
-Amet nisl suscipit adipiscing bibendum.
-Ultricies mi quis hendrerit dolor magna.
-Morbi quis commodo odio aenean.
-Dolor magna eget est lorem ipsum dolor sit amet.
-Nulla aliquet enim tortor at auctor urna.
-Pellentesque dignissim enim sit amet venenatis urna cursus eget nunc.
-Nunc lobortis mattis aliquam faucibus purus.
-Amet est placerat in egestas erat imperdiet.
-Turpis in eu mi bibendum neque egestas congue quisque.
-
-Et egestas quis ipsum suspendisse ultrices gravida dictum fusce ut.
-Risus sed vulputate odio ut enim blandit volutpat maecenas.
-Tristique senectus et netus et.
-Aenean euismod elementum nisi quis eleifend quam adipiscing vitae proin.
-Ac placerat vestibulum lectus mauris.
-Mauris ultrices eros in cursus turpis.
-Ipsum consequat nisl vel pretium lectus quam id leo in.
-Eu sem integer vitae justo eget magna.
-Mi sit amet mauris commodo quis imperdiet massa.
-Venenatis urna cursus eget nunc scelerisque.
-Fermentum leo vel orci porta non pulvinar.
-Diam donec adipiscing tristique risus nec feugiat in fermentum posuere.
-Nibh tellus molestie nunc non blandit.
-
-Vel eros donec ac odio tempor orci.
-Nibh cras pulvinar mattis nunc.
-Et magnis dis parturient montes nascetur ridiculus.
-Blandit turpis cursus in hac habitasse platea dictumst quisque.
-Blandit libero volutpat sed cras ornare arcu.
-Est pellentesque elit ullamcorper dignissim cras tincidunt lobortis.
-Dictumst vestibulum rhoncus est pellentesque.
-Sagittis orci a scelerisque purus semper eget duis.
-Nisi quis eleifend quam adipiscing vitae.
-Vehicula ipsum a arcu cursus vitae congue mauris rhoncus aenean.
-
-Curabitur gravida arcu ac tortor dignissim convallis aenean et.
-Senectus et netus et malesuada fames ac turpis egestas sed.
-Magna eget est lorem ipsum dolor sit amet consectetur.
-Congue mauris rhoncus aenean vel elit scelerisque.
-Erat nam at lectus urna duis convallis convallis tellus.
-Mauris sit amet massa vitae tortor condimentum lacinia.
-Egestas fringilla phasellus faucibus scelerisque eleifend donec pretium.
-Netus et malesuada fames ac turpis egestas maecenas pharetra convallis.
-Viverra accumsan in nisl nisi scelerisque eu ultrices.
-Proin sed libero enim sed faucibus turpis in eu mi.
-Id neque aliquam vestibulum morbi blandit.
-Laoreet non curabitur gravida arcu ac tortor dignissim.
-Iaculis nunc sed augue lacus viverra vitae congue eu consequat.
-Ut tortor pretium viverra suspendisse.
-Quisque sagittis purus sit amet volutpat consequat mauris nunc.
-Amet nulla facilisi morbi tempus iaculis.
-Amet cursus sit amet dictum sit amet justo donec.
-
-Diam maecenas sed enim ut sem viverra aliquet.
-Odio tempor orci dapibus ultrices.
-Natoque penatibus et magnis dis parturient montes nascetur ridiculus mus.
-Nisi lacus sed viverra tellus in hac habitasse platea dictumst.
-Id diam vel quam elementum.
-Nulla posuere sollicitudin aliquam ultrices sagittis orci a scelerisque purus.
-Facilisi nullam vehicula ipsum a arcu cursus vitae.
-Non nisi est sit amet facilisis magna.
-Molestie ac feugiat sed lectus vestibulum mattis ullamcorper velit sed.
-Odio pellentesque diam volutpat commodo sed egestas egestas fringilla.
-Pellentesque id nibh tortor id aliquet lectus proin.
-Quis eleifend quam adipiscing vitae proin sagittis.
-Risus sed vulputate odio ut enim blandit volutpat.
-Pellentesque id nibh tortor id aliquet lectus proin nibh.
-Ullamcorper a lacus vestibulum sed arcu non odio euismod.
-
-Ut tortor pretium viverra suspendisse potenti nullam ac tortor vitae.
-Aliquet nibh praesent tristique magna sit amet.
-Arcu cursus euismod quis viverra nibh cras pulvinar.
-Magnis dis parturient montes nascetur ridiculus mus mauris vitae.
-Diam sit amet nisl suscipit adipiscing.
-Consequat ac felis donec et odio pellentesque diam volutpat.
-Pellentesque pulvinar pellentesque habitant morbi tristique senectus et netus.
-Magna sit amet purus gravida quis blandit turpis cursus.
-Maecenas sed enim ut sem viverra aliquet eget sit.
-Consectetur adipiscing elit ut aliquam purus.
-Ut morbi tincidunt augue interdum velit euismod in pellentesque massa.
-
-Nunc pulvinar sapien et ligula ullamcorper malesuada proin.
-Faucibus a pellentesque sit amet porttitor eget.
-Quam adipiscing vitae proin sagittis nisl rhoncus.
-Quis blandit turpis cursus in hac habitasse platea dictumst.
-Feugiat vivamus at augue eget arcu.
-Duis convallis convallis tellus id interdum velit laoreet id donec.
-Ornare quam viverra orci sagittis eu volutpat odio.
-Netus et malesuada fames ac turpis egestas maecenas.
-Faucibus turpis in eu mi bibendum neque egestas.
-Sed velit dignissim sodales ut.
-Dolor sed viverra ipsum nunc aliquet bibendum enim facilisis gravida.
-
-Interdum varius sit amet mattis vulputate.
-Dui id ornare arcu odio ut sem nulla pharetra diam.
-Neque gravida in fermentum et sollicitudin ac orci.
-Nibh ipsum consequat nisl vel pretium lectus quam id leo.
-Mauris pellentesque pulvinar pellentesque habitant morbi tristique senectus et netus.
-Massa tempor nec feugiat nisl pretium fusce id velit ut.
-Vivamus at augue eget arcu dictum varius duis at consectetur.
-Odio ut enim blandit volutpat maecenas volutpat blandit aliquam etiam.
-Mauris ultrices eros in cursus.
-Tristique senectus et netus et malesuada.
-
-Imperdiet sed euismod nisi porta lorem mollis aliquam.
-Eget lorem dolor sed viverra ipsum nunc aliquet bibendum enim.
-Eget lorem dolor sed viverra.
-Vitae proin sagittis nisl rhoncus mattis.
-Mi sit amet mauris commodo quis imperdiet massa tincidunt.
-Quis auctor elit sed vulputate mi.
-Augue eget arcu dictum varius duis at consectetur lorem.
-Commodo elit at imperdiet dui accumsan sit amet.
-Consequat semper viverra nam libero justo laoreet sit.
-Quis hendrerit dolor magna eget est lorem ipsum.
-Eget arcu dictum varius duis at consectetur lorem.
-Fermentum posuere urna nec tincidunt praesent semper feugiat.
-Integer quis auctor elit sed vulputate mi sit amet.
-Ultricies integer quis auctor elit.
-Metus vulputate eu scelerisque felis imperdiet proin fermentum.
-Ut porttitor leo a diam sollicitudin tempor id eu nisl.
-Cras adipiscing enim eu turpis egestas.
-Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.
-
-Augue eget arcu dictum varius duis at.
-Tempor orci eu lobortis elementum nibh.
-Nibh sit amet commodo nulla.
-At varius vel pharetra vel.
-In metus vulputate eu scelerisque felis imperdiet.
-Venenatis tellus in metus vulputate eu.
-Aliquam sem fringilla ut morbi tincidunt augue.
-Risus feugiat in ante metus dictum at tempor commodo ullamcorper.
-In dictum non consectetur a erat nam.
-Ut sem viverra aliquet eget sit.
-Eleifend donec pretium vulputate sapien nec sagittis aliquam.
-Neque viverra justo nec ultrices dui.
-Turpis in eu mi bibendum neque egestas.
-Tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla facilisi.
-
-Semper eget duis at tellus at urna condimentum.
-Viverra justo nec ultrices dui sapien eget.
-Etiam dignissim diam quis enim lobortis scelerisque fermentum dui.
-Sapien nec sagittis aliquam malesuada.
-Ac auctor augue mauris augue neque.
-Enim sed faucibus turpis in eu mi bibendum neque.
-Proin sagittis nisl rhoncus mattis rhoncus.
-Vel elit scelerisque mauris pellentesque pulvinar.
-Aliquam etiam erat velit scelerisque in dictum.
-Dictum varius duis at consectetur lorem donec massa sapien.
-Risus at ultrices mi tempus imperdiet nulla malesuada pellentesque.
-Faucibus purus in massa tempor nec feugiat nisl pretium fusce.
-
-Arcu odio ut sem nulla pharetra diam sit amet.
-Lorem ipsum dolor sit amet consectetur.
-Vitae aliquet nec ullamcorper sit amet risus nullam eget.
-Condimentum lacinia quis vel eros donec ac odio.
-Nulla posuere sollicitudin aliquam ultrices sagittis.
-Quis blandit turpis cursus in hac habitasse platea dictumst quisque.
-Amet risus nullam eget felis.
-Nec sagittis aliquam malesuada bibendum arcu vitae.
-In vitae turpis massa sed elementum tempus egestas sed sed.
-Netus et malesuada fames ac turpis egestas integer.
-Turpis tincidunt id aliquet risus feugiat.
-Lorem ipsum dolor sit amet consectetur adipiscing elit ut aliquam.
-Pretium vulputate sapien nec sagittis aliquam malesuada bibendum arcu vitae.
-Lectus nulla at volutpat diam ut venenatis tellus.
-
-Lorem mollis aliquam ut porttitor leo a.
-Commodo elit at imperdiet dui accumsan sit amet nulla facilisi.
-Nec tincidunt praesent semper feugiat nibh sed.
-Tellus integer feugiat scelerisque varius morbi enim nunc.
-Euismod quis viverra nibh cras.
-Ipsum nunc aliquet bibendum enim facilisis gravida.
-Tincidunt lobortis feugiat vivamus at augue eget arcu dictum.
-Sodales neque sodales ut etiam sit amet nisl.
-Sollicitudin nibh sit amet commodo nulla facilisi.
-Elit ut aliquam purus sit amet luctus venenatis lectus magna.
-Auctor elit sed vulputate mi sit amet mauris commodo.
-Varius morbi enim nunc faucibus a.
-
-Malesuada bibendum arcu vitae elementum curabitur vitae nunc sed velit.
-Sed sed risus pretium quam vulputate dignissim.
-Ipsum a arcu cursus vitae.
-Et magnis dis parturient montes nascetur.
-Arcu cursus euismod quis viverra nibh cras pulvinar mattis.
-Quam lacus suspendisse faucibus interdum posuere lorem ipsum dolor.
-Adipiscing bibendum est ultricies integer quis auctor elit sed vulputate.
-Odio tempor orci dapibus ultrices in iaculis.
-Quis imperdiet massa tincidunt nunc pulvinar sapien et.
-Viverra adipiscing at in tellus integer feugiat scelerisque varius morbi.
-Urna nec tincidunt praesent semper feugiat nibh sed.
-Sit amet tellus cras adipiscing enim eu turpis egestas pretium.
-Ut venenatis tellus in metus vulputate eu scelerisque felis.
-Tempus quam pellentesque nec nam.
-Ac placerat vestibulum lectus mauris ultrices eros in.
-In vitae turpis massa sed elementum tempus egestas.
-
-Cursus in hac habitasse platea dictumst.
-Turpis egestas pretium aenean pharetra.
-Et odio pellentesque diam volutpat commodo sed egestas egestas.
-Dictumst quisque sagittis purus sit amet volutpat.
-Tortor posuere ac ut consequat semper viverra nam.
-Ornare arcu odio ut sem nulla pharetra diam sit amet.
-Sed enim ut sem viverra aliquet eget sit amet.
-Nam at lectus urna duis convallis convallis tellus id.
-Dui vivamus arcu felis bibendum ut tristique et egestas.
-Pretium viverra suspendisse potenti nullam ac tortor vitae purus faucibus.
-Quam id leo in vitae turpis massa sed elementum.
-Ornare arcu dui vivamus arcu felis bibendum ut tristique.
-Arcu non odio euismod lacinia at quis risus sed vulputate.
-Convallis posuere morbi leo urna molestie.
-Eget mi proin sed libero enim sed faucibus.
-Id consectetur purus ut faucibus pulvinar elementum integer enim neque.
-Tincidunt ornare massa eget egestas purus viverra accumsan in.
-Commodo quis imperdiet massa tincidunt nunc pulvinar sapien et.
-Risus quis varius quam quisque id diam vel.
-Velit ut tortor pretium viverra.
-
-Rutrum quisque non tellus orci.
-Eu mi bibendum neque egestas congue quisque egestas.
-Massa tincidunt nunc pulvinar sapien.
-Ac ut consequat semper viverra nam libero justo laoreet sit.
-Eget gravida cum sociis natoque penatibus et.
-Maecenas pharetra convallis posuere morbi leo urna molestie at.
-Vitae tempus quam pellentesque nec nam aliquam sem et.
-Consectetur adipiscing elit ut aliquam purus sit amet luctus venenatis.
-Aliquam vestibulum morbi blandit cursus risus at ultrices mi.
-At in tellus integer feugiat scelerisque varius morbi enim.
-In tellus integer feugiat scelerisque varius.
-Morbi non arcu risus quis varius.
-Rutrum quisque non tellus orci ac auctor augue mauris augue.
-Dolor purus non enim praesent elementum facilisis.
-Ornare aenean euismod elementum nisi.
-Venenatis tellus in metus vulputate eu scelerisque felis imperdiet proin.
-Scelerisque eleifend donec pretium vulputate sapien nec sagittis aliquam malesuada.
-Elementum tempus egestas sed sed risus.
-Velit sed ullamcorper morbi tincidunt ornare massa eget.
-Non consectetur a erat nam.
-
-Vel fringilla est ullamcorper eget nulla facilisi etiam dignissim.
-Sodales ut eu sem integer vitae justo eget.
-Leo urna molestie at elementum eu facilisis sed.
-Venenatis tellus in metus vulputate eu.
-Dictum fusce ut placerat orci nulla pellentesque dignissim.
-Ornare quam viverra orci sagittis eu volutpat odio facilisis.
-Feugiat nisl pretium fusce id velit ut.
-Sed nisi lacus sed viverra.
-Blandit turpis cursus in hac habitasse platea dictumst.
-Ut venenatis tellus in metus vulputate eu scelerisque.
-Neque viverra justo nec ultrices dui sapien eget mi.
-Hac habitasse platea dictumst quisque sagittis purus.
-Lorem ipsum dolor sit amet consectetur adipiscing.
-Venenatis lectus magna fringilla urna porttitor.
-
-Sit amet aliquam id diam maecenas.
-Turpis in eu mi bibendum neque egestas.
-Eu consequat ac felis donec.
-Sit amet mattis vulputate enim nulla aliquet porttitor.
-Rutrum quisque non tellus orci ac auctor augue mauris augue.
-Turpis tincidunt id aliquet risus feugiat in ante.
-Massa eget egestas purus viverra accumsan.
-Integer vitae justo eget magna fermentum iaculis.
-Fringilla phasellus faucibus scelerisque eleifend donec pretium vulputate.
-Neque convallis a cras semper auctor neque vitae tempus.
-Fames ac turpis egestas sed tempus.
-Id consectetur purus ut faucibus.
-Praesent elementum facilisis leo vel fringilla est.
-Senectus et netus et malesuada fames.
-Imperdiet massa tincidunt nunc pulvinar.
-Egestas integer eget aliquet nibh praesent tristique magna sit.
-Facilisi etiam dignissim diam quis enim.
-
-Maecenas volutpat blandit aliquam etiam erat velit scelerisque in.
-Consectetur adipiscing elit duis tristique sollicitudin nibh.
-Mattis aliquam faucibus purus in massa.
-Arcu cursus euismod quis viverra nibh cras pulvinar.
-Egestas purus viverra accumsan in.
-Enim sed faucibus turpis in eu.
-Quis varius quam quisque id diam vel.
-Viverra adipiscing at in tellus integer feugiat scelerisque varius.
-Donec ac odio tempor orci dapibus.
-Elit eget gravida cum sociis.
-Massa sapien faucibus et molestie ac feugiat sed lectus vestibulum.
-
-Amet volutpat consequat mauris nunc congue nisi.
-Donec adipiscing tristique risus nec feugiat in fermentum posuere.
-Ipsum dolor sit amet consectetur adipiscing elit.
-Ullamcorper eget nulla facilisi etiam dignissim diam quis.
-Ut lectus arcu bibendum at varius vel pharetra.
-Nulla posuere sollicitudin aliquam ultrices sagittis orci a scelerisque.
-Enim nulla aliquet porttitor lacus luctus accumsan tortor posuere.
-Tempor orci eu lobortis elementum nibh tellus molestie.
-Donec massa sapien faucibus et molestie ac feugiat sed.
-Morbi tristique senectus et netus et malesuada fames.
-Interdum velit laoreet id donec ultrices.
+...
 

### 2023-02-10 paper1.Rmd
Clean up of formatting and typesetting throughout.

@@
----
-title: ''
-output: pdf_document
-header-includes:
-  - \usepackage{float}
+```{r paper1code_libraries_data}
 
----
+# Loading libraries
+library(readxl)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(RColorBrewer)
+library(sp)
+library(broom)
+library(sf)
+library(scales)
+library(viridis)
+library(data.table)
+library(ggpubr)
+library(lemon)
+library(rnaturalearth)
+library(rnaturalearthdata)
+library(sysfonts)
+library(showtext)
+font_add_google("Source Sans Pro")
+library(gridExtra)
+showtext_auto() 
+showtext_opts(dpi = 300)
 
-# Chapter 1: Quantifying the global burden of mental disorders and their economic value
+# Setting directories - change these to your local directory
+path <- "C:/Users/danie/Dropbox (Harvard University)/Important Files/3. PhD/WQE/WQE II/gmh_econ/"
+datapath <- paste(path,'data', sep = "/")
+resultspath <- paste(path,'results', sep = "/")
+
+######################
+##       DATA       ##
+######################
+
+# Loading IHME Global Burden of Disease Data
+
+# The data are available for download at http://ghdx.healthdata.org/gbd-results-tool
+# Data should be downloaded for DALYs, YLLs, YLDs, deaths, and prevalence by cause and geographies
+# Save the file as IHME-GBD_2019_DATA-2019.csv
+# If prevalence data are saved separately, save it as IHME-GBD_2019_DATA-2019-prev.csv
+
+data <- read.csv(file = file.path(datapath,"IHME-GBD_2019_DATA-2019.csv"))
+
+# Adding alpha-3 codes from ISO 3166-1 (i.e., World Bank Codes)
+ihme_crosswalk <- read_excel(path = file.path(datapath, "ihme_crosswalk.xlsx")) %>% 
+  select(-c("location_name"))
+data <- left_join(data, ihme_crosswalk, by = "location_id")
+
+# Adding World Bank income classifications
+income_level <- read_excel(path = file.path(datapath, "OGHIST.xls"), sheet = 2) %>% 
+  select(-(c(2:34))) %>% 
+  rename("income_level" = "2019")
+data <- left_join(data, income_level, by = "iso_code")
+
+# Adding population (backed out using IHME rate data for consistency)
+data <- data %>% unique() %>% gather("numeric_name", "est", "val":"lower") 
+data_number <- data %>% filter(metric_id == 1) %>% rename("number" = "est")
+data_rate <- data %>% filter(metric_id == 3) %>% select("measure_id","location_id", "sex_id", "age_id", "cause_id", "year", "numeric_name", "est") %>% rename("rate" = "est")
+data <- left_join(data_number, data_rate, by = c("measure_id","location_id", "sex_id", "age_id", "cause_id", "year", "numeric_name")) %>% 
+  select(!c("metric_id", "metric_name")) %>%
+  unique()
+data$population_100k <- data$number/data$rate
+data$population <- data$population_100k  * 100000
+
+# Removing unused columns
+data <- data %>% select(!c("rate"))  %>% 
+  select(!c("sex_id", "sex_name", "age_id", "age_name", "year")) %>%
+  filter(measure_id != 5)
+
+#######################################################
+##  ORIGINAL AND 2016 REALLOCATION APPROACH  ##
+##################################################
+
+# VIGO EL AL. 2016 WEIGHTS: ALLOCATION OF THE FOLLOWING TO MENTAL HEALTH 
+# (PERCENTS DENOTE AMOUNT REALLOCATED TO MENTAL HEALTH)
+
+# Dementia - 100%
+# Epilepsy - 100%
+# Migraine - 100%
+# Tension-type headache - 100%
+# Self-harm - 100%
+# Chronic pain syndrome currently attributed to musculoskeletal disorders - 33%
+
+# Naming relevant IHME cause IDs
+mental_disorder_cause_id <- 558
+dementia_cause_id1 <- 543 # Alzheimer's disease and other dementias
+dementia_cause_id2 <- 544 # Parkinson's disease
+epilepsy_cause_id <- 545 # Idiopathic epilepsy
+migraine_cause_id <- 547
+tension_type_headache_cause_id <- 548
+self_harm_cause_id <- 718
+alcohol_use_disorders_cause_id <- 560
+drug_use_disorders_cause_id <- 561
+low_back_pain_cause_id <- 630
+neck_pain_cause_id <- 631
+other_musculoskeletal_cause_id <- 639
+all_cause_id <- 294
+
+# Original allocation
+
+# Cause ID 558 reflects the GBD 2019 mental disorder allocation
+# These lines of code retain this allocation and save it under "original value"
+cause_id <- c(mental_disorder_cause_id)
+original_weights <- c(1)
+original_weights_df <- data.frame(cause_id, original_weights)
+data_rev <- left_join(data, original_weights_df, by = c("cause_id"))
+data_rev$original_weights[is.na(data_rev$original_weights)] <- 0
+data_rev$original_value <- data_rev$number * data_rev$original_weights
+
+# 2016 reallocation
+
+cause_id <- c(mental_disorder_cause_id,
+              dementia_cause_id1,
+              dementia_cause_id2,
+              epilepsy_cause_id,
+              migraine_cause_id,
+              tension_type_headache_cause_id,
+              self_harm_cause_id,
+              alcohol_use_disorders_cause_id,
+              drug_use_disorders_cause_id,
+              low_back_pain_cause_id,
+              neck_pain_cause_id,
+              other_musculoskeletal_cause_id,
+              mental_disorder_cause_id,
+              dementia_cause_id1,
+              dementia_cause_id2,
+              epilepsy_cause_id,
+              migraine_cause_id,
+              tension_type_headache_cause_id,
+              self_harm_cause_id,
+              alcohol_use_disorders_cause_id,
+              drug_use_disorders_cause_id,
+              low_back_pain_cause_id,
+              neck_pain_cause_id,
+              other_musculoskeletal_cause_id,
+              mental_disorder_cause_id,
+              dementia_cause_id1,
+              dementia_cause_id2,
+              epilepsy_cause_id,
+              migraine_cause_id,
+              tension_type_headache_cause_id,
+              self_harm_cause_id,
+              alcohol_use_disorders_cause_id,
+              drug_use_disorders_cause_id,
+              low_back_pain_cause_id,
+              neck_pain_cause_id,
+              other_musculoskeletal_cause_id)
+
+numeric_name <- c("val", "val", "val", "val", "val","val", "val", "val", "val", "val", "val","val",
+                  "lower","lower","lower","lower","lower","lower","lower","lower","lower","lower","lower","lower",
+                  "upper","upper","upper","upper","upper","upper","upper","upper","upper","upper","upper","upper")
+
+# Allocations of low back pain, neck pain, and other musculoskeletal disorders is based on
+# the following section of Vigo et al. 2016
+
+# "Considering that a fraction of low back, neck pain,
+# and 50% of other musculoskeletal pain potentially
+# corresponds to chronic pain syndromes, and for the
+# purposes of producing a more accurate estimation and
+# stimulating debate, we assume given the limited data
+# that one third (rather than zero percent, as it is now) of
+# the disease burden of these pain syndromes is
+# potentially attributable to mental disorders and explore
+#  the effect on mental illness burden calculations..."
+
+rev_2016_weights <- c(1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      2/6, # Allocating 1/3
+                      2/6,
+                      1/2*2/6,
+
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1/6, # Allocating 1/6
+                      1/6,
+                      1/2*1/6,
+
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      1,
+                      3/6, # Allocating 1/2 
+                      3/6,
+                      1/2*3/6)
+
+rev_2016_weights_df <- data.frame(cause_id,numeric_name, rev_2016_weights)
+data_rev <- left_join(data_rev, rev_2016_weights_df, by = c("cause_id", "numeric_name"))
+
+data_rev$rev_2016_weights[is.na(data_rev$rev_2016_weights)] <- 0
+data_rev$rev_2016_value <- data_rev$number * data_rev$rev_2016_weights
+
+############################
+##  COMPOSITE APPROACH  ##
+############################
+
+# Due to the distributive property of the Population Attributable Fraction, a category-specific attribution fraction is estimated
+# using the formula from Rockhill et al, 1998:https://pubmed.ncbi.nlm.nih.gov/9584027/
+
+natural_cause_id <- 409 #NCDs
+unnatural_cause_id <- 687 # Injuries
+
+cause_id <- c(natural_cause_id,
+              unnatural_cause_id,
+              natural_cause_id,
+              unnatural_cause_id,
+              natural_cause_id,
+              unnatural_cause_id)
+
+numeric_name <- c("val", "val", 
+                  "lower","lower",
+                  "upper","upper")
+
+relative_risk <- c(1.8,
+                   7.22,
+                   1.71,
+                   6.43,
+                   1.88,
+                   8.12)
+
+relative_risk_df <- data.frame(cause_id,numeric_name, relative_risk)
+
+data_rev <- left_join(data_rev, relative_risk_df, by = c("cause_id", "numeric_name"))
+
+data_prev <- read.csv(file = file.path(datapath,"IHME-GBD_2019_DATA-2019-prev.csv"))
+data_prev <- data_prev %>%
+  gather("numeric_name", "prevalence", "val":"lower")  %>% 
+  select(!c("sex_id", "sex_name", "age_id", "age_name", "year")) %>% filter(cause_id == mental_disorder_cause_id) %>% select("location_id", "numeric_name", "prevalence")
+data_rev  <- left_join(data_rev, data_prev, by = c("location_id", "numeric_name"))
+
+# Two approaches to calculating the PAF are presented here. Later, only one will be retained for the creation of graphs, tables, and charts.
+# In Walker et al., the PAF formula numbered as formula 4 in Rockhill et al. is used, in which prevalence is meant to be the
+# prevalence of mental disorders among cases (i.e., the deceased). The conventional formula, formula 2, takes prevalence as 
+# the prevalence of mental disorders in the general population, but is not internally valid in cases of confounding.
+
+data_rev$paf2 <-     (data_rev$prevalence  * ((data_rev$relative_risk - 1))) /   ((data_rev$prevalence  * ((data_rev$relative_risk - 1))+1))
+data_rev$paf4 <-     data_rev$prevalence  * ((data_rev$relative_risk - 1) /    data_rev$relative_risk)
+
+data_rev <- data_rev%>% gather("paf_formula", "paf", "paf2":"paf4") 
+data_rev$paf[is.na(data_rev$paf)] <- 0
+data_rev$rev_2015_value <- data_rev$number * data_rev$paf
+
+# Combine original and re-allocated values by location, measure, PAF formula used, and numeric value (point estimate, and upper or lower bounds)
+data_rev <- data_rev %>% 
+  group_by(location_id, measure_id, numeric_name, paf_formula) %>% 
+  mutate(rev_2016_value_agg = sum(rev_2016_value),  rev_2015_value_agg = sum(rev_2015_value),original_value_agg = sum(original_value)) %>%
+  rename("measure_total" = number) %>%
+  ungroup %>%
+  filter(cause_id == "294") %>% select(!c("original_weights":"relative_risk", "paf":"rev_2015_value"))
+
+# Clean up
+
+############################
+##  COMPOSITE METHOD  ##
+############################
+
+# This method pulls YLLs from Walker et al. and YLDs from Vigo et al. together to re-estimate 
+# DALYs attributable to mental disorders.
+
+# Draw in YLDs from Vigo et al.
+data_rev$composite_ylds <-ifelse(data_rev$measure_id == 3, data_rev$rev_2016_value_agg, 0)
+
+# Draw in YLLs from Walker et al.
+data_rev$composite_ylls <-ifelse(data_rev$measure_id == 4, data_rev$rev_2015_value_agg, 0)
+
+# Combine to calculate DALYs
+data_rev_composite <- data_rev %>% select(location_id, numeric_name, paf_formula, measure_id, composite_ylds, composite_ylls) %>%
+  group_by(location_id, numeric_name, paf_formula) %>%
+  mutate(composite_dalys = sum(composite_ylds, composite_ylls))
+data_rev_composite <- data_rev_composite %>% filter(measure_id == 2) %>% ungroup() %>% unique() %>% select("location_id", "numeric_name", "paf_formula", "composite_dalys") 
+data_rev <- left_join(data_rev, data_rev_composite, by = c("location_id", "numeric_name", "paf_formula"))
+data_rev$composite_dalys[data_rev$measure_id != 2] <- 0
+data_rev$composite_ylds[data_rev$measure_id != 3] <- 0
+data_rev$composite_ylls[data_rev$measure_id != 4] <- 0
+
+# Draw in deaths from Walker et al.
+data_rev$composite_deaths <-ifelse(data_rev$measure_id == 1, data_rev$rev_2015_value_agg, 0)
+data_rev$composite_deaths[data_rev$measure_id != 1] <- 0
+
+# Combined columns, clean up, re-organizing, tidying, and labeling
+data_rev$composite <- data_rev$composite_ylds + data_rev$composite_ylls + data_rev$composite_dalys + data_rev$composite_deaths
+data_rev <- data_rev %>% select(!c("composite_ylds":"composite_deaths")) %>%  relocate(original_value_agg, .after = paf_formula) %>%
+  relocate(numeric_name, .after = prevalence) %>%  
+  rename("Composite method" = composite,
+         "PAF method" = rev_2015_value_agg,
+         "2016 reallocation approach" = rev_2016_value_agg,
+         "GBD 2019" = original_value_agg)
+
+data_rev$cause_name <- "Mental disorders"
+data_rev <- data_rev %>% gather("estimate", "number", "GBD 2019":"Composite method")
+
+data_rev$estimate_id <- ifelse(data_rev$estimate == "Composite method", 4, 
+                               ifelse(data_rev$estimate == "PAF method", 3,
+                                      ifelse(data_rev$estimate == "2016 reallocation approach", 2, 1)))
+data_rev <- data_rev %>% relocate(estimate_id, .after = estimate)
+
+# Calculate rates and percent of burden
+data_rev <- data_rev %>% relocate (population_100k, .after = population)
+data_rev$rate_per_100k <- data_rev$number/data_rev$population_100k
+data_rev$percent <- data_rev$number/data_rev$measure_total*100
+
+############################
+##        COSTING         ##
+############################
+
+# Import GDP
+gdp_data <- read.csv(file = file.path(datapath,# "wdi_gdp_ppp.csv"  # Using PPP
+                                      "wdi_gdp.csv"                  # Not using PPP
+)) %>%
+  select(-(c(3:62))) %>% 
+  rename("gdp" = "X2019")
+gdp <- gdp_data %>% select(c(iso_code, gdp))
+data_rev <- left_join(data_rev, gdp, by = "iso_code")
+data_rev <- data_rev %>% relocate(gdp, .after = iso_code)
+data_rev$gdp[data_rev$location_id == 1] <- gdp_data$gdp[gdp_data$iso_code == "WLD"] # GDP for the world
+
+# Calculate GDP per capita, with reference to IHME population values, for consistency
+data_rev$gdp_per_capita <- data_rev$gdp/data_rev$population
+data_rev <- data_rev %>% relocate (gdp_per_capita, .after = gdp)
+
+# Clean up
+
+# Import GDP PPP
+gdp_data <- read.csv(file = file.path(datapath, "wdi_gdp_ppp.csv"  # Using PPP
+                                      #"wdi_gdp.csv"                  # Not using PPP
+)) %>%
+  select(-(c(3:62))) %>% 
+  rename("gdp_ppp" = "X2019")
+gdp <- gdp_data %>% select(c(iso_code, gdp_ppp))
+data_rev <- left_join(data_rev, gdp, by = "iso_code")
+data_rev <- data_rev %>% relocate(gdp_ppp, .after = iso_code)
+data_rev$gdp_ppp[data_rev$location_id == 1] <- gdp_data$gdp_ppp[gdp_data$iso_code == "WLD"] # GDP for the world
+
+# Calculate GDP per capita, with reference to IHME population values, for consistency
+data_rev$gdp_ppp_per_capita <- data_rev$gdp_ppp/data_rev$population
+data_rev <- data_rev %>% relocate (gdp_ppp_per_capita, .after = gdp_ppp)
+
+# Clean up
+
+############################
+# Cost per DALY
+
+# Method 1: Copenhagen Consensus 1 - $1,000
+data_rev$cost_cc1 <- ifelse(data_rev$measure_id == 2,
+                            data_rev$number * 1000, 0)
+
+# Method 2: Copenhagen Consensus 2 - $5,000
+data_rev$cost_cc2 <- data_rev$cost_cc1 * 5
+
+# Method 3: WHO - GDP/capita
+data_rev$cost_who1 <-ifelse(data_rev$measure_id == 2,
+                            data_rev$number * data_rev$gdp_per_capita, 0)
+
+# Method 4: WHO - GDP/capita * 3
+data_rev$cost_who2 <- data_rev$cost_who1 * 3
+
+# Method 5: WHO - GDP PPP/capita
+data_rev$cost_who3 <-ifelse(data_rev$measure_id == 2,
+                            data_rev$number * data_rev$gdp_ppp_per_capita, 0)
+
+# Method 6: WHO - GDP PPP/capita * 3
+data_rev$cost_who4 <- data_rev$cost_who3 * 3
+
+##################################
+##         PAF FORMULA          ##
+##################################
+
+# Select which of the PAF formulae to use for the remainder of the analysis
+
+data_rev <- data_rev %>% filter(paf_formula == "paf2") # Conventional formula
+# data_rev <- data_rev %>% filter(paf_formula == "paf4") # Case prevalence formula
+
+################################
+##         MAP PREP           ##
+################################
+
+data_rev_gbd <- data_rev %>% filter(estimate_id == 1) %>% 
+  select (c(measure_id, location_id, numeric_name, paf_formula, number:cost_who4)) %>%
+  rename(
+    "number_gbd" = "number",
+    "rate_per_100k_gbd" = "rate_per_100k",
+    "percent_gbd" = "percent",
+    "cost_cc1_gbd" = "cost_cc1",
+    "cost_cc2_gbd" = "cost_cc2",
+    "cost_who1_gbd" = "cost_who1",
+    "cost_who2_gbd" = "cost_who2",
+    "cost_who3_gbd" = "cost_who3",
+    "cost_who4_gbd" = "cost_who4")
+
+data_rev <- left_join(data_rev, data_rev_gbd, by = c("location_id", "measure_id", "numeric_name", "paf_formula"))
+
+data_rev <- data_rev %>% mutate(
+  number_diff = number - number_gbd,
+  rate_per_100k_diff = rate_per_100k - rate_per_100k_gbd,
+  percent_diff = percent - percent_gbd,
+  cost_cc1_diff = cost_cc1 - cost_cc1_gbd,
+  cost_cc2_diff = cost_cc2 - cost_cc2_gbd,
+  cost_who1_diff = cost_who1 - cost_who1_gbd,
+  cost_who2_diff = cost_who2 - cost_who2_gbd,
+  cost_who3_diff = cost_who3 - cost_who3_gbd,
+  cost_who4_diff = cost_who4 - cost_who4_gbd)
+
+# Import regional data
+region <- read_excel(path = file.path(datapath, "regions.xlsx"))
+
+# Merge
+region <- region %>% select (iso_code, who_region, ihme_region)
+data_rev <- full_join(data_rev, region, by = "iso_code")
+
+# WHO region map prep
+
+data_rev <- data_rev %>% group_by(estimate_id, measure_id, numeric_name, paf_formula, who_region) %>% 
+  mutate(who_region_pop100k = sum(population_100k),
+         who_region_number = sum(number),
+         who_region_measure_total = sum(measure_total),
+         who_region_gdp = sum(gdp, na.rm=TRUE),
+         who_region_gdp_ppp = sum(gdp_ppp, na.rm=TRUE))%>%
+  mutate(who_region_rate_per_100k = who_region_number/who_region_pop100k,
+         who_region_percent = who_region_number/who_region_measure_total*100,
+         who_region_population = who_region_pop100k * 100000) %>%
+  mutate(who_region_gdp_per_capita = who_region_gdp/who_region_population,
+         who_region_gdp_ppp_per_capita = who_region_gdp_ppp/who_region_population,
+         who_region_cost_cc1 = ifelse(measure_id == 2,
+                                      who_region_number * 1000, 0),
+         who_region_cost_cc2 = who_region_cost_cc1 * 5,
+         who_region_cost_who1 = ifelse(measure_id == 2,
+                                       who_region_number * who_region_gdp_per_capita, 0),
+         who_region_cost_who2 = who_region_cost_who1 * 3,
+         who_region_cost_who3 = ifelse(measure_id == 2,
+                                       who_region_number * who_region_gdp_ppp_per_capita, 0),
+         who_region_cost_who4 = who_region_cost_who3 * 3) %>%
+  ungroup()
+
+data_rev_gbd_who_region<- data_rev %>% filter(estimate_id == 1) %>% 
+  select (c(measure_id, location_id, numeric_name, paf_formula, who_region_number:who_region_cost_who4)) %>%
+  rename(
+    "who_region_number_gbd" = "who_region_number",
+    "who_region_rate_per_100k_gbd" = "who_region_rate_per_100k",
+    "who_region_percent_gbd" = "who_region_percent",
+    "who_region_cost_cc1_gbd" = "who_region_cost_cc1",
+    "who_region_cost_cc2_gbd" = "who_region_cost_cc2",
+    "who_region_cost_who1_gbd" = "who_region_cost_who1",
+    "who_region_cost_who2_gbd" = "who_region_cost_who2",
+    "who_region_cost_who3_gbd" = "who_region_cost_who3",
+    "who_region_cost_who4_gbd" = "who_region_cost_who4"
+  )  %>%
+  select(measure_id, location_id, numeric_name, paf_formula, who_region_number_gbd, who_region_rate_per_100k_gbd, who_region_percent_gbd,
+         who_region_cost_cc1_gbd, who_region_cost_cc2_gbd, who_region_cost_who1_gbd, 
+         who_region_cost_who2_gbd, who_region_cost_who3_gbd, who_region_cost_who4_gbd)
+
+data_rev <- left_join(data_rev, data_rev_gbd_who_region, by = c("location_id", "measure_id", "numeric_name", "paf_formula"))
+
+data_rev <- data_rev %>% mutate(
+  who_region_number_diff = who_region_number - who_region_number_gbd,
+  who_region_rate_per_100k_diff = who_region_rate_per_100k - who_region_rate_per_100k_gbd,
+  who_region_percent_diff = who_region_percent - who_region_percent_gbd,
+  who_region_cost_cc1_diff = who_region_cost_cc1 - who_region_cost_cc1_gbd,
+  who_region_cost_cc2_diff = who_region_cost_cc2 - who_region_cost_cc2_gbd,
+  who_region_cost_who1_diff = who_region_cost_who1 - who_region_cost_who1_gbd,
+  who_region_cost_who2_diff = who_region_cost_who2 - who_region_cost_who2_gbd,
+  who_region_cost_who3_diff = who_region_cost_who3 - who_region_cost_who3_gbd,
+  who_region_cost_who4_diff = who_region_cost_who4 - who_region_cost_who4_gbd)
+
+# IHME region  map prep
+
+data_rev <- data_rev %>% group_by(estimate_id, measure_id, numeric_name, paf_formula, ihme_region) %>% 
+  mutate(ihme_region_pop100k = sum(population_100k),
+         ihme_region_number = sum(number),
+         ihme_region_measure_total = sum(measure_total),
+         ihme_region_gdp = sum(gdp, na.rm=TRUE),
+         ihme_region_gdp_ppp = sum(gdp_ppp, na.rm=TRUE))%>%
+  mutate(ihme_region_rate_per_100k = ihme_region_number/ihme_region_pop100k,
+         ihme_region_percent = ihme_region_number/ihme_region_measure_total*100,
+         ihme_region_population = ihme_region_pop100k * 100000) %>%
+  mutate(ihme_region_gdp_per_capita = ihme_region_gdp/ihme_region_population,
+         ihme_region_gdp_ppp_per_capita = ihme_region_gdp_ppp/ihme_region_population,
+         ihme_region_cost_cc1 = ifelse(measure_id == 2,
+                                       ihme_region_number * 1000, 0),
+         ihme_region_cost_cc2 = ihme_region_cost_cc1 * 5,
+         ihme_region_cost_who1 = ifelse(measure_id == 2,
+                                        ihme_region_number * ihme_region_gdp_per_capita, 0),
+         ihme_region_cost_who2 = ihme_region_cost_who1 * 3,
+         ihme_region_cost_who3 = ifelse(measure_id == 2,
+                                        ihme_region_number * ihme_region_gdp_ppp_per_capita, 0),
+         ihme_region_cost_who4 = ihme_region_cost_who3 * 3) %>%
+  ungroup()
+
+data_rev_gbd_ihme_region<- data_rev %>% filter(estimate_id == 1) %>% 
+  select (c(measure_id, location_id, numeric_name, paf_formula, ihme_region_number:ihme_region_cost_who4)) %>%
+  rename(
+    "ihme_region_number_gbd" = "ihme_region_number",
+    "ihme_region_rate_per_100k_gbd" = "ihme_region_rate_per_100k",
+    "ihme_region_percent_gbd" = "ihme_region_percent",
+    "ihme_region_cost_cc1_gbd" = "ihme_region_cost_cc1",
+    "ihme_region_cost_cc2_gbd" = "ihme_region_cost_cc2",
+    "ihme_region_cost_who1_gbd" = "ihme_region_cost_who1",
+    "ihme_region_cost_who2_gbd" = "ihme_region_cost_who2",
+    "ihme_region_cost_who3_gbd" = "ihme_region_cost_who3",
+    "ihme_region_cost_who4_gbd" = "ihme_region_cost_who4"
+  )  %>%
+  select(measure_id, location_id, numeric_name, paf_formula, ihme_region_number_gbd, ihme_region_rate_per_100k_gbd, ihme_region_percent_gbd,
+         ihme_region_cost_cc1_gbd, ihme_region_cost_cc2_gbd, ihme_region_cost_who1_gbd, 
+         ihme_region_cost_who2_gbd, ihme_region_cost_who3_gbd, ihme_region_cost_who4_gbd)
+
+data_rev <- left_join(data_rev, data_rev_gbd_ihme_region, by = c("location_id", "measure_id", "numeric_name", "paf_formula"))
+
+data_rev <- data_rev %>% mutate(
+  ihme_region_number_diff = ihme_region_number - ihme_region_number_gbd,
+  ihme_region_rate_per_100k_diff = ihme_region_rate_per_100k - ihme_region_rate_per_100k_gbd,
+  ihme_region_percent_diff = ihme_region_percent - ihme_region_percent_gbd,
+  ihme_region_cost_cc1_diff = ihme_region_cost_cc1 - ihme_region_cost_cc1_gbd,
+  ihme_region_cost_cc2_diff = ihme_region_cost_cc2 - ihme_region_cost_cc2_gbd,
+  ihme_region_cost_who1_diff = ihme_region_cost_who1 - ihme_region_cost_who1_gbd,
+  ihme_region_cost_who2_diff = ihme_region_cost_who2 - ihme_region_cost_who2_gbd,
+  ihme_region_cost_who3_diff = ihme_region_cost_who3 - ihme_region_cost_who3_gbd,
+  ihme_region_cost_who4_diff = ihme_region_cost_who4 - ihme_region_cost_who4_gbd)
+
+# Import map data
+world <- ne_countries(scale = "medium", returnclass = "sf")
+world$iso_code <- world$gu_a3
+world$iso_code[world$adm0_a3 == "SDS"] <- "SSD"
+
+# Re-order estimates: original, Vigo, Walker, composite
+
+data_rev <- data_rev %>% 
+  mutate(estimate_newlab = recode(estimate, 
+                                  'GBD 2019' = "Original approach",                
+                                  '2016 reallocation approach' = "Reallocation approach",
+                                  'PAF method' = "PAF method",              
+                                  'Composite method'= "Composite approach"  
+  ))
+
+data_rev$estimate_newlab <- factor(data_rev$estimate_newlab ,      # Reordering group factor levels
+                                   levels = c("Original approach",
+                                              "Reallocation approach",
+                                              "PAF method",
+                                              "Composite approach"))
+# Merging map and dataframe
+data_rev_map <- full_join(world, data_rev, by = "iso_code") %>% filter(numeric_name == "val")
+
+# Clean up
+
+# Standard subtitles, and captions
+subtitle_1 <- "Value per DALY: $1,000"
+subtitle_2 <- "Value per DALY: $5,000"
+subtitle_3 <- "Value per DALY: GDP/capita"
+subtitle_4 <- "Value per DALY: 3 X GDP/capita"
+#caption <- "Source: Global Burden of Disease Study. Reallocation approach from Vigo et al. 2016."
+
+```
+
+```{r paper1code_results}
+
+####################################
+##       REGIONAL CHARTS          ##
+####################################
+
+who_region_positions <- c("African Region", "Eastern Mediterranean Region", "European Region",
+                          "Region of the Americas", "South-East Asia Region", "Western Pacific Region",  "#NA")
+
+who_region_pal <-  c("#E74C3C", "#E67E22" , "#F4D03F", "#45B39D", "#5499C7", "#AF7AC5")
+
+ihme_region_positions <- c("East Asia", "Southeast Asia", "Oceania", "Central Asia", "Eastern Europe", "Central Europe",
+                           "Caribbean", "Central Latin America", "Tropical Latin America", "Andean Latin America", "North Africa and Middle East",
+                           "Southern Sub-Saharan Africa", "Western Sub-Saharan Africa", "Central Sub-Saharan Africa", "Eastern Sub-Saharan Africa",
+                           "South Asia", "Southern Latin America", "Western Europe", "High-income North America",
+                           "Australasia", "High-income Asia Pacific", "#NA")
+
+ihme_pal_new <- c("#002673", "#005CE6", "#73DFFF", "#E54800", "#E69800", "#FFD37F",
+                  "#216F00", "#33A600", "#4CE600", "#A3FF73", "#4E4E4E", 
+                  "#730000", "#FF0000", "#FF7F7F", "#FFBEBE", 
+                  "#E6E600", "#73004C", "#A80084", "#C500FF", "#E600A9", "#FFBEE8", "#7F7F7F")
+
+ihme_region_pal <- c("#8C95F1", "#D7ECFC" , "#B6CDD4", "#EAA144", "#F3DA89", "#F9EFC2", "#B1F585", "#B6F2D5",
+                     "#E3FD8C", "#E2FDD7", "#99ACA4", "#9D5F56", "#E989A9", "#F5DBD8", "#F8EEEF",
+                     "#F4FF7C", "#C42AF1", "#E986F8", "#D7C2FC", "#DD9BE9", "#FAE5FE", "#7F7F7F")
+
+############################
+##        TABLES          ##
+############################
+
+# Table 1: Burden of disease due to mental disorders
+
+data_global <- data_rev %>% filter(location_id == 1)  %>% filter(estimate_id != 3)  %>% select(location_name, measure_name, numeric_name, estimate, number, percent) %>%
+  mutate(number = round(number/1000000, 1),
+         percent = round(percent, 1))
+
+data_regional <- data_rev  %>% filter(estimate_id != 3)  %>% 
+  group_by(ihme_region,measure_name, numeric_name, estimate) %>% mutate(region_total = sum(measure_total),
+                                                                        region_number = sum(number)) %>%
+  mutate(region_percent = round(region_number / region_total * 100, 1)) %>% select(ihme_region, measure_name, numeric_name, estimate, region_number, region_percent) %>%
+  rename("number" = "region_number",
+         "percent" = "region_percent",
+         "location_name" = "ihme_region") %>%
+  ungroup() %>%
+  unique() %>% filter(!is.na(location_name)) %>%
+  mutate(number = round(number/1000000, 1)) %>% arrange((location_name))
+
+data_income <- data_rev  %>% filter(estimate_id != 3)  %>% 
+  group_by(income_level,measure_name, numeric_name, estimate) %>% mutate(region_total = sum(measure_total),
+                                                                         region_number = sum(number)) %>%
+  mutate(region_percent = round(region_number / region_total * 100, 1)) %>% select(income_level, measure_name, numeric_name, estimate, region_number, region_percent) %>%
+  rename("number" = "region_number",
+         "percent" = "region_percent",
+         "location_name" = "income_level") %>%
+  ungroup() %>%
+  unique() %>% filter(!is.na(location_name)) %>%
+  mutate(number = round(number/1000000, 1))
+
+location_name <- c("H","UM","LM","L")
+rank <- c(1,2,3,4)
+fullname <- c("High income",
+              "Upper-middle income",
+              "Lower-middle income",
+              "Low income")
+
+incomelevels <- data.frame(location_name,rank, fullname)
+
+data_income <- left_join(data_income, incomelevels, by = "location_name") %>% arrange(rank) %>% select(!c(location_name, rank)) %>% rename("location_name" = "fullname")
+
+data_table1 <- rbind(data_global, data_income, data_regional) %>% 
+  gather("metric","point","number":"percent" ) %>%  
+  pivot_wider(names_from = c(numeric_name, metric, estimate), values_from = point)
+
+col_order <- c(
+  "measure_name",
+  "location_name",                                    
+  "val_number_GBD 2019",                             
+  "lower_number_GBD 2019",                            
+  "upper_number_GBD 2019",   
+  "val_percent_GBD 2019",                            
+  "lower_percent_GBD 2019",  
+  "upper_percent_GBD 2019",                           
+  "val_number_2016 reallocation approach",   
+  "lower_number_2016 reallocation approach",  
+  "upper_number_2016 reallocation approach",  
+  "val_percent_2016 reallocation approach",  
+  "lower_percent_2016 reallocation approach", 
+  "upper_percent_2016 reallocation approach", 
+  "val_number_Composite method",           
+  "lower_number_Composite method",          
+  "upper_number_Composite method",          
+  "val_percent_Composite method",          
+  "lower_percent_Composite method",  
+  "upper_percent_Composite method")
+
+data_table1 <- data_table1[, col_order]
+
+data_table1 <- data_table1 %>% arrange(measure_name)
+
+write.csv(data_table1, file = paste0(resultspath, "/table1.csv"))
+
+# Table 2: Value of economic welfare estimates
+
+data_global <- data_rev %>% 
+  filter(location_id == 1)  %>% 
+  filter(measure_id == 2) %>%
+  filter(estimate_id != 3)  %>% 
+  select(location_name, numeric_name, 
+         estimate, cost_cc1, cost_cc2, cost_who1, cost_who2, cost_who3, cost_who4)
+
+data_global$location_name <- "Global"
+
+data_regional <- data_rev  %>%   
+  filter(measure_id == 2) %>%
+  filter(estimate_id != 3)  %>% 
+  select(ihme_region,numeric_name, estimate, ihme_region_cost_cc1,
+         ihme_region_cost_cc2, ihme_region_cost_who1, ihme_region_cost_who2, ihme_region_cost_who3, ihme_region_cost_who4) %>%
+  unique() %>%
+  rename("location_name" =ihme_region,
+         "cost_cc1" = ihme_region_cost_cc1,
+         "cost_cc2" = ihme_region_cost_cc2,
+         "cost_who1" = ihme_region_cost_who1,
+         "cost_who2" = ihme_region_cost_who2,
+         "cost_who3" = ihme_region_cost_who3,
+         "cost_who4" = ihme_region_cost_who4) %>%
+  filter(!is.na(location_name)) %>% 
+  arrange((location_name))
+
+data_income <- data_rev  %>% 
+  filter(measure_id == 2) %>%
+  filter(estimate_id != 3)  %>%  
+  select(income_level, estimate, numeric_name, cost_cc1, cost_cc2, cost_who1, cost_who2,  cost_who3, cost_who4) %>%
+  pivot_longer(cols = cost_cc1:cost_who4) %>%
+  group_by(income_level,numeric_name, name, estimate) %>% 
+  mutate(cost_total = sum(value, na.rm = TRUE)) %>%
+  ungroup() %>%
+  select(income_level, numeric_name, name, cost_total, estimate) %>% unique() %>%
+  rename("location_name" = income_level)
+
+location_name <- c("H","UM","LM","L")
+rank <- c(1,2,3,4)
+fullname <- c("High income",
+              "Upper-middle income",
+              "Lower-middle income",
+              "Low income")
+
+incomelevels <- data.frame(location_name,rank, fullname)
+
+data_income <- left_join(data_income, incomelevels, by = "location_name") %>% 
+  arrange(rank) %>% select(!c(location_name, rank)) %>% rename("location_name" = "fullname")
+
+data_income <- data_income %>% 
+  pivot_wider(values_from = cost_total, names_from = name) %>%
+  filter(!is.na(location_name))
+
+#### Pivot wider, change column names, drop NA for income levels
+
+data_table2 <- rbind(data_global, data_income, data_regional) %>% 
+  arrange(factor(numeric_name, levels = c("val", "lower", "upper"))) %>%
+  arrange(factor(estimate, levels = c("GBD 2019", "2016 reallocation approach", "Composite method"))) %>%
+  pivot_longer(cols = cost_cc1:cost_who4) %>%
+  mutate(value = round(value/1000000000000,2)) %>%
+  pivot_wider(names_from = c(numeric_name, estimate), values_from = value) %>%
+  arrange(name) %>%
+  relocate(name, .before = "location_name")
+
+# write.csv(data_table2, file = paste0(resultspath, "/table2.csv"))
+
+# Appendix 2: Value of economic welfare estimates (CC)
+
+appendix_table <- data_rev %>% filter(location_id == 1) %>%  
+  filter(measure_id == 2) %>% filter(estimate_id != 3) %>% 
+  select(estimate, numeric_name, cost_cc1, cost_cc2, cost_who1, cost_who2, cost_who3, cost_who4)
+appendix_table$cost_cc1 <- round(appendix_table$cost_cc1/1000000000000,2)
+appendix_table$cost_cc2 <- round(appendix_table$cost_cc2/1000000000000,2)
+appendix_table$cost_who1 <- round(appendix_table$cost_who1/1000000000000,2)
+appendix_table$cost_who2 <- round(appendix_table$cost_who2/1000000000000,2)
+appendix_table$cost_who3 <- round(appendix_table$cost_who3/1000000000000,2)
+appendix_table$cost_who4 <- round(appendix_table$cost_who4/1000000000000,2)
+appendix_table <- appendix_table %>% select(!c(cost_who1, cost_who2)) %>% arrange(estimate, factor(numeric_name, levels = c("val", "lower", "upper")))
+appendix_table_t <- transpose(appendix_table)
+
+colnames(appendix_table_t) <- rownames(appendix_table)
+rownames(appendix_table_t) <- colnames(appendix_table)
+
+# write.csv(appendix_table_t, file = paste0(resultspath, "/table_appendix.csv"))
+
+```
+
+```{r paper1code_text}
+
+############################
+##        VALUES          ##
+############################
+
+# Key values and calculations for Abstract and Results
+
+# Abstract
+
+abstract1 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Global") %>% 
+  select("val_number_Composite method") %>% 
+  unique()
+abstract1 <- as.numeric(abstract1)
+abstract1 <- round(abstract1, 0)
+
+abstract2 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Global") %>% 
+  select("val_percent_Composite method") %>% 
+  unique()
+abstract2 <- as.numeric(abstract2)
+abstract2 <- floor(abstract2)
+
+abstract3 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Global") %>% 
+  select("val_number_GBD 2019") %>% 
+  unique()
+abstract3 <- as.numeric(abstract3)
+abstract3 <- round(abstract3, 0)
+
+abstract_sentence1 <- paste0("We estimate that ",
+                             abstract1,
+                             " million disability-adjusted life years (DALYs) could be attributable to mental disorders in 2019 (",
+                             abstract2,
+                             "\\% of global DALYs)",
+                             ifelse(abstract1/abstract3>3,", a more than ",", an approximate "), 
+                             "three-fold increase compared to conventional estimates. ")
+
+abstract4 <- data_table2%>% 
+  filter(name == "cost_who1") %>% 
+  filter(location_name == "Global") %>%
+  select(`val_Composite method`) %>%
+  unique()
+abstract4 <- as.numeric(abstract4)
+abstract4 <- floor(abstract4*10)/10
+
+abstract_sentence2 <- paste0("The economic value associated with this burden is estimated at about USD ",
+                             abstract4,
+                             " trillion. ")
+
+table3 <- data_rev %>% 
+  filter(numeric_name == "val") %>%
+  select(measure_id, estimate, estimate_id, ihme_region, ihme_region_cost_who1, ihme_region_gdp) %>% 
+  unique %>%
+  filter(measure_id== "2") %>% 
+  filter(estimate_id== "4") %>% mutate(
+    regional_percent = ihme_region_cost_who1 / ihme_region_gdp *100)
+
+abstract5 <- table3$ihme_region[table3$regional_percent == max(table3$regional_percent)]
+abstract6 <- round(table3$regional_percent[table3$regional_percent == max(table3$regional_percent)],1)
+
+abstract7 <- table3$ihme_region[table3$regional_percent == min(table3$regional_percent)]
+abstract8 <- round(table3$regional_percent[table3$regional_percent == min(table3$regional_percent)],1)
+
+abstract_sentence3 <- paste0("At a regional level, the losses account for between ",
+                             abstract8,
+                             "\\% of gross domestic product in ",
+                             abstract7,
+                             " and ",
+                             abstract6,
+                             "\\% in ",
+                             abstract5,
+                             ". ")
+
+# Results
+
+results1 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Global") %>% 
+  select("val_number_GBD 2019") %>% 
+  unique()
+results1 <- as.numeric(results1)
+results1 <- floor(results1)
+
+results2 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Global") %>% 
+  select("val_percent_GBD 2019") %>% 
+  unique()
+results2 <- as.numeric(results2)
+results2 <- round(results2,0)
+
+results3 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Global") %>% 
+  select("val_percent_2016 reallocation approach") %>% 
+  unique()
+results3 <- as.numeric(results3)
+results3 <- floor(results3)
+
+results4 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Global") %>% 
+  select("val_number_2016 reallocation approach") %>% 
+  unique()
+results4 <- as.numeric(results4)
+results4 <- floor(results4)
+
+results5 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="High income") %>% 
+  select("val_number_Composite method") %>% 
+  unique()
+results5 <- as.numeric(results5)
+results5 <- round(results5, 0)
+
+results6 <- data_table1 %>% 
+  filter(measure_name=="DALYs (Disability-Adjusted Life Years)") %>% 
+  filter(location_name =="Low income") %>% 
+  select("val_number_Composite method") %>% 
+  unique()
+results6 <- as.numeric(results6)
+results6 <- round(results6, 0)
+
+results_sentence1 <- paste0(
+  "Under GBD 2019, over ",
+  results1,
+  " million DALYs were attributed to mental disorders, or roughly ",
+  results2,
+  "\\% of the global burden. After including alcohol and drug use, neurological disorders, chronic pain, suicide, and self-harm, the share due to mental disorders rose to ",
+  results3,
+  "\\% of global DALYs (approximately ",
+  results4,
+  " million DALYs). Under the composite approach, an additional  ",
+  abstract1-results4,
+  " million DALYs were attributed to mental disorders, encompassing, in total, over ",
+  abstract2,
+  "\\% of global DALYs. Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising ",
+  ifelse(results5/results6 > 2.4, "over twice", ifelse(results5/results6> 2, "roughly twice", "approximately twice")),
+  " the burden of disease in high-income countries compared to low-income countries.")
+
+results7 <- data_table2%>% 
+  filter(name == "cost_who1") %>% 
+  filter(location_name == "Global") %>%
+  select(`val_Composite method`) %>%
+  unique()
+results7 <- as.numeric(results7)
+
+results8 <- data_table2%>% 
+  filter(name == "cost_who1") %>% 
+  filter(location_name == "Global") %>%
+  select(`val_2016 reallocation approach`) %>%
+  unique()
+results8 <- as.numeric(results8)
+
+results9 <- data_table2%>% 
+  filter(name == "cost_who1") %>% 
+  filter(location_name == "Global") %>%
+  select(`val_GBD 2019`) %>%
+  unique()
+results9 <- as.numeric(results9)
+
+results_sentence2 <- paste0(
+  "Using GDP per capita as a proxy for the value per DALY, economic losses due to mental disorders were estimated at ",
+  abstract4,
+  " trillion USD using our composite approach. This estimate is ",
+  floor((results7 - results8)*10)/10,
+  " trillion USD larger than that reached using the 2016 reallocation approach and over ",
+  floor((results7 - results9)*10)/10,
+  " trillion USD larger than that reached from the unadjusted GBD 2019 estimates.")
+
+results_sentence3 <- paste0(
+  "Under the relative GDP-per-capita values the economic burden would account for between ",
+  abstract8,
+  "\\% of gross domestic product in ",
+  abstract7,
+  " and ",
+  abstract6,
+  "\\% in ",
+  abstract5,
+  " under our composite approach.")
+
+# Discussion
+
+discussion_sentence1 <- paste0(
+  "This approach suggests that the global DALYs attributable to mental disorders could exceed ",
+  abstract1,
+  " million per year, or ",
+  abstract2,
+  "\\% of the total burden.")
+
+discussion1 <- data_table2%>% 
+  filter(name == "cost_who1") %>% 
+  filter(location_name == "Global") %>%
+  select(`lower_Composite method`) %>%
+  unique()
+discussion1 <- as.numeric(discussion1)
+
+discussion2 <- data_table2%>% 
+  filter(name == "cost_who1") %>% 
+  filter(location_name == "Global") %>%
+  select(`upper_Composite method`) %>%
+  unique()
+discussion2 <- as.numeric(discussion2)
+
+discussion_sentence2 <- paste0(
+  "When applied against an economic value per DALY of one times GDP per capita, this approach further suggests that the per year losses associated with this burden could exceed ",
+  abstract4,
+  " trillion USD in 2019. When adjusting for the uncertainty in estimates of the attributable burden of disease, the losses could range from ",
+  floor((discussion1)*10)/10,
+  " trillion to more than ",
+  floor((discussion2)*10)/10,
+  " trillion USD.")
+
+discussion_sentence3 <- paste0("We estimate that in 2019, the losses would already be over ",
+                               floor((abstract4 - 2.9)*10)/10,
+                               " trillion USD greater than Bloom and colleagues’ global losses projections for 2030 (2.9 trillion 2019 USD, using the same value per DALY approach).")
+
+```
+
+# Quantifying the global burden of mental disorders and their economic value
+
+\begin{centering}
+
+\emph{Daniel Arias, Shekhar Saxena, Stéphane Verguet}
+
+\vspace{6pt}
+
+\noindent\rule{8cm}{0.4pt}
+
+A version of this paper was accepted for publication by \emph{eClinicalMedicine} on September 9, 2022 and was published in Volume 54, Issue 101675 in December 2022.
+
+\noindent\rule{8cm}{0.4pt}
+
+\end{centering}
 
@@
 
+\vspace{6pt}
+
 {\bf Background:} Epidemiological and economic estimates suggest that the global burden of mental disorders is considerable, both in its impacts on human health and losses to societal welfare.
-The availability of additional data and the emergence of new approaches present an opportunity to examine these estimates, which form a critical part in making the investment case for global mental health.
+The availability of additional data and the emergence of new approaches present an opportunity to examine these estimates, which form a critical part in making the investment case for mental health.
 
@@
 
-{\bf Findings:} We estimate that 418 million disability-adjusted life years (DALYs) could be attributable to mental disorders in 2019 (16\% of global DALYs)—a more than three-fold increase compared to conventional estimates.
-The economic value associated with this burden is estimated at about USD 5 trillion.
-At a regional level, the losses could account for between 4\% of gross domestic product in Eastern sub-Saharan Africa and 8\% in High-income North America.
-
-{\bf Interpretation:} The burden of mental illness in terms of both health and economic losses may be much higher than previously assessed.
-
-{\bf Funding:} None.
+{\bf Findings and interpretation:} `r paste0(abstract_sentence1, abstract_sentence2, abstract_sentence3)` Taken together, our findings suggest that the burden of mental illness in terms of both health and economic losses may be much higher than previously assessed.
 
@@
 
-With a third of disability-adjusted life years (DALYs) due to NCDs arising from mental disorders, this landmark paper estimated that the value of losses due to mental disorders was roughly 1·3 trillion USD in 2010 (1·6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2·5 trillion USD 2010 (or approximately 3·0 trillion USD in 2019) by 2030.
+With a third of disability-adjusted life years (DALYs) due to NCDs arising from mental disorders, this landmark paper estimated that the value of losses due to mental disorders was roughly 1.3 trillion USD in 2010 (1.6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion USD 2010 (or approximately 3.0 trillion USD in 2019) by 2030.
 (See Supplementary appendix Tables S1 and S2 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]
@@
 
+```{r table1_1, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table1_1.png")
+
+```
+\addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}
+
 Our approach to capturing premature mortality relies on a pooled relative risk estimate for mortality by natural and unnatural causes, drawn from 148 studies identified by Walker et al.[@walkerMortalityMentalDisorders2015] These studies collectively reflect over 338,000 deaths across 29 countries and 6 continents.
 The majority of deaths (67%) recorded in studies with disaggregated data arose from acute and chronic illnesses, while unnatural causes such as injury and suicide represented 18% of deaths (the rest being unallocated).
-Overall, the pooled risk of all-cause mortality was 2·2 times higher (95% confidence interval (CI): 2·1-2·3) among people with mental disorders compared to those without.
+Overall, the pooled risk of all-cause mortality was 2.2 times higher (95% confidence interval (CI): 2.1-2.3) among people with mental disorders compared to those without.
 Using this relative risk estimate, Walker and colleagues calculated a PAF to estimate that 8 million deaths were due to mental disorders in 2012.
@@
 
-All computations were conducted using R software (version 3·6·2).
+All analyses were completed using R (version 4.2.1).[@rcoreteamLanguageEnvironmentStatistical2022]
 
@@
 The Institutional Review Board (IRB) of the Harvard T.H.
-Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol # IRB20-1946, determined on November 13, 2020).
+Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).
 
@@
 
+\blandscape
+
+```{r table1_2, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table1_2.png")
+
+```
+\addcontentsline{lot}{table}{Table 1.2: Disability-adjusted life years (DALYs) attributable to mental disorders as totals (millions) and percentages of overall burden, by estimation approach.}
+
+\elandscape
+
 ## Results
 
-Under GBD 2019, over 125 million DALYs were attributed to mental disorders, or roughly 5% of the global burden.
-After including alcohol and drug use, neurological disorders, chronic pain, suicide, and self-harm, the share due to mental disorders rose to 12% of global DALYs (approximately 321 million DALYs).
-Under the composite approach, an additional 97 million DALYs were attributed to mental disorders, encompassing, in total, over 16% of global DALYs.
-Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising over twice the burden of disease in high-income countries compared to low-income countries.
+`r results_sentence1`
 
-Rates of DALYs and deaths attributable to mental disorders under the different estimation approaches are presented by GBD region (Figure 1).
+Rates of DALYs and deaths attributable to mental disorders under the different estimation approaches are presented by GBD region (Figure \ref{figure_gbd_adjusted}).
 Geographically, the composite approach allocated a large portion of DALYs (to mental disorders) in Eastern Europe, North and Latin America, and sub-Saharan Africa.
@@
 Under the three approaches, we calculated the economic value of mental disorder losses (Table 3).
-Using GDP per capita as a proxy for the value per DALY, economic losses due to mental disorders were estimated at 4·7 trillion USD using our composite approach.
-This estimate is 1·1 trillion USD larger than that reached using the 2016 reallocation approach and over 3·3 trillion USD larger than that reached from the unadjusted GBD 2019 estimates.
-Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7·2 trillion international dollars in 2019 (Table S7).
+`r results_sentence2`.
+Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S7).
+
+```{r table1_3, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table1_3.png")
+
+```
+\addcontentsline{lot}{table}{Table 1.3: Global economic value associated with premature mortality and morbidity from mental disorders, by estimation approach and value per DALY.}
+
+```{r figure_gbd_adjusted, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.", out.extra='', fig.cap=paste("\\label{figure_gbd_adjusted}DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.
+Values are aggregated by GBD region.
+DALYs: Disability-adjusted life years; YLDs: years lived with disability; YLLs: years of life lost; GBD: Global Burden of Disease.", sep=" "), fig.width = 11, fig.height = 11, fig.align='center', out.width = '97%'}
+
+# Figure 1
+sf_use_s2(FALSE)
+
+lancet_pal <- c("#5A56A4", 
+                "#318ABF",
+                "#62C2A4",
+                "#9DD1A4",
+                "#DBE79A",
+                "#FCDA8B",
+                '#FCAA66',
+                "#F2744C",
+                "#D84858",
+                "#9A154C")
+
+j = 1
+i = "ihme_region"
+k = "rate_per_100k"
+m = "abs"
+
+temp <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4))
+
+deaths <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4)) %>% 
+  mutate(var_cut = cut(ihme_region_rate_per_100k, 
+                       breaks =c(0, 1, 20, 40, 60, 80, 100, 120, 130, 140, max(temp$ihme_region_rate_per_100k)))) %>%
+  ggplot() +
+  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
+  geom_sf(data = . %>%   group_by(ihme_region) %>% 
+            st_set_precision(1e4) %>%
+            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
+  theme(panel.grid.major = element_blank(), 
+        panel.background = element_blank(),
+        axis.title = element_blank(), 
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        text = element_text(family = "Source Sans Pro")) + 
+  labs(subtitle = "D: Deaths",
+    fill=
+      ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
+             ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs", "% of DALYs"),
+                    ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs", "% of YLDs"), 
+                           ifelse(k == "rate_per_100k", "YLLs", "% of YLLs"))))) +
+  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map$var_cut))) +
+  coord_sf(ndiscr = F) + 
+  facet_grid(~estimate_newlab) +
+  theme(legend.position = "bottom",
+        legend.title = element_text(size = 11),
+        legend.text =  element_text(size = 10),
+        plot.subtitle=element_text(size=15),
+        text = element_text(family = "Source Sans Pro"),
+        strip.background = element_rect(colour="white",
+                                        fill="white")
+        ,
+        strip.text = element_text(size=14)
+  ) +
+  guides(fill = guide_legend(override.aes =
+                               list(size = 0.5),
+                             nrow = 1, 
+                             byrow = TRUE))
+
+j = 2
+
+temp <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4))
+
+dalys <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4)) %>% 
+  mutate(var_cut = cut(ihme_region_rate_per_100k/1000, 
+                       breaks =c(1, 1.5,
+                                 2, 2.5, 3, 4, 5, 6, 7, 7.5, 
+                                 max(temp$ihme_region_rate_per_100k)/1000))) %>% 
+  ggplot() +
+  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
+  geom_sf(data = . %>%   group_by(ihme_region) %>% 
+            st_set_precision(1e4) %>%
+            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
+  theme(panel.grid.major = element_blank(), 
+        panel.background = element_blank(),
+        axis.title = element_blank(), 
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        text = element_text(family = "Source Sans Pro")) + 
+  labs(subtitle = "A: Disability-adjusted life years",
+       fill=
+         ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
+                ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs, thousands", "% of DALYs"),
+                       ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs, thousands", "% of YLDs"), 
+                              ifelse(k == "rate_per_100k", "YLLs, thousands", "% of YLLs"))))) +
+  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map$var_cut))) +
+  coord_sf(ndiscr = F) + 
+  facet_grid(~estimate_newlab) +
+  theme(legend.position = "bottom",
+        legend.title = element_text(size = 11),
+        legend.text =  element_text(size = 10),
+        plot.subtitle=element_text(size=15),
+        text = element_text(family = "Source Sans Pro"),
+        strip.background = element_rect(colour="white",
+                                        fill="white")
+        ,
+        strip.text = element_text(size=14)
+  ) +
+  guides(fill = guide_legend(override.aes =
+                               list(size = 0.5),
+                             nrow = 1, 
+                             byrow = TRUE))
+
+j = 3
+
+temp <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4))
+
+ylds <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4)) %>% 
+  mutate(var_cut = cut(ihme_region_rate_per_100k/1000, 
+                       breaks =c(1, 1.25, 1.5,
+                                 2, 2.5, 3, 3.5, 4, 4.5, 5, 5.5, 
+                                 max(temp$ihme_region_rate_per_100k)/1000))) %>% 
+  ggplot() +
+  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
+  geom_sf(data = . %>%   group_by(ihme_region) %>% 
+            st_set_precision(1e4) %>%
+            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
+  theme(panel.grid.major = element_blank(), 
+        panel.background = element_blank(),
+        axis.title = element_blank(), 
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        text = element_text(family = "Source Sans Pro")) + 
+  labs(subtitle = "B: Years lived with disability",
+       fill=
+         ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
+                ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs, thousands", "% of DALYs"),
+                       ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs, thousands", "% of YLDs"), 
+                              ifelse(k == "rate_per_100k", "YLLs, thousands", "% of YLLs"))))) +
+  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map$var_cut))) +
+  coord_sf(ndiscr = F) + 
+  facet_grid(~estimate_newlab) +
+  theme(legend.position = "bottom",
+        legend.title = element_text(size = 11),
+        legend.text =  element_text(size = 10),
+        plot.subtitle=element_text(size=15),
+        text = element_text(family = "Source Sans Pro"),
+        strip.background = element_rect(colour="white",
+                                        fill="white")
+        ,
+        strip.text = element_text(size=14)
+  ) +
+  guides(fill = guide_legend(override.aes =
+                               list(size = 0.5),
+                             nrow = 1, 
+                             byrow = TRUE))
+
+j = 4
+
+temp <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4))
+
+ylls <- data_rev_map %>% 
+  filter(measure_id == j) %>% 
+  filter(estimate_id %in%  c(1,2,4)) %>% 
+  mutate(var_cut = cut(ihme_region_rate_per_100k/1000, 
+                       breaks =c(0, 0.25, 0.5, 0.75, 1, 1.5,
+                                 2, 2.5, 3, 3.5, 
+                                 max(temp$ihme_region_rate_per_100k)/1000))) %>% 
+  ggplot() +
+  geom_sf(mapping = aes(fill = var_cut), color = "grey95", size = 0.001) +
+  geom_sf(data = . %>%   group_by(ihme_region) %>% 
+            st_set_precision(1e4) %>%
+            summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
+  theme(panel.grid.major = element_blank(), 
+        panel.background = element_blank(),
+        axis.title = element_blank(), 
+        axis.text = element_blank(),
+        axis.ticks = element_blank(),
+        text = element_text(family = "Source Sans Pro")) + 
+  labs(subtitle = "C: Years of life lost",
+       fill=
+         ifelse(j == 1,ifelse(k == "rate_per_100k", "Deaths", "% of deaths"),
+                ifelse(j == 2, ifelse(k == "rate_per_100k", "DALYs, thousands", "% of DALYs"),
+                       ifelse(j == 3, ifelse(k == "rate_per_100k", "YLDs, thousands", "% of YLDs"), 
+                              ifelse(k == "rate_per_100k", "YLLs, thousands", "% of YLLs"))))) +
+  scale_fill_manual(values=setNames(lancet_pal, levels(data_rev_map                 $var_cut))) +
+  coord_sf(ndiscr = F) + 
+  facet_grid(~estimate_newlab) +
+  theme(legend.position = "bottom",
+        legend.title = element_text(size = 11),
+        legend.text =  element_text(size = 10),
+        plot.subtitle=element_text(size=15),
+        text = element_text(family = "Source Sans Pro"),
+        strip.background = element_rect(colour="white",
+                                        fill="white")
+         ,
+         strip.text = element_text(size=14)
+  ) +
+  guides(fill = guide_legend(override.aes =
+                               list(size = 0.5),
+                             nrow = 1, 
+                             byrow = TRUE))
+
+ggarrange(dalys, ylds, ylls, deaths, 
+          ncol = 1, nrow = 4)
+
+ggsave(filename = paste0("Figure_1.png"), 
+       plot = last_plot(), 
+       path = resultspath)
+
+       # ,
+       # width = 1689,
+       # height = 1153,
+       # units = "px",
+       # dpi = 320)
+
+```
+
+```{r figure_cost_by_region, fig.width = 8, fig.height = 6, fig.align='center', out.width = '95%',  fig.scap="Economic burden of mental disorders, as a percent of GDP.", out.extra='', fig.cap="\\label{figure_cost_by_region}Economic burden of mental disorders, as a percent of GDP.
+The economic value is determined by using GDP per capita (USD 2019) as the value of a DALY.
+Values are aggregated by GBD region.
+GDP: gross domestic product; USD: United States dollar; DALY: disability-adjusted life year; GBD: Global Burden of Disease.", echo = FALSE, include = TRUE}
+
+l = "cost_who1"
+m = "abs"
+i = "ihme_region"
+
+data_rev %>%
+  filter(numeric_name == "val") %>%
+  {if(i == "who_region") select(.,measure_id,estimate, estimate_id,estimate_newlab,  who_region, who_region_pop100k:who_region_cost_who2_diff)
+    else select(.,measure_id, estimate, estimate_id, estimate_newlab, ihme_region, ihme_region_pop100k:ihme_region_cost_who2_diff)} %>% unique %>%
+  filter(measure_id== "2") %>%
+  filter(estimate_id %in%  c(ifelse(m =="diff","",1), 2,4)) %>%
+  filter(!is.na(get(i))) %>%
+  mutate(region = factor(get(i) , levels =  get(paste0(i,"_positions")))) %>%
+  ggplot(aes(y = region, fill=region, x=get(paste0(i,"_",l,ifelse(m =="diff", "_diff","")))/ get(paste0(i,"_","gdp")) * 100)) +
+  geom_bar(stat="identity") +
+  labs(x="% of GDP") +
+  facet_wrap(~estimate_newlab) +
+  geom_text(aes(label=round(get(paste0(i,"_",l,ifelse(m =="diff", "_diff","")))/ get(paste0(i,"_","gdp"))
+                            * 100,1)),
+            position=position_dodge(width=0.9),
+            hjust=-0.25, color="grey10",
+            size = 3,
+            family = "Source Sans Pro") +
+  scale_fill_manual(name = "Region", values = get(paste0(i,"_pal"))) +
+  scale_x_continuous(expand = expansion(mult = c(0, .1)), limits = c(0,8)) +
+  geom_vline(xintercept = 0, size = 0.25)+
+  theme(panel.grid.major.x =  element_line(color = "grey90",
+                                           linewidth = 0.15,
+                                           linetype = "dashed"),
+        panel.background = element_blank(),
+        axis.line=element_line(size = 0.2),
+        axis.line.y=element_blank(),
+        axis.ticks.y = element_blank(),
+        axis.ticks.x = element_line(linewidth = 0.2),
+        axis.title.y = element_blank(),
+        # axis.text.y = element_blank(),
+        legend.position = "none",
+        text = element_text(family = "Source Sans Pro"),
+        strip.background = element_rect(colour="white",
+                                        fill="white"),
+        strip.text = element_text(size=10))
+
+ggsave(filename = paste0("Figure_2.png"),
+       path = resultspath,
+       width = 8,
+       height = 6)
+
+```
 
 Although economic losses do not represent an actual loss to GDP, a sense of the scale can be gained by expressing the economic consequences with respect to GDP.
-Figure 2 displays the economic burden of disease due to mental disorders under the three estimation approaches by GBD region, as a percent of regional GDP.
+Figure \ref{figure_cost_by_region} displays the economic burden of disease due to mental disorders under the three estimation approaches by GBD region, as a percent of regional GDP.
 (Estimates by absolute values per DALY are provided in the Supplementary appendix, along with mapped data visualizing estimates across all values per DALY.) Across approaches, the greatest change in estimated burden occurs in Eastern Europe, Latin America, North America, and Southern sub-Saharan Africa.
-Under the relative GDP-per-capita values the economic burden would account for between 4% of GDP in Eastern Sub-Saharan Africa and 8% in High-income North America under our composite approach.
+`r results_sentence3`
 
@@
 In particular, we propose a composite approach to address contention in the classification of mental disorders.
-This approach suggests that the global DALYs attributable to mental disorders could exceed 400 million per year, or 16% of the total burden.
+`r discussion_sentence1`
 
-When applied against an economic value per DALY of one times GDP per capita, this approach further suggests that the per year losses associated with this burden could exceed 4·7 trillion USD in 2019.
-When adjusting for the uncertainty in estimates of the attributable burden of disease, the losses could range from 3·1 trillion to more than 6·9 trillion USD.
-Adjusting for purchasing power parity would increase the magnitude of these estimates, with ranges from 4·8 to 10·6 trillion international dollars at the global scale.
+`r discussion_sentence2` Adjusting for purchasing power parity would increase the magnitude of these estimates, with ranges from 4.8 to 10.6 trillion international dollars at the global scale.
 
@@
 Second, when including these sources of attributable mortality, the economic findings suggest staggering loses.
-We estimate that in 2019, the losses would already be over 1·8 trillion USD greater than Bloom and colleagues’ global losses projections for 2030 (2·9 trillion 2019 USD, using the same value per DALY approach).[@bloomGlobalEconomicBurden2011]
+`r discussion_sentence3`[@bloomGlobalEconomicBurden2011]
 
@@
 By way of example, the GBD 2019 Data Input Sources Tool retrieves 3,084 separate data sources for mental disorders.
-Of these, only 60 pertain to sub-Saharan Africa (1·9%) and 58 to South Asia (1·8%).[@instituteforhealthmetricsandevaluationihmeGlobalBurdenDisease] By comparison, of the 6,064 records pertaining to maternal and neonatal disorders, 631 are for sub-Saharan Africa (10·4%) and 270 for South Asia (4·5%).
+Of these, only 60 pertain to sub-Saharan Africa (1.9%) and 58 to South Asia (1.8%).[@instituteforhealthmetricsandevaluationihmeGlobalBurdenDisease] By comparison, of the 6,064 records pertaining to maternal and neonatal disorders, 631 are for sub-Saharan Africa (10.4%) and 270 for South Asia (4.5%).
 These severely limited inputs reflect a dearth of global mental health data; as of 2017, the World Mental Health survey initiative had conducted interviews in just 26 countries, only 13 of which were classified as low- or middle-income.[@steinCrossnationalEpidemiologySocial2017]
 
-Relatedly, our composite approach relies on pooled estimates of the relative risk of mortality from a systematic review and meta-analysis that itself is limited by the available data it draws upon[@walkerMortalityMentalDisorders2015].
-The review identified 203 studies for inclusion, of which only two were located in Africa, 16 in Asia, and one in South America.
+Relatedly, our composite approach relies on pooled estimates of the relative risk of mortality from a systematic review and meta-analysis that itself is limited by the available data it draws upon.[@walkerMortalityMentalDisorders2015] The review identified 203 studies for inclusion, of which only two were located in Africa, 16 in Asia, and one in South America.
 While the authors found that the estimates of mortality risk did not vary by region, the limited representation of studies from the world’s most populous and epidemiologically diverse continents is a considerable shortcoming.
@@
 We thank David Bloom, Goodarz Danaei, and Daniel Vicente Vigo for their feedback on an earlier version of the paper, as well as five anonymous reviewers for their valuable and constructive comments on our manuscript.
-This study received no funding.
 
-### Author conntributors
+### Author contributions
 
@@
 All codes used for the analysis in this article are available on GitHub (https://github.com/darias5/gmh_econ).
+
+\newpage

### 2023-02-10 paper2.Rmd
Adding first cut of thesis
Clean up of formatting and typesetting throughout.

--- 2023-02-09 conclusion.Rmd
@@
----
-title: ''
-output: pdf_document
+```{r loading_libraries}
 
----
+source("C:/Users/danie/Dropbox (Harvard University)/madagascar_mh/code/0_a_packages_and_paremeters_do_file.R")
 
-\addcontentsline{toc}{section}{Conclusion}
-\section*{Conclusion}
+```
 
-Thank you for following this tutorial!
+```{r loading_data}
 
-I hope you'll find it useful to write a very professional dissertation.
+###### MH DATA
 
-\cite{ngTracingPathChikungunya2010}
+load(file = paste(mh_path, 
+                  "mh_data_all_facilities.Rdata", sep = "/"))
+
+###### OUTPUTS
+
+load(file = paste(gpspath_spread,"1_matched",
+                  "gps_outputs.Rdata", sep = "/"))
+
+load(file = paste(gpspath_spread,"1_matched", 
+                  "gps_facilities.Rdata", sep = "/"))
+
+load(file = paste(resultspath,"3_climate", 
+                  "climate_facilities.Rdata", sep = "/"))
+
+load(file = paste(resultspath,"3_climate", 
+                  "cyclone_data.Rdata", sep = "/"))
+
+# load(file = paste(analysispath,"2_data", 
+#                   "data.Rdata", sep = "/"))
+
+load(file = paste(analysispath,"2_data", 
+                  "outputs_models.Rdata", sep = "/"))
+
+load(file = paste(analysispath,"2_data", 
+                  "model_outputs_preferred_model.Rdata", sep = "/"))
+
+load(file = paste(analysispath,"2_data", 
+                  "outputs_lags.Rdata", sep = "/"))
+
+load(file = paste(analysispath,"2_data", 
+                  "model_outputs_regional.Rdata", sep = "/"))
+
+load(file = paste(analysispath,"2_data",
+                  "outputs_marginal_effects.Rdata", sep = "/"))
+
+load(file = paste(analysispath,"2_data",
+                  "outputs_marginal_effects_predictions.Rdata", sep = "/"))
+
+```
+
+```{r customizing_outputs}
+
+a = "All facilities"
+b = "Any mental or neurological disorders"
+c = "total"
+d = "both"
+e = "mean"
+
+num_facilities_CSB <- facilities_all_gps %>% filter(clinic_type_clean == "CSB/FSP") %>% nrow()
+num_facilities_CHD <- facilities_all_gps %>% filter(clinic_type_clean == "CHD") %>% nrow()
+num_facilities_CHRR_CHU <- facilities_all_gps %>% filter(clinic_type_clean == "CHR/CHU") %>% nrow()
+num_facilities <- facilities_all_gps %>% nrow()
+
+num_facilities_CSB = format(num_facilities_CSB, big.mark = ",") 
+num_facilities_CHD = format(num_facilities_CHD, big.mark = ",") 
+num_facilities_CHRR_CHU = format(num_facilities_CHRR_CHU, big.mark = ",") 
+num_facilities_pretty = format(num_facilities, big.mark = ",")
+
+n_facilities_who <- gps_outputs$value[gps_outputs$variable == "n_facilities_who"]
+n_facilities_rhino <- gps_outputs$value[gps_outputs$variable == "n_facilities_rhino"]
+n_gps_facilities_new <- gps_outputs$value[gps_outputs$variable == "n_gps_facilities_new"]
+n_gps_facilities <- gps_outputs$value[gps_outputs$variable == "n_gps_facilities"]
+
+validation_mean_dist <- gps_outputs$value[gps_outputs$variable == "validation_mean_dist"]
+
+validation_max_dist <- gps_outputs$value[gps_outputs$variable == "validation_max_dist"]
+
+n_matched_facilities <- facilities_all_gps %>% filter(source == "Exact - Validated sources") %>% nrow()
+n_matched_facilities_RHINO <- facilities_all_gps %>% filter(source == "Exact - RHINoVision") %>% nrow()
+n_gps_facilities_fuzzy <- facilities_all_gps %>% filter(source == "Exact - All sources") %>% nrow()
+n_centroid <- facilities_all_gps %>% filter(source == "Centroid") %>% nrow()
+n_gps_facilities_searches <- facilities_all_gps %>% filter(source == "Searches") %>% nrow()
+
+earliest_climate_date <- min(as.yearmon(start_date_climate), 
+                             as.yearmon(as.Date(paste0(as.character(date1), '01'), format='%Y%m%d')))
+earliest_climate_date <- format(as.yearmon(earliest_climate_date), "%B %Y")
+
+latest_climate_date <- as.yearmon(end_date_climate)
+latest_climate_date <- format(as.yearmon(latest_climate_date), "%B %Y")
+
+n_facilities_sm <- data_climate %>% 
+  filter(date == "Jan 2010") %>%
+  dplyr::select(sm_monthly, facility_ID) %>%
+  filter(!is.na(sm_monthly)) %>%
+  dplyr::select(facility_ID) %>%
+  unique() %>%
+  nrow()
+
+n_facilities_sm_missing <- data_climate %>% 
+  filter(date == "Jan 2010") %>%
+  dplyr::select(sm_monthly, facility_ID) %>%
+  filter(is.na(sm_monthly)) %>%
+  dplyr::select(facility_ID) %>%
+  unique() %>%
+  nrow()
+
+```
+
+```{r dynamic_text_results}
+
+function_dynamic_text_results <-
+  function(section = "main",         #c(main, lags, regional, multiverse)
+           coefficient_option,
+           lag_option,
+           region_option = "all",
+           model_option = "4",
+           value = "irr",
+           value_include = TRUE,
+           multiverse_sign = "positive",
+           multiverse_p = FALSE) #(TRUE, FALSE, only),) 
+  {
+    output_df <- get(paste0(
+      "model_outputs",
+      ifelse(
+        section == "main",
+        "_preferred_model",
+        ifelse(section == "multiverse", "",
+
+               paste0("_", section)))))
+
+    if(section == "multiverse"){
+
+      if(multiverse_sign == "positive"){
+
+        output_df <- output_df %>% filter(estimate >= 0)  %>% filter(coefficient == coefficient_option)
+
+      } else {output_df <- output_df %>% filter(estimate < 0)  %>% filter(coefficient == coefficient_option)}
+
+      if(multiverse_p != FALSE)
+      {
+        models_counts <- output_df <- output_df %>% filter(p_value < multiverse_p) %>% nrow()
+        return(models_counts)
+
+      } else {
+
+        models_counts <- output_df %>% nrow()
+
+        return(models_counts)
+
+      }
+
+    }else
+
+    {
+
+      if(section == "lags"){
+
+        output_df <-  output_df %>% filter(lag == lag_option) %>% filter(coefficient == coefficient_option)
+
+      }
+
+      if(section == "regional")
+
+      {
+
+        output_df <-  output_df %>% filter(coefficient == coefficient_option)  %>%
+          filter(region == region_option)
+      }
+
+      if(section != "lags" &  section != "regional"){
+
+        output_df <-
+          output_df %>% filter(coefficient == coefficient_option) %>%
+          filter(model_number == model_option)
+
+      }
+
+      if (value == "irr"){
+
+        val <- round(exp(output_df$estimate), 3)
+        p_val <- round(output_df$p_value, 3)
+        low <- round(exp(output_df$lower_99), 3)
+        high <- round(exp(output_df$upper_99), 3)
+
+        if (value_include == TRUE){
+
+          return(paste0(
+            "(IRR: ",
+            val,
+            ", p ",
+            ifelse(p_val < 0.001,
+                   "< 0.0001, ",
+                   paste0("= ",
+                          p_val,
+                          ", ")),
+            "99\\% CI: ",
+            low,
+            " – ",
+            high
+            ,
+            ")"))
+
+        }
+
+        if (value_include == FALSE){
+
+          return(paste0(
+            "(p ",
+            ifelse(p_val < 0.001,
+                   "< 0.0001, ",
+                   paste0("= ",
+                          p_val,
+                          ", ")),
+            "99\\% CI: ",
+            low,
+            " – ",
+            high
+            ,
+            ")"))
+
+        }
+
+        if (value_include == "only"){
+          # IRR only
+
+          return(paste0(ifelse(
+            val < 1,
+            paste0(round(1 - val, 3) * 100, "\\% fewer"),
+            paste0(round(val - 1, 3) * 100, "\\%")
+          )))
+
+        }
+
+      }
+
+      if (value == "ame"){
+        val <- round(output_df$ame, 3)
+        p_val <- round(output_df$ame_p_value, 3)
+        low <- round(output_df$ame_lower_99, 3)
+        high <- round(output_df$ame_upper_99, 3)
+
+        if (value_include == TRUE){
+          return(paste0(
+            "(AME: ",
+            val,
+            ", p ",
+            ifelse(p_val < 0.001,
+                   "< 0.001, ",
+                   paste0("= ",
+                          p_val,
+                          ", ")),
+            "99\\% CI: ",
+            low,
+            " – ",
+            high
+            ,
+            ")"))
+
+        }
+
+        if (value_include == FALSE) {
+          # AME without value
+
+          return(paste0(
+            "(p ",
+            ifelse(p_val < 0.001,
+                   "< 0.001, ",
+                   paste0("= ",
+                          p_val,
+                          ", ")),
+            "99\\% CI: ",
+            low,
+            " – ",
+            high
+            ,
+            ")"))
+
+        }
+
+        if (value_include == "only") {
+          # AME only
+
+          return(round(val, 2))
+
+        }
+      }
+    }
+  }
+
+num_models_multiverse = format(max(model_outputs$model_number), big.mark = ",")
+
+function_pval_stars <- function(x){
+
+  ifelse(stars.pval(x) ==".", "", stars.pval(x))
+
+  }
+
+```
+
+# Climate exposures and population mental health in Madagascar: an ecological study of national health information system data
+
+\begin{centering}
+
+\emph{Daniel Arias, Karestan Koenen, Christopher Golden}
+
+\vspace{12pt}
+
+\noindent\rule{8cm}{0.4pt}
+
+\end{centering}
+
+\begin{raggedright}
+
+{\bf Background:} Climate change-related exposures (CCEs) have been increasingly linked to worsened mental health, yet few studies of CCEs have taken place in low- and middle-income countries.
+
+{\bf Methods:} To better understand how climate conditions may be impacting population mental health in these settings, we leverage meteorologic, geospatial, and health system data reported by `r num_facilities_pretty` facilities in Madagascar from 2010 to 2020 to explore the mental health impacts of three exposures of climate using negative binomial regression: temperature, soil moisture, and duration of cyclones and tropical storms.
+
+{\bf Findings and interpretation:} We found a statistically significant reduction in monthly cases associated with temperature—approximately `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = "only")` cases reported per each degree Celsius `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = TRUE)`.
+A multiverse analysis of `r num_models_multiverse` models found this estimate to be robust to alternative specifications, while a subgroup analysis by ecoregion indicated that this association was primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
+We further found that higher soil moisture may be associated with higher case counts in the future, with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")`  elevation in incident cases reported `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`  after a lag of three months.
+We further found that greater soil moisture was associated with higher cases reported in the eastern lowlands and the northern dry deciduous forests, which is consistent with the geographic concentration of flood risk in Madagascar.
+
+\vspace*{\fill}
+
+\emph{Keywords: climate mental health, planetary health, eco-anxiety, climate change, humidity, soil moisture, drought, temperature, cyclones.}
+
+\end{raggedright}
+
+\newpage
+
+## Introduction
+
+As empirical evidence increasingly highlights the wide-scale impact of human activities on climate, there is a growing, parallel body of evidence documenting the impacts our changing climate has on human health.[@watts2020ReportLancet2021] Rising temperatures and extreme weather events (including floods, hurricanes, droughts, and fires) have been associated with worsened health outcomes in multiple settings.[@cianconiImpactClimateChange2020a; @rocqueHealthEffectsClimate2021] In particular, these and other climate change-related exposures (CCEs) have been increasingly linked to worsened mental health[@padhyMentalHealthEffects2015  @batterhamSystematicReviewQuantitative2022], with systematic reviews suggesting, among other climate condition impacts, positive associations between high ambient temperatures and mental disorders,[@liuThereAssociationHot2021] drought conditions and suicide,[@stankeHealthEffectsDrought2013] and cyclones and negative mental health outcomes.[@tasdikhasanExploringMentalHealth2020]
+
+Despite the weight of this evidence, few quantitative studies evaluating the effects of climate on population mental health have, to date, taken place in low- and middle-income countries (LMICs),[@sharpeClimateChangeClimaterelated2021] populations that—despite contributing the least to human-driven climate change—are among the most likely to be vulnerable to its impacts.[@bakerProjectingGlobalEmissions2020]
+
+Among low-income countries most vulnerable to the health consequences of climate change is Madagascar, a nation that generates less than a tenth of a percentage of global carbon dioxide emissions.
+Worsening CCEs in Madagascar (primarily in the form of droughts, floods, and cyclones) are likely to exacerbate endemic, climate-sensitive threats to health, including malnutrition and malaria.[@rakotoarisonAssessmentRiskVulnerability2018] In particular, persistent drought conditions in recent years have led to extensive food insecurity.[@adamtaylorMadagascarHeadedClimate] Though there is debate concerning the extent to which human activity is directly responsible for Madagascar's current drought,[@harringtonAttributionSevereLow; @zhongManyDimensionsDrought2021] the extremity of the situation has led some observers to classify conditions in Madagascar as the first climate change famine in history.[@worldfoodprogrammeMadagascarSevereDrought2021]
+
+Understanding how both incremental and extreme changes in climate impact population mental health is critical to gauging the full extent to which CCEs impact human health and wellbeing under a multidisciplinary approach to population health.[@berryCaseSystemsThinking2018] This understanding is particularly important in contexts such as Madagascar, where climate conditions are already demonstrating pronounced pressures on economic, social, and physical wellbeing.
+
+In this ecological study, we investigated the association of climate conditions and population mental health in Madagascar between 2010 and 2020 using routine health system data from Madagascar’s Ministry of Public Health.
+The use of health system data enabled us to indirectly evaluate the extent to which existing public health data may already be showing signals of CCEs, which may aid efforts to prevent and mitigate mental health stressors and better design systemic responses to mental health needs.
+As a measure of population mental health, we considered facility-level monthly counts of new diagnoses of mental disorders.
+To capture the importance of both variation in temperature and precipitation conditions in Madagascar, we explored the predictive association of three climate conditions with incident mental health disorders: mean monthly ambient air temperature, mean monthly soil moisture, and monthly cyclone activity.
+
+## Methods
+
+### Data
+
+To analyze the impact of climate on population mental health in Madagascar, we first obtained health management information system (HMIS) data from the Madagascar Ministère de la Santé Publique.
+We then obtained gridded temperature and soil moisture data from the European ReAnalysis (ERA5)[@copernicusclimatechangeservicec3sFifthGenerationECMWF2017] and the European Space Agency’s Climate Change Initiative (ESA CCI),[@europeanspaceagencyEuropeanSpaceAgency2022] respectively.
+Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@SouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the National Oceanic and Atmospheric Administration (NOAA)[@InternationalBestTrack2021] for accuracy.
+
+#### Outcomes
+
+Madagascar’s health information system provided facility-level data on counts of disease incidence summarized and reported monthly.
+Prior to 2019, this system was the Gestion du Système d'Information Sanitaire (GESIS); in early 2019, the system transitioned to using District Health Information Software 2 (DHIS2).
+
+Among facilities reporting any mental health data between 2010 and 2020, data were obtained from `r num_facilities_CSB` public and private primary health centers (known as Centres Santé de Base or CSBs and Formations Sanitaires Privées de Base or FSBs, respectively), `r num_facilities_CHD` district referral hospitals (CHDs), `r num_facilities_CHRR_CHU` regional referral hospitals (CHRRs) and university hospitals (CHUs), for a total of `r num_facilities_pretty` uniquely-identified facilities in our sample.
+
+Exploratory data analysis indicated that the classification and reporting of counts of mental disorders in GESIS varied across types of facilities in their level of detail.
+Among CHD facilities, incidence of mental disorders was aggregated with neurological disorders (coded as “neuro psychiatric disorders”), while CHRR and CHU facilities reported more detailed counts of specific mental disorders, such as depression, personality disorders, and schizophrenia.
+Across all facilities, disaggregated data was reported by age group but not by sex.
+Among CSB facilities, incidences of mental disorders were reported by age group under “mental illnesses and psychic disorders” until June 2015, when reporting was reclassified to “mental disorders,” and disaggregated data was reported by both age and sex.
+
+To address heterogeneity in reporting, our analysis aggregated any monthly incidence of mental or neurological disorders reported by a facility, irrespective of age and sex, into a summary outcome measure.
+To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series.
+The nonparametric Friedman’s super smoother regression estimator[@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation.[@hyndmanAutomaticTimeSeries2008] By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may reflect true variances in incidence (for example, incidences reported by a large, regional reference hospital) while addressing potential errors in data entry.
+(Additional detail on the data cleaning process is available in the Supplementary appendix.)
+
+#### Geospatial data
+
+To retrieve spatial climate data for the facilities in our sample, it was first necessary to geocode facilities to obtain their latitude and longitude.
+Facility data from GESIS included limited geospatial information.
+While exact facility coordinates were not available, information on the relevant administrative unit served by a facility was included in the data (e.g., regions for CHRRs, districts for CHDs, and communes for CSBs).
+These data informed a stepwise matching process to locate facilities in our sample.
+
+First, region, district, and commune names in our sample were standardized against reference shapefiles to address variations in translation, abbreviation, transposition, accent marks, spacing, hyphenation, and spelling.
+(A summary of the standardized names is provided in the Supplementary appendix.) Next, facility names, types, and associated administrative units were used to match facilities to a validated spatial inventory of health facilities in Sub-Saharan Africa,[@mainaSpatialDatabaseHealth2019] of which `r format(as.numeric(n_facilities_who), big.mark = ",")` coordinates were provided for public facilities in Madagascar.
+In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented approximate string matching, which allowed for facility names and administrative units to be matched approximately, rather than exactly, to corresponding patterns in the validated spatial inventory.
+Applying this matching technique, `r format(as.numeric(n_matched_facilities), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities)/num_facilities * 100,0)`%) in our sample were matched to validated coordinates.
+
+Among the remaining facilities, an additional `r format(as.numeric(n_matched_facilities_RHINO), big.mark = ",")` primary facilities were matched to coordinates from a spatial inventory of `r format(as.numeric(n_facilities_rhino), big.mark = ",")` coordinates obtained from the Routine Health Information Network (RHINO),[@rhinovisiondecisionsupportsystemMadagascarDecisionSupport] which supports an open source database of health facility data in conjunction with the United States Agency for International Development, the government of Madagascar, and other stakeholders.
+
+To geolocate the remaining facilities, our existing inventories were combined with additional spatial inventories of health facility coordinates gathered from local consultants, the Global Healthsites Mapping Project, and other sources to create a database of `r format(as.numeric(n_gps_facilities_new), big.mark = ",")` uniquely identified coordinates for potential matches.
+Using this database, an additional `r format(as.numeric(n_gps_facilities_fuzzy), big.mark = ",")` facilities in our sample were geolocated using manual and approximate string matching.
+
+An additional `r format(as.numeric(n_centroid), big.mark = ",")` facilities were matched to the centroid of their relevant administrative unit in cases where the unit was less than or equal to `r min(commune_lim, fokontany_lim)` square kilometers, as these administrative units are quite small relative to the spatial resolution of gridded climate data (approximately 900 km²).
+Among the remaining facilities, geolocations were manually identified for `r format(n_gps_facilities_searches, big.mark = ",")` facilities using targeted searches, resulting in `r format(as.numeric(n_matched_facilities) + as.numeric(n_matched_facilities_RHINO) + as.numeric(n_centroid) + as.numeric(n_gps_facilities_fuzzy) + as.numeric(n_gps_facilities_searches), big.mark = ",")` of the `r format(num_facilities, big.mark = ",")` facilities (`r round((as.numeric(n_matched_facilities) + as.numeric(n_matched_facilities_RHINO) + as.numeric(n_centroid) + as.numeric(n_gps_facilities_fuzzy) + as.numeric(n_gps_facilities_searches))/as.numeric(num_facilities) * 100,0)`%) in the sample being geolocated.
+
+To gauge the accuracy of the geolocating process, a subset of 1% of geolocated facilities was selected for validation against manually identified coordinates.
+Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` kilometers, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data.
+Additional detail on the geolocating and validation process is available in the Supplementary appendix.
+
+#### Climate data
+
+Facility geolocations were then used to retrieve spatially referenced monthly averages of temperature and soil moisture data from ERA5 and ESA CCI, respectively.
+To allow for modelling of lagged associations, data were obtained for both ERA5 and ESA CCI SM from `r earliest_climate_date` to `r latest_climate_date`.
+
+ERA 5 is a global atmospheric reanalysis from the European Centre for Medium-Range Weather Forecasts (ECMWF) and is freely available through its Copernicus Climate Change Service (C3S)@europeanspaceagencyEuropeanSpaceAgency2022.
+The spatial resolution of ERA 5 is approximately 30 km., with quality-assured hourly estimates available from 1959 to the present  @europeanspaceagencyEuropeanSpaceAgency2022.
+Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation  @ERA5MonthlyAggregates2022.
+Temperature data was then converted to degrees Celsius.
+
+We obtained soil moisture data from the European Space Agency’s soil moisture dataset (ESA CCI SM), the world’s first and most comprehensive, multi-decade, satellite-observed dataset of global soil moisture.
+The spatial resolution of ESA CCI SM is approximately 26 km., with daily estimates available from 1978 to 2021.
+Using ESA CCI SM active and passive radiometer data, a time series of monthly aggregate values for mean soil moisture—measured as saturation percentage—was constructed from daily observations at each land grid point within Madagascar.
+We then applied nearest neighbor matching to link these time series to our geolocated facilities.
+
+For a location to have soil moisture data available in ESA CCI SM, it must fall within one of 244,243 land grid points.
+For some facilities on Madagascar’s coastline, their location placed them outside of ESA CCI’s spatial coverage, resulting in missing values.
+To address facilities without any soil moisture data, nearest neighbor searching was conducted to identify the nearest land grid point for which ESA CCI SM data would be available; this nearest neighbor’s soil moisture time series data would then be applied to the facility with missing data.
+Within a time series of ESA CCI data for a given location, however, monthly data could still be missing if adequate satellite observation was not recorded anytime during a given month; for these values, we used linear interpolation to address missing data within a time series.
+
+In addition, we obtained data on tropical storms and cyclones in the South-West Indian Ocean for the 2009-2010 to 2020-2021 seasons, inclusive.
+Open source data on tropical cyclones in the south-west Indian Ocean was obtained by scraping information from Wikipedia summaries of each cyclone season, which were originally sourced from alerts issued by Météo-France La Réunion (MFR La Réunion), the World Meteorological Organisation designated Regional Specialized Meteorological Centre (RSMC) for the provision of forecasts and warnings of tropical cyclones in the South-West Indian Ocean.
+To ensure that the compiled data accurately reflected storms in Madagascar during the study period, we cross-referenced these data against storm trajectory data for the South Indian Basin from NOAA.[@InternationalBestTrack2021]
+
+With these data, we generated two indicators to measure exposure to storm activity in a given month: a binary indicator for whether a storm impacted Madagascar in that month and a count indicator for the number of days per month with a storm.
+To capture lingering post-dissipation effects, we defined impact as the storm's duration plus an additional 14 days.
+
+### Statistical analysis
+
+All analyses were completed using R (version 4.2.1).[@rcoreteamLanguageEnvironmentStatistical2022] Marginal effects were calculated using the 'margins' package (version 0.3.26)[@leeperMarginsMarginalEffects2021] for R.
+
+#### Modeling approach
+
+Exploratory data analysis highlighted that the variance of monthly facility-level counts of incident mental disorders highly exceeded the mean; consequently, our statistical analysis utilized negative binomial (NB) regression, which is recommended in the case of over-dispersed count data.
+
+Our primary analysis involved conducting four models to estimate the association between facility-level counts of incident mental disorders and climate conditions.
+Model 1 used temperature as the principal predictor of counts of incident mental disorders.
+Model 2 only used soil moisture as a predictor.
+Model 3 used both temperature and soil moisture independently as predictors, while Model 4—our preferred model—introduced an interaction term between the two.
+Duration of cyclone activity was included in all models using our count indicator of exposure.
+In all models, we included fixed effects for Madagascar’s twenty-two regions to account for geographic differences in climate patterns and case reporting.
+We further included month and year fixed effects to account for seasonality and time-varying omitted variables.
+
+In addition, to aid in the interpretation of results, our analysis further reported the average marginal effect of each model predictor.
+Marginal effects clarify the effect of a per-unit change in a continuous explanatory variable (e.g., temperature) on an outcome where the regression model involves interaction.
+(In models without interaction or higher-order terms, the slope coefficient from the model will equal the marginal effect.) In addition to estimating the average marginal effects of our temperature, soil moisture, and cyclone variables, we further calculated the marginal effect and predicted values of the outcome for each unit of climate exposure across the three variables of interest.
+
+To test for lagged associations—that is, whether in a given month, climate conditions in prior months were associated with counts of mental disorders—versions of Model 4 were conducted using lagged predictors.
+Measures of association were estimated for each monthly lag increment between 1 month and 18 months, inclusive.
+
+Owing to the large number of observations in our sample, significance was evaluated against an alpha of 0.01, with 99% confidence intervals reported.
+Coefficients and confidence intervals for our indicators of climate exposure were exponentiated to generated incidence rate ratios (IRRs).
+Confidence intervals were constructed using heteroskedasticity-robust standard errors.
+
+#### Subgroup analysis
+
+Madagascar is home to a diverse range of terrestrial ecoregions, each of which has unique physical, climatic, and ecological characteristics.
+These variations in the environment include distinct patterns of rainfall, temperature, and cyclone activity, potentially resulting in effect heterogeneity when examining how these exposures impact human health across different ecoregions.
+
+To explore potential heterogeneity of our effect estimates, we evaluated Models 1 through 4 among facilities in each of Madagascar's four predominant ecoregions: the lowland, humid forests of the east, the subhumid forests of the Central High Plateau, the desert and xeric shrublands of the south, and the northeastern Dry deciduous forests.
+(Ecoregions are presented in Figure \ref{figure_ecological_zone}.)
+
+```{r figure_ecological_zone, include = TRUE, echo=FALSE, warnings = FALSE,  fig.cap="\\label{figure_ecological_zone}Predominant ecoregions of Madagascar, summarized by administrative region.", fig.width = 8, fig.height = 9, fig.align='center', out.width = '90%'}
+
+ecological_zones <- read_excel(
+  paste(data_climate_path,
+        "ecological_zones.xlsx",
+        sep = "/")) %>%
+  rename(ecological_zone = 'ecological_zone (1 = Eastern rainforest; 2 = High Plateau; 3 = Arid/Desert; 4 = Dry Deciduos Forest)',
+         REGION_NAM = region_name)
+
+map_mdg_1 %>% inner_join(ecological_zones, by = "REGION_NAM") %>%
+  mutate(ecological_zone = ifelse(ecological_zone == 1, "Eastern lowland forests",
+                                  ifelse(ecological_zone == 2, "Highland subhumid forests",
+                                         ifelse(ecological_zone == 3, "Desert and xeric shrubland", "Dry deciduous forests")))) %>%
+  mutate(ecological_zone = factor(ecological_zone, levels = c("Eastern lowland forests",
+                                                              "Highland subhumid forests",
+                                                              "Desert and xeric shrubland",
+                                                              "Dry deciduous forests"))) %>%
+
+  ggplot(aes(geometry = geometry, fill = ecological_zone)) +
+  geom_sf(size = 0.2,
+          color = col_grey_med,
+          alpha = 0.6) +
+  geom_sf(data = map_mdg_1_un,
+          size = 0.2,
+          color = col_black,
+          fill = NA) +
+  theme_void() +
+  theme(text = element_text(family = "Source Sans Pro"),
+        legend.position = "right") +
+  scale_fill_manual(values = c(col_eco_rainforest,
+                               col_eco_highlands,
+                               col_eco_arid,
+                               col_eco_drydecid),
+                    name = "Ecoregion") +
+  theme_void()
+
+ggsave(filename = paste0("figure_4b.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 8,
+       height = 10,
+       bg = "white")
+
+```
+
+#### Sensitivity analysis
+
+In order to evaluate the robustness of our main results to alternative specifications, data processing, and modeling decisions, we generated `r num_models_multiverse` plausible model combinations to conduct a multiverse analysis to identify how sensitive effect estimates and confidence intervals were to different methodological choices.
+
+To generate the model combinations, we first detailed seven methodological choices and their potential specifications. These criteria are outlined in Table 1.
+
+```{r table2_1, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table2_1.png")
+
+```
+
+\addcontentsline{lot}{table}{Table 2.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis}
+
+First, we considered the role of data cleaning in the outcome data and chose to compare our analysis using the cleaned outcome data against the raw, unadjusted values.
+Second, we chose to compare our findings using data from all facilities (the full sample) against a sample without district and regional hospital (CSB/FSP facilities only).
+Primary care facilities have smaller catchment areas than hospitals; consequently, it is more plausible that climate data for primary care facilities will closely reflect climate exposure to patients compared to referral hospitals.
+Third, we considered the decision to model temperature and soil moisture as an additive or interactive relationship (Model 3 vs.
+Model 4), with both alternatives included in our multiverse analysis.
+Fourth, we evaluated our decision to account for overdispersion with a NB model by using a Poisson regression framework as an alternative.
+Fifth, we evaluated alternative specifications of exposure to cyclone activity, using three options: our binary indicator, our count indicator, and no term for cyclone activity included.
+Sixth, we toggled whether time fixed effects (month and year) were included.
+Seventh, we similarly toggled regional fixed effects.
+
+<!-- ```{r table1prep, fig.scap="scap table", fig.cap="Real caption of table", include = TRUE, echo=FALSE, warnings = FALSE} -->
+
+<!-- choice <- c("1. Data cleaning for outcome data", -->
+<!--             "1. Data cleaning for outcome data", -->
+<!--             "2. Sample", -->
+<!--             "2. Sample",  -->
+<!--             "3. Relationship of temperature and soil moisture", -->
+<!--             "3. Relationship of temperature and soil moisture", -->
+<!--             "4. Regression framework", -->
+<!--             "4. Regression framework", -->
+<!--             "5. Cyclone activity", -->
+<!--             "5. Cyclone activity", -->
+<!--             "5. Cyclone activity", -->
+<!--             "6. Month and year fixed effects", -->
+<!--             "6. Month and year fixed effects", -->
+<!--             "7. Regional fixed effects", -->
+<!--             "7. Regional fixed effects") -->
+
+<!-- criteria <- c("a) Linear interpolation to replace outliers*", -->
+<!--               " b) No adjustment (raw data)", -->
+<!--               "a) Full sample*", -->
+<!--               " b) Primary care facilities only (CSB/FSP)", -->
+<!--               "a) Additive model", -->
+<!--               "b) Interactive model*", -->
+<!--               "a) NB model*", -->
+<!--               "b) Poisson model", -->
+<!--               "a) Count indicator*", -->
+<!--               " b) Binary indicator", -->
+<!--               "c) Excluded (i.e., no indicator)", -->
+<!--               "a) Included*", -->
+<!--               "b) Excluded", -->
+<!--               "a) Included*", -->
+<!--               "b) Excluded") -->
+
+<!-- table_1 <- cbind(choice, criteria) -->
+
+<!-- table_1 <- as.data.frame(table_1) -->
+
+<!-- table_1 %>% -->
+<!--   group_by(choice) %>% -->
+<!--   gt(rowname_col = "criteria") %>% -->
+<!--   tab_header(title = md("Table 2.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis")) %>% -->
+<!--   tab_footnote(footnote = "*: preferred specification. CSB/FSP: Centres Santé de Base and Formations Sanitaires Privées de Base. NB: negative binomial model")  -->
+
+<!-- ``` -->
+
+<!-- ```{r table1, fig.scap="scap table", fig.cap="Real caption of table", include = TRUE, echo=FALSE, warnings = FALSE} -->
+
+<!-- kableExtra::kable((table_1$criteria)) %>% -->
+<!--     pack_rows(index = table(fct_inorder(table_1$choice)))  -->
+
+<!-- ``` -->
+
+We then interacted the methodological choices to generate `r num_models_multiverse` plausible models.
+Using the effect estimates and confidence intervals for these models, we constructed specification curves for monthly temperature, soil moisture, and—for the `r as.numeric(num_models_multiverse)/3` models that included the cyclone count indicator— cyclone activity to visually compare the distribution of plausible estimates under different combinations.
+
+#### Ethics statement
+The Institutional Review Board (IRB) of the Harvard T.H.
+Chan School of Public Health determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB21-1303, determined on October 19, 2021).
+
+## Results
+Our geolocated sample of facilities—which is displayed in Figure \ref{figure_gps}—showed geographic diversity and comprehensive coverage across Madagascar, with most geolocations identified through validated sources.
+
+Figure \ref{figure_gps_climate} shows the spatial distribution of temperature and soil moisture across the facilities in our sample during January and June 2015, corresponding to the warmer, wet season and the dryer, cool season, respectively.
+When evaluated over time, annual climate trends in Madagascar showed relatively stable distribution of average temperatures, while soil moisture had a slight upward shift through 2020 (Figure \ref{figure_climate_distribution}).
+Data of tropical storm and cyclone activity throughout the study period also exhibited seasonal patterns, with most major storms occurring in the hot season, with a peak between February and May (Figure \ref{figure_cyclone}).
+
+\blandscape
+
+```{r figure_gps, include = TRUE, echo=FALSE, warnings = FALSE,  fig.scap="Map of facilities in Madagascar, by GPS coordinate source and facility type.", out.extra='', fig.cap="\\label{figure_gps}Map of facilities in Madagascar, by GPS coordinate source (left panel) and facility type (right panel).", fig.width = 16, fig.height = 10, fig.align='center', out.height= '90%'}
+
+map_a <- facilities_all_gps %>%
+  ggplot(aes(geometry=geometry)) +
+  geom_sf(data = map_mdg_3_un,
+          size = 0.2,
+          color = col_grey_light,
+          fill = NA) +
+  geom_sf(data = map_mdg_2_un,
+          size = 0.2,
+          color = col_grey_med,
+          fill = NA) +
+  geom_sf(data = map_mdg_1_un,
+          size = 0.2,
+          color = col_black,
+          fill = NA) +
+  geom_sf(alpha = 0.5, aes(color = source)) +
+  theme_void() +
+  theme(text = element_text(size = 16, family = "Source Sans Pro"),
+        legend.position = "left") +
+  scale_color_manual(values = c(col_centroid,
+                                col_exact_all,
+                                col_exact_rhino,
+                                col_exact_val,
+                                col_search),
+                     name = "GPS type")
+
+map_b <- facilities_all_gps %>%
+  mutate(clinic_type_clean = ifelse(clinic_type_clean == "CSB/FSP", "Primary",
+                                    ifelse(clinic_type_clean == "CHD", "District hospital",
+                                           "Regional/university hospital"))) %>%
+  mutate(clinic_type_clean = factor(clinic_type_clean, levels = c("Primary",
+                                                                  "District hospital",
+                                                                  "Regional/university hospital"))) %>%
+  ggplot(aes(geometry=geometry)) +
+  geom_sf(data = map_mdg_3_un,
+          size = 0.2,
+          color = col_grey_light,
+          fill = NA) +
+  geom_sf(data = map_mdg_2_un,
+          size = 0.2,
+          color = col_grey_med,
+          fill = NA) +
+  geom_sf(data = map_mdg_1_un,
+          size = 0.2,
+          color = col_black,
+          fill = NA) +
+  geom_sf(alpha = 0.5, aes(color = clinic_type_clean)) +
+  theme_void() +
+  theme(text = element_text(size = 16, family = "Source Sans Pro"),
+        legend.position = "right") +
+  scale_color_manual(values = c(col_CSB,
+                                col_CHD,
+                                col_CHR),
+                     name = "Facility type")
+
+combined_plot <- ggarrange(map_a, map_b, ncol = 2)
+
+compass_file <- paste0(analysis_figures, "/compass.png")
+# From https://commons.wikimedia.org/wiki/File:Gray_compass_rose.svg
+
+ggdraw() +
+  draw_image(
+    compass_file, scale = .2, x = .51, y = .02,
+    hjust = 1, halign = 1, valign = 0
+  )  +
+  draw_plot(combined_plot)
+
+ggsave(filename = paste0("figure_1.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 16,
+       height = 10)
+
+```
+
+\elandscape
+
+```{r figure_gps_climate, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="Spatial distribution of climate conditions across clinics and seasons in Madagascar.", out.extra='', fig.cap="\\label{figure_gps_climate}Spatial distribution of climate conditions across clinics and seasons in Madagascar.
+Mean monthly temperature (top) is measured in degrees Celcius and mean soil moisture is measured in percent saturation (below).", fig.width = 6, fig.height = 7.5, fig.align='center', out.width = '90%'}
+
+panel_a <- data_climate %>%
+  filter(statistic == e) %>%
+  dplyr::select(date, facility_ID, temp_monthly) %>%
+  unique() %>%
+  inner_join(., facilities_all_gps) %>%
+  dplyr::select(date, geometry, facility_ID, temp_monthly) %>%
+  filter(date == "Jan 2015" | date == "June 2015" ) %>%
+  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
+  filter(!is.na(date_2)) %>%
+  ggplot(aes(geometry=geometry)) +
+  # geom_sf(data = map_mdg_3_un,
+  #         size = 0.2,
+  #         color = col_grey_light,
+  #         fill = NA) +
+  geom_sf(data = map_mdg_2_un,
+          size = 0.2,
+          color = "grey40",
+          fill = NA) +
+  geom_sf(data = map_mdg_1_un,
+          size = 0.2,
+          color = col_black,
+          fill = NA) +
+  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
+  #              size = 2, color = col_grey_lightest) +
+  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
+  geom_sf(alpha = 0.9, size = .7, aes(color = temp_monthly)) +
+  theme_void() +
+  # scale_alpha(range = c(0,1)) +
+  scale_color_viridis(option = "magma") +
+  labs(color = "Temperature ( ̊ C)") +
+  theme(text = element_text(family = "Source Sans Pro"),
+        strip.background = element_rect(colour="white",
+                                        fill="white")) +
+  facet_wrap(~date_2)
+
+panel_b <-  data_climate %>%
+  filter(statistic == e) %>%
+  dplyr::select(date, facility_ID, sm_monthly) %>%
+  unique() %>%
+  inner_join(., facilities_all_gps) %>%
+  dplyr::select(date, geometry, facility_ID, sm_monthly) %>%
+  filter(date == "Jan 2015" | date == "June 2015" ) %>%
+  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
+  filter(!is.na(date_2)) %>%
+  ggplot(aes(geometry=geometry)) +
+  # geom_sf(data = map_mdg_3_un,
+  #         size = 0.2,
+  #         color = col_grey_light,
+  #         fill = NA) +
+  geom_sf(data = map_mdg_2_un,
+          size = 0.2,
+          color = "grey40",
+          fill = NA) +
+  geom_sf(data = map_mdg_1_un,
+          size = 0.2,
+          color = col_black,
+          fill = NA) +
+  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
+  #              size = 2, color = col_grey_lightest) +
+  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
+  geom_sf(alpha = 0.9, size = .9, aes(color = sm_monthly)) +
+  theme_void() +
+  # scale_alpha(range = c(0,1)) +
+  scale_color_viridis(option = "mako", direction = -1) +
+  labs(color = "Soil moisture (%)") +
+  theme(text = element_text(family = "Source Sans Pro"),
+        strip.background = element_rect(colour="white",
+                                        fill="white")) +
+  facet_wrap(~date_2)
+
+ggarrange(panel_a,panel_b, nrow = 2)
+
+ggsave(filename = paste0("figure_2.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 6,
+       height = 7)
+
+```
+
+\newpage
+
+```{r figure_climate_distribution, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="Distribution of temperature and soil moisture across all month-years and all clinics.", out.extra='', fig.cap="\\label{figure_climate_distribution}Distribution of A) temperature and B) soil moisture across all month-years and all clinics.", fig.width = 6, fig.height = 7.5, fig.align='center', out.width = '90%'}
+
+panel_a <- data_climate %>%
+  mutate(date = as.yearmon(date),
+         year = as.factor(year(date)),
+         month = month(date)) %>%
+  filter(year != "2022") %>%
+  ggplot(aes(x=temp_monthly, y = year, fill = stat(x))) +
+  geom_density_ridges_gradient() +
+  labs(x = "Temperature ( ̊ C)",
+       title = "A:",
+       y = "Year") +
+  theme_classic() +
+  theme(text = element_text(family = "Source Sans Pro"),
+        legend.position = "") +
+  scale_fill_viridis(option = "magma")
+
+panel_b <- data_climate %>%
+  mutate(date = as.yearmon(date),
+         year = as.factor(year(date)),
+         month = month(date)) %>%
+  filter(year != "2022") %>%
+  ggplot(aes(x=sm_monthly, y = year, fill = stat(x))) +
+  geom_density_ridges_gradient() +
+  labs(x = "Soil moisture (%)",
+       title = "B:",
+       y = "Year") +
+  theme_classic() +
+  theme(text = element_text(family = "Source Sans Pro"),
+        legend.position = "") +
+  scale_fill_viridis(option = "mako", direction = -1)
+
+# panel_a <- data_climate %>%
+#   mutate(date = as.yearmon(date),
+#          year = as.factor(year(date)),
+#          month = month(date)) %>%
+#   filter(year != "2022") %>%
+#   ggplot(aes(x=temp_monthly, group = year, fill = year, color = year)) +
+#   geom_density(alpha=0.45, position="identity") +
+#   labs(x = "Temperature ( ̊ C)",
+#        title = "A:",
+#        y = "Density",
+#        fill = "Year",
+#        color = "Year") +
+#   theme_classic() +
+#   theme(text = element_text(family = "Source Sans Pro")) +
+#   scale_color_viridis(discrete = TRUE, option = "magma") +
+#   scale_fill_viridis(discrete = TRUE, option = "magma")
+#
+# panel_b <- data_climate %>%
+#   mutate(date = as.yearmon(date),
+#          year = as.factor(year(date)),
+#          month = month(date)) %>%
+#   filter(year != "2022") %>%
+#   ggplot(aes(x=sm_monthly, group = year, fill = year, color = year)) +
+#   geom_density(alpha=0.45, position="identity") +
+#   labs(x = "Soil moisture (%)",
+#        title = "B:",
+#        y = "Density",
+#        fill = "Year",
+#        color = "Year") +
+#   theme_classic() +
+#   theme(text = element_text(family = "Source Sans Pro")) +
+#   scale_color_viridis(discrete = TRUE, option = "mako") +
+#   scale_fill_viridis(discrete = TRUE, option = "mako")
+
+ggarrange(panel_a,panel_b, nrow = 2)
+
+ggsave(filename = paste0("figure_3.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 6,
+       height = 7)
+
+```
+
+\newpage
+
+\blandscape
+
+```{r figure_cyclone, include = TRUE, echo=FALSE, warnings = FALSE,  fig.cap="\\label{figure_cyclone}Tropical storms and cyclones in Madagascar by intensity and season, 2009-2010 to 2020-2021, inclusive.", fig.width = 8, fig.height = 5, fig.align='center', out.width = '90%'}
+
+library(vistime)
+
+category <- c("Moderate tropical storm",
+              "Severe tropical storm",
+              "Subtropical depression",
+              "Tropical cyclone",
+              "Intense tropical cyclone",
+              "Very intense tropical cyclone")
+
+color <- c("cyan2",
+           "lightblue1",
+           "steelblue3",
+           "palegoldenrod",
+           "orange",
+           "red")
+
+cylclone_col <- as.data.frame(cbind(category, color))
+
+data_cyclone_vis <- data_cyclone %>%
+  mutate(start = as.character(paste0(start_date_timeline, " 2020")),
+         end = as.character(paste0(end_date_timeline, " 2020"))) %>%
+  mutate(start =  as.Date(start, format = "%B %d %Y"),
+         end =  as.Date(end, format = "%B %d %Y")) %>%
+  left_join(.,cylclone_col)
+
+plot_data <- gg_vistime(data_cyclone_vis,
+                        col.event = "name",
+                        col.group = "season",
+                        show_labels = FALSE,
+                        background_lines = 0) +
+  scale_x_datetime(breaks = breaks_width("2 months"),
+                   labels = date_format("%B")) +
+  theme(text = element_text(size = 10,
+                            family = "Source Sans Pro"))
+
+col <- as.character(data_cyclone_vis$color)
+names(col) <- as.character(data_cyclone_vis$category)
+
+my_hist <- data_cyclone_vis %>%
+  ggplot(aes(wind_speed_kmh, fill = category)) +
+  geom_bar() +
+  scale_fill_manual(values = col,
+                    name = " ") +
+  theme(text = element_text(size = 8,
+                            family = "Source Sans Pro"),
+        legend.position = "bottom") +
+  guides(fill = guide_legend(nrow = 2))
+
+legend <- cowplot::get_legend(my_hist)
+
+### Combine the main plot and legend into a single figure
+plot_combined <- ggdraw(plot_data) +
+
+  draw_plot(
+    {legend},
+    # The distance along a (0,1) x-axis to draw the left edge of the plot
+    x = 0.4,
+    # The distance along a (0,1) y-axis to draw the bottom edge of the plot
+    y = 0.3,
+    # The width and height of the plot expressed as proportion of the entire ggdraw object
+    width = 0.6,
+    height = 0.5)
+
+plot_combined <- plot_grid(plot_data, legend,
+                           nrow = 2,
+                           rel_heights  = c(1, 0.15),
+                           rel_widths = c(1, 1))
+plot_combined
+
+ggsave(filename = paste0("figure_4.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 9,
+       height = 5,
+       bg = "white")
+
+```
+
+\elandscape
+
+\newpage
+
+```{r table 2,include = TRUE, echo=FALSE, warnings = FALSE}
+
+function_filter_results <- function(data,
+                                    preferred_model = FALSE,
+                                    filter_disease = "Any mental or neurological disorders",
+                                    filter_age = "total",
+                                    filter_sex = "both",
+                                    filter_temp_statistic = "mean",
+                                    filter_cleaned_data = TRUE,  
+                                    filter_sample = "all",
+                                    filter_cyclone = "count",
+                                    filter_time_fe = "fixed",
+                                    # filter_type_fe = "fixed",
+                                    filter_region_fe = "fixed",
+                                    filter_model_type = "NB"){
+
+  if(preferred_model == FALSE){
+
+    data %>% filter(disease == filter_disease & 
+                      age == filter_age & sex == filter_sex & 
+                      temp_statistic == filter_temp_statistic)
+
+  }else{
+
+    data %>%
+      filter(disease == filter_disease & 
+               age == filter_age & sex == filter_sex & 
+               temp_statistic == filter_temp_statistic) %>%
+      filter(cleaned_data == filter_cleaned_data &  
+               sample == filter_sample & cyclone == filter_cyclone & 
+               time_fe == filter_time_fe & 
+               region_fe == filter_region_fe & 
+               # clinic_type_fe == filter_type_fe &
+               model_type == filter_model_type)
+  }
+}
+
+model_outputs_preferred_model %>%
+  filter(model_type == "NB") %>%
+  filter(coefficient %in% c("exposure_temperature:exposure_sm", "exposure_temperature", "exposure_sm", "days_with_cyclone")) %>%
+  mutate(
+    cell_coef =
+      paste0(
+        signif(exp(estimate), 3),
+        " (",
+        signif(exp(lower_99), 3),
+        " – ",
+        signif(exp(upper_99), 3),
+        ")",
+        function_pval_stars(p_value)
+      ),
+    cell_me = ifelse(
+      coefficient == "exposure_temperature:exposure_sm",
+      "",
+      paste0(
+        signif(ame, 3),
+        " (",
+        signif(ame_lower_99, 3),
+        " – ",
+        signif(ame_upper_99, 3),
+        ")",
+        function_pval_stars(ame_p_value)
+      )
+    ),
+    coefficient = ifelse(
+      coefficient == "exposure_sm",
+      "Soil moisture",
+      ifelse(
+        coefficient == "exposure_temperature",
+        "Temperature",
+        ifelse(coefficient == "days_with_cyclone",
+               "Cyclone (count)",
+               "Temperature X Soil moisture"
+        )
+      )
+    ),
+    coefficient = factor(
+      coefficient ,
+      # Reordering group factor levels
+      levels = c("Temperature",
+                 "Soil moisture",
+                 "Temperature X Soil moisture",
+                 "Cyclone (count)")
+    ),
+    model = ifelse(
+      model_form == "Temperature only",
+      "Model 1 ",
+      ifelse(
+        model_form == "Soil moisture only",
+        "Model 2 ",
+        ifelse(model_form == "Temperature + Soil moisture",
+               "Model 3 ",
+               "Model 4 ")
+      )
+    ),
+    model = factor(model ,      # Reordering group factor levels
+                   levels = c("Model 1 ",
+                              "Model 2 ",
+                              "Model 3 ",
+                              "Model 4 "))
+  ) %>%
+  dplyr::select(model, coefficient, cell_coef, cell_me) %>%
+  rename('IRR (99% CI)' = cell_coef,
+         'M.E. (99% CI)' = cell_me) %>%
+  gt(rowname_col = "coefficient", groupname_col = "model") %>%
+  tab_header(title = md("Table 2.2: incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.")) %>%
+
+  cols_align(align = "left",
+             columns = c('IRR (99% CI)' , 'M.E. (99% CI)')) %>%
+  tab_footnote(footnote = "All models include month, year, and regional fixed effects.",
+               locations = cells_row_groups()) %>%
+  tab_footnote(footnote = "*** p < 0.001, ** p < 0.01, * p < 0.05",
+               locations = cells_row_groups()) %>%
+  opt_footnote_marks("letters") %>%
+  tab_options(table.font.names = "Source Sans Pro") %>%
+  tab_style(locations = cells_column_labels(),
+            style     = list(cell_text(weight = "bold"))) %>%
+  tab_options(table.width = pct(100))
+
+```
+
+\addcontentsline{lot}{table}{Table 2.2: main analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
+
+\newpage
+
+### Main analysis
+
+The regression models predicting monthly counts of any mental or neurological disorder (Table 2) showed significant associations with temperature across all models.
+A one-degree Celsius increase in temperature was associated with approximately `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` cases reported `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)` by primary clinics and hospitals in Model 1.
+Inclusion of both climate predictors resulted in little change to the measure of association for temperature.
+In an additive model with soil moisture included (Model 3), the effect estimate associated with temperature grew to `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` cases reported `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)`.
+Adopting an interactive model (Model 4) attenuated the association `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)`, but remained significant at a 95% level of confidence.
+Across all models with temperature, the average marginal effect associated with temperature (across a sample with all clinics) ranged between 2 and 3 fewer monthly cases reported and was statistically significant at an alpha of 0.01, with the average marginal effect in Model 4 being `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "ame", value_include ="only")` cases `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "ame", value_include =FALSE)`.
+
+Effect estimates associated with soil moisture were not statistically significant across all four models.
+In all models, we observed a modest reduction in cases reported per each additional day duration of cyclone activity, with the incidence ratio ratios of Models 3 `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "days_with_cyclone", value = "irr", value_include =TRUE)` and Models 4 `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "days_with_cyclone", value = "irr", value_include = TRUE)` being significant at a level of 0.05.
+In all models, however, the average marginal effect was close to 0, with the average marginal effect in Model 4 being only `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "days_with_cyclone", value = "ame", value_include ="only")` cases `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "days_with_cyclone", value = "ame", value_include ="FALSE")`.
+
+```{r figure_marginal, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 13, fig.height = 13, fig.align='center', out.width = '95%', fig.scap="Predicted values of monthly case counts and marginal effect estimates by coefficient and their 95\\% and 99\\% confidence intervals.", out.extra='', fig.cap="\\label{figure_marginal}Predicted values of monthly case counts and marginal effect estimates by coefficient and their 95\\% and 99\\% confidence intervals.
+The left panels show predicted values of monthly case counts of mental and neurological disorders in Madagascar, given different units of climate exposure.
+The right panels show marginal effect estimates over different units of climate exposure in the data.
+The dotted horizontal lines in the right panel depict no marginal effect on case counts.
+In all panels, the model used to generate predictions and marginal effects corresponds to Model 4.
+Units of climate exposure are degrees Celsius for temperature (top), saturation percentage for soil moisture (middle), and days with cyclone activity (bottom).", }
+
+panel_l <- outputs_marginal_effects_predictions %>%
+  pivot_wider(names_from = level, values_from = c(lower, upper)) %>%
+  mutate(factor = ifelse(factor == "exposure_sm", "Soil moisture",
+                         ifelse(factor == "exposure_temperature", "Temperature",
+                                ifelse(factor == "days_with_cyclone", "Days with cyclone activity",
+                                       "ERROR")))) %>%
+  mutate(factor = factor(factor ,      # Reordering group factor levels
+                         levels = c("Temperature",
+                                    "Soil moisture",
+                                    "Days with cyclone activity"))) %>%
+  ggplot(aes(x = xvals,
+             y = yvals,
+             group = factor,
+             fill = factor,
+             color= factor)) +
+  # geom_hline(yintercept = 0, color = col_grey_dark, linetype='dotted') +
+  geom_ribbon(aes(ymin = lower_0.99,
+                  ymax = upper_0.99),
+              alpha = 0.15) +
+  geom_ribbon(aes(ymin = lower_0.95,
+                  ymax = upper_0.95),
+              alpha = 0.25) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Predicted monthly case counts, given climate exposure",
+       x = "Units of climate exposure") +
+  theme_classic() +
+  theme(panel.grid.major.y = element_line(colour = col_grey_lightest),
+        legend.position = "none",
+        strip.background = element_rect(colour="white",
+                                        fill="white"),
+        strip.text = element_text(size=12),
+        text = element_text(family = "Source Sans Pro")) +
+  scale_color_manual(values =
+                       c(col_temperature,
+                         col_soilmoisture,
+                         col_cyclone)) +
+  scale_fill_manual(values =
+                      c(col_temperature,
+                        col_soilmoisture,
+                        col_cyclone)) +
+  facet_wrap(~factor,  scales = "free", nrow = 3)
+
+panel_r <- outputs_marginal_effects %>%
+  pivot_wider(names_from = level, values_from = c(lower, upper)) %>%
+  mutate(factor = ifelse(factor == "exposure_sm", "Soil moisture",
+                         ifelse(factor == "exposure_temperature", "Temperature",
+                                ifelse(factor == "days_with_cyclone", "Days with cyclone activity",
+                                       "ERROR")))) %>%
+  mutate(factor = factor(factor ,      # Reordering group factor levels
+                         levels = c("Temperature",
+                                    "Soil moisture",
+                                    "Days with cyclone activity"))) %>%
+  ggplot(aes(x = xvals,
+             y = yvals,
+             group = factor,
+             fill = factor,
+             color= factor)) +
+  geom_hline(yintercept = 0, color = col_grey_dark, linetype='dotted') +
+  # geom_ribbon(aes(ymin = lower_0.99,
+  #                 ymax = upper_0.99),
+  #             alpha = 0.15) +
+  geom_ribbon(aes(ymin = lower_0.95,
+                  ymax = upper_0.95),
+              alpha = 0.25) +
+  geom_line() +
+  geom_point() +
+  labs(y = "Marginal effect estimate",
+       x = "Units of climate exposure") +
+  theme_classic() +
+  theme(panel.grid.major.y = element_line(colour = col_grey_lightest),
+        legend.position = "none",
+        strip.background = element_rect(colour="white",
+                                        fill="white"),
+        strip.text = element_text(size=12),
+        text = element_text(family = "Source Sans Pro")) +
+  scale_color_manual(values =
+                       c(col_temperature,
+                         col_soilmoisture,
+                         col_cyclone)) +
+  scale_fill_manual(values =
+                      c(col_temperature,
+                        col_soilmoisture,
+                        col_cyclone)) +
+  facet_wrap(~factor,  scales = "free", nrow = 3)
+
+ggarrange(panel_l, panel_r, ncol = 2)
+
+ggsave(filename = paste0("figure_9.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 8,
+       height = 7)
+
+```
+
+```{r figure_lag, include = TRUE, echo=FALSE, warnings = FALSE,  fig.scap="Effect estimates by coefficient with lagged exposures and their 99\\% and 95\\% confidence intervals, Model 4.", out.extra='',  fig.cap="\\label{figure_lag}Effect estimates by coefficient with lagged exposures and their 99\\% and 95\\% confidence intervals, Model 4.
+The x-axis correspond to the length of the lag (e.g., a value of 2 reflects a lag of two months, such that case counts are predicted by climate conditions two months prior), with the value of 0 reflecting a model without any lag in exposure.
+The dotted horizontal lines depict a null effect.
+IRR: incidence rate ratio.", fig.width = 8, fig.height = 9, fig.align='center', out.width = '90%'}
+
+model_outputs_lags %>%
+  mutate(coefficient = ifelse(coefficient == "exposure_sm", "Soil moisture",
+                              ifelse(coefficient == "exposure_temperature", "Temperature",
+                                     ifelse(coefficient == "exposure_temperature:exposure_sm",
+                                            "Interaction (Temperature X Soil moisture)",
+                                            "Days with cyclone activity")))) %>%
+  mutate(coefficient = factor(coefficient , # Reordering group factor levels
+                              levels = c("Temperature",
+                                         "Soil moisture",
+                                         "Interaction (Temperature X Soil moisture)",
+                                         "Days with cyclone activity"))) %>%
+  filter(coefficient != "Interaction (Temperature X Soil moisture)") %>%
+  ggplot(aes(x = as.factor(as.numeric(lag)),
+             group = coefficient,
+             fill = coefficient,
+             color= coefficient)) +
+  geom_hline(yintercept = 1, color = col_grey_dark) +
+  geom_ribbon(aes(ymin = exp(lower_99),
+                  ymax = exp(upper_99)),
+              alpha = 0.15) +
+  geom_ribbon(aes(ymin = exp(lower_95),
+                  ymax = exp(upper_95)),
+              alpha = 0.25) +
+  geom_line(aes(y = exp(estimate))) +
+  geom_point(aes(y = exp(estimate))) +
+  labs(y = "IRR estimate",
+       x = "Lag (months)") +
+  theme_classic() +
+  scale_color_manual(values =
+                       c(col_temperature,
+                         col_soilmoisture,
+                         col_cyclone)) +
+  scale_fill_manual(values =
+                      c(col_temperature,
+                        col_soilmoisture,
+                        col_cyclone)) +
+  theme(panel.grid.major.y = element_line(colour = col_grey_light),
+        legend.position = "none",
+        strip.background = element_rect(colour="white",
+                                        fill="white"),
+        strip.text = element_text(size=11),
+        text = element_text(family = "Source Sans Pro")) +
+  facet_wrap(~coefficient,  scales = "free", nrow = 3)
+
+ggsave(filename = paste0("figure_8.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 6,
+       height = 7)
+
+```
+Predicted values of monthly case counts under Model 4 echoed the effect estimates from Table 2, with fewer cases reported in warmer months (Figure \ref{figure_marginal}).
+Marginal effect estimates across the distribution of temperatures in our data showed that the greatest level of reduction occurred between 10 and 15 degrees Celsius, with each degree increase associated with 4 to 5 fewer cases of mental or neurological disorders reported, controlling for other covariates.
+Months with greater levels of soil moisture and days with cyclone activity also showed fewer reported cases; however, the marginal effects associated with soil moisture were not significant across any unit of exposure, while those associated with days with cyclone activity were close to zero for all lengths of activity.
+
+Examining lagged effects showed potential temporal associations between soil moisture levels in preceding months and case counts in those following (Figure \ref{figure_lag}), with higher saturation leading to a statistically significant elevation in cases reported 1 to 5 months later.
+At a lag of 3 months, the elevation in cases was approximately `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`.
+There appeared to be a significant elevation of similar magnitude 13 to 17 months prior, suggesting potential annularity in lagged association.
+Effects for temperature were not significant across any lag; cyclone activity similarly showed no significance in lags under a year, but did show modest, statistically significant associations at lags of 12 months `r function_dynamic_text_results(section = "lags", lag_option = 12, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)` and 15 months `r function_dynamic_text_results(section = "lags", lag_option = 15, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)`.
+A slight increase in cases was associated with cyclone activity in a prior month, but this increase was not statistically significant `r function_dynamic_text_results(section = "lags", lag_option = 1, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)`.
+
+### Subgroup analysis
+
+```{r table_3, include = TRUE, echo=FALSE, warnings = FALSE}
+
+model_outputs_regional %>%
+  filter(coefficient %in% c("exposure_temperature:exposure_sm", "exposure_temperature", "exposure_sm", "days_with_cyclone")) %>%
+  mutate(
+    cell_coef =
+      paste0(
+        signif(exp(estimate), 3),
+        " (",
+        signif(exp(lower_99), 3),
+        " – ",
+        signif(exp(upper_99), 3),
+        ")",
+        function_pval_stars(p_value)
+      ),
+    cell_me = ifelse(
+      coefficient == "exposure_temperature:exposure_sm",
+      "",
+      paste0(
+        signif(ame, 3),
+        " (",
+        signif(ame_lower_99, 3),
+        " – ",
+        signif(ame_upper_99, 3),
+        ")",
+        function_pval_stars(ame_p_value)
+      )
+    ),
+    coefficient = ifelse(
+      coefficient == "exposure_sm",
+      "Soil moisture",
+      ifelse(
+        coefficient == "exposure_temperature",
+        "Temperature",
+        ifelse(coefficient == "days_with_cyclone",
+               "Cyclone (count)",
+               "Temperature X Soil moisture"
+        )
+      )
+    ),
+    coefficient = factor(
+      coefficient ,
+      # Reordering group factor levels
+      levels = c("Temperature",
+                 "Soil moisture",
+                 "Temperature X Soil moisture",
+                 "Cyclone (count)")
+    ),
+    model = ifelse(
+      model_form == "Temperature only",
+      "Model 1 ",
+      ifelse(
+        model_form == "Soil moisture only",
+        "Model 2 ",
+        ifelse(model_form == "Temperature + Soil moisture",
+               "Model 3 ",
+               "Model 4 ")
+      )
+    ),
+    model = factor(model ,      # Reordering group factor levels
+                   levels = c("Model 1 ",
+                              "Model 2 ",
+                              "Model 3 ",
+                              "Model 4 "))
+  ) %>%
+
+  mutate(ecological_zone = ifelse(region == "all", "All",
+                                  ifelse(region == 1, "Eastern lowland forests",
+                                         ifelse(region == 2, "Highland subhumid forests", 
+                                                ifelse(region == 3, "Desert and xeric shrubland", 
+                                                       "Dry deciduous forests"))))) %>%
+  mutate(ecological_zone = factor(ecological_zone, levels = c("All",
+                                                              "Eastern lowland forests",
+                                                              "Highland subhumid forests",
+                                                              "Desert and xeric shrubland", 
+                                                              "Dry deciduous forests"))) %>%
+
+  dplyr::select(coefficient, cell_coef, cell_me, ecological_zone) %>%
+  rename('IRR (99% CI)' = cell_coef,
+         'M.E. (99% CI)' = cell_me) %>%
+  gt(rowname_col = "ecological_zone", groupname_col = "coefficient") %>%
+  tab_header(title = md("Table 2.3: subgroup analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.")) %>%
+
+  cols_align(align = "left",
+             columns = c('IRR (99% CI)' , 'M.E. (99% CI)')) %>%
+  tab_footnote(footnote = "Estimates from Model 4 (interactive model), which include month, year, and regional fixed effects.",
+               locations = cells_row_groups()) %>%
+  tab_footnote(footnote = "*** p < 0.001, ** p < 0.01, * p < 0.05",
+               locations = cells_row_groups()) %>%
+  opt_footnote_marks("letters") %>%
+  tab_options(table.font.names = "Source Sans Pro") %>%
+  tab_style(locations = cells_column_labels(),
+            style     = list(cell_text(weight = "bold"))) %>%
+  tab_options(table.width = pct(100))
+
+```
+
+\addcontentsline{lot}{table}{Table 2.3: subgroup analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
+
+Results from our subgroup analysis showed evidence of potential effect heterogeneity by ecoregion.
+For temperature, estimates of association were only statistically significant in the highland subhumid forests, where each one-degree Celsius increase in temperature was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = "only")` cases reported `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = TRUE)`.
+Temperature was associated with a slight increase in temperature in the eastern lowland forests `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)` and the desert and xeric shrublands `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)`, but in neither case was the estimate significant at a level of 0.05.
+
+With respect to soil moisture, while our primary analysis found no evidence of a statistically significant association with reported cases in the full sample, we did find evidence of heterogeneity in our subgroup analysis.
+Among facilities in the highland subhumid forests, we found that each percentage point increase in soil moisture was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = TRUE)`, with an average marginal effect of `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = FALSE)`.
+Conversely, each percentage point increase in soil moisture in the dry deciduous forests was associated with a `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = "only")` increase in reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = TRUE)`, with an average marginal effect of `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "ame", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "ame", value_include = FALSE)`.
+
+Finally, our estimates of the incidence rate ratio associated with each additional day of cyclone duration in a given month were consistent between each ecoregion and our full sample.
+Among facilities in the dry deciduous forests, each additional day of cyclone activity was associated with the greatest reduction in reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "days_with_cyclone", region_option = "4", value = "irr", value_include = TRUE)`.
+
+### Multiverse analysis
+
+In our multiverse analysis, `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = FALSE)` of `r num_models_multiverse` models (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = FALSE)/as.numeric(num_models_multiverse)*100,0)`%) returned effect estimates for temperature associating a one-degree increase with fewer reported cases of mental or neurological disorders, with `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = 0.01)` (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = 0.01)/as.numeric(num_models_multiverse)*100,0)`%) of those estimates having p-values below 0.01 (Figure \ref{figure_sensitivity_analysis_temp}).
+Only `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "positive", multiverse_p = 0.01)` (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "positive", multiverse_p = 0.01)/as.numeric(num_models_multiverse)*100,0)`%)  models returned statistically significant IRR estimates greater than 1; all six models were negative binomial interactive models that excluded month and year fixed effects and were run on data that restricted to the CSB/FSP sample only.
+
+With respect to soil moisture, only `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "negative", multiverse_p = 0.01) + function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "positive", multiverse_p = 0.01)` of `r num_models_multiverse` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "negative", multiverse_p = 0.01) + function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "positive", multiverse_p = 0.01))/as.numeric(num_models_multiverse)*100,0)`%) returned effect estimates with p-values below 0.01, with `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "positive", multiverse_p = 0.01)` of such models reporting IRRs greater than 1 and `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "negative", multiverse_p = 0.01)` models reporting IRRs smaller than 1 (Figure \ref{figure_sensitivity_analysis_sm}).
+The overwhelming majority of models showed no significant association between soil moisture and monthly case counts, in either direction.
+Of models showing statistically significant IRRs of a magnitude greater than 1, all excluded both region and time fixed effects.
+
+Among the `r as.numeric(num_models_multiverse)/3` models that included cyclone activity measured in days per month, `r function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "negative", multiverse_p = FALSE)` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "negative", multiverse_p = FALSE)*100/(as.numeric(num_models_multiverse)/3)),0)`%) reported reduced case counts associated with cyclone duration, compared to `r function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "positive", multiverse_p = FALSE)` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "positive", multiverse_p = FALSE)*100/(as.numeric(num_models_multiverse)/3)),0)`%) showing IRRs below 1 (Figure \ref{figure_sensitivity_analysis_cyclone}).
+None of the `r as.numeric(num_models_multiverse)/3` models, however, had a p-value below 0.01.
+
+\newpage
+
+\blandscape
+
+```{r figure_sensitivity_analysis_temp, include = TRUE, echo=FALSE, warnings = FALSE,  fig.scap=paste("Specification curve depicting the effect estimates and confidence intervals for mean monthly temperature (degrees Celsius) across", num_models_multiverse, "models."), out.extra='',  fig.cap=paste("\\label{figure_sensitivity_analysis_temp}Specification curve depicting the effect estimates and confidence intervals for mean monthly temperature (degrees Celsius) across", num_models_multiverse, "models.
+In the top panel, estimated incidence rate ratios (IRRs) across different models are depicted as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+The dotted horizontal line depicts a null effect.
+The IRR estimate and confidence intervals of the preferred model, Model 4, are highlighted in orange.
+Below each model, a legend of shaded and unshaded boxes indicates which modeling decisions correspond to a given model, with boxes shaded teal showing active features.
+FE: fixed effects.
+CSB/FSP: Centres Santé de Base and Formations Sanitaires Privées de Base.
+NB: negative binomial model.", sep=" "), fig.width = 15, fig.height = 9, fig.align='center', out.width = '95%'}
+
+coef_plot_coefficients <- c("exposure_temperature")
+
+preferred_model <- model_outputs %>%
+  function_filter_results(preferred_model = TRUE) %>%
+  filter(model_form == "Temperature X Soil moisture") %>%
+  dplyr::select(model_number) %>% unique()
+
+preferred_model <- as.numeric(preferred_model$model_number)
+
+for (l in coef_plot_coefficients) {
+
+  model_outputs_temp <- model_outputs %>%
+    function_filter_results(preferred_model = FALSE) %>%
+    filter(coefficient == l) %>%
+    filter(model_type != "ZINB") %>%
+    filter(model_form == "Temperature X Soil moisture" |
+             model_form == "Temperature + Soil moisture")
+
+  min_space = 0.5
+  y_min_val = min(model_outputs_temp$lower_99)
+  y_max_val = max(model_outputs_temp$upper_99)
+  count_models <- nrow(model_outputs_temp)
+  # model_outputs_temp %>%
+  #   ggplot(aes(x = reorder(model_number, estimate))) +
+  #   geom_hline(yintercept=1, linetype='dotted') +
+  #   geom_errorbar(aes(x = reorder(model_number, estimate), ymin = estimate, ymax = standard_error),
+  #                 alpha = 0.15)
+
+  coef_plot <-  model_outputs_temp %>%
+    mutate(model_preference = ifelse(model_number == preferred_model,
+                                     "Main",
+                                     "Alternative")) %>%
+    mutate(model_preference = factor(model_preference,
+                                     levels = c("Main",
+                                                "Alternative"))) %>%
+    ggplot(aes(x = reorder(model_number, estimate),
+               y = exp(estimate),
+               color = model_preference,
+               fill = model_preference)) +
+    geom_hline(yintercept=1, linetype='dotted') +
+    geom_crossbar(aes(ymin = exp(lower_99),
+                      ymax = exp(upper_99)),
+                  fatten = 0,
+                  alpha = 0.2) +
+    geom_crossbar(aes(ymin = exp(lower_95),
+                      ymax = exp(upper_95)),
+                  fatten = 0,
+                  alpha = 0.3) +
+    geom_point(alpha = 1, size=1) +
+    theme_classic() +
+    theme(axis.text.x = element_blank(),
+          legend.position = "top",
+          axis.title = element_blank(),
+          axis.ticks.x = element_blank(),
+          strip.text = element_text(size=12),
+          text = element_text(family = "Source Sans Pro")) +
+    coord_cartesian(xlim=c(1-min_space, max(nrow(model_outputs_temp))+min_space)) +
+    scale_color_manual(values = c(col_model_main,
+                                  col_model_other),
+                       name = "") +
+    scale_fill_manual(values = c(col_model_main,
+                                 col_model_other),
+                      name = "") +
+    labs(title = ifelse(l == "exposure_temperature", "Temperature ( ̊ C)",
+                        ifelse(l == "exposure_sm", "Soil moisture",
+                               ifelse(l == "exposure_temperature:exposure_sm", "Interaction (temperature X soil moisture)",
+                                      ifelse(l == "cyclone_binary", "Cyclone (binary)",
+                                             "Cyclone (count)")))))
+
+  ggsave(filename = paste0("sensitivity_analysis_top_", l,".jpg"),
+         plot = last_plot(),
+         path = analysis_figures,
+         width = 7,
+         height = 5)
+
+  control_plot <-
+
+    model_outputs_temp %>%
+    mutate(
+      NB = ifelse(model_type == "NB", 1, 0),
+      Poisson = ifelse(model_type == "Poisson", 1, 0),
+      # ZINB = ifelse(zero_inflated == TRUE, 1, 0),
+      'Full sample' = ifelse(sample == "all", 1, 0),
+      'CSB/FSP only' = ifelse(sample == "primary", 1, 0),
+      'Cleaned data' = ifelse(cleaned_data == TRUE, 1, 0),
+      'Raw data' = ifelse(cleaned_data == FALSE, 1, 0),
+      'Interactive model' = ifelse(model_form == "Temperature X Soil moisture", 1, 0),
+      'Additive model' = ifelse(model_form == "Temperature + Soil moisture", 1, 0),
+      'Cyclone (count)' = ifelse(cyclone == "count", 1, 0),
+      'Cyclone (binary)' = ifelse(cyclone == "binary", 1, 0),
+      'Time FE' = ifelse(time_fe == "fixed", 1, 0),
+      'Region FE' = ifelse(region_fe == "fixed", 1, 0)) %>%
+    dplyr::select(model_number, estimate, NB:'Region FE') %>%
+    pivot_longer(cols = c(NB:'Region FE'),
+                 names_to = "spec_name",
+                 values_to = "spec_status") %>%
+    mutate(spec_name = factor(spec_name,
+                              levels = c("NB",
+                                         "Poisson",
+                                         'Full sample',
+                                         'CSB/FSP only',
+                                         'Cleaned data',
+                                         'Raw data',
+                                         'Interactive model',
+                                         'Additive model',
+                                         'Cyclone (count)',
+                                         'Cyclone (binary)',
+                                         'Time FE',
+                                         'Region FE'))) %>%
+    ggplot(aes(x = reorder(model_number, estimate),
+               y = spec_name,
+               fill = as.factor(spec_status))) +
+    geom_point(shape=22, size=2.2) +
+
+    scale_fill_manual(values = c(col_spec_no, col_spec_yes),
+                      name = "") +
+    guides(fill= "none") +
+    # scale_y_continuous(breaks = unique(control_grid_logit$y),
+    #                    labels = unique(control_grid_logit$key),
+    #                    limits=c(min(control_grid_logit$y)-1, max(control_grid_logit$y)+1)) +
+    #scale_x_continuous(breaks=c(1:nrow(model_outputs_temp))) +
+    coord_cartesian(xlim=c(1-min_space, nrow(model_outputs_temp)+min_space)) +
+    theme_classic() +
+    theme(panel.grid.major.y = element_blank(),
+          panel.grid.minor.y = element_blank(),
+          axis.text.x = element_blank(),
+          axis.title = element_blank(),
+          axis.text.y = element_text(size=10),
+          axis.ticks = element_blank(),
+          axis.line = element_blank(),
+          strip.text = element_text(size=12),
+          text = element_text(family = "Source Sans Pro"))
+
+  ggsave(filename = paste0("sensitivity_analysis_bottom_", l,".jpg"),
+         plot = last_plot(),
+         path = analysis_figures,
+         width = 7,
+         height = 3)
+
+  combined_plot <- cowplot::plot_grid(coef_plot,
+                                      control_plot,
+                                      rel_heights=c(1,0.5),
+                                      align='v', ncol=1, axis='b')
+
+  print(combined_plot)
+
+  ggsave(filename = paste0("sensitivity_analysis_0_", l,".jpg"),
+         plot = last_plot(),
+         path = analysis_figures,
+         width = 12.5,
+         height = 7)
+
+  ggsave(filename = paste0("figure_5.jpg"),
+         plot = last_plot(),
+         path = analysis_figures,
+         width = 12.5,
+         height = 7)
+
+}
+
+```
+
+```{r figure_sensitivity_analysis_sm, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap=paste("Specification curve depicting the effect estimates and confidence intervals for mean monthly soil moisture (percent saturation) across", num_models_multiverse, "models."), out.extra='',  fig.cap=paste("\\label{figure_sensitivity_analysis_sm}Specification curve depicting the effect estimates and confidence intervals for mean monthly soil moisture (percent saturation) across", num_models_multiverse, "models.
+In the top panel, estimated incidence rate ratios (IRRs) across different models are depicted as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+The dotted horizontal line depicts a null effect.
+The IRR estimate and confidence intervals of the preferred model, Model 4, are highlighted in orange.
+Below each model, a legend of shaded and unshaded boxes indicates which modeling decisions correspond to a given model, with boxes shaded teal showing active features.
+FE: fixed effects.
+CSB/FSP: Centres Santé de Base and Formations Sanitaires Privées de Base.
+NB: negative binomial model.", sep=" "), fig.width = 15, fig.height = 9, fig.align='center', out.width = '95%'}
+
+coef_plot_coefficients <- c("exposure_sm")
+
+preferred_model <- model_outputs %>%
+  function_filter_results(preferred_model = TRUE) %>%
+  filter(model_form == "Temperature X Soil moisture") %>%
+  dplyr::select(model_number) %>% unique()
+
+preferred_model <- as.numeric(preferred_model$model_number)
+
+for (l in coef_plot_coefficients) {
+
+model_outputs_temp <- model_outputs %>%
+  function_filter_results(preferred_model = FALSE) %>%
+  filter(coefficient == l) %>%
+  filter(model_type != "ZINB") %>%
+  filter(model_form == "Temperature X Soil moisture" |
+           model_form == "Temperature + Soil moisture")
+
+min_space = 0.5
+y_min_val = min(model_outputs_temp$lower_99)
+y_max_val = max(model_outputs_temp$upper_99)
+
+# model_outputs_temp %>%
+#   ggplot(aes(x = reorder(model_number, estimate))) +
+#   geom_hline(yintercept=1, linetype='dotted') +
+#   geom_errorbar(aes(x = reorder(model_number, estimate), ymin = estimate, ymax = standard_error),
+#                 alpha = 0.15)
+
+coef_plot <-  model_outputs_temp %>%
+  mutate(model_preference = ifelse(model_number == preferred_model,
+                                   "Main",
+                                   "Alternative")) %>%
+  mutate(model_preference = factor(model_preference,
+                                   levels = c("Main",
+                                              "Alternative"))) %>%
+  ggplot(aes(x = reorder(model_number, estimate),
+             y = exp(estimate),
+             color = model_preference,
+             fill = model_preference)) +
+  geom_hline(yintercept=1, linetype='dotted') +
+  geom_crossbar(aes(ymin = exp(lower_99),
+                    ymax = exp(upper_99)),
+                fatten = 0,
+                alpha = 0.2) +
+  geom_crossbar(aes(ymin = exp(lower_95),
+                    ymax = exp(upper_95)),
+                fatten = 0,
+                alpha = 0.3) +
+  geom_point(alpha = 1, size=1) +
+  theme_classic() +
+  theme(axis.text.x = element_blank(),
+        legend.position = "top",
+        axis.title = element_blank(),
+        axis.ticks.x = element_blank(),
+        strip.text = element_text(size=12),
+        text = element_text(family = "Source Sans Pro")) +
+  coord_cartesian(xlim=c(1-min_space, max(nrow(model_outputs_temp))+min_space)) +
+  scale_color_manual(values = c(col_model_main,
+                                col_model_other),
+                     name = "") +
+  scale_fill_manual(values = c(col_model_main,
+                                col_model_other),
+                     name = "") +
+  labs(title = ifelse(l == "exposure_temperature", "Temperature (C)",
+                      ifelse(l == "exposure_sm", "Soil moisture (%)",
+                             ifelse(l == "exposure_temperature:exposure_sm", "Interaction (temperature X soil moisture)",
+                               ifelse(l == "cyclone_binary", "Cyclone (binary)",
+                                      "Cyclone (count)")))))
+
+ggsave(filename = paste0("sensitivity_analysis_top_", l,".jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 7,
+       height = 5)
+
+control_plot <-
+
+  model_outputs_temp %>%
+  mutate(
+    NB = ifelse(model_type == "NB", 1, 0),
+    Poisson = ifelse(model_type == "Poisson", 1, 0),
+    # ZINB = ifelse(zero_inflated == TRUE, 1, 0),
+    'Full sample' = ifelse(sample == "all", 1, 0),
+    'CSB/FSP only' = ifelse(sample == "primary", 1, 0),
+    'Cleaned data' = ifelse(cleaned_data == TRUE, 1, 0),
+    'Raw data' = ifelse(cleaned_data == FALSE, 1, 0),
+    'Interactive model' = ifelse(model_form == "Temperature X Soil moisture", 1, 0),
+    'Additive model' = ifelse(model_form == "Temperature + Soil moisture", 1, 0),
+    'Cyclone (count)' = ifelse(cyclone == "count", 1, 0),
+    'Cyclone (binary)' = ifelse(cyclone == "binary", 1, 0),
+    'Time FE' = ifelse(time_fe == "fixed", 1, 0),
+    'Region FE' = ifelse(region_fe == "fixed", 1, 0)) %>%
+  dplyr::select(model_number, estimate, NB:'Region FE') %>%
+  pivot_longer(cols = c(NB:'Region FE'),
+               names_to = "spec_name",
+               values_to = "spec_status") %>%
+  mutate(spec_name = factor(spec_name,
+                            levels = c("NB",
+                                       "Poisson",
+                                       'Full sample',
+                                       'CSB/FSP only',
+                                       'Cleaned data',
+                                       'Raw data',
+                                       'Interactive model',
+                                       'Additive model',
+                                       'Cyclone (count)',
+                                       'Cyclone (binary)',
+                                       'Time FE',
+                                       'Region FE'))) %>%
+  ggplot(aes(x = reorder(model_number, estimate),
+             y = spec_name,
+             fill = as.factor(spec_status))) +
+  geom_point(shape=22, size=2.2) +
+
+  scale_fill_manual(values = c(col_spec_no, col_spec_yes),
+                     name = "") +
+  guides(fill= "none") +
+  # scale_y_continuous(breaks = unique(control_grid_logit$y),
+  #                    labels = unique(control_grid_logit$key),
+  #                    limits=c(min(control_grid_logit$y)-1, max(control_grid_logit$y)+1)) +
+  #scale_x_continuous(breaks=c(1:nrow(model_outputs_temp))) +
+  coord_cartesian(xlim=c(1-min_space, nrow(model_outputs_temp)+min_space)) +
+  theme_classic() +
+  theme(panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title = element_blank(),
+        axis.text.y = element_text(size=10),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        strip.text = element_text(size=12),
+        text = element_text(family = "Source Sans Pro"))
+
+ggsave(filename = paste0("sensitivity_analysis_bottom_", l,".jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 7,
+       height = 3)
+
+combined_plot <- cowplot::plot_grid(coef_plot,
+                   control_plot,
+                   rel_heights=c(1,0.5),
+                   align='v', ncol=1, axis='b')
+
+print(combined_plot)
+
+ggsave(filename = paste0("sensitivity_analysis_0_", l,".jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 12.5,
+       height = 7)
+
+ggsave(filename = paste0("figure_6.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 12.5,
+       height = 7)
+
+}
+
+```
+
+```{r figure_sensitivity_analysis_cyclone, include = TRUE, echo=FALSE, warnings = FALSE,  fig.width = 15, fig.height = 9, fig.align='center', out.width = '95%', fig.scap=paste("Specification curve depicting the effect estimates and confidence intervals for duration of cyclone activity across", num_models_multiverse, "models."), out.extra='', fig.cap=paste("\\label{figure_sensitivity_analysis_cyclone}Specification curve depicting the effect estimates and confidence intervals for cyclone activity (measured as days with a tropical storm or cyclone impacting Madagascar in a month) across", as.numeric(num_models_multiverse)/3, "models.
+In the top panel, estimated incidence rate ratios (IRRs) across different models are depicted as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+The dotted horizontal line depicts a null effect.
+The IRR estimate and confidence intervals of the preferred model, Model 4, are highlighted in orange.
+Below each model, a legend of shaded and unshaded boxes indicates which modeling decisions correspond to a given model, with boxes shaded teal showing active features.
+FE: fixed effects.
+CSB/FSP: Centres Santé de Base and Formations Sanitaires Privées de Base.
+NB: negative binomial model.", sep=" ")}
+
+coef_plot_coefficients <- c("days_with_cyclone")
+
+preferred_model <- model_outputs %>%
+  function_filter_results(preferred_model = TRUE) %>%
+  filter(model_form == "Temperature X Soil moisture") %>%
+  dplyr::select(model_number) %>% unique()
+
+preferred_model <- as.numeric(preferred_model$model_number)
+
+for (l in coef_plot_coefficients) {
+
+model_outputs_temp <- model_outputs %>%
+  function_filter_results(preferred_model = FALSE) %>%
+  filter(coefficient == l) %>%
+  filter(model_type != "ZINB") %>%
+  filter(model_form == "Temperature X Soil moisture" |
+           model_form == "Temperature + Soil moisture")
+
+min_space = 0.5
+y_min_val = min(model_outputs_temp$lower_99)
+y_max_val = max(model_outputs_temp$upper_99)
+
+# model_outputs_temp %>%
+#   ggplot(aes(x = reorder(model_number, estimate))) +
+#   geom_hline(yintercept=1, linetype='dotted') +
+#   geom_errorbar(aes(x = reorder(model_number, estimate), ymin = estimate, ymax = standard_error),
+#                 alpha = 0.15)
+
+coef_plot <-  model_outputs_temp %>%
+  mutate(model_preference = ifelse(model_number == preferred_model,
+                                   "Main",
+                                   "Alternative")) %>%
+  mutate(model_preference = factor(model_preference,
+                                   levels = c("Main",
+                                              "Alternative"))) %>%
+  ggplot(aes(x = reorder(model_number, estimate),
+             y = exp(estimate),
+             color = model_preference,
+             fill = model_preference)) +
+  geom_hline(yintercept=1, linetype='dotted') +
+  geom_crossbar(aes(ymin = exp(lower_99),
+                    ymax = exp(upper_99)),
+                fatten = 0,
+                alpha = 0.2) +
+  geom_crossbar(aes(ymin = exp(lower_95),
+                    ymax = exp(upper_95)),
+                fatten = 0,
+                alpha = 0.3) +
+  geom_point(alpha = 1, size=1) +
+  theme_classic() +
+  theme(axis.text.x = element_blank(),
+        legend.position = "top",
+        axis.title = element_blank(),
+        axis.ticks.x = element_blank(),
+        strip.text = element_text(size=12),
+        text = element_text(family = "Source Sans Pro")) +
+  coord_cartesian(xlim=c(1-min_space, max(nrow(model_outputs_temp))+min_space)) +
+  scale_color_manual(values = c(col_model_main,
+                                col_model_other),
+                     name = "") +
+  scale_fill_manual(values = c(col_model_main,
+                                col_model_other),
+                     name = "") +
+  labs(title = ifelse(l == "exposure_temperature", "Temperature (C)",
+                      ifelse(l == "exposure_sm", "Soil moisture (%)",
+                             ifelse(l == "exposure_temperature:exposure_sm", "Interaction (temperature X soil moisture)",
+                               ifelse(l == "cyclone_binary", "Cyclone (binary)",
+                                      "Cyclone activity (days per month)")))))
+
+ggsave(filename = paste0("sensitivity_analysis_top_", l,".jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 7,
+       height = 5)
+
+control_plot <-
+
+  model_outputs_temp %>%
+  mutate(
+    NB = ifelse(model_type == "NB", 1, 0),
+    Poisson = ifelse(model_type == "Poisson", 1, 0),
+    # ZINB = ifelse(zero_inflated == TRUE, 1, 0),
+    'Full sample' = ifelse(sample == "all", 1, 0),
+    'CSB/FSP only' = ifelse(sample == "primary", 1, 0),
+    'Cleaned data' = ifelse(cleaned_data == TRUE, 1, 0),
+    'Raw data' = ifelse(cleaned_data == FALSE, 1, 0),
+    'Interactive model' = ifelse(model_form == "Temperature X Soil moisture", 1, 0),
+    'Additive model' = ifelse(model_form == "Temperature + Soil moisture", 1, 0),
+    'Cyclone (count)' = ifelse(cyclone == "count", 1, 0),
+    'Cyclone (binary)' = ifelse(cyclone == "binary", 1, 0),
+    'Time FE' = ifelse(time_fe == "fixed", 1, 0),
+    'Region FE' = ifelse(region_fe == "fixed", 1, 0)) %>%
+  dplyr::select(model_number, estimate, NB:'Region FE') %>%
+  pivot_longer(cols = c(NB:'Region FE'),
+               names_to = "spec_name",
+               values_to = "spec_status") %>%
+  mutate(spec_name = factor(spec_name,
+                            levels = c("NB",
+                                       "Poisson",
+                                       'Full sample',
+                                       'CSB/FSP only',
+                                       'Cleaned data',
+                                       'Raw data',
+                                       'Interactive model',
+                                       'Additive model',
+                                       'Cyclone (count)',
+                                       'Cyclone (binary)',
+                                       'Time FE',
+                                       'Region FE'))) %>%
+  ggplot(aes(x = reorder(model_number, estimate),
+             y = spec_name,
+             fill = as.factor(spec_status))) +
+  geom_point(shape=22, size=4) +
+
+  scale_fill_manual(values = c(col_spec_no, col_spec_yes),
+                     name = "") +
+  guides(fill= "none") +
+  # scale_y_continuous(breaks = unique(control_grid_logit$y),
+  #                    labels = unique(control_grid_logit$key),
+  #                    limits=c(min(control_grid_logit$y)-1, max(control_grid_logit$y)+1)) +
+  #scale_x_continuous(breaks=c(1:nrow(model_outputs_temp))) +
+  coord_cartesian(xlim=c(1-min_space, nrow(model_outputs_temp)+min_space)) +
+  theme_classic() +
+  theme(panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank(),
+        axis.text.x = element_blank(),
+        axis.title = element_blank(),
+        axis.text.y = element_text(size=10),
+        axis.ticks = element_blank(),
+        axis.line = element_blank(),
+        strip.text = element_text(size=12),
+        text = element_text(family = "Source Sans Pro"))
+
+ggsave(filename = paste0("sensitivity_analysis_bottom_", l,".jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 7,
+       height = 3)
+
+combined_plot <- cowplot::plot_grid(coef_plot,
+                   control_plot,
+                   rel_heights=c(1,0.5),
+                   align='v', ncol=1, axis='b')
+
+print(combined_plot)
+
+ggsave(filename = paste0("sensitivity_analysis_0_", l,".jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 12.5,
+       height = 7)
+
+ggsave(filename = paste0("figure_7.jpg"),
+       plot = last_plot(),
+       path = analysis_figures,
+       width = 12.5,
+       height = 7)
+
+}
+
+```
+
+\elandscape
+
+\newpage
+
+## Discussion
+
+In our study of health facilities in Madagascar, we investigated how temperature, soil moisture, and exposure to cyclone activity impacted monthly incident cases of mental and neurological disorders reported by `r num_facilities_pretty`  facilities between 2010 and 2020.
+We found evidence of a statistically significant reduction in reported cases associated with mean monthly temperature, with warmer temperature being, on average, associated with 2 to 3 fewer cases per month.
+According to our multiverse analysis, the statistically significant inverse association we observed was robust to numerous specifications, while our subgroup analysis indicated that this association was primarily localized in the highland subhumid forest ecoregion.
+
+With respect to soil moisture, we found evidence to suggest potential lagged impacts, with higher soil saturation being associated with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in reported case counts in the subsequent quarter.
+We also found evidence of possible effect heterogeneity, with each percentage point increase in soil moisture leading to an *elevation* of cases in the dry deciduous forest ecoregion `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = TRUE)` and a *decrease* in cases in the highland subhumid forests `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = TRUE)`.
+
+Finally, while our lagged models and multiverse analysis suggested the possibility of a negative relationship between cyclone activity and incident case counts reported in Madagascar, the marginal effects associated with cyclone duration were negligible, and we did not observe sufficient statistically significant evidence to reject the null assumption of no association at a level of 0.01.
+
+It is important to note in our interpretation of these findings that the true relationship between reported mental health cases and actual cases of mental disorders is not well understood, particularly in Madagascar where data on disease etiology is limited.
+The changes in reported cases could reflect changes in the actual cases of mental disorders, but could also result from changes in help-seeking behavior, diagnostic capacity, or other factors.
+Additionally, it is widely recognized that a significant proportion of individuals with mental disorders do not receive any treatment, particularly in low-income settings.
+
+With these caveats in mind, our results concerning an inverse relationship between temperature and recorded cases of mental and neurological disorders are nonetheless surprising and run counter to our expectation, given that a robust body of literature has documented that heat and heat waves have a harmful effect on mental health outcomes[@thompsonAssociationsHighAmbient2018] and general aspects such as mood,[@connollyItMildNot2013] life satisfaction,[@maddisonImpactClimateLife2011] and happiness.[@rehdanzClimateHappiness2005]
+
+Research in subtropical regions, however, has found that the association between temperature and mental disorders is likely non-linear, with both extreme cold and extreme heat being associated with harmful effects on mental morbidity.[@zhangEffectTemperatureCausespecific2020] Degree increases in temperature, therefore, could show a protective effect in colder months, resulting in an overall inverse association between temperature and reported cases in a sample with few extremely warm months.
+This is consistent with our marginal effect estimates, which show the greatest reduction in case counts being associated with degree increases at the coldest temperatures.
+In addition, this explanation would be consistent with our subgroup analysis, which found that the protective effect of warmer temperatures was observed only among facilities in the central high plateau—where temperatures are generally cooler than those in the surrounding lowlands.
+
+An alternative explanation could be that access to mental health services is limited in warmer months due to factors such as increased demand for medical services related to heat-related illnesses.
+A crowding out of provider availability due to physical complaints in warmer months (for example, malaria-related fever) could lead to decreased availability of provider access for mental disorders, especially at primary health facilities with already limited diagnostic capacity.
+Understanding how climate conditions in Madagascar impact the broader burden of disease, including physical conditions, is the subject of current investigation, and will lend further insight into potential mechanistic explanations for our findings.
+
+With respect to soil moisture, to the best of our knowledge, there have been no studies that directly explore the association between soil saturation and mental health in non-emergency conditions.
+In terms of extremely low soil moisture, evidence from droughts suggest potential indirect pathways to worsened mental health outcomes,[@obrienDroughtMentalHealth2014] but these impacts are not well characterized and may not manifest over a short time horizon.[@vinsMentalHealthOutcomes2015]
+
+Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we did observe a significant association of higher soil moisture and cases of mental health complaints in the following quarter, echoing similar findings from U.S.
+meteorological data linking higher precipitation with worsened mental health.[@obradovichEmpiricalEvidenceMental2018] In addition, our subgroup analysis also indicated significant and diverging effects among different ecoregions.
+In particular, we found that greater soil moisture was associated with higher cases reported in the eastern lowlands and the northern dry deciduous forests, which echoes the geographic concentration of flood risk in Madagascar.[@rakotoarisonSpatialAnalysisRisks2021] Conversely, the observed (though statistically modest) reduction in cases associated with higher soil moisture in the desert and xeric shrublands overlaps with the concentration of drought risk, where increased soil moisture could be taken as an indicator of reduced drought vulnerability.
+It is important to note, however, that the time frame of available GESIS data excludes the most severe period of the ongoing drought in Madagascar, limiting our ability to directly study the impact of the current crisis on population mental health in this analysis.
+Further research could leverage spatial reanalysis data on precipitation to further characterize these associations.
+
+Madagascar’s wet season is marked by frequent tropical storms and cyclones—the intensification of which has been linked to rising temperatures in the Indian Ocean.[@ottoClimateChangeIncreased2022] In the majority of our models in the multiverse analysis, we found that months with greater duration of cyclone activity were associated with *fewer* monthly report cases of mental disorders, though none of these models were significant at the threshold of 0.01.
+In numerous studies, cyclones and similar disasters have been found to worsen mental health;[@obradovichEmpiricalEvidenceMental2018] however, these storms may also result in numerous conditions that make access to mental health resources more challenging.
+Disruptions to regular health care services and an intensification of acute health needs [@wangDisruptionExistingMental2008] in the post-disaster period could result in barriers to receiving care for incident mental disorders,[@shultzEpidemiologyTropicalCyclones2005] which would be consistent with a reduction in reported cases despite a rise in mental distress.
+
+Failure to observe effect heterogeneity in our subgroup analysis of the association of cyclone activity with reported case counts likely is due, in part, to our specification choice to define exposure to cyclone activity without geographic variation in intensity.
+While we felt justified in opting for a simplified indicator, given that storms in Madagascar typically impact the whole of the island, a more nuanced (but data-hungry) approach could define exposure with greater geographic precision based on additional climate metrics, including peak wind, rainfall, and distance from the storm’s track.[@andersonExposureAssessmentTropical2022]
+
+A further weakness of our analysis is that inherent to any ecological study relying on aggregated data: the lack of individual-level data substantively constraints our ability to draw causal inferences, account for and exclude potential confounding variables, and ascertain mechanistic explanations for observed associations.
+While these are important caveats in interpreting our results, we assert that there is considerable value in leveraging existing data from national health management information systems to generate epidemiologic evidence.
+The opportunity to employ health information system data is particularly important in countries like Madagascar, where, as in many LMICs, HMIS information is routinely generated but systematically underutilized.[@mbondjiHealthInformationSystems2014]
+
+Despite these limitations, our analysis brings together health data from over three thousand health facilities over ten years, utilizing the most comprehensive sources of climate data available, and linking the two via a rigorous, multistep geolocating process.
+This study—one of the only to investigate mental health and climate in Africa using national HMIS data—underscores the need for further research to understand the relationships and pathways between changing climate and population mental health.
+
+## Acknowledgements
+<!-- Update with names of internal reviewers -->
+
+We thank Jessica Cohen, Karestan Koenen, Margaret McConnell, and Stéphane Verguet for their feedback on an earlier version of this paper, as well Marissa Lynn Childs, Angela Jean Rigden, Oladimeji Mudele, and Wenchang Yang for their assistance in initially accessing and processing climate data.
+
+### Author contributions
+<!-- For future versions: All authors contributed to critical revision of the manuscript, with responses to reviewers and subsequent revisions led by DA.  -->
+
+All authors contributed to study conception, methodology, and interpretation.
+DA oversaw data acquisition, programming, formal analysis, visualization, and the first draft of the manuscript.
+All authors had access to and verified all the data and accept responsibility for the decision to submit for publication.
+
+### Funding statement
+<!-- Confirm with team -->
+
+This study was supported by funding from the Motsepe Presidential Research Accelerator Fund for Africa, the Ren Che Foundation, and the Harvard University Climate Change Solutions Fund.
+The funders had no role in the design and conduct of the study, nor in the collection, management, analysis, and interpretation of the data.
+The authors alone are responsible for the content and writing of the article.
+
+### Declaration of interests
+<!-- Confirm with team  -->
+
+We declare no competing interests.
+
+### Data sharing statement
+<!-- Would be good to provide information on whether the Madagascar mental health data is available  -->
+All codes used for the analysis in this article are available on GitHub (https://github.com/darias5/madagascar_mh).
+
+```{r paper2_cleanup}
+
+rm(packages_and_paremeters_on)
+
+```

### 2023-02-10 paper3.Rmd
Adding first cut of thesis
Clean up of formatting and typesetting throughout.

--- 2023-02-09 conclusion.Rmd
@@
----
-title: ''
-output: pdf_document
+```{r loading, include=FALSE}
 
----
+source("C:/Users/danie/Dropbox (Harvard University)/mh_scm/code/0_prep_file.R")
 
-\addcontentsline{toc}{section}{Conclusion}
-\section*{Conclusion}
+load(file = paste(datapath,"data_its_state.Rdata", sep = "/"))
 
-Thank you for following this tutorial!
+data_its_state <- data_temp
 
-I hope you'll find it useful to write a very professional dissertation.
+load(file = paste(datapath,"data_its_county.Rdata", sep = "/"))
 
-\cite{ngTracingPathChikungunya2010}
+data_its_county <- data_temp
+
+load(file = paste(datapath,"data_its_international.Rdata", sep = "/"))
+
+data_its_international <- data_temp
+
+rm(data_temp)
+
+load(file = paste(resultspath, "1_data",
+                  "model_outputs_all_main.Rdata", sep = "/"))
+
+load(file = paste(resultspath, "1_data",
+                  "model_outputs_all_US.Rdata", sep = "/"))
+
+load(file = paste(resultspath, "1_data",
+                  "model_outputs_all_international.Rdata", sep = "/"))
+
+load(file = paste(resultspath, "1_data",
+                  "model_outputs_all_diseases.Rdata", sep = "/"))
+
+ function_model_main <- function(data, polity = "include", levels = 
+                                   "exclude"){
+
+   data_temp <- data %>%
+     filter(bandwidth == 40 & 
+               cleaning == TRUE &
+              time == "daily" &
+               day_of_week_fe == TRUE &
+               month_fe == TRUE &
+               geograph_fe == TRUE &
+              cits == "TRUE" &
+              weights == "population")
+
+   if (levels == "exclude") {
+
+       data_temp <- data_temp %>%
+     filter( geography == "county")
+
+   }
+
+   if (polity == "exclude") {
+
+       data_temp <- data_temp %>%
+     filter(polity == "all")
+
+   }
+
+   return(data_temp)
+
+ }
+
+model_output_main <- model_outputs_all_US %>%
+  function_model_main()
+
+function_clean_diseases <- function(data){
+
+  data %>%
+    mutate(disease = str_to_sentence(str_replace_all(disease, "_", " "))) %>%
+    mutate(disease = ifelse(disease == "Attention deficit hyperactivity disorder", "ADHD", disease),
+           disease = ifelse(disease == "Generalized anxiety disorder", "GAD", disease),
+           disease = ifelse(disease == "Major depressive disorder", "MDD", disease),
+           disease = ifelse(disease == "Avoidant personality disorder", "AvPD", disease))
+
+}
+
+list_diseases_all <- read.xlsx(paste(datapath, 
+                         "list_of_diseases.xlsx", sep = "/")) %>%
+  filter(mh_indicator == 1) %>%
+  select(search)
+
+list_diseases_all <- list_diseases_all$search
+
+mental_disorders <- c("anxiety", "depression", "major_depressive_disorder")
+geography <- c("state", "county", "international")
+
+paper3_abstract <- paste0("For searches related to depression, we observe a statistically significant slope change of -0.0304 percentage points per day (p < 0.0001, 99\\% CI: -0.0321– -0.0286) and a level shift of -0.184 (p < 0.0001, 99\\% CI: -0.226– -0.143), above and beyond changes in slope and level observed for searches for headaches.
+For anxiety, we observe a similar slope change decline of 0.0383 percentage points per day (p < 0.0001, 99\\% CI: -0.0400– -0.0366) and a level shift of -0.339 (p < 0.0001, 99\\% CI: -0.378– -0.299).
+We do not observe significant variation of estimates across predominately Democrat or Republican voting states and counties, and our results are robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
+
+```
+
+# The impact of COVID-19 vaccine developments on Google COVID-19 search trends for mental health symptoms: a controlled interrupted time series analysis
+
+\begin{centering}
+
+\emph{Daniel Arias, Jessica Cohen, Karestan Koenen, Margaret McConnell, Stéphane Verguet}
+
+\vspace{24pt}
+
+\noindent\rule{8cm}{0.4pt}
+
+\end{centering}
+
+\begin{raggedright}
+
+\vspace*{\fill}
+
+{\bf Background:} A key obstacle to studying the effects of public health responses on population mental health in the US is a lack of daily surveillance data on mental health indicators.
+A potential marker of population mental health is the use of Internet search data, which offers the potential for real-time, large-scale analysis and identification of evolving mental health issues.
+
+{\bf Methods:} We utilize controlled interrupted time series (CITS) approach to evaluate whether the development and announcement of safe and effective COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety.
+By comparing how search trends changed in the post period for mental health symptoms above and beyond changes observed in the same period for physical health symptoms, we estimate measures of association between the vaccine announcement and changes in mental health symptom search density.
+We adjust for state, month, and day of week effects, and we apply a sensitivity analysis to assess the robustness of our estimates to alternative specifications.
+We further examine whether estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
+
+{\bf Findings and interpretation:} Under our main specification, we find evidence of reduced search density associated with the announcement of vaccine safety data for Google search trends for depression and anxiety.
+`r paper3_abstract`
+
+\emph{Keywords: mental health, controlled interrupted time series, Google searches, United States, COVID-19 vaccines.}
+
+\end{raggedright}
+
+\newpage
+
+## Introduction
+It has been well-documented that throughout the pandemic, symptoms of depression and anxiety have markedly increased among US adults.
+While it is likely that the pandemic has a direct effect on worsened mental health status due to fear of contracting and spreading the virus, public health responses to the pandemic—including lockdowns, school closures, and social distancing measures—likely have an indirect effect as well.
+Existing research suggests that the effects of these measures on mental health vary, and may be protective, null, or even harmful.
+Studies of lockdowns in multiple countries, for example, point to worsened feelings of isolation and hopelessness exacerbated by isolation measures.
+By contrast, the distribution of safe and effective vaccines against COVID-19 has been shown to reduce symptoms of depression and anxiety by as much as XXX.
+
+* Describe symptoms database and reference published literature using it to predict COVID-19 cases and deaths [@alruilyPredictionCovid19Transmission2022; @abbasAssociationsGoogleSearch2021; @saegnerForecastingSurveillanceCOVID192022]
+
+A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset found strong correlation between search trends for depression and anxiety with indicators of mental health service utilization and need reported in the US Census Household Pulse Survey (HPS) with rates of emergency department visits for mental health condition as reported in the US Centers for Disease Control and Prevention’s (CDC) National Syndromic Surveillance Program (NSSP).[@vaidyanathanEvaluationInternetSearches2022]
+
+* Motivation to explore vaccine announcement: evidence that vaccination itself reduced depression and anxiety -- do we see earlier reductions from an anticipatory effect?
+* Motivation to analyze by polity: Vaccination became politically charged in the US, possible bias from impact of 2020 election on mental health searches
+* Overview of approach: CITS using searches for headache as a control, adjusting for fixed effects, subgroup analysis by polity, analysis for 6 different mental health symptoms
+
+## Methods
+
+### Data
+
+#### Shock date
+
+We take as our first credible signal of the imminent availability of safe and effective COVID-19 vaccines to be November 16, 2020.
+On November 9, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16th, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S.
+Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners and laypersons as a substantial signal of a new phase of the pandemic, with Moderna's chief executive officer calling the news "a game changer" in the fight against COVID-19.
+
+#### Symptoms dataset
+
+We access U.S.
+county- and state-level data from Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020](hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021 for six symptoms: anxiety, depression, generalized anxiety disorders, headache, major depressive disorders, and panic attacks.
+Data on headaches was obtained to provide a control trend from a common health symptom with comparative characteristics to mental health complaints.
+
+* Linear interpolation to replace missing values
+* Also used smoothing to address outliers (sensitivity analysis showed no difference when unadjusted values were used)
+* Not all counties reported data (due to data privacy concerns, smaller county results were not included in the symptoms dataset)
+
+#### Voting dataset
+
+We further obtained county-level presidential election returns for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we then used to calculate aggregate county and state votes (including absentee, early, and election day ballots) won by each candidate.
+The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the candidate with the most votes to the runner up); margins were then used to sort counties and states into quintiles, with the 20% most Republican-voting localities appearing in the symptoms dataset sorted into bin 1 and the 20% most Democratic-voting localities sorted into bin 5.
+
+* Joined to symptoms dataset by FIPS code
+
+## Statistical analysis
+
+All analyses were completed using R (version 4.2.1).[@rcoreteamLanguageEnvironmentStatistical2022]
+
+### Modeling approach
+
+We use a controlled interrupted time series (CITS) approach.
+
+Model equation for Google search density (measured as the ratio between the normalized search volume for a given symptom during a given week and the median search volume for that symptom between 2018 and 2020):
+
+$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_i + \lambda_3 time_t*Post_i + $$
+$$ \alpha_d treated_{di} + \beta_d time_t*treated_{di} + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \epsilon_{it}$$
+where $time_t$: is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$: is an indicator variable which equals 1 in the "post" period and 0 otherwise, and $treated_di$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches.
+
+The CITS effect estimates of interest are given by $\delta$, which reflects the additional level shift among mental health related symptoms searches compared to searches for headaches after the vaccine announcement, and  $\gamma$, the additional change in search density over time (i.e., slope change) comparing the same.
+
+* Fixed effects included for day of week, month, and state
+* Trim bandwidth to 40 days before and after the announcement
+* Subgroup analysis by polity to examine whether effects were different in very Democrat leaning geographies vs. Republican leaning ones
+
+### Sensitivity analysis
+
+Interacted modeling decisions:
+
+* County vs. state level aggregated data
+* Replacement of outliers with smoothing
+* Fixed effects for day of week
+* Fixed effects for month
+* Fixed effects for state
+* Bandwidth selection (30, 40, 50, 60 days)
+
+128 models for each disease and polity level (384 models per disease, 2,304 in total across all 6 conditions)
+
+### Ethics statement
+The Institutional Review Board (IRB) of the Harvard T.H.
+Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).
+
+## Results
+
+```{r}
+
+```
+
+* Sharp declines in searches for depression and anxiety following vaccine announcement
+* No meaningful differences in searches for major depression and major anxiety, panic attacks, or sleep disorders
+* Results do not strongly vary by polity
+
+## Discussion
+
+* Shows that event the announcement of a safe and effective vaccine led to a significant shift in searches.
+If searches are taken as a reasonable proxy of mental health status, the period following the announcement saw both a sharp decline in depression and anxiety
+
+* Lack of heterogeneity by polity is interesting, given evidence that polity is a strong predictor of attitudes towards COVID-19 vaccination.
+Also makes bias from an uncommon shock (e.g., 2020 election) less likely to explain the results
+
+\newpage
+
+```{r figure_cits_outputs, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7, fig.height = 8, fig.align='center', out.width = '95%', fig.scap="Controlled interrupted time series effect estimates on Google Search density by symptom.", out.extra='',  fig.cap="\\label{figure_cits_outputs}Controlled interrupted time series effect estimates (A: slope change per 10 days and B: level shift)  on Google Search density by symptom.
+Effect estimates are represented as thick, horizontal lines in between colored bands, which represent the 99\\% confidence intervals for the estimates.
+Colors reflect the sign and magnitude of effect estimates.
+Dark blue values above zero indicate an increase in search density, while the yellow and green negative values indicate a decrease.
+The dotted horizontal line depicts a null effect.
+ADHD: Attention deficit hyperactivity disorder.
+GAD: Generalized anxiety disorder.
+MDD: Major depressive disorder."}
+
+model_outputs_all_main %>% 
+   function_model_main("exclude") %>%
+  function_clean_diseases () %>%
+  arrange(disease) %>%
+   mutate(estimate = ifelse(coefficient == "post:time:trt", estimate*10, estimate),
+         lower_99 = ifelse(coefficient == "post:time:trt", lower_99*10, lower_99),
+         upper_99 = ifelse(coefficient == "post:time:trt", upper_99*10, upper_99)
+         ) %>%
+    mutate(coefficient = ifelse(coefficient == "post:time:trt", "A: slope change (per 10 days)",
+                              ifelse(coefficient == "post:trt", "B: level shift", "ERROR"))) %>%
+  mutate(sign = ifelse(estimate >0, TRUE, FALSE)) %>%
+
+  ggplot(aes(x = disease, 
+             y = estimate, ymin = lower_99, ymax = upper_99, fill = estimate)) +
+  geom_crossbar() +
+    theme_classic() +
+      geom_hline(yintercept = 0, linetype='dotted') +
+
+   geom_point(alpha = 0.5) +
+  labs(x = "Symptom", y = "Estimate") +
+  theme(
+    legend.position = "none",
+    strip.text = element_text(size=12),
+    text = element_text(family = "Source Sans Pro"),
+    axis.text.x = element_text(#size = 4, 
+                               angle = 90, vjust = 0.5, hjust=1)) +
+  facet_wrap(~coefficient, scales = "free_y", dir = "v") +
+  scale_fill_viridis(direction = -1
+
+  )
+ #  
+ # scale_fill_manual(values = c(col_negative, col_positive),
+ #                      name = "")
+
+```
+
+```{r figure_all_diseases, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 6, fig.height = 4.5, fig.align='center', out.width = '95%',  fig.scap="Interrupted time series (ITS) effect estimates and confidence intervals by symptom.", out.extra='',  fig.cap="\\label{figure_all_diseases}Interrupted time series (ITS) effect estimates and confidence intervals by symptom.
+Effect estimates are presented by points;  for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
+The horizontal and vertical bars next to each point represent the 99\\% confidence intervals for the estimate slope change and level shift, respectively.
+Mental health-related symptoms are shown in blue, while physical symptoms are shown in grey.
+ADHD: Attention deficit hyperactivity disorder.
+MDD: Major depressive disorder."}
+
+model_outputs_all_diseases_graph <- model_outputs_all_diseases %>%
+  mutate(coefficient = ifelse(coefficient == "post:time", "slope",
+                              ifelse(coefficient == "post", "level", "ERROR"))) %>%
+  select(coefficient, estimate, lower_95, upper_95, disease, p_value) %>%
+  pivot_wider(names_from = coefficient,
+              values_from = c(estimate, lower_95, upper_95, p_value)) %>%
+  mutate(mh_indicator = ifelse(disease %in% list_diseases_all, 
+                               "Mental symptom",
+                               "Physical symptom"))  %>%
+      function_clean_diseases()
+
+model_outputs_all_diseases_graph %>%
+  ggplot(aes(y = estimate_level, x = estimate_slope, color = mh_indicator, label = disease)) +
+  geom_hline(yintercept = 0) +
+  geom_vline(xintercept = 0) +
+  geom_errorbarh(aes(xmin = lower_95_slope, xmax = upper_95_slope), alpha = 0.3) +
+  geom_errorbar(aes(ymin = lower_95_level, ymax = upper_95_level), alpha = 0.3) +
+  theme_classic() +
+  geom_point(alpha = 0.75) +
+  theme(
+    legend.position = "bottom",
+    strip.text = element_text(size=12),
+
+    text = element_text(family = "Source Sans Pro")) +
+      scale_color_manual(values = c(col_mh,
+                                    col_grey_lightest),
+                         name = "") +
+      labs(x = "Slope change", y = "Level shift") +
+  geom_text_repel(data=subset(model_outputs_all_diseases_graph, estimate_slope < -0.04 |
+                                (estimate_slope <.01 & mh_indicator ==  "Mental symptom")),
+                  size = 3)
+
+```
+
+```{r figures_cits_data, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 9.5, fig.height = 8, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends, by symptom and region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data}Density of Google Search trends, by symptom and region, as a function of time.
+In each row, search density data for two symptoms are displayed: one of three mental health symptoms (from top to bottom: anxiety, depression, and major depressive disorder) in blue and headaches in grey.
+In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
+In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
+Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
+The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
+US: United States."}
+
+n = 1
+
+for (m in mental_disorders) {
+  for (g in geography){
+    data_its <- get(paste0("data_its_",g))
+
+    data_its_temp <- data_its %>%
+      mutate(post = ifelse(date > date_shock_vax, 1, 0),
+             trt = ifelse(search == "headache", 0, 1)) %>%
+      mutate(days_post_shock = as.numeric(date - date_shock_vax)) %>%
+      filter(days_post_shock %in% (-40:40) ) %>%
+      filter(search == m | search == "headache" )
+
+    model <- glm(daily_mean_clean ~ post*days_post_shock*trt ,
+                 data_its_temp, family = "gaussian")
+
+    data_its_temp <- data_its_temp %>% 
+      mutate(fitted = fitted(model),
+             trt = ifelse(trt == 0, "Headache", 
+                          str_to_sentence(str_replace_all(m, "_", " "))))
+
+    m2 <- c(str_to_sentence(str_replace_all(m, "_", " ")))
+
+    if(g != "county"){
+
+      plot <- data_its_temp %>% 
+        filter(days_post_shock %in% (-40:40) ) %>%
+        mutate(trt = factor(trt, 
+                            levels = c(m2,
+                                       "Headache"))) %>%
+        ggplot(aes(x = days_post_shock, y = fitted, group = trt, color = trt)) +
+        geom_line() +
+        theme_classic() +
+        labs(x = "Days after November 16, 2020",
+             y = "Density of Google Search trends",
+             color = "",
+             title = ifelse(g == "state", "U.S. states", 
+                            ifelse(g == "county", "U.S. counties",
+                                   "International data"))) +
+        theme(legend.position = "bottom") +
+        geom_vline(xintercept = 0, linetype='dotted') +
+        geom_point(aes(y = daily_mean_clean),
+                   alpha = 0.05) +
+        scale_color_manual(values = c(col_mh, col_headache),
+                           name = "")
+    }else{
+
+      plot <- data_its_temp %>% 
+        filter(days_post_shock %in% (-40:40) ) %>%
+        mutate(trt = factor(trt, 
+                            levels = c(m2,
+                                       "Headache"))) %>%
+        ggplot(aes(x = days_post_shock, y = fitted, group = trt, color = trt)) +
+        geom_boxplot(aes(x = days_post_shock, y = daily_mean_clean, 
+                         group = interaction(trt, days_post_shock), color = trt, 
+                         fill = trt, outlier.shape = NA),
+                     outlier.shape = NA,
+                     alpha = 0.01) +
+        geom_line() +
+        theme_classic() +
+        labs(x = "Days after November 16, 2020",
+             y = "Density of Google Search trends",
+             color = "",
+             title = ifelse(g == "state", "US states", 
+                            ifelse(g == "county", "US counties",
+                                   "International data"))) +
+        theme(legend.position = "bottom") +
+        geom_vline(xintercept = 0, linetype='dotted') +
+        scale_color_manual(values = c(col_mh, col_headache),
+                           name = "") +
+        scale_fill_manual(values = c(col_mh, col_headache),
+                          name = "")
+
+    }
+
+assign(paste0("plot_",n), plot)
+
+n = n+1
+
+  }
+}
+
+    combo_plot_1 <- cowplot::plot_grid(plot_1,
+                                       plot_2,
+                                      plot_3,
+                                      plot_4,
+                                       plot_5,
+                                      plot_6,
+                                      plot_7,
+                                       plot_8,
+                                      plot_9,
+                       align='v', ncol=3, axis='b')
+
+    print(combo_plot_1)
+
+```
+
+\blandscape
+
+```{r fig_multiverse_analysis,include = TRUE, echo=FALSE, warnings = FALSE,  fig.width = 20, fig.height = 12, fig.align='center', out.width = '99%', fig.scap="Specification curve depicting the CITS effect estimates and confidence intervals for search density", out.extra='',  fig.cap="\\label{fig_multiverse_analysis}Specification curve depicting the CITS effect estimates and confidence intervals for search density, with panel A depicting the estimated slope change and panel B depicting the estimate level shift.
+Within each panel, the effect estimates across different models are depicted as circles in the upper graph; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+The dotted horizontal line depicts a null effect.
+The effect estimates and confidence intervals of the main specification are highlighted in orange.
+Below each model, a legend of shaded and unshaded boxes indicates which modeling decisions correspond to a given model, with boxes shaded teal showing active features.
+The three vertical columns show effect estimates by symptom.
+From left to right, these are anxiety, depression, and major depressive disorder.
+FE: fixed effects.
+CITS: controlled interrupted time series.
+FE: fixed effects.
+CITS: controlled interrupted time series."}
+
+    model_outputs_temp <- model_outputs_all_international %>%
+      filter(time == "daily") %>%
+  filter(disease %in% mental_disorders) %>%
+  mutate(disease = str_to_sentence(str_replace_all(disease, "_", " ")))
+
+    preferred_model <- model_outputs_temp %>% 
+      filter(bandwidth == 40 & 
+               cleaning == TRUE &
+               day_of_week_fe == TRUE &
+               month_fe == TRUE &
+               geograph_fe == TRUE &
+               geography == "county") %>%
+      select(model_number) %>%
+      unique()
+
+    preferred_model <- preferred_model$model_number
+
+    min_space = 0.5
+    y_min_val = min(model_outputs_temp$lower_99)
+    y_max_val = max(model_outputs_temp$upper_99)
+
+    coef_plot_a <-  model_outputs_temp %>%
+      filter(coefficient == "post:time:trt") %>%
+      mutate(model_preference = ifelse(model_number %in% preferred_model, 
+                                       "Main",
+                                       "Alternative")) %>%
+      mutate(model_preference = factor(model_preference, 
+                                       levels = c("Main", 
+                                                  "Alternative"))) %>%
+
+      ggplot(aes(x = reorder(model_number, estimate),
+                 y = (estimate),
+                 fill = model_preference,           
+                 color = model_preference)) +
+      geom_hline(yintercept=0, linetype='dotted') +
+      geom_crossbar(aes(ymin = (lower_99), 
+                        ymax = (upper_99)),
+                    fatten = 0,
+                    alpha = 0.2) +
+      geom_crossbar(aes(ymin = (lower_95),
+                        ymax = (upper_95)),
+                    fatten = 0,
+                    alpha = 0.3) +
+      geom_point(alpha = 1, size=1) +
+      theme_classic() +
+      theme(axis.text.x = element_blank(),
+            legend.position = "top",
+            axis.title = element_blank(),
+            axis.ticks.x = element_blank(),
+            strip.text = element_text(size=12),
+            text = element_text(family = "Source Sans Pro")) +
+      # coord_cartesian(xlim=c(1-min_space, max(nrow(model_outputs_temp))+min_space)) +
+      scale_color_manual(values = c(col_model_main,
+                                    col_model_other),
+                         name = "") +
+      scale_fill_manual(values = c(col_model_main,
+                                   col_model_other),
+                        name = "") +
+      # labs(title =  paste0("CITS effect estimates on Google search density for: ", tolower(str_replace_all(d, "_", " "))),
+      #      subtitle = "A: slope change") +
+      facet_wrap(~disease, scales = "free_x")
+
+    control_plot_a <-
+
+      model_outputs_temp %>%
+      filter(coefficient == "post:time:trt") %>%
+      mutate(
+        "State level" = ifelse(geography == "state", 1, 0),
+        "County level" = ifelse(geography == "county", 1, 0),
+        "International level" = ifelse(geography == "international", 1, 0),
+        # "Daily data" = ifelse(time == "daily", 1, 0),
+        # "Weekly data" = ifelse(time == "weekly", 1, 0),
+        "Replaced outliers?" = ifelse(cleaning == TRUE, 1, 0),
+        "FE: day of week" = ifelse(day_of_week_fe == TRUE, 1, 0),
+        "FE: month" = ifelse(month_fe == TRUE, 1, 0),
+        "FE: state" = ifelse(geograph_fe == TRUE, 1, 0),
+        # "Bandwidth = 30" = ifelse(bandwidth == 30, 1, 0),
+        "Bandwidth = 40" = ifelse(bandwidth == 40, 1, 0),
+        "Bandwidth = 50" = ifelse(bandwidth == 50, 1, 0),
+        "Bandwidth = 60" = ifelse(bandwidth == 60, 1, 0)
+
+        ) %>%
+
+      dplyr::select(model_number, estimate, disease, 'State level':'Bandwidth = 60') %>%
+      pivot_longer(cols = c('State level':'Bandwidth = 60'), 
+                   names_to = "spec_name", 
+                   values_to = "spec_status") %>%
+      mutate(spec_name = factor(spec_name, 
+                                levels = c("State level",
+                                           "County level",
+                                           "International level",
+                                           # "Daily data",
+                                           # "Weekly data",
+                                           "Replaced outliers?",
+                                           "FE: day of week",
+                                           "FE: month",
+                                           "FE: state",
+                                           # "Bandwidth = 30",
+                                           "Bandwidth = 40",
+                                           "Bandwidth = 50",
+                                           "Bandwidth = 60"))) %>%
+      mutate(spec_name = fct_rev(spec_name)) %>%
+
+      ggplot(aes(x = reorder(model_number, estimate), 
+                 y = spec_name, 
+                 fill = as.factor(spec_status))) +
+      geom_point(shape=22, size=1.25) +
+
+      scale_fill_manual(values = c(col_spec_no, col_spec_yes),
+                        name = "") +
+      guides(fill= "none") +
+      # scale_y_continuous(breaks = unique(control_grid_logit$y), 
+      #                    labels = unique(control_grid_logit$key),
+      #                    limits=c(min(control_grid_logit$y)-1, max(control_grid_logit$y)+1)) +
+      #scale_x_continuous(breaks=c(1:nrow(model_outputs_temp))) +
+      # coord_cartesian(xlim=c(1-min_space, nrow(model_outputs_temp)+min_space)) +
+      theme_classic() +
+      theme(panel.grid.major.y = element_blank(),
+            panel.grid.minor.y = element_blank(),
+            axis.text.x = element_blank(),
+            strip.text.x = element_blank(),
+            axis.title = element_blank(),
+            axis.text.y = element_text(size=10),
+            axis.ticks = element_blank(),
+            axis.line = element_blank(),
+            strip.text = element_text(size=12),
+            text = element_text(family = "Source Sans Pro"))+
+      facet_wrap(~disease, scales = "free_x")
+
+    coef_plot_b <-  model_outputs_temp %>%
+      filter(coefficient != "post:time:trt") %>%
+
+      mutate(model_preference = ifelse(model_number %in% preferred_model, 
+                                       "Main",
+                                       "Alternative")) %>%
+      mutate(model_preference = factor(model_preference, 
+                                       levels = c("Main", 
+                                                  "Alternative"))) %>%
+
+      ggplot(aes(x = reorder(model_number, estimate),
+                 y = (estimate),
+                 fill = model_preference,           
+                 color = model_preference)) +
+      geom_hline(yintercept=0, linetype='dotted') +
+      geom_crossbar(aes(ymin = (lower_99), 
+                        ymax = (upper_99)),
+                    fatten = 0,
+                    alpha = 0.2) +
+      geom_crossbar(aes(ymin = (lower_95),
+                        ymax = (upper_95)),
+                    fatten = 0,
+                    alpha = 0.3) +
+      geom_point(alpha = 1, size=1) +
+      theme_classic() +
+      theme(axis.text.x = element_blank(),
+            legend.position = "none",
+            axis.title = element_blank(),
+            axis.ticks.x = element_blank(),
+            strip.text = element_text(size=12),
+            text = element_text(family = "Source Sans Pro")) +
+      # coord_cartesian(xlim=c(1-min_space, max(nrow(model_outputs_temp))+min_space)) +
+      scale_color_manual(values = c(col_model_main,
+                                    col_model_other),
+                         name = "") +
+      scale_fill_manual(values = c(col_model_main,
+                                   col_model_other),
+                        name = "") +
+      labs(subtitle = "B: level shift")  +
+      facet_wrap(~disease, scales = "free_x")
+
+    control_plot_b <-
+
+      model_outputs_temp %>%
+      filter(coefficient != "post:time:trt") %>%
+     mutate(
+        "State level" = ifelse(geography == "state", 1, 0),
+        "County level" = ifelse(geography == "county", 1, 0),
+        "International level" = ifelse(geography == "international", 1, 0),
+        # "Daily data" = ifelse(time == "daily", 1, 0),
+        # "Weekly data" = ifelse(time == "weekly", 1, 0),
+        "Replaced outliers?" = ifelse(cleaning == TRUE, 1, 0),
+        "FE: day of week" = ifelse(day_of_week_fe == TRUE, 1, 0),
+        "FE: month" = ifelse(month_fe == TRUE, 1, 0),
+        "FE: state" = ifelse(geograph_fe == TRUE, 1, 0),
+        # "Bandwidth = 30" = ifelse(bandwidth == 30, 1, 0),
+        "Bandwidth = 40" = ifelse(bandwidth == 40, 1, 0),
+        "Bandwidth = 50" = ifelse(bandwidth == 50, 1, 0),
+        "Bandwidth = 60" = ifelse(bandwidth == 60, 1, 0)
+
+        ) %>%
+
+      dplyr::select(model_number, estimate, disease, 'State level':'Bandwidth = 60') %>%
+      pivot_longer(cols = c('State level':'Bandwidth = 60'), 
+                   names_to = "spec_name", 
+                   values_to = "spec_status") %>%
+      mutate(spec_name = factor(spec_name, 
+                                levels = c("State level",
+                                           "County level",
+                                           "International level",
+                                           # "Daily data",
+                                           # "Weekly data",
+                                           "Replaced outliers?",
+                                           "FE: day of week",
+                                           "FE: month",
+                                           "FE: state",
+                                           # "Bandwidth = 30",
+                                           "Bandwidth = 40",
+                                           "Bandwidth = 50",
+                                           "Bandwidth = 60"))) %>%
+      mutate(spec_name = fct_rev(spec_name)) %>%
+
+      ggplot(aes(x = reorder(model_number, estimate), 
+                 y = spec_name, 
+                 fill = as.factor(spec_status))) +
+      geom_point(shape=22, size=1.25) +
+
+      scale_fill_manual(values = c(col_spec_no, col_spec_yes),
+                        name = "") +
+      guides(fill= "none") +
+      # scale_y_continuous(breaks = unique(control_grid_logit$y), 
+      #                    labels = unique(control_grid_logit$key),
+      #                    limits=c(min(control_grid_logit$y)-1, max(control_grid_logit$y)+1)) +
+      #scale_x_continuous(breaks=c(1:nrow(model_outputs_temp))) +
+      # coord_cartesian(xlim=c(1-min_space, nrow(model_outputs_temp)+min_space)) +
+      theme_classic() +
+      theme(panel.grid.major.y = element_blank(),
+            panel.grid.minor.y = element_blank(),
+            axis.text.x = element_blank(),
+            strip.text.x = element_blank(),
+            axis.title = element_blank(),
+            axis.text.y = element_text(size=10),
+            axis.ticks = element_blank(),
+            axis.line = element_blank(),
+            strip.text = element_text(size=12),
+            text = element_text(family = "Source Sans Pro"))+
+      facet_wrap(~disease, scales = "free_x")
+
+    combo_plot <- cowplot::plot_grid(coef_plot_a, 
+                       control_plot_a, 
+                       coef_plot_b, 
+                       control_plot_b, 
+                       rel_heights=c(1,0.5, 1,0.5), 
+                       align='v', ncol=1, axis='b')
+
+    ggsave(filename = paste0("sensitivity_analysis_all_international.jpg"),
+           plot = last_plot(),
+           path = resultspath,
+           width = 18,
+           height = 14)
+
+        print(combo_plot)
+
+```
+
+```{r fig_political, include = TRUE, echo=FALSE, warnings = FALSE,fig.scap="CITS effect estimates and confidence intervals symptom, region, and predominant political ideology.", out.extra='', fig.width = 10, fig.height = 5, fig.align='center', out.width = '95%',  fig.cap="\\label{fig_political}CITS effect estimates and confidence intervals symptom, region, and predominant political ideology, with panel A depicting the estimated slope change and panel B depicting the estimate level shift.
+The vertical panels show CITS effect estimates by three mental health symptoms (from left to right: anxiety, depression, and major depressive disorder); for each symptom, estimates are separately reported using county- and state-level data.
+For a given symptom and region, three CITS estimates are reported: one estimated from a sample of all counties or states (shown in purple), one conducted solely among the most Democratic counties or states (by 2020 presidential election vote share, shown in blue, and one among the most Republican counties or states (shown in red).
+Within each panel, the effect estimates across different models are depicted as points on a horizontal bar; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+The dotted horizontal line in each panel depicts a null effect.
+CITS: controlled interrupted time series.
+US: United States."}
+
+model_outputs_all_US %>%
+  function_model_main(levels = "include") %>%
+  filter(disease %in% mental_disorders) %>%
+  function_clean_diseases() %>%
+  mutate(geography = ifelse(geography == "state", "US states", "US counties")) %>%
+  mutate(polity = ifelse(polity == 1, "Red states/counties (top 20% most Republican", 
+                         ifelse(polity == 5, "Blue states/counties (top 20% most Democratic)", "All"))) %>%
+  mutate(polity = factor(polity, 
+                         levels = c("All", 
+                                    "Blue states/counties (top 20% most Democratic)",
+                                    "Red states/counties (top 20% most Republican"))) %>%
+  mutate(coefficient = ifelse(coefficient == "post:time:trt", "A: slope change",
+                              ifelse(coefficient == "post:trt", "B: level shift", "ERROR"))) %>%
+ ggplot(aes(x = reorder(model_number, estimate),
+                 y = (estimate),
+                 fill = polity,           
+                 color = polity)) +
+      geom_hline(yintercept=0, linetype='dotted') +
+      geom_crossbar(aes(ymin = (lower_99), 
+                        ymax = (upper_99)),
+                    fatten = 0,
+                    alpha = 0.2) +
+      geom_crossbar(aes(ymin = (lower_95),
+                        ymax = (upper_95)),
+                    fatten = 0,
+                    alpha = 0.3) +
+      geom_point(alpha = 1, size=1) +
+      theme_classic() +
+      theme(axis.text.x = element_blank(),
+            legend.position = "bottom",
+            axis.title = element_blank(),
+            axis.ticks.x = element_blank(),
+            strip.text = element_text(size=12),
+            text = element_text(family = "Source Sans Pro")) +
+  facet_grid( coefficient ~ disease + geography, scales = "free") +
+   scale_fill_manual(values = c(col_all, col_dem, col_red),
+                        name = "Political ideology")  +
+
+   scale_color_manual(values = c(col_all, col_dem, col_red),
+                        name = "Political ideology")
+
+rm(packages_and_paremeters_on)
+
+```
+
+\elandscape
+
+\newpage

### 2023-02-10 thesis.Rmd
Clean up of formatting and typesetting throughout.

@@
     number_sections: TRUE
+    # citation_package: natbib
+
+    # pandoc_args: ['--lua-filter=section-bibliographies.lua.txt']
+    # pandoc_args: ['--lua-filter=multibib.lua']
+
+reference-section-title: Works Cited
 
 geometry: margin=1in
-fontsize: 12pt
+fontsize: 11pt
 indent: true
 header-includes:
-  - \usepackage{float}
   - \usepackage{sectsty}
@@
   - \usepackage{fancyhdr}
-  - \usepackage{lastpage}
-  - \usepackage{dcolumn}
-  # - \usepackage{natbib}\bibliographystyle{agsm}
-  # - \usepackage[nottoc]{tocbibind}
+  - \usepackage[utf8]{inputenc}
+  - \usepackage[utf8]{lscape}
+  - \newcommand{\blandscape}{\begin{landscape}}
+  - \newcommand{\elandscape}{\end{landscape}}
+  - \usepackage[nottoc]{tocbibind}
+  # - \usepackage{float}
+  # - \usepackage{chapterbib}
+  # - \usepackage{lastpage}
+  # - \usepackage{dcolumn}
+  # - \usepackage[backend=biber,style=authoryear-icomp]{biblatex}
+  # - \addbibresource{bibliography.bib}
 
-bibliography: bibliography.bib
+bibliography: main.bib
+# natbiboptions: "numbers"
+csl: https://www.zotero.org/styles/the-lancet
+
+  # intro: intro.bib
+  # ch1: chapter1.bib
+  #
 
@@
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r setup0, include=FALSE}
+knitr::opts_chunk$set(warning = FALSE, message = FALSE, include = FALSE, echo = TRUE)
 
@@
 \subsubsectionfont{\raggedright}
+
 \pagenumbering{roman}
@@
 
-\vspace*{24pt}
+\vspace*{36pt}
 
@@
 
-\vspace{24pt}
+\vspace{36pt}
 
@@
 
-\vspace{36pt}
+\vspace{42pt}
 
 Harvard University \\
-Boston, Massachusetts
+Cambridge, Massachusetts
 
-\vspace{36pt}
+\vspace{42pt}
 
@@
 \end{centering}
-
-testsets
-
-etstestsetest . estsetset
-
-Lorem ipsum dolor sit amet, nunc pulvinar sapien et ligula ullamcorper malesuada proin.
-Faucibus a pellentesque sit amet porttitor eget.
-Quam adipiscing vitae proin sagittis nisl rhoncus.
-Quis blandit turpis cursus in hac habitasse platea dictumst.
-Feugiat vivamus at augue eget arcu.
-Duis convallis convallis tellus id interdum velit laoreet id donec.
-Ornare quam viverra orci sagittis eu volutpat odio.
-Netus et malesuada fames ac turpis egestas maecenas.
-Faucibus turpis in eu mi bibendum neque egestas.
-Sed velit dignissim sodales ut.
-Dolor sed viverra ipsum nunc aliquet bibendum enim facilisis gravida.
-
-Interdum varius sit amet mattis vulputate.
-Dui id ornare arcu odio ut sem nulla pharetra diam.
-Neque gravida in fermentum et sollicitudin ac orci.
-Nibh ipsum consequat nisl vel pretium lectus quam id leo.
-Mauris pellentesque pulvinar pellentesque habitant morbi tristique senectus et netus.
-Massa tempor nec feugiat nisl pretium fusce id velit ut.
-Vivamus at augue eget arcu dictum varius duis at consectetur.
-Odio ut enim blandit volutpat maecenas volutpat blandit aliquam etiam.
-Mauris ultrices eros in cursus.
-Tristique senectus et netus et malesuada.
 
@@
 
-Semper eget duis at tellus at urna condimentum.
-Viverra justo nec ultrices dui sapien eget.
-Etiam dignissim diam quis enim lobortis scelerisque fermentum dui.
-Sapien nec sagittis aliquam malesuada.
-Ac auctor augue mauris augue neque.
-Enim sed faucibus turpis in eu mi bibendum neque.
-Proin sagittis nisl rhoncus mattis rhoncus.
-Vel elit scelerisque mauris pellentesque pulvinar.
-Aliquam etiam erat velit scelerisque in dictum.
-Dictum varius duis at consectetur lorem donec massa sapien.
-Risus at ultrices mi tempus imperdiet nulla malesuada pellentesque.
-Faucibus purus in massa tempor nec feugiat nisl pretium fusce.
+Augue eget arcu dictum varius duis at.
+Tempor orci eu lobortis elementum nibh.
+Nibh sit amet commodo nulla.
+At varius vel pharetra vel.
+In metus vulputate eu scelerisque felis imperdiet.
+Venenatis tellus in metus vulputate eu.
+Aliquam sem fringilla ut morbi tincidunt augue.
+Risus feugiat in ante metus dictum at tempor commodo ullamcorper.
+In dictum non consectetur a erat nam.
+Ut sem viverra aliquet eget sit.
+Eleifend donec pretium vulputate sapien nec sagittis aliquam.
+Neque viverra justo nec ultrices dui.
+Turpis in eu mi bibendum neque egestas.
+Tellus rutrum tellus pellentesque eu tincidunt tortor aliquam nulla facilisi.
 
-Arcu odio ut sem nulla pharetra diam sit amet.
-Lorem ipsum dolor sit amet consectetur.
-Vitae aliquet nec ullamcorper sit amet risus nullam eget.
-Condimentum lacinia quis vel eros donec ac odio.
-Nulla posuere sollicitudin aliquam ultrices sagittis.
-Quis blandit turpis cursus in hac habitasse platea dictumst quisque.
-Amet risus nullam eget felis.
-Nec sagittis aliquam malesuada bibendum arcu vitae.
-In vitae turpis massa sed elementum tempus egestas sed sed.
-Netus et malesuada fames ac turpis egestas integer.
-Turpis tincidunt id aliquet risus feugiat.
-Lorem ipsum dolor sit amet consectetur adipiscing elit ut aliquam.
-Pretium vulputate sapien nec sagittis aliquam malesuada bibendum arcu vitae.
-Lectus nulla at volutpat diam ut venenatis tellus.
-
-\newpage
+\cleardoublepage
 
@@
 
-\newpage
+\cleardoublepage
 
@@
 
-\newpage
+\cleardoublepage
+
+```{r todo}
+
+### TO DO / KNOWN ISSUES
+
+# Separate bibliography for each section
+# Numbered figures and tables by section
+# Check that sequential articles are represented by a dash
+# Table of figures and tables
+# Acronyms with acronym down
+# Institutional authors need to be fixed in bibliography
+
+```

### 2023-02-10 paper1.Rmd
Revisions to table captions and page layouts.

@@
 
+\begin{spacing}{1}
+
 A version of this paper was accepted for publication by \emph{eClinicalMedicine} on September 9, 2022 and was published in Volume 54, Issue 101675 in December 2022.
+
+\end{spacing}
 
@@
 We then estimate the PAF of mortality due to mental disorders, using GBD prevalence estimates and relative risk estimates for natural-cause and unnatural-cause mortality generated from a systematic review and meta-analysis by Walker et al.[@walkerMortalityMentalDisorders2015] A comparison of our allocation approach with those of Vigo et al.
-and the original GBD hierarchical allocation is shown in Table 1.
+and the original GBD hierarchical allocation is shown in Table 1.1.
 
@@
 The PAF for a given disorder d and country c is given by:
-\[ PAF_{(d,c)}= \frac{p_{(d,c)}\ (RR_d-1)}{1+p_{(d,c)}\ (RR_d-1)}\ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (1)\]
+\[ PAF_{(d,c)}= \frac{p_{(d,c)}\ (RR_d-1)}{1+p_{(d,c)}\ (RR_d-1)}\ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (1.1)\]
 
@@
 \blandscape
-
 ```{r table1_2, echo = FALSE, include = TRUE, out.width = '100%'}
@@
 This is largely driven by the inclusion of premature mortality in the composite approach.
-Estimates of DALYs by country income group and GBD region are reported in Table 2.
+Estimates of DALYs by country income group and GBD region are reported in Table 1.2.
 (Estimates of deaths are reported in Table S4-6.)
 
-Under the three approaches, we calculated the economic value of mental disorder losses (Table 3).
+Under the three approaches, we calculated the economic value of mental disorder losses (Table 1.3).
 `r results_sentence2`.

### 2023-02-10 paper2.Rmd
Revisions to table captions and page layouts.

@@
 
-To generate the model combinations, we first detailed seven methodological choices and their potential specifications. These criteria are outlined in Table 1.
+To generate the model combinations, we first detailed seven methodological choices and their potential specifications. These criteria are outlined in Table 2.1.
+
+\vspace{12pt}
 
@@
 
-\addcontentsline{lot}{table}{Table 2.2: main analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
+\addcontentsline{lot}{table}{Table 2.2: Main analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
 
@@
 
-The regression models predicting monthly counts of any mental or neurological disorder (Table 2) showed significant associations with temperature across all models.
+The regression models predicting monthly counts of any mental or neurological disorder (Table 2.2) showed significant associations with temperature across all models.
 A one-degree Celsius increase in temperature was associated with approximately `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` cases reported `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)` by primary clinics and hospitals in Model 1.
@@
 
-\addcontentsline{lot}{table}{Table 2.3: subgroup analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
-
-Results from our subgroup analysis showed evidence of potential effect heterogeneity by ecoregion.
+\addcontentsline{lot}{table}{Table 2.3: Subgroup analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
+
+Results from our subgroup analysis showed evidence of potential effect heterogeneity by ecoregion (Table 2.3).
 For temperature, estimates of association were only statistically significant in the highland subhumid forests, where each one-degree Celsius increase in temperature was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = "only")` cases reported `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = TRUE)`.

### 2023-02-10 paper3.Rmd
Revisions to table captions and page layouts.

@@
 
-$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_i + \lambda_3 time_t*Post_i + $$
-$$ \alpha_d treated_{di} + \beta_d time_t*treated_{di} + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \epsilon_{it}$$
+\[ Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_i + \lambda_3 time_t*Post_i + 
+ \alpha_d treated_{di} + \beta_d time_t*treated_{di} + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)\]
+
 where $time_t$: is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$: is an indicator variable which equals 1 in the "post" period and 0 otherwise, and $treated_di$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches.

### 2023-02-22 appendix.Rmd
Addition of appendices, revisions throughout papers, acknowledgements

\subsection*{Appendix 1}

\addcontentsline{toc}{subsection}{Appendix 1}

```{r appendix_1, child='appendix_1.Rmd'}
```

\newpage

\subsection*{Appendix 2}

```{r library_appendix, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Loading libraries
# library(MASS) # We load this and then detach it just to clear the package
# library(margins) # We load this and then detach it just to clear the package
# library(lme4) # We load this and then detach it just to clear the package
# detach("package:lme4", unload=TRUE) # Needed to use dplyr's select function
# detach("package:margins", unload=TRUE) # Needed to use dplyr's select function
# detach("package:MASS", unload=TRUE) # Needed to use dplyr's select function
library(readxl)
library(readr)
library(dplyr)
library(zoo)
library(tidyr)
library(psych)
library(ggplot2)
library(RColorBrewer)
library(sp)
library(broom)
library(sf)
library(scales)
library(viridis)
library(data.table)
library(ggpubr)
library(ggmap)
library(maps)
library(mapdata)
library(ggrepel)
library(table1)
library(stringr) 
library(stringi)
library(fixest)
library(stats)
library(lubridate)
library(forecast)
library(gtools)
# library(devtools)
library(reticulate)
library(stargazer)
library(lwgeom)
if (!require("ggsflabel")) devtools::install_github("yutannihilation/ggsflabel")
library(openxlsx)
library(gganimate)
library(transformr)
library(huxtable)
library(ggtext)
library(margins)
library(ncdf4) # package for netcdf manipulation
library(magrittr)
library(lmtest)
library(sandwich)
library(rgee)
library(gt)
library(knitr)
library(webshot2)
library(sysfonts)
library(showtext)
font_add_google("Source Sans Pro")
library(gridExtra)
library(tibble)
showtext_auto() 
showtext_opts(dpi = 300)  
# library(googledrive)
# drive_auth(email = TRUE)
library(rmdHelpers)
library(gtExtras)
library(kableExtra)
library(DescTools)
library(rvest)
library(httr)
library(polite)
library(janitor)
library(cowplot)
library(ggridges)
# library(ggsn)

# library(glmmTMB)

# Setting directories - change these to your local directory
path <- 'C:/Users/danie/Dropbox (Harvard University)/madagascar_mh'
code <- paste(path,'code', sep = "/")
path_python  = "C:/Users/danie/AppData/Local/Programs/Python/Python310/python.exe"

# Data
datasource <- paste('C:/Users/danie/Dropbox (Harvard University)/data',
                    sep = "/") # The complete data set is not uploaded to 
# Github. Ask golden@hsph.harvard.edu for access. 
datapath <- paste(path,'data', sep = "/")
datapath_reference  <- paste(datapath,'0_reference', sep = "/")
data_mh_chd  <- paste(datapath,'1_mental_health', sep = "/")
data_mh_csb <- data_mh_chd  
data_mh_chu_chrr <- paste(data_mh_chd,'pathologies neuropsychiatriques CHU CHRR', sep = "/")
data_gps <- paste(datapath,'2_gps', sep = "/")
data_gps_sources <- paste(data_gps,'gps_sources', sep = "/")
data_gps_sources_searches <- paste(data_gps_sources,'searches', sep = "/")
data_gps_sources_reposit <- paste(data_gps_sources,'repositories', sep = "/")
data_climate_path  <- paste(datapath,'3_climate', sep = "/")
data_climate_era  <- paste(data_climate_path,'ERA5', sep = "/")
data_climate_esa  <- paste(data_climate_path,'ESA_CCI', sep = "/")

# Results
resultspath <- paste(path,'results', sep = "/")
mh_path <- paste(resultspath,'1_mental_health', sep = "/")
gpspath <- paste(resultspath,'2_gps', sep = "/")
gpspath_admin_names <- paste(gpspath,'0_reference', sep = "/")
gpspath_fig <-  paste(gpspath,'1_figures', sep = "/")
gpspath_spread <-  paste(gpspath,'2_spreadsheets', sep = "/")
gpspath_spread_fuzzy <-  paste(gpspath_spread,'3_fuzzy_matching', sep = "/")
analysispath <- paste(resultspath,'4_analysis', sep = "/")
analysis_figures <- paste(analysispath,'1_figures', sep = "/")
analysis_models <- paste(analysispath,'3_models', sep = "/")

# Shapefiles
mappath <- paste(path,'shapefiles', sep = "/")
mappath_MOH <- paste(mappath,'MOH', sep = "/")
mappath_OCHA <- paste(mappath,'OCHA', sep = "/")

# Color palette 
col_light = "cyan4"
col_dark = "cyan3"
col_bright = "coral"
col_black = "black"
col_grey_dark = "grey20"
col_grey_med = "grey40"
col_grey_light = "grey80"
col_grey_lightest = "grey85"
col_soilmoisture = col_dark
col_temperature = col_light
col_interaction = col_bright
col_cyclone = "steelblue2"

pal <- c("lightskyblue2", "steelblue2", "dodgerblue2", "dodgerblue3", "dodgerblue4", "darkblue")

col_within_threshold = "cyan3"
col_beyond_threshold = "coral"

col_centroid <- "grey20"
col_exact_all <- "cyan2"
col_exact_rhino <- "cyan3"
col_exact_val <- "cyan4"
col_search <- "coral"

col_CH <- "coral"
col_CHD <- "coral1"
col_CHR <- "coral3"
col_CSB <- "steelblue2"
col_CSB1 <- "steelblue1"
col_CSB2 <- "steelblue3"
col_other <-  "grey20"

col_model_main <- "#F3AB00"
col_model_other <- col_grey_med
col_spec_yes <-  "#73BDBF"
col_spec_no <-  "white"

col_cases <- "chartreuse3"
col_no_cases <- "deeppink3"

col_eco_rainforest <-"#32A42F"
col_eco_highlands <- "#B9CF19"
col_eco_arid <- "#FEEE19"
col_eco_drydecid <- "#FCAF3E"

# Thresholds
# These are cut off values that will be used in the GPS do file

length_lim <- 15  # The maximum distance allowed when the same facility has
# two GPS coordinates in the data sources for the center of
# those two coordinates to be used as the facility's location.
# Note: the selection of 15 is arbitrarily conservative. Spatial resolution of 
# climate data is typically ~ 30km x 30 km

area_lim <- length_lim*length_lim

# The maximum area of the convex hull allowed when the same facility has
# 3+ GPS coordinates in the data sources for the centroid of
# that convex hull to be used as the facility's location

fokontany_lim <- area_lim    # A small fokotanty is one that is ____ km ^2 or smaller

commune_lim <- area_lim    # A small commune is one that is ____ km ^2 or smaller

# Lags: specify how many lags you want for the explanatory variables (e.g., soil moisture, temp)

lags_number <- 18

# Climate data start and end date
start_date <- as.Date("2010-01-01")
end_date <- as.Date("2020-07-01")

start_date_climate <- start_date - lags_number*31 #This ensures there is data for the lagged exposure
end_date_climate <- end_date

# ESA CCI trim dates
date1 <- 200801
date2 <- 202112

# Seed and sampling fraction
set.seed(1960) # Madgascar's year of independence
sample_fraction = .01

######################
##      MAPS        ##
######################
#   
# # There are two map options available. One set of shapefiles were available
# # from humdata.org, while the other set was provided by the MOH.
#   
# # Loading high-resolution maps of St. Lucia (from data.humdata.org)
map_mdg_0_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm0_BNGRC_OCHA_20181031.shp"))
map_mdg_1_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm1_BNGRC_OCHA_20181031.shp"))
map_mdg_2_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm2_BNGRC_OCHA_20181031.shp"))
map_mdg_3_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm3_BNGRC_OCHA_20181031.shp"))
loaded_maps_un <- 1

# Load in data from MOH
map_mdg_0 <- st_read(paste0(mappath_MOH,"/",
                            "adm0_mada_utm38S.shp"))
map_mdg_1 <- st_read(paste0(mappath_MOH,"/",
                            "adm1_mada_utm38S.shp"))
map_mdg_2 <- st_read(paste0(mappath_MOH,"/",
                            "adm2_mada_utm38S.shp"))
map_mdg_3 <- st_read(paste0(mappath_MOH,"/",
                            "adm3_mada_utm38S.shp"))
map_mdg_4 <- st_read(paste0(mappath_MOH,"/",
                            "adm4_mada_utm38S.shp"))

```

\addcontentsline{toc}{subsection}{Appendix 2}

\subsubsection*{Appendix 2.1: Health system data cleaning}

\addcontentsline{toc}{subsubsection}{Appendix 2.1}

```{r appendix_2, child='appendix_2.1.Rmd'}
```
\newpage

\subsubsection*{Appendix 2.2: Health facility geocoding and validation}

\addcontentsline{toc}{subsubsection}{Appendix 2.2}

```{r appendix_3, child='appendix_2.2.Rmd'}
```

\newpage

### 2023-02-22 appendix_1.Rmd
Addition of appendices, revisions throughout papers, acknowledgements

---
title: ""
subtitle: ""
---

\begin{centering}

\addcontentsline{lot}{table}{Table S1.1: The global economic burden of mental disorders, by year and approach, calculated by Bloom and colleagues and adjusted to 2019 USD using gross domestic product deflator adjustment. Estimates are in trillions.}

```{r table_s_1_1, echo = FALSE, include = TRUE, out.width = '100%'}

knitr::include_graphics("table_s_1_1.png")

```

\newpage

\addcontentsline{lot}{table}{Table S1.2: The economic value of mental disorder losses, using VSL approach, by year and monetary value assigned to one DALY. Authors’ calculations based on Bloom and colleagues and adjusted to 2019 USD using gross domestic product deflator adjustment. Estimates are in trillions.}

```{r table_s_1_2, echo = FALSE, include = TRUE, out.width = '100%'}

knitr::include_graphics("table_s_1_2.png")

```

\newpage

\addcontentsline{lot}{table}{Table S1.3: Hierarchical classification of mental disorders in the Global Burden of Disease (GBD) 2019 study.}

```{r table_s_1_3, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_1_3.png")

```
\blandscape

\addcontentsline{lot}{table}{Table S1.4: Years lived with disability (YLDs) attributable to mental disorders as totals (millions) and percentages of overall burden, by World Bank income group classification and GBD region, under three estimation approaches.}

```{r table_s_1_4, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_1_4.png")

```

\newpage

\addcontentsline{lot}{table}{Table S1.5: Years of life lost (YLLs) attributable to mental disorders as totals (millions) and percentages of overall burden, by World Bank income group classification and GBD region, under three estimation approaches.}

```{r table_s_1_5, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_1_5.png")

```

\newpage

\addcontentsline{lot}{table}{Table S1.6: Deaths attributable to mental disorders as totals (millions) and percentages of overall burden, by World Bank income classification and GBD region, under three estimation approaches.}

```{r table_s_1_6, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_1_6.png")

```

\elandscape

\newpage

\addcontentsline{lot}{table}{Table S1.7: The global economic burden associated with premature mortality and morbidity from mental disorders, by estimation approach and value per DALY, using alternative valuations.}

```{r table_s_1_7, echo = FALSE, include = TRUE, out.width = '100%'}

knitr::include_graphics("table_s_1_7.png")

```
\newpage

\blandscape

\addcontentsline{lot}{table}{Table S1.8: The economic burden associated with premature mortality and morbidity from mental disorders, by estimation approach and value per DALY, using alternative valuations and by World Bank income classification and GBD region.}

```{r table_s_1_8, echo = FALSE, include = TRUE, out.height = '97%'}

knitr::include_graphics("table_s_1_8a.png")
knitr::include_graphics("table_s_1_8b.png")
knitr::include_graphics("table_s_1_8c.png")
knitr::include_graphics("table_s_1_8d.png")
knitr::include_graphics("table_s_1_8e.png")
knitr::include_graphics("table_s_1_8f.png")

```

\elandscape

\end{centering}

### 2023-02-22 appendix_2.1.Rmd
Addition of appendices, revisions throughout papers, acknowledgements

---
title: ""
subtitle: ""
---

```{r parameters-and-data_s2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

## Saving start time (to help time the code)
start <- proc.time()
start <- as.numeric(start["elapsed"])

csb_10to15 <- read.csv(paste(data_mh_csb, 'Affections mentales et troubles psychiques GESIS CSB 2010-2015.csv',
                             sep = "/"), 
                       header=TRUE) %>%
  mutate(across(.cols=where(is.integer), .fns=as.numeric)) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  rename(year = cAnnee,
         month = Periode,
         region = Region,
         district = District,
         commune = commune,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days' = X0.à.28j,
         '29-days-to-11-months' = X29j.à.11.m,
         '1-to-4-years' = X1.à.4.ans,
         '5-to-14-years' = X5.à.14.ans,
         '15-to-24-years' = X15.à.24.ans,
         '25-years-plus' = X25.et.plus,
         total = total,     
         referalls = Référés) %>%
  mutate(sex = "both",
         year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  pivot_longer(cols = '0-to-28-days':referalls, names_to = "subgroup", values_to = "count")

csb_15to16 <- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2015-2016.csv',
                             sep = "/"), 
                       header=TRUE)

csb_17<- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2017.csv',
                             sep = "/"), 
                       header=TRUE)

csb_18 <- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2018.csv',
                         sep = "/"), 
                   header=TRUE)

csb_19 <- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2019.csv',
                         sep = "/"), 
                   header=TRUE)

csb_15to19 <- rbind(csb_15to16,csb_17, csb_18, csb_19) %>%
  mutate(across(.cols=where(is.integer), .fns=as.numeric)) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  mutate(total_male = X0.à.28j_Masculin + 
           X29j.à.11.m_Masculin + 
           X1.à.4.ans_Masculin + 
           X5.à.14.ans_Masculin + 
           X15.à.24.ans_Masculin +
           X25.à.59.ans_Masculin +
           X60.ans.et.plus_Masculin,

         total_female = X0.à.28j_Feminin + 
           X29j.à.11.m_Feminin + 
           X1.à.4.ans_Feminin + 
           X5.à.14.ans_Feminin + 
           X15.à.24.ans_Feminin +
           X25.à.59.ans_Feminin +
           X60.ans.et.plus_Feminin) %>%

  rename(year = cAnnee,
         month = Periode,
         region = Region,
         district = District,
         commune = Commune,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days_male' =  X0.à.28j_Masculin,
         '0-to-28-days_female' =  X0.à.28j_Feminin,  
         '29-days-to-11-months_male' = X29j.à.11.m_Masculin,
         '29-days-to-11-months_female' = X29j.à.11.m_Feminin,
         '1-to-4-years_male' = X1.à.4.ans_Masculin,
         '1-to-4-years_female' = X1.à.4.ans_Feminin,
         '5-to-14-years_male' = X5.à.14.ans_Masculin,
         '5-to-14-years_female' = X5.à.14.ans_Feminin,
         '15-to-24-years_male' =X15.à.24.ans_Masculin,
         '15-to-24-years_female' = X15.à.24.ans_Feminin,
         '25-to-59-years_male' = X25.à.59.ans_Masculin,
         '25-to-59-years_female' = X25.à.59.ans_Feminin,
         '60-years-plus_male' = X60.ans.et.plus_Masculin,
         '60-years-plus_female' = X60.ans.et.plus_Feminin,
         referalls_male = Référés_Masculin,
         referalls_female = Référés__Feminin) %>% 
  mutate(year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  pivot_longer(cols = '0-to-28-days_male':total_female,
               names_to = c("subgroup","sex"), 
               names_sep = "_",
               values_to = "count") %>%
  group_by(date, clinic_name, disease, subgroup) %>%
  mutate(both = sum(count)) %>%
  pivot_wider(names_from = sex, values_from = count) %>%
  pivot_longer(cols = c(both, male, female),
               names_to = "sex",
               values_to = "count") %>%
  ungroup()

csb_data <- rbind(csb_10to15, csb_15to19)
rm(csb_10to15, csb_15to19, csb_15to16,csb_17, csb_18, csb_19)

## CHD 
chd_data <- read.csv(paste(data_mh_chd, 'Maladies neuro-psychiques CHD.csv',
                             sep = "/"), 
                       header=TRUE) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  mutate(total = X0.à.28j +
           X29j.à.11.m +
           X1.à.4.ans +
           X5.à.14.ans +
           X15.à.24.ans +
           X25.et.plus,
         commune = "NA") %>%
  rename(year = cAnnee,
         month = Periode,
         region = Region,
         district = District,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days' = X0.à.28j,
         '29-days-to-11-months' = X29j.à.11.m,
         '1-to-4-years' = X1.à.4.ans,
         '5-to-14-years' = X5.à.14.ans,
         '15-to-24-years' = X15.à.24.ans,
         '25-years-plus' = X25.et.plus,
         referalls = Référés) %>%
  mutate(sex = "both",
         year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  relocate(commune, .after = district) %>%
  pivot_longer(cols = '0-to-28-days':total, names_to = "subgroup", values_to = "count")

## CHU and CHRR

chu_files <- as.vector(list.files(data_mh_chu_chrr))
chu_data <- data.frame(matrix(ncol = 12, nrow = 0))

for (x in chu_files) {

chu_data_r <- read.csv(paste(data_mh_chu_chrr, x,
                           sep = "/"), 
                     header=TRUE)

chu_data <- rbind(chu_data, chu_data_r)

rm(chu_data_r)

}
chu_data <- chu_data %>%
  mutate(across(.cols=where(is.integer), .fns=as.numeric)) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  mutate(district = "NA",
         commune = "NA") %>%
  rename(year = cAnnee,
         month = Periode,
         region = Region,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days' = X0.à.28j,
         '29-days-to-11-months' = X29j.à.11.m,
         '1-to-4-years' = X1.à.4.ans,
         '5-to-14-years' = X5.à.14.ans,
         '15-to-24-years' = X15.à.24.ans,
         '25-years-plus' = X25.et.plus,
         total = total) %>%
  mutate(sex = "both",
         year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  relocate(district, .after = region) %>%
  relocate(commune, .after = district) %>%
  pivot_longer(cols = '0-to-28-days':total, names_to = "subgroup", values_to = "count")

data_mh <- rbind(csb_data, chd_data, chu_data) %>% ## Join all data
  mutate(region = str_to_title(region), ## Capitalizing region names
         clinic_name = str_squish(clinic_name))

mh_english_disease <- read_excel(
  paste(datapath_reference, "disease_names_crosswalk.xlsx", sep = "/"))

```

\paragraph*{Overview of health system data}

\addcontentsline{toc}{paragraph}{Overview of health system data}

The health facility data used in our study was obtained from Madagascar's *Gestion du Système d'Information Sanitaire* (GESIS), a Microsoft Access electronic health management information systems database.

While primary, district-level, and regional referral facilities in Madagascar all report monthly case counts of mental disorders in GESIS, case definitions vary across facilities of different levels. Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) are only reported among regional referral hospitals and university hospitals; for all other facilities, cases are reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).

Disaggregated data is available by age; among adults, however, disaggregated data for adults ages 25 to 59 and adults 60 years and older has only been reported by primary health facilities since 2015. For all other years and all other facilities, these age categories are not separately reported. Similarly, data by sex is only reported for primary health facilities since 2015. Referrals are reported by primary health facilities and district hospitals.

A summary of the GESIS data availability is provided in Table S2.1.

\begin{raggedright}

\addcontentsline{lot}{table}{Table S2.1: Availability of disaggregated health system data by year and level of care.}

```{r table_s_2_1, echo = FALSE, include = TRUE, out.width = '100%'}

knitr::include_graphics("table_s_2_1.png")

```
\end{raggedright}

\vspace{24 pt}

After compiling the GESIS data, we translated the case definitions from French to English. The translations are provided in Table S2.2.

\begin{spacing}{1}

\addcontentsline{lot}{table}{Table S2.2: Mental health disorders reported in GESIS, in French and English.}

```{r  table_s_2_2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

mh_english_disease %>% unique() %>%
  arrange(disease) %>%
  relocate(disease, .before=disease_english) %>%
    mutate(disease = gsub(" and ", " & ", disease),
           disease =  StrTrunc(disease, maxlen = 40, ellipsis = "...", wbound = TRUE),
           disease_english = gsub(" and ", " & ", disease_english),
   disease_english = case_when(
       str_detect(disease_english, "Bouffées délirantes aiguës") ~
                   "Short-lived psychosis",
   TRUE ~ disease_english),
      disease_english = gsub("of diseases classified elsewhere", "(d.c.e.)", disease_english),
      disease_english = gsub("in diseases classified elsewhere", "(d.c.e.)", disease_english),
   disease_english = gsub(" nervous system", " N.S.", disease_english)) %>%
  rename(English = disease_english, French = disease) %>%
  gt() %>%
  tab_footnote(
    footnote = "d.c.e.: in or among diseases classified elsewhere. N.S.: nervous system",
    locations = cells_column_labels(
      columns = English
    )
  ) %>%
  tab_style(locations = cells_column_labels(),
            style     = list(cell_text(weight = "bold", size = 9))) %>%
    tab_header(
    title ="Table S2.2: Mental health disorders reported in GESIS, in French and English")

```

```{r  function_table_s2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

reporting_table <- function(data, title_option){

data %>% filter(sex == "both" & subgroup == "total") %>% 
    group_by(disease, year) %>%
    # mutate(count = sum(count)) %>% 
    # filter(count != 0 & count != 14 & count != 7 & count != 21 & count != 28 & count != 35 & count != 42  & count != 49  & count != 56  & count != 63  & count != 70) %>% 
    # ungroup() %>%
    # select(clinic_name, disease, year, ) %>%
    # unique() %>%
    # mutate(n = 1) %>% 
    # group_by(year, disease) %>%  
    mutate(sum = sum(count)) %>%  
    select(sum, year, disease) %>% 
    ungroup() %>%
    unique() %>% 
  left_join(mh_english_disease, by = "disease") %>%
  mutate(disease = paste0(disease_english, " (", 
                          StrTrunc(disease, maxlen = 25, ellipsis = "...", wbound = TRUE),")")) %>%
      select(year, disease, sum) %>%
    rename(Year = year, Total = sum) %>%
  mutate(disease = gsub(" and ", " & ", disease),
         disease = case_when(

             str_detect(disease, "Bouffées délirantes aiguës") ~
                         "Short-lived psychosis (Bouffées délirantes aiguës)",
   TRUE ~ disease)) %>%

  rename(Disease = disease) %>%
  arrange(Year, Disease) %>%
  pivot_wider(names_from = Year, values_from = Total) %>%
  gt(groupname_col = "Disease") %>%
    tab_style(locations = cells_column_labels(),
            style     = list(cell_text(weight = "bold", size = 9))) %>%
    tab_header(
    title = title_option) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  fmt(
    rows = everything(),
    fns = function(x) ifelse(is.na(x), "—", prettyNum(x, big.mark = ",")))
}

n_chu <- chu_data %>% select(disease) %>% unique() %>% nrow

```

\end{spacing}

\vspace{24 pt}

We then conducted exploratory data analysis to gauge data availability by condition, year, and facility level, which are reported in Tables S2.3-5. These tables show yearly cumulative cases of mental and neurological disorders, by facility level.

Among primary health facilities, we observed that the case definition for mental disorders changed during 2015, alongside the changes in GESIS that enabled disaggregated reporting by sex and greater disaggregation for data by age.

Among district hospitals, reporting of mental disorders has been consistent between 2010 and 2020.

Reporting of mental disorders is most detailed among regional referral hospitals (CHRRs) and university hospitals (CHUs), with case counts reported for `r  prettyNum(n_chu, big.mark = ",", scientific = FALSE)` unique conditions.

\newpage

\begin{spacing}{1}

\addcontentsline{lot}{table}{Table S2.3: Yearly cumulative cases of mental and neurological disorders reported at primary facilities.}

```{r  reporting_tables1a, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

reporting_table(csb_data, "Table S2.3: Yearly cumulative cases of mental and neurological disorders reported at primary facilities")

```

\addcontentsline{lot}{table}{Table S2.4: Yearly cumulative cases of mental and neurological disorders reported at district hospitals.}

```{r  reporting_tables1b, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

reporting_table(chd_data, "Table S2.4: Yearly cumulative cases of mental and neurological disorders reported at district hospitals")

```

\newpage

\addcontentsline{lot}{table}{Table S2.5: Yearly cumulative cases of mental and neurological disorders reported at regional hospitals.}

```{r  reporting_tables2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

reporting_table(chu_data, "Table S2.5: Yearly cumulative cases of mental and neurological disorders reported at regional hospitals")

```

\end{spacing}

```{r  adding_english_disease_names, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

data_mh <- data_mh %>%

  ## Add English translations for diseases, drop French disease names
  left_join(., mh_english_disease, by = "disease") %>%
  select(!c(disease)) %>%
  rename(disease = disease_english) %>%
  relocate(disease, .after = clinic_name) %>%

  ## Ensure that the remaining rows are unique
  unique()

```

```{r  functions_for_disease_names_and_cleaning, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

capwords <- function(s, strict = FALSE) {
  cap <- function(s) paste(toupper(substring(s, 1, 1)),
                           {s <- substring(s, 2); if(strict) tolower(s) else s},
                           sep = "", collapse = " " )
  sapply(strsplit(s, split = " "), cap, USE.NAMES = !is.null(names(s)))
}

clean_clinic_type <- function(data){
  data %>%
    mutate(clinic_type = case_when(
      str_detect(clinic_name, "CBS1") ~ "CSB1",
      str_detect(clinic_name, "Centre de santé de base 2 ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base de Deuxième Niveau ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base de Niveau 2 ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base de niveau II ") ~ "CSB2",
      str_detect(clinic_name, "Centre De Santé De Base De Niveau II") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base I ") ~ "CSB1",
      str_detect(clinic_name, "Centre de Santé de Base II ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base Niveau 1 ") ~ "CSB1",
      str_detect(clinic_name, "Centre de Santé de Base Niveau 2 ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base Niveau I ")~ "CSB1",
      str_detect(clinic_name, "Centre de Santé de Base Niveau II")~ "CSB2",
      str_detect(clinic_name, "Centre du Santé de Base I ") ~ "CSB1",
      str_detect(clinic_name, "Centre Hospitalier de District ") ~ "CHD",
      str_detect(clinic_name, "Centre Hospitalier De Référence De District ") ~ "CHD",
      str_detect(clinic_name, "Centre Hospitalier de Référence Régional ") ~ "CHRR",
      str_detect(clinic_name, "Centre Hospitalier de Référence Régional de ") ~ "CHRR",
      str_detect(clinic_name, "Centre Hospitalier Régional De Référence ") ~ "CHRR",
      str_detect(clinic_name, "Centre Hosptalier de Référence du District du ") ~ "CHD",
      str_detect(clinic_name, "Centre sante de base niveau II ") ~ "CSB2",
      str_detect(clinic_name, "CHD 1") ~ "CHD1",
      str_detect(clinic_name, "CHD 2") ~ "CHD2",
      str_detect(clinic_name, "CHD1") ~ "CHD1",
      str_detect(clinic_name, "CHD2") ~ "CHD2",
      str_detect(clinic_name, "CHRD 1") ~ "CHD1",
      str_detect(clinic_name, "CHRD 2") ~ "CHD2",
      str_detect(clinic_name, "CHRD II ") ~ "CHD2",
      str_detect(clinic_name, "CHRD1") ~ "CHD1",
      str_detect(clinic_name, "CHRD2 ") ~ "CHD2",
      str_detect(clinic_name, "CHRD2") ~ "CHD2",
      str_detect(clinic_name, "CHRR ") ~ "CHRR",
      str_detect(clinic_name, "CHRR II ") ~ "CHRR",
      str_detect(clinic_name, "CHU ") ~ "CHU",
      str_detect(clinic_name, "Csb 1 ") ~ "CSB1",
      str_detect(clinic_name, "CSB 1") ~ "CSB1",
      str_detect(clinic_name, "CSB 2") ~ "CSB2",
      str_detect(clinic_name, "CSB I ")~ "CSB1",
      str_detect(clinic_name, "CSB II")~ "CSB2",
      str_detect(clinic_name, "Csb1") ~ "CSB1",
      str_detect(clinic_name, "CSB1") ~ "CSB1",
      str_detect(clinic_name, "CSB2") ~ "CSB2",

      str_detect(clinic_name, "depot de medicament") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôt de médicaments ") ~ "Pharmacy",
      str_detect(clinic_name, "Dépot de médicaments") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôt de médicaments") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôtde médicament ") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôts de médicaments") ~ "Pharmacy",
      str_detect(clinic_name, "Dispensaire") ~ "Pharmacy",
      str_detect(clinic_name, "Docteur ") ~ "FSP",
      str_detect(clinic_name, "Dokotera ") ~ "FSP",
      str_detect(clinic_name, "Dr ") ~ "FSP",
      str_detect(clinic_name, "Fivarotampanafody ") ~ "Pharmacy",
      str_detect(clinic_name, "Fivarotam-panafody ") ~ "Pharmacy",
      str_detect(clinic_name, "FSP") ~ "FSP",
      str_detect(clinic_name, "HP ") ~ "HP",
      str_detect(clinic_name, "pharmacie de ") ~ "Pharmacy",
      str_detect(clinic_name, "Pharmacie") ~ "Pharmacy",
      str_detect(clinic_name, "Pharmacrie") ~ "Pharmacy",
      str_detect(clinic_name, "Pharmacy") ~ "Pharmacy",
      str_detect(clinic_name, "Pavillon Sainte Fleur") ~ "CHU", #https://maternitesaintefleur.wordpress.com/
      TRUE ~ "Other/Unknown")) %>%

    mutate(clinic_type = case_when(
          and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "Centre de santé de base")) ~ "CSB",
                  and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "Centre De Santé ")) ~ "CSB",
                  and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "Centre De Santé De Base ")) ~ "CSB",
                  and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "CSB")) ~ "CSB",
     TRUE ~ clinic_type))

}

clean_clinic_name <- function(data){
  data %>%
    mutate(clinic_name_clean = clinic_name) %>%
    mutate(clinic_name_clean = gsub("CBS1", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Rééducation Motrice De Madagascar Antsirabe", "Centre De Rééducation Motrice Antsirabe", clinic_name_clean),
           clinic_name_clean = gsub("Centre de santé de base 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de Deuxième Niveau ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de Niveau 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de niveau II ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de Niveau II ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Santé De Base De Niveau II", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base I ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base II ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau 1 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau I ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau II", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de santé de base", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre du Santé de Base I ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Santé ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de santé ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Santé De Base ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de District ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier De Référence De District ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de Référence de District ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de Référence Régional ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de Référence Régional de ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier De Référence Régional De ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier Régional De Référence ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier Régional de Référence ", "", clinic_name_clean),  
           clinic_name_clean = gsub("Centre Hosptalier de Référence du District du ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre sante de base niveau II ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD 1", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD 2", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD1", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD2", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD2", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRR", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRR II", "", clinic_name_clean),
           clinic_name_clean = gsub("CHU ", "", clinic_name_clean),
           clinic_name_clean = gsub("Csb 1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB 1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB 2", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB I ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD II ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB II", "", clinic_name_clean),
           clinic_name_clean = gsub("Csb1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB2", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBU ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB ", "", clinic_name_clean),
           clinic_name_clean = gsub("csb ", "", clinic_name_clean),
           clinic_name_clean = gsub("FSP_", "", clinic_name_clean),
           clinic_name_clean = gsub("FSP_", "", clinic_name_clean),
           clinic_name_clean = gsub("FSP ", "", clinic_name_clean),
           clinic_name_clean = gsub("Pharmacie", "", clinic_name_clean),
           clinic_name_clean = gsub("pharmacie de ", "", clinic_name_clean),
           clinic_name_clean = gsub("Pharmacy", "", clinic_name_clean),
           clinic_name_clean = gsub("Pharmacrie", "", clinic_name_clean),
           clinic_name_clean = gsub("PHARMACIE", "", clinic_name_clean),
           clinic_name_clean = gsub("Dispensaire", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt  de médicament ", "", clinic_name_clean),
           clinic_name_clean = gsub("depot de medicament", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Fivarotam-panafody", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépot de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépot de Médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôts de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôts de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Docteur ", "", clinic_name_clean),
           clinic_name_clean = gsub("Dokotera ", "", clinic_name_clean),
           clinic_name_clean = gsub("Dr ", "", clinic_name_clean),
           clinic_name_clean = gsub("Fivarotam-Panafody", "", clinic_name_clean),
           clinic_name_clean = gsub("Fivarotampanafody ", "", clinic_name_clean),
           clinic_name_clean = gsub("HP HP", "", clinic_name_clean),
           clinic_name_clean = gsub("HP", "", clinic_name_clean),
           clinic_name_clean = gsub("Polyclinique", "", clinic_name_clean),
           clinic_name_clean = gsub("Clinique ", "", clinic_name_clean),
           clinic_name_clean = gsub("CH ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBD ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBU", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBD ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBDS ", "", clinic_name_clean),
           clinic_name_clean = gsub("Medico Chirurgicale ", "", clinic_name_clean),
           clinic_name_clean = gsub("CMC ", "", clinic_name_clean),
           clinic_name_clean = gsub("Loterana", "Luthérien", clinic_name_clean),
           clinic_name_clean = gsub("Saint Luc Toliara I", "Saint Luc", clinic_name_clean),
           clinic_name_clean = gsub(" Hospital", "", clinic_name_clean),
           clinic_name_clean = gsub("Hôpital", "", clinic_name_clean),
           clinic_name_clean = gsub("Hopitaly ", "", clinic_name_clean),
           clinic_name_clean = gsub("Hopital ", "", clinic_name_clean),
           clinic_name_clean = gsub(" Health Centre", "", clinic_name_clean),
           clinic_name_clean = gsub(" Health Post", "", clinic_name_clean),

           ## Finally, we replace hypens and underscores with spaces in the 
           ## clinic and district names. We also remove double spaces in 
           #between words, and remove leading and trailing whitespace

           clinic_name_clean = gsub("-", " ", clinic_name_clean),
           clinic_name_clean = gsub("_", " ", clinic_name_clean),
           clinic_name_clean = gsub("  ", " ", clinic_name_clean),
           clinic_name_clean = trimws(clinic_name_clean),
           clinic_name_clean = capwords(clinic_name_clean)) %>%

    filter(clinic_name_clean != "")
}

clean_catchment_area <- function(data){

  data %>% 
    mutate(
      region_name = gsub("NA", NA, region_name),
      district_name = gsub("NA", NA, district_name),
      commune_name = gsub("NA", NA, commune_name)
    ) %>%

    mutate(
      clinic_type = ifelse(
        is.na(district_name) &
          is.na(commune_name) &
          clinic_type != "CHRR" &
          clinic_type != "CHU",
        "CHRR/CHU",
        ifelse(
          !is.na(district_name) &
            is.na(commune_name) &
            clinic_type != "CHD1" &
            clinic_type != "CHD2",
          "CHD",
          clinic_type
        )
      )
    ) %>%

    mutate(clinic_type_clean = ifelse(
      and(is.na(district_name) | district_name =="",
          is.na(commune_name) | commune_name ==""),

      ## If the facility's catchment area is a
      ## region only, assign it as a cHR or CHU

      "CHR/CHU",

      ## If the facility's catchment area is a district
      ## only, assign it as a CHD (no level specified)

      ifelse(is.na(commune_name) | commune_name =="",
             "CHD",

             ## If the facility's catchment area is
             ## a commune, assign it as a CSB or FSP
             ## (no level specified)

             "CSB/FSP")
    )) %>%

    mutate(region_name = case_when(
      str_detect(region_name, "Amoron'i Mania") ~ "Amoron I Mania",
      TRUE ~ region_name
    )) %>%

    mutate(
      district_name = case_when(
        str_detect(district_name, "Anosibe An'Ala") ~ "Anosibe-An'ala",
        str_detect(district_name, "Antananarivo Atsimon") ~ "Antananarivo Atsimondrano",
        str_detect(district_name, "Antananarivo Avaradr") ~ "Antananarivo Avaradrano",
        str_detect(district_name, "Antananarivo Renivoh") ~ "Antananarivo Renivohitra",
        str_detect(district_name, "Fenoarivo Atsinanana") ~ "Fenerive Est",
        str_detect(district_name, "Mananara Avaratra") ~ "Mananara-Avaratra",
        str_detect(district_name, "Nosy Boraha") ~ "Sainte Marie",
        str_detect(district_name, "Ambovombe Androy") ~ "Ambovombe-Androy",
        str_detect(district_name, "Tsiombe") ~ "Tsihombe",
        str_detect(district_name, "Amboasary Atsimo") ~ "Amboasary-Atsimo",
        str_detect(district_name, "Ankazoabo Atsimo") ~ "Ankazoabo",
        str_detect(district_name, "Toliara I") ~ "Toliary-I",
        str_detect(district_name, "Toliara II") ~ "Toliary-II",
        str_detect(district_name, "Toliara-I") ~ "Toliary-I",
        str_detect(district_name, "Toliara-II") ~ "Toliary-II",
        str_detect(district_name, "Midongy Atsimo") ~ "Midongy-Atsimo",
        str_detect(district_name, "Antanambao Manampont") ~ "Antanambao Manampontsy",
        str_detect(district_name, "Antanambao Manampotsy") ~ "Antanambao Manampontsy",
        str_detect(district_name, "Vohibinany") ~ "Brickaville",
        str_detect(district_name, "Ambatoboeny") ~ "Ambato Boeni",
        str_detect(district_name, "FenoarivoBe") ~ "Fenoarivobe",
        str_detect(district_name, "Nosy Be") ~ "Nosy-Be",
        str_detect(district_name, "Fianarantsoa II") ~ "Fianarantsoa I",
        str_detect(district_name, "lalangina") ~ "Lalangina",
        str_detect(district_name, "Belo Tsiribihina") ~ "Belo Sur Tsiribihina",
        str_detect(district_name, "Vohimarina") ~ "Vohemar",
        str_detect(district_name, "Befandriana Avaratra") ~ "Befandriana Nord",
        str_detect(district_name, "Boriziny") ~ "Port-Berge (Boriziny-Vaovao)",
        str_detect(district_name, "Nosy Varika") ~ "Nosy-Varika",
        TRUE ~ district_name
      )
    ) %>%

    ## A number of communes in the districts of Fianarantsoa and Toliara
    ## have been reclassifed under new district named (e., Lalangina), requiring
    ## that the district names for these communes be manually updated.

    mutate(
      district_name = ifelse(
        commune_name == "Alakamisy Ambohimahy" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Alakamisy Itenina" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambalakely" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambalamahasoa" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambalamidera" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambohimahavelona" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambolofoty" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Anakao" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Analamisampy" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andianjanto Est" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andoharanomaintso" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andrainjanto Centre" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranohinaly" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranomiditra" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranovorivato" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranovory" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andribavontsona" &
          district_name == "Port-Berge (Boriziny-Vaovao),",
        "Analalava",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Androy" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Anjoma-tsara" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankarinarivo" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankaromalaza Mifanas" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankililoaka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankilimalinika" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Antanamalaza" &
          district_name == "Antsirabe II",
        "Ambatolampy",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Antanambao Ambary" &
          district_name == "Betafo",
        "Mandoto",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Antsahavaribe" &
          district_name == "Vohemar",
        "Sambava",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Beheloka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Behompy" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Belalanda" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Betsinjaka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Fandravandava" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Fanjakana" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ialananidro" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Iavinomby" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ihazoara" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Isorana" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ivoamba" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahaditra" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahasoabe" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahatsinjo" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahatsinjony" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Maneva" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Manombo" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Manorofify" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "MarofotyMarofoty" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Maromiandra" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Miary" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Milenaka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mitsinjo" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Nasandratrony" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Sahambavy" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Soaindrana" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Soalara" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Soatanana" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "St Augustin" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Taindambo" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Talata Ampano" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Tsianisiha" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Vohibato Ouest" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Vohimarina" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Vohitrafeno" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      )
    ) %>%

    mutate(
      commune_name = case_when(
        str_detect(commune_name, "Alakamisy Ambohimahy") ~ "Alakamisy Ambohimaha",
        str_detect(commune_name, "Alakamisy Itenina") ~ "Alakamisy Itenina",
        str_detect(commune_name, "Ambadrika") ~ "Ambandrika",
        str_detect(commune_name, "Ambalakely") ~ "Ambalakely",
        str_detect(commune_name, "Ambalamahasoa") ~ "Ambalamahasoa",
        str_detect(commune_name, "Ambalamanasy   II") ~ "Ambalamanasy II",
        str_detect(commune_name, "Ambalamidera") ~ "Ambalamidera II",
        str_detect(commune_name, "AmbalapaisoII") ~ "Ambalapaiso II",
        str_detect(commune_name, "Ambararatabe /Nord") ~ "Ambararatabe Nord",
        str_detect(commune_name, "Ambarijeby Atsimo") ~ "Ambarijeby Sud",
        str_detect(commune_name, "Ambatoben'anja") ~ "Ambatoben'anjavy",
        str_detect(commune_name, "AmbatofisakaII") ~ "Ambatofisaka II",
        str_detect(commune_name, "AmbatoharananaI") ~ "Ambatoharanana",
        str_detect(commune_name, "Ambatolampy Tsimahaf") ~ "Ambatolampy",
        str_detect(commune_name, "Ambatolampy Tsimahafotsy") ~ "Ambatolampy",
        str_detect(commune_name, "Ambatoriha/Est") ~ "Ambatoriha Est",
        str_detect(commune_name, "Ambatotsipihana") ~ "Ambatotsipihina",
        str_detect(commune_name, "Ambatovala") ~ "Ambatolava",
        str_detect(commune_name, "Ambatry") ~ "Ambatry Mitsinjo",
        str_detect(commune_name, "Ambinanin'Andravory") ~ "Ambinanin'andravory",
        str_detect(commune_name, "Ambinaninandro") ~ "Ambinanindrano",
        str_detect(commune_name, "Ambinaniroa-Andonaka") ~ "Ambinaniroa",
        str_detect(commune_name, "Ambodiadabo Maitsokely") ~ "Ambodiadabo",
        str_detect(commune_name, "Ambodiadabo") ~ "Ambodiadabo M",
        str_detect(commune_name, "Ambodiampana Lokoho") ~ "Ambodiampana",
        str_detect(commune_name, "Ambodiampanana") ~ "Ambodiampana",
        str_detect(commune_name, "Ambodifarihy") ~ "Ambodifarihy Fenomanana",
        str_detect(commune_name, "Ambodihazambo") ~ "Ambodihazoambo",
        str_detect(commune_name, "Ambodimanga  I") ~ "Ambodimanga I",
        str_detect(commune_name, "Ambodimanga II-B") ~ "Ambodimanga II",
        str_detect(commune_name, "Ambodimotso Atsimo") ~ "Ambodimotso Sud",
        str_detect(commune_name, "AmbodinonokaAntaratr") ~ "Ambodinonoka",
        str_detect(commune_name, "Ambodirian'Isahafary") ~ "Ambodirian'i Sahafary",
        str_detect(commune_name, "Amboditandroho") ~ "Amboditandroroho",
        str_detect(commune_name, "Ambohibao Atsimo") ~ "Ambohibao Sud",
        str_detect(commune_name, "Ambohibary") ~ "Ambohibary Vohilena",
        str_detect(commune_name, "Ambohijato Mandritsara") ~ "Mandritsara",
        str_detect(commune_name, "Ambohimahavelona") ~ " Ambohimahavelona",
        str_detect(commune_name, "Ambohimalaza") ~ "Ambohimalaza Miray",
        str_detect(commune_name, "Ambohimàna") ~ "Ambohimana",
        str_detect(commune_name, "Ambohimanga Sud") ~ "Ambohimanga Du Sud",
        str_detect(commune_name, "Ambohimanjaka") ~ "Sahatsiho Ambohimanjaka",
        str_detect(commune_name, "AmbohimiarinaII") ~ "Ambohimiarina II",
        str_detect(commune_name, "Ambohitralalana") ~ "Ambohitralanana",
        str_detect(commune_name, "Ambohitrandriamanitr") ~ "Ambohitrandriamanitra",
        str_detect(commune_name, "AmbohitsaraEst") ~ "Ambohitsara Est",
        str_detect(commune_name, "Ambolidibe Atsinanana") ~ "Ambolidibe Est",
        str_detect(commune_name, "Ambolofoty") ~ "Ambolofoty",
        str_detect(commune_name, "Amboropotsy") ~ "Amborompotsy",
        str_detect(commune_name, "Ampasimadinika") ~ "Ampasimadinika Manambolo",
        str_detect(commune_name, "Ampasimborajka") ~ "Ampasimboraka",
        str_detect(commune_name, "Ampasimpotsy") ~ "Ampasimpotsy Sud",
        str_detect(commune_name, "Ampasipotsy Gare") ~ "Ampasimpotsy Gara",
        str_detect(commune_name, "Ampasipotsy Madialaz") ~ "Ampasipotsy Mandialaza",
        str_detect(commune_name, "Ampataka Manampaneva") ~ "Manampaneva",
        str_detect(commune_name, "Ampataka Maroreny") ~ "Ampatakamaroreny",
        str_detect(commune_name, "Anakao") ~ "Anakao",
        str_detect(commune_name, "Analalaiva") ~ "Analaiva",
        str_detect(commune_name, "Analamisampy") ~ "Analamisampy",
        str_detect(commune_name, "Analamitsivala") ~ "Analamitsivalana",
        str_detect(commune_name, "Anbatomainty") ~ "Ambatomainty",
        str_detect(commune_name, "Andanandava") ~ "Antanandava",
        str_detect(commune_name, "Andianjanto Est") ~ "Andrainjato Est",
        str_detect(commune_name, "Andimaka") ~ "Andimaky Manambolo",
        str_detect(commune_name, "Andoharanomaintso") ~ "Andoharanomaitso",
        str_detect(commune_name, "Andoharanomaintso") ~ "Andoharanomaitso",
        str_detect(commune_name, "Andrainjanto Centre") ~ "Andrainjato Centre",
        str_detect(commune_name, "Andranohinaly") ~ "Andranohinaly",
        str_detect(commune_name, "Andranomiditra") ~ "Andranomiditra",
        str_detect(commune_name, "Andranomiely") ~ "Rambolamasoandro Andranomiely",
        str_detect(commune_name, "Andranovorivato") ~ "Andranovorivato",
        str_detect(commune_name, "Andranovory") ~ "Andranovory",
        str_detect(commune_name, "Andravola") ~ "Andravola Vohipeno",
        str_detect(commune_name, "Andrebakely") ~ "Andrebakely Nord",
        str_detect(commune_name, "Andribavontsona") ~ "Andribavontsona",
        str_detect(commune_name, "Androndrona") ~ "Androndrono",
        str_detect(commune_name, "Androy") ~ "Androy",
        str_detect(commune_name, "Anjapaly") ~ "Anjampaly",
        str_detect(commune_name, "Anjeke Ankilira") ~ "Anjeky Ankilikira",
        str_detect(commune_name, "Anjeva Gare") ~ "Anjeva Gara",
        str_detect(commune_name, "Anjiabe") ~ "Anjiabe Ambony",
        str_detect(commune_name, "Anjiaija") ~ "Anjiajia",
        str_detect(commune_name, "Anjoman'Ankona") ~ "Anjoman'ankona",
        str_detect(commune_name, "Anjoma-tsara") ~ "Anjoma Itsara",
        str_detect(commune_name, "Ankadinondry") ~ "Ankadinondry Sakay",
        str_detect(commune_name, "Ankafina") ~ "Ankafina Tsarafidy",
        str_detect(commune_name, "Ankarinarivo") ~ "Ankarinarivo Manirisoa",
        str_detect(commune_name, "Ankaromalaza Mifanas") ~ "Ankaromalaza Mifanasoa",
        str_detect(commune_name, "Ankasakasa") ~ "Ankasakasa Tsibiray",
        str_detect(commune_name, "Ankazoabo") ~ "Ankazoabo Sud",
        str_detect(commune_name, "Ankazotokana I") ~ "Ankazotokana",
        str_detect(commune_name, "Ankiabe Salohy") ~ "Ankiabe-Salohy",
        str_detect(commune_name, "Ankiakabe-Nord") ~ " Ankiakabe Nord",
        str_detect(commune_name, "Ankililoaka") ~ "Ankililoaka",
        str_detect(commune_name, "Ankilimalinika") ~ "Ankilimalinike",
        str_detect(commune_name, "Ankirondro") ~ "Bemarivo Ankirondro",
        str_detect(commune_name, "Anontsibe") ~ "Anontsibe Centre",
        str_detect(commune_name, "Anosiarivo") ~ "Anosiarivo I",
        str_detect(commune_name, "Anosy Tsararafara") ~ "Anosy Tsararafa",
        str_detect(commune_name, "Antalaha") ~ " Antalaha Ambonivohitra",
        str_detect(commune_name, "Antanamalaza") ~ "Antanamalaza",
        str_detect(commune_name, "Antanambao Ambary") ~ "Antanambao Ambary",
        str_detect(commune_name, "Antanambao I") ~ "Antanambao",
        str_detect(commune_name, "Antanambao Manampotsy") ~ "Antanambao Manampontsy",
        str_detect(commune_name, "Antanambaon'Amberina") ~ "Antanambaon'amberina",
        str_detect(commune_name, "Antananarivo I") ~ "1er Arrondissement",
        str_detect(commune_name, "Antananarivo II") ~ "2e Arrondissement",
        str_detect(commune_name, "Antananarivo III") ~ "3e Arrondissement",
        str_detect(commune_name, "Antananarivo IV") ~ "4e Arrondissement",
        str_detect(commune_name, "Antananarivo V") ~ "5e Arrondissement",
        str_detect(commune_name, "Antananarivo VI") ~ "6e Arrondissement",
        str_detect(commune_name, "Antanandava Nord") ~ "Antanandava",
        str_detect(commune_name, "Antananivo /Haut") ~ "Antananivo Haut",
        str_detect(commune_name, "Antanetibe Mahazaza") ~ "Antanetibe",
        str_detect(commune_name, "Antanimora- Sud") ~ "Antanimora Atsimo",
        str_detect(commune_name, "Antenina I") ~ "Antenina",
        str_detect(commune_name, "Antoby") ~ "Antoby Est",
        str_detect(commune_name, "Antohaboto") ~ "Antohabato",
        str_detect(commune_name, "Antongo") ~ "Antongo Vaovao",
        str_detect(commune_name, "Antokoboritelo") ~ "Marovitsika Sud",
        str_detect(commune_name, "Antranonkarany") ~ "Antranokarany",
        str_detect(commune_name, "Antsahavaribe") ~ "Antsahavaribe",
        str_detect(commune_name, "Antsakomanondro") ~ "Antsakoamanondro",
        str_detect(commune_name, "Antsapanimahazo") ~ "Antsampanimahazo",
        str_detect(commune_name, "Antsirabe I") ~ "Antsirabe Afovoany Atsinanana",
        str_detect(commune_name, "Antsiranana I") ~ "Diego Suarez",
        str_detect(commune_name, "Antsoantany") ~ "Antsoatany",
        str_detect(commune_name, "Bealampoana") ~ "Bealampona",
        str_detect(commune_name, "Bealanana I") ~ "Bealanana",
        str_detect(commune_name, "Beampombo  I") ~ "Beampombo I",
        str_detect(commune_name, "Beandrarezona I") ~ "Beandrarezona",
        str_detect(commune_name, "Befandriana Avaratra") ~ "Befandriana Nord",
        str_detect(commune_name, "Befandriana-Sud") ~ "Befandriana Sud",
        str_detect(commune_name, "Befetra") ~ "Befeta",
        str_detect(commune_name, "Befotaka Avaratra") ~ "Befotaka Nord",
        str_detect(commune_name, "Befotaka") ~ "Befotaka Sud",
        str_detect(commune_name, "Beheloka") ~ "Beheloka",
        str_detect(commune_name, "Behera") ~ "Behara",
        str_detect(commune_name, "Behompy") ~ "Behompy",
        str_detect(commune_name, "Belafika Haut") ~ "Belafike Haut",
        str_detect(commune_name, "Belalanda") ~ "Belalanda",
        str_detect(commune_name, "Belambo") ~ "Belambo Firaisana",
        str_detect(commune_name, "Belaoko Marovato") ~ "Belaoka Marovato",
        str_detect(commune_name, "Belo sur Mer") ~ "Belo Sur Mer",
        str_detect(commune_name, "Belo Tsiribihina") ~ "Belo Sur Tsiribihina",
        str_detect(commune_name, "Belotsiribihina") ~ "Belo Sur Tsiribihina",
        str_detect(commune_name, "Bemaneviky H") ~ "Bemaneviky Haut Sambirano",
        str_detect(commune_name, "BenatoToby") ~ "Benato Toby",
        str_detect(commune_name, "Mangarivot") ~ "Mangarivotra",
        str_detect(commune_name, "Beraketa") ~ "Bereketa",
        str_detect(commune_name, "Berevo Ranobe") ~ "Berevo/ranobe",
        str_detect(commune_name, "Beroy Sud") ~ "Beroy Atsimo",
        str_detect(commune_name, "Betioky Sud") ~ "Betioky Atsimo",
        str_detect(commune_name, "Betsakotsako Andrano") ~ "Betsakotsako Andranotsara",
        str_detect(commune_name, "Betsimiositra") ~ "Betsimisotra",
        str_detect(commune_name, "Betsinjaka") ~ "Betsinjaka",
        str_detect(commune_name, "Bevoay Beretra") ~ " Beretra Bevoay",
        str_detect(commune_name, "Bevonotro") ~ "Bevonotra",
        str_detect(commune_name, "Efatsy Anandroza") ~ "Efatsy",
        str_detect(commune_name, "Enakara Haut") ~ "Enakara-Haut",
        str_detect(commune_name, "Enaniiliha") ~ "Enaniliha",
        str_detect(commune_name, "Ereda") ~ "Erada",
        str_detect(commune_name, "Etrotroka") ~ "Etrotroka Atsimo",
        str_detect(commune_name, "Fandravandava") ~ "Fandrandava",
        str_detect(commune_name, "Fanjakana") ~ "Fanjakana",
        str_detect(commune_name, "Faux-Cap") ~ "Betanty (Faux Cap)",
        str_detect(commune_name, "Fenoevo") ~ "Fenoevo-Efita",
        str_detect(commune_name, "Fieferana") ~ "Fiaferana",
        str_detect(commune_name, "Foulpointe") ~ "Mahavelona (Foulpointe)",
        str_detect(commune_name, "Ialananidro") ~ "Ialananindro",
        str_detect(commune_name, "Iavinomby") ~ "Iavonomby Vohibola",
        str_detect(commune_name, "Ibity") ~ "Alatsinainy Ibity",
        str_detect(commune_name, "Ihaborano Namohora") ~ "Namohora Iaborano",
        str_detect(commune_name, "Ihazoara") ~ "Ihazoara",
        str_detect(commune_name, "Iloto") ~ "Menamaty Iloto",
        str_detect(commune_name, "Imady") ~ "Imerina Imady",
        str_detect(commune_name, "Imeritsiatosika") ~ "Imerintsiatosika",
        str_detect(commune_name, "Isaka Ivondro") ~ "Isaka-Ivondro",
        str_detect(commune_name, "Isaraha") ~ "Isahara",
        str_detect(commune_name, "Isorana") ~ "Isorana",
        str_detect(commune_name, "Ivatana") ~ "Vatana",
        str_detect(commune_name, "Ivato Aéroport") ~ "Ivato Aeroport",
        str_detect(commune_name, "Ivoamba") ~ "Ivoamba",
        str_detect(commune_name, "Ivony") ~ "Ivony Miaramiasa",
        str_detect(commune_name, "Kalalao") ~ "Ikalalao",
        str_detect(commune_name, "Kianjandrandrakefina") ~ "Kianjandrakefina",
        str_detect(commune_name, "labohazo") ~ "Iabohazo",
        str_detect(commune_name, "Lavaraty Ivondro") ~ "Ivondro",
        str_detect(commune_name, "Mahaditra") ~ "Mahaditra",
        str_detect(commune_name, "Mahafasa") ~ "Mahafasa Centre",
        str_detect(commune_name, "Mahajanga I") ~ "Mahajanga",
        str_detect(commune_name, "Mahasoabe") ~ "Mahasoabe",
        str_detect(commune_name, "Mahatsara Lefaka") ~ "Mahatsara Iefaka",
        str_detect(commune_name, "Mahatsinjo Atsinanana") ~ "Mahatsinjo Est",
        str_detect(commune_name, "Mahatsinjo") ~ "Mahatsinjony",
        str_detect(commune_name, "Mahatsinjony") ~ "Mahatsinjony",
        str_detect(commune_name, "Mahazina") ~ "Mahazina Ambohipierenana",
        str_detect(commune_name, "Manajary Urbain") ~ "Mananjary",
        str_detect(commune_name, "Manakambahiny Est") ~ "Manakambahiny Antsinanana",
        str_detect(commune_name, "Manakambahiny Ouest") ~ "Manakambahiny Andrefana",
        str_detect(commune_name, "Manakara") ~ "Manakara",
        str_detect(commune_name, "Manambotra Sud") ~ "Manambotra Atsimo",
        str_detect(commune_name, "Manapatrana") ~ "Manampatrana",
        str_detect(commune_name, "Mandromodromotra") ~ "Mandromondromotra",
        str_detect(commune_name, "Maneva") ~ "Maneva",
        str_detect(commune_name, "Manombo") ~ "Manombo Sud",
        str_detect(commune_name, "Manorofify") ~ "Manorofify",
        str_detect(commune_name, "Marintampona") ~ "Maritampona",
        str_detect(commune_name, "Marivorahona") ~ "Tanambao Marivorahona",
        str_detect(commune_name, "Maroarivo") ~ "Maroarivo Ankazomanga",
        str_detect(commune_name, "MarofotyMarofoty") ~ "Marofoty",
        str_detect(commune_name, "Maromiandra") ~ "Maromiandra",
        str_detect(commune_name, "Maromokotra-Loky") ~ "Maromokotra Loky",
        str_detect(commune_name, "Marosavoa Bas") ~ "Marosavoa",
        str_detect(commune_name, "Marovitsika") ~ "Marovitsika Sud",
        str_detect(commune_name, "Merimandroso") ~ "Imerimandroso",
        str_detect(commune_name, "Miary") ~ "Miary Ambohibola",
        str_detect(commune_name, "Milenaka") ~ "Milenaka",
        str_detect(commune_name, "Mitsinjo") ~ "Mitsinjo Betanimena",
        str_detect(commune_name, "Mizilo Gare") ~ "Mizilo Gara",
        str_detect(commune_name, "Moramanga Urbain") ~ "Moramanga",
        str_detect(commune_name, "Morarano Gare") ~ "Morarano Gara",
        str_detect(commune_name, "Morombe") ~ "Cu Morombe",
        str_detect(commune_name, "Nagnarena") ~ "Nanarena Besakoa",
        str_detect(commune_name, "Nasandratrony") ~ "Nasandratrony",
        str_detect(commune_name, "Niarovana") ~ "Niarovana Marosampanana",
        str_detect(commune_name, "Nosibe Masianaka") ~ "Masianaka",
        str_detect(commune_name, "Onilhy") ~ "Onilahy",
        str_detect(commune_name, "Port Bergé I") ~ "Port Berge",
        str_detect(commune_name, "Port Bergé II") ~ "Port Berge II",
        str_detect(commune_name, "Rantabe Est") ~ "Rantabe",
        str_detect(commune_name, "Rantabe Sud") ~ "Rantabe",
        str_detect(commune_name, "Razanaka") ~ "Vohipeno Razanaka",
        str_detect(commune_name, "Sahamadio") ~ "Sahamadio Fisakana",
        str_detect(commune_name, "Sahambavy") ~ "Sahambavy",
        str_detect(commune_name, "Sahambo") ~ "Sahambano",
        str_detect(commune_name, "Sahanivotry Atsimo") ~ "Sahanivotry Manandona",
        str_detect(commune_name, "Sakamahily-Ouest") ~ "Sakamahily",
        str_detect(commune_name, "Sakay") ~ "Tanamarina Sakay",
        str_detect(commune_name, "Sakona") ~ "Sakoana",
        str_detect(commune_name, "Sambava Urbain") ~ "Sambava Cu",
        str_detect(commune_name, "Sarobaratra") ~ "Sarobaratra Ifanja",
        str_detect(commune_name, "Soaindrana") ~ "Soaindrana",
        str_detect(commune_name, "Soalara") ~ "Soalara Sud",
        str_detect(commune_name, "Soatanana") ~ "Soatanana",
        str_detect(commune_name, "St Augustin") ~ "Saint Augustin",
        str_detect(commune_name, "Taindambo") ~ "Taindambo",
        str_detect(commune_name, "Talata Ampano") ~ "Tatala Ampano",
        str_detect(commune_name, "Talatan'Angavo") ~ "Talata Angavo",
        str_detect(commune_name, "Taolagnaro") ~ "Fort-Dauphin",
        str_detect(commune_name, "Tanakamba") ~ "Tanakambana",
        str_detect(commune_name, "Tanambao  Daoud") ~ "Tanambao Daoud",
        str_detect(commune_name, "Tanambaovatrakaka") ~ "Tanambao Vahatrakaka",
        str_detect(commune_name, "Tanandava-Sud") ~ "Tanandava Sud",
        str_detect(commune_name, "Tanandrano") ~ "Tandrano",
        str_detect(commune_name, "Toamasina Suburbain") ~ "Toamasina Suburbaine",
        str_detect(commune_name, "Tovòna") ~ "Tovona",
        str_detect(commune_name, "Tsarahonenana") ~ "Tsarahonenana Sahanivotry",
        str_detect(commune_name, "Tsarajomoko") ~ "Tsarajomoka",
        str_detect(commune_name, "Tsaratanana") ~ "Tsaratanana I",
        str_detect(commune_name, "Tsiafajavona Ankarat") ~ "Tsiafajavona Ankaratra",
        str_detect(commune_name, "Tsianisiha") ~ "Tsianisiha",
        str_detect(commune_name, "Tsianofàna") ~ "Tsianofana",
        str_detect(commune_name, "Tsinjoarivo") ~ "Tsinjoarivo Imanga",
        str_detect(commune_name, "Tsiombe") ~ "Tsihombe",
        str_detect(commune_name, "Tsiroanomadidy Ville") ~ "Tsiroanomandidy Fihaonana",
        str_detect(commune_name, "Tsiroanomandidy Ville") ~ "Tsiroanomandidy Fihaonana",
        str_detect(commune_name, "Vatolatsaky") ~ "Vatolatsaka",
        str_detect(commune_name, "Vilihazo") ~ "Viliahazo",
        str_detect(commune_name, "Vinaninony Avaratra") ~ "Vinaninony Atsimo",
        str_detect(commune_name, "Vineta Andamasiny") ~ "Andamasiny Vineta",
        str_detect(commune_name, "Vohibato Ouest") ~ "Vohibato Ouest",
        str_detect(commune_name, "Vohimarina") ~ "Vohimarina",
        str_detect(commune_name, "Vohitrafeno") ~ "Vohitrafeno",
        str_detect(commune_name, "Zomabealoka") ~ "Zoma Bealoka",
        TRUE ~ commune_name
      )
    )

}

```

```{r facility-name-standardization-application_s2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

data_mh <- data_mh %>%
  rename(region_name = region,
         district_name = district,
         commune_name = commune) %>%
  clean_clinic_type() %>%
  clean_clinic_name() %>%
  clean_catchment_area() %>%
  mutate(
      clinic_type=
      gsub(
        "Pharmacy",
        "FSP",
        clinic_type
      ),
    clinic_name_clean=
      gsub(
        "MANARA PENITRA",
        "Manara Penitra",
        clinic_name_clean
      ),
    clinic_name_clean=
      gsub(
        "Manara-Penitra Antsiranana",
        "Manara Penitra",
        clinic_name_clean
      ),
    clinic_name_clean=
      gsub("Vakinakaratra", "Vakinankaratra", clinic_name_clean),
    clinic_name =
      gsub(
        "Hopitaly MANARA-PENITRA",
        "Hopitaly Manara Penitra",
        clinic_name
      ),
    clinic_name =
      gsub(
        "Hopitaly Manara-Penitra Antsiranana",
        "Hopitaly Manara Penitra",
        clinic_name
      ),

        clinic_name_clean =
      gsub(
        "Manara Penitra Antsiranana",
        "Manara Penitra",
        clinic_name_clean
      ),
    clinic_name =
      gsub("Vakinakaratra", "Vakinankaratra", clinic_name)) %>% 
  group_by( year, month, date, region_name, district_name, commune_name, 
                  clinic_name, disease, sex, subgroup, clinic_type, 
                  clinic_name_clean, clinic_type_clean) %>%
  mutate(count = sum(count)) %>%
  ungroup() %>%
  unique()

## Create a unique facility ID based on the clinic name and location
data_mh_temp <- data_mh %>%
  select(clinic_name, region_name, district_name, commune_name) %>%
  unique() %>%
  arrange(clinic_name, region_name, district_name, commune_name) %>%
  mutate(facility_ID = seq.int(nrow(.)))

## Create a catch all variable that includes any mental or neurological condition
data_mh <- data_mh %>%
  inner_join(., data_mh_temp, by = c("clinic_name", "region_name", "district_name", "commune_name")) %>%

  ## Create an "any condition" variable that sums the counts across all time series
  group_by(facility_ID, date, sex, subgroup) %>%
  mutate('Any mental or neurological disorders' = sum(count)) %>%
  ungroup()

rm(data_mh_temp)

data_mh_temp <- data_mh %>%
   select(!c(disease, count)) %>%
   unique() %>%
   pivot_longer('Any mental or neurological disorders', names_to = "disease", values_to = "count")

data_mh <- data_mh %>%
  select(!c('Any mental or neurological disorders')) %>%
  rbind(., data_mh_temp)

rm(data_mh_temp,csb_data, chd_data, chu_data, mh_english_disease)

data_mh %>% filter(sex == "both") %>% select(clinic_name, district_name, region_name, commune_name) %>% unique() %>% nrow()

max(data_mh$facility_ID)
```

```{r  data_cleaning_s2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

## To clean the data, we will use tsclean(), which requires at least two non-NA
## values to run

data_mh <- data_mh %>%

  ## Each unique combination of a disease counts for a given disease, clinic, subgroup,
  ## and sex is its own time series trend, with some time series having entirely missing values.
  ## Let's create an indicator for whether a time series has at least 2 non-NA values
  group_by(facility_ID, disease, subgroup, sex) %>%
  arrange(date, .by_group = TRUE) %>%

  ## We can now apply tsclean on those trends
  mutate(count_clean = tsclean(count, replace.missing = FALSE, lambda = NULL)) %>%
  mutate(count_clean = as.integer(count_clean)) %>%
  rename(count_raw = count) %>%
  ungroup() %>%
  ## Create an identifier to flag if an observation was an outlier that was replaced
  mutate(outlier_status = ifelse(count_raw != count_clean, "Outlier", 
                                 "Unadjusted")) %>%

  pivot_longer(c(count_raw, count_clean),
               names_to = "cleaning_status",
               values_to = "count") %>%
  mutate(count = as.integer(count))

```

```{r  saving_data_outputs_s2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
save(data_mh,
           file = paste(mh_path,"mh_data_all_facilities.Rdata", sep = "/"))

data_mh <- data_mh %>% 
  filter(sex == "both") %>%
  filter(subgroup == "total") %>%
  filter(disease == "Any mental or neurological disorders") 
```

\paragraph*{Data cleaning approach}

\addcontentsline{toc}{paragraph}{Data cleaning approach}

To address heterogeneity in reporting across primary, district-level, and regional-level facilities, our analysis constructed a single, summary outcome measure: any mental or neurological disorders reported in a given month by a given facility, irrespective of age and sex. This outcome measure was constructed by grouping our count data by facility and month-year, and then summing the incidence of mental and neurological disorders reported in GESIS within groups, preventing double counting and the inclusion of referrals in the summary measure.

<!-- The distribution of monthly case counts by facility type is shown below: -->

```{r  visualization_trends, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

data_mh %>%
  filter(cleaning_status == "count_raw") %>%
  ggplot(aes(x = as.Date(date), y = count)) +
  geom_point(alpha = 0.05, aes(color = clinic_type_clean)) +
    geom_smooth(colour = col_black, fill = col_grey_med) +
  scale_y_log10() +
    theme_classic() +
  theme(strip.background = element_rect(colour="white",
                                        fill="white"),
        text = element_text(family = "Source Sans Pro")) +
  theme(legend.position = "none") +
  labs(x = "Date", y = "Monthly count of cases") +
  facet_wrap(~clinic_type_clean, nrow = 3) +
  scale_color_manual(values = c(col_CHD, col_CHR, col_CSB))

n_unchanged <-
  data_mh %>%  filter(cleaning_status == "count_raw") %>%
 filter(outlier_status == "Unadjusted") %>% nrow()
n_changed <-
  data_mh %>%   filter(cleaning_status == "count_raw") %>%
filter(outlier_status != "Unadjusted") %>% nrow()
n_obs <- data_mh %>%  filter(cleaning_status == "count_raw") %>%
 nrow()
```

Visual inspect of our data showed potential outliers. which may have arisen due to data entry mistakes, synchronization errors, and other sources. To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series. The nonparametric Friedman’s super smoother regression estimator [@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation [@hyndmanAutomaticTimeSeries2008]. By considering outliers on a facility-by-facility basis, the data cleaning approach preserves extreme values that may reflect true variances in incidence (for example, incidences reported by a large, regional reference hospital) while addressing potential errors in data entry. Interpolated values were coerced to the nearest integer.

Linear interpolation ultimately only impacted `r format(as.numeric(n_changed), big.mark = ",")` of `r format(as.numeric(n_obs), big.mark = ",")` observations of our summary outcome measure, leaving approximately `r round(as.numeric(n_unchanged)/as.numeric(n_obs) * 100,0)`% of observations unadjusted.

<!-- A visual comparison of the raw and cleaned data is presented below. Observations on the identy line y = x are unadjusted. -->

<!-- ```{r  data_outputs_1, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- data_mh %>%  -->
<!--   pivot_wider(names_from = cleaning_status, values_from = count) %>% -->
<!--   ggplot(aes(x = count_raw, y = count_clean, -->
<!--              color = outlier_status)) + -->
<!--   geom_point() + -->
<!--   geom_abline(intercept = 0, slope = 1) + -->
<!--   facet_wrap(~clinic_type_clean, scales = "free") +  -->
<!--   theme_classic() + -->
<!--   theme(strip.background = element_rect(colour="white", -->
<!--                                         fill="white"), -->
<!--         text = element_text(family = "Source Sans Pro")) + -->
<!--   labs(x = "Unadjusted", y = "Adjusted for outliers", -->
<!--        color = "Outlier")  -->

<!-- ## Saving plot -->
<!-- ggsave(filename = "cleaning_1.jpg", plot = last_plot(), -->
<!--        path = mh_path) -->

<!-- ``` -->

<!-- ## References -->

<!-- ```{r  data_outputs_2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE} -->

<!-- data_mh %>%  -->
<!--   ggplot(aes(x=count, group = cleaning_status, fill = cleaning_status, color = cleaning_status)) + -->
<!--   geom_density(alpha=0.45, position="identity") + -->
<!--   scale_x_log10() + -->
<!--   labs(x = "Monthly count of cases (log 10)", -->
<!--        title = "Distribution of monthly case counts across all clinics", -->
<!--        y = "Density", -->
<!--        fill = "Year", -->
<!--        color = "Year") + -->
<!--   facet_wrap(~clinic_type_clean, scales = "free") +  -->
<!--   theme_classic() + -->
<!--   theme(strip.background = element_rect(colour="white", -->
<!--                                         fill="white"), -->
<!--         text = element_text(family = "Source Sans Pro"))  -->

<!-- ## Saving plot -->
<!-- ggsave(filename = "cleaning_2.jpg", plot = last_plot(), -->
<!--        path = mh_path, -->
<!--        width = 8, -->
<!--        height = 7) -->

<!-- data_mh %>%  -->
<!--   filter(count != 0) %>% -->
<!--   ggplot(aes(x=count, group = cleaning_status, fill = cleaning_status, color = cleaning_status)) + -->
<!--   geom_density(alpha=0.45, position="identity") + -->
<!--   labs(x = "Monthly count of cases", -->
<!--        title = "Distribution of non-zero monthly case counts across all clinics", -->
<!--        y = "Density", -->
<!--        fill = "Year", -->
<!--        color = "Year") + -->
<!--   facet_wrap(~clinic_type_clean, scales = "free") +  -->
<!--   theme_classic() + -->
<!--   theme(strip.background = element_rect(colour="white", -->
<!--                                         fill="white"), -->
<!--         text = element_text(family = "Source Sans Pro"))  -->

<!-- ## Saving plot -->
<!-- ggsave(filename = "cleaning_3.jpg", plot = last_plot(), -->
<!--        path = mh_path, -->
<!--        width = 8, -->
<!--        height = 7) -->

<!-- data_mh %>%  -->
<!--   filter(count <= 100) %>% -->
<!--   ggplot(aes(x=count, group = cleaning_status, fill = cleaning_status, color = cleaning_status)) + -->
<!--   geom_density(alpha=0.45, position="identity") + -->
<!--   labs(x = "Monthly count of cases", -->
<!--        title = "Distribution of non-zero monthly case counts across all clinics", -->
<!--        y = "Density", -->
<!--        fill = "Year", -->
<!--        color = "Year") + -->
<!--   facet_wrap(~clinic_type_clean, scales = "free") +  -->
<!--   theme_classic() + -->
<!--   theme(strip.background = element_rect(colour="white", -->
<!--                                         fill="white"), -->
<!--         text = element_text(family = "Source Sans Pro"))  -->

<!-- ## Saving plot -->
<!-- ggsave(filename = "cleaning_4.jpg", plot = last_plot(), -->
<!--        path = mh_path, -->
<!--        width = 8, -->
<!--        height = 7) -->

<!-- ## Record end of code time -->
<!-- end <- proc.time() -->
<!-- end <- as.numeric(end["elapsed"]) -->

<!-- pb_text <- paste0("This section of R code ran in ",  -->
<!--        round((end-start)/60,0), -->
<!--        " minutes.") -->

<!-- print(pb_text) -->

<!-- ifelse(require("RPushbullet") == TRUE,  -->
<!--        pbPost("note", "Health system data compiled", pb_text), -->
<!--        "") -->

<!-- ``` -->

<!-- ```{r  facility_upgrades, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE} -->

<!-- data_facility_reporting <- data_mh %>%  -->
<!--   filter(disease == "Any mental or neurological disorders") %>% -->
<!--   filter(sex == "both") %>% -->
<!--   filter(subgroup == "total") %>% -->
<!--   filter(cleaning_status == "count_raw") %>% -->
<!--   mutate(reporting = ifelse(count == 0, NA, "Yes")) %>% -->
<!--   select(date, region_name, district_name, commune_name, clinic_name_clean, clinic_type, reporting) %>% -->
<!--   unique() -->

<!-- duplicate_name_facilities <- data_facility_reporting %>% -->
<!--   select(region_name, district_name, commune_name, clinic_name_clean, clinic_type) %>% -->
<!--   unique() %>% -->
<!--   mutate(full_string = paste0(region_name, district_name, commune_name, clinic_name_clean)) -->

<!-- duplicates <- duplicate_name_facilities$full_string[duplicated(duplicate_name_facilities$full_string)] -->

<!-- data_facility_reporting %>% -->
<!--   filter(!is.na(reporting)) %>% -->
<!--   mutate(full_string = paste0(region_name, district_name, commune_name, clinic_name_clean)) %>% -->
<!--   filter(full_string %in% duplicates) %>% -->
<!--   select(!full_string) %>% -->
<!--   arrange(clinic_name_clean) %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_name_clean) %>% -->
<!--   mutate(n=1) %>% -->
<!--   mutate(sum1 = sum(n, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_type) %>% -->
<!--   mutate(sum2 = sum(n, na.rm = TRUE)) %>% -->
<!--   ungroup() %>% -->
<!--   filter(sum2 != sum1) %>% -->
<!--   unique() %>% -->
<!--   mutate(date = as.Date(date)) %>% -->
<!--   ggplot(aes(x = date, y = clinic_type, fill = reporting)) + -->
<!--   geom_tile() + -->
<!--   facet_wrap(~clinic_name_clean, scales = "free_y") + -->
<!--   theme(text = element_text(family = "Source Sans Pro")) + -->
<!--   theme(legend.position = "none")  + -->
<!--   scale_x_date(date_labels = "%Y") + -->
<!--   labs(x = "Date", y = "") + -->
<!--   theme_classic() -->

<!-- ## Saving plot -->
<!-- ggsave(filename = "facility_upgrades.jpg", plot = last_plot(), -->
<!--        path = mh_path) -->

<!-- duplicate_name_facilities %>% -->
<!--   filter(full_string %in% duplicates) %>% -->
<!--   select(!full_string) %>% -->
<!--   arrange(clinic_name_clean) %>% -->
<!--   group_by(region_name, district_name, commune_name, clinic_name_clean) %>% -->
<!--   summarise(clinic_type = paste(clinic_type, collapse = " | ")) %>% -->
<!--   ungroup() %>% -->
<!--   unique() %>% -->
<!--   select(clinic_name_clean, clinic_type) %>% -->
<!--   rename("Facility name" = clinic_name_clean, -->
<!--          "Types" = clinic_type) %>% -->
<!--   gt() %>%  -->
<!--   tab_header( -->
<!--     title = md("**Examples of duplicate facility names in different regions**")) %>% -->
<!--   tab_options(table.font.names = "Source Sans Pro") %>% -->
<!--   tab_style( -->
<!--     locations = cells_column_labels(), -->
<!--     style     = list( -->
<!--       cell_text(weight = "bold")) -->
<!--   ) -->

<!-- ``` -->

```{r  legac_code_s2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

######################
###   LEGACY CODE    ##
#######################

## ## 
## ## Summarize data by summing total number of referrals across facilities per month-year
## mh_data %>% 
##   filter(sex == "both") %>%
##   filter(disease == "Neuro-psychic diseases") %>%
##   filter(subgroup == "total") %>%
##   filter(count != 0) %>%
##   ggplot(aes(x = date, y = count)) +
##   geom_point(color = col_dark) +
##   geom_smooth(color = col_light) +
##   theme_minimal() +
##   labs(y = "Total",
##        x = "Month",
##        title = "Referrals for neuro-psych conditions") +
##   ylim(0,1000)
## 
## rm(data_npsy)

## ###################################
## ###      HEALTH SYSTEM DATA       ##
## ###################################
## 
## 
## ## Import raw data
## data_raw <- read.csv(paste(datasource, 'data.csv.gz', sep = "/"), 
##                      header=TRUE) %>%
##   
##   ## Create a yearmon variable to combine year and month columns
##   mutate(date = as.yearmon(paste(year, month), "%Y %m"))
## 
## ## Identify all unique variable descriptions, names, tables, and medical codes
## variable_descrip <- data_raw %>% select(description) %>% unique()
## variable_name <- data_raw %>% select(variable) %>% unique()
## variable_tabname <- data_raw %>% select(table_name) %>% unique()
## variable_medco <- data_raw %>% select(medical_code) %>% unique()
## 
## ## Export unique values 
## write.csv(variable_descrip, file = "results/variable_descriptions.csv")
## write.csv(variable_name, file = "results/variable_names.csv")
## write.csv(variable_tabname, file = "results/variable_table_names.csv")
## write.csv(variable_medco, file = "results/variable_medical_codes.csv")
## rm(variable_descrip, variable_name, variable_tabname)
## 
## ## Bring in descriptions of medical codes 
## medical_codes <- read.csv(paste(datapath, "medical_codes.csv", sep = "/")) %>%
##   select(code, description) %>% 
##   rename(medical_code = code)
## variable_medco_joined <- inner_join(variable_medco, medical_codes, by = "medical_code") %>% 
##   unique()
## 
## ## Export unique medical codes with descriptions
## write.csv(variable_medco_joined, file = "results/variable_medical_codes_included.csv")
## rm(variable_medco, medical_codes, variable_medco_joined)
## 
## ## Subset data to variable on referrals for neuro-psychic (NP) disorders
## data_mh <- data_raw %>% 
##   filter(medical_code == "NPSY") 
## 
## ## Summarize data by summing total number of referrals across facilities per month-year
## data_npsy <- data_mh %>% 
##   group_by(date) %>% 
##   mutate(count = sum(as.numeric(value))) %>% 
##   ungroup() %>%
##   select(date, count) %>%
##   unique()
## 
## ## Plot total number of NP referrals over time
## data_npsy %>% ggplot(aes(x = date, y = count)) +
##   geom_point(color = col_dark) +
##   geom_smooth(color = col_light) +
##   theme_minimal() +
##   labs(y = "Total",
##        x = "Month",
##        title = "Referrals for neuro-psych conditions")
## 
## ## Save plot
## ggsave(filename = "npsy_plot.jpg", plot = last_plot(),
##        path = resultspath,
##        width = 9,
##        height = 6)
## 
## ## Extraction of unique clinics and district appearing in the data
## facilities_clinic_codes <- data_raw %>% select(clinic_code) %>% unique()
## facilities_district_codes <- data_raw %>% select(district_code) %>% unique()
## 
## ## Exporting unique values
## write.csv(facilities_clinic_codes, file = "results/facilities_clinic_codes.csv")
## write.csv(facilities_district_codes, file = "results/facilities_district_codes.csv")
## rm(facilities_district_codes)
## 
## ## Crosswalking facility information. This section tries to draw in district
## ## and GIS information from available resources for any clinics appearing in the data.
## 
## ## Clinic names
## facilities_crosswalk <- read.csv(paste(datapath, 'clinics.csv', sep = "/"), 
##                                  header=TRUE) %>% 
##   select(district_code, clinic_code, name) %>%
##   rename(clinic_name = name) %>%
##   unique()
## 
## facilities_clinic_codes_merged <- left_join(facilities_clinic_codes, facilities_crosswalk, by = "clinic_code")
## 
## ## District names and types
## facilities_district <- read.csv(paste(datapath, 'districts.csv', sep = "/"), 
##                                 header=TRUE) %>% 
##   select(district_code, district_type, name) %>%
##   rename(district_name = name) %>%
##   unique()
## 
## facilities_clinic_codes_merged_district <- left_join(facilities_clinic_codes_merged, facilities_district, by = "district_code")
## 
## ## Latitude and longitude of clinics
## facilities_coordinates <- read.csv(paste(datapath, 'Health clinic data points.csv', sep = "/"), 
##                                    header=TRUE) %>%
##   select(Nom.complet.FS.1, latitude, longitude) %>% 
##   rename(clinic_name = Nom.complet.FS.1) %>%
##   unique() 
## 
## facilities_clinic_codes_merged_district_coord <- left_join(facilities_clinic_codes_merged_district, facilities_coordinates, by = "clinic_name")
## 
## write.csv(facilities_clinic_codes_merged_district_coord, 
##           file = "results/clinics_districts_coordinates.csv")
## 
## ## District information
## map_mdg_2_trim <- map_mdg_2_trim %>% 
##   rename(district_name = ADM2_EN) %>%
##   select(district_name, ADM2_PCODE)
## 
## facilities_map <- left_join(
##   facilities_clinic_codes_merged_district_coord,
##   map_mdg_2_trim, by = "district_name")
## 
## facilities_unmatched <- facilities_map %>%
##   filter(!is.na(ADM2_PCODE)) %>%
##   select(district_code, district_name, ADM2_PCODE) %>%
##   unique()
## 
## write.csv(facilities_unmatched, 
##           file = "results/clinics_unmatched.csv")
## 
## 
## ## Standardizing district names to shapefile names (ADM2_EN)
## facilities_map_clean <- facilities_map %>% select(clinic_code:clinic_name) %>%
##   left_join(., district_crosswalk, by = "district_code") %>%
##   select(!c(district_name)) %>%
##   rename(district_name = rename) %>%
##   unique()
## 
## ## Summarizing number of facilities per district
## facility_district_count <- count(as_tibble(map_clean), ADM2_PCODE) 
## 
## ## Create map of district-level summary data
## map_clean %>%
##   select(ADM2_PCODE, district_name, district_code, geometry) %>%
##   left_join(., facility_district_count, by = "ADM2_PCODE") %>%
##   unique() %>% 
##   mutate(manual_fill = cut(n, breaks = c(-0.1, 0.1, 1.1, 2.1, 3.1, 4.1, 9.1, Inf),
##                            labels = c("None", "1", "2", 
##                                       "3", "4", "5-9", "10+"),
##                            right = TRUE)) %>%
##   ggplot(aes(geometry = geometry)) +
##   geom_sf(size = 0.2, 
##           color = "grey55",
##           aes(fill = manual_fill)) + 
##   theme_void() +
##   scale_fill_manual(name = "Facilities in dataset", values = pal) 
## 
## ## Saving plot
## ggsave(filename = "facilities_map.jpg", plot = last_plot(),
##        path = resultspath,
##        width = 8,
##        height = 7)

```

### 2023-02-22 appendix_2.2.Rmd
Addition of appendices, revisions throughout papers, acknowledgements

---
title: ""
subtitle: ""
---

```{r parameters-and-data_2_2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

### CSB

csb_10to15 <- read.csv(paste(data_mh_csb, 'Affections mentales et troubles psychiques GESIS CSB 2010-2015.csv',
                             sep = "/"), 
                       header=TRUE) %>%
  mutate(across(.cols=where(is.integer), .fns=as.numeric)) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  rename(year = cAnnee,
         month = Periode,
         region = Region,
         district = District,
         commune = commune,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days' = X0.à.28j,
         '29-days-to-11-months' = X29j.à.11.m,
         '1-to-4-years' = X1.à.4.ans,
         '5-to-14-years' = X5.à.14.ans,
         '15-to-24-years' = X15.à.24.ans,
         '25-years-plus' = X25.et.plus,
         total = total,     
         referalls = Référés) %>%
  mutate(sex = "both",
         year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  pivot_longer(cols = '0-to-28-days':referalls, names_to = "subgroup", values_to = "count")

csb_15to16 <- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2015-2016.csv',
                             sep = "/"), 
                       header=TRUE)

csb_17 <- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2017.csv',
                         sep = "/"), 
                   header=TRUE)

csb_18 <- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2018.csv',
                         sep = "/"), 
                   header=TRUE)

csb_19 <- read.csv(paste(data_mh_csb, 'troubles mentaux GESIS CSB 2019.csv',
                         sep = "/"), 
                   header=TRUE)

csb_15to19 <- rbind(csb_15to16,csb_17, csb_18, csb_19) %>%
  mutate(across(.cols=where(is.integer), .fns=as.numeric)) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  mutate(total_male = X0.à.28j_Masculin + 
           X29j.à.11.m_Masculin + 
           X1.à.4.ans_Masculin + 
           X5.à.14.ans_Masculin + 
           X15.à.24.ans_Masculin +
           X25.à.59.ans_Masculin +
           X60.ans.et.plus_Masculin,

         total_female = X0.à.28j_Feminin + 
           X29j.à.11.m_Feminin + 
           X1.à.4.ans_Feminin + 
           X5.à.14.ans_Feminin + 
           X15.à.24.ans_Feminin +
           X25.à.59.ans_Feminin +
           X60.ans.et.plus_Feminin) %>%

  rename(year = cAnnee,
         month = Periode,
         region = Region,
         district = District,
         commune = Commune,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days_male' =  X0.à.28j_Masculin,
         '0-to-28-days_female' =  X0.à.28j_Feminin,  
         '29-days-to-11-months_male' = X29j.à.11.m_Masculin,
         '29-days-to-11-months_female' = X29j.à.11.m_Feminin,
         '1-to-4-years_male' = X1.à.4.ans_Masculin,
         '1-to-4-years_female' = X1.à.4.ans_Feminin,
         '5-to-14-years_male' = X5.à.14.ans_Masculin,
         '5-to-14-years_female' = X5.à.14.ans_Feminin,
         '15-to-24-years_male' =X15.à.24.ans_Masculin,
         '15-to-24-years_female' = X15.à.24.ans_Feminin,
         '25-to-59-years_male' = X25.à.59.ans_Masculin,
         '25-to-59-years_female' = X25.à.59.ans_Feminin,
         '60-years-plus_male' = X60.ans.et.plus_Masculin,
         '60-years-plus_female' = X60.ans.et.plus_Feminin,
         referalls_male = Référés_Masculin,
         referalls_female = Référés__Feminin) %>% 
  mutate(year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  pivot_longer(cols = '0-to-28-days_male':total_female,
               names_to = c("subgroup","sex"), 
               names_sep = "_",
               values_to = "count") %>%
  group_by(date, clinic_name, disease, subgroup) %>%
  mutate(both = sum(count)) %>%
  pivot_wider(names_from = sex, values_from = count) %>%
  pivot_longer(cols = c(both, male, female),
               names_to = "sex",
               values_to = "count") %>%
  ungroup()

csb_data <- rbind(csb_10to15, csb_15to19)
rm(csb_10to15, csb_15to19, csb_15to16,csb_17, csb_18, csb_19)

# CHD 
chd_data <- read.csv(paste(data_mh_chd, 'Maladies neuro-psychiques CHD.csv',
                           sep = "/"), 
                     header=TRUE) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  mutate(total = X0.à.28j +
           X29j.à.11.m +
           X1.à.4.ans +
           X5.à.14.ans +
           X15.à.24.ans +
           X25.et.plus,
         commune = "NA") %>%
  rename(year = cAnnee,
         month = Periode,
         region = Region,
         district = District,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days' = X0.à.28j,
         '29-days-to-11-months' = X29j.à.11.m,
         '1-to-4-years' = X1.à.4.ans,
         '5-to-14-years' = X5.à.14.ans,
         '15-to-24-years' = X15.à.24.ans,
         '25-years-plus' = X25.et.plus,
         referalls = Référés) %>%
  mutate(sex = "both",
         year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  relocate(commune, .after = district) %>%
  pivot_longer(cols = '0-to-28-days':total, names_to = "subgroup", values_to = "count")

# CHU and CHRR

chu_files <- as.vector(list.files(data_mh_chu_chrr))
chu_data <- data.frame(matrix(ncol = 12, nrow = 0))

for (x in chu_files) {

  chu_data_r <- read.csv(paste(data_mh_chu_chrr, x,
                               sep = "/"), 
                         header=TRUE)

  chu_data <- rbind(chu_data, chu_data_r)

  rm(chu_data_r)

}
chu_data <- chu_data %>%
  mutate(across(.cols=where(is.integer), .fns=as.numeric)) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  mutate(district = "NA",
         commune = "NA") %>%
  rename(year = cAnnee,
         month = Periode,
         region = Region,
         clinic_name = FS,
         disease = cDesc,
         '0-to-28-days' = X0.à.28j,
         '29-days-to-11-months' = X29j.à.11.m,
         '1-to-4-years' = X1.à.4.ans,
         '5-to-14-years' = X5.à.14.ans,
         '15-to-24-years' = X15.à.24.ans,
         '25-years-plus' = X25.et.plus,
         total = total) %>%
  mutate(sex = "both",
         year = as.character(year),
         month = as.integer(factor(month, levels = month.name)),
         date = as.yearmon(paste(year, month), "%Y %m")) %>%
  relocate(date, .after = month) %>%
  relocate(district, .after = region) %>%
  relocate(commune, .after = district) %>%
  pivot_longer(cols = '0-to-28-days':total, names_to = "subgroup", values_to = "count")

mh_english_disease <- read_excel(
  paste(datapath_reference, "disease_names_crosswalk.xlsx", sep = "/"))

data_mh <- rbind(csb_data, chd_data, chu_data) %>% # Join all data
  select(commune, district, region, clinic_name) %>%
  mutate(region = str_to_title(region), # Capitalizing region names
         clinic_name = str_squish(clinic_name)) %>%
  unique()

rm(chd_data, chu_data, csb_data, mh_english_disease)

# Saving start time (to help time the code)
start <- proc.time()
start <- as.numeric(start["elapsed"])

# RPushbullet is a package that uses the app Pushbullet to send notifcations
# to a device. This is entirely optional, but is handly for tracking progress.
ifelse(require("RPushbullet") == TRUE, 
       pbPost("note", "Appendix 2 started", paste0("GPS do file started.")),
       "")

n_facilities_name <- data_mh %>% select(clinic_name) %>% unique %>% nrow()
n_facilities <- data_mh %>% unique %>% nrow()

```
\paragraph*{Overview of Madagascar's health sector}

\addcontentsline{toc}{paragraph}{Overview of Madagascar's health sector}

In Madagascar, public health facilities can be broadly classified under four types:

* **Basic** health facilities (*centre santé de base*, or CSB)
* **District** referral hospitals (*centre hospitalier de référence de district*, or CHD/CHRD)
* **Regional** referral hospitals (*centre hospitalier de référence régionale*, or CHRR)
* **University** hospitals (*centre hospitalier universitaire*, or CHU)

According to the World Bank, there were 3,246 of these facilities operating in Madagascar in 2012. @guillemotMadagascarClimateChange2018 Of these, 3,074 were CSB facilities. CSB facilities are classified as either level 1 or 2 based on population, staffing, and services provided. Facilities may be upgraded over time, such that a CSB1 facility is converted into a CSB2. At the district level, 150 CHD facilities were functional in 2012. Like CSB facilities, CHD facilities are classified as either level 1 or level 2; these facilities provide essential medical services and—in the case of CHD2 facilities—surgical care. At the regional level, 16 CHRR and 6 CHU facilities were operational in 2012, providing specialized medical and surgical care.

In addition to these public facilities, private primary health facilities (*formations sanitaires privées de base*, or FSB) are also operational and report data to the Ministère de la Santé Publique. A USAID private health sector report identified 825 FSB facilities in  Madagascar operating and providing data in 2017. @brunnerMadagascarPrivateHealth2017

\paragraph*{Sample of health facilities}

\addcontentsline{toc}{paragraph}{Sample of health facilities}

The sample of health facilities in our study was obtained from health facility data from Madagascar's *Gestion du Système d'Information Sanitaire* (GESIS). While the format of outputs from GESIS vary across years and facility type, there are four variables which uniquely identify facilities.

* **Region**: The region of Madagascar that contains the facility's catchment area. All facilities have a value for this variable.
* **District**: The district of Madagascar (2nd largest administrative unit) that contains the facility's catchment area. Only district- and commune-level facilities will have a value for this variable; regional-level hospitals  have an "*NA*" for this variable.
* **Commune**: The commune of Madagascar (3rd largest unit) that contains the facility's catchment area. District- and regional-level hospitals have an "*NA*" for this variable.
* **FS**: The facility type and name. The facility type will typically be identified with an acronym (e.g., CSB2, CHD1, etc.), with the facility name following thereafter. The facility name will occasionally be the same as the commune, district, or region that corresponds with the facility's catchment area (e.g., CHRR Alaotra Mangoro). Some facilities are named for the village (*fokontany*) that they are located in. Other facilities are named for the groups that operate them (e.g., facilities named "EKAR" are operated by the *Eglizy Katôlika Apôstôlika Rômanina*, or the Roman Catholic Church).

Before beginning to geolocate our sample, we began by identifying the unique facilities therein. At first pass, our sample included `r  prettyNum(n_facilities_name, big.mark = ",", scientific = FALSE)` uniquely named facilities. We observed, however, several instances where facilities in different regions shared the same facility name: for example, there is a CSB2 facility named "Ambalabe" in both the Sava and Atsimo Atsinanana regions, which are located at the northern and southern ends of Madagascar, respectively.

```{r table_facility-names-duplicates_1, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

data_mh_dup_names <- data_mh %>%
  select(region, clinic_name) %>% unique()

duplicates <- data_mh_dup_names$clinic_name[duplicated(data_mh_dup_names$clinic_name)]

# data_mh_dup_names %>%
#   select(region, clinic_name) %>%
#   unique() %>%
#   filter(clinic_name %in% duplicates) %>%
#   relocate(clinic_name, .before = region) %>%
#   arrange(clinic_name) %>%
#   group_by(clinic_name) %>%
#   summarise(region = paste(region, collapse = " | ")) %>%
#   unique() %>%
#   rename("Facility name" = clinic_name,
#          "Regions" = region) %>%
#   gt() %>% 
#   tab_header(
#     title = md("**Examples of duplicate facility names in different regions**")) %>%
#   tab_options(table.font.names = "Source Sans Pro") %>%
#   tab_style(
#     locations = cells_column_labels(),
#     style     = list(
#       cell_text(weight = "bold"))
#   )

```

These cases indicated that identifying unique facilities would require catchment area information (as well as facility name and type) to avoid erroneously classifying unique facilities as duplicates.

Using facility name, type, and catchment area to uniquely identify facilities in our sample, we identified `r  prettyNum(n_facilities, big.mark = ",", scientific = FALSE)` unique facilities. In order to classify these facilities by type, we extracted the relevant data from the "FS' variable; in doing so, we observed slight orthographic variations in the classification of facilities types (e.g., "CSB 1" vs. "CSB1") that required standardization.

We further standardized region, district, and commune names in our sample against reference shapefiles to address variations in translation (e.g., "Atsimo" and "Sud" being the Malagasy and French words for "South"), abbreviation (e.g., "St." as an abbreviation for "Saint"), transposition (e.g., "Bevoay Beretra" transposed as "Beretra Bevoay"), accent marks (e.g., "Tovòna" vs. "Tovona"), spacing (e.g., "AmbalapaisoII" vs. "Ambalapaiso II"), separation vs. combination of names (e.g., "Tanambaovatrakaka" vs. "Tanambao Vahatrakaka"), hyphenation (e.g, "Ankiabe Salohy" and "Ankiabe-Salohy"), and spelling (e.g., "Mizilo Gare" vs.	"Mizilo Gara").

```{r facility-name-standardization-function_1,  warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

capwords <- function(s, strict = FALSE) {
  cap <- function(s) paste(toupper(substring(s, 1, 1)),
                           {s <- substring(s, 2); if(strict) tolower(s) else s},
                           sep = "", collapse = " " )
  sapply(strsplit(s, split = " "), cap, USE.NAMES = !is.null(names(s)))
}

clean_clinic_type <- function(data){
  data %>%
    mutate(clinic_type = case_when(
      str_detect(clinic_name, "CBS1") ~ "CSB1",
      str_detect(clinic_name, "Centre de santé de base 2 ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base de Deuxième Niveau ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base de Niveau 2 ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base de niveau II ") ~ "CSB2",
      str_detect(clinic_name, "Centre De Santé De Base De Niveau II") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base I ") ~ "CSB1",
      str_detect(clinic_name, "Centre de Santé de Base II ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base Niveau 1 ") ~ "CSB1",
      str_detect(clinic_name, "Centre de Santé de Base Niveau 2 ") ~ "CSB2",
      str_detect(clinic_name, "Centre de Santé de Base Niveau I ")~ "CSB1",
      str_detect(clinic_name, "Centre de Santé de Base Niveau II")~ "CSB2",
      str_detect(clinic_name, "Centre du Santé de Base I ") ~ "CSB1",
      str_detect(clinic_name, "Centre Hospitalier de District ") ~ "CHD",
      str_detect(clinic_name, "Centre Hospitalier De Référence De District ") ~ "CHD",
      str_detect(clinic_name, "Centre Hospitalier de Référence Régional ") ~ "CHRR",
      str_detect(clinic_name, "Centre Hospitalier de Référence Régional de ") ~ "CHRR",
      str_detect(clinic_name, "Centre Hospitalier Régional De Référence ") ~ "CHRR",
      str_detect(clinic_name, "Centre Hosptalier de Référence du District du ") ~ "CHD",
      str_detect(clinic_name, "Centre sante de base niveau II ") ~ "CSB2",
      str_detect(clinic_name, "CHD 1") ~ "CHD1",
      str_detect(clinic_name, "CHD 2") ~ "CHD2",
      str_detect(clinic_name, "CHD1") ~ "CHD1",
      str_detect(clinic_name, "CHD2") ~ "CHD2",
      str_detect(clinic_name, "CHRD 1") ~ "CHD1",
      str_detect(clinic_name, "CHRD 2") ~ "CHD2",
      str_detect(clinic_name, "CHRD II ") ~ "CHD2",
      str_detect(clinic_name, "CHRD1") ~ "CHD1",
      str_detect(clinic_name, "CHRD2 ") ~ "CHD2",
      str_detect(clinic_name, "CHRD2") ~ "CHD2",
      str_detect(clinic_name, "CHRR ") ~ "CHRR",
      str_detect(clinic_name, "CHRR II ") ~ "CHRR",
      str_detect(clinic_name, "CHU ") ~ "CHU",
      str_detect(clinic_name, "Csb 1 ") ~ "CSB1",
      str_detect(clinic_name, "CSB 1") ~ "CSB1",
      str_detect(clinic_name, "CSB 2") ~ "CSB2",
      str_detect(clinic_name, "CSB I ")~ "CSB1",
      str_detect(clinic_name, "CSB II")~ "CSB2",
      str_detect(clinic_name, "Csb1") ~ "CSB1",
      str_detect(clinic_name, "CSB1") ~ "CSB1",
      str_detect(clinic_name, "CSB2") ~ "CSB2",

      str_detect(clinic_name, "depot de medicament") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôt de médicaments ") ~ "Pharmacy",
      str_detect(clinic_name, "Dépot de médicaments") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôt de médicaments") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôtde médicament ") ~ "Pharmacy",
      str_detect(clinic_name, "Dépôts de médicaments") ~ "Pharmacy",
      str_detect(clinic_name, "Dispensaire") ~ "Pharmacy",
      str_detect(clinic_name, "Docteur ") ~ "FSP",
      str_detect(clinic_name, "Dokotera ") ~ "FSP",
      str_detect(clinic_name, "Dr ") ~ "FSP",
      str_detect(clinic_name, "Fivarotampanafody ") ~ "Pharmacy",
      str_detect(clinic_name, "Fivarotam-panafody ") ~ "Pharmacy",
      str_detect(clinic_name, "FSP") ~ "FSP",
      str_detect(clinic_name, "HP ") ~ "HP",
      str_detect(clinic_name, "pharmacie de ") ~ "Pharmacy",
      str_detect(clinic_name, "Pharmacie") ~ "Pharmacy",
      str_detect(clinic_name, "Pharmacrie") ~ "Pharmacy",
      str_detect(clinic_name, "Pharmacy") ~ "Pharmacy",
      str_detect(clinic_name, "Pavillon Sainte Fleur") ~ "CHU", #https://maternitesaintefleur.wordpress.com/
      TRUE ~ "Other/Unknown")) %>%

    mutate(clinic_type = case_when(
          and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "Centre de santé de base")) ~ "CSB",
                  and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "Centre De Santé ")) ~ "CSB",
                  and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "Centre De Santé De Base ")) ~ "CSB",
                  and(clinic_type == "Other/Unknown", 
              str_detect(clinic_name, "CSB")) ~ "CSB",
     TRUE ~ clinic_type))

}

clean_clinic_name <- function(data){
  data %>%
    mutate(clinic_name_clean = clinic_name) %>%
    mutate(clinic_name_clean = gsub("CBS1", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Rééducation Motrice De Madagascar Antsirabe", "Centre De Rééducation Motrice Antsirabe", clinic_name_clean),
           clinic_name_clean = gsub("Centre de santé de base 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de Deuxième Niveau ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de Niveau 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de niveau II ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base de Niveau II ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Santé De Base De Niveau II", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base I ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base II ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau 1 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau I ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé de Base Niveau II", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de santé de base", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre du Santé de Base I ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Santé ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de Santé ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre de santé ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre De Santé De Base ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de District ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier De Référence De District ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de Référence de District ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de Référence Régional ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier de Référence Régional de ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier De Référence Régional De ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier Régional De Référence ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre Hospitalier Régional de Référence ", "", clinic_name_clean),  
           clinic_name_clean = gsub("Centre Hosptalier de Référence du District du ", "", clinic_name_clean),
           clinic_name_clean = gsub("Centre sante de base niveau II ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD 1", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD 2", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD1", "", clinic_name_clean),
           clinic_name_clean = gsub("CHD2", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD2", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRR", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRR II", "", clinic_name_clean),
           clinic_name_clean = gsub("CHU ", "", clinic_name_clean),
           clinic_name_clean = gsub("Csb 1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB 1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB 2", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB I ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD II ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("CHRD 2 ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB II", "", clinic_name_clean),
           clinic_name_clean = gsub("Csb1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB1", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB2", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBU ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSB ", "", clinic_name_clean),
           clinic_name_clean = gsub("csb ", "", clinic_name_clean),
           clinic_name_clean = gsub("FSP_", "", clinic_name_clean),
           clinic_name_clean = gsub("FSP_", "", clinic_name_clean),
           clinic_name_clean = gsub("FSP ", "", clinic_name_clean),
           clinic_name_clean = gsub("Pharmacie", "", clinic_name_clean),
           clinic_name_clean = gsub("pharmacie de ", "", clinic_name_clean),
           clinic_name_clean = gsub("Pharmacy", "", clinic_name_clean),
           clinic_name_clean = gsub("Pharmacrie", "", clinic_name_clean),
           clinic_name_clean = gsub("PHARMACIE", "", clinic_name_clean),
           clinic_name_clean = gsub("Dispensaire", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt  de médicament ", "", clinic_name_clean),
           clinic_name_clean = gsub("depot de medicament", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Fivarotam-panafody", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépot de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépot de Médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôt de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôts de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Dépôts de médicaments", "", clinic_name_clean),
           clinic_name_clean = gsub("Docteur ", "", clinic_name_clean),
           clinic_name_clean = gsub("Dokotera ", "", clinic_name_clean),
           clinic_name_clean = gsub("Dr ", "", clinic_name_clean),
           clinic_name_clean = gsub("Fivarotam-Panafody", "", clinic_name_clean),
           clinic_name_clean = gsub("Fivarotampanafody ", "", clinic_name_clean),
           clinic_name_clean = gsub("HP HP", "", clinic_name_clean),
           clinic_name_clean = gsub("HP", "", clinic_name_clean),
           clinic_name_clean = gsub("Polyclinique", "", clinic_name_clean),
           clinic_name_clean = gsub("Clinique ", "", clinic_name_clean),
           clinic_name_clean = gsub("CH ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBD ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBU", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBD ", "", clinic_name_clean),
           clinic_name_clean = gsub("CSBDS ", "", clinic_name_clean),
           clinic_name_clean = gsub("Medico Chirurgicale ", "", clinic_name_clean),
           clinic_name_clean = gsub("CMC ", "", clinic_name_clean),
           clinic_name_clean = gsub("Loterana", "Luthérien", clinic_name_clean),
           clinic_name_clean = gsub("Saint Luc Toliara I", "Saint Luc", clinic_name_clean),
           clinic_name_clean = gsub(" Hospital", "", clinic_name_clean),
           clinic_name_clean = gsub("Hôpital", "", clinic_name_clean),
           clinic_name_clean = gsub("Hopitaly ", "", clinic_name_clean),
           clinic_name_clean = gsub("Hopital ", "", clinic_name_clean),
           clinic_name_clean = gsub(" Health Centre", "", clinic_name_clean),
           clinic_name_clean = gsub(" Health Post", "", clinic_name_clean),

           # Finally, we replace hypens and underscores with spaces in the 
           # clinic and district names. We also remove double spaces in 
           #between words, and remove leading and trailing whitespace

           clinic_name_clean = gsub("-", " ", clinic_name_clean),
           clinic_name_clean = gsub("_", " ", clinic_name_clean),
           clinic_name_clean = gsub("  ", " ", clinic_name_clean),
           clinic_name_clean = trimws(clinic_name_clean),
           clinic_name_clean = capwords(clinic_name_clean)) %>%

    filter(clinic_name_clean != "")
}

clean_catchment_area <- function(data){

  data %>% 
    mutate(
      region_name = gsub("NA", NA, region_name),
      district_name = gsub("NA", NA, district_name),
      commune_name = gsub("NA", NA, commune_name)
    ) %>%

    mutate(
      clinic_type = ifelse(
        is.na(district_name) &
          is.na(commune_name) &
          clinic_type != "CHRR" &
          clinic_type != "CHU",
        "CHRR/CHU",
        ifelse(
          !is.na(district_name) &
            is.na(commune_name) &
            clinic_type != "CHD1" &
            clinic_type != "CHD2",
          "CHD",
          clinic_type
        )
      )
    ) %>%

    mutate(clinic_type_clean = ifelse(
      and(is.na(district_name) | district_name =="",
          is.na(commune_name) | commune_name ==""),

      # If the facility's catchment area is a
      # region only, assign it as a cHR or CHU

      "CHR/CHU",

      # If the facility's catchment area is a district
      # only, assign it as a CHD (no level specified)

      ifelse(is.na(commune_name) | commune_name =="",
             "CHD",

             # If the facility's catchment area is
             # a commune, assign it as a CSB or FSP
             # (no level specified)

             "CSB/FSP")
    )) %>%

    mutate(region_name = case_when(
      str_detect(region_name, "Amoron'i Mania") ~ "Amoron I Mania",
      TRUE ~ region_name
    )) %>%

    mutate(
      district_name = case_when(
        str_detect(district_name, "Anosibe An'Ala") ~ "Anosibe-An'ala",
        str_detect(district_name, "Antananarivo Atsimon") ~ "Antananarivo Atsimondrano",
        str_detect(district_name, "Antananarivo Avaradr") ~ "Antananarivo Avaradrano",
        str_detect(district_name, "Antananarivo Renivoh") ~ "Antananarivo Renivohitra",
        str_detect(district_name, "Fenoarivo Atsinanana") ~ "Fenerive Est",
        str_detect(district_name, "Mananara Avaratra") ~ "Mananara-Avaratra",
        str_detect(district_name, "Nosy Boraha") ~ "Sainte Marie",
        str_detect(district_name, "Ambovombe Androy") ~ "Ambovombe-Androy",
        str_detect(district_name, "Tsiombe") ~ "Tsihombe",
        str_detect(district_name, "Amboasary Atsimo") ~ "Amboasary-Atsimo",
        str_detect(district_name, "Ankazoabo Atsimo") ~ "Ankazoabo",
        str_detect(district_name, "Toliara I") ~ "Toliary-I",
        str_detect(district_name, "Toliara II") ~ "Toliary-II",
        str_detect(district_name, "Toliara-I") ~ "Toliary-I",
        str_detect(district_name, "Toliara-II") ~ "Toliary-II",
        str_detect(district_name, "Midongy Atsimo") ~ "Midongy-Atsimo",
        str_detect(district_name, "Antanambao Manampont") ~ "Antanambao Manampontsy",
        str_detect(district_name, "Antanambao Manampotsy") ~ "Antanambao Manampontsy",
        str_detect(district_name, "Vohibinany") ~ "Brickaville",
        str_detect(district_name, "Ambatoboeny") ~ "Ambato Boeni",
        str_detect(district_name, "FenoarivoBe") ~ "Fenoarivobe",
        str_detect(district_name, "Nosy Be") ~ "Nosy-Be",
        str_detect(district_name, "Fianarantsoa II") ~ "Fianarantsoa I",
        str_detect(district_name, "lalangina") ~ "Lalangina",
        str_detect(district_name, "Belo Tsiribihina") ~ "Belo Sur Tsiribihina",
        str_detect(district_name, "Vohimarina") ~ "Vohemar",
        str_detect(district_name, "Befandriana Avaratra") ~ "Befandriana Nord",
        str_detect(district_name, "Boriziny") ~ "Port-Berge (Boriziny-Vaovao)",
        str_detect(district_name, "Nosy Varika") ~ "Nosy-Varika",
        TRUE ~ district_name
      )
    ) %>%

    # A number of communes in the districts of Fianarantsoa and Toliara
    # have been reclassifed under new district named (e., Lalangina), requiring
    # that the district names for these communes be manually updated.

    mutate(
      district_name = ifelse(
        commune_name == "Alakamisy Ambohimahy" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Alakamisy Itenina" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambalakely" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambalamahasoa" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambalamidera" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambohimahavelona" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ambolofoty" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Anakao" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Analamisampy" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andianjanto Est" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andoharanomaintso" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andrainjanto Centre" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranohinaly" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranomiditra" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranovorivato" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andranovory" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Andribavontsona" &
          district_name == "Port-Berge (Boriziny-Vaovao),",
        "Analalava",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Androy" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Anjoma-tsara" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankarinarivo" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankaromalaza Mifanas" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankililoaka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ankilimalinika" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Antanamalaza" &
          district_name == "Antsirabe II",
        "Ambatolampy",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Antanambao Ambary" &
          district_name == "Betafo",
        "Mandoto",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Antsahavaribe" &
          district_name == "Vohemar",
        "Sambava",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Beheloka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Behompy" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Belalanda" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Betsinjaka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Fandravandava" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Fanjakana" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ialananidro" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Iavinomby" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ihazoara" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Isorana" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Ivoamba" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahaditra" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahasoabe" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahatsinjo" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mahatsinjony" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Maneva" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Manombo" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Manorofify" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "MarofotyMarofoty" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Maromiandra" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Miary" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Milenaka" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Mitsinjo" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Nasandratrony" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Sahambavy" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Soaindrana" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Soalara" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Soatanana" &
          district_name == "Fianarantsoa I",
        "Isandra",
        district_name
      ),
      district_name = ifelse(
        commune_name == "St Augustin" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Taindambo" &
          district_name == "Fianarantsoa I",
        "Lalangina",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Talata Ampano" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Tsianisiha" &
          district_name == "Toliara-I",
        "Toliary-II",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Vohibato Ouest" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Vohimarina" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      ),
      district_name = ifelse(
        commune_name == "Vohitrafeno" &
          district_name == "Fianarantsoa I",
        "Vohibato",
        district_name
      )
    ) %>%

    mutate(
      commune_name = case_when(
        str_detect(commune_name, "Alakamisy Ambohimahy") ~ "Alakamisy Ambohimaha",
        str_detect(commune_name, "Alakamisy Itenina") ~ "Alakamisy Itenina",
        str_detect(commune_name, "Ambadrika") ~ "Ambandrika",
        str_detect(commune_name, "Ambalakely") ~ "Ambalakely",
        str_detect(commune_name, "Ambalamahasoa") ~ "Ambalamahasoa",
        str_detect(commune_name, "Ambalamanasy   II") ~ "Ambalamanasy II",
        str_detect(commune_name, "Ambalamidera") ~ "Ambalamidera II",
        str_detect(commune_name, "AmbalapaisoII") ~ "Ambalapaiso II",
        str_detect(commune_name, "Ambararatabe /Nord") ~ "Ambararatabe Nord",
        str_detect(commune_name, "Ambarijeby Atsimo") ~ "Ambarijeby Sud",
        str_detect(commune_name, "Ambatoben'anja") ~ "Ambatoben'anjavy",
        str_detect(commune_name, "AmbatofisakaII") ~ "Ambatofisaka II",
        str_detect(commune_name, "AmbatoharananaI") ~ "Ambatoharanana",
        str_detect(commune_name, "Ambatolampy Tsimahaf") ~ "Ambatolampy",
        str_detect(commune_name, "Ambatolampy Tsimahafotsy") ~ "Ambatolampy",
        str_detect(commune_name, "Ambatoriha/Est") ~ "Ambatoriha Est",
        str_detect(commune_name, "Ambatotsipihana") ~ "Ambatotsipihina",
        str_detect(commune_name, "Ambatovala") ~ "Ambatolava",
        str_detect(commune_name, "Ambatry") ~ "Ambatry Mitsinjo",
        str_detect(commune_name, "Ambinanin'Andravory") ~ "Ambinanin'andravory",
        str_detect(commune_name, "Ambinaninandro") ~ "Ambinanindrano",
        str_detect(commune_name, "Ambinaniroa-Andonaka") ~ "Ambinaniroa",
        str_detect(commune_name, "Ambodiadabo Maitsokely") ~ "Ambodiadabo",
        str_detect(commune_name, "Ambodiadabo") ~ "Ambodiadabo M",
        str_detect(commune_name, "Ambodiampana Lokoho") ~ "Ambodiampana",
        str_detect(commune_name, "Ambodiampanana") ~ "Ambodiampana",
        str_detect(commune_name, "Ambodifarihy") ~ "Ambodifarihy Fenomanana",
        str_detect(commune_name, "Ambodihazambo") ~ "Ambodihazoambo",
        str_detect(commune_name, "Ambodimanga  I") ~ "Ambodimanga I",
        str_detect(commune_name, "Ambodimanga II-B") ~ "Ambodimanga II",
        str_detect(commune_name, "Ambodimotso Atsimo") ~ "Ambodimotso Sud",
        str_detect(commune_name, "AmbodinonokaAntaratr") ~ "Ambodinonoka",
        str_detect(commune_name, "Ambodirian'Isahafary") ~ "Ambodirian'i Sahafary",
        str_detect(commune_name, "Amboditandroho") ~ "Amboditandroroho",
        str_detect(commune_name, "Ambohibao Atsimo") ~ "Ambohibao Sud",
        str_detect(commune_name, "Ambohibary") ~ "Ambohibary Vohilena",
        str_detect(commune_name, "Ambohijato Mandritsara") ~ "Mandritsara",
        str_detect(commune_name, "Ambohimahavelona") ~ " Ambohimahavelona",
        str_detect(commune_name, "Ambohimalaza") ~ "Ambohimalaza Miray",
        str_detect(commune_name, "Ambohimàna") ~ "Ambohimana",
        str_detect(commune_name, "Ambohimanga Sud") ~ "Ambohimanga Du Sud",
        str_detect(commune_name, "Ambohimanjaka") ~ "Sahatsiho Ambohimanjaka",
        str_detect(commune_name, "AmbohimiarinaII") ~ "Ambohimiarina II",
        str_detect(commune_name, "Ambohitralalana") ~ "Ambohitralanana",
        str_detect(commune_name, "Ambohitrandriamanitr") ~ "Ambohitrandriamanitra",
        str_detect(commune_name, "AmbohitsaraEst") ~ "Ambohitsara Est",
        str_detect(commune_name, "Ambolidibe Atsinanana") ~ "Ambolidibe Est",
        str_detect(commune_name, "Ambolofoty") ~ "Ambolofoty",
        str_detect(commune_name, "Amboropotsy") ~ "Amborompotsy",
        str_detect(commune_name, "Ampasimadinika") ~ "Ampasimadinika Manambolo",
        str_detect(commune_name, "Ampasimborajka") ~ "Ampasimboraka",
        str_detect(commune_name, "Ampasimpotsy") ~ "Ampasimpotsy Sud",
        str_detect(commune_name, "Ampasipotsy Gare") ~ "Ampasimpotsy Gara",
        str_detect(commune_name, "Ampasipotsy Madialaz") ~ "Ampasipotsy Mandialaza",
        str_detect(commune_name, "Ampataka Manampaneva") ~ "Manampaneva",
        str_detect(commune_name, "Ampataka Maroreny") ~ "Ampatakamaroreny",
        str_detect(commune_name, "Anakao") ~ "Anakao",
        str_detect(commune_name, "Analalaiva") ~ "Analaiva",
        str_detect(commune_name, "Analamisampy") ~ "Analamisampy",
        str_detect(commune_name, "Analamitsivala") ~ "Analamitsivalana",
        str_detect(commune_name, "Anbatomainty") ~ "Ambatomainty",
        str_detect(commune_name, "Andanandava") ~ "Antanandava",
        str_detect(commune_name, "Andianjanto Est") ~ "Andrainjato Est",
        str_detect(commune_name, "Andimaka") ~ "Andimaky Manambolo",
        str_detect(commune_name, "Andoharanomaintso") ~ "Andoharanomaitso",
        str_detect(commune_name, "Andoharanomaintso") ~ "Andoharanomaitso",
        str_detect(commune_name, "Andrainjanto Centre") ~ "Andrainjato Centre",
        str_detect(commune_name, "Andranohinaly") ~ "Andranohinaly",
        str_detect(commune_name, "Andranomiditra") ~ "Andranomiditra",
        str_detect(commune_name, "Andranomiely") ~ "Rambolamasoandro Andranomiely",
        str_detect(commune_name, "Andranovorivato") ~ "Andranovorivato",
        str_detect(commune_name, "Andranovory") ~ "Andranovory",
        str_detect(commune_name, "Andravola") ~ "Andravola Vohipeno",
        str_detect(commune_name, "Andrebakely") ~ "Andrebakely Nord",
        str_detect(commune_name, "Andribavontsona") ~ "Andribavontsona",
        str_detect(commune_name, "Androndrona") ~ "Androndrono",
        str_detect(commune_name, "Androy") ~ "Androy",
        str_detect(commune_name, "Anjapaly") ~ "Anjampaly",
        str_detect(commune_name, "Anjeke Ankilira") ~ "Anjeky Ankilikira",
        str_detect(commune_name, "Anjeva Gare") ~ "Anjeva Gara",
        str_detect(commune_name, "Anjiabe") ~ "Anjiabe Ambony",
        str_detect(commune_name, "Anjiaija") ~ "Anjiajia",
        str_detect(commune_name, "Anjoman'Ankona") ~ "Anjoman'ankona",
        str_detect(commune_name, "Anjoma-tsara") ~ "Anjoma Itsara",
        str_detect(commune_name, "Ankadinondry") ~ "Ankadinondry Sakay",
        str_detect(commune_name, "Ankafina") ~ "Ankafina Tsarafidy",
        str_detect(commune_name, "Ankarinarivo") ~ "Ankarinarivo Manirisoa",
        str_detect(commune_name, "Ankaromalaza Mifanas") ~ "Ankaromalaza Mifanasoa",
        str_detect(commune_name, "Ankasakasa") ~ "Ankasakasa Tsibiray",
        str_detect(commune_name, "Ankazoabo") ~ "Ankazoabo Sud",
        str_detect(commune_name, "Ankazotokana I") ~ "Ankazotokana",
        str_detect(commune_name, "Ankiabe Salohy") ~ "Ankiabe-Salohy",
        str_detect(commune_name, "Ankiakabe-Nord") ~ " Ankiakabe Nord",
        str_detect(commune_name, "Ankililoaka") ~ "Ankililoaka",
        str_detect(commune_name, "Ankilimalinika") ~ "Ankilimalinike",
        str_detect(commune_name, "Ankirondro") ~ "Bemarivo Ankirondro",
        str_detect(commune_name, "Anontsibe") ~ "Anontsibe Centre",
        str_detect(commune_name, "Anosiarivo") ~ "Anosiarivo I",
        str_detect(commune_name, "Anosy Tsararafara") ~ "Anosy Tsararafa",
        str_detect(commune_name, "Antalaha") ~ " Antalaha Ambonivohitra",
        str_detect(commune_name, "Antanamalaza") ~ "Antanamalaza",
        str_detect(commune_name, "Antanambao Ambary") ~ "Antanambao Ambary",
        str_detect(commune_name, "Antanambao I") ~ "Antanambao",
        str_detect(commune_name, "Antanambao Manampotsy") ~ "Antanambao Manampontsy",
        str_detect(commune_name, "Antanambaon'Amberina") ~ "Antanambaon'amberina",
        str_detect(commune_name, "Antananarivo I") ~ "1er Arrondissement",
        str_detect(commune_name, "Antananarivo II") ~ "2e Arrondissement",
        str_detect(commune_name, "Antananarivo III") ~ "3e Arrondissement",
        str_detect(commune_name, "Antananarivo IV") ~ "4e Arrondissement",
        str_detect(commune_name, "Antananarivo V") ~ "5e Arrondissement",
        str_detect(commune_name, "Antananarivo VI") ~ "6e Arrondissement",
        str_detect(commune_name, "Antanandava Nord") ~ "Antanandava",
        str_detect(commune_name, "Antananivo /Haut") ~ "Antananivo Haut",
        str_detect(commune_name, "Antanetibe Mahazaza") ~ "Antanetibe",
        str_detect(commune_name, "Antanimora- Sud") ~ "Antanimora Atsimo",
        str_detect(commune_name, "Antenina I") ~ "Antenina",
        str_detect(commune_name, "Antoby") ~ "Antoby Est",
        str_detect(commune_name, "Antohaboto") ~ "Antohabato",
        str_detect(commune_name, "Antongo") ~ "Antongo Vaovao",
        str_detect(commune_name, "Antokoboritelo") ~ "Marovitsika Sud",
        str_detect(commune_name, "Antranonkarany") ~ "Antranokarany",
        str_detect(commune_name, "Antsahavaribe") ~ "Antsahavaribe",
        str_detect(commune_name, "Antsakomanondro") ~ "Antsakoamanondro",
        str_detect(commune_name, "Antsapanimahazo") ~ "Antsampanimahazo",
        str_detect(commune_name, "Antsirabe I") ~ "Antsirabe Afovoany Atsinanana",
        str_detect(commune_name, "Antsiranana I") ~ "Diego Suarez",
        str_detect(commune_name, "Antsoantany") ~ "Antsoatany",
        str_detect(commune_name, "Bealampoana") ~ "Bealampona",
        str_detect(commune_name, "Bealanana I") ~ "Bealanana",
        str_detect(commune_name, "Beampombo  I") ~ "Beampombo I",
        str_detect(commune_name, "Beandrarezona I") ~ "Beandrarezona",
        str_detect(commune_name, "Befandriana Avaratra") ~ "Befandriana Nord",
        str_detect(commune_name, "Befandriana-Sud") ~ "Befandriana Sud",
        str_detect(commune_name, "Befetra") ~ "Befeta",
        str_detect(commune_name, "Befotaka Avaratra") ~ "Befotaka Nord",
        str_detect(commune_name, "Befotaka") ~ "Befotaka Sud",
        str_detect(commune_name, "Beheloka") ~ "Beheloka",
        str_detect(commune_name, "Behera") ~ "Behara",
        str_detect(commune_name, "Behompy") ~ "Behompy",
        str_detect(commune_name, "Belafika Haut") ~ "Belafike Haut",
        str_detect(commune_name, "Belalanda") ~ "Belalanda",
        str_detect(commune_name, "Belambo") ~ "Belambo Firaisana",
        str_detect(commune_name, "Belaoko Marovato") ~ "Belaoka Marovato",
        str_detect(commune_name, "Belo sur Mer") ~ "Belo Sur Mer",
        str_detect(commune_name, "Belo Tsiribihina") ~ "Belo Sur Tsiribihina",
        str_detect(commune_name, "Belotsiribihina") ~ "Belo Sur Tsiribihina",
        str_detect(commune_name, "Bemaneviky H") ~ "Bemaneviky Haut Sambirano",
        str_detect(commune_name, "BenatoToby") ~ "Benato Toby",
        str_detect(commune_name, "Mangarivot") ~ "Mangarivotra",
        str_detect(commune_name, "Beraketa") ~ "Bereketa",
        str_detect(commune_name, "Berevo Ranobe") ~ "Berevo/ranobe",
        str_detect(commune_name, "Beroy Sud") ~ "Beroy Atsimo",
        str_detect(commune_name, "Betioky Sud") ~ "Betioky Atsimo",
        str_detect(commune_name, "Betsakotsako Andrano") ~ "Betsakotsako Andranotsara",
        str_detect(commune_name, "Betsimiositra") ~ "Betsimisotra",
        str_detect(commune_name, "Betsinjaka") ~ "Betsinjaka",
        str_detect(commune_name, "Bevoay Beretra") ~ " Beretra Bevoay",
        str_detect(commune_name, "Bevonotro") ~ "Bevonotra",
        str_detect(commune_name, "Efatsy Anandroza") ~ "Efatsy",
        str_detect(commune_name, "Enakara Haut") ~ "Enakara-Haut",
        str_detect(commune_name, "Enaniiliha") ~ "Enaniliha",
        str_detect(commune_name, "Ereda") ~ "Erada",
        str_detect(commune_name, "Etrotroka") ~ "Etrotroka Atsimo",
        str_detect(commune_name, "Fandravandava") ~ "Fandrandava",
        str_detect(commune_name, "Fanjakana") ~ "Fanjakana",
        str_detect(commune_name, "Faux-Cap") ~ "Betanty (Faux Cap)",
        str_detect(commune_name, "Fenoevo") ~ "Fenoevo-Efita",
        str_detect(commune_name, "Fieferana") ~ "Fiaferana",
        str_detect(commune_name, "Foulpointe") ~ "Mahavelona (Foulpointe)",
        str_detect(commune_name, "Ialananidro") ~ "Ialananindro",
        str_detect(commune_name, "Iavinomby") ~ "Iavonomby Vohibola",
        str_detect(commune_name, "Ibity") ~ "Alatsinainy Ibity",
        str_detect(commune_name, "Ihaborano Namohora") ~ "Namohora Iaborano",
        str_detect(commune_name, "Ihazoara") ~ "Ihazoara",
        str_detect(commune_name, "Iloto") ~ "Menamaty Iloto",
        str_detect(commune_name, "Imady") ~ "Imerina Imady",
        str_detect(commune_name, "Imeritsiatosika") ~ "Imerintsiatosika",
        str_detect(commune_name, "Isaka Ivondro") ~ "Isaka-Ivondro",
        str_detect(commune_name, "Isaraha") ~ "Isahara",
        str_detect(commune_name, "Isorana") ~ "Isorana",
        str_detect(commune_name, "Ivatana") ~ "Vatana",
        str_detect(commune_name, "Ivato Aéroport") ~ "Ivato Aeroport",
        str_detect(commune_name, "Ivoamba") ~ "Ivoamba",
        str_detect(commune_name, "Ivony") ~ "Ivony Miaramiasa",
        str_detect(commune_name, "Kalalao") ~ "Ikalalao",
        str_detect(commune_name, "Kianjandrandrakefina") ~ "Kianjandrakefina",
        str_detect(commune_name, "labohazo") ~ "Iabohazo",
        str_detect(commune_name, "Lavaraty Ivondro") ~ "Ivondro",
        str_detect(commune_name, "Mahaditra") ~ "Mahaditra",
        str_detect(commune_name, "Mahafasa") ~ "Mahafasa Centre",
        str_detect(commune_name, "Mahajanga I") ~ "Mahajanga",
        str_detect(commune_name, "Mahasoabe") ~ "Mahasoabe",
        str_detect(commune_name, "Mahatsara Lefaka") ~ "Mahatsara Iefaka",
        str_detect(commune_name, "Mahatsinjo Atsinanana") ~ "Mahatsinjo Est",
        str_detect(commune_name, "Mahatsinjo") ~ "Mahatsinjony",
        str_detect(commune_name, "Mahatsinjony") ~ "Mahatsinjony",
        str_detect(commune_name, "Mahazina") ~ "Mahazina Ambohipierenana",
        str_detect(commune_name, "Manajary Urbain") ~ "Mananjary",
        str_detect(commune_name, "Manakambahiny Est") ~ "Manakambahiny Antsinanana",
        str_detect(commune_name, "Manakambahiny Ouest") ~ "Manakambahiny Andrefana",
        str_detect(commune_name, "Manakara") ~ "Manakara",
        str_detect(commune_name, "Manambotra Sud") ~ "Manambotra Atsimo",
        str_detect(commune_name, "Manapatrana") ~ "Manampatrana",
        str_detect(commune_name, "Mandromodromotra") ~ "Mandromondromotra",
        str_detect(commune_name, "Maneva") ~ "Maneva",
        str_detect(commune_name, "Manombo") ~ "Manombo Sud",
        str_detect(commune_name, "Manorofify") ~ "Manorofify",
        str_detect(commune_name, "Marintampona") ~ "Maritampona",
        str_detect(commune_name, "Marivorahona") ~ "Tanambao Marivorahona",
        str_detect(commune_name, "Maroarivo") ~ "Maroarivo Ankazomanga",
        str_detect(commune_name, "MarofotyMarofoty") ~ "Marofoty",
        str_detect(commune_name, "Maromiandra") ~ "Maromiandra",
        str_detect(commune_name, "Maromokotra-Loky") ~ "Maromokotra Loky",
        str_detect(commune_name, "Marosavoa Bas") ~ "Marosavoa",
        str_detect(commune_name, "Marovitsika") ~ "Marovitsika Sud",
        str_detect(commune_name, "Merimandroso") ~ "Imerimandroso",
        str_detect(commune_name, "Miary") ~ "Miary Ambohibola",
        str_detect(commune_name, "Milenaka") ~ "Milenaka",
        str_detect(commune_name, "Mitsinjo") ~ "Mitsinjo Betanimena",
        str_detect(commune_name, "Mizilo Gare") ~ "Mizilo Gara",
        str_detect(commune_name, "Moramanga Urbain") ~ "Moramanga",
        str_detect(commune_name, "Morarano Gare") ~ "Morarano Gara",
        str_detect(commune_name, "Morombe") ~ "Cu Morombe",
        str_detect(commune_name, "Nagnarena") ~ "Nanarena Besakoa",
        str_detect(commune_name, "Nasandratrony") ~ "Nasandratrony",
        str_detect(commune_name, "Niarovana") ~ "Niarovana Marosampanana",
        str_detect(commune_name, "Nosibe Masianaka") ~ "Masianaka",
        str_detect(commune_name, "Onilhy") ~ "Onilahy",
        str_detect(commune_name, "Port Bergé I") ~ "Port Berge",
        str_detect(commune_name, "Port Bergé II") ~ "Port Berge II",
        str_detect(commune_name, "Rantabe Est") ~ "Rantabe",
        str_detect(commune_name, "Rantabe Sud") ~ "Rantabe",
        str_detect(commune_name, "Razanaka") ~ "Vohipeno Razanaka",
        str_detect(commune_name, "Sahamadio") ~ "Sahamadio Fisakana",
        str_detect(commune_name, "Sahambavy") ~ "Sahambavy",
        str_detect(commune_name, "Sahambo") ~ "Sahambano",
        str_detect(commune_name, "Sahanivotry Atsimo") ~ "Sahanivotry Manandona",
        str_detect(commune_name, "Sakamahily-Ouest") ~ "Sakamahily",
        str_detect(commune_name, "Sakay") ~ "Tanamarina Sakay",
        str_detect(commune_name, "Sakona") ~ "Sakoana",
        str_detect(commune_name, "Sambava Urbain") ~ "Sambava Cu",
        str_detect(commune_name, "Sarobaratra") ~ "Sarobaratra Ifanja",
        str_detect(commune_name, "Soaindrana") ~ "Soaindrana",
        str_detect(commune_name, "Soalara") ~ "Soalara Sud",
        str_detect(commune_name, "Soatanana") ~ "Soatanana",
        str_detect(commune_name, "St Augustin") ~ "Saint Augustin",
        str_detect(commune_name, "Taindambo") ~ "Taindambo",
        str_detect(commune_name, "Talata Ampano") ~ "Tatala Ampano",
        str_detect(commune_name, "Talatan'Angavo") ~ "Talata Angavo",
        str_detect(commune_name, "Taolagnaro") ~ "Fort-Dauphin",
        str_detect(commune_name, "Tanakamba") ~ "Tanakambana",
        str_detect(commune_name, "Tanambao  Daoud") ~ "Tanambao Daoud",
        str_detect(commune_name, "Tanambaovatrakaka") ~ "Tanambao Vahatrakaka",
        str_detect(commune_name, "Tanandava-Sud") ~ "Tanandava Sud",
        str_detect(commune_name, "Tanandrano") ~ "Tandrano",
        str_detect(commune_name, "Toamasina Suburbain") ~ "Toamasina Suburbaine",
        str_detect(commune_name, "Tovòna") ~ "Tovona",
        str_detect(commune_name, "Tsarahonenana") ~ "Tsarahonenana Sahanivotry",
        str_detect(commune_name, "Tsarajomoko") ~ "Tsarajomoka",
        str_detect(commune_name, "Tsaratanana") ~ "Tsaratanana I",
        str_detect(commune_name, "Tsiafajavona Ankarat") ~ "Tsiafajavona Ankaratra",
        str_detect(commune_name, "Tsianisiha") ~ "Tsianisiha",
        str_detect(commune_name, "Tsianofàna") ~ "Tsianofana",
        str_detect(commune_name, "Tsinjoarivo") ~ "Tsinjoarivo Imanga",
        str_detect(commune_name, "Tsiombe") ~ "Tsihombe",
        str_detect(commune_name, "Tsiroanomadidy Ville") ~ "Tsiroanomandidy Fihaonana",
        str_detect(commune_name, "Tsiroanomandidy Ville") ~ "Tsiroanomandidy Fihaonana",
        str_detect(commune_name, "Vatolatsaky") ~ "Vatolatsaka",
        str_detect(commune_name, "Vilihazo") ~ "Viliahazo",
        str_detect(commune_name, "Vinaninony Avaratra") ~ "Vinaninony Atsimo",
        str_detect(commune_name, "Vineta Andamasiny") ~ "Andamasiny Vineta",
        str_detect(commune_name, "Vohibato Ouest") ~ "Vohibato Ouest",
        str_detect(commune_name, "Vohimarina") ~ "Vohimarina",
        str_detect(commune_name, "Vohitrafeno") ~ "Vohitrafeno",
        str_detect(commune_name, "Zomabealoka") ~ "Zoma Bealoka",
        TRUE ~ commune_name
      )
    ) %>%
    unique()

}

```

```{r facility-name-standardization-application_1, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

facilities_all <- data_mh %>%
  rename(region_name = region,
         district_name = district,
         commune_name = commune) %>%
  clean_clinic_type() %>%
  clean_clinic_name() %>%
  clean_catchment_area()

```

A summary of the standardization changes is provided below.

\begin{spacing}{1}

\addcontentsline{lot}{table}{Table S2.6: Standardization of region names.}

``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

column2 <- data_mh %>% select(commune, district, region) %>% unique()
column1 <- facilities_all %>% select(region_name, district_name, commune_name) %>% unique()

r_old <- column1 %>% select(region_name) %>% unique()
r_new <- column2 %>% select(region) %>% unique()

cbind(r_old, r_new) %>% mutate(test = region_name == region) %>%
  filter(test == FALSE) %>%
  relocate(region, .before = region_name) %>%
  rename("Name in data" = region,
         "Standardized name" = region_name) %>%
  select(!test) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.6: Standardization of region names**"))

```

\addcontentsline{lot}{table}{Table S2.7: Standardization of district names.}

``` {r table_standardization_district_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

district_old <- c("Anosibe An'Ala", "Antananarivo Atsimon", "Antananarivo Avaradr", "Antananarivo Renivoh", "Fenoarivo Atsinanana", "Mananara Avaratra", "Nosy Boraha", "Ambovombe Androy", "Tsiombe", "Amboasary Atsimo", "Ankazoabo Atsimo", "Toliara I", "Toliara II", "Toliara-I", "Toliara-II", "Midongy Atsimo", "Antanambao Manampont", "Antanambao Manampotsy", "Vohibinany", "Ambatoboeny", "FenoarivoBe", "Nosy Be", "Fianarantsoa II", "lalangina", "Belo Tsiribihina", "Vohimarina", "Befandriana Avaratra", "Boriziny", "Nosy Varika")

district_new <- c("Anosibe-An'ala", "Antananarivo Atsimondrano", "Antananarivo Avaradrano", "Antananarivo Renivohitra", "Fenerive Est", "Mananara-Avaratra", "Sainte Marie", "Ambovombe-Androy", "Tsihombe", "Amboasary-Atsimo", "Ankazoabo", "Toliary-I", "Toliary-II", "Toliary-I", "Toliary-II", "Midongy-Atsimo", "Antanambao Manampontsy", "Antanambao Manampontsy", "Brickaville", "Ambato Boeni", "Fenoarivobe", "Nosy-Be", "Fianarantsoa I", "Lalangina", "Belo Sur Tsiribihina", "Vohemar", "Befandriana Nord", "Port-Berge (Boriziny-Vaovao)", "Nosy-Varika")

as.data.frame(cbind(district_old, district_new)) %>%
  arrange(district_old) %>%
  rename("Name in data" = district_old,
         "Standardized name" = district_new) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.7: Standardization of district names**")) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )
```

\addcontentsline{lot}{table}{Table S2.8: Standardization of district names, based on commune name.}

``` {r table_standardization_district_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

district_tobechanged <- c("Antsirabe II", "Port-Berge (Boriziny-Vaovao)", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Betafo", "Vohemar", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I")

district_communes_affected <- c("Antanamalaza", "Andribavontsona", "Ambalamidera", "Andoharanomaintso", "Anjoma-tsara", "Ankarinarivo", "Fanjakana", "Iavinomby", "Isorana", "Nasandratrony", "Soatanana", "Alakamisy Ambohimahy", "Ambalakely", "Ambalamahasoa", "Andianjanto Est", "Andrainjanto Centre", "Androy", "Fandravandava", "Ialananidro", "Ivoamba", "Mahatsinjo", "Mahatsinjony", "Sahambavy", "Taindambo", "Antanambao Ambary", "Antsahavaribe", "Ambohimahavelona", "Ambolofoty", "Anakao", "Analamisampy", "Andranohinaly", "Andranovory", "Ankililoaka", "Ankilimalinika", "Beheloka", "Behompy", "Belalanda", "Betsinjaka", "Manombo", "Manorofify", "MarofotyMarofoty", "Maromiandra", "Miary", "Milenaka", "Mitsinjo", "Soalara", "St Augustin", "Tsianisiha", "Alakamisy Itenina", "Andranomiditra", "Andranovorivato", "Ankaromalaza Mifanas", "Ihazoara", "Mahaditra", "Mahasoabe", "Maneva", "Soaindrana", "Talata Ampano", "Vohibato Ouest", "Vohimarina", "Vohitrafeno")

district_changed <- c("Ambatolampy", "Analalava", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Mandoto", "Sambava", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato")

as.data.frame(cbind(district_tobechanged, district_changed, district_communes_affected)) %>%
  arrange(district_tobechanged) %>%
  relocate(district_communes_affected, .before = district_tobechanged) %>%
  rename("District name in data" = district_tobechanged,
         "Communes" = district_communes_affected,
         "District name, updated" = district_changed) %>%
  gt() %>% 
  tab_header(
    title = md("**Table S2.8: Standardization of district names, based on commune name**")) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )

```
\addcontentsline{lot}{table}{Table S2.9: Standardization of commune names.}

``` {r table_standardization_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}

commune_old <- c("Alakamisy Ambohimahy", "Alakamisy Itenina", "Ambadrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy   II", "Ambalamidera", "AmbalapaisoII", "Ambararatabe /Nord",
                 "Ambarijeby Atsimo", "Ambatoben'anja", "AmbatofisakaII", "AmbatoharananaI", "Ambatolampy Tsimahaf", "Ambatolampy Tsimahafotsy", "Ambatoriha/Est", "Ambatotsipihana", 
                 "Ambatovala", "Ambatry", "Ambinanin'Andravory", "Ambinaninandro", "Ambinaniroa-Andonaka", "Ambodiadabo Maitsokely", "Ambodiadabo", "Ambodiampana Lokoho",
                 "Ambodiampanana", "Ambodifarihy", "Ambodihazambo", "Ambodimanga  I", "Ambodimanga II-B", "Ambodimotso Atsimo", "AmbodinonokaAntaratr", "Ambodirian'Isahafary",
                 "Amboditandroho", "Ambohibao Atsimo", "Ambohibary", "Ambohijato Mandritsara", "Ambohimahavelona", "Ambohimalaza", "Ambohimàna", "Ambohimanga Sud",
                 "Ambohimanjaka", "AmbohimiarinaII", "Ambohitralalana", "Ambohitrandriamanitr", "AmbohitsaraEst", "Ambolidibe Atsinanana", "Ambolofoty", "Amboropotsy",
                 "Ampasimadinika", "Ampasimborajka", "Ampasimpotsy", "Ampasipotsy Gare", "Ampasipotsy Madialaz", "Ampataka Manampaneva", "Ampataka Maroreny", "Anakao",
                 "Analalaiva", "Analamisampy", "Analamitsivala", "Anbatomainty", "Andanandava", "Andianjanto Est", "Andimaka", "Andoharanomaintso", "Andoharanomaintso",
                 "Andrainjanto Centre", "Andranohinaly", "Andranomiditra", "Andranomiely", "Andranovorivato", "Andranovory", "Andravola", "Andrebakely", "Andribavontsona",
                 "Androndrona", "Androy", "Anjapaly", "Anjeke Ankilira", "Anjeva Gare", "Anjiabe", "Anjiaija", "Anjoman'Ankona", "Anjoma-tsara", "Ankadinondry", "Ankafina",
                 "Ankarinarivo", "Ankaromalaza Mifanas", "Ankasakasa", "Ankazoabo", "Ankazotokana I", "Ankiabe Salohy", "Ankiakabe-Nord", "Ankililoaka", "Ankilimalinika",
                 "Ankirondro", "Anontsibe", "Anosiarivo", "Anosy Tsararafara", "Antalaha", "Antanamalaza", "Antanambao Ambary", "Antanambao I", "Antanambao Manampotsy",
                 "Antanambaon'Amberina", "Antananarivo I", "Antananarivo II", "Antananarivo III", "Antananarivo IV", "Antananarivo V", "Antananarivo VI", "Antanandava Nord",
                 "Antananivo /Haut", "Antanetibe Mahazaza", "Antanimora- Sud", "Antenina I", "Antoby", "Antohaboto", "Antongo", "Antokoboritelo", "Antranonkarany", "Antsahavaribe",
                 "Antsakomanondro", "Antsapanimahazo", "Antsirabe I", "Antsiranana I", "Antsoantany", "Bealampoana", "Bealanana I", "Beampombo  I", "Beandrarezona I",
                 "Befandriana Avaratra", "Befandriana-Sud", "Befetra", "Befotaka Avaratra", "Befotaka", "Beheloka", "Behera", "Behompy", "Belafika Haut", "Belalanda",
                 "Belambo", "Belaoko Marovato", "Belo sur Mer", "Belo Tsiribihina", "Belotsiribihina", "Bemaneviky H", "BenatoToby", "Beraketa", "Berevo Ranobe",
                 "Beroy Sud", "Betioky Sud", "Betsakotsako Andrano", "Betsimiositra", "Betsinjaka", "Bevoay Beretra", "Bevonotro", "Efatsy Anandroza", "Enakara Haut",
                 "Enaniiliha", "Ereda", "Etrotroka", "Fandravandava", "Fanjakana", "Faux-Cap", "Fenoevo", "Fieferana", "Foulpointe", "Ialananidro", "Iavinomby", "Ibity",
                 "Ihaborano Namohora", "Ihazoara", "Iloto", "Imady", "Imeritsiatosika", "Isaka Ivondro", "Isaraha", "Isorana", "Ivatana", "Ivato Aéroport", "Ivoamba",
                 "Ivony", "Kalalao", "Kianjandrandrakefina", "labohazo", "Lavaraty Ivondro", "Mahaditra", "Mahafasa", "Mahajanga I", "Mahasoabe", "Mahatsara Lefaka",
                 "Mahatsinjo Atsinanana", "Mahatsinjo", "Mahatsinjony", "Mahazina", "Manajary Urbain", "Manakambahiny Est", "Manakambahiny Ouest", "Manakara(com)",
                 "Manambotra Sud", "Manapatrana", "Mandromodromotra", "Maneva", "Mangarivot", "Manombo", "Manorofify", "Marintampona", "Marivorahona", "Maroarivo", 
                 "MarofotyMarofoty", "Maromiandra", "Maromokotra-Loky", "Marosavoa Bas", "Marovitsika", "Merimandroso", "Miary", "Milenaka", "Mitsinjo", "Mizilo Gare", 
                 "Moramanga Urbain", "Morarano Gare", "Morombe", "Nagnarena", "Nasandratrony", "Niarovana", "Nosibe Masianaka", "Onilhy", "Port Bergé I", "Port Bergé II",
                 "Rantabe Est", "Rantabe Sud", "Razanaka", "Sahamadio", "Sahambavy", "Sahambo", "Sahanivotry Atsimo", "Sakamahily-Ouest", "Sakay", "Sakona", "Sambava Urbain",
                 "Sarobaratra", "Soaindrana", "Soalara", "Soatanana", "St Augustin", "Taindambo", "Talata Ampano", "Talatan'Angavo", "Taolognaro", "Tanakamba", "Tanambao  Daoud",
                 "Tanambaovatrakaka", "Tanandava-Sud", "Tanandrano", "Toamasina Suburbain", "Tovòna", "Tsarahonenana", "Tsarajomoko", "Tsaratanana", "Tsiafajavona Ankarat",
                 "Tsianisiha", "Tsianofàna", "Tsinjoarivo", "Tsiombe", "Tsiroanomadidy Ville", "Tsiroanomandidy Ville", "Vatolatsaky", "Vilihazo", "Vinaninony Avaratra",
                 "Vineta Andamasiny", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zomabealoka")

commune_new <- c("Alakamisy Ambohimaha", "Alakamisy Itenina", "Ambandrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy II", "Ambalamidera II", "Ambalapaiso II", "Ambararatabe Nord",
                 "Ambarijeby Sud", "Ambatoben'anjavy", "Ambatofisaka II", "Ambatoharanana", "Ambatolampy", "Ambatolampy", "Ambatoriha Est", "Ambatotsipihina", "Ambatolava", 
                 "Ambatry Mitsinjo", "Ambinanin'andravory", "Ambinanindrano", "Ambinaniroa", "Ambodiadabo", "Ambodiadabo M", "Ambodiampana", "Ambodiampana", "Ambodifarihy Fenomanana",
                 "Ambodihazoambo", "Ambodimanga I","Ambodimanga II", "Ambodimotso Sud", "Ambodinonoka", "Ambodirian'i Sahafary", "Amboditandroroho", "Ambohibao Sud",
                 "Ambohibary Vohilena", "Mandritsara", " Ambohimahavelona", "Ambohimalaza Miray", "Ambohimana", "Ambohimanga Du Sud", "Sahatsiho Ambohimanjaka",
                 "Ambohimiarina II", "Ambohitralanana", "Ambohitrandriamanitra", "Ambohitsara Est", "Ambolidibe Est", "Ambolofoty", "Amborompotsy", "Ampasimadinika Manambolo",
                 "Ampasimboraka", "Ampasimpotsy Sud", "Ampasimpotsy Gara", "Ampasipotsy Mandialaza", "Manampaneva", "Ampatakamaroreny", "Anakao", "Analaiva", "Analamisampy",
                 "Analamitsivalana", "Ambatomainty", "Antanandava", "Andrainjato Est", "Andimaky Manambolo", "Andoharanomaitso", "Andoharanomaitso", "Andrainjato Centre",
                 "Andranohinaly", "Andranomiditra", "Rambolamasoandro Andranomiely", "Andranovorivato", "Andranovory", "Andravola Vohipeno", "Andrebakely Nord", "Andribavontsona",
                 "Androndrono", "Androy", "Anjampaly", "Anjeky Ankilikira", "Anjeva Gara", "Anjiabe Ambony", "Anjiajia", "Anjoman'ankona", "Anjoma Itsara", "Ankadinondry Sakay",
                 "Ankafina Tsarafidy", "Ankarinarivo Manirisoa", "Ankaromalaza Mifanasoa", "Ankasakasa Tsibiray", "Ankazoabo Sud", "Ankazotokana", "Ankiabe-Salohy", " Ankiakabe Nord",
                 "Ankililoaka", "Ankilimalinike", "Bemarivo Ankirondro", "Anontsibe Centre", "Anosiarivo I", "Anosy Tsararafa", " Antalaha Ambonivohitra", "Antanamalaza", "Antanambao Ambary",
                 "Antanambao", "Antanambao Manampontsy", "Antanambaon'amberina", "1er Arrondissement", "2e Arrondissement", "3e Arrondissement", "4e Arrondissement", "5e Arrondissement",
                 "6e Arrondissement", "Antanandava", "Antananivo Haut", "Antanetibe", "Antanimora Atsimo", "Antenina", "Antoby Est", "Antohabato", "Antongo Vaovao", "Marovitsika Sud", "Antranokarany",
                 "Antsahavaribe", "Antsakoamanondro", "Antsampanimahazo", "Antsirabe Afovoany Atsinanana", "Diego Suarez", "Antsoatany", "Bealampona", "Bealanana", "Beampombo I",
                 "Beandrarezona", "Befandriana Nord", "Befandriana Sud", "Befeta", "Befotaka Nord", "Befotaka Sud", "Beheloka", "Behara", "Behompy", "Belafike Haut", "Belalanda",
                 "Belambo Firaisana", "Belaoka Marovato", "Belo Sur Mer", "Belo Sur Tsiribihina", "Belo Sur Tsiribihina", "Bemaneviky Haut Sambirano", "Benato Toby", "Bereketa", 
                 "Berevo/ranobe", "Beroy Atsimo", "Betioky Atsimo", "Betsakotsako Andranotsara", "Betsimisotra", "Betsinjaka", " Beretra Bevoay", "Bevonotra", "Efatsy", "Enakara-Haut",
                 "Enaniliha", "Erada", "Etrotroka Atsimo", "Fandrandava", "Fanjakana", "Betanty (Faux Cap)", "Fenoevo-Efita", "Fiaferana", "Mahavelona (Foulpointe)", "Ialananindro", 
                 "Iavonomby Vohibola", "Alatsinainy Ibity", "Namohora Iaborano", "Ihazoara", "Menamaty Iloto", "Imerina Imady", "Imerintsiatosika", "Isaka-Ivondro", "Isahara",
                 "Isorana", "Vatana", "Ivato Aeroport", "Ivoamba", "Ivony Miaramiasa", "Ikalalao", "Kianjandrakefina", "Iabohazo", "Ivondro", "Mahaditra", "Mahafasa Centre", 
                 "Mahajanga", "Mahasoabe", "Mahatsara Iefaka", "Mahatsinjo Est", "Mahatsinjony", "Mahatsinjony", "Mahazina Ambohipierenana", "Mananjary", "Manakambahiny Antsinanana",
                 "Manakambahiny Andrefana", "Manakara", "Manambotra Atsimo", "Manampatrana", "Mandromondromotra", "Maneva", "Mangarivotra", "Manombo Sud", "Manorofify", "Maritampona", 
                 "Tanambao Marivorahona", "Maroarivo Ankazomanga", "Marofoty", "Maromiandra", "Maromokotra Loky", "Marosavoa", "Marovitsika Sud", "Imerimandroso", "Miary Ambohibola", 
                 "Milenaka", "Mitsinjo Betanimena", "Mizilo Gara", "Moramanga", "Morarano Gara", "Cu Morombe", "Nanarena Besakoa", "Nasandratrony", "Niarovana Marosampanana", 
                 "Masianaka", "Onilahy", "Port Berge", "Port Berge II", "Rantabe", "Rantabe", "Vohipeno Razanaka", "Sahamadio Fisakana", "Sahambavy", "Sahambano", "Sahanivotry Manandona",
                 "Sakamahily", "Tanamarina Sakay", "Sakoana", "Sambava Cu", "Sarobaratra Ifanja", "Soaindrana", "Soalara Sud", "Soatanana", "Saint Augustin", "Taindambo", "Tatala Ampano", 
                 "Talata Angavo", "Fort-Dauphin", "Tanakambana", "Tanambao Daoud", "Tanambao Vahatrakaka", "Tanandava Sud", "Tandrano", "Toamasina Suburbaine", "Tovona", "Tsarahonenana Sahanivotry",
                 "Tsarajomoka", "Tsaratanana I", "Tsiafajavona Ankaratra", "Tsianisiha", "Tsianofana", "Tsinjoarivo Imanga", "Tsihombe", "Tsiroanomandidy Fihaonana", 
                 "Tsiroanomandidy Fihaonana", "Vatolatsaka", "Viliahazo", "Vinaninony Atsimo", "Andamasiny Vineta", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zoma Bealoka")

as.data.frame(cbind(commune_old, commune_new)) %>%
  arrange(commune_old) %>%
  mutate(test = commune_new == commune_old) %>%
  filter(test == FALSE) %>%
  select(!test) %>%
  rename("Name in data" = commune_old,
         "Standardized name" = commune_new) %>%
  gt() %>%
  tab_header(
    title = md("**Table S2.9: Standardization of commune names**")) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )

n_facilities_combined <- facilities_all  %>% nrow()

```

```{r housekeeping_1a, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

rm(column1, column2, data_mh_dup_names, r_new, r_old, chu_files, commune_new, commune_old, district_new, district_communes_affected, district_old, district_tobechanged, duplicates)

```

\end{spacing}

\vspace{24 pt}

```{r facility-name-manual-cleaning_1, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

facilities_all <- facilities_all %>%
  mutate(
      clinic_type=
      gsub(
        "Pharmacy",
        "FSP",
        clinic_type
      ),

    #Standardizing clinic names
    clinic_name_clean=
      gsub(
        "MANARA PENITRA",
        "Manara Penitra",
        clinic_name_clean
      ),
    clinic_name_clean=
      gsub(
        "Manara-Penitra Antsiranana",
        "Manara Penitra",
        clinic_name_clean
      ),
    clinic_name_clean=
      gsub("Vakinakaratra", "Vakinankaratra", clinic_name_clean),
    clinic_name =
      gsub(
        "Hopitaly MANARA-PENITRA",
        "Hopitaly Manara Penitra",
        clinic_name
      ),
    clinic_name =
      gsub(
        "Hopitaly Manara-Penitra Antsiranana",
        "Hopitaly Manara Penitra",
        clinic_name
      ),

        clinic_name_clean =
      gsub(
        "Manara Penitra Antsiranana",
        "Manara Penitra",
        clinic_name_clean
      ),
    clinic_name =
      gsub("Vakinakaratra", "Vakinankaratra", clinic_name)
  ) %>%
  unique()

n_FSP <- facilities_all %>% filter(clinic_type == "FSP") %>% nrow()
n_CSB <- facilities_all %>% filter(clinic_type == "CSB") %>% nrow()
n_CSB1 <- facilities_all %>% filter(clinic_type == "CSB1") %>% nrow()
n_CSB2 <- facilities_all %>% filter(clinic_type == "CSB2") %>% nrow()
n_CHD <- facilities_all %>% filter(clinic_type == "CHD") %>% nrow()
n_CHD1 <- facilities_all %>% filter(clinic_type == "CHD1") %>% nrow()
n_CHD2 <- facilities_all %>% filter(clinic_type == "CHD2") %>% nrow()
n_CHRR <- facilities_all %>% filter(clinic_type == "CHRR") %>% nrow()
n_CHU <- facilities_all %>% filter(clinic_type == "CHU") %>% nrow()
n_CHRRCHU <- facilities_all %>% filter(clinic_type == "CHRR/CHU") %>% nrow()

n_dif <- facilities_all %>% nrow
n_dif <- n_facilities_combined - n_dif

facilities_all <- facilities_all %>%
    arrange(clinic_name, region_name, district_name, commune_name) %>%
  mutate(facility_ID = seq.int(nrow(.)))

n_facilities_new <- facilities_all  %>% nrow()

facilities_all_nogps <- facilities_all
facilities_all_gps <- facilities_all_nogps[-(1:nrow(facilities_all_nogps)),]
facilities_all_gps <- facilities_all_gps %>% mutate(source ="") %>% mutate(geometry ="")
```

After standardizing facility types and catchment areas, the sample consisted of `r  prettyNum(n_facilities_combined, big.mark = ",", scientific = FALSE)` unique facilities. This list of facilities was then manually inspected for any remaining duplicates. From reviewing this list, we observed that in the Diana region, the regional hospitals named "Hopitaly MANARA-PENITRA" and "Hopitaly Manara-Penitra Antsiranana" are duplicates, but appear separately because the later name contains the city the hospital is located in, Antsiranana. We standardized the names of those facilities, which resolved `r  prettyNum(n_dif, big.mark = ",", scientific = FALSE)` duplicate(s).

The final sample of `r  prettyNum(n_facilities_new, big.mark = ",", scientific = FALSE)` unique facilities consisted of:

*  `r  prettyNum(n_CSB +n_CSB1 +n_CSB2, big.mark = ",", scientific = FALSE)` CSB facilities, including `r  prettyNum(n_CSB1, big.mark = ",", scientific = FALSE)` CSB1s, `r  prettyNum(n_CSB2, big.mark = ",", scientific = FALSE)` CSB2s, and `r  prettyNum(n_CSB, big.mark = ",", scientific = FALSE)` of unknown level;
*   `r  prettyNum(n_FSP, big.mark = ",", scientific = FALSE)`  FSP facilities;
*  `r  prettyNum(n_CHD + n_CHD1 + n_CHD2, big.mark = ",", scientific = FALSE)`  district hospitals, including `r  prettyNum(n_CHD1, big.mark = ",", scientific = FALSE)` CHD1 facilities, `r  prettyNum(n_CHD2, big.mark = ",", scientific = FALSE)` CHD2 facilities, and `r  prettyNum(n_CHD, big.mark = ",", scientific = FALSE)` facilities of unknown level, and
*  `r  prettyNum(n_CHRR +n_CHU +n_CHRRCHU, big.mark = ",", scientific = FALSE)` regional hospitals, including `r  prettyNum(n_CHRR, big.mark = ",", scientific = FALSE)` CHRRs, `r  prettyNum(n_CHU, big.mark = ",", scientific = FALSE)` CHUs, and `r  prettyNum(n_CHRRCHU, big.mark = ",", scientific = FALSE)` of unknown type.

\newpage

\paragraph*{Matching Approach}

\addcontentsline{toc}{paragraph}{Matching Approach}

```{r function_gps-source-prep_1, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Throughout the code, we will be creating unique IDs to help match strings 
# and facility joining of subseted data more easily. We define some prep functions here:

gps_source_join_map <- function(data){
  map_mdg_3 %>%
  st_transform(., crs = 4326) %>% 
  st_join(data,., join = st_within) %>%
  select(clinic_name, clinic_type, source, 
         COMMUNE_NA, DISTRICT_N, REGION_NAM, geometry) %>%
  rename(commune_name = COMMUNE_NA, 
         district_name = DISTRICT_N,
         region_name = REGION_NAM) %>%
      clean_clinic_name() %>%
      clean_catchment_area() %>%
      gps_source_match_prep() %>%
    filter(!is.na(commune_name) & !is.na(district_name) & !is.na(region_name))

  }

gps_source_match_prep <- function(data){

  data %>% mutate(ID =  seq.int(nrow(.)))

}

n_facilities <- function(data){
  nam <- paste("n_facilities", gps_source, sep = "_")
  n_fac <- data %>% nrow()
  assign(nam, n_fac,envir = .GlobalEnv)
}

map_clean_arrondis <- function(data){

data %>%

    #  We drop the commune name for ALL hospitals
    mutate(commune_name = ifelse(str_detect(clinic_type, "CH"),"",commune_name)) %>%

    #  We drop the district name for district and regional hospitals
    mutate(district_name = ifelse(str_detect(clinic_type, "CHR"),"",district_name)) %>%
    mutate(district_name = ifelse(str_detect(clinic_type, "CHU"),"",district_name)) %>%

    # In our data, Antananarivo Renivohitra had not yet been separated into separate
    # districts whose names were the same as the communes. To aid in matching, we 
    # replace the 6 district names for the 6 arrondissemenets as follows:
    mutate(district_name = case_when(
      str_detect(district_name, "Arrondissement") ~ "Antananarivo Renivohitra",
      TRUE ~ district_name)) 
}

map_coordinates <- function(data, palette){

  data %>%
  mutate(type_2 = clinic_type,
         type_2 = gsub("Pharmacy", "Other/Unknown", type_2),
         type_2 = case_when(
           str_detect(type_2, "CH") 
           ~ "CHD/CHRR/CHU",
           str_detect(type_2, "Hospital") 
           ~ "CHD/CHRR/CHU",
           TRUE ~ type_2)) %>%
  ggplot(aes(geometry = geometry)) +
  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_light) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  geom_sf(aes(color = (type_2)), alpha = 0.5, size = .75) +
  scale_color_manual(values = palette,
                     name = "Facility type")
}

# This code is not implemented, but is from 
# https://milospopovic.net/crisp-topography-map-with-r/
# and would add elevation for the image.

# windowsFonts(georg = windowsFont('Georgia'))
# 
# # libraries we need
# libs <- c("elevatr", "terra", "tidyverse", 
#           "sf", "giscoR", "marmap")
# 
# # install missing libraries
# installed_libs <- libs %in% rownames(installed.packages())
# if (any(installed_libs == F)) {
#   install.packages(libs[!installed_libs])
# }
# 
# # load libraries
# invisible(lapply(libs, library, character.only = T))
# 
# # 1. GET COUNTRY MAP
# #---------
# 
# crsLONGLAT <- "+proj=longlat +datum=WGS84 +no_defs"
# 
# get_sf <- function(country_sf, country_transformed) {
#   
#   country_sf <- giscoR::gisco_get_countries(
#     year = "2016",
#     epsg = "4326",
#     resolution = "10",
#     country = "Madagascar")
#   
#   country_transformed <- st_transform(country_sf, crs = crsLONGLAT)
#   
#   return(country_transformed)
# }
# 
# country_transformed <- get_sf()
# 
# # 2. GET ELEVATION DATA
# #---------
# 
# get_elevation_data <- function(country_elevation, country_elevation_df) {
#   
#   country_elevation <- get_elev_raster(
#     locations = country_transformed, 
#     z = 9, 
#     clip = "locations") 
#   
#   country_elevation_df <- as.data.frame(country_elevation, xy = T) %>%
#     na.omit()
#   
#   colnames(country_elevation_df)[3] <- "elevation"
#   
#   return(country_elevation_df)
# }
# 
# country_elevation_df <- get_elevation_data()
# 
# 
# 
# # 3. MAP
# #---------
# 
# get_elevation_map <- function(country_map) {
#   
#   country_map <- ggplot() +
#     geom_tile(data = country_elevation_df, 
#               aes(x = x, y = y, fill = elevation)) +
#     scale_fill_etopo() +
#     coord_sf(crs = crsLONGLAT)+
#     theme_minimal() +
#     theme(text = element_text(family = "georg", color = "#22211d"),
#           axis.line = element_blank(),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x = element_blank(),
#           axis.title.y = element_blank(),
#           legend.position = "none",
#           panel.grid.major = element_line(color = "white", size = 0.2),
#           panel.grid.minor = element_blank(),
#           plot.title = element_text(size=18, color="grey20", hjust=1, vjust=-5),
#           plot.caption = element_text(size=8, color="grey70", hjust=.15, vjust=20),
#           plot.margin = unit(c(t=0, r=0, b=0, l=0),"lines"), #added these narrower margins to enlarge maps
#           plot.background = element_rect(fill = "white", color = NA), 
#           panel.background = element_rect(fill = "white", color = NA),
#           panel.border = element_blank()) +
#     labs(x = "", 
#          y = NULL, 
#          title = "Topographic map of Madagascar", 
#          subtitle = "")
#   
#   return(country_map)
# }
# 
# 
# get_elevation_map()

```

```{r function_approximate-string-matching, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

approximate_string_match  <- function(data,   # Df w/o coordinates
                                      data_2, # Df w/ coordinates
                                      option, # What level of catchment area should matching be done against?
                                      type, # What restriction of facility type, if any, should be placed on the sample? 
                                      strip_type = FALSE # Should the clinic type be ommitted?
){

  if (type == "all") {
    print("Matching against ALL facilities without coordinates")
    data_2 <- data_2 %>%  map_clean_arrondis()
  }

  if (type == "primary"){

    print("Matching against CSB/FSP facilities without coordinates")

          data <- data %>% filter(clinic_type == "CSB" | clinic_type == "FSP" | 
                                clinic_type == "CSB1" |clinic_type == "CSB2" )
      data_2 <- data_2 %>%  filter(clinic_type == "CSB" | clinic_type == "FSP" | 
                                clinic_type == "CSB1" |clinic_type == "CSB2" ) %>%
        map_clean_arrondis()

  }

  if (type == "district"){

    print("Matching against CHD facilities without coordinates")

      data <- data %>% filter(clinic_type_clean == "CHD")
      data_2 <- data_2 %>% filter(clinic_type_clean == "CHD") %>%
        map_clean_arrondis()
  }

  if (type == "region"){

    print("Matching against CHR and CHU facilities without coordinates")

      data <- data %>% filter(clinic_type_clean == "CHR/CHU")
      data_2 <- data_2 %>% filter(clinic_type_clean == "CHR/CHU") %>%
        map_clean_arrondis()

  }

    if (type == "hospitals"){

    print("Matching against CHD, CHR, and CHU facilities without coordinates")

      data <- data %>% filter(clinic_type != "CSB" & clinic_type != "FSP" &
                                clinic_type != "CSB1" & clinic_type != "CSB2" )
      data_2 <- data_2 %>%  filter(clinic_type != "CSB" & clinic_type != "FSP" & 
                                clinic_type != "CSB1" & clinic_type != "CSB2" ) %>%
        map_clean_arrondis()

  }

  if (type == "centroid_fokontany") {

    data_trim <- data %>% 
      filter(!is.na(commune_name)) %>%
      mutate(full_name = paste(region_name, district_name, commune_name, clinic_name_clean, sep = " ")) %>%
      mutate(full_name = gsub("  ", " ", full_name),
             full_name = trimws(full_name)) %>%
      arrange(full_name) %>%
      filter(!str_detect(full_name, "MSI"))

    # We then retrieve the unique commune-district-region names from our map data
    data_trim_2 <- data_2 %>% 
        mutate(DISTRICT_N = case_when(
        str_detect(DISTRICT_N, "Arrondissement") ~ "Antananarivo Renivohitra",
        TRUE ~ DISTRICT_N)) %>%
      mutate(full_name = paste(REGION_NAM, DISTRICT_N, COMMUNE_NA, FOKONTANY_, 
                                         sep = " ")) %>%
      mutate(full_name = gsub("  ", " ", full_name),
             full_name = trimws(full_name)) %>%
      arrange(full_name) %>%
      unique() %>%

      # We then calculate the area in km^2 for each commune
      mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%

      # Find the centroid of each commune
      st_centroid() %>%

      # And drop all columns except for the unique commune-district-region name, centroid, and area
      select(area_km, full_name, geometry)

    }

      if (type == "centroid_commune") {

# We select all commune-level facilities and create a unique commune name, which includes
# the commune, district, and region name (as some commune names may not be unique)
data_trim <- data %>% 
  filter(!is.na(commune_name)) %>%
  mutate(full_name = paste(region_name, district_name, commune_name, sep = " ")) %>%
  mutate(full_name = gsub("  ", " ", full_name),
         full_name = trimws(full_name)) %>%
  arrange(full_name)

# We then retrieve the unique commune-district-region names from our map data
data_trim_2 <- data_2 %>%
    mutate(DISTRICT_N = case_when(
    str_detect(DISTRICT_N, "Arrondissement") ~ "Antananarivo Renivohitra",
    TRUE ~ DISTRICT_N)) %>%
  mutate(full_name = paste(REGION_NAM, DISTRICT_N, COMMUNE_NA, sep = " ")) %>%
  mutate(full_name = gsub("  ", " ", full_name),
         full_name = trimws(full_name)) %>%
  arrange(full_name) %>%
  unique() %>%

  # We then calculate the area in km^2 for each commune
  mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%

  # Find the centroid of each commune
  st_centroid() %>%

  # And drop all columns except for the unique commune-district-region name, centroid, and area
  select(area_km, full_name, geometry)

  }

  if (option == "commune") {
    data_trim <- data %>%
      mutate(
        full_name = paste(
          ifelse(strip_type == TRUE,"", clinic_type),
          clinic_name_clean,
          commune_name,
          district_name,
          region_name,
          sep = " "
        )
      )

    data_trim_2 <- data_2 %>%
      mutate(
        full_name = paste(
          ifelse(strip_type == TRUE,"", clinic_type),
          clinic_name_clean,
          commune_name,
          district_name,
          region_name,
          sep = " "
        )
      )

  }

  if (option == "district") {
    data_trim <- data %>%
      mutate(full_name = paste(
          ifelse(strip_type == TRUE,"", clinic_type),
                               clinic_name_clean,
                               district_name,
                               region_name,
                               sep = " "))

    data_trim_2 <- data_2 %>%
      mutate(full_name = paste(
          ifelse(strip_type == TRUE,"", clinic_type),
                               clinic_name_clean,
                               district_name,
                               region_name,
                               sep = " "))

  }

  if (option == "region") {
    data_trim <- data %>%
      mutate(full_name = paste(
          ifelse(strip_type == TRUE,"", clinic_type),
                               clinic_name_clean,
                               region_name,
                               sep = " "))

    data_trim_2 <- data_2 %>%
      mutate(full_name = paste(
          ifelse(strip_type == TRUE,"", clinic_type),
                               clinic_name_clean,
                               region_name,
                               sep = " "))

  }

  # Now that the concatenated string for matching has been specified, a subset of the data
  # are created that contain only the concatenated string ("full name") and an ID

  data_no_gps <- data_trim %>%
    select(full_name, facility_ID) %>%
    mutate(full_name = str_squish(full_name))

     if (option == "none"){

    print("Matching on centroid")
    data_gps <- data_trim_2 %>%
    select(full_name, area_km) %>%
    mutate(full_name = str_squish(full_name))
    } else(
  data_gps <- data_trim_2 %>%
    select(full_name, ID) %>%
    mutate(full_name = str_squish(full_name))
    )

  ## We can save on run time by using innerjoin to match facilities where a match is identical
  perfect_matches <- inner_join(data_gps, data_no_gps)
in_perfect_matches <- perfect_matches %>% select(facility_ID) %>% unique()
  in_perfect_matches <- as.vector(in_perfect_matches$facility_ID)
  data_no_gps <- data_no_gps %>%    
    filter(!facility_ID %in% in_perfect_matches)

  perfect_matches <-  perfect_matches %>% mutate(adist = 0, full_name_gps = full_name)

  # We then create apply the approximate string matching function, adist()
  # and calculate for each member of the dataframe w/o coordinates its
  # closest (by Levenshtein distance) pair in the dataframe w/ coordinates

  dist.name <- adist(
    data_no_gps$full_name,
    data_gps$full_name,
    partial = TRUE,
    ignore.case = TRUE
  )

  min.name <- apply(dist.name, 1, min)

  match.nogps.gps <- NULL
  for (i in 1:nrow(dist.name)) {
    s2.i <- match(min.name[i], dist.name[i, ])
    s1.i <- i

    match.nogps.gps <- rbind(
      data.frame(
        s2.i = s2.i,
        s1.i = s1.i,
        s2name = data_gps[s2.i, ]$full_name,
        s1name = data_no_gps[s1.i, ]$full_name,
        adist = min.name[i]
      ),
      match.nogps.gps
    )

  }

 asm_matches <- match.nogps.gps %>%
    rename(full_name = s2name) %>%
    inner_join(., data_gps) %>%
    rename(full_name_gps = full_name,
           full_name = s1name)  %>%
    inner_join(., data_no_gps) %>%
    select(!c(s2.i, s1.i)) %>%
   rbind(perfect_matches) %>%
       arrange(adist)

  assign("asm_match", asm_matches, envir = .GlobalEnv)

}

table_aprox_string_matches <- function() {

  asm_match %>%
    sample_frac(sample_fraction) %>% 
    st_drop_geometry %>%
    arrange(adist) %>%
    select(full_name, full_name_gps, adist) %>%
    rename("String (sample)" = full_name,
           "String (coord.)"= full_name_gps,
           "Levenshtein distance" = adist) %>%
    gt() %>%
    tab_header(
    title = md(paste0("Step ",
                            gsub("step_", "", step),
                            ": Approximate string matches"))) %>%
  tab_options(table.font.names = "Source Sans Pro") %>%
  tab_style(
    locations = cells_column_labels(),
    style     = list(
      cell_text(weight = "bold"))
  )
}

# Now that the approximate string matches have been calculated, it is
# possible to apply a maximum tolerable Levenshtein distance between pairs.
# This function then applies that maximum, keeping only
# pairs that are equal to or below that maximum distance.
# It then adds those coordinates to the dataframe of facilities w/ coordinates.

approximate_string_match_bind <- function(max_distance) {
  asm_matches_retained <-
    asm_match %>% filter(adist <= max_distance) %>%
    unique()

  # Save matches that have been retained

  assign(paste("asm_matches_retained", step, sep = "_"), asm_matches_retained, envir = .GlobalEnv)

  # Save the number of matches, based on Levenshtein distance

  for (i in 0:max_distance) {
    nam <- paste("n_adist", gps_source, i, sep = "_")
    n_adist <-
      asm_matches_retained %>% filter(adist == i) %>% nrow()
    assign(nam, n_adist, envir = .GlobalEnv)
  }

  facilities_all_gps_temp <- asm_matches_retained %>%
    select(geometry, facility_ID) %>%
    unique()

  duplicates <-
    facilities_all_gps_temp$facility_ID[duplicated(facilities_all_gps_temp$facility_ID)]

  facilities_all_gps_temp <- facilities_all_gps_temp %>%
    filter(!facility_ID %in% duplicates) %>%
    mutate(source = label) %>%
    inner_join(facilities_all)

  n_matched_facilities_temp <-   facilities_all_gps_temp %>% nrow()

  facilities_all_gps <-
    rbind(facilities_all_gps, facilities_all_gps_temp) %>% unique()

  n_matched_facilities <- facilities_all_gps %>% nrow()

  with_gps <- facilities_all_gps %>% select(facility_ID) %>% unique()
  with_gps <- as.vector(with_gps$facility_ID)

  facilities_all_nogps <- facilities_all %>%
    filter(!facility_ID %in% with_gps) %>%
    unique()

  n_unmatched_facilities <- facilities_all_nogps %>% nrow()

  assign("facilities_all_gps", facilities_all_gps, envir = .GlobalEnv)
  assign("facilities_all_nogps", facilities_all_nogps, envir = .GlobalEnv)
  assign(paste("n_matched_facilities", gps_source, sep = "_"),
         n_matched_facilities_temp,
         envir = .GlobalEnv  )
  assign(paste("n_matched_facilities", step, sep = "_"),
         n_matched_facilities, 
         envir = .GlobalEnv)
  assign("n_unmatched_facilities", n_unmatched_facilities, envir = .GlobalEnv)

}

approximate_string_match_bind_centroid <- function(max_distance) {

  asm_matches_retained <-
    asm_match %>% filter(adist <= max_distance) %>%
    unique()

  # Save matches that have been retained

  assign(paste("asm_matches_retained", step, sep = "_"), asm_matches_retained, envir = .GlobalEnv)

  # Save the number of matches, based on Levenshtein distance

  for (i in 0:max_distance) {
    nam <- paste("n_adist", gps_source, i, sep = "_")
    n_adist <-
      asm_matches_retained %>% filter(adist == i) %>% nrow()
    assign(nam, n_adist, envir = .GlobalEnv)
  }

  facilities_all_gps_temp <- asm_matches_retained %>%
    filter(area_km <= ifelse(gps_source == "commune", commune_lim, fokontany_lim)) %>%
    st_sf() %>% 
    st_transform(crs = 4326) %>%
    select(geometry, facility_ID) %>%
    unique()

  duplicates <-
    facilities_all_gps_temp$facility_ID[duplicated(facilities_all_gps_temp$facility_ID)]

  facilities_all_gps_temp <- facilities_all_gps_temp %>%
    filter(!facility_ID %in% duplicates) %>%
    mutate(source = label) %>%
    inner_join(facilities_all)

  n_matched_facilities_temp <-   facilities_all_gps_temp %>% nrow()

  facilities_all_gps <-
    rbind(facilities_all_gps, facilities_all_gps_temp) %>% unique()

  n_matched_facilities <- facilities_all_gps %>% nrow()

  with_gps <- facilities_all_gps %>% select(facility_ID) %>% unique()
  with_gps <- as.vector(with_gps$facility_ID)

  facilities_all_nogps <- facilities_all %>%
    filter(!facility_ID %in% with_gps) %>%
    unique()

  n_unmatched_facilities <- facilities_all_nogps %>% nrow()

  assign("facilities_all_gps", facilities_all_gps, envir = .GlobalEnv)
  assign("facilities_all_nogps", facilities_all_nogps, envir = .GlobalEnv)
  assign(paste("n_matched_facilities", gps_source, sep = "_"),
         n_matched_facilities_temp,
         envir = .GlobalEnv  )
  assign(paste("n_matched_facilities", step, sep = "_"),
         n_matched_facilities, 
         envir = .GlobalEnv)
  assign("n_unmatched_facilities", n_unmatched_facilities, envir = .GlobalEnv)

}

```

**Step 1: Matching to validated spatial inventory of public facilities in Sub-Saharan Africa (Maina et al.)**
``` {r step_1-loading_data, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

step = "step_1"
gps_source = "who"
label = "Exact - Validated sources"

facilities_gps_who <- st_read(paste(data_gps_sources_reposit, 
                                    "OCHA",
                                    "suhsharan_health_facilities",
                                    "sub-saharan_health_facilities.shp",
                                    sep = "/")) %>%
  filter(Country == "Madagascar") %>%
  filter(Lat !=0 & Long !=0) %>%
  mutate(clinic_name = Facility.n,
         clinic_type = Facility.t,

         # Unfortunately, CHD, CHR, and CHU hospitals 
         # are combined under "Hospital"
         # so the shared prefix "CH" is used to reduce distance 
         # to any hospital match

         clinic_type = gsub("Hospital", "CH", clinic_type),

         # "Health Post" corresponds to CSB1

         clinic_type = gsub("Health Post", "CSB1", clinic_type),

         # "Health Centre" corresponds to CSB2
         clinic_type = gsub("Health Centre", "CSB2", clinic_type)) %>%
  select(!c(Country, Ownership)) %>%
    rename(source = LL.source,
         latitude = Lat,
         longitude = Long)

# We will be adding these data to an expanded spatial inventory later;
# let us save a standardized subset of the columns for later use

facilities_gps_who_0 <- facilities_gps_who %>%
  select(clinic_type, latitude, longitude, source, clinic_name) %>%
  st_drop_geometry()

# Returning to the original inventory, we standardize commune, district,
# and region names for the coordinates we observed

facilities_gps_who <- facilities_gps_who%>%
  gps_source_join_map()

n_facilities(facilities_gps_who)

```

We began by gathering data from a validated spatial inventory of health facilities in Sub-Saharan Africa, @mainaSpatialDatabaseHealth2019 of which `r format(as.numeric(n_facilities_who), big.mark = ",")` coordinates were available for public facilities in Madagascar.

<!-- A figure of the facilities from the validated spatial inventory is below: -->

<!-- ```{r figure_avail_gps_val,  results = TRUE, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- #fig.cap="\\label{figure_avail_gps}Validated spatial inventory of health facilities."} -->

<!-- # Let's visualize the different coordinates we have available. -->

<!-- facilities_gps_who %>%  -->
<!--   map_coordinates(c(col_CH, col_CSB1, col_CSB2)) -->

<!-- ``` -->

In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented an approximate string matching technique. This technique—also known as "fuzzy string searching"—is a common approach to record linkage, where information from one source (e.g., our sample) needs to be linked to data from another (e.g., the spatial inventory). As its name suggests, this techniques allows for "strings" of text to be matched approximately, rather than exactly, to corresponding patterns. In our case, this can be helpful if the facility name is spelled slightly differently in our sample versus the spatial inventory, due to typographic errors in the raw data or small orthographic variations (e.g., writing "2" as "II", inclusion or omission of a dash, etc.). A description of how this approach can be implemented in R is available at www.R-bloggers.com. @docFuzzyStringMatching2015

To account for similarly named facilities located in different regions, we constructed a full, standardized name for each facility that included facility name and catchment area prior to applying our matching technique. Facility type was standardized to align with the facility types in our sample. For example, the full, standardized name for the Alakamisy Tsarazaza Health Post located in the commune of Tsarazazaa in the Fandrian district of Amoron'I Mania region would be "Alakamisy Tsarazaza Tsarazazaa Fandrian Amoron'I Mania", with the facility classified as a CSB1 facility).

The similarity between two strings of text can be measured numerically using the Levenshtein (or edit) distance. @konstantinidisComputingEditDistance2007 The Levenshtein distance between two identical strings will be zero, while strings involving a single character edit (insertions, deletions or substitutions) will involve a distance of 1.

To identify the closest matches between the full, standardized facility names in our sample and the spatial inventory, we calculated a matrix identifying the pair-wise Levenshtein distance between all possible combinations. For each member of our sample, we then selected the facility in the spatial inventory with the lowest Levenshtein distance (i.e., the nearest pair).

To maximize pair accuracy, we separately conducting matching among primary health facilities (i.e., FSPs and CSBs) and among hospitals (i.e., CHDs, CHRRs, and CHUs). For primary health facilities, the full, standardized facility names included the facility's region, district, and commune; for hospitals, the full name included the region and district only. To apply a conservative matching approach, we restricted matches to those with a Levenshtein distance no greater than 2.

```{r step_1-approximate-string-matches-1, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Identify matched pairs with plausible matched information
gps_source = "who_primary"
approximate_string_match(facilities_all_nogps, facilities_gps_who, option = "commune", type = "primary", strip_type = TRUE)
approximate_string_match_bind(2)

```

```{r step_1-approximate-string-matches-2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Identify matched pairs with plausible matched information
gps_source = "who_hospitals"
approximate_string_match(facilities_all_nogps, facilities_gps_who, option = "district", type = "hospitals", strip_type = TRUE)
approximate_string_match_bind(2)

```

<!-- A sample of nearest pairs from this matching in Step 1 is provided below: -->

<!-- ```{r table_step_1_approximate_matches, results = TRUE, out.width="100%", warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- tab_step_1 <-  table_aprox_string_matches() %>% -->
<!--   tab_options(table.font.size = 10) %>% -->
<!--   cols_width( -->
<!--     ends_with("distance") ~ px(60), -->
<!--     everything() ~ px(280) -->
<!--   ) -->

<!-- tab_step_1 %>% gtsave("tab_step_1.png") -->

<!-- knitr::include_graphics("tab_step_1.png") -->

<!-- # We restricted matches to those where hospitals were matched with hospitals, CSB1 facilities were matched to CSB1 facilities, and CSB2 facilities were matched to CSB2 facilities.   -->

<!-- <!-- ``` --> 
<!-- \newpage -->

Using this approach, `r format(as.numeric(n_matched_facilities_step_1), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_1)/n_facilities_new * 100,0)`%) in our sample were matched to validated coordinates, of which `r format(as.numeric(n_adist_who_primary_0 + n_adist_who_hospitals_0), big.mark = ",")` facilities were matched based on identical string matches,  `r format(as.numeric(n_adist_who_primary_1 + n_adist_who_hospitals_1), big.mark = ",")` facilities were matched based on string matches with a Levenshtein distance of 1, and `r format(as.numeric(n_adist_who_primary_2 + n_adist_who_hospitals_2), big.mark = ",")` facilities  were matched based on string matches with a Levenshtein distance of 2.

**Step 2: Matching to facility data from RHINoVision Decision Support System**

We then gathered public health facility coordinate data from the RHINoVision Decision Support System, @rhinovisiondecisionsupportsystemMadagascarDecisionSupport which supports an open source database of health facility data in conjunction with USAID, the government of Madagascar, and other stakeholders.

```{r step_2-loading_data, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

step = "step_2"
gps_source = "rhino"
label = "Exact - RHINoVision"

facilities_gps_3 <- read.csv(paste(data_gps_sources_reposit,
                                   'MDMFL.csv', sep = "/"), 
                             header=TRUE) %>%
  rename(longitude = Longitude, latitude = Latitude, 
         district_name = CommuneNom,
         clinic_name = FacilityNom, 
         clinic_type = FacilityType) %>%
  select(district_name, clinic_name, 
         clinic_type, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "RHINoVision Decision Support System") %>%
  select(clinic_name, longitude, latitude, source, clinic_type)

facilities_gps_rhino <- facilities_gps_3 %>%
  st_as_sf(., coords = c("longitude", "latitude"), 
           crs = 4326)

facilities_gps_rhino <- facilities_gps_rhino %>%
 gps_source_join_map()

n_facilities(facilities_gps_rhino)

```

RHINoVision's spatial inventory included coordinates for `r format(as.numeric(n_facilities_rhino), big.mark = ",")` primary health facilities in Madagascar.

<!-- A visualization of the available coordinates is provided below: -->

<!-- ```{r figure_avail_gps_RHINO, results = TRUE, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- #fig.cap="\\label{figure_avail_gps}Expanded spatial inventory of health facilities."} -->

<!-- # Let's visualize the different coordinates we have available. -->

<!-- facilities_gps_rhino %>%  -->
<!--   map_coordinates(c(col_CSB1, col_CSB2)) -->

<!-- ``` -->

We applied the same approximate string matching technique as in Step 1 against the RHINoVision spatial inventory, restricting matches only to primary health facilities in our sample (so as not to allow hospitals to be matched against the spatial inventory of basic health facilities).

```{r step_2-approximate-string-matches, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Identify matched pairs with plausible matched information

approximate_string_match(facilities_all_nogps, facilities_gps_rhino, option = "commune", type = "primary", strip_type = TRUE)

```

<!-- \newpage -->

<!-- A sample of nearest pairs from this matching in Step 2 is provided below: -->

<!-- ```{r table_step_2_approximate_matches,results = TRUE, out.width="100%", warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->

<!-- tab_step_2 <- table_aprox_string_matches() %>% -->
<!--   tab_options(table.font.size = 10) %>% -->
<!--   cols_width( -->
<!--     ends_with("distance") ~ px(60), -->
<!--     everything() ~ px(280) -->
<!--   ) -->

<!-- tab_step_2 %>% gtsave("tab_step_2.png") -->

<!-- knitr::include_graphics("tab_step_2.png") -->

<!-- ``` -->

Following visual inspection of the nearest approximate pairs, we retained matches with a maximum Levenshtein distance of 3, to allow for greater flexibility in matching.

```{r step_2-approximate-string-filtering, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

approximate_string_match_bind(3)

```

Using this approach, `r format(as.numeric(n_matched_facilities_rhino), big.mark = ",")` facilities were matched to coordinates in the RHINoVision spatial inventory, of which `r format(as.numeric(n_adist_rhino_0), big.mark = ",")` facilities were matched based on identical string matches,  `r format(as.numeric(n_adist_rhino_1), big.mark = ",")` facilities were matched based on string matches with a Levenshtein distance of 1, `r format(as.numeric(n_adist_rhino_2), big.mark = ",")` facilities were matched based on string matches with a Levenshtein distance of 2, and `r format(as.numeric(n_adist_rhino_3), big.mark = ",")` facilities were matched based on string matches with a Levenshtein distance of 3. (`r format(as.numeric(n_adist_rhino_0+n_adist_rhino_1+n_adist_rhino_2+n_adist_rhino_3 - n_matched_facilities_rhino), big.mark = ",")` matches were duplicates and were removed.)

In total, matching to our expanded inventory in Step 2 led to `r format(as.numeric(n_matched_facilities_step_2), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_2)/n_facilities_new * 100,0)`% of our sample) being geolocated.

**Step 3: Matching to any spatial sources**

```{r step_3-loading_data, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

step = "step_3"
gps_source = "any"
label = "Exact - All sources"

facilities_gps_who_0 <- facilities_gps_who_0 %>%
  rename(type = clinic_type)

facilities_gps_OCHA_1 <- st_read(paste(data_gps_sources_reposit, 
                                       "OCHA",
                                       "hotosm_mdg_health_facilities_points_shp",
                                       "hotosm_mdg_health_facilities_points.shp",
                                       sep = "/")) %>%
  select(name, geometry, osm_id) %>%
  unique() %>%
  filter(!is.na(name)) %>%
  rename(clinic_name = name, ID_OSM = osm_id)

facilities_gps_coordinates <- facilities_gps_OCHA_1 %>%
  st_coordinates()
facilities_gps_coordinates <- as.data.frame(facilities_gps_coordinates)
facilities_gps_OCHA_1 <- cbind(facilities_gps_OCHA_1, facilities_gps_coordinates)

facilities_gps_OCHA_1 <- facilities_gps_OCHA_1 %>%
  st_drop_geometry() %>%
  select(clinic_name, X, Y, ID_OSM)

crs_system <- st_crs(facilities_gps_OCHA_1)
with_gps_OCHA <- facilities_gps_OCHA_1 %>% select(ID_OSM) %>% unique()
with_gps_OCHA <- with_gps_OCHA$ID_OSM

#OpenStreetMap contributors
# Contributor	Global Healthsites Mapping Project

facilities_gps_OCHA_2 <- read_csv(paste(data_gps_sources_reposit, 
                                        "OCHA",
                                        "madagascar.csv", 
                                        sep = "/")) %>%
  filter(!is.na(X)) %>%
  filter(!is.na(Y)) %>%
  filter(!is.na(name)) %>%
  select(name, X, Y, osm_id) %>%
  rename(clinic_name = name, ID_OSM = osm_id) %>%
  unique() %>%
  filter(!ID_OSM %in% with_gps_OCHA) %>%
  st_drop_geometry()

facilities_gps_OCHA <- rbind(facilities_gps_OCHA_1, 
                             facilities_gps_OCHA_2)

rm(facilities_gps_OCHA_1, facilities_gps_OCHA_2, facilities_gps_coordinates)

# Import first source of data: OpenStreetMap data
facilities_gps_0 <- facilities_gps_OCHA %>%
  rename(latitude = Y,
         longitude = X) %>%
  mutate(source = "OpenStreetMap", type = NA) %>%
  select(!c(ID_OSM))

rm(facilities_gps_OCHA)

# Import next source of GPS data
facilities_gps_1 <- read_excel(paste(data_gps_sources_reposit, 
                                     "20220630 Health clinic GPS points.xlsx", 
                                     sep = "/")) %>%
  unique() %>%

  # GPS coordinates are saved in a single string. Separate these into long and lat columns
  mutate(geometry = str_sub(Geometry, 8,-2)) %>%
  mutate(latitude = as.numeric(sub(".* ", "", geometry)),
         longitude = as.numeric(sub(" .*", "", geometry))) %>%

  # Trim dataset
  select(region, district, commune, type, FS, longitude, latitude) %>%
  rename(clinic_name = FS, district_name = commune) %>%

  # Drop missing values
  filter(!is.na(longitude)) %>%
  filter(!is.na(latitude)) %>%
  mutate(source = "File 1 (Consultant?)") %>%
  select(clinic_name, longitude, latitude, source, type)

# Import next source of GPS data
facilities_gps_2 <- read.csv(paste(data_gps_sources_reposit,
                                   'Health clinic data points.csv', sep = "/"), 
                             header=TRUE) %>%

  # Ensure longitude is saved as numeric, not character 
  mutate(longitude = as.numeric(longitude)) %>%
  select(Nom.Commune, Type..CSB1..CSB2.., 
         Nom.complet.FS.1, latitude, longitude) %>% 
  rename(clinic_name = Nom.complet.FS.1, 
         district_name = Nom.Commune, type = Type..CSB1..CSB2..) %>%
  unique() %>%
  mutate(source = "File 2 (MOH?)") %>%
  select(clinic_name, longitude, latitude, source, type) %>%

  # Drop missing values
  filter(!is.na(longitude)) %>%
  filter(!is.na(latitude))

# Import next source of GPS data: RHINoVision Decision Support System
facilities_gps_3 <- facilities_gps_3 %>%
  rename(type = clinic_type)

# Import next source of GPS data
facilities_gps_4 <- read.csv(paste(data_gps_sources_reposit, 
                                   '20210415 Palu_CSB_last 3.csv',
                                   sep = "/"), 
                             header=TRUE) %>%
  rename(district_name = District, clinic_name = Health.center.names) %>%
  select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 3 (?)", type = NA) %>%
  select(clinic_name, longitude, latitude, source, type)

facilities_gps_5 <- read_excel(paste(data_gps_sources_reposit, 
                                     "CHD ET CHU XY 2012.xls", sep = "/")) %>%
  rename(district_name = "Nom District", 
         clinic_name = "Nom FS GESIS",
         latitude = "Y", longitude = "X") %>%
  select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 4 (Consultant)", type = NA) %>%
  select(clinic_name, longitude, latitude, source, type)

# Import next source of GPS data
facilities_gps_6 <- read.csv(paste(data_gps_sources_reposit, 
                                   'CSB GPS points.csv', sep = "/"), 
                             header=TRUE) %>%
  rename(district_name = district_n, clinic_name = clinic_nam,
         latitude = Latitude, longitude = Longitude) %>%
  select(district_name, clinic_name, latitude, longitude) %>%

  # Drop missing values
  filter(latitude != 0) %>%
  filter(longitude != 0) %>%
  unique() %>%
  mutate(source = "File 5 (Chris)", type = NA) %>%
  select(clinic_name, longitude, latitude, source, type)

# Merge the GPS data sources and reconcile duplicate data
facilities_gps_any <- facilities_gps_0 %>%

  # Bind the sources and eliminate any perfect duplicates and missing values
  rbind(., facilities_gps_1, facilities_gps_2, facilities_gps_3, 
        facilities_gps_4, facilities_gps_5, facilities_gps_6, facilities_gps_who_0) %>%
  unique() %>%

  # Drop any rows where one or more of the coordinates are missing
  filter(!is.na(longitude)) %>%
  filter(!is.na(latitude)) %>%
  arrange(clinic_name) %>%
  st_as_sf(., coords = c("longitude", "latitude"), 
           crs = 4326) %>%
  rename(clinic_type = type) %>%
  mutate(clinic_name = paste(clinic_type, clinic_name, sep = " "),
         clinic_name = gsub("NA ","", clinic_name)) %>%
  gps_source_join_map() %>%
  clean_clinic_type() %>%
  clean_clinic_name() %>%
  clean_catchment_area()

n_facilities(facilities_gps_any)

# Clean up
rm(facilities_gps_0, facilities_gps_1,  facilities_gps_2, facilities_gps_3, 
   facilities_gps_4, facilities_gps_5, facilities_gps_6, facilities_gps_who_0,
   facilities_gps_who, facilities_gps_rhino)

```

To geolocate the remaining facilities, we expanded our spatial inventories with health facility coordinates gathered from local consultants, the Global Healthsites Mapping Project, and other sources to create an expanded database of `r format(as.numeric(n_facilities_any), big.mark = ",")` uniquely identified coordinates.

<!-- Coordinates by facility type and source are provided below: -->

```{r step_3-table-coordinates-by-type-setup, include = FALSE, results = FALSE, warning = FALSE, message = FALSE, echo = FALSE}

facility_gps_types <- facilities_gps_any %>%
  st_drop_geometry() %>%
  mutate(count = 1) %>%
  group_by(source, clinic_type) %>%
  mutate(value = sum(count, na.rm = FALSE)) %>%
  ungroup() %>%
  select(source, clinic_type, value) %>%
  unique() %>%
  arrange(source) %>%
  pivot_wider(names_from = source) %>%
  arrange(clinic_type)

facility_gps_types[is.na(facility_gps_types)] = 0

```

```{r step_3-table-coordinates-by-type, include = TRUE, results = TRUE, out.width="90%", warning = FALSE, message = FALSE, echo = FALSE}

tab_step_3 <- facility_gps_types %>%
  mutate(group = ifelse(
    clinic_type == "CHD" | clinic_type == "CHD1" | clinic_type == "CHD2",
    "District hospital",
    ifelse(
      clinic_type == "CHRR" |
        clinic_type == "CHU" |
        clinic_type == "CH",
      "Regional hospital",
      ifelse(
        clinic_type == "CSB" |
          clinic_type == "CSB1" |
          clinic_type == "FSP" |
          clinic_type == "CSB2",
        "Basic health facility",
        "Other"
      )
    )
  )) %>%
  rename('Facility type' = clinic_type) %>%
    rename('Combo.' = Combination) %>%

    rename('RHINo' = 'RHINoVision Decision Support System') %>%

    rename('Open Street Map' = OpenStreetMap) %>%
  mutate(Total =  rowSums(across(where(is.numeric))))

tab_step_3 <- tab_step_3 %>%
  gt(groupname_col = "group") %>%
  tab_options(table.font.names = "CMU Serif Roman",
              table.font.size = 11) %>%
  tab_style(locations = cells_column_labels(),
            style     = list(cell_text(weight = "bold", size = 9))) %>%
  summary_rows(
    groups = TRUE,
    columns = 2:ncol(tab_step_3),
    fns = list(Subtotal = "sum"),
        decimals = 0,
    sep_mark = ","
  ) %>%
  grand_summary_rows(
    columns =2:ncol(tab_step_3),
    fns = list('Grand total' = "sum"),    decimals = 0,
    sep_mark = ","
  )   %>%
  fmt(
    rows = everything(),
    fns = function(x) ifelse(x == 0, "—", prettyNum(x, big.mark = ","))) %>%
  cols_width(
    everything() ~ px(61)
  )
# 
# tab_step_3 %>% gtsave("tab_step_3.png")
#  
# knitr::include_graphics("tab_step_3.png")

```

```{r step_3-removing-pharmacies, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

facilities_gps_any <- facilities_gps_any %>% filter(clinic_type != "Pharmacy")
n_gps_facilities_new <- facilities_gps_any %>% nrow()

```

We removed pharmacies from our spatial inventory, as pharmacies were not included in our sample. Removing pharmacies from our expanded spatial inventory resulted in `r format(as.numeric(n_gps_facilities_new), big.mark = ",")` coordinates available for matching.

Most of the coordinates in this expanded inventory were duplicates (i.e., the same facility will appear in different sources). Importantly, coordinates for the same facility could be slightly different across sources, due to variation in precision and geolocation.

Using the same approach to uniquely identifying facilities in our sample, we grouped coordinates in our expanded inventory by facility name, type, and geographic information (namely, which commune, district, and region a coordinate fell within). In other words, in order to be grouped together, coordinates would need to be of the same facility type and name, and would need to be located in the same region and in the boundaries of the same district (for hospitals) or commune (for all other facilities).

```{r step_3-data-grouping, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# To improve matching, we can identify what region, district, and commune
# each of our data points falls into. By then grouping on clinic name AND
# commune/district/region, we can ensure that matched groups actually reflect the 
# same facility, and not similarly named facilities in different districts.
#

#

facilities_gps_any <- facilities_gps_any %>%
  map_clean_arrondis() %>%

  # Due to variations in precision, there may be different GPS coordinates 
  # for the same facility across different data sources. We will 
  # smooth this out by taking the centroid of each group of coordinates,
  # but only if we feel confident that the different points for the same clinic
  # are close to each other.

  # First, let's say that points must have the same clinic name, district name, and type
  # to be considered to be referring to the same clinic
  group_by(clinic_name_clean, commune_name, district_name, region_name, clinic_type) %>%

  # For points meeting that criteria, let's gather them into lines (2 points) and polygons (3+ points)
  summarise() %>%

  # For polygons, let's draw the smallest possible border around all points that captures each of them
  st_convex_hull() %>%

  # And calculate the length and area of the resulting groups
  mutate(length = as.numeric(st_length(geometry)/1000),
         area_km = as.numeric(st_area(geometry)/1000000)) %>%

  # We can identify the type of geometry as follows:
  mutate(shape_type = ifelse(length == 0 & area_km == 0, 
                             "point",
                             ifelse(length != 0 & area_km == 0, 
                                    "line", "polygon"))) %>%

                                    # 
                                    # 
                                    # ifelse(length == 0,
                                    #        "polygon", "other")))) %>%

  # Let's apply our thresholds from the PARENT file
  mutate(retain = ifelse(length == 0 & area_km == 0, 
                         "Within threshold",
                         ifelse(length <= length_lim & area_km == 0, 
                                "Within threshold",
                                ifelse(length == 0 & area_km <= area_lim,
                                       "Within threshold", 
                                       "Above threshold")))) %>%
  ungroup()

n_point <- facilities_gps_any %>% filter(shape_type == "point") %>% nrow()
n_line <- facilities_gps_any %>% filter(shape_type == "line") %>% nrow()
n_poly <- facilities_gps_any %>% filter(shape_type == "polygon") %>% nrow()

n_groups <- facilities_gps_any %>% nrow()

n_mean_area_polygons <- facilities_gps_any %>% filter(shape_type == "polygon") %>% 
  st_drop_geometry() %>%
  select(area_km) %>%
  mutate(mean = mean(area_km)) %>%
  select(mean) %>%
  unique()

n_mean_area_polygons <- n_mean_area_polygons$mean

n_max_area_polygons <- facilities_gps_any %>% filter(shape_type == "polygon") %>% 
  st_drop_geometry() %>%
  select(area_km) %>%
  mutate(max = max(area_km)) %>%
  select(max) %>%
  unique()
n_max_area_polygons <- n_max_area_polygons$max

n_mean_length <- facilities_gps_any %>% filter(shape_type == "line") %>% 
  st_drop_geometry() %>%
  select(length) %>%
  mutate(mean = mean(length)) %>%
  select(mean) %>%
  unique()

n_mean_length <- n_mean_length$mean

n_max_length <- facilities_gps_any %>% filter(shape_type == "line") %>% 
  st_drop_geometry() %>%
  select(length) %>%
  mutate(max = max(length)) %>%
  select(max) %>%
  unique()
n_max_length <- n_max_length$max

n_length_retained <- facilities_gps_any %>% filter(shape_type == "line") %>% 
  filter(retain == "Within threshold") %>% nrow()

```

Grouping resulted in `r format(as.numeric(n_groups), big.mark = ",")` coordinate groups in our expanded inventory. Of these, `r format(as.numeric(n_poly), big.mark = ",")` consisted of three or more coordinates, `r format(as.numeric(n_line), big.mark = ",")` consisted of two coordinates, and `r format(as.numeric(n_point), big.mark = ",")` consisted of a single coordinate.

In order to evaluate whether groups of two coordinates (which we referred to as "line groups") and groups of three or more coordinate ("polygon groups") were internally consistent (i.e., the points within a group were not geographically far apart, suggesting uncertainty in the location of a facility), we calculated the length (for line groups) and area (for polygon groups) of groups with more than one coordinate.

We applied an arbitrary restriction to line and polygon groups, such that the length or area, respectively, would not exceed a particular threshold. The threshold for length (`r format(as.numeric(length_lim), big.mark = ",")` km.) was selected to be approximately half the distance of one side of a spatial climate resolution tile (~31 km for ERA-5 data). The threshold for area (`r format(as.numeric(area_lim), big.mark = ",")` square km.) was assigned to be the length threshold, squared. Groups that exceeded their respective thresholds were discarded.

```{r step_3-histogram-prep, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Here is a histogram of the polygons

panel_a <- facilities_gps_any %>% 
  filter(shape_type == "polygon") %>%
  mutate(area = ifelse(area_km > area_lim, area_lim,
                       ifelse(area_km < 1, 1, 
                              area_km))) %>%
  ggplot() +
  geom_histogram(aes(x=area_km, fill = retain),
                 bins = 100) +
  geom_vline(xintercept = area_lim) +
  labs(x = "Area (km^(2))",
       title = "Polygons of GPS coordinates, by area",
       subtitle = "Smaller areas mean greater agreement across data sources",
       caption = paste0("Line shows threshold limit of ",
                        prettyNum(area_lim, big.mark = ",", scientific = FALSE),
                        " km sq."),
       y = "Count",
       fill = "") +
  theme_classic() +
  theme(axis.title.x = element_markdown(),
        text = element_text(family = "Source Sans Pro"),
        legend.position = "bottom") +
  scale_fill_manual(values = c(col_within_threshold))

# Saving plot
ggsave(filename = "gps_data_polygons.jpg", plot = last_plot(),
       path = gpspath_fig,
       width = 8,
       height = 7)

panel_a <- facilities_gps_any %>% 
  filter(shape_type == "polygon") %>%
  mutate(area = ifelse(area_km > area_lim, area_lim,
                       ifelse(area_km < 1, 1, 
                              area_km))) %>%
  ggplot() +
  geom_histogram(aes(x=area_km, fill = retain),
                 bins = 100) +
  geom_vline(xintercept = area_lim) +
  labs(x = "Area (km^(2))",
       title = "Polygons of GPS coordinates, by area",
       subtitle = "Smaller areas mean greater agreement across data sources",
       caption = paste0("Line shows threshold limit of ",
                        prettyNum(area_lim, big.mark = ",", scientific = FALSE),
                        " km sq."),
       y = "Count",
       fill = "") +
  theme_classic() +
  theme(axis.title.x = element_markdown(),
        text = element_text(family = "Source Sans Pro"),
        legend.position = "none") +
  scale_fill_manual(values = c(col_within_threshold))

# And here is a histogram of the lines

panel_b <- facilities_gps_any %>% 
  filter(shape_type == "line") %>%
  mutate(len = ifelse(length > length_lim, length_lim,
                      ifelse(length < 1, 1, 
                             length))) %>%
  ggplot() +
  geom_histogram(aes(x=length, fill = retain),
                 bins = 100) +
  geom_vline(xintercept = length_lim) +
  labs(x = "Length (km)",
       title = "Lines of GPS coordinates, by distance",
       subtitle = "Smaller lengths mean greater agreement across data sources",
       caption = paste0("Line shows threshold limit of ",
                        prettyNum(length_lim, big.mark = ",", scientific = FALSE),
                        " km"),
       y = "Count",
       fill = "") +
  theme_classic() +
  theme(axis.title.x = element_markdown(),
        text = element_text(family = "Source Sans Pro"),
        legend.position = "bottom") +
  scale_fill_manual(values = c(col_beyond_threshold, col_within_threshold))

# # Saving plot
ggsave(filename = "gps_data_lines.jpg", plot = last_plot(),
       path = gpspath_fig,
       width = 8,
       height = 7)

```

<!-- ```{r figure_histograms, fig.height = 6,  include=TRUE, results = TRUE, warning = FALSE, message = FALSE, echo = FALSE} -->

<!-- #fig.cap="\\label{figure_histograms}Polygon and line groups, by area and length, respectively."} -->

<!-- ggarrange(panel_a, panel_b, -->
<!--           nrow = 2,    -->
<!--           heights  = c(1, 1.5), -->
<!--           common.legend = FALSE) -->

<!-- ``` -->

Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km sq, with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km sq. At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` square km., all polygon groups fell within the cut-off. Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km., with a maximum distance of `r format(round(n_max_length), big.mark = ",")` kilometers. At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` km.,  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).

```{r step_3-retaining-coordinates-within-threshold, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

facilities_gps_any <- facilities_gps_any %>% 
  filter(retain == "Within threshold") %>%
  st_centroid() %>% 
  select(!c(shape_type, length, area_km, retain)) %>%
  clean_catchment_area() %>%
  unique() %>%
  gps_source_match_prep()

n_gps_facilities <- nrow(facilities_gps_any)

```

After applying the thresholds, we retained `r format(as.numeric(n_gps_facilities), big.mark = ",")` coordinate groups in our expanded inventory.

To identify a single coordinate from each group, we computed the convex hull of polygon groups and selected the centroid of the grouped coordinates. For line groups, we selected the midpoint. For groups with a single member, the coordinates of that sole member were used.

<!-- The figure below displays the expanded spatial inventory, by facility type: -->

```{r figure_avail_gps, include = FALSE, results = FALSE, warning = FALSE, message = FALSE, echo = FALSE}

#fig.cap="\\label{figure_avail_gps}Expanded spatial inventory of health facilities."}
# Let's visualize the different coordinates we have available.

facilities_gps_any %>%
 mutate(clinic_type = case_when(
   str_detect(clinic_type, "CH")
   ~ "CHD/CHRR/CHU",
   str_detect(clinic_type, "CS")
   ~ "CSB/FSP",
   str_detect(clinic_type, "FS")
   ~ "CSB/FSP",
   TRUE ~ "Other")) %>%
  map_coordinates(c(col_CH, col_CSB, col_other))

```

```{r step_3-saving-of-figure, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Saving plot
ggsave(filename = "available_gps_coordinates.jpg", plot = last_plot(),
       path = gpspath_fig,
       width = 8,
       height = 7,
       bg = "white")

facilities_gps_temp <- facilities_gps_any %>% st_drop_geometry()

write.xlsx(facilities_gps_temp, file = paste(gpspath_spread,
                                              "2_unmatched",
                                              "gps_facilities_all.xlsx",
                                              sep = "/"))
rm(facilities_gps_temp)

```

We then applied the same approximate string matching technique as in Step 1, using the remaining facilities without geolocations in our sample and the expanded spatial inventory. To maximize match accuracy, we applied the approximate string matching technique separately based on the three geographic levels of service, akin to our approach in Step 1. In other words, regional facilities in our sample are only evaluated for possible matches against regional facilities in the expanded spatial inventory, and so one for district-level facilities and for commune-level facilities.

Visual inspection of closest pairs across the regional, district, and commune level facilities indicated that likely matches had a Levenshtein distance no greater than 3.

```{r step_3-approximate-string-matches, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# Commune matching

gps_source = "any_commune"
approximate_string_match(facilities_all_nogps, facilities_gps_any, option = "district", type = "primary", strip_type = TRUE) 
approximate_string_match_bind(3)

# District matching

gps_source = "any_district"
approximate_string_match(facilities_all_nogps, facilities_gps_any , option = "district", type = "district", strip_type = TRUE) 
approximate_string_match_bind(3)

# Regional matching

gps_source = "any_region"
approximate_string_match(facilities_all_nogps, facilities_gps_any, option = "region", type = "region", strip_type = TRUE) 
approximate_string_match_bind(3)

```

Using this approach, `r format(as.numeric(n_matched_facilities_any_region + n_matched_facilities_any_district + n_matched_facilities_any_commune), big.mark = ",")` facilities were matched to coordinate groups in our expanded spatial inventory, including `r format(as.numeric(n_matched_facilities_any_region), big.mark = ",")` regional facilities, `r format(as.numeric(n_matched_facilities_any_district), big.mark = ",")` district-level facilities, and `r format(as.numeric(n_matched_facilities_any_commune), big.mark = ",")` commune-level facilities. In total, matching to our expanded inventory in Step 3 led to `r format(as.numeric(n_matched_facilities_step_3), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_3)/n_facilities_new * 100,0)`% of our sample) being geolocated.

**Step 4: Manual matching to coordinates in the expanded spatial inventory**

Despite the use of approximate string matching in Step 3 to link facilities in our sample to coordinates in our expanded spatial inventory, visual inspection and comparison of unmatched facilities to the spatial inventory revealed match failures due to variations in clinic names (e.g., “Notre Dame De Bon Remede Kiranomena” versus “Notre Dame de bon Remède”), clinic types (e.g., FSP and CSB facilities being coded interchangeably), district names (e.g., Toliary-I versus Toliary-II), and commune names (e.g., Toliara I versus Tanambao I).

We manually reviewed unmatched facilities and identified those with unambiguous matches to the spatial inventory which, for various reasons, failed to match under Step 3.

``` {r step_4-prepwork, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

step = "step_4"
gps_source = "any"
label = "Exact - All sources"

facilities_manual_matches <- read_xlsx(path = paste(data_gps_sources,
                                                    "manual_matching",
                                                    "facilities_manual_matches.xlsx",
                                                    sep = "/")) %>%
    mutate(commune_name_new = ifelse(is.na(commune_name_new), "", commune_name_new))

# tab_step_4 <-

  facilities_manual_matches %>%
  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # select(!c(region_name, region_name_new)) %>%
      select(c(clinic_name, clinic_name_new)) %>%

  rename("Facility name, data" = clinic_name,
         "Facility name, inventory" = clinic_name_new,
         # "Facility type, data" = clinic_type,
         # "Facility type, inventory" = clinic_type_new,
         # "Commune name, data" = commune_name,
         # "Commune name, inventory" = commune_name_new,
         # "District name, data" = district_name,
         # "District name, inventory" = district_name_new,
         # "Region name, data" = region_name,
         # "Region name, inventory" = region_name_new

          )  %>%
  # kable(longtable = T, booktabs = F, caption = "Manual matches across data and expanded spatial inventory") %>%
  #   kable_styling(latex_options = "scale_down") %>%
  #   kable_styling(font_size = 7)

  gt() %>%
    tab_header(
      title = md("**Manual matches across data and expanded spatial inventory: facility names**")) %>%
         tab_options(table.font.names = "Source Sans Pro") %>%
            tab_style(
              locations = cells_column_labels(),
              style     = list(
                cell_text(weight = "bold"))
            ) %>%
      fmt_markdown(columns = everything())

  # %>%
  #   cols_width(
  #     starts_with("Facility name") ~ px(70),
  #           starts_with("Commune name") ~ px(70),
  #
  #   everything() ~ px(60)
  # )

#
# tab_step_4 %>% gtsave("tab_step_4.png")
#
# knitr::include_graphics("tab_step_4.png")

```

``` {r step_4-prepwork-2, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# tab_step_4 <-

  facilities_manual_matches %>%
  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # select(!c(region_name, region_name_new)) %>%
      select(c(clinic_name, clinic_type, clinic_type_new)) %>%

  rename("Facility name, data" = clinic_name,
         # "Facility name, inventory" = clinic_name_new,
         "Facility type, data" = clinic_type,
         "Facility type, inventory" = clinic_type_new,
         # "Commune name, data" = commune_name,
         # "Commune name, inventory" = commune_name_new,
         # "District name, data" = district_name,
         # "District name, inventory" = district_name_new,
         # "Region name, data" = region_name,
         # "Region name, inventory" = region_name_new

          )  %>%
  # kable(longtable = T, booktabs = F, caption = "Manual matches across data and expanded spatial inventory") %>%
  #   kable_styling(latex_options = "scale_down") %>%
  #   kable_styling(font_size = 7)

  gt() %>%
    tab_header(
      title = md("**Manual matches across data and expanded spatial inventory: facility types**")) %>%
         tab_options(table.font.names = "Source Sans Pro") %>%
            tab_style(
              locations = cells_column_labels(),
              style     = list(
                cell_text(weight = "bold"))
            ) %>%
      fmt_markdown(columns = everything())

  # %>%
  #   cols_width(
  #     starts_with("Facility name") ~ px(70),
  #           starts_with("Commune name") ~ px(70),
  #
  #   everything() ~ px(60)
  # )

#
# tab_step_4 %>% gtsave("tab_step_4.png")
#
# knitr::include_graphics("tab_step_4.png")

```

``` {r step_4-prepwork-3, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# tab_step_4 <-

  facilities_manual_matches %>%
  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # select(!c(region_name, region_name_new)) %>%
      select(c(clinic_name, district_name, district_name_new)) %>%

  rename("Facility name, data" = clinic_name,
         # "Facility name, inventory" = clinic_name_new,
         # "Facility type, data" = clinic_type,
         # "Facility type, inventory" = clinic_type_new,
         # "Commune name, data" = commune_name,
         # "Commune name, inventory" = commune_name_new,
         "District name, data" = district_name,
         "District name, inventory" = district_name_new,
         # "Region name, data" = region_name,
         # "Region name, inventory" = region_name_new

          )  %>%
  # kable(longtable = T, booktabs = F, caption = "Manual matches across data and expanded spatial inventory") %>%
  #   kable_styling(latex_options = "scale_down") %>%
  #   kable_styling(font_size = 7)

  gt() %>%
    tab_header(
      title = md("**Manual matches across data and expanded spatial inventory: facility districts**")) %>%
         tab_options(table.font.names = "Source Sans Pro") %>%
            tab_style(
              locations = cells_column_labels(),
              style     = list(
                cell_text(weight = "bold"))
            ) %>%
      fmt_markdown(columns = everything())

  # %>%
  #   cols_width(
  #     starts_with("Facility name") ~ px(70),
  #           starts_with("Commune name") ~ px(70),
  #
  #   everything() ~ px(60)
  # )

#
# tab_step_4 %>% gtsave("tab_step_4.png")
#
# knitr::include_graphics("tab_step_4.png")

```

``` {r step_4-prepwork-4, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# tab_step_4 <-

  facilities_manual_matches %>%
  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
         clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
  mutate(clinic_type_new = ifelse(clinic_type_new == clinic_type, " ~ ", clinic_type_new),
         clinic_name_new = ifelse(clinic_name_new == clinic_name, " ~ ", clinic_name_new),
         district_name_new = ifelse(district_name_new == district_name, " ~ ", district_name_new),
         commune_name_new = ifelse(commune_name_new == commune_name, " ~ ", commune_name_new),
         region_name_new = ifelse(region_name_new == region_name, " ~ ", region_name_new)) %>%
  na_if(., "") %>%
  mutate_all(~replace_na(.,"")) %>%
select(order(colnames(.),
                      decreasing = FALSE)) %>%
#   mutate(clinic_name=str_replace_all(clinic_name," ","<br>"),
# clinic_name_new=str_replace_all(clinic_name_new," ","<br>"),
# clinic_type=str_replace_all(clinic_type," ","<br>"),
# clinic_type_new=str_replace_all(clinic_type_new," ","<br>"),
# commune_name=str_replace_all(commune_name," ","<br>"),
# commune_name_new=str_replace_all(commune_name_new," ","<br>"),
# district_name=str_replace_all(district_name," ","<br>"),
# district_name_new=str_replace_all(district_name_new," ","<br>"),
# region_name=str_replace_all(region_name," ","<br>"),
# region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
    # select(!c(region_name, region_name_new)) %>%
      select(c(clinic_name, commune_name, commune_name_new)) %>%

  rename("Facility name, data" = clinic_name,
         # "Facility name, inventory" = clinic_name_new,
         # "Facility type, data" = clinic_type,
         # "Facility type, inventory" = clinic_type_new,
         "Commune name, data" = commune_name,
         "Commune name, inventory" = commune_name_new,
         # "District name, data" = district_name,
         # "District name, inventory" = district_name_new,
         # "Region name, data" = region_name,
         # "Region name, inventory" = region_name_new

          )  %>%
  # kable(longtable = T, booktabs = F, caption = "Manual matches across data and expanded spatial inventory") %>%
  #   kable_styling(latex_options = "scale_down") %>%
  #   kable_styling(font_size = 7)

  gt() %>%
    tab_header(
      title = md("**Manual matches across data and expanded spatial inventory: facility communes**")) %>%
         tab_options(table.font.names = "Source Sans Pro") %>%
            tab_style(
              locations = cells_column_labels(),
              style     = list(
                cell_text(weight = "bold"))
            ) %>%
      fmt_markdown(columns = everything())

  # %>%
  #   cols_width(
  #     starts_with("Facility name") ~ px(70),
  #           starts_with("Commune name") ~ px(70),
  #
  #   everything() ~ px(60)
  # )

#
# tab_step_4 %>% gtsave("tab_step_4.png")
#
# knitr::include_graphics("tab_step_4.png")

```

``` {r step_4-data-cleaning, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

facilities_manual_matches_temp <- facilities_gps_any %>%
  rename(clinic_name_new = clinic_name_clean,
         clinic_type_new = clinic_type,
         clinic_type_clean_new = clinic_type_clean,
         district_name_new = district_name,
         commune_name_new = commune_name,
         region_name_new = region_name) %>%
  mutate(commune_name_new = ifelse(is.na(commune_name_new), "", commune_name_new)) %>%
  inner_join(., facilities_manual_matches, by = c("clinic_type_new", "clinic_name_new", "region_name_new", "district_name_new", "commune_name_new")) %>%
  select(geometry, commune_name,  region_name, clinic_name_full) %>%
  rename(clinic_name = clinic_name_full) %>%
  inner_join(., facilities_all_nogps, by = c("commune_name", "region_name", "clinic_name")) %>%
  mutate(source = label)

n_manual_matches <- facilities_manual_matches_temp %>% nrow()

facilities_all_gps <- rbind(facilities_all_gps,facilities_manual_matches_temp) %>% unique()

n_matched_facilities_step_3 <- facilities_all_gps %>% nrow()

with_gps <- facilities_all_gps %>% select(facility_ID) %>% unique()
with_gps <- as.vector(with_gps$facility_ID)

facilities_all_nogps <- facilities_all_nogps %>%
  filter(!facility_ID %in% with_gps) %>%
  unique()

rm(facilities_manual_matches_temp, facilities_manual_matches)

```

Manual matching allowed for an additional `r format(as.numeric(n_manual_matches), big.mark = ",")` facilities in our sample being linked to coordinates in our expanded spatial inventory. In total, matching to our expanded inventory in Step 4 led to `r format(as.numeric(n_matched_facilities_step_3), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_3)/n_facilities_new * 100,0)`% of our sample) being geolocated.

**Step 5: Using commune and village centroids as proxies for facility locations**

Among commune-level facilities, there are two potential catchment areas: communes and *fokontany* (villages). Many CSB facilities are named after the village they are located in; this provided us with additional information that could be helpful in geolocation.

```{r step_5-setup, , warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
step = "step_5"
gps_source = "centroid"
label = "Centroid"

```

While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used. The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 30 km. sq. will have the same time series for a given variable. Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.

For commune-level facilities, knowing the catchment area may therefore be just as informative as knowing the facility's precise location if the catchment area was sufficiently small. Determining a cut-off was, again, arbitrary; to adopt a conservative threshold, we considered a catchment area small if its area was  no greater than `r format(as.numeric(area_lim), big.mark = ",")` square km, which corresponded to approximately `r round(as.numeric(area_lim)/(30*30) * 100,0)`% of the area of a climate data spatial resolution tile (Figure \ref{figure_communes_fokontany}).

```{r figure_communes_fokontany, include = TRUE, results = TRUE, warning = FALSE, message = FALSE, echo = FALSE, fig.width = 9, fig.height = 8.5, fig.align='center', out.width = '95%',  fig.scap="Communes and fokontany in Madagascar, by area.", out.extra='',  fig.cap="\\label{figure_communes_fokontany}Communes and fokontany in Madagascar, by area. Units colored in teal are within the 225 square kilometer threshold for use in Step 5 of the matching process."}

#fig.cap="\\label{figure_communes_fokontany}Communes and fokontany, by area."}

# Map where area is binary (smaller than value of commune_lim km sq., vs larger)

map_a <- map_mdg_3 %>%
  mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%
  mutate(area_km_1 = ifelse(area_km <= commune_lim,
                            paste0("<= ",
                                   prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
                                   " km sq."),
                            paste0("> ",
                                   prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
                                   " km sq.")))%>%
  ggplot(aes(geometry = geometry))  +
  geom_sf(size = 0.2,
          aes(fill = area_km_1),
          color = col_grey_light) +
  geom_sf(data = map_mdg_2,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1,
          size = 0.2,
          color = col_black,
          fill = NA) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  labs(fill = "Area (km sq.)",
       title = "Communes",
       subtitle = "(second smallest admin. unit in Madagascar)") +
  scale_fill_manual(values = c(col_within_threshold, col_grey_lightest))

# Saving plot
ggsave(filename = "commune_size_binary.jpg", plot = last_plot(),
       path = gpspath_fig,
       width = 8,
       height = 7,
       bg = "white")

map_b <- map_mdg_4 %>%
  mutate(area_km = as.numeric(st_area(geometry)/1000000)) %>%
  mutate(area_km_1 = ifelse(area_km <= fokontany_lim,
                            paste0("<= ",
                                   prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
                                   " km sq."),
                            paste0("> ",
                                   prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
                                   " km sq.")))%>%
  ggplot(aes(geometry = geometry))  +

  geom_sf(size = 0.2,
          aes(fill = area_km_1),
          color = col_grey_lightest) +
    geom_sf(data = map_mdg_3,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1,
          size = 0.2,
          color = col_black,
          fill = NA) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  labs(fill = "Area (km sq.)",
       title = "Fokontany",
       subtitle = "(smallest admin. unit in Madagascar)") +
  scale_fill_manual(values = c(col_within_threshold, col_grey_lightest))

# Saving plot
ggsave(filename = "fokontany_size_binary.jpg", plot = last_plot(),
       path = gpspath_fig,
       width = 8,
       height = 7,
       bg = "white")

ggarrange(map_a, map_b, ncol = 2, common.legend = TRUE, legend = "bottom")

```

To exploit all available information for geolocation, we first attempted to match commune-level facilities to known *fokontany* based on the facility name and catchment area. We used approximate string matching to link facilities named for their locations in our sample to known villages; if the village area was smaller than our threshold, the centroid of the village was used as a proxy for the facility location. We then applied the same approach to unmatched commune-level facilities to known communes.

```{r step_5-approximate-matches, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

gps_source = "fokontany"
approximate_string_match(facilities_all_nogps, map_mdg_4 , option = "none", type = "centroid_fokontany") # DELETE
approximate_string_match_bind_centroid(1)

gps_source = "commune"
approximate_string_match(facilities_all_nogps, map_mdg_3 , option = "none", type = "centroid_commune") # DELETE
approximate_string_match_bind_centroid(1)

```

Visual inspection of village and commune matches indicated that likely matches had a Levenshtein distance no greater than 1. Using approximate string matching, we linked  `r format(as.numeric(n_adist_fokontany_0), big.mark = ",")` facilities to *fokontany* with identical string matches and  `r format(as.numeric(n_adist_fokontany_1), big.mark = ",")` facilities with near identical matches. After applying our threshold,  `r format(as.numeric(n_matched_facilities_fokontany), big.mark = ",")` facilities in our sample were matched to *fokontany* centroids. We were then able to link `r format(as.numeric(n_adist_commune_0), big.mark = ",")` facilities to communes with identical string matches and  `r format(as.numeric(n_adist_commune_1), big.mark = ",")` facilities with near identical matches. After applying our threshold,  `r format(as.numeric(n_matched_facilities_commune), big.mark = ",")` facilities in our sample were matched to commune centroids.

Altogether, matching to centroids of communes and *fokontany* in Step 5 led to `r format(as.numeric(n_matched_facilities_step_5), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_5)/n_facilities_new * 100,0)`% of our sample) being geolocated.

\newpage

**Step 6: Targeted searches**

```{r step_6-loading-data, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
step = "step_6"
gps_source = "searches"
label = "Searches"

# From this list, some of the facilities have GPS coordinates that can be 
# found from Google and other sources

# CHD facilities from Symphonia    
facilities_chd <- read.xlsx(paste(data_gps_sources_searches, 'CHDD GPS points.xlsx', sep = "/")) %>%
  rename(clinic_name = clinic_nam) %>%
  select(clinic_name, clinic_typ,	region_nam,	district_n, Latitude, Longitude) %>%
  unique() %>%
  mutate(longitude = as.numeric(Longitude),
         latitude = as.numeric(Latitude)) %>%
  rename(clinic_type = clinic_typ, region_name = region_nam, district_name = district_n) %>%
  select(clinic_type, clinic_name,  region_name, district_name, latitude, longitude) %>%
  unique() %>%
  st_as_sf(coords = c("longitude", "latitude"), 
           crs = 4326) %>%
    mutate(gps_type = "Search") %>%
  mutate(full_name = paste(clinic_type, clinic_name, region_name, district_name)) %>%
  mutate(commune_name = "")

# Facilities from Google searching
facilities_gps_search_1 <- read.xlsx(paste(data_gps_sources_searches, 'gps_search.xlsx', sep = "/")) %>%
  filter(location != "") %>%
  select(!c(source, X1)) %>%
  separate(location, c("latitude", "longitude"), sep = ',') %>%
  mutate(longitude = as.numeric(longitude),
         latitude = as.numeric(latitude)) %>%
  unique() %>%
  st_as_sf(coords = c("longitude", "latitude"), 
           crs = 4326) %>%
  select(clinic_name, clinic_type, district_name,  geometry) %>%
  mutate(gps_type = "Search") %>%
  mutate(full_name = paste(clinic_type, clinic_name, district_name, sep = " ")) %>%
  mutate(region_name = "", commune_name = "")

# Facility from additional searches
facilities_gps_search_2 <- read.xlsx(paste(data_gps_sources_searches, 'no_gps_facilities_coordinates.xlsx', sep = "/")) %>%
  filter(LAT != "" | LONG != "") %>%
  select(!c(clinic_name_w_type, ID)) %>%
  mutate(longitude = as.numeric(LONG)/1000000,
         latitude = as.numeric(LAT)/1000000) %>%
  select(!c(LONG, LAT)) %>%
  unique() %>%
  st_as_sf(coords = c("longitude", "latitude"), 
           crs = 4326) %>%
  select(clinic_name, clinic_type, district_name, commune_name, region_name, geometry) %>%
  mutate(gps_type = "Search") %>%
  mutate(full_name = paste(clinic_type, clinic_name,district_name, sep = " "))

# Facility from additional searches
facilities_gps_search_3 <- read.xlsx(paste(data_gps_sources_searches, 'no_gps_facilities_coordinates_2.xlsx', sep = "/")) %>%
  mutate(location = gsub("[\\(\\)]",          # Extract characters within parentheses
                   "",
                   regmatches(location,
                              gregexpr("\\(.*?\\)",
                                       location)))) %>%
  separate(col = location, into = c("longitude", "latitude"), sep = ",") %>%
  st_as_sf(coords = c("longitude", "latitude"), 
           crs = 4326) %>%
  select(clinic_name, clinic_type, district_name, commune_name, region_name, geometry) %>%
  mutate(gps_type = "Search") %>%
  mutate(full_name = paste(clinic_type, clinic_name,district_name, sep = " "))

facilities_gps_searches <- rbind(facilities_chd, facilities_gps_search_1, facilities_gps_search_2, facilities_gps_search_3) %>%
  rename(source = gps_type) %>%
  select(!full_name) %>%
  map_clean_arrondis() %>%
  clean_clinic_name() %>%
  clean_catchment_area() %>%
  select(clinic_name_clean, region_name, district_name, clinic_type_clean, geometry, source) %>%
  group_by(clinic_name_clean, region_name, district_name, clinic_type_clean) %>%
  summarise() %>%
  st_convex_hull() %>%
  st_centroid() %>%
  unique() %>%
  mutate(region_name = ifelse(region_name == "", NA, region_name),
         district_name = ifelse(district_name == "", NA, district_name),
         source = label) %>%
  inner_join(., facilities_all_nogps, by = c("clinic_name_clean", "region_name", "district_name", "clinic_type_clean"))

duplicates <-
    facilities_gps_searches$facility_ID[duplicated(facilities_gps_searches$facility_ID)]

  facilities_gps_searches <- facilities_gps_searches %>%
    filter(!facility_ID %in% duplicates) %>%
    select(facility_ID, geometry, source) %>%
    inner_join(facilities_all)

facilities_all_gps<-rbind(facilities_all_gps, facilities_gps_searches) %>% unique()

clinic_name <- c("FSP Antavy", "CSB1 Andranomanjaka", "FSP Privé Manarenja Doany",
                  "CSB2 Tanandava", "HP Sambaina", "HP RAPHA",
                  "HP Clinique Médico-chirurcical Fénérivé-Est")
longitude <- c(45.5667, 46.8122, 46.6536, 43.74806, 47.136799713867624,
                   47.087107305696314, 49.419187619869184)

latitude <- c(-25.5167, -19.3062, -15.8393, -21.70162, -19.618509327798684,
                  -21.451742175693784, -17.382414260993205)
facilities_all_gps_temp <- as.data.frame(cbind(clinic_name, longitude, latitude)) %>%
  st_as_sf(coords = c("longitude", "latitude"), 
           crs = 4326) %>%
  mutate(source = label) %>%
  inner_join(facilities_all_nogps)

n_targeted_searches_1 <- facilities_gps_searches %>% nrow()

n_targeted_searches_2 <- facilities_all_gps_temp %>% nrow()

facilities_all_gps<-rbind(facilities_all_gps, facilities_all_gps_temp) %>% unique()

n_matched_facilities_step_6 <- facilities_all_gps %>% nrow()

with_gps <- facilities_all_gps %>% select(facility_ID) %>% unique()
with_gps <- as.vector(with_gps$facility_ID)

facilities_all_nogps <- facilities_all %>%
  filter(!facility_ID %in% with_gps) %>%
  unique()

rm(facilities_chd, facilities_gps_search_1, facilities_gps_search_2)

```

We then conducted targeted searches to identify coordinates for unmatched facilities from Google Maps, Mapcarta, and other sources. We identified coordinates for `r format(as.numeric(n_targeted_searches_1 + n_targeted_searches_2), big.mark = ",")` unmatched facilities.

Combined with the previous steps, targeted searches led to `r format(as.numeric(n_matched_facilities_step_6), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_6)/n_facilities_new * 100,1)`% of our sample) being geolocated.

<!-- A visualization of matches across all steps is provided below: -->

```{r step_6-final-prep, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE, results=FALSE}

  # Let's create a map of facilities with GPS data, 
  # by GPS type (exact, centroid, or search)

facilities_all_gps %>%
  ggplot(aes(geometry=geometry)) +
  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_light) +
  geom_sf(alpha = 0.5, aes(color = source)) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  scale_color_manual(values = c(col_centroid,
                                col_exact_all,
                                col_exact_rhino,
                                col_exact_val,
                                col_search),
                     name = "GPS type") +
  labs(title = "Map of facilities in database, by GPS coordinate source")

# Saving plot
ggsave(filename = "facilities_gps_by_source.jpg", plot = last_plot(),
       path = gpspath_fig,
       width = 8,
       height = 7,
       bg = "white")

facilities_all_gps %>%
  mutate(type_2 = clinic_type) %>%
  mutate(type_2 = gsub("CSBU", "CSB", type_2),
         type_2 = gsub("HP", "CH", type_2),
         type_2 = gsub("FSP", "Other/Unknown", type_2),
         type_2 = gsub("Pharmacy", "Other/Unknown", type_2),
         type_2 = case_when(
           str_detect(type_2, "CH") 
           ~ "CHD/CHRR/CHU",
           str_detect(type_2, "CSB") 
           ~ "CSB",
           TRUE ~ type_2)) %>%
  ggplot(aes(geometry=geometry)) +
  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_light) +
  geom_sf(alpha = 0.5, aes(color = type_2)) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  scale_color_manual(values = c(col_CH, col_CSB, col_other),
                     name = "Clinic type") +
  labs(title = "Map of facilities in database, by type",
       color = "Clinic type")

# Saving plot
ggsave(filename = "facilities_gps_by_type.jpg", plot = last_plot(),
       path = gpspath_fig,
       width = 8,
       height = 7,
       bg = "white")
```

```{r step_6-final, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE, results=FALSE}

facilities_all_gps %>%
  ggplot(aes(geometry=geometry)) +
  geom_sf(data = map_mdg_3_un,
          size = 0.2,
          color = col_grey_light,
          fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = col_grey_med,
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_light) +
  geom_sf(alpha = 0.5, aes(color = source)) +
  theme_void() +
  theme(text = element_text(family = "Source Sans Pro")) +
  scale_color_manual(values = c(col_centroid,
                                col_exact_all,
                                col_exact_rhino,
                                col_exact_val,
                                col_search),
                     name = "GPS type")

# facilities_all_gps %>%
#   mutate(type_2 = clinic_type) %>%
#   mutate(type_2 = gsub("CSBU", "CSB", type_2),
#          type_2 = gsub("HP", "CH", type_2),
#          type_2 = gsub("FSP", "Other/Unknown", type_2),
#          type_2 = gsub("Pharmacy", "Other/Unknown", type_2),
#          type_2 = case_when(
#            str_detect(type_2, "CH") 
#            ~ "CHD/CHRR/CHU",
#            str_detect(type_2, "CSB") 
#            ~ "CSB",
#            TRUE ~ type_2)) %>%
#   ggplot(aes(geometry=geometry)) +
#   geom_sf(data = map_mdg_3_un,
#           size = 0.2,
#           color = col_grey_light,
#           fill = NA) +
#   geom_sf(data = map_mdg_2_un,
#           size = 0.2,
#           color = col_grey_med,
#           fill = NA) +
#   geom_sf(data = map_mdg_1_un,
#           size = 0.2,
#           color = col_black,
#           fill = NA) +
#   # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
#   #              size = 2, color = col_grey_light) +
#   geom_sf(alpha = 0.5, aes(color = type_2)) +
#   theme_void() +
#   theme(text = element_text(family = "Source Sans Pro")) +
#   scale_color_manual(values = c(col_CH, col_CSB, col_other),
#                      name = "Clinic type") +
#   labs(#title = "Map of facilities in database, by type",
#        color = "Clinic type")

```

\paragraph*{Validation}

\addcontentsline{toc}{paragraph}{Validation}

```{r validation_prep , warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

# facilities_sample <- facilities_all_gps %>%  sample_frac(sample_fraction)
facilities_sample <- read_excel(paste(gpspath_spread,
                                              "3_validation",
                                              "validation_sample - coordinates.xlsx",
                                              sep = "/")) %>%
  select(!c(Longitude, Latitude, Longitude_search, Latitude_search, Source)) %>%
  rename(clinic_name = "Clinic name",
         region_name = Region,
         district_name= District,
         commune_name = Commune) %>%
  inner_join(., facilities_all_gps, by = c("clinic_name", "region_name", "district_name", "commune_name")) %>%
  st_as_sf() %>%
  mutate(Longitude = sf::st_coordinates(.)[,1],

                          Latitude = sf::st_coordinates(.)[,2]) %>%
   st_drop_geometry()

n_facilities_sample <- facilities_sample %>% nrow()

```

To verify the accuracy of the geolocating process, we randomly selected `r round(as.numeric(sample_fraction * 100,0))`% of our sample of geolocated facilities (n = `r format(as.numeric(n_facilities_sample), big.mark = ",")`) and independently identified coordinates for each facility. We then compared these coordinates to those identified from our geolocating process. We then calculated the physical distance between the independently identified coordinates and the coordinates identified from our geolocating process for each facility.

Table S2.10 provides the list of facilities in the validation sample.

\newpage

\begin{spacing}{1}

\addcontentsline{lot}{table}{Table S2.10: Sample of facilities for validation.}

```{r validation_start, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, results=TRUE}

# facilities_sample <- facilities_sample %>%
#   select(clinic_name_full,  region_name, district_name, commune_name, geometry) %>%
#   st_as_sf() %>%
#       mutate(Longitude = sf::st_coordinates(.)[,1],
#                 Latitude = sf::st_coordinates(.)[,2]) %>%
#   st_drop_geometry() %>%
#   rename("Clinic name" = clinic_name_full,
#          "Region" = region_name,
#          "District" = district_name,
#          "Commune" = commune_name)
# 
# write.xlsx(facilities_sample, file = paste(gpspath_spread,
#                                               "3_validation",
#                                               "validation_sample.xlsx",
#                                               sep = "/"))

tab_2 <- facilities_sample %>%    
  # rename(name = clinic_name) %>%
    #     mutate(name=str_replace_all(name," ","<br>")) %>% 
    #   mutate(region_name=str_replace_all(region_name," ","<br>")) %>% 
    # 
    # mutate(district_name=str_replace_all(district_name," ","<br>")) %>% 
    # mutate(commune_name=str_replace_all(commune_name," ","<br>")) %>%

  select(!c(district_name, commune_name, clinic_name, clinic_type,
            clinic_type_clean, source, facility_ID)) %>%
    rename("Clinic name" = clinic_name_clean,
           Region = region_name) %>%
  mutate(Latitude = round(Latitude, 2),
         Longitude = round(Longitude,2)) %>%
  arrange(Region) %>%
  gt() %>%
    gt_color_rows(Longitude, palette = "ggsci::blue_material") %>%
      gt_color_rows(Latitude) %>%
    tab_header(
      title = md("**Table S2.10: Sample of facilities for validation**")) %>%
  tab_options(table.font.names = "CMU Serif Roman") %>%
  tab_style(locations = cells_column_labels(),
            style     = list(cell_text(weight = "bold"))) %>%
      fmt_markdown(columns = everything())

tab_2
# tab_2 %>% gtsave("tab_2.png")
# 
# knitr::include_graphics("tab_2.png")

```

\end{spacing}

```{r validation-cross, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

facilities_sample <- facilities_sample %>%
  select(clinic_name, region_name, district_name, commune_name,
         Latitude, Longitude) %>%
  rename(Region = region_name, District = district_name, Commune = commune_name)

facilities_sample_matches <- read_excel(paste(gpspath_spread,
                                              "3_validation",
                                              "validation_sample - coordinates.xlsx",
                                              sep = "/")) %>%
  select(!c(Longitude, Latitude)) %>%
  rename(clinic_name = "Clinic name") %>%
  inner_join(., facilities_sample) %>%

  # First, let's say that points must have the same clinic name, district name, and type
  # to be considered to be referring to the same clinic
  mutate(old = paste0(Longitude, " ", Latitude),
         new = paste0(Longitude_search," ", Latitude_search)) %>%
  # select(!c(Longitude, Latitude, "Longitude, search", "Latitude, search")) %>%
  pivot_longer(cols = c("old", "new"), values_to = "geometry", names_to = "type" ) %>%
  separate(   col = geometry,
    sep = " ",
    into = c("long", "lat")) %>%
  st_as_sf(., coords = c("long", "lat"), 
           crs = 4326) %>%

  group_by(clinic_name) %>%

  # For points meeting that criteria, let's gather them into lines (2 points) and polygons (3+ points)
  summarise() %>%

  # For polygons, let's draw the smallest possible border around all points that captures each of them
  st_convex_hull() %>%

  # And calculate the length and area of the resulting groups
  mutate(length = as.numeric(st_length(geometry)/1000)) %>%

  select(clinic_name, length) %>%
  arrange(length)

validation_mean_dist <- mean(facilities_sample_matches$length)
validation_max_dist <- max(facilities_sample_matches$length)

```
\vspace{24 pt}

Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(validation_mean_dist,2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(validation_max_dist, 1), big.mark = ",")` kilometers. The distance between geolocated and validated coordinates for each of the facilities in the validation sample is reported in Table S2.11.

\begin{spacing}{1}

\addcontentsline{lot}{table}{Table S2.11: Distance between geolocated and validated coordinates.}

```{r validation_table, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, results=TRUE}

 facilities_sample_matches %>%         
  st_drop_geometry() %>%
  mutate(length = round(length, 1)) %>%
  rename('Facility name' = clinic_name,
         'Distance (km)' = length) %>%
    gt() %>%
    tab_header(
      title = md("**Table S2.11: Distance between geolocated and validated coordinates**")) %>%
  tab_options(table.font.names = "CMU Serif Roman") %>%
  tab_style(locations = cells_column_labels(),
            style     = list(cell_text(weight = "bold"))) %>%
      fmt_markdown(columns = everything())

```
\end{spacing}

\vspace{24 pt}

From this analysis, we drew strong confidence in the accuracy of our geolocating process and proceeded to obtain climate data for the identified coordinates in our sample.

\newpage

**Glossary**

Translations:

* *Andrefana*: west (Malagasy)
* *Atsimo*: south (Malagasy)
* *Atsinanana*: east (Malagasy)
* *Avaratra*: north (Malagasy)
* *Est*: west (French)
* *Haute*: high (French)
* *Nord*: north (French)
* *Ouest*: west (French)
* *Sud*: south (French)
* *Vaovao*: new (Malagasy)

Acronyms:

* *CMC*: *Clinique Médico-Chirurgicale* (French), medical-surgical clinic
* *EKAR*: *Eglizy Katôlika Apôstôlika Rômanina* (Malagasy), the Roman Catholic Church
* *FJKM*:  *Fiangonan'i Jesoa Kristy eto Madagasikara* (Malagasy), the Church of Jesus Christ in Madagascar 
* *MSI*: MSI Reproductive Choices, formerly Marie Stopes International
* *SALFA*: *Sampanasa Loterana momba ny Fahasalamana* (Malagasy), the health care program of the Malagasy Lutheran Church

\newpage

```{r final_housekeeping, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}

value <- c(n_facilities_who, n_facilities_rhino, n_gps_facilities_new, validation_mean_dist, validation_max_dist)

variable <- c("n_facilities_who",
              "n_facilities_rhino",
              "n_gps_facilities_new",
              "validation_mean_dist",
              "validation_max_dist")

gps_outputs <- as.data.frame(cbind(variable, value))

save(gps_outputs,
     file = paste(gpspath_spread,"1_matched",
                  "gps_outputs.Rdata", sep = "/"))

save(facilities_all_gps,
       file = paste(gpspath_spread,"1_matched",
                    "gps_facilities.Rdata", sep = "/"))

# st_write(facilities_all_gps,
#          paste(gpspath,"3_shapefiles","data_gps.shp", sep = "/"))

write.xlsx(facilities_all_nogps, file = paste(gpspath_spread,
                                              "2_unmatched",
                                              "no_gps_facilities_supplement_2.xlsx",
                                              sep = "/"))

facilities_all_gps_temp <- facilities_all_gps %>%
  st_as_sf()%>%
  unique() %>%
  mutate(longitude = sf::st_coordinates(.)[,1],
         latitude = sf::st_coordinates(.)[,2]) %>%
  st_drop_geometry() %>%
  arrange(facility_ID) %>%
  rename(clinic_code = facility_ID) %>%
  relocate(longitude, .after = latitude)

write.csv(facilities_all_gps_temp, 
     file = paste(gpspath_spread,"1_matched", 
                  "gps_facilities.csv", sep = "/"))

# Record end of code time
end <- proc.time()
end <- as.numeric(end["elapsed"])

pb_text <- paste0("This section of R code ran in ", 
       round((end-start)/60,0),
       " minutes.")

ifelse(require("RPushbullet") == TRUE, 
       pbPost("note", "GSP data compiled", pb_text),
       "")

# st_write(facilities_all_gps,
#          paste(gpspath,"3_shapefiles","data_gps.shp", sep = "/"))

# LEGACY CODE

  # region_names_data <- facilities_all %>% select(region_name) %>% unique()
  # region_names_standard <- map_mdg_1 %>% st_drop_geometry() %>%select(REGION_NAM) %>% unique() %>% arrange(REGION_NAM)
  #
  # region_crosswalk <- cbind(region_names_data, region_names_standard) %>%
  #   mutate(crosswalk = region_name == REGION_NAM)
  #
  #
  #  facilities_all <- facilities_all %>%
  #   mutate(region_name = case_when(
  #     str_detect(region_name, "Amoron'i Mania") ~ "Amoron I Mania",
#     TRUE ~ region_name))
#
# district_names_data <- facilities_all %>% select(region_name, district_name) %>% unique()  %>% arrange(region_name, district_name) %>%
#    filter(!is.na(district_name)) %>% mutate(flag1 = 1)
# district_names_standard <- map_mdg_2 %>% st_drop_geometry() %>%select(REGION_NAM, DISTRICT_N) %>%
#     mutate(DISTRICT_N = case_when(
#     str_detect(DISTRICT_N, "Arrondissement") ~ "Antananarivo Renivohitra",
#     TRUE ~ DISTRICT_N)) %>%
#   unique() %>%
#   arrange(REGION_NAM, DISTRICT_N) %>% mutate(flag2 = 1) %>%
#   rename(region_name = REGION_NAM, district_name = DISTRICT_N)
#
#   district_crosswalk <- full_join(district_names_data, district_names_standard, keep = TRUE)

# 
# %>%
#      mutate(district_name = ifelse(commune_name != "Andrainjato Avaratra" & 
#                                      commune_name != "Andrainjato Sud" &
#                                      commune_name != "Manolafaka" &
#                                      commune_name != "Lalazana" &
#                                      commune_name != "Tanana Ambany" &
#                                      commune_name != "Tanana Ambony" &
#                                      commune_name != "Vatosola" &
#                                      district_name =="Fianarantsoa I",
#                                   "Lalangina",
#                                   district_name ))

# commune_names_data <- facilities_all %>% select(region_name, district_name, commune_name) %>% unique()  %>% arrange(region_name, district_name, commune_name) %>%
#    filter(!is.na(district_name)) %>% filter(!is.na(commune_name)) %>% mutate(flag1 = 1) %>%
#    mutate(full_name = paste(region_name, district_name, commune_name, sep = "-"))
# 
# commune_names_standard <- map_mdg_3 %>% st_drop_geometry() %>%select(COMMUNE_NA, REGION_NAM, DISTRICT_N) %>%
#     mutate(DISTRICT_N = case_when(
#     str_detect(DISTRICT_N, "Arrondissement") ~ "Antananarivo Renivohitra",
#     TRUE ~ DISTRICT_N)) %>%
#   unique() %>%
#   arrange(REGION_NAM, DISTRICT_N, COMMUNE_NA) %>% mutate(flag2 = 1) %>%
#   rename(region_name = REGION_NAM, district_name = DISTRICT_N, commune_name = COMMUNE_NA) %>%
#   mutate(full_name = paste(region_name, district_name, commune_name, sep = "-")) %>%
#   relocate(commune_name, .after = district_name)
# 
# 
# perfect_matches <- commune_names_standard %>% select(full_name) 
# perfect_matches <- perfect_matches$full_name
# 
# commune_names_data_fix <- commune_names_data %>% filter(!full_name %in% perfect_matches)

```

### 2023-02-22 frontmatter.Rmd
Addition of appendices, revisions throughout papers, acknowledgements

--- 2023-02-09 frontmatter.Rmd
@@
 
+\section*{Acknowledgements}
+
 \addcontentsline{toc}{section}{Acknowledgements}
 
-\section*{Acknowledgements}
+I am grateful to the many individuals who have supported and encouraged me throughout my doctoral studies
 
-<!-- Thank you to: -->
+First and foremost, I would like to thank the members of my dissertation committee, Stéphane Verguet, Jessica Cohen, Karestan Koenen, and Margaret McConnell.
+I thank the committee chair, Stéphane Verguet, for his service, and for his exceptional mentorship as my academic advisor.
+Throughout the last four years, he has consistently offered unwavering support and insightful guidance throughout my academic journey, and in the moments where I faltered or doubted myself most, his confidence and cheer always helped see me through.
 
-<!-- Stéphane Verguet -->
-<!-- Margaret McConnell -->
-<!-- Jessica Cohen -->
+Jessica Cohen has been a constant source of joy and inspiration throughout my studies, and her exceptional teaching and scholarship have set a standard to aspire to.
+In addition to being a brilliant scholar, she is an incredible mentor and instructor, bringing genuine joy to the rigorous study of challenging questions.
+Her enthusiasm for econometrics and public health is infectious, and I feel extremely grateful to have learned so much by her example.
 
-<!-- Feedback from: -->
+Karestan Koenen has my deepest gratitude for inviting me to join her research collaboration on climate and mental health in Madagascar, an invitation which transformed the arc of my research and led to subject of this thesis.
+Despite the incredible demands on her schedule as an accomplished scholar and public health leader, she generously shared her expertise with me and her fellow committee members.
+Her insights and suggestions were instrumental in shaping this research, and her encouragement kept me motivated throughout the entire process.
 
-<!-- <!-- Sebastian Bauhoff (early ideas) -->
-<!-- <!-- Kevin Croke (early ideas) --> 
-<!-- <!-- Harvard Center for Population and Development Studies  --> 
-<!-- <!-- David Canning (teaching and econometrics) -->
+Margaret McConnell has been an exceptional teacher, mentor, and colleague, and is one of the most dependable people I know.
+She manages a myriad of commitments with grace, always finding the time to kindle excitement for discovery and to share her thoughts and guidance.
+So many individuals in our department have been fortunate to have her in their corner, and I am ever grateful to be one of them.
 
-<!-- Support from: -->
+I am also deeply grateful to my coauthors, without whom the research in these pages would be immeasurably lessened, and to the reviewers whose thoughtful reflections strengthened every page.
+I thank Shekhar Saxena for his guiding leadership in global mental health and for welcoming me into the field when I first arrived at Harvard, and I thank Christopher Golden for welcoming me into his lab and providing every opportunity, guidance, and support a student could wish for throughout the development of the second paper of this thesis.
 
-<!-- Jarvis Chen -->
-<!-- Bruce Villineau -->
-<!-- Matthew Boccuzzi -->
-<!-- Claudette Agustin -->
+<!-- I also wish to express my gratitude to Judith Bass, who graciously offered to serve as the External Reader for this dissertation, and who fostered my interest in mental health while undertaking my Masters of Public Health degree at Johns Hopkins.
+-->
 
-<!-- Allison Conary -->
-<!-- Barbara Heil -->
+The community in the Department of Global Health and Population has been a treasured home away from home, and I am grateful to so many of its members for the opportunity to learn at their side.
+My deep appreciation goes to David Bloom, David Canning, Margaret Kruk, and Vikram Patel, whose classes and coffee chats all have shaped my interests and the course of my career.
 
-<!-- Friends at HSPH: -->
-<!-- ... -->
-<!-- Family: -->
-<!-- Partner: -->
+Among the acknowledgements of our department's dissertations past, two people who have tirelessly worked to support students on their journeys are highlighted, without fail.
+This dissertation is no exception: to Barbara Heil and Allison Conary, I owe a debt of gratitude for all the mountains they have moved and the uphill struggles they have seen me soundly through.
+
+I also would like to thank the many other individuals at the School of Public Health who have made the last four years so memorable and full of warm memories.
+I am thankful to Claudette Agustin, Matthew Boccuzzi, Jarvis Chen, and Bruce Villineau for all the care and welcome they have shared with me and with each cohort of students in the Population Health Sciences program.
+
+<!--For MIP: Eric Di'Giovanni and Deborah Blacker -->
+
+Across the Charles River are many dear colleagues who have dedicated themselves to ensuring that Harvard feel like home to all its students.
+To Jackie Yun and Janet Daniels at the GSAS Student Center, and to Sheila Thomas, Katie Saibara, and Karina Gonzalez Herrera of the GSAS Office of Equity, Diversity, Inclusion & Belonging, I wish to express my deepest admiration and appreciation.
+
+I am also thankful to the Harvard Center for Population and Development Studies for allowing me to be a part of a vibrant research community, and to Bobby and Johnny Lamont for welcoming me into their home through many trips to Cambridge.
+
+Finally, I would like to thank my friends and family for their love, support, and encouragement.
+They have been a constant source of strength and motivation, and without them none of this would have been possible.
 
@@
 
+\begin{centering}
+
+ *     *     *
+ \vspace{12pt}
+
+\end{centering}
+
 \begin{raggedright}
 
-\emph{Dedicated to ....}
+With all my love and wholehearted gratitude, I dedicate this work to my parents, Drs. Jonathan Arias and Marisela Morales, and to my partner, John Iselin.
+
+\vspace{12pt}
+
+To my parents, your \emph{hijito} hopes that this work honors your lifelong commitment to the pursuit of knowledge and a better world—a devotion only exceeded by the love and support you have shared with me every day of my life.
+
+\vspace{12pt}
+
+To John, my partner, words cannot express how much it has meant to me to call you that. Every step on this journey, love, has been easier with you at my side, with your hand in mine.
+
+\vspace{12pt}
+
+\emph{To the steps we have taken already, and to the many we have ahead.}
 
 \end{raggedright}
+
+\begin{centering}
+
+\vspace{12pt}
+
+ *     *     *
+
+\end{centering}
 

### 2023-02-22 paper1.Rmd
Revising tables to improve readability
Addition of appendices, revisions throughout papers, acknowledgements

@@
 showtext_opts(dpi = 300)  
+library(rnaturalearthhires) # install.packages("rnaturalearthhires", repos = "http://packages.ropensci.org", type = "source")
+
+col_light = "#b1f2ff"
+col_white = "white"
+col_black = "black"
+col_grey_dark = "grey20"
+col_grey_med = "grey40"
+col_grey_light = "grey80"
+col_grey_lightest = "grey85"
+pal <- c("lightskyblue2", "steelblue2", "dodgerblue2", "dodgerblue3", "dodgerblue4", "darkblue")
 
@@
 # Import map data
+# world <- ne_countries(scale = "large", returnclass = "sf")
 world <- ne_countries(scale = "medium", returnclass = "sf")
@@
 world$iso_code[world$adm0_a3 == "SDS"] <- "SSD"
+
+world$iso_code[world$adm0_a3 == "SOL"] <- "SOM"
+
+world <- world %>%
+  group_by(iso_code) %>%
+  st_make_valid() %>% 
+            summarize(geometry = st_union(geometry))
 
@@
 # Merging map and dataframe
-data_rev_map <- full_join(world, data_rev, by = "iso_code") %>% filter(numeric_name == "val")
+data_rev_map <- left_join(world, data_rev, by = "iso_code") %>% filter(numeric_name == "val")
 
@@
   abstract2,
-  "\\% of global DALYs. Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising ",
+  "\\% of global DALYs (Figure 1). Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising ",
   ifelse(results5/results6 > 2.4, "over twice", ifelse(results5/results6> 2, "roughly twice", "approximately twice")),
@@
 With a third of disability-adjusted life years (DALYs) due to NCDs arising from mental disorders, this landmark paper estimated that the value of losses due to mental disorders was roughly 1.3 trillion USD in 2010 (1.6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion USD 2010 (or approximately 3.0 trillion USD in 2019) by 2030.
-(See Supplementary appendix Tables S1 and S2 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]
+(See Tables S1.1 and S1.2 in Appendix 1 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]
 
@@
 The most recent estimates of morbidity and mortality due to mental disorders come from the Global Burden of Disease (GBD) 2019 study.[@vosGlobalBurden3692020a] The GBD study provides disease burden estimates using DALYs, years of life lost (YLLs), and years lived with disability (YLDs), which are then aggregated within a hierarchical grouping scheme that classifies causes of disability and death at different levels of mutually exclusive and completely exhaustive categories.
-(Mental disorders are a Level 2 condition, nested under NCDs; see Table S3.)
+(Mental disorders are a Level 2 condition, nested under NCDs; see Table S1.3.)
 
@@
 
+\begin{raggedright}
+
+\addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}
+
 ```{r table1_1, echo = FALSE, include = TRUE, out.width = '100%'}
@@
 ```
-\addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}
+\end{raggedright}
 
@@
 In addition to our base-case economic valuation, we further report our VSL estimates using three times GDP per capita as the value of a DALY.
-(Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S5 and S6 of the Supplementary appendix.)
+(Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S1.5 and S1.6 of Appendix 1)
 
@@
 \blandscape
-```{r table1_2, echo = FALSE, include = TRUE, out.width = '100%'}
+
+\begin{raggedright}
+
+\addcontentsline{lot}{table}{Table 1.2: Disability-adjusted life years (DALYs) attributable to mental disorders as totals (millions) and percentages of overall burden, by estimation approach.}
+
+```{r table1_2, echo = FALSE, include = TRUE, out.height = '99%'}
 
@@
 ```
-\addcontentsline{lot}{table}{Table 1.2: Disability-adjusted life years (DALYs) attributable to mental disorders as totals (millions) and percentages of overall burden, by estimation approach.}
+
+\end{raggedright}
 
@@
 Estimates of DALYs by country income group and GBD region are reported in Table 1.2.
-(Estimates of deaths are reported in Table S4-6.)
+(Estimates of deaths are reported in Table S1.4-1.6.)
 
@@
 `r results_sentence2`.
-Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S7).
+Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S1.7).
+
+\begin{raggedright}
 
@@
 
-```{r figure_gbd_adjusted, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.", out.extra='', fig.cap=paste("\\label{figure_gbd_adjusted}DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.
-Values are aggregated by GBD region.
-DALYs: Disability-adjusted life years; YLDs: years lived with disability; YLLs: years of life lost; GBD: Global Burden of Disease.", sep=" "), fig.width = 11, fig.height = 11, fig.align='center', out.width = '97%'}
-
-# Figure 1
+\blandscape
+
+```{r figure_dalys_nation, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="DALYs attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.", out.extra='', fig.cap=paste0("\\label{figure_dalys_nation}DALYs attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.
+ATG: Antigua and Barbuda; DALYs: disability-adjusted life years; FSM: Federated States of Micronesia; LCA: Saint Lucia; TLS: East Timor; TTO: Trinidad and Tobago; VCT: Saint Vincent and the Grenadines."), fig.width = 13.7, fig.height = 7.5, fig.align='center', out.width = '98%'}
+
 sf_use_s2(FALSE)
@@
 
+data_temporary <- data_rev_map %>% 
+  filter(measure_id == 2) %>% 
+  filter(estimate_id == 4) %>%
+  st_drop_geometry() %>%
+  select(iso_code, percent)
+
+world_map <- ne_countries(scale = "large", returnclass = "sf")
+# world <- ne_countries(scale = "medium", returnclass = "sf")
+world_map$iso_code <- world_map$gu_a3
+world_map$iso_code[world_map$adm0_a3 == "SDS"] <- "SSD"
+world_map <- left_join(world_map, data_temporary, by = "iso_code")
+
+# First, we make the main map
+fun_create_map_helper <- function(data){
+
+  data_temp <- data %>% 
+  mutate(var_cut = cut(percent, 
+                       breaks =c(0,
+                                 6,
+                                 7,
+                                 8, 
+                                 10,
+                                 12,
+                                 15,
+                                 20, 
+                                 25, 
+                                 30,
+                                 35)))
+
+  data_temp %>%
+    filter(admin != "Antarctica") %>%
+    # group_by(iso_code) %>%
+    # st_make_valid() %>% 
+    # summarize(geometry = st_union(geometry)) %>%
+    # mutate(var_cut = cut(gdp_md_est/1000000, 
+    #                      breaks =c(0, 0.1, 0.2, 0.5, 1, 2, 5, 10, 20, 50, 100))) %>%
+    ggplot(aes(geometry = geometry, fill = var_cut)) +
+    geom_sf(color = col_grey_dark, linewidth = 0.25) +
+    scale_fill_manual(values=setNames(lancet_pal, levels(data_temp$var_cut))) +
+
+    # scale_fill_viridis(option = "mako", discrete = TRUE) +
+    theme_void()
+}
+
+fun_create_map <- function(data, x_1 = -180, x_2 = 180, y_1 = -90, y_2 = 90){
+
+  if(x_1 == -180 &
+     x_2 == 180  & 
+     y_1 == -90  &
+     y_2 == 90 ){
+
+    fun_create_map_helper(data) +
+    theme(legend.position = "bottom") +
+      labs(fill = "% of DALYs") +
+      guides(fill = guide_legend(override.aes =
+                                   list(size = 0.5),
+                                 nrow = 1, 
+                                 byrow = TRUE))
+
+  }else{
+
+    # print(paste0("The x limits of this map are c(",
+    #              min(x_1, x_2),", ",
+    #              max(x_1, x_2)," and the y limits are c(",
+    #              min(y_1, y_2), ", ",
+    #              max(y_1, y_2)))
+
+    fun_create_map_helper(data) + theme(legend.position = "",
+            panel.border = element_rect(colour = "black", fill = NA, linewidth=.5))   +
+      xlim(min(x_1, x_2), max(x_1, x_2)) +
+      ylim(min(y_1, y_2), max(y_1, y_2))
+
+  }
+
+}
+
+main_map_upper <- world_map %>%
+  fun_create_map()
+
+##### Generate band of countries under neath in blocks
+
+distance <- function(measure, coord1, coord2){
+
+  if(measure == "width"){
+    a = coord1[2]
+    b = coord2[2]
+
+  }
+
+  if(measure == "height"){
+    a = coord1[1]
+    b = coord2[1]
+
+  }
+
+  ifelse(a >= 0 & b >= 0, abs(a - b),
+         ifelse(a < 0 & b < 0, 
+                max(abs(a), abs(b)) - min(abs(a), abs(b)),
+
+                abs(abs(a) + abs(b))))
+
+}
+
+fun_lower_block <- function(country = "all", y1 = -90, x1 = -180, y2 = 90, x2 = 180, 
+                            ratio_h_over_w = (0.72/.6), padding = 0.15,
+                            nudge = -9, label = country, 
+                            text_size = 8, orientation = 0.5){
+
+  if(length(country) == 1){
+
+    if(country == "all")
+    {country = world_map$admin}
+
+  }
+
+  coord1 <- c(y1, x1) 
+  coord2 <- c(y2, x2)
+
+  # Calculate the width and width of the original rectangle
+  width <- distance("width", coord1 = coord1, coord2 = coord2)
+  height <- distance("height", coord1 = coord1, coord2 = coord2)
+
+# 
+#   print(paste('Height is ', height,
+#               "and width is ", width))
+
+  # Determine the center point of the rectangle
+  center_lat <- mean(c(coord1[1], coord2[1]))
+  center_lon <- mean(c(coord1[2], coord2[2]))
+
+  ratio = height/width
+
+  x1_new = max(x1, x2)
+  x2_new = min(x1, x2)
+  y1_new = max(y1, y2)
+  y2_new = min(y1, y2)
+
+  # print(paste('Midpoint is ', center_lon,
+  #             ", ", center_lat,
+  #       ". Ratio is ", 
+  #       ratio,
+  #       ". The target is ",
+  #       ratio_h_over_w))
+
+  if (ratio != ratio_h_over_w) {
+
+    # If our ratio is not on target...
+
+    if (ratio > ratio_h_over_w) {
+
+      # and if the height is greater than width, then our figure
+      # is too tall, so we will widen our coordinates...
+
+      width_new_half = (height / ratio_h_over_w)/2
+
+      x1_new = center_lon + width_new_half
+      x2_new = center_lon - width_new_half
+
+    }
+
+    if (ratio < ratio_h_over_w) {
+
+      # but if the height is less than width, then
+      height_new_half = ((width * ratio_h_over_w))/2
+
+      y1_new = center_lat + height_new_half
+      y2_new = center_lat - height_new_half
+
+    }
+
+  } else {
+
+    # print("Ratio is perfect!")
+
+  }
+
+  coord1_new <- c(y1_new, x1_new) 
+  coord2_new <- c(y2_new, x2_new)
+
+  # Calculate the width and width of the original rectangle
+  width <- distance("width", coord1 = coord1_new, coord2 = coord2_new)
+  height <- distance("height", coord1 = coord1_new, coord2 = coord2_new)
+
+  # print(paste0("New ratio is ", height/width))
+
+  # print("Making map")
+
+  map <- world_map %>%
+    filter(admin %in% country) %>%
+    fun_create_map(y_1 = y1_new,  x_1 = x1_new, y_2 = y2_new, x_2 = x2_new) +
+    labs(x = label) +
+    theme(plot.margin = margin(padding, padding, padding, padding, "cm"),
+          panel.border = element_rect(colour = "black", fill = NA, linewidth=.5), 
+          axis.title.x =  element_text(size= text_size,
+                                       margin = margin(t = nudge),
+                                       hjust = orientation),
+          text = element_text(family = "Source Sans Pro")
+
+    )
+          # ,
+          # aspect.ratio=1)
+
+  # print(map)
+
+  return(map)
+
+}
+
+## First block: Caribbean
+
+lower_block_1 <-  fun_lower_block(country = "all",
+                                  23.688123201320412, -86.03651405368969,
+                                  18.26121082729241, -67.8554147013031, 
+                                  label = "Caribbean",
+                                  ratio_h_over_w = 2.5/3.35)
+
+## Second block: Islands in Caribbean
+
+lower_block_2_1 <- fun_lower_block("Antigua and Barbuda",  17.78141711279741, -62.2022030527118,
+                                   16.79458198479592, -61.39269148570997, label = "ATG")
+
+lower_block_2_2 <- fun_lower_block("Saint Vincent and the Grenadines",
+                                     12.391456412985622, -61.60886995955927,
+                                     13.419487110651687, -60.88102575796276, label = "VCT")
+lower_block_2_3 <- fun_lower_block("Barbados", 13.467115495468354, -59.85117377289456,
+                                     12.990476644508814, -59.33382541849154)
+lower_block_2_4 <- fun_lower_block("Comoros", -11.24866626955447, 43.00637992019884,
+                                     -12.442325445847862, 44.68437738632322)
+lower_block_2_5 <- fun_lower_block("Dominica", 15.680375533672533, -61.55835363143402,
+                                    15.069402810985572, -61.143539270458746)
+lower_block_2_6 <- fun_lower_block("Grenada", 12.54522173412346, -61.87752420403268,
+                                     11.883716350869527, -61.371600190809104)
+lower_block_2_7 <- fun_lower_block("Maldives", -0.7281644242049007, 73.00822457449168,
+                                     -0.5575134138293779, 73.29728811799717)
+lower_block_2_8 <- fun_lower_block("Mauritius", -20.620191444040987, 57.15892632861276, 
+                                     -19.903825092697055, 58.00959028441021)
+lower_block_2_9 <- fun_lower_block("Saint Lucia", 14.16262019208292, -61.164375443799265,
+                                     13.539415451808365, -60.76138414727761, label = "LCA")
+lower_block_2_10 <- fun_lower_block("Trinidad and Tobago",11.332779122191509, -61.96117584168811,
+                                    9.724954484064446, -60.4948421071539, label = "TTO")
+lower_block_2_11 <- fun_lower_block("all", -8.055776256847395, 127.5033419027598, 
+                                      -10.365527592170913, 123.86686747667004, label = "TLS")
+
+lower_block_2_12 <- fun_lower_block("Seychelles", -4.164500664831933, 55.08971811357248,
+                                      -4.87593984585334, 56.013554481127436)
+
+lower_block_2 <- cowplot::plot_grid(lower_block_2_1,
+                                    lower_block_2_2,
+                                    lower_block_2_3,
+                                    lower_block_2_4,
+                                    lower_block_2_5,
+                                    lower_block_2_6,
+                                    lower_block_2_7,
+                                    lower_block_2_8,
+                                    lower_block_2_9,
+                                    lower_block_2_10,
+                                    lower_block_2_11,
+                                    lower_block_2_12,
+                                    rel_heights  = c(1,1,1,1,
+                                                   1,1,1,1,
+                                                   1,1,1,1),
+                                    rel_widths = c(1,1,1,1,
+                                                   1,1,1,1,
+                                                   1,1,1,1),
+                                     # align='h', 
+                                     ncol= 4,
+                                     axis='t')
+
+# print(lower_block_2)
+
+## Third block:
+
+lower_block_3_1 <-  fun_lower_block(country = "all",
+                                    label = "West \nAfrica",
+                                    17.55830898122733, -25.766648641326874,
+                                    9.591111921718683, -7.308676054124459,
+                                    ratio_h_over_w = 0.69/0.95,
+                                    nudge = 1)
+
+lower_block_3_2 <-  fun_lower_block(country = "all",
+                                    label = "Persian Gulf",
+                                    31.578724269583038, 46.68534937362107,
+                                    22.201628755387656, 57.91919943035645,
+                                    ratio_h_over_w = 1.34/0.89)
+
+lower_block_3_3 <-  fun_lower_block(country = "all",
+                                    label = "Eastern \nMediterranean",
+                                    35.84337817700235, 32.93408225309256, 
+                                    29.953432571862056, 36.94230952794229,
+                                    ratio_h_over_w = 0.99/0.82,
+                                    nudge = 1) +  theme(aspect.ratio = 1)
+
+lower_block_3_4 <-  fun_lower_block(country = "Malta",
+                                    36.11205138041496, 14.109153467789213,
+                                    35.749543918885365, 14.641990358572649,
+                                    ratio_h_over_w = 0.66/0.82) +  
+  theme(aspect.ratio = 1)
+
+lower_block_3_5 <-  fun_lower_block(country = "Singapore",
+                                    1.562021407805435, 103.52835737520651, 
+                                    1.1508368937798996, 104.17655070980254,
+                                    ratio_h_over_w = 0.8/0.82)
+
+lower_block_3a <- cowplot::plot_grid(lower_block_3_1,
+                                     lower_block_3_2,
+
+                                     rel_heights  = c(0.99,1.72),
+                                     rel_widths = c(1,1),
+                                     align='h',
+                                     nrow= 2,
+                                     axis='t')
+
+lower_block_3b <- cowplot::plot_grid(lower_block_3_3,
+                                     lower_block_3_4,
+                                     lower_block_3_5,
+                                     rel_heights  = c(0.99,
+                                                      0.8,
+                                                      0.8),
+                                     rel_widths = c(1,1,1),
+                                     align='h',
+                                     nrow= 3,
+                                     axis='t')
+
+lower_block_3 <- cowplot::plot_grid(lower_block_3a,
+                                    lower_block_3b,
+                                    rel_widths =  c(0.89,0.82),
+                                    rel_heights = c(1,1),
+                                    align='h',
+                                    ncol= 2,
+                                    axis='t')
+
+# print(lower_block_3)
+
+## Fourth block: Balkans
+
+lower_block_4 <-  fun_lower_block(country = "all",
+                                  51.618805792153864, 32.14547175934774, 
+                                  35.76671479197162, 12.574073798467166, 
+                                  label = "Balkan Peninsula",
+                                  ratio_h_over_w = 2.47/2.75) +
+  theme(aspect.ratio = 1)
+
+# print(lower_block_4)
+
+## Fifth block: Pacific Islands
+lower_block_5_1 <-  fun_lower_block(country = "Marshall Islands",
+                                    7.271576767058141, 170.97346175839462,
+                                    7.0021405106753924, 171.43254628562116,
+                                  label = "Marshall Isl",
+                                  ratio_h_over_w = 0.67/0.72)
+
+lower_block_5_2 <-  fun_lower_block(country = "Solomon Islands",
+                                    -6.19982314293495, 156.2033043837379,
+                                    -12.305942792508677, 162.7810192195895,
+                                    label = "Solomon Isl",
+                                    ratio_h_over_w = 0.43/0.72)
+
+lower_block_5_3 <-  fun_lower_block(country = "Vanuatu",
+                                    -12.522849273606965, 164.09680570696634,
+                                    -21.865505295764667, 170.85928793776827,
+                                    ratio_h_over_w = 0.43/0.72)
+
+lower_block_5_4 <-  fun_lower_block(country = "Fiji",
+                                    -16.016715539187006, 177.43916612705263,
+                                    -19.202928284064122, 180,
+                                    ratio_h_over_w = 0.55/0.72)
+
+lower_block_5_5 <-  fun_lower_block(country = "Kiribati",
+                                    1.6783742083055109, 172.8245591145513,
+                                    1.2886789414361417, 173.1873840281737,
+                                    ratio_h_over_w = 0.67/0.69)
+
+lower_block_5_6 <-  fun_lower_block(country = "Federated States of Micronesia",
+                                    7.123620054481302, 157.66021976354537,
+                                    6.527385048863808, 158.46395741107983,
+                                    label = "FSM",
+                                    ratio_h_over_w = 0.43/0.69)
+
+lower_block_5_7 <-  fun_lower_block(country = "Samoa",
+                                   -13.245725830105162, -173.15052189891833,
+                                   -14.849661425405092, -171.1345307337241,
+                                    ratio_h_over_w = 0.43/0.69)
+
+lower_block_5_8 <-  fun_lower_block(country = "Tonga",
+                                    -20.999167868460994, -175.48041913403475,
+                                    -21.50983734571705, -174.8335990873945,
+                                    ratio_h_over_w = 0.55/0.69)
+
+lower_block_5a <- cowplot::plot_grid(lower_block_5_1,
+                                     lower_block_5_2,
+                                     lower_block_5_3,
+                                     lower_block_5_4,
+                                    rel_heights  = c(0.67,0.43,
+                                                     0.43, 0.55),
+                                    rel_widths = c(1,1,1,1),
+                                    align='h',
+                                    nrow= 4,
+                                    axis='t') 
+lower_block_5b <- cowplot::plot_grid(lower_block_5_5,
+                                     lower_block_5_6,
+                                     lower_block_5_7,
+                                     lower_block_5_8,
+                                     rel_heights  = c(0.67,0.43,
+                                                      0.43, 0.55),
+                                     rel_widths = c(1,1,1,1),
+                                     align='h',
+                                     nrow= 4,
+                                     axis='t')
+
+lower_block_5 <- cowplot::plot_grid(lower_block_5a,
+                                    lower_block_5b,
+                                    rel_widths =  c(0.72,0.69),
+                                    rel_heights = c(1,1),
+                                    align='h',
+                                    ncol= 2,
+                                     axis='t')
+
+# print(lower_block_5)
+
+### Joining all blocks together
+
+main_map_lower <- cowplot::plot_grid(lower_block_1,
+                                     lower_block_2,
+                                     lower_block_3,
+                                     lower_block_4,
+                                     lower_block_5,
+                                     rel_widths = c(3.32,
+                                                    3.22,
+                                                    1.92,
+                                                    2.73,
+                                                    1.82),
+                                     rel_heights = c(1,1,1,1,1),
+                                     align='h', 
+                                     ncol=5, 
+                                     axis='t')
+
+### Joining upper and lower blocks together
+
+main_map_combined <- cowplot::plot_grid(main_map_upper,
+                                        main_map_lower,
+                                        rel_heights = c(5.9, 2.8),
+                                        rel_widths = c(1,1),
+                                        align='v', 
+                                        nrow = 2,
+                                        axis='l')
+main_map_combined
+
+```
+
+\elandscape
+
+\end{raggedright}
+
+```{r figure_gbd_adjusted, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.", out.extra='', fig.cap=paste0("\\label{figure_gbd_adjusted}DALYs, YLDs, YLLs, and deaths attributable to mental disorders in 2019, by estimation approach, per 100,000 population.
+Values are aggregated by GBD region.
+DALYs: Disability-adjusted life years; YLDs: years lived with disability; YLLs: years of life lost; GBD: Global Burden of Disease."), fig.width = 11, fig.height = 11, fig.align='center', out.width = '97%'}
+
+# Figure 1
+sf_use_s2(FALSE)
+
+k = "rate_per_100k"
+
 j = 1
-i = "ihme_region"
-k = "rate_per_100k"
-m = "abs"
 
@@
   geom_sf(data = . %>%   group_by(ihme_region) %>% 
-            st_set_precision(1e4) %>%
+            st_make_valid() %>% 
             summarize(geometry = st_union(geometry)), fill = "transparent", color = 'black', size = 0.02) +
@@
 Figure \ref{figure_cost_by_region} displays the economic burden of disease due to mental disorders under the three estimation approaches by GBD region, as a percent of regional GDP.
-(Estimates by absolute values per DALY are provided in the Supplementary appendix, along with mapped data visualizing estimates across all values per DALY.) Across approaches, the greatest change in estimated burden occurs in Eastern Europe, Latin America, North America, and Southern sub-Saharan Africa.
+(Estimates by absolute values per DALY are provided in Appendix 1, along with mapped data visualizing estimates across all values per DALY.) Across approaches, the greatest change in estimated burden occurs in Eastern Europe, Latin America, North America, and Southern sub-Saharan Africa.
 `r results_sentence3`

### 2023-02-22 paper2.Rmd
Revising tables to improve readability
Addition of appendices, revisions throughout papers, acknowledgements

@@
 
-source("C:/Users/danie/Dropbox (Harvard University)/madagascar_mh/code/0_a_packages_and_paremeters_do_file.R")
+# Loading libraries
+# library(MASS) # We load this and then detach it just to clear the package
+# library(margins) # We load this and then detach it just to clear the package
+# library(lme4) # We load this and then detach it just to clear the package
+# detach("package:lme4", unload=TRUE) # Needed to use dplyr's select function
+# detach("package:margins", unload=TRUE) # Needed to use dplyr's select function
+# detach("package:MASS", unload=TRUE) # Needed to use dplyr's select function
+library(readxl)
+library(readr)
+library(dplyr)
+library(zoo)
+library(tidyr)
+library(psych)
+library(ggplot2)
+library(RColorBrewer)
+library(sp)
+library(broom)
+library(sf)
+library(scales)
+library(viridis)
+library(data.table)
+library(ggpubr)
+library(ggmap)
+library(maps)
+library(mapdata)
+library(ggrepel)
+library(table1)
+library(stringr) 
+library(stringi)
+library(fixest)
+library(stats)
+library(lubridate)
+library(forecast)
+library(gtools)
+# library(devtools)
+library(reticulate)
+library(stargazer)
+library(lwgeom)
+if (!require("ggsflabel")) devtools::install_github("yutannihilation/ggsflabel")
+library(openxlsx)
+library(gganimate)
+library(transformr)
+library(huxtable)
+library(ggtext)
+library(margins)
+library(ncdf4) # package for netcdf manipulation
+library(magrittr)
+library(lmtest)
+library(sandwich)
+library(rgee)
+library(gt)
+library(knitr)
+library(webshot2)
+library(sysfonts)
+library(showtext)
+font_add_google("Source Sans Pro")
+library(gridExtra)
+library(tibble)
+showtext_auto() 
+showtext_opts(dpi = 300)  
+# library(googledrive)
+# drive_auth(email = TRUE)
+library(rmdHelpers)
+library(gtExtras)
+library(kableExtra)
+library(DescTools)
+library(rvest)
+library(httr)
+library(polite)
+library(janitor)
+library(cowplot)
+library(ggridges)
+# library(ggsn)
+
+# library(glmmTMB)
+
+# Setting directories - change these to your local directory
+path <- 'C:/Users/danie/Dropbox (Harvard University)/madagascar_mh'
+code <- paste(path,'code', sep = "/")
+path_python  = "C:/Users/danie/AppData/Local/Programs/Python/Python310/python.exe"
+
+# Data
+datasource <- paste('C:/Users/danie/Dropbox (Harvard University)/data',
+                    sep = "/") # The complete data set is not uploaded to 
+# Github. Ask golden@hsph.harvard.edu for access. 
+datapath <- paste(path,'data', sep = "/")
+datapath_reference  <- paste(datapath,'0_reference', sep = "/")
+data_mh_chd  <- paste(datapath,'1_mental_health', sep = "/")
+data_mh_csb <- data_mh_chd  
+data_mh_chu_chrr <- paste(data_mh_chd,'pathologies neuropsychiatriques CHU CHRR', sep = "/")
+data_gps <- paste(datapath,'2_gps', sep = "/")
+data_gps_sources <- paste(data_gps,'gps_sources', sep = "/")
+data_gps_sources_searches <- paste(data_gps_sources,'searches', sep = "/")
+data_gps_sources_reposit <- paste(data_gps_sources,'repositories', sep = "/")
+data_climate_path  <- paste(datapath,'3_climate', sep = "/")
+data_climate_era  <- paste(data_climate_path,'ERA5', sep = "/")
+data_climate_esa  <- paste(data_climate_path,'ESA_CCI', sep = "/")
+
+# Results
+resultspath <- paste(path,'results', sep = "/")
+mh_path <- paste(resultspath,'1_mental_health', sep = "/")
+gpspath <- paste(resultspath,'2_gps', sep = "/")
+gpspath_admin_names <- paste(gpspath,'0_reference', sep = "/")
+gpspath_fig <-  paste(gpspath,'1_figures', sep = "/")
+gpspath_spread <-  paste(gpspath,'2_spreadsheets', sep = "/")
+gpspath_spread_fuzzy <-  paste(gpspath_spread,'3_fuzzy_matching', sep = "/")
+analysispath <- paste(resultspath,'4_analysis', sep = "/")
+analysis_figures <- paste(analysispath,'1_figures', sep = "/")
+analysis_models <- paste(analysispath,'3_models', sep = "/")
+
+# Shapefiles
+mappath <- paste(path,'shapefiles', sep = "/")
+mappath_MOH <- paste(mappath,'MOH', sep = "/")
+mappath_OCHA <- paste(mappath,'OCHA', sep = "/")
+
+# Color palette 
+col_light = "cyan4"
+col_dark = "cyan3"
+col_bright = "coral"
+col_black = "black"
+col_grey_dark = "grey20"
+col_grey_med = "grey40"
+col_grey_light = "grey80"
+col_grey_lightest = "grey85"
+col_soilmoisture = col_dark
+col_temperature = col_light
+col_interaction = col_bright
+col_cyclone = "steelblue2"
+
+pal <- c("lightskyblue2", "steelblue2", "dodgerblue2", "dodgerblue3", "dodgerblue4", "darkblue")
+
+col_within_threshold = "cyan3"
+col_beyond_threshold = "coral"
+
+col_centroid <- "grey20"
+col_exact_all <- "cyan2"
+col_exact_rhino <- "cyan3"
+col_exact_val <- "cyan4"
+col_search <- "coral"
+
+col_CH <- "coral"
+col_CHD <- "coral1"
+col_CHR <- "coral3"
+col_CSB <- "steelblue2"
+col_CSB1 <- "steelblue1"
+col_CSB2 <- "steelblue3"
+col_other <-  "grey20"
+
+col_model_main <- "#F3AB00"
+col_model_other <- col_grey_med
+col_spec_yes <-  "#73BDBF"
+col_spec_no <-  "white"
+
+col_cases <- "chartreuse3"
+col_no_cases <- "deeppink3"
+
+col_eco_rainforest <-"#32A42F"
+col_eco_highlands <- "#B9CF19"
+col_eco_arid <- "#FEEE19"
+col_eco_drydecid <- "#FCAF3E"
+
+# Thresholds
+# These are cut off values that will be used in the GPS do file
+
+length_lim <- 15  # The maximum distance allowed when the same facility has
+# two GPS coordinates in the data sources for the center of
+# those two coordinates to be used as the facility's location.
+# Note: the selection of 15 is arbitrarily conservative. Spatial resolution of 
+# climate data is typically ~ 30km x 30 km
+
+area_lim <- length_lim*length_lim
+
+# The maximum area of the convex hull allowed when the same facility has
+# 3+ GPS coordinates in the data sources for the centroid of
+# that convex hull to be used as the facility's location
+
+fokontany_lim <- area_lim    # A small fokotanty is one that is ____ km ^2 or smaller
+
+commune_lim <- area_lim    # A small commune is one that is ____ km ^2 or smaller
+
+# Lags: specify how many lags you want for the explanatory variables (e.g., soil moisture, temp)
+
+lags_number <- 18
+
+# Climate data start and end date
+start_date <- as.Date("2010-01-01")
+end_date <- as.Date("2020-07-01")
+
+start_date_climate <- start_date - lags_number*31 #This ensures there is data for the lagged exposure
+end_date_climate <- end_date
+
+# ESA CCI trim dates
+date1 <- 200801
+date2 <- 202112
+
+# Seed and sampling fraction
+set.seed(1960) # Madgascar's year of independence
+sample_fraction = .01
+
+######################
+##      MAPS        ##
+######################
+#   
+# # There are two map options available. One set of shapefiles were available
+# # from humdata.org, while the other set was provided by the MOH.
+#   
+# # Loading high-resolution maps of St. Lucia (from data.humdata.org)
+map_mdg_0_un <- st_read(paste0(mappath_OCHA,"/",
+                               "mdg_admbnda_adm0_BNGRC_OCHA_20181031.shp"))
+map_mdg_1_un <- st_read(paste0(mappath_OCHA,"/",
+                               "mdg_admbnda_adm1_BNGRC_OCHA_20181031.shp"))
+map_mdg_2_un <- st_read(paste0(mappath_OCHA,"/",
+                               "mdg_admbnda_adm2_BNGRC_OCHA_20181031.shp"))
+map_mdg_3_un <- st_read(paste0(mappath_OCHA,"/",
+                               "mdg_admbnda_adm3_BNGRC_OCHA_20181031.shp"))
+loaded_maps_un <- 1
+
+# Load in data from MOH
+map_mdg_0 <- st_read(paste0(mappath_MOH,"/",
+                            "adm0_mada_utm38S.shp"))
+map_mdg_1 <- st_read(paste0(mappath_MOH,"/",
+                            "adm1_mada_utm38S.shp"))
+map_mdg_2 <- st_read(paste0(mappath_MOH,"/",
+                            "adm2_mada_utm38S.shp"))
+map_mdg_3 <- st_read(paste0(mappath_MOH,"/",
+                            "adm3_mada_utm38S.shp"))
+map_mdg_4 <- st_read(paste0(mappath_MOH,"/",
+                            "adm4_mada_utm38S.shp"))
 
@@
 load(file = paste(resultspath,"3_climate", 
-                  "climate_facilities.Rdata", sep = "/"))
+                  "climate_facilities_subset.Rdata", sep = "/"))
 
@@
 
-n_facilities_sm <- data_climate %>% 
+n_facilities_sm <- data_climate_subset %>% 
   filter(date == "Jan 2010") %>%
-  dplyr::select(sm_monthly, facility_ID) %>%
-  filter(!is.na(sm_monthly)) %>%
+  dplyr::select(sm_mean, facility_ID) %>%
+  filter(!is.na(sm_mean)) %>%
   dplyr::select(facility_ID) %>%
@@
 
-n_facilities_sm_missing <- data_climate %>% 
+n_facilities_sm_missing <- data_climate_subset %>% 
   filter(date == "Jan 2010") %>%
-  dplyr::select(sm_monthly, facility_ID) %>%
-  filter(is.na(sm_monthly)) %>%
+  dplyr::select(sm_mean, facility_ID) %>%
+  filter(is.na(sm_mean)) %>%
   dplyr::select(facility_ID) %>%
@@
 The nonparametric Friedman’s super smoother regression estimator[@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation.[@hyndmanAutomaticTimeSeries2008] By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may reflect true variances in incidence (for example, incidences reported by a large, regional reference hospital) while addressing potential errors in data entry.
-(Additional detail on the data cleaning process is available in the Supplementary appendix.)
+(Additional detail on the data cleaning process is available in Appendix 2.1)
 
@@
 First, region, district, and commune names in our sample were standardized against reference shapefiles to address variations in translation, abbreviation, transposition, accent marks, spacing, hyphenation, and spelling.
-(A summary of the standardized names is provided in the Supplementary appendix.) Next, facility names, types, and associated administrative units were used to match facilities to a validated spatial inventory of health facilities in Sub-Saharan Africa,[@mainaSpatialDatabaseHealth2019] of which `r format(as.numeric(n_facilities_who), big.mark = ",")` coordinates were provided for public facilities in Madagascar.
+(A summary of the standardized names is provided in Appendix 2.2.) Next, facility names, types, and associated administrative units were used to match facilities to a validated spatial inventory of health facilities in Sub-Saharan Africa,[@mainaSpatialDatabaseHealth2019] of which `r format(as.numeric(n_facilities_who), big.mark = ",")` coordinates were provided for public facilities in Madagascar.
 In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented approximate string matching, which allowed for facility names and administrative units to be matched approximately, rather than exactly, to corresponding patterns in the validated spatial inventory.
@@
 Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` kilometers, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data.
-Additional detail on the geolocating and validation process is available in the Supplementary appendix.
+Additional detail on the geolocating and validation process is available in Appendix 2.2.
 
@@
 Model 3 used both temperature and soil moisture independently as predictors, while Model 4—our preferred model—introduced an interaction term between the two.
+
 Duration of cyclone activity was included in all models using our count indicator of exposure.
@@
 
+\begin{raggedright}
+
 ```{r table2_1, echo = FALSE, include = TRUE, out.width = '100%'}
@@
 \addcontentsline{lot}{table}{Table 2.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis}
+
+\end{raggedright}
 
@@
 
-panel_a <- data_climate %>%
-  filter(statistic == e) %>%
-  dplyr::select(date, facility_ID, temp_monthly) %>%
+panel_a <- data_climate_subset %>%
+  dplyr::select(date, facility_ID, mean_2m_air_temperature) %>%
   unique() %>%
   inner_join(., facilities_all_gps) %>%
-  dplyr::select(date, geometry, facility_ID, temp_monthly) %>%
+  dplyr::select(date, geometry, facility_ID, mean_2m_air_temperature) %>%
   filter(date == "Jan 2015" | date == "June 2015" ) %>%
@@
   # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
-  geom_sf(alpha = 0.9, size = .7, aes(color = temp_monthly)) +
+  geom_sf(alpha = 0.9, size = .7, aes(color = mean_2m_air_temperature)) +
   theme_void() +
@@
 
-panel_b <-  data_climate %>%
-  filter(statistic == e) %>%
-  dplyr::select(date, facility_ID, sm_monthly) %>%
+panel_b <-  data_climate_subset %>%
+  dplyr::select(date, facility_ID, sm_mean) %>%
   unique() %>%
   inner_join(., facilities_all_gps) %>%
-  dplyr::select(date, geometry, facility_ID, sm_monthly) %>%
+  dplyr::select(date, geometry, facility_ID, sm_mean) %>%
   filter(date == "Jan 2015" | date == "June 2015" ) %>%
@@
   # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
-  geom_sf(alpha = 0.9, size = .9, aes(color = sm_monthly)) +
+  geom_sf(alpha = 0.9, size = .9, aes(color = sm_mean)) +
   theme_void() +
@@
 
-panel_a <- data_climate %>%
+panel_a <- data_climate_subset %>%
   mutate(date = as.yearmon(date),
@@
   filter(year != "2022") %>%
-  ggplot(aes(x=temp_monthly, y = year, fill = stat(x))) +
+  ggplot(aes(x=mean_2m_air_temperature, y = year, fill = stat(x))) +
   geom_density_ridges_gradient() +
@@
 
-panel_b <- data_climate %>%
+panel_b <- data_climate_subset %>%
   mutate(date = as.yearmon(date),
@@
   filter(year != "2022") %>%
-  ggplot(aes(x=sm_monthly, y = year, fill = stat(x))) +
+  ggplot(aes(x=sm_mean, y = year, fill = stat(x))) +
   geom_density_ridges_gradient() +
@@
 
-# panel_a <- data_climate %>%
+# panel_a <- data_climate_subset %>%
 #   mutate(date = as.yearmon(date),
@@
 #
-# panel_b <- data_climate %>%
+# panel_b <- data_climate_subset %>%
 #   mutate(date = as.yearmon(date),
@@
 
+Results from our subgroup analysis showed evidence of potential effect heterogeneity by ecoregion (Table 2.3).
+For temperature, estimates of association were only statistically significant in the highland subhumid forests, where each one-degree Celsius increase in temperature was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = "only")` cases reported `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = TRUE)`.
+Temperature was associated with a slight increase in temperature in the eastern lowland forests `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)` and the desert and xeric shrublands `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)`, but in neither case was the estimate significant at a level of 0.05.
+
+\begin{spacing}{1.5}
+
 ```{r table_3, include = TRUE, echo=FALSE, warnings = FALSE}
@@
 
+\end{spacing}
+
 \addcontentsline{lot}{table}{Table 2.3: Subgroup analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
-
-Results from our subgroup analysis showed evidence of potential effect heterogeneity by ecoregion (Table 2.3).
-For temperature, estimates of association were only statistically significant in the highland subhumid forests, where each one-degree Celsius increase in temperature was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = "only")` cases reported `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = TRUE)`.
-Temperature was associated with a slight increase in temperature in the eastern lowland forests `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)` and the desert and xeric shrublands `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)`, but in neither case was the estimate significant at a level of 0.05.
 
@@
 
-rm(packages_and_paremeters_on)
+rm(packages_and_paremeters_on, data_climate, data_climate_subset, map_mdg_0, map_mdg_0_un,
+   map_mdg_1, map_mdg_1_un, map_mdg_2, map_mdg_2_un)
 

### 2023-02-22 paper3.Rmd
Revising tables to improve readability
Addition of appendices, revisions throughout papers, acknowledgements

--- 2023-02-10 paper3.Rmd
@@
 ```{r loading, include=FALSE}
+  # Loading libraries
+  library(readxl)
+  library(readr)
+  library(dplyr)
+  library(zoo)
+  library(tidyr)
+  library(psych)
+  library(ggplot2)
+  library(RColorBrewer)
+  library(sp)
+  library(broom)
+  library(sf)
+  library(scales)
+  library(viridis)
+  library(data.table)
+  library(ggpubr)
+  library(ggmap)
+  library(maps)
+  library(mapdata)
+  library(ggrepel)
+  library(table1)
+  library(stringr) 
+  library(stringi)
+  library(fixest)
+  library(stats)
+  library(lubridate)
+  library(forecast)
+  library(gtools)
+  library(stargazer)
+  library(lwgeom)
+  library(openxlsx)
+  library(gganimate)
+  library(transformr)
+  library(huxtable)
+  library(ggtext)
+  library(magrittr)
+  library(lmtest)
+  library(sandwich)
+  library(rgee)
+  library(gt)
+  library(knitr)
+  library(webshot2)
+  library(sysfonts)
+  library(showtext)
+  font_add_google("Source Sans Pro")
+  library(gridExtra)
+  library(tibble)
+  showtext_auto() 
+  showtext_opts(dpi = 300)  
+  library(augsynth)
+  library(dvmisc)
+  library(forcats)
+  library(rmdHelpers)
 
-source("C:/Users/danie/Dropbox (Harvard University)/mh_scm/code/0_prep_file.R")
+  # Setting directories - change these to your local directory
+  path <- 'C:/Users/danie/Dropbox (Harvard University)/mh_scm'
+
+  codepath <- paste(path,'code', sep = "/")
+
+  # Github. Ask golden@hsph.harvard.edu for access. 
+  datapath <- paste(path,'data', sep = "/")
+
+  # Results
+  resultspath <- paste(path,'results', sep = "/")
+
+  # Shapefiles
+  mappath <- paste(path,'shapefiles', sep = "/")
+
+  # Color palette 
+  col_light = "cyan4"
+  col_dark = "cyan3"
+  col_bright = "coral"
+  col_black = "black"
+  col_grey_dark = "grey20"
+  col_grey_med = "grey40"
+  col_grey_light = "grey80"
+  col_grey_lightest = "grey85"
+  col_soilmoisture = col_dark
+  col_temperature = col_light
+  col_interaction = col_bright
+  col_mh = "steelblue3"
+  col_headache = "grey50"
+
+  col_model_main <- "#F3AB00"
+  col_model_other <- col_grey_med
+  col_spec_yes <-  "#73BDBF"
+  col_spec_no <-  "white"
+
+  col_positive <- "salmon1"
+  col_negative <-"steelblue2"
+
+  col_all <- "plum3"
+  col_dem <- "steelblue2"
+  col_red <- "red2"
+
+  # Seed 
+  set.seed(4800)
+
+  ######################
+  ##      DATES        ##
+  ######################
+
+  date_shock_vax <- as.Date("2020-11-16")
+  trim_bandwidth = 60
+
+  start_date <-  date_shock_vax -  trim_bandwidth  #as.Date("2020-06-01")
+  end_date <- date_shock_vax + trim_bandwidth  #as.Date("2021-05-31")
+
+  disorders <- c("anxiety", "depression", "fever", "generalized_anxiety_disorder",
+                 "hair_loss", "headache", "major_depressive_disorder",
+                 "pain","panic_attack","sleep_disorder")
+
+  week_shock_vax <- floor(as.numeric((date_shock_vax - start_date) / 7))
 
@@
 load(file = paste(resultspath, "1_data",
-                  "model_outputs_all_main.Rdata", sep = "/"))
+                  "model_outputs_main.Rdata", sep = "/"))
 
 load(file = paste(resultspath, "1_data",
-                  "model_outputs_all_US.Rdata", sep = "/"))
+                  "model_outputs_political.Rdata", sep = "/"))
 
 load(file = paste(resultspath, "1_data",
-                  "model_outputs_all_international.Rdata", sep = "/"))
+                  "model_outputs_multiverse.Rdata", sep = "/"))
 
 load(file = paste(resultspath, "1_data",
-                  "model_outputs_all_diseases.Rdata", sep = "/"))
+                  "model_outputs_international.Rdata", sep = "/"))
+
+load(file = paste(resultspath, "1_data",
+                  "model_outputs_its.Rdata", sep = "/"))
 
@@
 
-model_output_main <- model_outputs_all_US %>%
+model_output_main <- model_outputs_political %>%
   function_model_main()
@@
     mutate(disease = ifelse(disease == "Attention deficit hyperactivity disorder", "ADHD", disease),
+           disease = ifelse(disease == "Clouding of consciousness", "CoC", disease),
            disease = ifelse(disease == "Generalized anxiety disorder", "GAD", disease),
@@
 
-list_diseases_all <- read.xlsx(paste(datapath, 
+list_mental_health_symptoms <- read.xlsx(paste(datapath, 
                                                "list_of_diseases.xlsx", sep = "/")) %>%
@@
 
-list_diseases_all <- list_diseases_all$search
+list_mental_health_symptoms <- list_mental_health_symptoms$search
 
@@
 
+controlled interrupted time series (CITS) 
+interrupted time series (ITS)
+
 * Motivation to explore vaccine announcement: evidence that vaccination itself reduced depression and anxiety -- do we see earlier reductions from an anticipatory effect?
@@
 
-We take as our first credible signal of the imminent availability of safe and effective COVID-19 vaccines to be November 16, 2020.
+We take as our first credible signal of the imminent availability of multiple safe and effective COVID-19 vaccines to be November 16, 2020.
 On November 9, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16th, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S.
-Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners and laypersons as a substantial signal of a new phase of the pandemic, with Moderna's chief executive officer calling the news "a game changer" in the fight against COVID-19.
+Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
 
@@
 
-We access U.S.
-county- and state-level data from Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020](hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021 for six symptoms: anxiety, depression, generalized anxiety disorders, headache, major depressive disorders, and panic attacks.
-Data on headaches was obtained to provide a control trend from a common health symptom with comparative characteristics to mental health complaints.
+We accessed aggregated national and subnational data from Google’s COVID-19 Search Trends
+Symptoms Dataset [@Wahltinez2020] (hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021.
+The symptoms dataset provides time series data of search term density, standardized to pairs of health symptoms and regions (e.g., searches for depression in Australia or for fever in Cook County, Illinois) and normalized within each pair based on the symptom’s relative popularity.
+The time series of search density for each symptom-region pair also contains artificial noise, as Google’s differential privacy technique to data aggregation and anonymization adds random noise to protect user privacy (the errors are symmetrically distributed).
 
-* Linear interpolation to replace missing values
-* Also used smoothing to address outliers (sensitivity analysis showed no difference when unadjusted values were used)
-* Not all counties reported data (due to data privacy concerns, smaller county results were not included in the symptoms dataset)
+Search density data for over 400 symptoms are reported across national and subnational regions of six countries: Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States.
+In the United States, subnational regions include states and counties.
+Because the aggregated search density trends were constructed based on relative search population within each region, comparison of search density for a specific symptom between different regions is not meaningful; however, comparing search density within regions (or a group of regions) is feasible both over time and across different symptoms.
+
+```{r methods_text_1}
+
+n_states <- data_its_state %>% select(state_name) %>% unique() %>% nrow()
+n_counties <- data_its_county %>% select(county_fips) %>% unique() %>% nrow()
+
+n_states <- format(n_states, big.mark = ",")
+
+n_counties <- format(n_counties, big.mark = ",")
+
+```
+
+For our analysis, we utilized three levels of region from the symptoms dataset: 1) national level data from the six countries in the dataset; 2) U.S.
+state level data across `r n_states` states; and 3) U.S.
+county level data reported by `r n_counties` counties.
+(Though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset.) Following the convention of the symptoms dataset, we will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."
 
@@
 We further obtained county-level presidential election returns for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we then used to calculate aggregate county and state votes (including absentee, early, and election day ballots) won by each candidate.
-The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the candidate with the most votes to the runner up); margins were then used to sort counties and states into quintiles, with the 20% most Republican-voting localities appearing in the symptoms dataset sorted into bin 1 and the 20% most Democratic-voting localities sorted into bin 5.
+The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the candidate with the most votes to the runner up).
+These margins were then used to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth).
 
-* Joined to symptoms dataset by FIPS code
+#### Population data
 
-## Statistical analysis
+Population estimates for 2020 by Federal Information Processing Standards (FIPS) code were obtained from the United States Department of Agriculture (USDA) Economic Research Service.
+
+### Statistical analysis
 
@@
 
-### Modeling approach
+#### Modeling approach
 
-We use a controlled interrupted time series (CITS) approach.
+We use an ITS approach to model Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$ is an indicator variable which equals 1 in the period after the shock data and 0 otherwise, $\theta_r$ is a fixed effect for region $r$, and $T^{'}_t\chi$ is a matrix of time-vary fixed effects (i.e., month and day of week).
 
-Model equation for Google search density (measured as the ratio between the normalized search volume for a given symptom during a given week and the median search volume for that symptom between 2018 and 2020):
+In our model, $\alpha_d$ can be interpreted as a level or intercept associated with the shock date—that is, the immediate difference in search density for a disease $d$ following November 19, 2020.
+The term $\beta_d$—i.e., the slope change—can be interpreted as the sustained change in search density in the days following November 16th.
 
-$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_i + \lambda_3 time_t*Post_i + $$
-$$ \alpha_d treated_{di} + \beta_d time_t*treated_{di} + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \epsilon_{it}$$
-where $time_t$: is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$: is an indicator variable which equals 1 in the "post" period and 0 otherwise, and $treated_di$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches.
+```{r methods_text}
 
+diseases_n <- format(max(model_outputs_its$model_number), big.mark = ",")  
+mh_diseases_n <- format(length(list_mental_health_symptoms), big.mark = ",")  
+num_models_multiverse = format(max(model_outputs_multiverse$model_number), big.mark = ",")
+
+```
+We apply this model for all available `r diseases_n` diseases with county-level data.
+As search density may rapidly change in response to a shock, we trimmed the bandwidth of dates to fit our model to forty days before and after November 16, 2020.
+
+To control for time-varying confounders which may have affected symptom search trends during the study period, we applied a CITS approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
+
+After reviewing the list of symptoms for which search density data were available, we identified the following `r mh_diseases_n` mental health related symptoms: `r paste0(gsub("asperger", "Asperger", gsub("_", " ", printList(toPrint = sort(list_mental_health_symptoms), finalSepWord = "and", midSep = ","))),".")`
+
+For each of these mental health symptoms, $d$, we ran the following model to predict search density:
+
+\begin{spacing}{1}
+
+$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d treated_{di} + 
+\ \ \ \ \ $$
+$$\beta_d time_t*treated_{di}  + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \theta_g + T^{'}_t\chi +  \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ (3.2)$$
+\end{spacing}
+
+\vspace{12pt}
+
+where $treated_{di}$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches.
 The CITS effect estimates of interest are given by $\delta$, which reflects the additional level shift among mental health related symptoms searches compared to searches for headaches after the vaccine announcement, and  $\gamma$, the additional change in search density over time (i.e., slope change) comparing the same.
 
-* Fixed effects included for day of week, month, and state
-* Trim bandwidth to 40 days before and after the announcement
-* Subgroup analysis by polity to examine whether effects were different in very Democrat leaning geographies vs. Republican leaning ones
+Given the high number of observations in our sample, we evaluated significance against an alpha of 0.01, and we constructed 99% confidence intervals using heteroskedasticity-robust standard errors.
 
-### Sensitivity analysis
+##### Sensitivity analysis
 
-Interacted modeling decisions:
+As with other quasi-experimental methods, it is recommended that the modeling choices and specifications of a CITS analysis be evaluated using a sensitivity analysis.
+To do so, we defined a list of seven methodological choices concerning data processing and modeling assumptions and interacted these choices to generate all their plausible  combinations.
+These combinations were then conducted to allow for a multiverse analysis to identify how sensitive effect estimates and confidence intervals were to different methodological choices.
 
-* County vs. state level aggregated data
-* Replacement of outliers with smoothing
-* Fixed effects for day of week
-* Fixed effects for month
-* Fixed effects for state
-* Bandwidth selection (30, 40, 50, 60 days)
+These criteria used to generate the plausible model combinations are outlined in Table 3.1.
 
-128 models for each disease and polity level (384 models per disease, 2,304 in total across all 6 conditions)
+\vspace{12pt}
+
+\begin{raggedright}
+
+```{r table3_1, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table3_1.png")
+
+```
+
+\addcontentsline{lot}{table}{Table 3.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis}
+
+\end{raggedright}
+
+First, we considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, we compared the level of region of aggregated data, using U.S.
+counties, U.S.
+states, and, finally, national trends from the six counties in the sample.
+Third, we evaluated sensitivity to our specification of the bandwidth cut-off around the shock date, extending this from ±40 days to 40 and 60 days.
+Fourth, we toggled whether to account for day of week fixed effects.
+Fifth, we toggled month fixed effects.
+Sixth, we similarly toggled regional fixed effects (i.e., fixed effects for states in the U.S.
+state level data, fixed effects for counties in the U.S.
+county level data, etc.).
+
+Interacting these choices resulted in 144 plausible models for each symptom.
+Each of the 144 models were run for all `r mh_diseases_n` mental health related symptoms, resulting in `r num_models_multiverse` models being conducted overall.
+
+##### Subgroup analysis
+
+Two subgroup analyses were conducted to investigate the generalizability of the findings of the main analysis and to explore potential heterogeneities in measures of association.
+
+The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using our nationally aggregated data.
+This analysis aimed to investigate the extent to which effects observed in US states and counties were also seen in other countries.
+
+The second subgroup analysis applied the CITS approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share.
+A growing body of evidence has documented that political ideology can play a role in how receptive people are to vaccination; this has been highlighted throughout the COVID-19 pandemic, with people identifying as conservative being more likely to express skepticism of public health authorities and the scientific community and being more likely to express concerns about the safety, effectiveness, or necessity of vaccines.
+Our subgroup analysis comparing CITS effect estimates in blue vs.
+red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
 
 ### Ethics statement
+
 The Institutional Review Board (IRB) of the Harvard T.H.
@@
 
-```
+function_dynamic_text_results <-
+  function(section = "its",         #c(its, main, international, polity, multiverse)
+           disease_option,
+           coefficient_option,
+           lag_option,
+           region_option = "all",
+           geography_option = "county",
+           value_include = TRUE,
+           multiverse_sign = "positive",
+           multiverse_p = FALSE) #(TRUE, FALSE, only),)
 
-* Sharp declines in searches for depression and anxiety following vaccine announcement
-* No meaningful differences in searches for major depression and major anxiety, panic attacks, or sleep disorders
-* Results do not strongly vary by polity
+  {output_df <- get(paste0(
+    "model_outputs_",section))
 
-## Discussion
+  term <- ifelse(section == "its" & coefficient_option == "intercept",
+                 "post", 
+                 ifelse(section != "its" & coefficient_option == "intercept",
+                        "post:trt",
+                        ifelse(section == "its" & coefficient_option == "slope",
+                               "post:time", "post:time:trt")))
 
-* Shows that event the announcement of a safe and effective vaccine led to a significant shift in searches.
-If searches are taken as a reasonable proxy of mental health status, the period following the announcement saw both a sharp decline in depression and anxiety
+  if(section == "multiverse"){
 
-* Lack of heterogeneity by polity is interesting, given evidence that polity is a strong predictor of attitudes towards COVID-19 vaccination.
-Also makes bias from an uncommon shock (e.g., 2020 election) less likely to explain the results
+    if(multiverse_sign == "positive"){
 
-\newpage
+      output_df <- output_df %>% filter(estimate >= 0)  %>% 
+        filter(coefficient == term) %>%   
+        filter(disease == disease_option)
 
-```{r figure_cits_outputs, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7, fig.height = 8, fig.align='center', out.width = '95%', fig.scap="Controlled interrupted time series effect estimates on Google Search density by symptom.", out.extra='',  fig.cap="\\label{figure_cits_outputs}Controlled interrupted time series effect estimates (A: slope change per 10 days and B: level shift)  on Google Search density by symptom.
-Effect estimates are represented as thick, horizontal lines in between colored bands, which represent the 99\\% confidence intervals for the estimates.
-Colors reflect the sign and magnitude of effect estimates.
-Dark blue values above zero indicate an increase in search density, while the yellow and green negative values indicate a decrease.
-The dotted horizontal line depicts a null effect.
-ADHD: Attention deficit hyperactivity disorder.
-GAD: Generalized anxiety disorder.
-MDD: Major depressive disorder."}
+    } else {output_df <- output_df %>% filter(estimate < 0)   %>% 
+      filter(coefficient == term) %>%   
+      filter(disease == disease_option)}
 
-model_outputs_all_main %>% 
-   function_model_main("exclude") %>%
-  function_clean_diseases () %>%
-  arrange(disease) %>%
-   mutate(estimate = ifelse(coefficient == "post:time:trt", estimate*10, estimate),
-         lower_99 = ifelse(coefficient == "post:time:trt", lower_99*10, lower_99),
-         upper_99 = ifelse(coefficient == "post:time:trt", upper_99*10, upper_99)
-         ) %>%
-    mutate(coefficient = ifelse(coefficient == "post:time:trt", "A: slope change (per 10 days)",
-                              ifelse(coefficient == "post:trt", "B: level shift", "ERROR"))) %>%
-  mutate(sign = ifelse(estimate >0, TRUE, FALSE)) %>%
+    if(multiverse_p != FALSE)
+    {
+      models_counts <- output_df <- output_df %>% filter(p_value < multiverse_p) %>% nrow()
+      return(models_counts)
 
-  ggplot(aes(x = disease, 
-             y = estimate, ymin = lower_99, ymax = upper_99, fill = estimate)) +
-  geom_crossbar() +
-    theme_classic() +
-      geom_hline(yintercept = 0, linetype='dotted') +
+    } else {
 
-   geom_point(alpha = 0.5) +
-  labs(x = "Symptom", y = "Estimate") +
-  theme(
-    legend.position = "none",
-    strip.text = element_text(size=12),
-    text = element_text(family = "Source Sans Pro"),
-    axis.text.x = element_text(#size = 4, 
-                               angle = 90, vjust = 0.5, hjust=1)) +
-  facet_wrap(~coefficient, scales = "free_y", dir = "v") +
-  scale_fill_viridis(direction = -1
+      models_counts <- output_df %>% nrow()
 
-  )
- #  
- # scale_fill_manual(values = c(col_negative, col_positive),
- #                      name = "")
+      return(models_counts)
 
-```
+    }
 
-```{r figure_all_diseases, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 6, fig.height = 4.5, fig.align='center', out.width = '95%',  fig.scap="Interrupted time series (ITS) effect estimates and confidence intervals by symptom.", out.extra='',  fig.cap="\\label{figure_all_diseases}Interrupted time series (ITS) effect estimates and confidence intervals by symptom.
-Effect estimates are presented by points;  for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
-The horizontal and vertical bars next to each point represent the 99\\% confidence intervals for the estimate slope change and level shift, respectively.
-Mental health-related symptoms are shown in blue, while physical symptoms are shown in grey.
-ADHD: Attention deficit hyperactivity disorder.
-MDD: Major depressive disorder."}
+  }else{
 
-model_outputs_all_diseases_graph <- model_outputs_all_diseases %>%
-  mutate(coefficient = ifelse(coefficient == "post:time", "slope",
-                              ifelse(coefficient == "post", "level", "ERROR"))) %>%
-  select(coefficient, estimate, lower_95, upper_95, disease, p_value) %>%
-  pivot_wider(names_from = coefficient,
-              values_from = c(estimate, lower_95, upper_95, p_value)) %>%
-  mutate(mh_indicator = ifelse(disease %in% list_diseases_all, 
-                               "Mental symptom",
-                               "Physical symptom"))  %>%
-      function_clean_diseases()
+    output_df <-
+      output_df %>% filter(coefficient == term) %>%
+      filter(disease == disease_option)
 
-model_outputs_all_diseases_graph %>%
-  ggplot(aes(y = estimate_level, x = estimate_slope, color = mh_indicator, label = disease)) +
-  geom_hline(yintercept = 0) +
-  geom_vline(xintercept = 0) +
-  geom_errorbarh(aes(xmin = lower_95_slope, xmax = upper_95_slope), alpha = 0.3) +
-  geom_errorbar(aes(ymin = lower_95_level, ymax = upper_95_level), alpha = 0.3) +
-  theme_classic() +
-  geom_point(alpha = 0.75) +
-  theme(
-    legend.position = "bottom",
-    strip.text = element_text(size=12),
+     if(section == "political"){ output_df <- output_df %>% filter(polity == region_option) %>%
+       filter(geography == geography_option)}
 
-    text = element_text(family = "Source Sans Pro")) +
-      scale_color_manual(values = c(col_mh,
-                                    col_grey_lightest),
-                         name = "") +
-      labs(x = "Slope change", y = "Level shift") +
-  geom_text_repel(data=subset(model_outputs_all_diseases_graph, estimate_slope < -0.04 |
-                                (estimate_slope <.01 & mh_indicator ==  "Mental symptom")),
-                  size = 3)
+    val <- round((output_df$estimate), 3)
+    p_val <- round(output_df$p_value, 3)
+    low <- round((output_df$lower_99), 3)
+    high <- round((output_df$upper_99), 3)
 
-```
+    if (value_include == TRUE){
 
-```{r figures_cits_data, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 9.5, fig.height = 8, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends, by symptom and region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data}Density of Google Search trends, by symptom and region, as a function of time.
-In each row, search density data for two symptoms are displayed: one of three mental health symptoms (from top to bottom: anxiety, depression, and major depressive disorder) in blue and headaches in grey.
-In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
-In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
-Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
-The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
-US: United States."}
+      return(paste0(
+        val,
+        " percentage points",
+        ifelse(coefficient_option == "slope",
+               " per day "," "),
+        "(p ",
+        ifelse(p_val < 0.001,
+               "< 0.0001, ",
+               paste0("= ",
+                      p_val,
+                      ", ")),
+        "99\\% CI: ",
+        low,
+        " – ",
+        high
+        ,
+        ")"))
+
+    }
+
+    if (value_include == "allnumber"){
+
+      return(paste0(
+        "(",
+        val,
+        ", p ",
+        ifelse(p_val < 0.001,
+               "< 0.0001, ",
+               paste0("= ",
+                      p_val,
+                      ", ")),
+        "99\\% CI: ",
+        low,
+        " – ",
+        high
+        ,
+        ")"))
+
+    }
+
+    if (value_include == FALSE){
+
+      return(paste0(
+        "(p ",
+        ifelse(p_val < 0.001,
+               "< 0.0001, ",
+               paste0("= ",
+                      p_val,
+                      ", ")),
+        "99\\% CI: ",
+        low,
+        " – ",
+        high
+        ,
+        ")"))
+
+    }
+
+    if (value_include == "only"){
+      # Estimate only
+
+      return(val)
+
+    }
+
+  }
+
+  }
+
+function_pval_stars <- function(x){
+
+  ifelse(stars.pval(x) ==".", "", stars.pval(x))
+
+}
+
+function_figures_cits_data <- function(geography,m){
 
@@
 
-for (m in mental_disorders) {
   for (g in geography){
+
     data_its <- get(paste0("data_its_",g))
@@
   }
-}
 
@@
                                    plot_3,
-                                      plot_4,
-                                       plot_5,
-                                      plot_6,
-                                      plot_7,
-                                       plot_8,
-                                      plot_9,
-                       align='v', ncol=3, axis='b')
-
+                                   # plot_4,
+                                   # plot_5,
+                                   # plot_6,
+                                   # plot_7,
+                                   # plot_8,
+                                   # plot_9,
+                                   align='v', ncol=1, axis='b') 
  print(combo_plot_1)
 
+}
+
 ```
+
+The ITS estimates for the immediate (level shift) and sustained (slope change) effects associated with the announcement of vaccine safety and efficacy data on search density for all `r diseases_n` are presented in Figure \ref{figure_all_diseases}.
+
+For most symptoms, search density exhibited negligible differences following the announcement, with small positive level shifts offset by modest negative slope changes.
+For four mental health symptoms, however, we observed relatively large, negative slope changes for searches for anxiety `r function_dynamic_text_results("its","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("its","depression", "slope", value_include = "allnumber")`, major depressive disorder (MDD)`r function_dynamic_text_results("its","major_depressive_disorder", "slope", value_include = "allnumber")`, and attention deficit hyperactivity disorder (ADHD)`r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "slope", value_include = "allnumber")`.
+With respect to level shifts, changes for anxiety `r function_dynamic_text_results("its","anxiety", "intercept", value_include = "allnumber")` and depression `r function_dynamic_text_results("its","depression", "intercept", value_include = "allnumber")` were close to zero, while those for MDD `r function_dynamic_text_results("its","major_depressive_disorder", "intercept", value_include = "allnumber")` and ADHD `r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "intercept", value_include = "allnumber")` were approximately 0.3 percentage points.
+
+```{r figure_all_diseases, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 6, fig.height = 4.5, fig.align='center', out.width = '95%',  fig.scap="Interrupted time series (ITS) effect estimates and confidence intervals by symptom.", out.extra='',  fig.cap="\\label{figure_all_diseases}Interrupted time series (ITS) effect estimates and confidence intervals by symptom.
+Effect estimates are presented by points;  for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
+The horizontal and vertical bars next to each point represent the 99\\% confidence intervals for the estimate slope change and level shift, respectively.
+Mental health-related symptoms are shown in blue, while physical symptoms are shown in grey.
+ADHD: Attention deficit hyperactivity disorder.
+MDD: Major depressive disorder."}
+
+model_outputs_its_graph <- model_outputs_its %>%
+  mutate(coefficient = ifelse(coefficient == "post:time", "slope",
+                              ifelse(coefficient == "post", "level", "ERROR"))) %>%
+  select(coefficient, estimate, lower_95, upper_95, disease, p_value) %>%
+  pivot_wider(names_from = coefficient,
+              values_from = c(estimate, lower_95, upper_95, p_value)) %>%
+  mutate(mh_indicator = ifelse(disease %in% list_mental_health_symptoms, 
+                               "Mental symptom",
+                               ifelse(disease == "headache", 
+                                      "Headache (control)",
+                                      "Physical symptom")))  %>%
+  mutate(mh_indicator = factor(mh_indicator, 
+                               levels = c("Mental symptom", 
+                                          "Headache (control)",
+                                          "Physical symptom"))) %>%
+  function_clean_diseases()
+
+model_outputs_its_graph %>%
+  ggplot(aes(y = estimate_level, x = estimate_slope, color = mh_indicator, label = disease)) +
+  geom_hline(yintercept = 0) +
+  geom_vline(xintercept = 0) +
+  geom_errorbarh(aes(xmin = lower_95_slope, xmax = upper_95_slope), alpha = 0.3) +
+  geom_errorbar(aes(ymin = lower_95_level, ymax = upper_95_level), alpha = 0.3) +
+  theme_classic() +
+  geom_point(alpha = 0.75) +
+  theme(
+    legend.position = "bottom",
+    strip.text = element_text(size=12),
+
+    text = element_text(family = "Source Sans Pro")) +
+  scale_color_manual(values = c(col_mh,
+                                col_headache,
+                                col_grey_lightest),
+                     name = "") +
+  labs(x = "Slope change", y = "Level shift") +
+  geom_text_repel(data=subset(model_outputs_its_graph, estimate_slope < -0.04 |
+                                (estimate_level <.1 & mh_indicator ==  "Mental symptom" |
+                                   mh_indicator == "Headache (control)")), max.overlaps = 10,
+                  size = 3)
+
+```
+
+While our ITS analysis provided suggestive evidence that search density for mental health symptoms might have changed in the post-announcement period, it also highlighted that searches may have generally changed across other diseases at the same time.
+Our CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed our ITS analysis, with most conditions showing level and slope changes close to the null.
+For three conditions, our CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")` all showing sustained declines.
+All three of these symptoms had relatively large slope changes in our ITS analysis.
+In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "level")`, a decrease double in magnitude compared to the majority of estimates for other symptoms.
+
+```{r figure_cits_outputs, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7, fig.height = 8, fig.align='center', out.width = '95%', fig.scap="Controlled interrupted time series effect estimates on Google Search density by symptom.", out.extra='',  fig.cap="\\label{figure_cits_outputs}Controlled interrupted time series effect estimates (A: slope change per 10 days and B: level shift)  on Google Search density by symptom.
+Effect estimates are represented as thick, horizontal lines in between colored bands, which represent the 99\\% confidence intervals for the estimates.
+Colors reflect the sign and magnitude of effect estimates.
+Dark blue values above zero indicate an increase in search density, while the yellow and green negative values indicate a decrease.
+The dotted horizontal line depicts a null effect.
+ADHD: Attention deficit hyperactivity disorder.
+CoC: clouding of consciousness.
+GAD: Generalized anxiety disorder.
+MDD: Major depressive disorder."}
+
+model_outputs_main %>% 
+  filter(disease %in% list_mental_health_symptoms) %>%
+  function_model_main("exclude") %>%
+  function_clean_diseases () %>%
+  arrange(disease) %>%
+  mutate(estimate = ifelse(coefficient == "post:time:trt", estimate*10, estimate),
+         lower_99 = ifelse(coefficient == "post:time:trt", lower_99*10, lower_99),
+         upper_99 = ifelse(coefficient == "post:time:trt", upper_99*10, upper_99)
+  ) %>%
+  mutate(coefficient = ifelse(coefficient == "post:time:trt", "A: slope change (per 10 days)",
+                              ifelse(coefficient == "post:trt", "B: level shift", "ERROR"))) %>%
+  mutate(sign = ifelse(estimate >0, TRUE, FALSE)) %>%
+
+  ggplot(aes(x = disease, 
+             y = estimate, ymin = lower_99, ymax = upper_99, fill = estimate)) +
+  geom_crossbar() +
+  theme_classic() +
+  geom_hline(yintercept = 0, linetype='dotted') +
+
+  geom_point(alpha = 0.5) +
+  labs(x = "Symptom", y = "Estimate") +
+  theme(
+    legend.position = "none",
+    strip.text = element_text(size=12),
+    text = element_text(family = "Source Sans Pro"),
+    axis.text.x = element_text(#size = 4, 
+      angle = 90, vjust = 0.5, hjust=1)) +
+  facet_wrap(~coefficient, scales = "free_y", dir = "v") +
+  scale_fill_viridis(direction = -1
+
+  )
+#  
+# scale_fill_manual(values = c(col_negative, col_positive),
+#                      name = "")
+
+```
+
+In both our analyses, search trends for anxiety, depression, and MDD showed potential immediate and sustained declines in density following November 16th.
+Search density for these three symptoms and the comparison search data for headaches is plotted in Figures \ref{figures_cits_data_anxiety} through \ref{figures_cits_data_mdd} at the level of U.S.
+states, U.S.
+counties, and international data.
+We observed relatively strong concordance between our CITS estimates and the observed trends in the data, with strong fit to both mental health symptoms and headaches.
+We further observed strong within-week patterns in searches, supporting our inclusion of fixed effects to account for this weekly periodicity.
+
+```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
+In each row, search density data for two symptoms are displayed: anxiety in blue and headaches in grey.
+In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
+In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
+Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
+The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
+US: United States."}
+
+function_figures_cits_data(geography = geography, "anxiety")
+
+```
+```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
+In each row, search density data for two symptoms are displayed: depression in blue and headaches in grey.
+In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
+In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
+Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
+The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
+US: United States."}
+
+function_figures_cits_data(geography = geography, "depression")
+
+```
+
+```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
+In each row, search density data for two symptoms are displayed: MDD in blue and headaches in grey.
+In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
+In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
+Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
+The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
+US: United States."}
+
+function_figures_cits_data(geography = geography, "major_depressive_disorder")
+
+```
+
+Our multiverse analysis further underscored the robustness of our findings concerning the relatively large negative immediate and sustained effects on searches for anxiety and depression, in particular (Figure \ref{fig_multiverse_analysis_all}).
+For anxiety, all 144 models had negative level shifts and slope changes.
+For depression, all `r function_dynamic_text_results("multiverse","depression", "slope", multiverse_sign = "negative")` models had negative slope changes, of which only `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "positive")` models had any positive level shift.
+For MDD, we similarly observed a universally negative slope change in all `r function_dynamic_text_results("multiverse","major_depressive_disorder", "slope", multiverse_sign = "negative", multiverse_p = FALSE)` models; however, the majority of models showed a positive level shift (`r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "positive", multiverse_p = FALSE)` models), whereas only `r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "negative", multiverse_p = FALSE)` showed a downward level shift.
+
+```{r fig_multiverse_analysis_all, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 9.5, fig.align='center', out.width = '95%',  fig.scap="CITS effect estimates and confidence intervals by mental health symptom, all model combinations.", out.extra='',  fig.cap="\\label{fig_multiverse_analysis_all}Controlled interrupted time series effect estimates by mental health related symptom for each model specification combination in multiverse analysis.
+Each point presents the effect estimates of a sinlge model; for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
+ADHD: Attention deficit hyperactivity disorder.
+CoC: clouding of consciousness.
+GAD: generalized anxiety disorder.
+MDD: Major depressive disorder."}
+
+model_outputs_its_graph <- model_outputs_multiverse %>%
+  filter(disease %in% list_mental_health_symptoms) %>%
+
+  mutate(coefficient = ifelse(coefficient == "post:time:trt", "slope",
+                              ifelse(coefficient == "post:trt", "level", "ERROR"))) %>%
+  select(!c(z_score, lower_99, upper_99, standard_error)) %>%
+  pivot_wider(names_from = coefficient,
+              values_from = c(estimate, lower_95, upper_95, p_value)) %>%
+  function_clean_diseases()
+
+model_outputs_its_graph %>%
+  ggplot(aes(y = estimate_level, x = estimate_slope,  color = disease)) +
+  geom_hline(yintercept = 0) +
+  geom_vline(xintercept = 0) +
+  # geom_errorbarh(aes(xmin = lower_95_slope, xmax = upper_95_slope), alpha = 0.3) +
+  # geom_errorbar(aes(ymin = lower_95_level, ymax = upper_95_level), alpha = 0.3) +
+  theme_classic() +
+  geom_point(alpha = 0.75) +
+  theme(
+    legend.position = "bottom",
+    # strip.text = element_text(size=12),
+    text = element_text(family = "Source Sans Pro")) +
+  labs(x = "Slope change", y = "Level shift", color = "Symptom") +
+  scale_color_viridis(discrete = TRUE) + 
+  facet_wrap(~disease)
+```
+
+Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates to state level estimates for each CITS estimand, but with much tighter confidence intervals, even when geographic fixed effects and narrower bandwidths were included.
+Slope changes and level shifts for anxiety, depression, and MDD are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}.
+Across all models, the sustained change in search density for anxiety and depression is negative and significant an alpha of 0.01.
+In terms of the estimated level shifts, `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models for anxiety (`r round(function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)*100/144,0)`%) had a statistically significant negative change, compared to `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "positive", multiverse_p = 0.01)` models with a positive one.
+For depression, of the `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "positive", multiverse_p = 0.01) + function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models with a statistically significant level shift estimate, all `r  function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models returned a negative level shift coefficient.
+
+Turning to our subgroup analysis, we found modest evidence of effect estimates of similar magnitude comparing across nations (Figure \ref{fig_international}).
+Across the most populous countries (Australia, the United Kingdom, and the United States), effect estimates were broadly consistent, with wider confidence intervals than our ITS or CITS main analysis results due to the smaller number of observations.
+Negative level shifts and slope changes were more pronounced in New Zealand compared to other nations; we caution, however, that owing to the construction of the Google search density data being relative to regions, this may be due to differences in seach volume intensity for depression in New Zealand compared to other nations, and not due to a strong effect itself.
 
@@
 
-    model_outputs_temp <- model_outputs_all_international %>%
+model_outputs_temp <- model_outputs_multiverse %>%
   filter(time == "daily") %>%
@@
 
+\elandscape
+
+```{r fig_international, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 6.5, fig.align='center', out.width = '95%',  fig.scap="CITS effect estimates and confidence intervals by mental health symptom, all model combinations.", out.extra='',  fig.cap="\\label{fig_international}Controlled interrupted time series effect estimates by mental health related symptom for each model specification combination in multiverse analysis.
+Each point presents the effect estimates of a sinlge model; for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
+ADHD: Attention deficit hyperactivity disorder.
+CoC: clouding of consciousness.
+GAD: generalized anxiety disorder.
+MDD: Major depressive disorder."}
+
+model_outputs_international %>%
+  filter(disease %in% mental_disorders) %>%
+  mutate(coefficient = ifelse(coefficient == "post:time:trt", "Slope change",
+                              ifelse(coefficient == "post:trt", "Level shift", "ERROR"))) %>%
+  # select(!c(z_score, lower_99, upper_99, standard_error)) %>%
+  # pivot_wider(names_from = coefficient,
+  #             values_from = c(estimate, lower_95, upper_95, p_value)) %>%
+  function_clean_diseases() %>%
+  # ggplot(aes(y = estimate_level, x = estimate_slope,  color = nation)) +
+  ggplot(aes(x = nation, 
+             y = estimate, ymin = lower_95, ymax = upper_95, fill = nation)) +
+  geom_crossbar() +  geom_hline(yintercept = 0) +
+  geom_vline(xintercept = 0) +
+  # geom_errorbarh(aes(xmin = lower_95_slope, xmax = upper_95_slope), alpha = 0.3) +
+  # geom_errorbar(aes(ymin = lower_95_level, ymax = upper_95_level), alpha = 0.3) +
+  theme_classic() +
+  # geom_col(alpha = 0.75) +
+  theme(
+    legend.position = "bottom",
+    # strip.text = element_text(size=12),
+    axis.text.x = element_blank(),
+    axis.ticks.x = element_blank(),
+
+    text = element_text(family = "Source Sans Pro")) +
+  labs(y = "Estimate", x = "", fill = "Nation") +
+  scale_fill_viridis(discrete = TRUE, option = "C", direction = -1) + 
+  facet_grid(coefficient~disease, scales = "free_y")
+
+```
+
+Results from our analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and MDD as found in our main analysis (Figure \ref{fig_political}).
+This was particular observed in our analysis of U.S.
+state-level data, where confidence intervals for the CITS effect estimates were statistically equivalent across red and blue states.
+In our county-level analysis, however, we observed larger immediate and sustained declines in searches for depression among red counties than blue ones, with minor overlap in confidence intervals.
+The observed slope change for searches related to depression among red counties was `r function_dynamic_text_results("political", "depression", "slope", region_option = 1)`, compared to `r function_dynamic_text_results("political", "depression", "slope", region_option = 5)` for blue counties.
+Similarly, a more pronounced level shift was observed in red counties than blue ones, `r function_dynamic_text_results("political", "depression", "intercept", region_option = 1)` vs.
+`r function_dynamic_text_results("political", "depression", "intercept", region_option = 5)`, respectively.
+
+\blandscape
+
 ```{r fig_political, include = TRUE, echo=FALSE, warnings = FALSE,fig.scap="CITS effect estimates and confidence intervals symptom, region, and predominant political ideology.", out.extra='', fig.width = 10, fig.height = 5, fig.align='center', out.width = '95%',  fig.cap="\\label{fig_political}CITS effect estimates and confidence intervals symptom, region, and predominant political ideology, with panel A depicting the estimated slope change and panel B depicting the estimate level shift.
@@
 
-model_outputs_all_US %>%
+model_outputs_political %>%
   function_model_main(levels = "include") %>%
@@
 
-\newpage
+## Discussion
+
+* Shows that event the announcement of a safe and effective vaccine led to a significant shift in searches.
+If searches are taken as a reasonable proxy of mental health status, the period following the announcement saw both a sharp decline in depression and anxiety
+
+* Lack of heterogeneity by polity is interesting, given evidence that polity is a strong predictor of attitudes towards COVID-19 vaccination.
+Also makes bias from an uncommon shock (e.g., 2020 election) less likely to explain the results
+
+```{r todolist}
+
+# To Do:
+
+# Make tables
+# Run international comparison models
+# Generate in text formulas
+
+```

### 2023-02-22 thesis.Rmd
Addition of appendices, revisions throughout papers, acknowledgements

@@
   pdf_document:
+    pandoc_args: !expr acronymsdown::add_filter()
     number_sections: TRUE
@@
   - \usepackage[nottoc]{tocbibind}
+  # - \usepackage{acro}
   # - \usepackage{float}
@@
 
+acronyms:
+  insert_loa: false
+  loa_title: ""
+
+  # loa_title: "List of Acronyms"
+  keys:
+    - shortname: LMIC
+      longname: low and middle income country
+
 ---
@@
 knitr::opts_chunk$set(warning = FALSE, message = FALSE, include = FALSE, echo = TRUE) 
-
+library(acronymsdown)
 ```
@@
 Cras adipiscing enim eu turpis egestas.
-Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.
+Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.[@vaidyanathanEvaluationInternetSearches2022]
+
+This is a \acr{LMIC}. This is also a \acr{LMIC}.
 
@@
 
+\newpage
+
 \cleardoublepage
@@
 
-\cleardoublepage
+\newpage
 
@@
 
+\section*{References}
+
+\addcontentsline{toc}{section}{References}
+
+<div id="refs"></div>
+
+\cleardoublepage
+
+\section*{Supplementary materials}
+
+\addcontentsline{toc}{section}{Supplementary materials}
+
+```{r appendix_all, child='appendix.Rmd'}
+```
+
+\newpage
+
 ```{r todo}
@@
 
+# Maps in Chapter 1 need to be improved to eliminate errors in cartographic resolution
 # Separate bibliography for each section

### 2023-02-23 paper1.Rmd
Edits to map in Paper 1

@@
                                     label = "West \nAfrica",
-                                    17.55830898122733, -25.766648641326874,
-                                    9.591111921718683, -7.308676054124459,
+                                    15.333951130672313, -20.03959428947879,
+                                    8.941590169786489, -7.402043441729575,
                                     ratio_h_over_w = 0.69/0.95,
@@
 
-                                     rel_heights  = c(0.99,1.72),
-                                     rel_widths = c(1,1),
+                                     rel_heights  = c(1.1,1.72),
+                                     rel_widths = c(1.1,1),
                                      align='h',
@@
                                                     3.22,
-                                                    1.92,
+                                                    2,
                                                     2.73,
-                                                    1.82),
+                                                    1.83),
                                      rel_heights = c(1,1,1,1,1),
@@
                                         main_map_lower,
-                                        rel_heights = c(5.9, 2.8),
-                                        rel_widths = c(1,1),
+                                        rel_heights = c(5.9, 
+                                                        2.7),
+                                        rel_widths = c(1.2,1),
                                         align='v', 
@@
 
+data_temporary <- data_rev_map %>% 
+  filter(estimate_id %in%  c(1,2,4)) %>%
+  st_drop_geometry()
+
+world_map <- ne_countries(scale = "large", returnclass = "sf")
+# world <- ne_countries(scale = "medium", returnclass = "sf")
+world_map$iso_code <- world_map$gu_a3
+world_map$iso_code[world_map$adm0_a3 == "SDS"] <- "SSD"
+
+data_rev_map <- left_join(world_map, data_temporary, by = "iso_code")
+
 k = "rate_per_100k"
-
 j = 1

### 2023-02-23 paper3.Rmd
Edits to Paper 3

@@
                                 col_headache,
-                                col_grey_lightest),
+                                col_grey_light),
                      name = "") +
@@
 Our CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed our ITS analysis, with most conditions showing level and slope changes close to the null.
-For three conditions, our CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")` all showing sustained declines.
+For three conditions, our CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")`, all showing sustained declines.
 All three of these symptoms had relatively large slope changes in our ITS analysis.
@@
 
-```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
+```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: anxiety in blue and headaches in grey.
@@
 ```
-```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
+
+```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: depression in blue and headaches in grey.
@@
 
-```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
+```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: MDD in blue and headaches in grey.
@@
 
+Slope changes and level shifts for anxiety, depression, and MDD are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}.
 Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates to state level estimates for each CITS estimand, but with much tighter confidence intervals, even when geographic fixed effects and narrower bandwidths were included.
-Slope changes and level shifts for anxiety, depression, and MDD are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}.
 Across all models, the sustained change in search density for anxiety and depression is negative and significant an alpha of 0.01.
@@
 
-```{r fig_international, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 6.5, fig.align='center', out.width = '95%',  fig.scap="CITS effect estimates and confidence intervals by mental health symptom, all model combinations.", out.extra='',  fig.cap="\\label{fig_international}Controlled interrupted time series effect estimates by mental health related symptom for each model specification combination in multiverse analysis.
-Each point presents the effect estimates of a sinlge model; for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
-ADHD: Attention deficit hyperactivity disorder.
-CoC: clouding of consciousness.
-GAD: generalized anxiety disorder.
+```{r fig_international, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 6.5, fig.align='center', out.width = '95%',  fig.scap="International CITS effect estimates and confidence intervals by mental health symptom.", out.extra='',  fig.cap="\\label{fig_international}International controlled interrupted time series effect estimates of changes in search density by mental health related symptom, reported across six nations (Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States).
+The top panel reports estimates of the level shift and the lower panel reports the estimates for the slope change.
+Effect estimates are represented as solid black lines, with the shaded regions above and below the lines showing the 95% confidence intervals.
+The solid black line across all panels reflects a null effect.
 MDD: Major depressive disorder."}
@@
 
-* Shows that event the announcement of a safe and effective vaccine led to a significant shift in searches.
-If searches are taken as a reasonable proxy of mental health status, the period following the announcement saw both a sharp decline in depression and anxiety
-
-* Lack of heterogeneity by polity is interesting, given evidence that polity is a strong predictor of attitudes towards COVID-19 vaccination.
-Also makes bias from an uncommon shock (e.g., 2020 election) less likely to explain the results
+This study sought to evaluate whether two contemporary announcements of COVID-19 vaccine safety and efficacy on November 9th and November 16th, 2020 were associated with changes in health-related Google search density related to symptoms concerning mental health.
+Using search data from U.S.
+counties, states, and international trends, we applied an ITS and CITS modeling approach to investigate associations between the announcements and changes in search density.
+We found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following the announcements of vaccine safety and efficacy.
+These declines were relatively large compared to changes in other symptoms, both physical and mental, and a multiverse analysis indicated that they were robust to alternative specifications.
+
+To interpret these observed changes as reactions to the vaccine safety and efficacy announcements, it is important to evaluate whether they may be responses to other contemporary events.
+We highlight two potential alternatives that coincided with the period under study: the 2020 U.S.
+general election on November 3rd and the observance of the Thanksgiving holiday in the United States on November 26th.
+While it is possible that our estimates encompass possible impacts from these events, data from our subgroup analysis lends support for our interpretation that these alternatives may not be sufficient to explain the observed declines in search trends for anxiety, depression, and MDD.
+
+With respect to the U.S.
+general election, we would anticipate any post-election decline in mental health related symptoms to be concentrated in the United States, given its domestic importance and the political fervor that surrounded it.
+Similarly, we would expect that impacts of the Thanksgiving holiday would be unique to the U.S., as it is not celebrated by the other nations in the sample and there were no other national holidays observed both those nations at the same time (with the exception of Singapore’s observance of Deepavali on November 14).
+
+In our subgroup analysis comparing search trends across Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, we do not observe evidence of U.S.-specific effect, with our analysis showing broad similarities in estimates of declines in searches related to anxiety and depression.
+Furthermore, the estimated declines in search density in Australia and the United Kingdom—which, along with the U.S., reflect the more populous nations in the sample—were greater than that of the U.S.
+for these two symptom searches, providing additional counterevidence to these alternative explanations.
+
+Further countering the explanation that observed declines in search trends for mental health symptoms were due to the U.S.
+general election are the results from our subgroup analysis comparing blue and red states and counties.
+If voters expressed relief following the election if their candidate was the winner, a greater decline in searches related to anxiety and depression in states and counties would be expected in those that more heavily voted for Joe Biden, the Democratic candidate and subsequent President-elect, than for former President Donald Trump, the Republic candidate who lost his bid for reelection.
+This gradient would also echo our hypothesis that, given findings that political ideology may affect receptiveness to vaccination, the announcement of vaccine safety and efficacy would have had a less pronounced effect among conservative voters compared to liberal ones.
+Instead, we observed the opposite: among the counties that most heavily voted for the Republican presidential candidate, the estimated declines in search density for anxiety and depression were larger than in those that most heavily voted Democrat.
+We do, however, observe broad similarities in the confidence intervals of these estimates, such that we do not rule out the possibility that the effects were the same across red and blue counties.
+However, even this finding would be striking, giving the enduring political controversy over vaccination in the U.S.; while subsequent attitudes towards vaccination may show an ideological split by political affiliation, our findings—if taken as a reasonably reflection of individual attitudes—suggest that whatever relief the vaccine announcements brought was shared across the aisle.
+
+The aggregated nature of our data, however, imposes a constraint to our interpretations, as we are unable to identify whether individual political ideologies were correlated with changes in search trends.
+Instead, we rely on population aggregates that reflect political orientation (i.e., vote share by county and state) as a proxy, focusing on the 20% most Democrat and Republican-voting areas to strengthen the plausibility of this proxy.
+
+Additionally, we highlight that the use of Google search density as a proxy for population mental health could not be directly validated in our study, as the search data is anonymized and aggregated.
+While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and U.S.
+population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.
+Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective wellbeing and care seeking.
+
+Despite these limitations, our findings suggest that the announcement of COVID-19 vaccine safety and efficacy led to a robust and sustained reduction in Google search density for anxiety and depression, relative to search density prior to the announcements and to searches for other symptoms.
+If search density echoes population mental health, our results would indicate that these announcements-as a hopeful signal of a new phase of the COVID-19 pandemic-led to an improvement in mental health, underscoring the importance of timely and transparent communication in public health.
 

### 2023-02-25 conclusion.Rmd
Abstract and Introduction for Paper 3

--- 2023-02-09 conclusion.Rmd
@@
----
-title: ''
-output: pdf_document
-
----
+\section*{Conclusion}
 
 \addcontentsline{toc}{section}{Conclusion}
-\section*{Conclusion}
 
-Thank you for following this tutorial!
+Overview of Paper 1
 
-I hope you'll find it useful to write a very professional dissertation.
+Overview of Paper 2
 
-\cite{ngTracingPathChikungunya2010}
+Overview of Paper 3
+
+Policy implications and future research
+
+Burden may be larger than traditionally conceptualized
+
+Papers also show that mental health is linked to broader contextual challenges (climate change, COVID-19) – resilience/vulnerability, exacerbating existing disparities, but also could be critical to overcoming them…
+
+In the absence of population mental health metrics, innovative uses of health data may be helpful in conducting research, but come with limitations

### 2023-02-25 intro.Rmd
Abstract and Introduction for Paper 3

@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
-Lacinia quis vel eros donec ac odio tempor.
-Urna nec tincidunt praesent semper feugiat nibh.
-Tortor aliquam nulla facilisi cras fermentum odio eu feugiat.
-Magna ac placerat vestibulum lectus mauris ultrices eros.
-Pulvinar proin gravida hendrerit lectus.
-Nisi scelerisque eu ultrices vitae auctor eu.
-Quis hendrerit dolor magna eget est lorem ipsum.
-At consectetur lorem donec massa sapien faucibus et molestie.
-Feugiat in fermentum posuere urna nec tincidunt praesent.
-Facilisis gravida neque convallis a cras.
-Massa id neque aliquam vestibulum morbi blandit.
-Faucibus purus in massa tempor nec feugiat nisl pretium fusce.
-Amet facilisis magna etiam tempor orci eu lobortis.
-Odio tempor orci dapibus ultrices in iaculis nunc sed augue.
-Nulla aliquet porttitor lacus luctus accumsan tortor posuere ac ut.
-Sit amet aliquam id diam maecenas.
-Rhoncus aenean vel elit scelerisque mauris pellentesque pulvinar pellentesque habitant.
-Urna nunc id cursus metus aliquam.
+Overview of the global burden of mental health
 
-...
+Cite key literature – systematic reviews, Lancet series, Vikram’s work, DC3P findings, Walker et al.
+EMERALD health systems & mental health study, Mental Health Atlas from WHO, GBD for estimates of burden
 
-Iaculis nunc sed augue lacus viverra vitae congue eu consequat.
-Sodales ut eu sem integer vitae.
-Pulvinar mattis nunc sed blandit libero volutpat sed cras.
-Maecenas volutpat blandit aliquam etiam erat velit scelerisque in dictum.
-Ultricies integer quis auctor elit sed vulputate mi.
-Ornare suspendisse sed nisi lacus sed viverra tellus in.
-Quis commodo odio aenean sed adipiscing diam donec.
-Platea dictumst vestibulum rhoncus est pellentesque elit.
-Commodo nulla facilisi nullam vehicula ipsum a arcu cursus.
-Ut faucibus pulvinar elementum integer enim neque volutpat.
-Diam quis enim lobortis scelerisque fermentum dui.
+Implications of this global burden for health systems
+
+Highlight interconnectedness of mental health and physical health
+
+Links of mental health to financial risk protection / vulnerabilities to poverty
+
+Underscore under-investment in mental health systems, coupled with lack of data on mental health, which constrains research and policy
+
+Also note that mental health is a truly global issue, impacting HICs and LMICs alike
+
+Overview of Paper 1
+
+Overview of Paper 2
+
+Overview of Paper 3

### 2023-02-25 paper3.Rmd
Abstract and Introduction for Paper 3

@@
 
-paper3_abstract <- paste0("For searches related to depression, we observe a statistically significant slope change of -0.0304 percentage points per day (p < 0.0001, 99\\% CI: -0.0321– -0.0286) and a level shift of -0.184 (p < 0.0001, 99\\% CI: -0.226– -0.143), above and beyond changes in slope and level observed for searches for headaches.
-For anxiety, we observe a similar slope change decline of 0.0383 percentage points per day (p < 0.0001, 99\\% CI: -0.0400– -0.0366) and a level shift of -0.339 (p < 0.0001, 99\\% CI: -0.378– -0.299).
-We do not observe significant variation of estimates across predominately Democrat or Republican voting states and counties, and our results are robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
-
-```
-
-# The impact of COVID-19 vaccine developments on Google COVID-19 search trends for mental health symptoms: a controlled interrupted time series analysis
-
-\begin{centering}
-
-\emph{Daniel Arias, Jessica Cohen, Karestan Koenen, Margaret McConnell, Stéphane Verguet}
-
-\vspace{24pt}
-
-\noindent\rule{8cm}{0.4pt}
-
-\end{centering}
-
-\begin{raggedright}
-
-\vspace*{\fill}
-
-{\bf Background:} A key obstacle to studying the effects of public health responses on population mental health in the US is a lack of daily surveillance data on mental health indicators.
-A potential marker of population mental health is the use of Internet search data, which offers the potential for real-time, large-scale analysis and identification of evolving mental health issues.
-
-{\bf Methods:} We utilize controlled interrupted time series (CITS) approach to evaluate whether the development and announcement of safe and effective COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety.
-By comparing how search trends changed in the post period for mental health symptoms above and beyond changes observed in the same period for physical health symptoms, we estimate measures of association between the vaccine announcement and changes in mental health symptom search density.
-We adjust for state, month, and day of week effects, and we apply a sensitivity analysis to assess the robustness of our estimates to alternative specifications.
-We further examine whether estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
-
-{\bf Findings and interpretation:} Under our main specification, we find evidence of reduced search density associated with the announcement of vaccine safety data for Google search trends for depression and anxiety.
-`r paper3_abstract`
-
-\emph{Keywords: mental health, controlled interrupted time series, Google searches, United States, COVID-19 vaccines.}
-
-\end{raggedright}
-
-\newpage
-
-## Introduction
-It has been well-documented that throughout the pandemic, symptoms of depression and anxiety have markedly increased among US adults.
-While it is likely that the pandemic has a direct effect on worsened mental health status due to fear of contracting and spreading the virus, public health responses to the pandemic—including lockdowns, school closures, and social distancing measures—likely have an indirect effect as well.
-Existing research suggests that the effects of these measures on mental health vary, and may be protective, null, or even harmful.
-Studies of lockdowns in multiple countries, for example, point to worsened feelings of isolation and hopelessness exacerbated by isolation measures.
-By contrast, the distribution of safe and effective vaccines against COVID-19 has been shown to reduce symptoms of depression and anxiety by as much as XXX.
-
-* Describe symptoms database and reference published literature using it to predict COVID-19 cases and deaths [@alruilyPredictionCovid19Transmission2022; @abbasAssociationsGoogleSearch2021; @saegnerForecastingSurveillanceCOVID192022]
-
-A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset found strong correlation between search trends for depression and anxiety with indicators of mental health service utilization and need reported in the US Census Household Pulse Survey (HPS) with rates of emergency department visits for mental health condition as reported in the US Centers for Disease Control and Prevention’s (CDC) National Syndromic Surveillance Program (NSSP).[@vaidyanathanEvaluationInternetSearches2022]
-
-controlled interrupted time series (CITS) 
-interrupted time series (ITS)
-
-* Motivation to explore vaccine announcement: evidence that vaccination itself reduced depression and anxiety -- do we see earlier reductions from an anticipatory effect?
-* Motivation to analyze by polity: Vaccination became politically charged in the US, possible bias from impact of 2020 election on mental health searches
-* Overview of approach: CITS using searches for headache as a control, adjusting for fixed effects, subgroup analysis by polity, analysis for 6 different mental health symptoms
-
-## Methods
-
-### Data
-
-#### Shock date
-
-We take as our first credible signal of the imminent availability of multiple safe and effective COVID-19 vaccines to be November 16, 2020.
-On November 9, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16th, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S.
-Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
-
-#### Symptoms dataset
-
-We accessed aggregated national and subnational data from Google’s COVID-19 Search Trends
-Symptoms Dataset [@Wahltinez2020] (hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021.
-The symptoms dataset provides time series data of search term density, standardized to pairs of health symptoms and regions (e.g., searches for depression in Australia or for fever in Cook County, Illinois) and normalized within each pair based on the symptom’s relative popularity.
-The time series of search density for each symptom-region pair also contains artificial noise, as Google’s differential privacy technique to data aggregation and anonymization adds random noise to protect user privacy (the errors are symmetrically distributed).
-
-Search density data for over 400 symptoms are reported across national and subnational regions of six countries: Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States.
-In the United States, subnational regions include states and counties.
-Because the aggregated search density trends were constructed based on relative search population within each region, comparison of search density for a specific symptom between different regions is not meaningful; however, comparing search density within regions (or a group of regions) is feasible both over time and across different symptoms.
-
-```{r methods_text_1}
-
-n_states <- data_its_state %>% select(state_name) %>% unique() %>% nrow()
-n_counties <- data_its_county %>% select(county_fips) %>% unique() %>% nrow()
-
-n_states <- format(n_states, big.mark = ",")
-
-n_counties <- format(n_counties, big.mark = ",")
-
-```
-
-For our analysis, we utilized three levels of region from the symptoms dataset: 1) national level data from the six countries in the dataset; 2) U.S.
-state level data across `r n_states` states; and 3) U.S.
-county level data reported by `r n_counties` counties.
-(Though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset.) Following the convention of the symptoms dataset, we will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."
-
-#### Voting dataset
-
-We further obtained county-level presidential election returns for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we then used to calculate aggregate county and state votes (including absentee, early, and election day ballots) won by each candidate.
-The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the candidate with the most votes to the runner up).
-These margins were then used to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth).
-
-#### Population data
-
-Population estimates for 2020 by Federal Information Processing Standards (FIPS) code were obtained from the United States Department of Agriculture (USDA) Economic Research Service.
-
-### Statistical analysis
-
-All analyses were completed using R (version 4.2.1).[@rcoreteamLanguageEnvironmentStatistical2022]
-
-#### Modeling approach
-
-We use an ITS approach to model Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$ is an indicator variable which equals 1 in the period after the shock data and 0 otherwise, $\theta_r$ is a fixed effect for region $r$, and $T^{'}_t\chi$ is a matrix of time-vary fixed effects (i.e., month and day of week).
-
-In our model, $\alpha_d$ can be interpreted as a level or intercept associated with the shock date—that is, the immediate difference in search density for a disease $d$ following November 19, 2020.
-The term $\beta_d$—i.e., the slope change—can be interpreted as the sustained change in search density in the days following November 16th.
-
-```{r methods_text}
-
-diseases_n <- format(max(model_outputs_its$model_number), big.mark = ",")  
-mh_diseases_n <- format(length(list_mental_health_symptoms), big.mark = ",")  
-num_models_multiverse = format(max(model_outputs_multiverse$model_number), big.mark = ",")
-
-```
-We apply this model for all available `r diseases_n` diseases with county-level data.
-As search density may rapidly change in response to a shock, we trimmed the bandwidth of dates to fit our model to forty days before and after November 16, 2020.
-
-To control for time-varying confounders which may have affected symptom search trends during the study period, we applied a CITS approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
-
-After reviewing the list of symptoms for which search density data were available, we identified the following `r mh_diseases_n` mental health related symptoms: `r paste0(gsub("asperger", "Asperger", gsub("_", " ", printList(toPrint = sort(list_mental_health_symptoms), finalSepWord = "and", midSep = ","))),".")`
-
-For each of these mental health symptoms, $d$, we ran the following model to predict search density:
-
-\begin{spacing}{1}
-
-$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d treated_{di} + 
-\ \ \ \ \ $$
-$$\beta_d time_t*treated_{di}  + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \theta_g + T^{'}_t\chi +  \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ (3.2)$$
-\end{spacing}
-
-\vspace{12pt}
-
-where $treated_{di}$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches.
-The CITS effect estimates of interest are given by $\delta$, which reflects the additional level shift among mental health related symptoms searches compared to searches for headaches after the vaccine announcement, and  $\gamma$, the additional change in search density over time (i.e., slope change) comparing the same.
-
-Given the high number of observations in our sample, we evaluated significance against an alpha of 0.01, and we constructed 99% confidence intervals using heteroskedasticity-robust standard errors.
-
-##### Sensitivity analysis
-
-As with other quasi-experimental methods, it is recommended that the modeling choices and specifications of a CITS analysis be evaluated using a sensitivity analysis.
-To do so, we defined a list of seven methodological choices concerning data processing and modeling assumptions and interacted these choices to generate all their plausible  combinations.
-These combinations were then conducted to allow for a multiverse analysis to identify how sensitive effect estimates and confidence intervals were to different methodological choices.
-
-These criteria used to generate the plausible model combinations are outlined in Table 3.1.
-
-\vspace{12pt}
-
-\begin{raggedright}
-
-```{r table3_1, echo = FALSE, include = TRUE, out.width = '100%'}
-
-knitr::include_graphics("table3_1.png")
-
-```
-
-\addcontentsline{lot}{table}{Table 3.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis}
-
-\end{raggedright}
-
-First, we considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, we compared the level of region of aggregated data, using U.S.
-counties, U.S.
-states, and, finally, national trends from the six counties in the sample.
-Third, we evaluated sensitivity to our specification of the bandwidth cut-off around the shock date, extending this from ±40 days to 40 and 60 days.
-Fourth, we toggled whether to account for day of week fixed effects.
-Fifth, we toggled month fixed effects.
-Sixth, we similarly toggled regional fixed effects (i.e., fixed effects for states in the U.S.
-state level data, fixed effects for counties in the U.S.
-county level data, etc.).
-
-Interacting these choices resulted in 144 plausible models for each symptom.
-Each of the 144 models were run for all `r mh_diseases_n` mental health related symptoms, resulting in `r num_models_multiverse` models being conducted overall.
-
-##### Subgroup analysis
-
-Two subgroup analyses were conducted to investigate the generalizability of the findings of the main analysis and to explore potential heterogeneities in measures of association.
-
-The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using our nationally aggregated data.
-This analysis aimed to investigate the extent to which effects observed in US states and counties were also seen in other countries.
-
-The second subgroup analysis applied the CITS approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share.
-A growing body of evidence has documented that political ideology can play a role in how receptive people are to vaccination; this has been highlighted throughout the COVID-19 pandemic, with people identifying as conservative being more likely to express skepticism of public health authorities and the scientific community and being more likely to express concerns about the safety, effectiveness, or necessity of vaccines.
-Our subgroup analysis comparing CITS effect estimates in blue vs.
-red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
-
-### Ethics statement
-
-The Institutional Review Board (IRB) of the Harvard T.H.
-Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).
-
-## Results
+```
 
@@
                                    # plot_9,
-                                   align='v', ncol=1, axis='b') 
+                                   align='v', nrow=3, axis='b') 
  print(combo_plot_1)
@@
 
-```
+paper3_abstract <- paste0("For searches related to depression, we observe a statistically significant slope change of ",
+                          function_dynamic_text_results("main","depression", "slope"), " and a level shift of ",
+                          function_dynamic_text_results("main","depression", "intercept"),
+                          ", above and beyond changes in slope and level observed for searches for headaches. For anxiety, we observe a similar slope change decline of",
+                          function_dynamic_text_results("main","anxiety", "slope"), 
+                          " and a level shift of ",
+                          function_dynamic_text_results("main","anxiety", "intercept"),
+ ".
+We do not observe significant variation of estimates across predominately Democrat or Republican voting states and counties, and our results are robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
+
+```
+
+# The impact of COVID-19 vaccine developments on Google COVID-19 search trends for mental health symptoms: a controlled interrupted time series analysis
+
+\begin{centering}
+
+\emph{Daniel Arias, Jessica Cohen, Karestan Koenen, Margaret McConnell, Stéphane Verguet}
+
+\vspace{24pt}
+
+\noindent\rule{8cm}{0.4pt}
+
+\end{centering}
+
+\begin{raggedright}
+
+\vspace*{\fill}
+
+{\bf Background:} A key obstacle to studying the effects of public health responses on population mental health in the US is a lack of daily surveillance data on mental health indicators.
+A potential marker of population mental health is the use of Internet search data, which offers the potential for real-time, large-scale analysis and identification of evolving mental health issues.
+
+{\bf Methods:} We utilize controlled interrupted time series (CITS) approach to evaluate whether the development and announcement of safe and effective COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety.
+By comparing how search trends changed in the post period for mental health symptoms above and beyond changes observed in the same period for physical health symptoms, we estimate measures of association between the vaccine announcement and changes in mental health symptom search density.
+We adjust for state, month, and day of week effects, and we apply a sensitivity analysis to assess the robustness of our estimates to alternative specifications.
+We further examine whether estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
+
+{\bf Findings and interpretation:} Under our main specification, we find evidence of reduced search density associated with the announcement of vaccine safety data for Google search trends for depression and anxiety.
+`r paper3_abstract`
+
+\emph{Keywords: mental health, controlled interrupted time series, Google searches, United States, COVID-19 vaccines.}
+
+\end{raggedright}
+
+\newpage
+
+## Introduction
+The coronavirus disease 2019 (COVID-19) pandemic has had a profound effect on the mental health and wellbeing of individuals worldwide.
+In the United States, approximately four in ten adults reported experiencing symptoms of anxiety or depression in December 2020—a four-fold increase from January-June 2019.[@panchalImplicationsCOVID19Mental2021, p.
+19] Studies from Australia,[@batterhamTrajectoriesDepressionAnxiety2021] China,[@ahmedEpidemicCOVID19China2020; @gaoMentalHealthProblems2020; @hwangLonelinessSocialIsolation; @leiComparisonPrevalenceAssociated2020; @liuPrevalencePredictorsPTSS2020; @qiuNationwideSurveyPsychological2020; @wangImmediatePsychologicalResponses2020; @wangStudyPublicPsychological2021; @wangPsychologicalDistressCoping2020; @zhangImpactCOVID19Pandemic2020] Denmark,[@sonderskovDepressiveStateDenmark] Europe,[@hajekPrevalenceDeterminantsProbable2022] Iran,[@moghanibashi-mansouriehAssessingAnxietyLevel2020] Ireland,[@hylandAnxietyDepressionRepublic2020]  Italy,[@mazzaNationwideSurveyPsychological2020; @mocciaAffectiveTemperamentAttachment2020] Nepal,[@samadarshiOnlineSurveyFactors2020] New Zealand,[@gasteigerDepressionAnxietyStress2021] Spain,[@gonzalez-sanguinoMentalHealthConsequences2020; @ozamiz-etxebarriaStressAnxietyDepression2020] Turkey[@ozdinLevelsPredictorsAnxiety2020],  the United States,[@jiaNationalStateTrends2021, p.
+2020–2021; @kujawaExposureCOVID19Pandemic2020] and the United Kingdom[@dettmannInvestigatingPrevalenceAnxiety2022] report high levels of anxiety (6-51%), depression (15-48%), and post-traumatic stress disorder (7-54%) associated with aspects of the pandemic.
+Globally, it is estimated that the prevalence of depression during the COVID-19 pandemic may be as high as 24%, with the prevalence of anxiety estimated at 21.3%.[@banko-ferranImpactCOVID19Mental2020; @castaldelli-maiaInvestigatingEffectNational2021] This striking burden has been described as a mental health crisis[@melimopoulosHowCOVID19Pandemic2021] and a pandemic in its own right.[@kwaiWhatPointYoung2021]
+
+While COVID-19 continues to bring unprecedented challenges to individuals and societies around the world, the development and distribution of safe and effective vaccines against COVID-19 has fundamentally changed the trajectory of the pandemic.
+Beyond the physical benefits vaccines provide in reducing the risk of infection and associated morbidity and mortality, a growing body of evidence suggests that vaccination has also contributed to improved mental health.[@agrawalImpactCOVID19Vaccine2021; @chourpiliadisShorttermImprovementMental2023; @nguyenPsychologicalBenefitsCOVID192021; @rubinsteinEffectCOVID19Vaccinations2023] Research drawing from the United States Census Bureau’s Household Pulse Survey, for example, has found that the secondary benefits of the protective effects of vaccination may include up to a 30% reduction in symptoms of anxiety and depression in vaccinated adults.[@agrawalImpactCOVID19Vaccine2021]
+
+While this literature suggests that that receiving a COVID-19 vaccine can improve mental health state, the potential mental health benefits of public health announcements regarding the development of vaccines have received comparatively little attention.
+In the context of a deadly pandemic, the announcement of a novel safe and effective vaccine could be a powerful signal, providing a psychological boost and hope that the worst might soon be mitigated.
+Studying how population mental health may have been impacted by the release of vaccine efficacy and safety trial data may provide insights into how emotional well-being changed throughout the COVID-19 pandemic in response to these signals, which, in turn, could inform public health communication and contribute to our understanding of how the public processes and responds to information about vaccines—a necessary understanding for increasing vaccine uptake and trust in public health responses.
+
+A key obstacle to studying the effects of public health responses on population mental health in the US, however, is a lack of daily surveillance data on mental health indicators; a potential marker of population mental health is the use of Internet search data, which offers the potential for real-time, large-scale analysis and identification of evolving mental health issues.
+A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset found strong correlation between search trends for depression and anxiety with indicators of mental health service utilization and need reported in the US Census Household Pulse Survey (HPS) with rates of emergency department visits for mental health condition as reported in the US Centers for Disease Control and Prevention’s (CDC) National Syndromic Surveillance Program (NSSP).[@vaidyanathanEvaluationInternetSearches2022] If taken as a reasonable proxy for mental health complaints, search data can provide valuable information on how population mental health reacts to real-time events and evolves over different shocks, enabling policymakers to better respond to mental health needs and assess reactions to public health efforts.
+
+Our study examines how news regarding the imminent availability of multiple safe and effective COVID-19 vaccines in November 2020 may have impacted population mental health even before these vaccines were made available to the public.
+Using Google search density data, we employed an interrupted time series approach to investigate how these announcements may have affected search trends for mental health symptoms in the United States and in five other countries.
+Owing to emerging evidence that political ideology may be a predictor of confidence in public health and vaccine hesitancy[@debusPoliticalIdeologyVaccination2021; @baumgaertnerInfluencePoliticalIdeology2018; @stolerSociopoliticalPsychologicalCorrelates2022] (with people identifying as conservative being more likely to express skepticism of public health authorities and the scientific community and being more likely to express concerns about the safety, effectiveness, or necessity of vaccines), we further explored whether changes in search trends for mental health symptoms varied across states and counties that predominantly voted Democrat versus Republic in the 2020 president election.
+Our findings suggest both immediate and sustained declines in search density for searches related to anxiety, depression, and major depressive disorder; these declines were observed both in the U.S.
+and abroad, and were found to be consistent irrespective of political ideology.
+
+## Methods
+
+### Data
+
+#### Shock date
+
+We take as our first credible signal of the imminent availability of multiple safe and effective COVID-19 vaccines to be November 16, 2020.
+On November 9, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16th, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S.
+Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
+
+#### Symptoms dataset
+
+We accessed aggregated national and subnational data from Google’s COVID-19 Search Trends
+Symptoms Dataset [@Wahltinez2020] (hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021.
+The symptoms dataset provides time series data of search term density, standardized to pairs of health symptoms and regions (e.g., searches for depression in Australia or for fever in Cook County, Illinois) and normalized within each pair based on the symptom’s relative popularity.
+The time series of search density for each symptom-region pair also contains artificial noise, as Google’s differential privacy technique to data aggregation and anonymization adds random noise to protect user privacy (the errors are symmetrically distributed).
+
+Search density data for over 400 symptoms are reported across national and subnational regions of six countries: Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States.
+In the United States, subnational regions include states and counties.
+Because the aggregated search density trends were constructed based on relative search population within each region, comparison of search density for a specific symptom between different regions is not meaningful; however, comparing search density within regions (or a group of regions) is feasible both over time and across different symptoms.
+
+```{r methods_text_1}
+
+n_states <- data_its_state %>% select(state_name) %>% unique() %>% nrow()
+n_counties <- data_its_county %>% select(county_fips) %>% unique() %>% nrow()
+
+n_states <- format(n_states, big.mark = ",")
+
+n_counties <- format(n_counties, big.mark = ",")
+
+```
+
+For our analysis, we utilized three levels of region from the symptoms dataset: 1) national level data from the six countries in the dataset; 2) U.S.
+state level data across `r n_states` states; and 3) U.S.
+county level data reported by `r n_counties` counties.
+(Though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset.) Following the convention of the symptoms dataset, we will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."
+
+#### Voting dataset
+
+We further obtained county-level presidential election returns for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we then used to calculate aggregate county and state votes (including absentee, early, and election day ballots) won by each candidate.
+The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the candidate with the most votes to the runner up).
+These margins were then used to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth).
+
+#### Population data
+
+Population estimates for 2020 by Federal Information Processing Standards (FIPS) code were obtained from the United States Department of Agriculture (USDA) Economic Research Service.
+
+### Statistical analysis
+
+All analyses were completed using R (version 4.2.1).[@rcoreteamLanguageEnvironmentStatistical2022]
+
+#### Modeling approach
+
+We use an ITS approach to model Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days leading to the vaccine announcement, $Post_i$ is an indicator variable which equals 1 in the period after the shock data and 0 otherwise, $\theta_r$ is a fixed effect for region $r$, and $T^{'}_t\chi$ is a matrix of time-vary fixed effects (i.e., month and day of week).
+
+In our model, $\alpha_d$ can be interpreted as a level or intercept associated with the shock date—that is, the immediate difference in search density for a disease $d$ following November 19, 2020.
+The term $\beta_d$—i.e., the slope change—can be interpreted as the sustained change in search density in the days following November 16th.
+
+```{r methods_text}
+
+diseases_n <- format(max(model_outputs_its$model_number), big.mark = ",")  
+mh_diseases_n <- format(length(list_mental_health_symptoms), big.mark = ",")  
+num_models_multiverse = format(max(model_outputs_multiverse$model_number), big.mark = ",")
+
+```
+We apply this model for all available `r diseases_n` diseases with county-level data.
+As search density may rapidly change in response to a shock, we trimmed the bandwidth of dates to fit our model to forty days before and after November 16, 2020.
+
+To control for time-varying confounders which may have affected symptom search trends during the study period, we applied a CITS approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
+
+After reviewing the list of symptoms for which search density data were available, we identified the following `r mh_diseases_n` mental health related symptoms: `r paste0(gsub("asperger", "Asperger", gsub("_", " ", printList(toPrint = sort(list_mental_health_symptoms), finalSepWord = "and", midSep = ","))),".")`
+
+For each of these mental health symptoms, $d$, we ran the following model to predict search density:
+
+\begin{spacing}{1}
+
+$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d treated_{di} + 
+\ \ \ \ \ $$
+$$\beta_d time_t*treated_{di}  + \delta_{d} Post_i*treated_{di} + \gamma_d time_t*Post_i*treated_{di} + \theta_g + T^{'}_t\chi +  \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ (3.2)$$
+\end{spacing}
+
+\vspace{12pt}
+
+where $treated_{di}$: is an indicator variable which equals 1 if the observation is for a mental health condition $d$, 0 if for headaches.
+The CITS effect estimates of interest are given by $\delta$, which reflects the additional level shift among mental health related symptoms searches compared to searches for headaches after the vaccine announcement, and  $\gamma$, the additional change in search density over time (i.e., slope change) comparing the same.
+
+Given the high number of observations in our sample, we evaluated significance against an alpha of 0.01, and we constructed 99% confidence intervals using heteroskedasticity-robust standard errors.
+
+##### Sensitivity analysis
+
+As with other quasi-experimental methods, it is recommended that the modeling choices and specifications of a CITS analysis be evaluated using a sensitivity analysis.
+To do so, we defined a list of seven methodological choices concerning data processing and modeling assumptions and interacted these choices to generate all their plausible  combinations.
+These combinations were then conducted to allow for a multiverse analysis to identify how sensitive effect estimates and confidence intervals were to different methodological choices.
+
+These criteria used to generate the plausible model combinations are outlined in Table 3.1.
+
+\vspace{12pt}
+
+\begin{raggedright}
+
+```{r table3_1, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table3_1.png")
+
+```
+
+\addcontentsline{lot}{table}{Table 3.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis}
+
+\end{raggedright}
+
+First, we considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, we compared the level of region of aggregated data, using U.S.
+counties, U.S.
+states, and, finally, national trends from the six counties in the sample.
+Third, we evaluated sensitivity to our specification of the bandwidth cut-off around the shock date, extending this from ±40 days to 40 and 60 days.
+Fourth, we toggled whether to account for day of week fixed effects.
+Fifth, we toggled month fixed effects.
+Sixth, we similarly toggled regional fixed effects (i.e., fixed effects for states in the U.S.
+state level data, fixed effects for counties in the U.S.
+county level data, etc.).
+
+Interacting these choices resulted in 144 plausible models for each symptom.
+Each of the 144 models were run for all `r mh_diseases_n` mental health related symptoms, resulting in `r num_models_multiverse` models being conducted overall.
+
+##### Subgroup analysis
+
+Two subgroup analyses were conducted to investigate the generalizability of the findings of the main analysis and to explore potential heterogeneities in measures of association.
+
+The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using our nationally aggregated data.
+This analysis aimed to investigate the extent to which effects observed in US states and counties were also seen in other countries.
+
+The second subgroup analysis applied the CITS approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share.
+Our subgroup analysis comparing CITS effect estimates in blue vs.
+red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
+
+### Ethics statement
+
+The Institutional Review Board (IRB) of the Harvard T.H.
+Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).
+
+## Results
 
@@
 All three of these symptoms had relatively large slope changes in our ITS analysis.
-In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "level")`, a decrease double in magnitude compared to the majority of estimates for other symptoms.
+In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "intercept")`, a decrease double in magnitude compared to the majority of estimates for other symptoms.
 
@@
 
-```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
+```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='', fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: anxiety in blue and headaches in grey.
@@
 
-```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
+```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: depression in blue and headaches in grey.
@@
 
-```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
+```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: MDD in blue and headaches in grey.
@@
 The top panel reports estimates of the level shift and the lower panel reports the estimates for the slope change.
-Effect estimates are represented as solid black lines, with the shaded regions above and below the lines showing the 95% confidence intervals.
+Effect estimates are represented as solid black lines, with the shaded regions above and below the lines showing the 95\\% confidence intervals.
 The solid black line across all panels reflects a null effect.

### 2023-02-25 thesis.Rmd
Abstract and Introduction for Paper 3

@@
 
-# Maps in Chapter 1 need to be improved to eliminate errors in cartographic resolution
+# Acronyms with acronym down
 # Separate bibliography for each section
 # Numbered figures and tables by section
+
 # Check that sequential articles are represented by a dash
 # Table of figures and tables
-# Acronyms with acronym down
 # Institutional authors need to be fixed in bibliography

### 2023-02-28 paper2.Rmd
Adding rayshader to Madagascar maps

@@
 
+```{r rayshader}
+
+crsLONGLAT <- "+proj=longlat +datum=WGS84 +no_defs"
+map_mdg_0_un <- map_mdg_0_un %>%
+  st_as_sf(crs= crsLONGLAT)
+
+# map_mdg_0 <- map_mdg_0 %>%
+#   st_as_sf(crs= crsLONGLAT)
+
+library(rayshader)
+
+z_level = 6
+
+country_elevation <- get_elev_raster(
+  locations = map_mdg_0_un,
+  z = z_level,
+  clip = "locations")
+
+extent_map = extent(country_elevation)
+
+country_elevation = raster_to_matrix(country_elevation)
+
+ground_units <- ifelse(z_level == 5, 4892.0, 
+                       ifelse(z_level == 6, 2446.0,
+                              "ERROR"))
+
+height_max <- max(country_elevation, na.rm = TRUE)
+
+zscale_selected <- ground_units/40
+
+country_elevation %>%
+  sphere_shade(colorintensity=0.25,
+               sunangle = 360-90+15,
+               texture = 
+                 create_texture(lightcolor = "#FEFEFE",
+                                shadowcolor = "#C6C6C6",
+                                leftcolor = "#EAEAEA",
+                                rightcolor = "#EAEAEA",
+                                centercolor = "#FDFDFD")
+
+                 # grey70","grey60","grey75","grey80","white")
+               # create_texture(col_grey_lightest, col_grey_dark, col_grey_med ,col_grey_light,"white")
+               # create_texture("#8AD7FE","#051C2D","#1D3EDB","white","white")
+               ) %>%
+  # add_shadow(ray_shade(country_elevation, zscale = zscale_selected), max_darken=0.95) %>%
+  # add_shadow(ambient_shade(country_elevation, zscale = zscale_selected), max_darken=0.95) %>%
+  add_water(detect_water(country_elevation), color = "white")  %>%
+  save_png(paste0(gpspath_fig, "/elevation_map.png"))
+
+  library(png)
+
+  madagascar_topo_map <- readPNG(source = paste0(gpspath_fig, "/elevation_map.png"))
+
+# Get the spatial extent of the shapefile
+
+  madagascar_bbox <- st_bbox(map_mdg_0_un)
+
+# Get the spatial extent of the PNG image
+madagascar_map_bbox <- c(xmin = 0, ymin = 0, xmax = ncol(madagascar_topo_map), ymax = nrow(madagascar_topo_map))
+
+# Calculate the scaling factor for the x-axis
+x_scale_factor <- diff(madagascar_bbox[c("xmin", "xmax")]) / diff(madagascar_map_bbox[c("xmin", "xmax")])
+
+# Calculate the scaling factor for the y-axis
+y_scale_factor <- diff(madagascar_bbox[c("ymin", "ymax")]) / diff(madagascar_map_bbox[c("ymin", "ymax")])
+
+# Extract minimum and maximum longitude and latitude
+min_lon <- as.numeric(bbox["xmin"])
+max_lon <-  as.numeric(bbox["xmax"])
+min_lat <-  as.numeric(bbox["ymin"])
+max_lat <-  as.numeric(bbox["ymax"])
+
+function_add_rayshading <- function(){
+   annotation_raster(madagascar_topo_map, 
+                    xmin = madagascar_bbox["xmin"], 
+                    ymin = madagascar_bbox["ymin"], 
+                    xmax = madagascar_bbox["xmax"], # + (1-x_scale_factor * ncol(madagascar_topo_map)), 
+                    ymax = madagascar_bbox["ymax"])  # + (1-y_scale_factor * nrow(madagascar_topo_map))) +
+  }
+
+```
+
 ```{r loading_data}
@@
 
-ecological_zones <- read_excel(
-  paste(data_climate_path,
-        "ecological_zones.xlsx",
-        sep = "/")) %>%
-  rename(ecological_zone = 'ecological_zone (1 = Eastern rainforest; 2 = High Plateau; 3 = Arid/Desert; 4 = Dry Deciduos Forest)',
-         REGION_NAM = region_name)
-
-map_mdg_1 %>% inner_join(ecological_zones, by = "REGION_NAM") %>%
+map_mdg_1_un %>% rename(REGION_NAM = ADM1_EN) %>% inner_join(ecological_zones, by = "REGION_NAM") %>%
   mutate(ecological_zone = ifelse(ecological_zone == 1, "Eastern lowland forests",
@@
                                                               "Dry deciduous forests"))) %>%
-
   ggplot(aes(geometry = geometry, fill = ecological_zone)) +
+  function_add_rayshading() + 
     geom_sf(size = 0.2,
           color = col_grey_med,
-          alpha = 0.6) +
-  geom_sf(data = map_mdg_1_un,
+          alpha = 0.4) +
+  geom_sf(data = map_mdg_0_un,
           size = 0.2,
           color = col_black,
-          fill = NA) +
-  theme_void() +
-  theme(text = element_text(family = "Source Sans Pro"),
+          fill = NA) +theme(text = element_text(family = "Source Sans Pro"),
         legend.position = "right") +
@@
   ggplot(aes(geometry=geometry)) +
+     function_add_rayshading() +
+
   geom_sf(data = map_mdg_3_un,
@@
   ggplot(aes(geometry=geometry)) +
+    function_add_rayshading() +
+
   geom_sf(data = map_mdg_3_un,
@@
 
-ggdraw() +
+ggdraw() +   draw_plot(combined_plot) +
   draw_image(
@@
     hjust = 1, halign = 1, valign = 0
-  )  +
-  draw_plot(combined_plot)
+  )
 
@@
        width = 16,
-       height = 10)
+       height = 10,
+       bg = "white")
 
@@
        width = 6,
-       height = 7)
+       height = 7,
+       bg = "white")
 

### 2023-03-01 appendix_2.2.Rmd
Revisions to Paper 2 from KK, MM, SV, and JC

@@
                         prettyNum(area_lim, big.mark = ",", scientific = FALSE),
-                        " km sq."),
+                        " km²"),
        y = "Count",
@@
 
-Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km sq, with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km sq.
+Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km², with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km².
 At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` square km., all polygon groups fell within the cut-off.
-Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km., with a maximum distance of `r format(round(n_max_length), big.mark = ",")` kilometers.
-At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` km.,  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).
+Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km, with a maximum distance of `r format(round(n_max_length), big.mark = ",")` km.
+At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` km,  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).
 
@@
 While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used.
-The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 30 km.
-sq.
-will have the same time series for a given variable.
+The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 30 km² will have the same time series for a given variable.
 Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.
@@
 ```{r figure_communes_fokontany, include = TRUE, results = TRUE, warning = FALSE, message = FALSE, echo = FALSE, fig.width = 9, fig.height = 8.5, fig.align='center', out.width = '95%',  fig.scap="Communes and fokontany in Madagascar, by area.", out.extra='',  fig.cap="\\label{figure_communes_fokontany}Communes and fokontany in Madagascar, by area.
-Units colored in teal are within the 225 square kilometer threshold for use in Step 5 of the matching process."}
+Units colored in teal are within the 225 km² threshold for use in Step 5 of the matching process."}
 
@@
 
-# Map where area is binary (smaller than value of commune_lim km sq., vs larger)
+# Map where area is binary (smaller than value of commune_lim km², vs larger)
 
@@
                                    prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
-                                   " km sq."),
+                                   " km²"),
                             paste0("> ",
                                    prettyNum(commune_lim, big.mark = ",", scientific = FALSE),
-                                   " km sq.")))%>%
+                                   " km²")))%>%
   ggplot(aes(geometry = geometry))  +
@@
   theme(text = element_text(family = "Source Sans Pro")) +
-  labs(fill = "Area (km sq.)",
+  labs(fill = "Area (km²)",
        title = "Communes",
@@
                                    prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
-                                   " km sq."),
+                                   " km²"),
                             paste0("> ",
                                    prettyNum(fokontany_lim, big.mark = ",", scientific = FALSE),
-                                   " km sq.")))%>%
+                                   " km²")))%>%
   ggplot(aes(geometry = geometry))  +
@@
   theme(text = element_text(family = "Source Sans Pro")) +
-  labs(fill = "Area (km sq.)",
+  labs(fill = "Area (km²)",
        title = "Fokontany",
@@
 
-Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(validation_mean_dist,2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(validation_max_dist, 1), big.mark = ",")` kilometers.
+Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(validation_mean_dist,2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(validation_max_dist, 1), big.mark = ",")` km.
 The distance between geolocated and validated coordinates for each of the facilities in the validation sample is reported in Table S2.11.

### 2023-03-01 paper2.Rmd
Revisions to Paper 2 from KK, MM, SV, and JC

@@
 library(ggridges)
+library(elevatr)
+library(raster)
+library(rayshader)
+
 # library(ggsn)
@@
 
-library(rayshader)
-
 z_level = 6
@@
                   "outputs_marginal_effects_predictions.Rdata", sep = "/"))
+
+ecological_zones <- read_excel(
+  paste(data_climate_path,
+        "ecological_zones.xlsx",
+        sep = "/")) %>%
+  rename(ecological_zone = 'ecological_zone (1 = Eastern rainforest; 2 = High Plateau; 3 = Arid/Desert; 4 = Dry Deciduos Forest)',
+         REGION_NAM = region_name)
 
@@
 
-{\bf Background:} Climate change-related exposures (CCEs) have been increasingly linked to worsened mental health, yet few studies of CCEs have taken place in low- and middle-income countries.
-
-{\bf Methods:} To better understand how climate conditions may be impacting population mental health in these settings, we leverage meteorologic, geospatial, and health system data reported by `r num_facilities_pretty` facilities in Madagascar from 2010 to 2020 to explore the mental health impacts of three exposures of climate using negative binomial regression: temperature, soil moisture, and duration of cyclones and tropical storms.
-
-{\bf Findings and interpretation:} We found a statistically significant reduction in monthly cases associated with temperature—approximately `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = "only")` cases reported per each degree Celsius `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = TRUE)`.
-A multiverse analysis of `r num_models_multiverse` models found this estimate to be robust to alternative specifications, while a subgroup analysis by ecoregion indicated that this association was primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
-We further found that higher soil moisture may be associated with higher case counts in the future, with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")`  elevation in incident cases reported `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`  after a lag of three months.
-We further found that greater soil moisture was associated with higher cases reported in the eastern lowlands and the northern dry deciduous forests, which is consistent with the geographic concentration of flood risk in Madagascar.
+{\bf Background:} Climate change-related exposures (CCEs) are linked to worsened mental health, yet few studies of CCEs have taken place in low- and middle-income countries.
+
+{\bf Methods:} To better understand climate conditions and population mental health in these settings, we leverage meteorologic, geospatial, and monthly cases of mental and neurological disorders reported by `r num_facilities_pretty` facilities in Madagascar from 2010 to 2020 to explore the mental health impacts of three CCEs using negative binomial regression: temperature, soil moisture, and duration of cyclones and tropical storms.
+
+{\bf Findings and interpretation:} We found a statistically significant reduction in monthly cases reported associated with temperature—approximately `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = "only")` cases reported per each degree Celsius increase `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = TRUE)`.
+A multiverse analysis of `r num_models_multiverse` models found this estimate to be robust to alternative specifications; ecoregion analysis indicated that this association was primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
+We further found that higher soil moisture may be associated with higher case counts in the future, with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")`  elevation in incident cases reported `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`  after a three month lag.
+Ecoloregion analysis suggest higher cases are reported in the eastern lowlands and the northern dry deciduous forests when soil moisture rises, which is consistent with the geographic concentration of flood risk in Madagascar.
+Our findings highlight the complex interactions between CCEs and population mental health and suggest potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.
 
@@
 
-Among low-income countries most vulnerable to the health consequences of climate change is Madagascar, a nation that generates less than a tenth of a percentage of global carbon dioxide emissions.
+Among low-income countries most vulnerable to the health consequences of climate change is Madagascar, a nation that generates one percent *of* one percent of global carbon dioxide emissions.
 Worsening CCEs in Madagascar (primarily in the form of droughts, floods, and cyclones) are likely to exacerbate endemic, climate-sensitive threats to health, including malnutrition and malaria.[@rakotoarisonAssessmentRiskVulnerability2018] In particular, persistent drought conditions in recent years have led to extensive food insecurity.[@adamtaylorMadagascarHeadedClimate] Though there is debate concerning the extent to which human activity is directly responsible for Madagascar's current drought,[@harringtonAttributionSevereLow; @zhongManyDimensionsDrought2021] the extremity of the situation has led some observers to classify conditions in Madagascar as the first climate change famine in history.[@worldfoodprogrammeMadagascarSevereDrought2021]
@@
 Understanding how both incremental and extreme changes in climate impact population mental health is critical to gauging the full extent to which CCEs impact human health and wellbeing under a multidisciplinary approach to population health.[@berryCaseSystemsThinking2018] This understanding is particularly important in contexts such as Madagascar, where climate conditions are already demonstrating pronounced pressures on economic, social, and physical wellbeing.
+
+In investigating the impact of climate exposures on mental health, health system data can serve as a useful tool in settings where epidemiological survey data is sparse.
+Despite the poor availability of mental health services in many settings, routine health system data can still provide valuable insights into trends and patterns of service use and the need and distribution of care for mental health issues.
+Although these data may only capture a share of the true burden of disease, reported cases and visits related can be a valuable starting point for preliminary research into the impact of climate change on population mental health in resource-constrained settings.
 
@@
 The use of health system data enabled us to indirectly evaluate the extent to which existing public health data may already be showing signals of CCEs, which may aid efforts to prevent and mitigate mental health stressors and better design systemic responses to mental health needs.
-As a measure of population mental health, we considered facility-level monthly counts of new diagnoses of mental disorders.
-To capture the importance of both variation in temperature and precipitation conditions in Madagascar, we explored the predictive association of three climate conditions with incident mental health disorders: mean monthly ambient air temperature, mean monthly soil moisture, and monthly cyclone activity.
+
+As a measure of population mental health, we considered facility-level monthly reports cases of mental disorders; in terms of exposure, we explored the predictive association of three CCEs with incident mental health visits: mean monthly ambient air temperature, mean monthly soil moisture, and monthly cyclone activity.
+As exposure to these stressors could involve a delay in onset of mental health symptoms and subsequent care seeking, we further explored whether exposures in prior months were associated with monthly reported cases in sequent ones.
+We further considered interactive and additive models to account for complexity in the interaction of climate variables in Madagascar, as well as ecological variation to capture differences in regional climate systems.
 
@@
 Among CSB facilities, incidences of mental disorders were reported by age group under “mental illnesses and psychic disorders” until June 2015, when reporting was reclassified to “mental disorders,” and disaggregated data was reported by both age and sex.
+A summary of classification by facility type and year is provided in Appendix 2.1, Table S2.1, with English translations of the French disease names provided in Table S2.2.
+and yearly cumulative reported case totals by disorder reported by facility level and year in Tables S2.3-5.
 
@@
 To gauge the accuracy of the geolocating process, a subset of 1% of geolocated facilities was selected for validation against manually identified coordinates.
-Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` kilometers, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data.
+Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` km, with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` km, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data.
 Additional detail on the geolocating and validation process is available in Appendix 2.2.
@@
 ERA 5 is a global atmospheric reanalysis from the European Centre for Medium-Range Weather Forecasts (ECMWF) and is freely available through its Copernicus Climate Change Service (C3S)@europeanspaceagencyEuropeanSpaceAgency2022.
-The spatial resolution of ERA 5 is approximately 30 km., with quality-assured hourly estimates available from 1959 to the present  @europeanspaceagencyEuropeanSpaceAgency2022.
+The spatial resolution of ERA 5 is approximately 30 km, with quality-assured hourly estimates available from 1959 to the present  @europeanspaceagencyEuropeanSpaceAgency2022.
 Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation  @ERA5MonthlyAggregates2022.
@@
 We obtained soil moisture data from the European Space Agency’s soil moisture dataset (ESA CCI SM), the world’s first and most comprehensive, multi-decade, satellite-observed dataset of global soil moisture.
-The spatial resolution of ESA CCI SM is approximately 26 km., with daily estimates available from 1978 to 2021.
+The spatial resolution of ESA CCI SM is approximately 26 km, with daily estimates available from 1978 to 2021.
 Using ESA CCI SM active and passive radiometer data, a time series of monthly aggregate values for mean soil moisture—measured as saturation percentage—was constructed from daily observations at each land grid point within Madagascar.
@@
 
+Though CCEs could acutely impact mental health in our sample, we could anticipate that these impacts might not immediately result in changes to monthly case and visit counts, owing to delays in symptom onset, care seeking, and care delivery.
 To test for lagged associations—that is, whether in a given month, climate conditions in prior months were associated with counts of mental disorders—versions of Model 4 were conducted using lagged predictors.
@@
 Fifth, we evaluated alternative specifications of exposure to cyclone activity, using three options: our binary indicator, our count indicator, and no term for cyclone activity included.
-Sixth, we toggled whether time fixed effects (month and year) were included.
-Seventh, we similarly toggled regional fixed effects.
+Sixth, we varied whether time fixed effects (month and year) were included.
+Seventh, we similarly included and excluded regional fixed effects for comparison.
 
@@
   gt(rowname_col = "coefficient", groupname_col = "model") %>%
-  tab_header(title = md("Table 2.2: incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.")) %>%
+  tab_header(title = md("Table 2.2: incidence rate ratios (IRRs) and average marginal effects (AME) of climate exposures on monthly reported cases of mental and neurological disorders, Models 1 through 4.")) %>%
 
@@
              columns = c('IRR (99% CI)' , 'M.E. (99% CI)')) %>%
-  tab_footnote(footnote = "All models include month, year, and regional fixed effects.",
+  tab_footnote(footnote = "Model 1: Temperature only.
+Model 2: Soil moisture only.
+Model 3: Temperature and soil moisture, additive model.
+Model 4: Temperature and soil moisture, interactive model.
+All models include a count indicator for days of exposure to cyclone activity, as well as month, year, and regional fixed effects.",
                locations = cells_row_groups()) %>%
@@
 
-With respect to soil moisture, while our primary analysis found no evidence of a statistically significant association with reported cases in the full sample, we did find evidence of heterogeneity in our subgroup analysis.
+With respect to soil moisture, while our primary analysis found no evidence of a statistically significant association with reported cases in the full sample, we found evidence of heterogeneity in our subgroup analysis.
 Among facilities in the highland subhumid forests, we found that each percentage point increase in soil moisture was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = TRUE)`, with an average marginal effect of `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = FALSE)`.
@@
 In our study of health facilities in Madagascar, we investigated how temperature, soil moisture, and exposure to cyclone activity impacted monthly incident cases of mental and neurological disorders reported by `r num_facilities_pretty`  facilities between 2010 and 2020.
-We found evidence of a statistically significant reduction in reported cases associated with mean monthly temperature, with warmer temperature being, on average, associated with 2 to 3 fewer cases per month.
+This study had three major findings.
+First, we found evidence of a statistically significant reduction in reported cases of approximately 4.5% associated with mean monthly temperature, with warmer temperature being, on average, associated with 2 to 3 fewer cases per month.
 According to our multiverse analysis, the statistically significant inverse association we observed was robust to numerous specifications, while our subgroup analysis indicated that this association was primarily localized in the highland subhumid forest ecoregion.
-
-With respect to soil moisture, we found evidence to suggest potential lagged impacts, with higher soil saturation being associated with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in reported case counts in the subsequent quarter.
-We also found evidence of possible effect heterogeneity, with each percentage point increase in soil moisture leading to an *elevation* of cases in the dry deciduous forest ecoregion `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = TRUE)` and a *decrease* in cases in the highland subhumid forests `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = TRUE)`.
-
-Finally, while our lagged models and multiverse analysis suggested the possibility of a negative relationship between cyclone activity and incident case counts reported in Madagascar, the marginal effects associated with cyclone duration were negligible, and we did not observe sufficient statistically significant evidence to reject the null assumption of no association at a level of 0.01.
-
-It is important to note in our interpretation of these findings that the true relationship between reported mental health cases and actual cases of mental disorders is not well understood, particularly in Madagascar where data on disease etiology is limited.
-The changes in reported cases could reflect changes in the actual cases of mental disorders, but could also result from changes in help-seeking behavior, diagnostic capacity, or other factors.
-Additionally, it is widely recognized that a significant proportion of individuals with mental disorders do not receive any treatment, particularly in low-income settings.
+Second, we found evidence to suggest potential lagged impacts, with higher soil saturation being associated with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in reported case counts in the subsequent quarter.
+We also found evidence of possible effect heterogeneity, with each percentage point increase in soil moisture leading to an *elevation* of cases in the dry deciduous forest ecoregion and a *decrease* in cases in the highland subhumid forests.
+Third, while our lagged models and multiverse analysis suggested the possibility of a negative relationship between cyclone activity and incident case counts reported in Madagascar, the marginal effects associated with cyclone duration were negligible, and we did not observe sufficient statistically significant evidence to reject the null assumption of no association at a level of 0.01.
+
+It is important to note in our interpretation of these findings that the true relationship between reported mental health cases and actual cases of mental disorders is not well understood, particularly in Madagascar, where there is no epidemiological data on the prevalence or distribution of mental disorders in the general population.
+The changes in reported cases could reflect changes in the actual cases of mental disorders, but could also result from the influence of CCEs on help-seeking behavior, diagnostic capacity, or other factors.
+Additionally, it has been widely recognized that the majority individuals with mental disorders often do not receive any mental health treatment, particularly in low-income settings.
+[@demyttenaerePrevalenceSeverityUnmet2004]
 
@@
 
-Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we did observe a significant association of higher soil moisture and cases of mental health complaints in the following quarter, echoing similar findings from U.S.
+Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we observed a significant association of higher soil moisture and cases of mental health complaints in the following quarter, echoing similar findings from U.S.
 meteorological data linking higher precipitation with worsened mental health.[@obradovichEmpiricalEvidenceMental2018] In addition, our subgroup analysis also indicated significant and diverging effects among different ecoregions.
@@
 
-Despite these limitations, our analysis brings together health data from over three thousand health facilities over ten years, utilizing the most comprehensive sources of climate data available, and linking the two via a rigorous, multistep geolocating process.
-This study—one of the only to investigate mental health and climate in Africa using national HMIS data—underscores the need for further research to understand the relationships and pathways between changing climate and population mental health.
+Despite these limitations, our study has important implications for future research on the relationship between climate change exposures and population mental health.
+By leveraging, reported cases from over three thousand health facilities over ten years, utilizing the most comprehensive sources of climate data available, and linking the two via a rigorous, multistep geolocating process, our analysis demonstrates how routine health system data may offer valuable insights, particularly when other epidemiological data are not available.
+As one of the only studies to investigate mental health and climate in Africa using national HMIS data, our findings also underscore the need for further research to understand the relationships and pathways between changing climate and population mental health, particularly countries most vulnerable to climate change.
+Finally, our findings and interpretations highlight the importance of local knowledge and collaboration with local ministries in global health research, to make best use of existing data and to foster research to support health system strengthening.
+We believe that this approach to research is essential for understanding the complex relationships and mechanisms linking climate change exposures to mental health, as well as identifying strategies to mitigate these impacts amid the unfolding global climate crisis.
 

### 2023-03-02 appendix_2.1.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

@@
     # ungroup() %>%
-    # select(clinic_name, disease, year, ) %>%
+    # dplyr::select(clinic_name, disease, year, ) %>%
     # unique() %>%
@@
     mutate(sum = sum(count)) %>%  
-    select(sum, year, disease) %>% 
+    dplyr::select(sum, year, disease) %>% 
     ungroup() %>%
@@
                           StrTrunc(disease, maxlen = 25, ellipsis = "...", wbound = TRUE),")")) %>%
-      select(year, disease, sum) %>%
+      dplyr::select(year, disease, sum) %>%
     rename(Year = year, Total = sum) %>%
@@
 
-n_chu <- chu_data %>% select(disease) %>% unique() %>% nrow
+n_chu <- chu_data %>% dplyr::select(disease) %>% unique() %>% nrow
 
@@
   left_join(., mh_english_disease, by = "disease") %>%
-  select(!c(disease)) %>%
+  dplyr::select(!c(disease)) %>%
   rename(disease = disease_english) %>%
@@
 data_mh_temp <- data_mh %>%
-  select(clinic_name, region_name, district_name, commune_name) %>%
+  dplyr::select(clinic_name, region_name, district_name, commune_name) %>%
   unique() %>%
@@
 data_mh_temp <- data_mh %>%
-   select(!c(disease, count)) %>%
+   dplyr::select(!c(disease, count)) %>%
    unique() %>%
@@
 data_mh <- data_mh %>%
-  select(!c('Any mental or neurological disorders')) %>%
+  dplyr::select(!c('Any mental or neurological disorders')) %>%
   rbind(., data_mh_temp)
@@
 
-data_mh %>% filter(sex == "both") %>% select(clinic_name, district_name, region_name, commune_name) %>% unique() %>% nrow()
+data_mh %>% filter(sex == "both") %>% dplyr::select(clinic_name, district_name, region_name, commune_name) %>% unique() %>% nrow()
 
@@
 <!--   mutate(reporting = ifelse(count == 0, NA, "Yes")) %>% -->
-<!--   select(date, region_name, district_name, commune_name, clinic_name_clean, clinic_type, reporting) %>% -->
+<!--   dplyr::select(date, region_name, district_name, commune_name, clinic_name_clean, clinic_type, reporting) %>% -->
 <!--   unique() -->
@@
 <!-- duplicate_name_facilities <- data_facility_reporting %>% -->
-<!--   select(region_name, district_name, commune_name, clinic_name_clean, clinic_type) %>% -->
+<!--   dplyr::select(region_name, district_name, commune_name, clinic_name_clean, clinic_type) %>% -->
 <!--   unique() %>% -->
@@
 <!--   filter(full_string %in% duplicates) %>% -->
-<!--   select(!full_string) %>% -->
+<!--   dplyr::select(!full_string) %>% -->
 <!--   arrange(clinic_name_clean) %>% -->
@@
 <!--   unique() %>% -->
-<!--   select(clinic_name_clean, clinic_type) %>% -->
+<!--   dplyr::select(clinic_name_clean, clinic_type) %>% -->
 <!--   rename("Facility name" = clinic_name_clean, -->
@@
 ## ## Identify all unique variable descriptions, names, tables, and medical codes
-## variable_descrip <- data_raw %>% select(description) %>% unique()
-## variable_name <- data_raw %>% select(variable) %>% unique()
-## variable_tabname <- data_raw %>% select(table_name) %>% unique()
-## variable_medco <- data_raw %>% select(medical_code) %>% unique()
+## variable_descrip <- data_raw %>% dplyr::select(description) %>% unique()
+## variable_name <- data_raw %>% dplyr::select(variable) %>% unique()
+## variable_tabname <- data_raw %>% dplyr::select(table_name) %>% unique()
+## variable_medco <- data_raw %>% dplyr::select(medical_code) %>% unique()
 ## 
@@
 ## medical_codes <- read.csv(paste(datapath, "medical_codes.csv", sep = "/")) %>%
-##   select(code, description) %>% 
+##   dplyr::select(code, description) %>% 
 ##   rename(medical_code = code)
@@
 ##   ungroup() %>%
-##   select(date, count) %>%
+##   dplyr::select(date, count) %>%
 ##   unique()
@@
 ## ## Extraction of unique clinics and district appearing in the data
-## facilities_clinic_codes <- data_raw %>% select(clinic_code) %>% unique()
-## facilities_district_codes <- data_raw %>% select(district_code) %>% unique()
+## facilities_clinic_codes <- data_raw %>% dplyr::select(clinic_code) %>% unique()
+## facilities_district_codes <- data_raw %>% dplyr::select(district_code) %>% unique()
 ## 
@@
 ##                                  header=TRUE) %>% 
-##   select(district_code, clinic_code, name) %>%
+##   dplyr::select(district_code, clinic_code, name) %>%
 ##   rename(clinic_name = name) %>%
@@
 ##                                 header=TRUE) %>% 
-##   select(district_code, district_type, name) %>%
+##   dplyr::select(district_code, district_type, name) %>%
 ##   rename(district_name = name) %>%
@@
 ##                                    header=TRUE) %>%
-##   select(Nom.complet.FS.1, latitude, longitude) %>% 
+##   dplyr::select(Nom.complet.FS.1, latitude, longitude) %>% 
 ##   rename(clinic_name = Nom.complet.FS.1) %>%
@@
 ##   rename(district_name = ADM2_EN) %>%
-##   select(district_name, ADM2_PCODE)
+##   dplyr::select(district_name, ADM2_PCODE)
 ## 
@@
 ##   filter(!is.na(ADM2_PCODE)) %>%
-##   select(district_code, district_name, ADM2_PCODE) %>%
+##   dplyr::select(district_code, district_name, ADM2_PCODE) %>%
 ##   unique()
@@
 ## ## Standardizing district names to shapefile names (ADM2_EN)
-## facilities_map_clean <- facilities_map %>% select(clinic_code:clinic_name) %>%
+## facilities_map_clean <- facilities_map %>% dplyr::select(clinic_code:clinic_name) %>%
 ##   left_join(., district_crosswalk, by = "district_code") %>%
-##   select(!c(district_name)) %>%
+##   dplyr::select(!c(district_name)) %>%
 ##   rename(district_name = rename) %>%
@@
 ## map_clean %>%
-##   select(ADM2_PCODE, district_name, district_code, geometry) %>%
+##   dplyr::select(ADM2_PCODE, district_name, district_code, geometry) %>%
 ##   left_join(., facility_district_count, by = "ADM2_PCODE") %>%

### 2023-03-02 appendix_2.2.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

@@
 data_mh <- rbind(csb_data, chd_data, chu_data) %>% # Join all data
-  select(commune, district, region, clinic_name) %>%
+  dplyr::select(commune, district, region, clinic_name) %>%
   mutate(region = str_to_title(region), # Capitalizing region names
@@
 
-n_facilities_name <- data_mh %>% select(clinic_name) %>% unique %>% nrow()
+n_facilities_name <- data_mh %>% dplyr::select(clinic_name) %>% unique %>% nrow()
 n_facilities <- data_mh %>% unique %>% nrow()
@@
 data_mh_dup_names <- data_mh %>%
-  select(region, clinic_name) %>% unique()
+  dplyr::select(region, clinic_name) %>% unique()
 
@@
 # data_mh_dup_names %>%
-#   select(region, clinic_name) %>%
+#   dplyr::select(region, clinic_name) %>%
 #   unique() %>%
@@
 
-column2 <- data_mh %>% select(commune, district, region) %>% unique()
-column1 <- facilities_all %>% select(region_name, district_name, commune_name) %>% unique()
-
-r_old <- column1 %>% select(region_name) %>% unique()
-r_new <- column2 %>% select(region) %>% unique()
+column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique()
+column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique()
+
+r_old <- column1 %>% dplyr::select(region_name) %>% unique()
+r_new <- column2 %>% dplyr::select(region) %>% unique()
 
@@
          "Standardized name" = region_name) %>%
-  select(!test) %>%
+  dplyr::select(!test) %>%
   gt() %>%
@@
   filter(test == FALSE) %>%
-  select(!test) %>%
+  dplyr::select(!test) %>%
   rename("Name in data" = commune_old,
@@
   st_join(data,., join = st_within) %>%
-  select(clinic_name, clinic_type, source, 
+  dplyr::select(clinic_name, clinic_type, source, 
          COMMUNE_NA, DISTRICT_N, REGION_NAM, geometry) %>%
@@
       # And drop all columns except for the unique commune-district-region name, centroid, and area
-      select(area_km, full_name, geometry)
+      dplyr::select(area_km, full_name, geometry)
 
@@
   # And drop all columns except for the unique commune-district-region name, centroid, and area
-  select(area_km, full_name, geometry)
+  dplyr::select(area_km, full_name, geometry)
 
@@
   data_no_gps <- data_trim %>%
-    select(full_name, facility_ID) %>%
+    dplyr::select(full_name, facility_ID) %>%
     mutate(full_name = str_squish(full_name))
@@
     data_gps <- data_trim_2 %>%
-    select(full_name, area_km) %>%
+    dplyr::select(full_name, area_km) %>%
     mutate(full_name = str_squish(full_name))
@@
   data_gps <- data_trim_2 %>%
-    select(full_name, ID) %>%
+    dplyr::select(full_name, ID) %>%
     mutate(full_name = str_squish(full_name))
@@
   perfect_matches <- inner_join(data_gps, data_no_gps)
-in_perfect_matches <- perfect_matches %>% select(facility_ID) %>% unique()
+in_perfect_matches <- perfect_matches %>% dplyr::select(facility_ID) %>% unique()
   in_perfect_matches <- as.vector(in_perfect_matches$facility_ID)
@@
     inner_join(., data_no_gps) %>%
-    select(!c(s2.i, s1.i)) %>%
+    dplyr::select(!c(s2.i, s1.i)) %>%
    rbind(perfect_matches) %>%
@@
     arrange(adist) %>%
-    select(full_name, full_name_gps, adist) %>%
+    dplyr::select(full_name, full_name_gps, adist) %>%
     rename("String (sample)" = full_name,
@@
   facilities_all_gps_temp <- asm_matches_retained %>%
-    select(geometry, facility_ID) %>%
+    dplyr::select(geometry, facility_ID) %>%
     unique()
@@
 
-  with_gps <- facilities_all_gps %>% select(facility_ID) %>% unique()
+  with_gps <- facilities_all_gps %>% dplyr::select(facility_ID) %>% unique()
   with_gps <- as.vector(with_gps$facility_ID)
@@
     st_transform(crs = 4326) %>%
-    select(geometry, facility_ID) %>%
+    dplyr::select(geometry, facility_ID) %>%
     unique()
@@
          clinic_type = gsub("Health Centre", "CSB2", clinic_type)) %>%
-  select(!c(Country, Ownership)) %>%
+  dplyr::select(!c(Country, Ownership)) %>%
     rename(source = LL.source,
@@
 facilities_gps_who_0 <- facilities_gps_who %>%
-  select(clinic_type, latitude, longitude, source, clinic_name) %>%
+  dplyr::select(clinic_type, latitude, longitude, source, clinic_name) %>%
   st_drop_geometry()
@@
          clinic_type = FacilityType) %>%
-  select(district_name, clinic_name, 
+  dplyr::select(district_name, clinic_name, 
          clinic_type, latitude, longitude) %>%
@@
   mutate(source = "RHINoVision Decision Support System") %>%
-  select(clinic_name, longitude, latitude, source, clinic_type)
+  dplyr::select(clinic_name, longitude, latitude, source, clinic_type)
 
@@
                                        sep = "/")) %>%
-  select(name, geometry, osm_id) %>%
+  dplyr::select(name, geometry, osm_id) %>%
   unique() %>%
@@
   st_drop_geometry() %>%
-  select(clinic_name, X, Y, ID_OSM)
+  dplyr::select(clinic_name, X, Y, ID_OSM)
 
 crs_system <- st_crs(facilities_gps_OCHA_1)
-with_gps_OCHA <- facilities_gps_OCHA_1 %>% select(ID_OSM) %>% unique()
+with_gps_OCHA <- facilities_gps_OCHA_1 %>% dplyr::select(ID_OSM) %>% unique()
 with_gps_OCHA <- with_gps_OCHA$ID_OSM
@@
   filter(!is.na(name)) %>%
-  select(name, X, Y, osm_id) %>%
+  dplyr::select(name, X, Y, osm_id) %>%
   rename(clinic_name = name, ID_OSM = osm_id) %>%
@@
   mutate(source = "OpenStreetMap", type = NA) %>%
-  select(!c(ID_OSM))
+  dplyr::select(!c(ID_OSM))
 
@@
   # Trim dataset
-  select(region, district, commune, type, FS, longitude, latitude) %>%
+  dplyr::select(region, district, commune, type, FS, longitude, latitude) %>%
   rename(clinic_name = FS, district_name = commune) %>%
@@
   mutate(source = "File 1 (Consultant?)") %>%
-  select(clinic_name, longitude, latitude, source, type)
+  dplyr::select(clinic_name, longitude, latitude, source, type)
 
@@
   mutate(longitude = as.numeric(longitude)) %>%
-  select(Nom.Commune, Type..CSB1..CSB2.., 
+  dplyr::select(Nom.Commune, Type..CSB1..CSB2.., 
          Nom.complet.FS.1, latitude, longitude) %>% 
@@
   mutate(source = "File 2 (MOH?)") %>%
-  select(clinic_name, longitude, latitude, source, type) %>%
+  dplyr::select(clinic_name, longitude, latitude, source, type) %>%
 
@@
   rename(district_name = District, clinic_name = Health.center.names) %>%
-  select(district_name, clinic_name, latitude, longitude) %>%
+  dplyr::select(district_name, clinic_name, latitude, longitude) %>%
 
@@
   mutate(source = "File 3 (?)", type = NA) %>%
-  select(clinic_name, longitude, latitude, source, type)
+  dplyr::select(clinic_name, longitude, latitude, source, type)
 
@@
          latitude = "Y", longitude = "X") %>%
-  select(district_name, clinic_name, latitude, longitude) %>%
+  dplyr::select(district_name, clinic_name, latitude, longitude) %>%
 
@@
   mutate(source = "File 4 (Consultant)", type = NA) %>%
-  select(clinic_name, longitude, latitude, source, type)
+  dplyr::select(clinic_name, longitude, latitude, source, type)
 
@@
          latitude = Latitude, longitude = Longitude) %>%
-  select(district_name, clinic_name, latitude, longitude) %>%
+  dplyr::select(district_name, clinic_name, latitude, longitude) %>%
 
@@
   mutate(source = "File 5 (Chris)", type = NA) %>%
-  select(clinic_name, longitude, latitude, source, type)
+  dplyr::select(clinic_name, longitude, latitude, source, type)
 
@@
   ungroup() %>%
-  select(source, clinic_type, value) %>%
+  dplyr::select(source, clinic_type, value) %>%
   unique() %>%
@@
   st_drop_geometry() %>%
-  select(area_km) %>%
+  dplyr::select(area_km) %>%
   mutate(mean = mean(area_km)) %>%
-  select(mean) %>%
+  dplyr::select(mean) %>%
   unique()
@@
   st_drop_geometry() %>%
-  select(area_km) %>%
+  dplyr::select(area_km) %>%
   mutate(max = max(area_km)) %>%
-  select(max) %>%
+  dplyr::select(max) %>%
   unique()
@@
   st_drop_geometry() %>%
-  select(length) %>%
+  dplyr::select(length) %>%
   mutate(mean = mean(length)) %>%
-  select(mean) %>%
+  dplyr::select(mean) %>%
   unique()
@@
   st_drop_geometry() %>%
-  select(length) %>%
+  dplyr::select(length) %>%
   mutate(max = max(length)) %>%
-  select(max) %>%
+  dplyr::select(max) %>%
   unique()
@@
   st_centroid() %>% 
-  select(!c(shape_type, length, area_km, retain)) %>%
+  dplyr::select(!c(shape_type, length, area_km, retain)) %>%
   clean_catchment_area() %>%
@@
   facilities_manual_matches %>%
-  select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
+  dplyr::select(commune_name, district_name, clinic_name, clinic_type, clinic_type_new,
          clinic_name_new, district_name_new, commune_name_new, region_name, region_name_new) %>%
@@
   mutate_all(~replace_na(.,"")) %>%
-select(order(colnames(.),
+dplyr::select(order(colnames(.),
                       decreasing = FALSE)) %>%
@@
 # region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
-    # select(!c(region_name, region_name_new)) %>%
-      select(c(clinic_name, clinic_name_new)) %>%
+    # dplyr::select(!c(region_name, region_name_new)) %>%
+      dplyr::select(c(clinic_name, clinic_name_new)) %>%
 
@@
 # region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
-    # select(!c(region_name, region_name_new)) %>%
-      select(c(clinic_name, clinic_type, clinic_type_new)) %>%
+    # dplyr::select(!c(region_name, region_name_new)) %>%
+      dplyr::select(c(clinic_name, clinic_type, clinic_type_new)) %>%
 
@@
 # region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
-    # select(!c(region_name, region_name_new)) %>%
-      select(c(clinic_name, district_name, district_name_new)) %>%
+    # dplyr::select(!c(region_name, region_name_new)) %>%
+      dplyr::select(c(clinic_name, district_name, district_name_new)) %>%
 
@@
 # region_name_new=str_replace_all(region_name_new," ","<br>")) %>%
-    # select(!c(region_name, region_name_new)) %>%
-      select(c(clinic_name, commune_name, commune_name_new)) %>%
+    # dplyr::select(!c(region_name, region_name_new)) %>%
+      dplyr::select(c(clinic_name, commune_name, commune_name_new)) %>%
 
@@
   inner_join(., facilities_manual_matches, by = c("clinic_type_new", "clinic_name_new", "region_name_new", "district_name_new", "commune_name_new")) %>%
-  select(geometry, commune_name,  region_name, clinic_name_full) %>%
+  dplyr::select(geometry, commune_name,  region_name, clinic_name_full) %>%
   rename(clinic_name = clinic_name_full) %>%
@@
 
-with_gps <- facilities_all_gps %>% select(facility_ID) %>% unique()
+with_gps <- facilities_all_gps %>% dplyr::select(facility_ID) %>% unique()
 with_gps <- as.vector(with_gps$facility_ID)
@@
   rename(clinic_name = clinic_nam) %>%
-  select(clinic_name, clinic_typ,	region_nam,	district_n, Latitude, Longitude) %>%
+  dplyr::select(clinic_name, clinic_typ,	region_nam,	district_n, Latitude, Longitude) %>%
   unique() %>%
@@
   rename(clinic_type = clinic_typ, region_name = region_nam, district_name = district_n) %>%
-  select(clinic_type, clinic_name,  region_name, district_name, latitude, longitude) %>%
+  dplyr::select(clinic_type, clinic_name,  region_name, district_name, latitude, longitude) %>%
   unique() %>%
@@
   filter(location != "") %>%
-  select(!c(source, X1)) %>%
+  dplyr::select(!c(source, X1)) %>%
   separate(location, c("latitude", "longitude"), sep = ',') %>%
@@
            crs = 4326) %>%
-  select(clinic_name, clinic_type, district_name,  geometry) %>%
+  dplyr::select(clinic_name, clinic_type, district_name,  geometry) %>%
   mutate(gps_type = "Search") %>%
@@
   filter(LAT != "" | LONG != "") %>%
-  select(!c(clinic_name_w_type, ID)) %>%
+  dplyr::select(!c(clinic_name_w_type, ID)) %>%
   mutate(longitude = as.numeric(LONG)/1000000,
          latitude = as.numeric(LAT)/1000000) %>%
-  select(!c(LONG, LAT)) %>%
+  dplyr::select(!c(LONG, LAT)) %>%
   unique() %>%
@@
            crs = 4326) %>%
-  select(clinic_name, clinic_type, district_name, commune_name, region_name, geometry) %>%
+  dplyr::select(clinic_name, clinic_type, district_name, commune_name, region_name, geometry) %>%
   mutate(gps_type = "Search") %>%
@@
   rename(source = gps_type) %>%
-  select(!full_name) %>%
+  dplyr::select(!full_name) %>%
   map_clean_arrondis() %>%
@@
   clean_catchment_area() %>%
-  select(clinic_name_clean, region_name, district_name, clinic_type_clean, geometry, source) %>%
+  dplyr::select(clinic_name_clean, region_name, district_name, clinic_type_clean, geometry, source) %>%
   group_by(clinic_name_clean, region_name, district_name, clinic_type_clean) %>%
@@
     filter(!facility_ID %in% duplicates) %>%
-    select(facility_ID, geometry, source) %>%
+    dplyr::select(facility_ID, geometry, source) %>%
     inner_join(facilities_all)
@@
                                               sep = "/")) %>%
-  select(!c(Longitude, Latitude, Longitude_search, Latitude_search, Source)) %>%
+  dplyr::select(!c(Longitude, Latitude, Longitude_search, Latitude_search, Source)) %>%
   rename(clinic_name = "Clinic name",
@@
 # facilities_sample <- facilities_sample %>%
-#   select(clinic_name_full,  region_name, district_name, commune_name, geometry) %>%
+#   dplyr::select(clinic_name_full,  region_name, district_name, commune_name, geometry) %>%
 #   st_as_sf() %>%
@@
 
-  select(!c(district_name, commune_name, clinic_name, clinic_type,
+  dplyr::select(!c(district_name, commune_name, clinic_name, clinic_type,
             clinic_type_clean, source, facility_ID)) %>%
@@
 facilities_sample <- facilities_sample %>%
-  select(clinic_name, region_name, district_name, commune_name,
+  dplyr::select(clinic_name, region_name, district_name, commune_name,
          Latitude, Longitude) %>%
@@
                                               sep = "/")) %>%
-  select(!c(Longitude, Latitude)) %>%
+  dplyr::select(!c(Longitude, Latitude)) %>%
   rename(clinic_name = "Clinic name") %>%
@@
          new = paste0(Longitude_search," ", Latitude_search)) %>%
-  # select(!c(Longitude, Latitude, "Longitude, search", "Latitude, search")) %>%
+  # dplyr::select(!c(Longitude, Latitude, "Longitude, search", "Latitude, search")) %>%
   pivot_longer(cols = c("old", "new"), values_to = "geometry", names_to = "type" ) %>%
@@
 
-  select(clinic_name, length) %>%
+  dplyr::select(clinic_name, length) %>%
   arrange(length)
@@
 
-  # region_names_data <- facilities_all %>% select(region_name) %>% unique()
-  # region_names_standard <- map_mdg_1 %>% st_drop_geometry() %>%select(REGION_NAM) %>% unique() %>% arrange(REGION_NAM)
+  # region_names_data <- facilities_all %>% dplyr::select(region_name) %>% unique()
+  # region_names_standard <- map_mdg_1 %>% st_drop_geometry() %>%dplyr::select(REGION_NAM) %>% unique() %>% arrange(REGION_NAM)
   #
@@
 #
-# district_names_data <- facilities_all %>% select(region_name, district_name) %>% unique()  %>% arrange(region_name, district_name) %>%
+# district_names_data <- facilities_all %>% dplyr::select(region_name, district_name) %>% unique()  %>% arrange(region_name, district_name) %>%
 #    filter(!is.na(district_name)) %>% mutate(flag1 = 1)
-# district_names_standard <- map_mdg_2 %>% st_drop_geometry() %>%select(REGION_NAM, DISTRICT_N) %>%
+# district_names_standard <- map_mdg_2 %>% st_drop_geometry() %>%dplyr::select(REGION_NAM, DISTRICT_N) %>%
 #     mutate(DISTRICT_N = case_when(
@@
 
-# commune_names_data <- facilities_all %>% select(region_name, district_name, commune_name) %>% unique()  %>% arrange(region_name, district_name, commune_name) %>%
+# commune_names_data <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique()  %>% arrange(region_name, district_name, commune_name) %>%
 #    filter(!is.na(district_name)) %>% filter(!is.na(commune_name)) %>% mutate(flag1 = 1) %>%
@@
 # 
-# commune_names_standard <- map_mdg_3 %>% st_drop_geometry() %>%select(COMMUNE_NA, REGION_NAM, DISTRICT_N) %>%
+# commune_names_standard <- map_mdg_3 %>% st_drop_geometry() %>%dplyr::select(COMMUNE_NA, REGION_NAM, DISTRICT_N) %>%
 #     mutate(DISTRICT_N = case_when(
@@
 # 
-# perfect_matches <- commune_names_standard %>% select(full_name) 
+# perfect_matches <- commune_names_standard %>% dplyr::select(full_name) 
 # perfect_matches <- perfect_matches$full_name

### 2023-03-02 paper1.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

@@
 The Institutional Review Board (IRB) of the Harvard T.H.
-Chan School of Public Health has determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).
+Chan School of Public Health determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).
 

### 2023-03-02 paper2.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

@@
 library(ggtext)
-library(margins)
+# library(margins)
 library(ncdf4) # package for netcdf manipulation
@@
 
-# map_mdg_0 <- map_mdg_0 %>%
-#   st_as_sf(crs= crsLONGLAT)
+library(elevatr)
+library(rayshader)
+library(raster)
 
@@
 
-# Get the spatial extent of the shapefile
-
   madagascar_bbox <- st_bbox(map_mdg_0_un)
 
-# Get the spatial extent of the PNG image
-madagascar_map_bbox <- c(xmin = 0, ymin = 0, xmax = ncol(madagascar_topo_map), ymax = nrow(madagascar_topo_map))
-
-# Calculate the scaling factor for the x-axis
-x_scale_factor <- diff(madagascar_bbox[c("xmin", "xmax")]) / diff(madagascar_map_bbox[c("xmin", "xmax")])
-
-# Calculate the scaling factor for the y-axis
-y_scale_factor <- diff(madagascar_bbox[c("ymin", "ymax")]) / diff(madagascar_map_bbox[c("ymin", "ymax")])
-
-# Extract minimum and maximum longitude and latitude
-min_lon <- as.numeric(bbox["xmin"])
-max_lon <-  as.numeric(bbox["xmax"])
-min_lat <-  as.numeric(bbox["ymin"])
-max_lat <-  as.numeric(bbox["ymax"])
+# # Get the spatial extent of the PNG image
+# madagascar_map_bbox <- c(xmin = 0, ymin = 0, xmax = ncol(madagascar_topo_map), ymax = nrow(madagascar_topo_map))
+# 
+# 
+# # Calculate the scaling factor for the x-axis
+# x_scale_factor <- diff(madagascar_bbox[c("xmin", "xmax")]) / diff(madagascar_map_bbox[c("xmin", "xmax")])
+# 
+# # Calculate the scaling factor for the y-axis
+# y_scale_factor <- diff(madagascar_bbox[c("ymin", "ymax")]) / diff(madagascar_map_bbox[c("ymin", "ymax")])
+# 
+# 
+# # Extract minimum and maximum longitude and latitude
+# min_lon <- as.numeric(bbox["xmin"])
+# max_lon <-  as.numeric(bbox["xmax"])
+# min_lat <-  as.numeric(bbox["ymin"])
+# max_lat <-  as.numeric(bbox["ymax"])
 
@@
 
-\vspace{12pt}
+\vspace{8pt}
 
@@
 
-\vspace*{\fill}
-
 \emph{Keywords: climate mental health, planetary health, eco-anxiety, climate change, humidity, soil moisture, drought, temperature, cyclones.}
@@
 \end{raggedright}
-
-\newpage
 
@@
 ```
+\newpage
 
@@
 
-  geom_sf(data = map_mdg_3_un,
-          size = 0.2,
-          color = col_grey_light,
-          fill = NA) +
+  # geom_sf(data = map_mdg_3_un,
+  #         size = 0.2,
+  #         color = col_grey_light,
+  #         fill = NA) +
   geom_sf(data = map_mdg_2_un,
@@
   #         fill = NA) +
-  geom_sf(data = map_mdg_2_un,
-          size = 0.2,
-          color = "grey40",
-          fill = NA) +
+  # geom_sf(data = map_mdg_2_un,
+  #         size = 0.2,
+  #         color = "grey40",
+  #         fill = NA) +
   geom_sf(data = map_mdg_1_un,
@@
 \newpage
+
+\begin{spacing}{1.5}
 
@@
 ```
+\end{spacing}{1.5}
 

### 2023-03-02 paper3.Rmd
Revisions to make dplyr::select command run without errors, revisions to Paper 3

--- 2023-02-22 paper3.Rmd
@@
   filter(mh_indicator == 1) %>%
-  select(search)
+  dplyr::select(search)
 
@@
            coefficient_option,
-           lag_option,
+           abstract_option = FALSE,
+           abstract_option_CI = FALSE,
            region_option = "all",
@@
 
-    val <- round((output_df$estimate), 3)
-    p_val <- round(output_df$p_value, 3)
-    low <- round((output_df$lower_99), 3)
-    high <- round((output_df$upper_99), 3)
+    val <- format(round((output_df$estimate), 3), nsmall = 3)
+    p_val <- format(round(output_df$p_value, 3), nsmall = 3)
+    low <- format(round((output_df$lower_99), 3), nsmall = 3)
+    high <- format(round((output_df$upper_99), 3), nsmall = 3)
 
@@
 
+      if(abstract_option == TRUE){
+
+        return(paste0(
+        val,
+        " percentage points",
+        ifelse(coefficient_option == "slope",
+               " per day "," "),
+        "(99\\% ",
+        ifelse(abstract_option_CI == TRUE, "confidence interval (CI): ",
+               "CI: "),
+        low,
+        " to ",
+        high
+        , 
+        "; p ",
+        ifelse(p_val < 0.001,
+               "< 0.0001)",
+               paste0("= ",
+                      p_val,
+                      ")"))))
+
+      }
+
+      else {
       return(paste0(
@@
 
+      }
     }
@@
              color = "",
-             title = ifelse(g == "state", "US states", 
-                            ifelse(g == "county", "US counties",
+             title = ifelse(g == "state", "U.S. states", 
+                            ifelse(g == "county", "U.S. counties",
                                    "International data"))) +
@@
 
-```
-
-The ITS estimates for the immediate (level shift) and sustained (slope change) effects associated with the announcement of vaccine safety and efficacy data on search density for all `r diseases_n` are presented in Figure \ref{figure_all_diseases}.
+paper3_abstract <- paste0("For searches related to depression, we observe a sustained decline in search density of ",
+                          function_dynamic_text_results("main","depression", "slope" , TRUE, TRUE), " and an immediate downward level shift of ",
+                          function_dynamic_text_results("main","depression", "intercept", TRUE),
+                          " relative to comparable symptom searches. For anxiety, we estimated a similar slope change of",
+                          function_dynamic_text_results("main","anxiety", "slope", TRUE), 
+                          " and a level shift of ",
+                          function_dynamic_text_results("main","anxiety", "intercept", TRUE),
+ ".
+We did not observe significant variations across predominately Democrat or Republican voting states and counties, and our findings were robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
+
+```
+
+# The impact of COVID-19 vaccine developments on Google COVID-19 search trends for mental health symptoms: a controlled interrupted time series analysis
+
+\begin{centering}
+
+\emph{Daniel Arias, Jessica Cohen, Karestan Koenen, Margaret McConnell, Stéphane Verguet}
+
+\vspace{24pt}
+
+\noindent\rule{8cm}{0.4pt}
+
+\end{centering}
+
+\begin{raggedright}
+
+\vspace*{\fill}
+
+{\bf Background:} A key obstacle to studying the impact of policies on population mental health in the U.S.
+is a lack of appropriate high frequency surveillance data.
+A potential marker of population mental health is the use of Internet search data, which enables real-time, large-scale analysis of evolving mental health issues.
+
+{\bf Methods:} We utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety in the U.S..
+We examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptoms compared with physical health symptoms, and estimated associations between vaccine announcement and changes in mental health symptom search density.
+We adjusted for state, month, and weekday effects, and applied numerous sensitivity analyses to assess the robustness of our findings.
+To explore heterogeneity by predominate political affiliation, we also tested whether our estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
+
+{\bf Findings and interpretation:} Under our main model specification, we observed reduced search density for depression and anxiety associated with the announcement of vaccine safety data.
+`r paper3_abstract` If symptom search density echoes population health, our results would indicate that announcements regarding the development of safe and effective COVID-19 vaccines led to a robust and sustained improvement in mental health.
+Our findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
+
+\emph{Keywords: mental health; controlled interrupted time series; COVID-19 vaccines; United States; Google searches.}
+
+\end{raggedright}
+
+\newpage
+
+## Introduction
+The COVID-19 pandemic has had a profound effect on the mental health and wellbeing of individuals worldwide.
+Studies from Australia,[@batterhamTrajectoriesDepressionAnxiety2021] China,[@ahmedEpidemicCOVID19China2020; @gaoMentalHealthProblems2020; @hwangLonelinessSocialIsolation; @leiComparisonPrevalenceAssociated2020; @liuPrevalencePredictorsPTSS2020; @qiuNationwideSurveyPsychological2020; @wangImmediatePsychologicalResponses2020; @wangStudyPublicPsychological2021; @wangPsychologicalDistressCoping2020; @zhangImpactCOVID19Pandemic2020] Denmark,[@sonderskovDepressiveStateDenmark] Europe,[@hajekPrevalenceDeterminantsProbable2022] Iran,[@moghanibashi-mansouriehAssessingAnxietyLevel2020] Ireland,[@hylandAnxietyDepressionRepublic2020]  Italy,[@mazzaNationwideSurveyPsychological2020; @mocciaAffectiveTemperamentAttachment2020] Nepal,[@samadarshiOnlineSurveyFactors2020] New Zealand,[@gasteigerDepressionAnxietyStress2021; @lawRiskFactorsChanges2022] Spain,[@gonzalez-sanguinoMentalHealthConsequences2020; @ozamiz-etxebarriaStressAnxietyDepression2020] Turkey[@ozdinLevelsPredictorsAnxiety2020],  the United States,[@jiaNationalStateTrends2021, p.
+2020–2021; @kujawaExposureCOVID19Pandemic2020] and the United Kingdom[@dettmannInvestigatingPrevalenceAnxiety2022] have reported high levels of anxiety (6-51%), depression (15-48%), and post-traumatic stress disorder (7-54%) associated with the onset of the pandemic.
+In the United States, approximately four in ten adults reported experiencing symptoms of anxiety or depression in December 2020—a four-fold increase from January-June 2019.[@panchalImplicationsCOVID19Mental2021, p.
+19] Globally, it has been estimated that the prevalence of depression and anxiety during the COVID-19 pandemic may be as high as 24% and 21%, respectively.[@banko-ferranImpactCOVID19Mental2020; @castaldelli-maiaInvestigatingEffectNational2021] This striking burden has been described as a mental health crisis[@melimopoulosHowCOVID19Pandemic2021] and as a pandemic in its own right.[@kwaiWhatPointYoung2021]
+
+While COVID-19 continues to bring unprecedented challenges to societies around the world, the development and distribution of safe and effective vaccines has fundamentally changed the trajectory of the pandemic.
+Beyond the physical benefits vaccines provide in reducing the risk of infection and associated morbidity and mortality, a growing body of evidence suggests that vaccination has also
+contributed to improved mental health.[@agrawalImpactCOVID19Vaccine2021; @chourpiliadisShorttermImprovementMental2023; @nguyenPsychologicalBenefitsCOVID192021; @rubinsteinEffectCOVID19Vaccinations2023] While there is limited international data on the secondary mental health impact of COVID-19 vaccination, research drawing from the U.S.
+Census Bureau’s Household Pulse Survey has found that benefits of vaccination may include up to a 30% reduction in symptoms of anxiety and depression among vaccinated adults,[@agrawalImpactCOVID19Vaccine2021] while research using the University of Southern California Understanding America Survey suggests a reduction in loneliness associated with greater social interactions following vaccination.[@leeEffectVaccinationSocial2022]
+
+While this literature suggests that receiving a COVID-19 vaccine can improve mental health, the potential mental health benefits of announcements regarding the development of vaccines have received comparatively less attention.[@cotfasLongestMonthAnalyzing2021; @kesselEffectCOVID19Pandemic2023] In the context of a deadly pandemic, the announcement of a safe and effective vaccine could be a powerful signal, providing a psychological boost that the worst might soon be mitigated.
+Studying how population mental health may have been impacted by the release of vaccine efficacy and safety trial data may provide insights into how emotional well-being changed throughout the pandemic in response to these signals, which, in turn, could inform public health communication and contribute to our understanding of how the public responds to information about vaccines—a necessary understanding for increasing vaccine uptake and trust in public health responses.
+
+A key obstacle to studying the impact of public health policies on population mental health, however, is a lack of appropriate high frequency surveillance data.
+A potential marker of population mental health is the use of internet search data, which enables real-time, large-scale analysis of evolving mental health issues.
+A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020] found a strong correlation between search trends for depression and anxiety with indicators of mental health services utilization (reported in the U.S.
+Census Household Pulse Survey) and rates of emergency department visits for mental health conditions (from the U.S.
+Centers for Disease Control and Prevention’s (CDC) National Syndromic Surveillance Program).[@vaidyanathanEvaluationInternetSearches2022] If taken as a reasonable proxy for mental health disorders, search data can provide valuable information on how population mental health reacts to real-time events, enabling policymakers to better respond to mental health needs in a timely manner.
+
+Our study analyzes whether news announcements (in November 2020) regarding the imminent availability of safe and effective COVID-19 vaccines impacted population mental health—even before these vaccines were made available to the public.
+Using Google search density data, we applied interrupted time series approaches to investigate how these announcements might have affected search trends for mental health symptoms in the U.S.
+and five other countries where data were available: Australia, the United Kingdom, Ireland, New Zealand, Singapore.
+Owing to emerging evidence that political ideology may be a predictor of confidence in public health and vaccine hesitancy,[@debusPoliticalIdeologyVaccination2021; @baumgaertnerInfluencePoliticalIdeology2018; @stolerSociopoliticalPsychologicalCorrelates2022] we further explored whether changes in search trends for mental health symptoms varied across U.S.
+states and counties that predominantly voted Democrat vs.
+Republican in the 2020 presidential election.
+Our findings suggest declines in density for searches related to anxiety and depression in all of the countries examined; in the U.S., these declines were found to be consistent irrespective of political ideology.
+
+## Methods
+
+### Data sources
+
+#### Vaccine announcements
+
+We take as our first credible signal of the imminent availability of safe and effective COVID-19 vaccines to be November 16, 2020.
+On November 9^th^, Pzifer announced that early vaccine trial data showed 90% efficacy[@thomasPfizerEarlyData2020] and on the 16^th^, Moderna announced preliminary results showing 95% efficacy.[@gradyEarlyDataShow2020] While U.S.
+Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
+
+#### Symptoms dataset
+
+We accessed aggregated national and subnational data from Google’s COVID-19 Search Trends Symptoms Dataset [@Wahltinez2020] (hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021.
+The symptoms dataset provides time series data of search term density, standardized to pairs of health symptoms and regions (e.g., searches for depression in Australia or fever in Cook County, Illinois) and normalized within each pair based on the symptom’s relative popularity.
+The time series of search density for each symptom-region pair also contains artificial noise, as Google’s differential privacy technique to data aggregation and anonymization adds random noise to protect user privacy (the errors are symmetrically distributed).[@Wahltinez2020]
+
+Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominately English-speaking countries: Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the U.S.
+In the U.S., subnational regions include states and counties.
+Because the aggregated search density data were constructed based on relative search population within each region, we could not compare search density for specific symptoms across different regions; however, comparing search density within regions (or a group of regions) was feasible both over time and across different symptoms.
+
+```{r methods_text_1}
+
+n_states <- data_its_state %>% dplyr::select(state_name) %>% unique() %>% nrow()
+n_counties <- data_its_county %>% dplyr::select(county_fips) %>% unique() %>% nrow()
+
+n_states <- format(n_states - 1, big.mark = ",")
+
+n_counties <- format(n_counties, big.mark = ",")
+
+```
+
+We utilized three levels of region: 1) national level for the six countries; 2) U.S.
+state level data across `r n_states` states and the District of Colombia; and 3) U.S.
+county level across `r n_counties` counties (though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset).
+Following the convention of the symptoms dataset, we will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."
+
+#### Voting dataset
+
+We obtained county-level presidential election results for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we used to calculate aggregate county and state votes (including absentee, early, and election day ballots) for each candidate.
+The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the winning candidate and the runner up).
+Applying a similar approach as other research into COVID-19 and political party inclination,[@grossmannAllStatesClose2021] we used these margins to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth quintile.
+
+\newpage
+
+#### Population data
+
+Population estimates for 2020 by Federal Information Processing Standards (FIPS) code were obtained from the U.S. Department of Agriculture (USDA) Economic Research Service.
+
+### Statistical analysis
+
+All analyses were conducted using R software (version 4.2.1).[@rcoreteamLanguageEnvironmentStatistical2022]
+
+#### Modeling approach
+
+We used an interrupted time series (ITS) approach to model the Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days before the vaccine announcement ($time_0$), $Post_i$ is an indicator variable equal to 1 in the period after the announcement (0 otherwise), $\theta_r$ indicates a series of fixed effects for each region $(r)$, $T^{'}_t\chi$ is a matrix of time fixed effects (i.e., month and day of week), and $\epsilon_{it}$ is an error term.
+$\alpha_d$ can be interpreted as a level change associated with the announcement date—that is, the immediate difference in search density for a disease $d$ following November 19, 2020; $\beta_d$—the slope change—can be interpreted as the sustained change in search density in the days following November 16th.
+
+```{r methods_text}
+
+diseases_n <- format(max(model_outputs_its$model_number), big.mark = ",")  
+mh_diseases_n <- format(length(list_mental_health_symptoms), big.mark = ",")  
+num_models_multiverse = format(max(model_outputs_multiverse$model_number), big.mark = ",")
+
+```
+We apply this model for all available `r diseases_n` diseases with county-level data.
+As search density may rapidly change in response to new announcements, we trimmed the bandwidth of dates to fit our model to 40 days before and after November 16, 2020.
+
+To control for time-varying confounders which may affect symptom search trends, we applied a controlled interrupted time series (CITS) approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
+
+After reviewing the list of symptoms for which search density data were available, we identified the following `r mh_diseases_n` mental health symptoms: `r paste0(gsub("asperger", "Asperger", gsub("_", " ", printList(toPrint = sort(list_mental_health_symptoms), finalSepWord = "and", midSep = ","))),".")`
+
+For each of these symptoms, $d$, we ran the following model:
+
+\begin{spacing}{1}
+
+$$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d mhealth_{di} + 
+\ \ \ \ \ $$
+$$\beta_d time_t*mhealth_{di}  + \delta_{d} Post_i*mhealth_{di} + \gamma_d time_t*Post_i*mhealth_{di} + \theta_g + T^{'}_t\chi +  \epsilon_{it}\ \ \ ,\ \ \ \ \ \ \ \ \ \ (3.2)$$
+\end{spacing}
+
+\vspace{12pt}
+
+where $mhealth_{di}$ equals 1 if the observation is for a mental health symptom $d$ (0 for headaches).
+The estimates of interest are given by $\delta$, which reflects the additional level shift among symptom searches (compared to searches for headaches) after vaccine announcement, and  $\gamma$, the additional relative change in search density over time (i.e., slope change).
+
+Given the high number of observations in our sample, we evaluated significance against an alpha of 0.01, and we constructed 99% confidence intervals (CIs) using heteroskedasticity-robust standard errors.
+
+##### Sensitivity analysis
+
+As with other quasi-experimental methods, it is recommended that the modeling specifications be evaluated using a sensitivity analysis.
+To do so, we defined a list of seven methodological choices concerning data processing and modeling assumptions and interacted these choices to generate all plausible combinations.
+These combinations were then conducted to allow for a multiverse analysis to identify how sensitive effect estimates and CIs were to different methodological choices.
+The criteria used to generate the plausible model combinations are outlined in Table 3.1.
+
+\vspace{12pt}
+
+\begin{raggedright}
+
+```{r table3_1, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table3_1.png")
+
+```
+
+\addcontentsline{lot}{table}{Table 3.1: Alternative specifications, data processing, and modeling decisions for multiverse analysis}
+
+\end{raggedright}
+
+First, we considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, we compared the level of region of aggregated data, using U.S.
+counties, U.S.
+states, and, finally, national trends from the six counties in the sample.
+Third, we evaluated sensitivity to our specification of the bandwidth cut-off around the announcement date, extending it from ±40 days to ±50 and ±60 days.
+Fourth, we toggled whether to account for day of week fixed effects; fifth, we toggled month fixed effects; and sixth, we toggled regional fixed effects (i.e., fixed effects for states in the U.S.
+state level data, fixed effects for counties in the U.S.
+county level data, etc.).
+
+Interacting these choices resulted in 144 plausible models for each symptom.
+Each model was run for all `r mh_diseases_n` mental health related symptoms, resulting in `r num_models_multiverse` models being conducted overall.
+
+##### Subgroup analysis
+
+Two subgroup analyses were conducted to investigate the generalizability of the findings of the main analysis and to explore potential heterogeneities in measures of association.
+
+The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using our nationally aggregated data.
+This analysis aimed to investigate the extent to which effects observed in U.S.
+states and counties were also seen in other countries.
+
+The second subgroup analysis applied the CITS approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share.
+Our subgroup analysis comparing CITS effect estimates in blue vs.
+red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
+
+### Ethics statement
+
+The Institutional Review Board (IRB) of the Harvard T.H.
+Chan School of Public Health determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).
+
+## Results
+
+The estimates for the immediate (level shift) and sustained (slope change) effects associated with the announcement of vaccine safety and efficacy data on search density for all `r diseases_n` are presented in Figure \ref{figure_all_diseases}.
 
@@
 
-```{r figure_all_diseases, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 6, fig.height = 4.5, fig.align='center', out.width = '95%',  fig.scap="Interrupted time series (ITS) effect estimates and confidence intervals by symptom.", out.extra='',  fig.cap="\\label{figure_all_diseases}Interrupted time series (ITS) effect estimates and confidence intervals by symptom.
+```{r figure_all_diseases, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 6, fig.height = 4.5, fig.align='center', out.width = '95%',  fig.scap="Interrupted time series effect estimates and confidence intervals by symptom.", out.extra='',  fig.cap="\\label{figure_all_diseases}Interrupted time series effect estimates and confidence intervals by symptom.
 Effect estimates are presented by points;  for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
@@
                               ifelse(coefficient == "post", "level", "ERROR"))) %>%
-  select(coefficient, estimate, lower_95, upper_95, disease, p_value) %>%
+  dplyr::select(coefficient, estimate, lower_95, upper_95, disease, p_value) %>%
   pivot_wider(names_from = coefficient,
@@
                                 col_headache,
-                                col_grey_lightest),
+                                col_grey_light),
                      name = "") +
-  labs(x = "Slope change", y = "Level shift") +
+  labs(x = "Sustained change in search density percentage points over time", y = "Immediate change in search density percentage points") +
   geom_text_repel(data=subset(model_outputs_its_graph, estimate_slope < -0.04 |
@@
 While our ITS analysis provided suggestive evidence that search density for mental health symptoms might have changed in the post-announcement period, it also highlighted that searches may have generally changed across other diseases at the same time.
-Our CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed our ITS analysis, with most conditions showing level and slope changes close to the null.
-For three conditions, our CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")` all showing sustained declines.
-All three of these symptoms had relatively large slope changes in our ITS analysis.
-In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "level")`, a decrease double in magnitude compared to the majority of estimates for other symptoms.
+Our CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed our ITS analysis, with most conditions showing level and slope changes close to 0.
+For three conditions, our CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")`, all showing sustained declines.
+All three symptoms had relatively large slope changes in our ITS analysis.
+In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "intercept")`, a decrease double in magnitude compared to the majority of estimates for other symptoms.
 
@@
 
-```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
+```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='', fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: anxiety in blue and headaches in grey.
-In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
+In the first column, data from U.S.
+states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second column, data from U.S.
+counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
 In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
 Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
-The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
-US: United States."}
+The solid lines show predicted lines of best fit under a basic controlled interrupted time series model (i.e., no fixed effects).
+U.S.: United States."}
 
@@
 ```
-```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
+
+```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: depression in blue and headaches in grey.
-In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
+In the first column, data from U.S.
+states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second column, data from U.S.
+counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
 In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
 Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
-The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
-US: United States."}
+The solid lines show predicted lines of best fit under a basic controlled interrupted time series model (i.e., no fixed effects).
+U.S.: United States."}
 
@@
 
-```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 5.5, fig.height = 6.5, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
+```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: MDD in blue and headaches in grey.
-In the first column, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second column, data from US counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
+In the first column, data from U.S.
+states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second column, data from U.S.
+counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
 In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
 Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
-The solid lines show predicted lines of best fit under a basic controlled interrupted time series (CITS) model (i.e., no fixed effects).
-US: United States."}
+The solid lines show predicted lines of best fit under a basic controlled interrupted time series model (i.e., no fixed effects).
+U.S.: United States."}
 
@@
 ```{r fig_multiverse_analysis_all, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 9.5, fig.align='center', out.width = '95%',  fig.scap="CITS effect estimates and confidence intervals by mental health symptom, all model combinations.", out.extra='',  fig.cap="\\label{fig_multiverse_analysis_all}Controlled interrupted time series effect estimates by mental health related symptom for each model specification combination in multiverse analysis.
-Each point presents the effect estimates of a sinlge model; for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
+Each point presents the effect estimates of a single model; for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
 ADHD: Attention deficit hyperactivity disorder.
@@
                               ifelse(coefficient == "post:trt", "level", "ERROR"))) %>%
-  select(!c(z_score, lower_99, upper_99, standard_error)) %>%
+  dplyr::select(!c(z_score, lower_99, upper_99, standard_error)) %>%
   pivot_wider(names_from = coefficient,
@@
 
-Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates to state level estimates for each CITS estimand, but with much tighter confidence intervals, even when geographic fixed effects and narrower bandwidths were included.
 Slope changes and level shifts for anxiety, depression, and MDD are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}.
-Across all models, the sustained change in search density for anxiety and depression is negative and significant an alpha of 0.01.
+Examining the plausible model combinations of the multiverse analysis for these three  symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates compared to state level estimates, but with much tighter CIs, even when geographic fixed effects and narrower bandwidths were included.
+Across all models, the sustained change in search density for anxiety and depression was negative and significant with an alpha of 0.01.
 In terms of the estimated level shifts, `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models for anxiety (`r round(function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)*100/144,0)`%) had a statistically significant negative change, compared to `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "positive", multiverse_p = 0.01)` models with a positive one.
@@
 
-Turning to our subgroup analysis, we found modest evidence of effect estimates of similar magnitude comparing across nations (Figure \ref{fig_international}).
-Across the most populous countries (Australia, the United Kingdom, and the United States), effect estimates were broadly consistent, with wider confidence intervals than our ITS or CITS main analysis results due to the smaller number of observations.
-Negative level shifts and slope changes were more pronounced in New Zealand compared to other nations; we caution, however, that owing to the construction of the Google search density data being relative to regions, this may be due to differences in seach volume intensity for depression in New Zealand compared to other nations, and not due to a strong effect itself.
+Turning to our subgroup analysis, we found modest evidence of effect estimates of similar magnitude comparing across countries (Figure \ref{fig_international}).
+Across the most populous countries (Australia, the United Kingdom, and the United States), effect estimates were broadly consistent, with wider CIs than our ITS or CITS main analysis results due to the smaller number of observations.
+Negative level shifts and slope changes were more pronounced in New Zealand compared to other countries, while the level shift estimated for searches for depression in Ireland was positive; we caution, however, that owing to the construction of the Google search density data being relative to regions, this may be due to differences in search volume intensity for depression in Ireland and New Zealand compared to other countries, and not due to a strong effect itself.
 
@@
 
-```{r fig_multiverse_analysis,include = TRUE, echo=FALSE, warnings = FALSE,  fig.width = 20, fig.height = 12, fig.align='center', out.width = '99%', fig.scap="Specification curve depicting the CITS effect estimates and confidence intervals for search density", out.extra='',  fig.cap="\\label{fig_multiverse_analysis}Specification curve depicting the CITS effect estimates and confidence intervals for search density, with panel A depicting the estimated slope change and panel B depicting the estimate level shift.
+```{r fig_multiverse_analysis,include = TRUE, echo=FALSE, warnings = FALSE,  fig.width = 20, fig.height = 12, fig.align='center', out.width = '99%', fig.scap="Specification curve depicting the CITS effect estimates and confidence intervals for search density", out.extra='',  fig.cap="\\label{fig_multiverse_analysis}Specification curve depicting the CITS effect estimates and confidence intervals for search density, with panel A depicting the estimated slope change and panel B depicting the estimated level shift.
 Within each panel, the effect estimates across different models are depicted as circles in the upper graph; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
@@
 From left to right, these are anxiety, depression, and major depressive disorder.
-FE: fixed effects.
 CITS: controlled interrupted time series.
-FE: fixed effects.
-CITS: controlled interrupted time series."}
+FE: fixed effects."}
 
@@
            geography == "county") %>%
-  select(model_number) %>%
+  dplyr::select(model_number) %>%
   unique()
@@
 
-```{r fig_international, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 6.5, fig.align='center', out.width = '95%',  fig.scap="CITS effect estimates and confidence intervals by mental health symptom, all model combinations.", out.extra='',  fig.cap="\\label{fig_international}Controlled interrupted time series effect estimates by mental health related symptom for each model specification combination in multiverse analysis.
-Each point presents the effect estimates of a sinlge model; for each symptom, the estimated slope change per day is shown on the x-axis, while the level shift over the post-announcement period is shown on the y-axis.
-ADHD: Attention deficit hyperactivity disorder.
-CoC: clouding of consciousness.
-GAD: generalized anxiety disorder.
+```{r fig_international, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 6.5, fig.align='center', out.width = '95%',  fig.scap="International CITS effect estimates and confidence intervals by mental health symptom.", out.extra='',  fig.cap="\\label{fig_international}Controlled interrupted time series estimates of changes in search density by mental health related symptom, reported across six countries (Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States).
+The top panel reports estimates of associated level shift and the lower panel estimates of the associated slope change.
+Estimates are represented as solid black lines, with the shaded regions above and below the lines showing the 95\\% confidence intervals.
+The solid black line across all panels reflects a null effect.
 MDD: Major depressive disorder."}
@@
     text = element_text(family = "Source Sans Pro")) +
-  labs(y = "Estimate", x = "", fill = "Nation") +
+  labs(y = "Estimate", x = "", fill = "Country") +
   scale_fill_viridis(discrete = TRUE, option = "C", direction = -1) + 
@@
 Results from our analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and MDD as found in our main analysis (Figure \ref{fig_political}).
-This was particular observed in our analysis of U.S.
+This was particularly observed in our analysis of U.S.
 state-level data, where confidence intervals for the CITS effect estimates were statistically equivalent across red and blue states.
@@
 
-```{r fig_political, include = TRUE, echo=FALSE, warnings = FALSE,fig.scap="CITS effect estimates and confidence intervals symptom, region, and predominant political ideology.", out.extra='', fig.width = 10, fig.height = 5, fig.align='center', out.width = '95%',  fig.cap="\\label{fig_political}CITS effect estimates and confidence intervals symptom, region, and predominant political ideology, with panel A depicting the estimated slope change and panel B depicting the estimate level shift.
-The vertical panels show CITS effect estimates by three mental health symptoms (from left to right: anxiety, depression, and major depressive disorder); for each symptom, estimates are separately reported using county- and state-level data.
+```{r fig_political, include = TRUE, echo=FALSE, warnings = FALSE,fig.scap="CITS effect estimates and confidence intervals per symptom, region, and predominant political ideology.", out.extra='', fig.width = 10, fig.height = 5, fig.align='center', out.width = '95%', fig.cap="\\label{fig_political}CITS effect estimates and confidence intervals per symptom, region, and predominant political ideology.
+Panel A depicts the estimated slope change and panel B the estimated level shift.
+The vertical panels show CITS effect estimates by mental health symptom (from left to right: anxiety, depression, and major depressive disorder); for each symptom, estimates are separately reported using county- and state-level data.
 For a given symptom and region, three CITS estimates are reported: one estimated from a sample of all counties or states (shown in purple), one conducted solely among the most Democratic counties or states (by 2020 presidential election vote share, shown in blue, and one among the most Republican counties or states (shown in red).
@@
 CITS: controlled interrupted time series.
-US: United States."}
+U.S.: United States."}
 
@@
   function_clean_diseases() %>%
-  mutate(geography = ifelse(geography == "state", "US states", "US counties")) %>%
+  mutate(geography = ifelse(geography == "state", "U.S. states", "U.S. counties")) %>%
   mutate(polity = ifelse(polity == 1, "Red states/counties (top 20% most Republican", 
@@
 
-* Shows that event the announcement of a safe and effective vaccine led to a significant shift in searches.
-If searches are taken as a reasonable proxy of mental health status, the period following the announcement saw both a sharp decline in depression and anxiety
-
-* Lack of heterogeneity by polity is interesting, given evidence that polity is a strong predictor of attitudes towards COVID-19 vaccination.
-Also makes bias from an uncommon shock (e.g., 2020 election) less likely to explain the results
-
-```{r todolist}
+This study evaluated whether two contemporary announcements of COVID-19 vaccine safety and efficacy data on November 9th and November 16^th^, 2020 were associated with changes in health-related Google search density related to mental health symptoms.
+Using search data from U.S.
+counties, states, and international trends, we applied ITS and CITS modeling approaches to investigate possible associations between these announcements and search density changes.
+We found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
+The declines were relatively large compared to changes in other symptoms, both physical and mental, and a multiverse analysis indicated that our findings were robust to alternative specifications.
+
+To interpret these observed changes as reactions to the vaccine safety and efficacy announcements, it is important to evaluate whether they may be responses to other contemporary events.
+We highlight two potential alternatives that coincided with the period under study: the 2020 U.S.
+general election on November 3^rd^ and the observance of the Thanksgiving holiday in the United States on November 26^th^.
+While it is possible that our estimates encompass impacts from these events, data from our subgroup analysis lends support for our interpretation that these alternatives are insufficient to explain the observed declines in search trends for anxiety, depression, and MDD.
+
+With respect to the U.S.
+general election, we would anticipate any post-election decline in mental health related symptoms to be concentrated in the United States, given its domestic importance and the political fervor that surrounded it.
+Similarly, we would expect that impacts of the Thanksgiving holiday would be unique to the U.S., as it is not celebrated by the other nations in the sample and there were no other national holidays observed by those nations at the same time (with the exception of Singapore’s observance of Deepavali on November 14^th^).
+
+In our subgroup analysis comparing Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, we did not observe evidence of U.S.-specific effects, with our analysis showing consistent declines in searches related to anxiety and depression (though these differed in degree).
+Furthermore, the estimated declines in search density in Australia and the United Kingdom—which, along with the U.S., are the most populous nations in the sample—were greater than that of the U.S.
+for these two symptom searches, providing additional counterevidence to these alternative explanations.
+
+Further countering the explanation that observed declines in search trends for mental health symptoms were due to the U.S.
+general election are the results from our subgroup analysis comparing blue and red states/counties.
+If voters expressed relief following the election if their candidate was the winner, a greater decline in searches related to anxiety and depression in states and counties would be expected in those that more heavily voted for Joe Biden, the Democratic candidate and subsequent President-elect, than for former President Donald Trump, the Republican candidate.
+This gradient would also echo our hypothesis that, given findings that political ideology may affect receptiveness to vaccination, the announcement of vaccine safety and efficacy would have had a less pronounced effect among Republican vs.
+Democratic voters compared to liberal ones.
+Instead, we observed the opposite: among the counties that most heavily voted for the Republican candidate, the estimated declines in search density for anxiety and depression were larger than in those that most heavily voted Democrat.
+We did, however, observe broad similarities in the confidence intervals of these estimates, such that we did not rule out the possibility that the effects were the same across red and blue counties.
+However, even this finding would be striking, giving the enduring political controversy over vaccination in the U.S.; while subsequent attitudes towards vaccination may show an ideological split by political affiliation, our findings—if taken as a reasonable reflection of individual attitudes—suggest that whatever relief the vaccine announcements brought was shared across the aisle.
+
+Our findings should be interpreted with some limitation in mind.
+First, the aggregated and anonymized nature of our data imposes a constraint to our interpretations, as we are unable to identify whether individual political ideologies were correlated with changes in search trends.
+Instead, we relied on population aggregates that reflect political orientation (i.e., vote share by county and state) as a proxy, focusing on the 20% most Democrat and Republican-voting areas to strengthen the plausibility of this proxy.
+In addition, we highlighted that the use of Google search density as a proxy for population mental health could not be directly validated in our study, as the search data was anonymized and aggregated.
+While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and U.S.
+population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective wellbeing and care seeking.
+
+Despite these limitations, our findings suggest that the announcement of COVID-19 vaccine safety and efficacy led to a robust and sustained reduction in Google search density for anxiety and depression, relative to search density prior to the announcements and to searches for other symptoms.
+If symptom search density echoes population health, our results would indicate that these announcements led to an improvement in mental health, an improvement observed across countries and predominant political party inclination.
+Our findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
+
+```{r todolist_PAPER3}
 
@@
 # Make tables
-# Run international comparison models
-# Generate in text formulas
-
-```
+
+```

### 2023-03-02 thesis.Rmd
Adding rayshader to Madagascar maps
Revisions to make dplyr::select command run without errors, revisions to Paper 3

@@
     # pandoc_args: ['--lua-filter=multibib.lua']
+  # pdf_document:
+    # pandoc_args: !expr acronymsdown::add_filter()
+    # number_sections: TRUE
 
@@
 
-{\ Daniel Arias}
+{\ Daniel Alejandro Arias}
 
@@
 
-Imperdiet sed euismod nisi porta lorem mollis aliquam.
-Eget lorem dolor sed viverra ipsum nunc aliquet bibendum enim.
-Eget lorem dolor sed viverra.
-Vitae proin sagittis nisl rhoncus mattis.
-Mi sit amet mauris commodo quis imperdiet massa tincidunt.
-Quis auctor elit sed vulputate mi.
-Augue eget arcu dictum varius duis at consectetur lorem.
-Commodo elit at imperdiet dui accumsan sit amet.
-Consequat semper viverra nam libero justo laoreet sit.
-Quis hendrerit dolor magna eget est lorem ipsum.
-Eget arcu dictum varius duis at consectetur lorem.
-Fermentum posuere urna nec tincidunt praesent semper feugiat.
-Integer quis auctor elit sed vulputate mi sit amet.
-Ultricies integer quis auctor elit.
-Metus vulputate eu scelerisque felis imperdiet proin fermentum.
-Ut porttitor leo a diam sollicitudin tempor id eu nisl.
-Cras adipiscing enim eu turpis egestas.
-Cursus euismod quis viverra nibh cras pulvinar mattis nunc sed.[@vaidyanathanEvaluationInternetSearches2022]
+We take as our first credible signal of the imminent availability of multiple safe and effective COVID-19 vaccines to be November 16, 2020.
+On November 9^th^, Pzifer announced than early vaccine trial data showed 90% efficacy;[@thomasPfizerEarlyData2020] on the 16^th^, Moderna similarly announced preliminary results showing 94.5% efficacy for their vaccine.[@gradyEarlyDataShow2020] While U.S.
+Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
 

### 2023-03-04 conclusion.Rmd
Revisions throughout to all chapters, introduction, conclusion.

@@
 
+The magnitude of this burden has galvanized a global movement and a call to action for greater investment and prioritization for mental health.[@patelRenewedAgendaGlobal2011] This movement has emphasized the importance of investing in mental health as a means of promoting sustainable development, human rights, and social inclusion.[@patelLancetCommissionGlobal2018]
+
 Burden may be larger than traditionally conceptualized

### 2023-03-04 intro.Rmd
Revisions throughout to all chapters, introduction, conclusion.

@@
 
-Overview of the global burden of mental health
+Mental health is an essential part of human flourishing.
+As defined by the World Health Organization (WHO), it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community”.[@worldhealthorganizationComprehensiveMentalHealth2013]
 
-Cite key literature – systematic reviews, Lancet series, Vikram’s work, DC3P findings, Walker et al.
-EMERALD health systems & mental health study, Mental Health Atlas from WHO, GBD for estimates of burden
+For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are a leading cause of disability,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] with the Global Burden of Disease (GBD) 2019 study estimating that 4.9% of disability-adjusted life years (DALYs) and 14.6% of years lived with disability (YLDs) are attributable to mental disorders.[@vosGlobalBurden3692020a] Mental disorders are closely linked to physical health, and can be a significant risk factor for premature mortality.[@walkerMortalityMentalDisorders2015] Among patients living with the most severe mental illnesses, premature mortality may reduce life expectancy by as much as 10 to 20 years.[@demooijDyingTooSoon2019]
 
-Implications of this global burden for health systems
+At all levels of sociodemographic development, this burden of morbidity and mortality is rising.[@patelLancetCommissionGlobal2018] Yet despite this global scale and despite a growing evidence base for impactful, cost-effective interventions that may help,[@patelMentalNeurologicalSubstance2016] the profound impact of mental disorders has been met by a profound treatment gap.[@demyttenaerePrevalenceSeverityUnmet2004] The majority of people living with a mental disorder do not have access to adequate care,[@bassUnitedNationsGeneral2012a; @demyttenaerePrevalenceSeverityUnmet2004] and many face stigma,[@alonsoPerceivedStigmaIndividuals2009; @angermeyerStigmaMentalIllness2003] discrimination,[@stuartMentalIllnessEmployment2006; @thornicroftDiscriminationHealthCare2007] and abuse.[@humanrightswatchDeathSentenceAbuses2012; @mfoafo-mcarthyHumanRightsViolations2014; @rahmanMentalDistressHuman2021]
 
-Highlight interconnectedness of mental health and physical health
+In addition to the long-standing challenges of these unmet needs, new and emerging dangers such as climate change and COVID-19 reveal additional stressors that threaten to exacerbate this burden.
+Global climate change—an accelerating existential threat to planetary health that the United Nations considers the “defining crisis of our time”—is already manifesting profound impacts on mental health.[@worldhealthorganizationMentalHealthClimate2022] The impacts are shaped both by the disastrous upheaval caused by worsening extreme weather events and by the incremental change rising temperatures and sea levels have wrought on livelihoods and means of living—altering the availability and access to natural resources, land use, infrastructure, and community.[@atwoliMentalHealthClimate2022; @hayesClimateChangeMental2018] This essential connections between mental health and human wellbeing have been further underscored by the devastating impacts of the COVID-19 pandemic, which continues to deal psychological and psychiatric harm to patients, health care workers, and the public overall.[@vindegaardCOVID19PandemicMental2020]
 
-Links of mental health to financial risk protection / vulnerabilities to poverty
+The extant and evolving challenges of global mental health, in turn, entail jeopardy to health systems and to the three intrinsic goals of improving health, responsiveness, and financial protection.
+According to the WHO’s Mental Health Atlas report from 2020, mental health system governance, capacity, and integration into routine service delivery is fundamentally lacking across nations of all levels of economic development, with only 15% of countries having functional integration of mental health into primary health care.[@worldhealthorganizationMentalHealthAtlas2021] This lack of service delivery echoes a lack of basic epidemiological data,[@steinCrossnationalEpidemiologySocial2017] constraining researching and frustrating efforts to respond to mental health needs.
+Among nations, the Atlas report highlights widening disparities in health system indicators, with worsened gaps in service availability and public health expenditure for mental health between low- and middle-income countries and high-income peers.
+With respect to health spending in many countries, mental health care services have relied primarily or exclusively on out-of-pocket payments,[@dixonFinancingMentalHealth2006] resulting in a greater risk of catastrophic health expenditure among households with patients living with a mental disorder.
+These direct costs, when coupled with the indirect costs of diminished due to disability, may exacerbate conditions of poverty, [@patelPovertyCommonMental2003] which, in turn, may lead to worsening mental health[@lundPovertyCommonMental2010]—exacerbating a vicious cycle that harms households and nations alike.
 
-Underscore under-investment in mental health systems, coupled with lack of data on mental health, which constrains research and policy
+A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequence to strengthening of health system responses to mental disorders and improving health outcomes for millions of individuals worldwide.
+Contributing to such an understanding has motivated this dissertation, which takes as its focus different quantitative aspects of the global burden of mental illness—how we measure and evaluate it, how it may be changing, and how novel data sources may help in characterizing it, particularly in the absence of robust, high-frequency epidemiological surveillance.
+The papers presented in the subsequent three chapters echo the interdisciplinary nature of global mental health, drawing on a broad range of quantitative methods and applying analytic tools and insights from epidemiology, health economics, and econometrics.
 
-Also note that mental health is a truly global issue, impacting HICs and LMICs alike
+In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value.
+We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available GBD data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in the year 2019.
+Using value of statistical life approaches, we estimated that the economic value of this mental health burden would exceed 4.7 trillion USD.
 
-Overview of Paper 1
+In Chapter 2, we investigated how health system visits for mental disorders in Madagascar may be shifting in respond to changes in climate.
+Madagascar has little to no mental health surveillance data and is among the nations most vulnerable to climate change.
+To address these gaps, we studied the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms—by leveraging meteorologic, geospatial, and health system data reported by 3,413 facilities in Madagascar from 2010 to 2020.
+We found a statistically significant reduction in monthly cases reported associated with temperature, primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
+We further found that higher soil moisture may be associated with higher case counts in the future, after a three month lag; this increase was primarily found in the eastern lowlands and the northern dry deciduous forests, consistent with the geographic concentration of flood risk in Madagascar.
+Our findings point to suggest potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.
 
-Overview of Paper 2
+In Chapter 3, we investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic.
+Using search data from U.S.
+counties, states, and international trends, we explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms.
+We found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
+The findings underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.
 
-Overview of Paper 3
+Overall, these three chapters highlight different facets of the global burden of mental disorders and speak to the interconnectedness of mental health and human well-being, as well as the urgent need for greater research and resources to better illuminate such pathways.
+Taken together, they contribute to a growing effort to generate a more comprehensive understanding of the challenges posed by this burden—as well as opportunities for improving mental health at local, regional, and global levels.

### 2023-03-04 paper1.Rmd
Revisions throughout to all chapters, introduction, conclusion.

@@
 
-Mental health is an essential part of human flourishing.
-As defined by the World Health Organization (WHO), it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community.[@worldhealthorganizationComprehensiveMentalHealth2013]” For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are both leading causes of disability and significant risk factors for premature mortality.[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] At all levels of sociodemographic development, this burden of morbidity and mortality is rising.[@patelLancetCommissionGlobal2018] Furthermore, as the COVID-19 pandemic continues, there is growing and alarming evidence of its detrimental psychological and psychiatric effects—for patients, health care workers, and the public overall.[@vindegaardCOVID19PandemicMental2020]
-
-The magnitude of disability caused by mental disorders has galvanized a global movement and a call to action for greater investment and prioritization for mental health.[@patelRenewedAgendaGlobal2011] This movement has emphasized the importance of investing in mental health as a means of promoting sustainable development, human rights, and social inclusion.[@patelLancetCommissionGlobal2018]
-
-A critical link between mental health and development arises from the economic consequences of mental disorders.
 A growing body of literature suggests that mental disorders are costly, both in the direct medical costs of care, outpatient visits, and hospitalizations, and in indirect costs, such as losses in income and productivity due to disability, which may cause absenteeism and presenteeism.[@trautmannEconomicCostsMental2016] These costs further worsen conditions of poverty[@patelPovertyCommonMental2003]—a vulnerability that, in turn, worsens mental health, feeding a vicious cycle of poverty and illness.[@lundPovertyCommonMental2010] At the national level, mental disorders deplete the supply of labor and capital, resulting in poorer economic output.[@canavanPsychologicalDistressGhana2013] Among households and nations alike, the burden of mental illness thus has considerable economic consequences and poses a challenge to both health and wealth.
 
-Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This study used three distinct approaches to quantify the economic burden of non-communicable diseases (NCDs), including mental illnesses.[@bloomGlobalEconomicBurden2011] The first is a cost-of-illness (COI) analysis, which includes the direct costs of illness as well as the indirect costs (e.g., lost productivity).
-The second is a value of lost output approach, which estimates the effects of illness on gross domestic product (GDP) due to the depletion of labor and capital.
-The third builds from value of a statistical life (VSL) approaches and attempts to capture a population’s willingness to pay to reduce morbidity and mortality associated with illness.
-This expands on the COI and value of lost output approaches, as it puts an economic value on the loss of health itself.
-
-With a third of disability-adjusted life years (DALYs) due to NCDs arising from mental disorders, this landmark paper estimated that the value of losses due to mental disorders was roughly 1.3 trillion USD in 2010 (1.6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion USD 2010 (or approximately 3.0 trillion USD in 2019) by 2030.
+Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This landmark paper by Bloom and colleagues estimated that the value of losses due to mental disorders was roughly 1.3 trillion USD in 2010 (1.6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion USD 2010 (or approximately 3.0 trillion USD in 2019) by 2030.
 (See Tables S1.1 and S1.2 in Appendix 1 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]
@@
 Inclusion of premature mortality through the PAF presents a novel composite approach that can more broadly capture attributable morbidity and mortality.
-Using this approach on GBD 2019 estimates, we then apply monetary values to DALYs to reach estimates of the global economic value of the mental burden of disease using a VSL approach.
-The VSL approach—in contrast to COI and VLO approaches—includes an economic valuation of mortality risk reductions in monetary terms, and thus enables comparison across sectors (beyond the sole health sector) which can motivate decision-making toward ameliorating welfare and societal mental health.
+Using this approach on GBD 2019 estimates, we then apply monetary values to DALYs to reach estimates of the global economic value of the mental burden of disease using a value of a statistical life (VSL) approach similar to that of Bloom and colleagues,[@bloomGlobalEconomicBurden2011] which attempts to capture a population’s willingness to pay to reduce morbidity and mortality associated with illness.
+The VSL approach—in contrast alternatives such as cost of illness and value of lost output approaches—includes an economic valuation of mortality risk reductions in monetary terms, and thus enables comparison across sectors (beyond the sole health sector) which can motivate decision-making toward ameliorating welfare and societal mental health.
 Our findings suggest that both the epidemiological and economic burden of mental disorders could be larger than previously estimated, and that underestimation would be larger among regions where premature mortality due to mental disorders is greater.
@@
     ggplot(aes(geometry = geometry, fill = var_cut)) +
-    geom_sf(color = col_grey_dark, linewidth = 0.25) +
+    geom_sf(color = col_grey_dark, linewidth = 0.15) +
     scale_fill_manual(values=setNames(lancet_pal, levels(data_temp$var_cut))) +
@@
                                      lower_block_3_5,
-                                     rel_heights  = c(0.99,
+                                     rel_heights  = c(1,
                                                       0.8,
@@
                                      rel_widths = c(3.32,
-                                                    3.22,
+                                                    3.24,
                                                     2,
@@
 First, our estimation approaches themselves all draw upon modeled data (i.e., GBD estimates).
-While GBD generates descriptions of morbidity and mortality at fine demographic and geographic levels, it is important to emphasize that the sophisticated modeling approaches implemented often draw on (potentially little) available underlying empirical data.[@tichenorMetricPartnershipsGlobal2020] These inputs can be extremely limited for particular diseases and geographical locations, especially so for mental disorders.
+While GBD generates descriptions of morbidity and mortality at fine demographic and geographic levels, it is important to emphasize that the sophisticated modeling approaches implemented often draw on (potentially little) available underlying empirical data.[@tichenorMetricPartnershipsGlobal2019] These inputs can be extremely limited for particular diseases and geographical locations, especially so for mental disorders.
 By way of example, the GBD 2019 Data Input Sources Tool retrieves 3,084 separate data sources for mental disorders.

### 2023-03-04 paper2.Rmd
Revisions throughout to all chapters, introduction, conclusion.

@@
 library(elevatr)
-library(raster)
 library(rayshader)
@@
 
+detach("package:raster", unload=TRUE)
+
 ```
@@
 
-\vspace{8pt}
+\vspace{24pt}
 
@@
 We then obtained gridded temperature and soil moisture data from the European ReAnalysis (ERA5)[@copernicusclimatechangeservicec3sFifthGenerationECMWF2017] and the European Space Agency’s Climate Change Initiative (ESA CCI),[@europeanspaceagencyEuropeanSpaceAgency2022] respectively.
-Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@SouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the National Oceanic and Atmospheric Administration (NOAA)[@InternationalBestTrack2021] for accuracy.
+Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@wikipediaSouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the National Oceanic and Atmospheric Administration (NOAA)[@InternationalBestTrack2021] for accuracy.
 
@@
 Madagascar’s health information system provided facility-level data on counts of disease incidence summarized and reported monthly.
-Prior to 2019, this system was the Gestion du Système d'Information Sanitaire (GESIS); in early 2019, the system transitioned to using District Health Information Software 2 (DHIS2).
+Prior to 2019, this system was the Gestion du Système d'Information Sanitaire (GESIS); in early 2019, the system transitioned to using District Health Information Software 2 (DHIS2).[@measureevaluationStrengtheningHealthInformation2019]
 
@@
 
-ERA 5 is a global atmospheric reanalysis from the European Centre for Medium-Range Weather Forecasts (ECMWF) and is freely available through its Copernicus Climate Change Service (C3S)@europeanspaceagencyEuropeanSpaceAgency2022.
-The spatial resolution of ERA 5 is approximately 30 km, with quality-assured hourly estimates available from 1959 to the present  @europeanspaceagencyEuropeanSpaceAgency2022.
-Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation  @ERA5MonthlyAggregates2022.
-Temperature data was then converted to degrees Celsius.
+ERA 5 is a global atmospheric reanalysis from the European Centre for Medium-Range Weather Forecasts (ECMWF) and is freely available through its Copernicus Climate Change Service (C3S)[@europeanspaceagencyEuropeanSpaceAgency2022].
+The spatial resolution of ERA 5 is approximately 30 km, with quality-assured hourly estimates available from 1959 to the present.[@europeanspaceagencyEuropeanSpaceAgency2022] Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation  [@googleearthengineERA5MonthlyAggregates2022] Temperature data was then converted to degrees Celsius.
 
@@
 Open source data on tropical cyclones in the south-west Indian Ocean was obtained by scraping information from Wikipedia summaries of each cyclone season, which were originally sourced from alerts issued by Météo-France La Réunion (MFR La Réunion), the World Meteorological Organisation designated Regional Specialized Meteorological Centre (RSMC) for the provision of forecasts and warnings of tropical cyclones in the South-West Indian Ocean.
-To ensure that the compiled data accurately reflected storms in Madagascar during the study period, we cross-referenced these data against storm trajectory data for the South Indian Basin from NOAA.[@InternationalBestTrack2021]
+To ensure that the compiled data accurately reflected storms in Madagascar during the study period, we cross-referenced these data against storm trajectory data for the South Indian Basin from NOAA.[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021]
 
@@
 ### Author contributions
-<!-- For future versions: All authors contributed to critical revision of the manuscript, with responses to reviewers and subsequent revisions led by DA.  -->
-
-All authors contributed to study conception, methodology, and interpretation.
-DA oversaw data acquisition, programming, formal analysis, visualization, and the first draft of the manuscript.
+<!-- For future versions: All authors contributed to critical revision of the manuscript, with responses to reviewers and subsequent revisions led by DA.
 All authors had access to and verified all the data and accept responsibility for the decision to submit for publication.
+-->
+
+All authors contributed to study conception, methodology, and interpretation. DA oversaw data acquisition, programming, formal analysis, visualization, and the first draft of the manuscript.
 

### 2023-03-04 paper3.Rmd
Revisions throughout to all chapters, introduction, conclusion.

@@
 
-\emph{Daniel Arias, Jessica Cohen, Karestan Koenen, Margaret McConnell, Stéphane Verguet}
+\emph{Daniel Arias, Jessica Cohen, Margaret McConnell, Stéphane Verguet}
 
@@
 Applying a similar approach as other research into COVID-19 and political party inclination,[@grossmannAllStatesClose2021] we used these margins to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth quintile.
-
-\newpage
 
@@
 
+## Acknowledgements
+<!-- Update with names of internal reviewers -->
+
+We thank Karestan Koenen for feedback on an earlier version of this paper.
+
+### Author contributions
+<!-- For future versions: All authors contributed to critical revision of the manuscript, with responses to reviewers and subsequent revisions led by DA.  -->
+
+All authors contributed to study conception, methodology, and interpretation. DA oversaw data acquisition, programming, formal analysis, visualization, and the first draft of the manuscript.
+
+### Funding statement
+<!-- Confirm with team -->
+
+This study recieved no funding.
+
+### Declaration of interests
+<!-- Confirm with team  -->
+
+We declare no competing interests.
+
+### Data sharing statement
+<!-- Would be good to provide information on whether the Madagascar mental health data is available  -->
+All codes used for the analysis in this article are available on GitHub (https://github.com/darias5/mh_google_search_trends).
+
 ```{r todolist_PAPER3}

### 2023-03-04 thesis.Rmd
Revisions throughout to all chapters, introduction, conclusion.

@@
     # pandoc_args: ['--lua-filter=multibib.lua']
-  # pdf_document:
+  # word_document:
   #   pandoc_args: !expr acronymsdown::add_filter()
@@
 
-\newpage
+<!-- \newpage -->
 
-```{r conclusion, child='conclusion.Rmd'}
-```
+<!-- ```{r conclusion, child='conclusion.Rmd'} -->
+<!-- ``` -->
 
-\cleardoublepage
+<!-- \cleardoublepage -->
 
-\section*{References}
+<!-- \section*{References} -->
 
-\addcontentsline{toc}{section}{References}
+<!-- \addcontentsline{toc}{section}{References} -->
 
-<div id="refs"></div>
+<!-- <div id="refs"></div> -->
 
-\cleardoublepage
+<!-- \cleardoublepage -->
 
-\section*{Supplementary materials}
+<!-- \section*{Supplementary materials} -->
 
-\addcontentsline{toc}{section}{Supplementary materials}
+<!-- \addcontentsline{toc}{section}{Supplementary materials} -->
 
-```{r appendix_all, child='appendix.Rmd'}
-```
+<!-- ```{r appendix_all, child='appendix.Rmd'} -->
+<!-- ``` -->
 
-\newpage
+<!-- \newpage -->
 

### 2023-03-05 intro.Rmd
New figure for Introduction

@@
 
-At all levels of sociodemographic development, this burden of morbidity and mortality is rising.[@patelLancetCommissionGlobal2018] Yet despite this global scale and despite a growing evidence base for impactful, cost-effective interventions that may help,[@patelMentalNeurologicalSubstance2016] the profound impact of mental disorders has been met by a profound treatment gap.[@demyttenaerePrevalenceSeverityUnmet2004] The majority of people living with a mental disorder do not have access to adequate care,[@bassUnitedNationsGeneral2012a; @demyttenaerePrevalenceSeverityUnmet2004] and many face stigma,[@alonsoPerceivedStigmaIndividuals2009; @angermeyerStigmaMentalIllness2003] discrimination,[@stuartMentalIllnessEmployment2006; @thornicroftDiscriminationHealthCare2007] and abuse.[@humanrightswatchDeathSentenceAbuses2012; @mfoafo-mcarthyHumanRightsViolations2014; @rahmanMentalDistressHuman2021]
+At all levels of sociodemographic development, this burden of morbidity and mortality is rising.[@patelLancetCommissionGlobal2018] Yet despite this global scale and despite a growing evidence base for impactful, cost-effective interventions that may help,[@patelMentalNeurologicalSubstance2016] the profound impact of mental disorders has been met by a profound treatment gap.[@demyttenaerePrevalenceSeverityUnmet2004] The majority of people living with a mental disorder do not have access to adequate care (Figure \ref{figure_service_gap}),[@bassUnitedNationsGeneral2012a; @demyttenaerePrevalenceSeverityUnmet2004] and many face stigma,[@alonsoPerceivedStigmaIndividuals2009; @angermeyerStigmaMentalIllness2003] discrimination,[@stuartMentalIllnessEmployment2006; @thornicroftDiscriminationHealthCare2007] and abuse.[@humanrightswatchDeathSentenceAbuses2012; @mfoafo-mcarthyHumanRightsViolations2014; @rahmanMentalDistressHuman2021]
+
+\blandscape
+
+```{r figure_service_gap, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 11, fig.height = 6.5, fig.align='center', out.width = '97%',  fig.scap="Countries where fewer than 10 psychiastrists per 100,000 capita were working in the health sector, 2013-2017.", out.extra='',  fig.cap="\\label{figure_all_diseases}Countries where fewer than 10 psychiastrists per 100,000 capita were working in the health sector between 2013-2017, average.
+Data from the Globa Health Observator (GHO) of the World Health Organization (WHO)."}
+
+# Loading libraries
+library(readxl)
+library(dplyr)
+library(tidyr)
+library(ggplot2)
+library(RColorBrewer)
+library(sp)
+library(broom)
+library(sf)
+library(scales)
+library(viridis)
+library(data.table)
+library(ggpubr)
+library(lemon)
+library(rnaturalearth)
+library(rnaturalearthdata)
+library(sysfonts)
+library(showtext)
+font_add_google("Source Sans Pro")
+library(gridExtra)
+showtext_auto() 
+showtext_opts(dpi = 300)  
+library(rnaturalearthhires) # install.packages("rnaturalearthhires", repos = "http://packages.ropensci.org", type = "source")
+library(ggtext)
+
+world_map <- ne_countries(scale = "large", returnclass = "sf")
+
+who_gho_data <- read.csv("C:/Users/danie/Dropbox (Harvard University)/Important Files/3.
+PhD/Thesis/3.
+Draft/1.
+RMarkdown/phd_thesis/who_gho_data.csv") %>% rename_with(~ gsub("_working_in_mental_health_sector_.per_100_000_population.", "", .),
+              contains("_working_in_mental_health_sector_.per_100_000_population.")) %>%
+    pivot_longer(cols = -country, 
+               names_to = c("type", "year"), 
+               names_pattern = "(.*)_(.*)",
+               values_to = "value") %>%
+  group_by(country, type) %>%
+  mutate(average = mean(value, na.rm = TRUE)) %>%
+  ungroup() %>%
+  select(average, country, type) %>%
+  unique() %>%
+  filter(type == "psychiatrists")
+
+country <- c("Afghanistan", "Albania", "Angola", "Antigua and Barbuda", "Argentina", "Armenia", "Australia", "Azerbaijan", "Bahrain", "Bangladesh", "Barbados", "Belarus", "Belgium", "Belize", "Bhutan", "Bolivia (Plurinational State of)", "Bosnia and Herzegovina", "Brazil", "Brunei Darussalam", "Bulgaria", "Burkina Faso", "Burundi", "Cambodia", "Canada", "Central African Republic", "Chad", "Chile", "China", "Colombia", "Comoros", "Congo", "Cook Islands", "Costa Rica", "Côte d'Ivoire", "Croatia", "Cuba", "Cyprus", "Czechia", "Dominican Republic", "Ecuador", "Egypt", "El Salvador", "Equatorial Guinea", "Eritrea", "Estonia", "Eswatini", "Ethiopia", "Fiji", "Finland", "France", "Gabon", "Gambia", "Georgia", "Germany", "Ghana", "Greece", "Grenada", "Guatemala", "Guinea", "Guinea-Bissau", "Guyana", "Haiti", "Honduras", "Hungary", "India", "Indonesia", "Iran (Islamic Republic of)", "Iraq", "Israel", "Italy", "Jamaica", "Japan", "Jordan", "Kenya", "Kiribati", "Kyrgyzstan", "Latvia", "Lebanon", "Liberia", "Lithuania", "Luxembourg", "Madagascar", "Malaysia", "Maldives", "Mali", "Marshall Islands", "Mauritania", "Mauritius", "Mexico", "Monaco", "Mongolia", "Montenegro", "Morocco", "Mozambique", "Myanmar", "Namibia", "Nauru", "Nepal", "Netherlands", "New Zealand", "Nicaragua", "Niger", "Norway", "Oman", "Panama", "Peru", "Philippines", "Poland", "Qatar", "Republic of Korea", "Republic of Moldova", "North Macedonia", "Romania", "Russian Federation", "Rwanda", "Saint Kitts and Nevis", "Saint Lucia", "Saint Vincent and the Grenadines", "Samoa", "Sao Tome and Principe", "Saudi Arabia", "Senegal", "Serbia", "Seychelles", "Sierra Leone", "Singapore", "Slovenia", "South Africa", "South Sudan", "Spain", "Sri Lanka", "Sudan", "Suriname", "Sweden", "Switzerland", "Syrian Arab Republic", "Tajikistan", "Thailand", "Timor-Leste", "Togo", "Tonga", "Tunisia", "Türkiye", "Uganda", "Ukraine", "United Arab Emirates", "United Republic of Tanzania", "United States of America", "Uruguay", "Uzbekistan", "Vanuatu", "Yemen", "Zambia", "Zimbabwe")
+
+adm0_a3 <- c("AFG", "ALB", "AGO", "ATG", "ARG", "ARM", "AUS", "AZE", "BHR", "BGD", "BRB", "BLR", "BEL", "BLZ", "BTN", "BOL", "BIH", "BRA", "BRN", "BGR", "BFA", "BDI", "KHM", "CAN", "CAF", "TCD", "CHL", "CHN", "COL", "COM", "COG", "COK", "CRI", "CIV", "HRV", "CUB", "CYP", "CZE", "DOM", "ECU", "EGY", "SLV", "GNQ", "ERI", "EST", "SWZ", "ETH", "FJI", "FIN", "FRA", "GAB", "GMB", "GEO", "DEU", "GHA", "GRC", "GRD", "GTM", "GIN", "GNB", "GUY", "HTI", "HND", "HUN", "IND", "IDN", "IRN", "IRQ", "ISR", "ITA", "JAM", "JPN", "JOR", "KEN", "KIR", "KGZ", "LVA", "LBN", "LBR", "LTU", "LUX", "MDG", "MYS", "MDV", "MLI", "MHL", "MRT", "MUS", "MEX", "MCO", "MNG", "MNE", "MAR", "MOZ", "MMR", "NAM", "NRU", "NPL", "NLD", "NZL", "NIC", "NER", "NOR", "OMN", "PAN", "PER", "PHL", "POL", "QAT", "KOR", "MDA", "MKD", "ROU", "RUS", "RWA", "KNA", "LCA", "VCT", "WSM", "STP", "SAU", "SEN", "SRB", "SYC", "SLE", "SGP", "SVN", "ZAF", "SSD", "ESP", "LKA", "SDN", "SUR", "SWE", "CHE", "SYR", "TJK", "THA", "TLS", "TGO", "TON", "TUN", "TUR", "UGA", "UKR", "ARE", "TZA", "USA", "URY", "UZB", "VUT", "YEM", "ZMB", "ZWE")
+
+iso_crosswalk <- as.data.frame(cbind(country, adm0_a3))
+
+who_gho_data <- who_gho_data %>%
+  inner_join(., iso_crosswalk)
+
+col_light_blue = "deeppink3"
+col_grey = "#CCCCCC"
+col_light_grey = "#F2F2F2"
+
+world_map <- world_map %>%
+  st_as_sf() %>%
+  st_transform(CRS("+proj=robin"))
+
+map <- world_map %>%
+  filter(admin != "Antarctica") %>%
+  full_join(who_gho_data, by = "adm0_a3") %>%
+  mutate(fill = ifelse(average < 10,
+                       "Fewer than 10 psychiatrists per 100,000 capita",
+                       "Others")) %>%
+  mutate(fill = ifelse(is.na(fill), "No data", fill)) %>%
+  mutate(fill = factor(fill, 
+                                   levels = c("Fewer than 10 psychiatrists per 100,000 capita", 
+                                              "Others",
+                                              "No data"))) %>%
+  ggplot(aes(geometry = geometry, fill = fill)) +
+  geom_sf(color = NA) +
+  theme_void() +
+  # labs(title = "Availability of psychiastrists",
+  #      subtitle = " ") +
+  scale_fill_manual(name = "",
+                    values  = c(col_light_blue, col_grey, col_light_grey)) +
+  theme(legend.position = "bottom",
+        legend.justification='center',
+        legend.direction='horizontal',
+        text = element_text(family = "Arial"),
+        # plot.title =element_text(size=18,   
+        #                            face = "bold",
+        #                            hjust = 0),
+        axis.title.x = element_text(color=col_grey, size=10, hjust = 0),
+        plot.caption = element_text(hjust = 0, 
+                                          vjust = 1,
+                                    face = "bold",
+                                    size=10))
+
+data <- world_map %>%
+  filter(admin != "Antarctica") %>%
+  full_join(who_gho_data, by = "adm0_a3") %>%
+  mutate(category = ifelse(average < 10,
+                           "A",
+                           "B")) %>%
+  select(category, pop_est) %>%
+  st_drop_geometry() %>%
+  group_by(category) %>%
+  mutate(count = sum(as.numeric(pop_est), na.rm = TRUE)) %>%
+  select(category, count) %>%
+  ungroup() %>%
+  unique()  %>%
+  mutate(category = ifelse(is.na(category), "B", category)) %>%
+  mutate(category = factor(category, 
+                           levels = c("A", 
+                                      "B"))) %>%
+  arrange(category)
+
+# Compute percentages
+data$fraction <- data$count / sum(data$count)
+
+# Compute the cumulative percentages (top of each rectangle)
+data$ymax <- cumsum(data$fraction)
+
+# Compute the bottom of each rectangle
+data$ymin <- c(0, head(data$ymax, n=-1))
+
+# Make the plot
+circle <- data %>%
+  ggplot(aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=category)) +
+  geom_rect() +
+  # geom_label( x=3.5, aes(y=labelPosition, label=label), size=6) +
+  geom_richtext(aes(x = 0,
+                    y = 0),
+                label = paste0(round(data$fraction[data$category == "A"]*100,0),
+                               "%"),
+                color = "black",  
+                fill = NA,
+                label.color = NA,
+                size = 10 / .pt,
+                hjust = 0.5,
+                vjust = .9) +
+  coord_polar(theta="y") +
+  xlim(c(-1, 4)) +
+  theme_void() +
+  theme(legend.position = "none") +
+  scale_fill_manual(values = c(col_light_blue, col_grey))
+
+text <- ggplot() +
+  theme_void() +
+  xlim(0, Inf) +
+  geom_richtext(aes(x = 0,
+                    y = 0),
+                label = paste0('**',
+                               "of the world's",
+                               "**<br>**",
+                               "population",
+                               ",",
+                               "**<br>",
+                               paste0(round(data$count[data$category == "A"]/1000000000,1),
+                                            " billion")),
+                color = "black",  
+                fill = NA,
+                label.color = NA,
+                size = 12 / .pt,
+                hjust = 0,
+                vjust = 0.5)
+
+circle_text <- cowplot::plot_grid(circle, text, 
+                     ncol = 2,
+                     rel_heights =    c(7,1.3))
+
+# title <- ggplot() +
+#   geom_segment(aes(x = 0, y = 0, xend = .25, yend = 0), linewidth = .9, color = col_grey) +
+#   # annotate("text", x = 0, y = 0, size=12, label = "Average, 2013-2017",
+#   #          hjust = 0, vjust = -0.3,
+#   #          color = "black", fontface = 'bold', family = "Martel") + 
+#   theme_void() +
+#   xlim(0, 0.25) +
+#   ylim(-0.01, 0.04)
+
+# combo <- cowplot::plot_grid(title, circle_text, 
+#                             nrow = 2,
+#                             rel_heights =  c(1.2,3)) 
+#
+
+# ggsave(map,
+#        filename = paste0("gdp_",
+#                          year,
+#                          ".png"),
+#        path = "C:/Users/danie/Dropbox (Harvard University)/Important Files/7. Data Science/mckinsey",
+#        height = 7.5,
+#        width= 12,
+# #        bg = "white")
+# 
+# ggsave(combo,
+#        filename = paste0("gdp_pie_",
+#                          year,
+#                          ".png"),
+#        path = "C:/Users/danie/Dropbox (Harvard University)/Important Files/7. Data Science/mckinsey",
+#        height = 2.05,
+#        width= 2.25,
+#        bg = "white")
+
+final_figure <- cowplot::ggdraw(map) +
+  cowplot::draw_plot(
+    {circle_text}
+
+    ,
+    # The distance along a (0,1) x-axis to draw the left edge of the plot
+    x = 0.05, 
+    # The distance along a (0,1) y-axis to draw the bottom edge of the plot
+    y = 0.20,
+    # The width and height of the plot expressed as proportion of the entire ggdraw object
+    width = 0.225, 
+    height = 0.25)
+
+print(final_figure)
+
+```
+
+\elandscape
 

### 2023-03-11 Arias,-Daniel---Thesis---2023.03.10.Rmd
Revisions throughout and final version for External Reader

---
title: " "		
output:
  pdf_document:
    pandoc_args: !expr acronymsdown::add_filter()
    number_sections: TRUE

  # pdf_document:
  #   pandoc_args: !expr acronymsdown::add_filter()
  #   number_sections: TRUE

reference-section-title: Works Cited

geometry: margin=1in
fontsize: 11pt
indent: true
header-includes:
  - \usepackage{sectsty}
  - \usepackage{setspace}\spacing{2}
  - \usepackage{fancyhdr}
  - \usepackage[utf8]{inputenc}
  - \usepackage[utf8]{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage[nottoc]{tocbibind}
  # - \usepackage{acro}
  # - \usepackage{float}
  # - \usepackage{chapterbib}
  # - \usepackage{lastpage}
  # - \usepackage{dcolumn}
  # - \usepackage[backend=biber,style=authoryear-icomp]{biblatex}
  # - \addbibresource{bibliography.bib}

bibliography: main.bib
# natbiboptions: "numbers"
csl: https://www.zotero.org/styles/the-lancet

  # intro: intro.bib
  # ch1: chapter1.bib
  #

acronyms:
  insert_loa: false
  loa_title: ""

  # loa_title: "List of Acronyms"
  keys:
    - shortname: LMIC
      longname: low and middle income country

---

```{r setup0, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, include = FALSE, echo = TRUE) 
library(acronymsdown)
```

\allsectionsfont{\centering\normalsize}
\subsectionfont{\raggedright}
\subsubsectionfont{\raggedright}

\pagenumbering{roman}
\pagestyle{empty}

\begin{centering}

\vspace*{36pt}

\large

{\bf `r toupper("Quantitative Approaches Towards Evaluating the Global Burden of Mental Illness")`}

\vspace{12pt}

\normalsize

by

\vspace{12pt}

{\ Daniel Alejandro Arias}

\vspace{36pt}

A dissertation submitted to the faculty of \\
the Harvard T.H. Chan School of Public Health\\
in partial fulfillment of the requirements\\
for the degree of \emph{Doctor of Philosophy}\\
in the Department of Global Health and Population

\vspace{42pt}

Harvard University \\
Cambridge, Massachusetts

\vspace{42pt}

`r format(Sys.time(), '%B %Y')`

\end{centering}

\newpage

\vspace*{\fill}
© `r format(Sys.time(), '%Y')` Daniel Arias. All rights reserved.

\newpage

\pagestyle{plain}

\normalsize

\begin{centering}

Dissertation Advisor: Stéphane Verguet \hfill Daniel Arias

\vspace{24 pt}

{\bf `r toupper("Quantitative Approaches Towards Evaluating the Global Burden of Mental Illness")`}

\vspace{12pt}

\section*{Abstract}

\addcontentsline{toc}{section}{Abstract}

\end{centering}

Mental disorders are a leading cause of morbidity and mortality, affecting over one billion people worldwide. This burden, across all levels of socioeconomic development, is rising, yet the majority of people living with a mental disorder do not have access to adequate mental health services, with many facing stigma and high out-of-pocket payments for their care. Moreover, new and emerging dangers such as climate change and the COVID-19 pandemic pose additional stressors that threaten to exacerbate this burden.

This dissertation aims to contribute to a better understanding of the evolving burden and dynamics of global mental health. The three studies it presents take as their focus different quantitative aspects of how the global burden is measured and evaluated, how it may be changing in response to global challenges, and how novel data sources may help in characterizing these changes, particularly in the absence of robust, high-frequency epidemiological surveillance.

In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value. To capture premature mortality due to mental disorders, as well as disability from associated causes, we proposed a composite approach to estimation. Using the most recently available estimates from the Global Burden of Disease study, we found that the burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019. The economic value of this mental health burden was estimated to exceed 4.7 trillion USD using a value of statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.

In Chapter 2, we focused on Madagascar—a low income country that is among the most vulnerable to the health consequences of climate change—and examine how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones. Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities in Madagascar from 2010 to 2020, we conducted an ecological analysis using negative binomial regression.  Our results indicated that warmer temperatures in the cooler central highlands were associated with a decrease in monthly reported visits for mental disorders, while higher soil moisture could lead to an increase in visits, particular in high flood-risk regions and after a three-month lag, indicating potential variation in the impact of climate change on mental health needs and system responses.

In Chapter 3, we investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic. Using an interrupted time series approach with search data from U.S. counties, states, and international trends, we found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for searches related to anxiety and depression. These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

Taken together, these chapters highlight different facets of the global burden of mental disorder and contribute to a growing effort to generate a more comprehensive understanding of the challenges posed by this burden at local, regional, and global levels.

\cleardoublepage

\begin{spacing}{1}

\renewcommand*\contentsname{Table of Contents}

\tableofcontents

\addcontentsline{toc}{section}{Table of Contents}

\newpage

\listoffigures

\newpage

\listoftables

\newpage

\cleardoublepage

\end{spacing}

```{r frontmatter, child='frontmatter.Rmd'}
```

\cleardoublepage

\pagenumbering{arabic}

```{r intro, child='intro.Rmd'}
```

\cleardoublepage

```{r paper1, child='paper1.Rmd'}
```

\cleardoublepage

```{r paper2, child='paper2.Rmd'}
```

\cleardoublepage

```{r paper3, child='paper3.Rmd'}
```

\cleardoublepage

```{r conclusion, child='conclusion.Rmd'}
```

\cleardoublepage

\section*{References}

\addcontentsline{toc}{section}{References}

<div id="refs"></div>

\cleardoublepage

\section*{Supplementary materials}

\addcontentsline{toc}{section}{Supplementary materials}

```{r appendix_all, child='appendix.Rmd'}
```

\newpage

```{r todo}

### TO DO / KNOWN ISSUES

# Acronyms with acronym down
# Separate bibliography for each section
# Numbered figures and tables by section

# Check that sequential articles are represented by a dash
# Table of figures and tables
# Institutional authors need to be fixed in bibliography

```

### 2023-03-11 appendix.Rmd
Revisions throughout and final version for External Reader

@@
 col_CHD <- "coral1"
-col_CHR <- "coral3"
+col_CHR <- "deeppink3"
 col_CSB <- "steelblue2"

### 2023-03-11 appendix_2.1.Rmd
Revisions throughout and final version for External Reader

@@
 
-The health facility data used in our study was obtained from Madagascar's *Gestion du Système d'Information Sanitaire* (GESIS), a Microsoft Access electronic health management information systems database.
-
-While primary, district-level, and regional referral facilities in Madagascar all report monthly case counts of mental disorders in GESIS, case definitions vary across facilities of different levels.
-Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) are only reported among regional referral hospitals and university hospitals; for all other facilities, cases are reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).
-
-Disaggregated data is available by age; among adults, however, disaggregated data for adults ages 25 to 59 and adults 60 years and older has only been reported by primary health facilities since 2015.
-For all other years and all other facilities, these age categories are not separately reported.
-Similarly, data by sex is only reported for primary health facilities since 2015.
-Referrals are reported by primary health facilities and district hospitals.
-
-A summary of the GESIS data availability is provided in Table S2.1.
+The health facility data used in our study were obtained from Madagascar's *Gestion du Système d'Information Sanitaire* (GESIS), a Microsoft Access electronic health management information systems database.
+
+While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in GESIS, case definitions varied across facilities of different levels.
+Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visit by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).
+
+Disaggregated data was available by age; among adults, however, disaggregated data for adults ages 25 to 59 and adults 60 years and older was only reported by primary health facilities after 2015.
+For all other years and all other facilities, these age categories were not separately reported.
+Similarly, data by sex was only reported for primary health facilities after 2015.
+Referrals were reported by primary health facilities and district hospitals.
+
+A summary of GESIS data availability is provided in Table S2.1.
 
@@
 
+\vspace{6 pt}
+
+After compiling the GESIS data, we translated the case definitions from French to English. The translations are provided in Table S2.2.
+
 \vspace{24 pt}
-
-After compiling the GESIS data, we translated the case definitions from French to English. The translations are provided in Table S2.2.
 
@@
 We then conducted exploratory data analysis to gauge data availability by condition, year, and facility level, which are reported in Tables S2.3-5.
-These tables show yearly cumulative cases of mental and neurological disorders, by facility level.
+These tables show yearly cumulative visits for mental and neurological disorders, by facility level.
 
@@
 
-Among district hospitals, reporting of mental disorders has been consistent between 2010 and 2020.
-
-Reporting of mental disorders is most detailed among regional referral hospitals (CHRRs) and university hospitals (CHUs), with case counts reported for `r  prettyNum(n_chu, big.mark = ",", scientific = FALSE)` unique conditions.
+Among district hospitals, reporting of mental disorders was consistent between 2010 and 2020.
+
+Reporting of mental disorders was most detailed among regional referral hospitals (CHRRs) and university hospitals (CHUs), with visit counts reported for `r  prettyNum(n_chu, big.mark = ",", scientific = FALSE)` unique conditions.
 
@@
 
-\addcontentsline{lot}{table}{Table S2.3: Yearly cumulative cases of mental and neurological disorders reported at primary facilities.}
+\addcontentsline{lot}{table}{Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities.}
 
@@
 
-reporting_table(csb_data, "Table S2.3: Yearly cumulative cases of mental and neurological disorders reported at primary facilities")
+reporting_table(csb_data, "Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities")
 
@@
 
-\addcontentsline{lot}{table}{Table S2.4: Yearly cumulative cases of mental and neurological disorders reported at district hospitals.}
+\addcontentsline{lot}{table}{Table S2.4:  Yearly cumulative visits for mental and neurological disorders reported at district hospitals.}
 
@@
 
-reporting_table(chd_data, "Table S2.4: Yearly cumulative cases of mental and neurological disorders reported at district hospitals")
+reporting_table(chd_data, "Table S2.4: Yearly cumulative visits for mental and neurological disorders reported at district hospitals")
 
@@
 
-\addcontentsline{lot}{table}{Table S2.5: Yearly cumulative cases of mental and neurological disorders reported at regional hospitals.}
+\addcontentsline{lot}{table}{Table S2.5: Yearly cumulative visits for mental and neurological disorders reported at regional hospitals.}
 
@@
 
-reporting_table(chu_data, "Table S2.5: Yearly cumulative cases of mental and neurological disorders reported at regional hospitals")
+reporting_table(chu_data, "Table S2.5: Yearly cumulative visits for mental and neurological disorders reported at regional hospitals")
 
@@
 
-To address heterogeneity in reporting across primary, district-level, and regional-level facilities, our analysis constructed a single, summary outcome measure: any mental or neurological disorders reported in a given month by a given facility, irrespective of age and sex.
+To address heterogeneity in reporting across primary, district, and regional facilities, our analysis constructed a single, summary outcome measure: any mental or neurological disorders reported in a given month by a given facility, irrespective of age and sex.
 This outcome measure was constructed by grouping our count data by facility and month-year, and then summing the incidence of mental and neurological disorders reported in GESIS within groups, preventing double counting and the inclusion of referrals in the summary measure.
@@
   theme(legend.position = "none") +
-  labs(x = "Date", y = "Monthly count of cases") +
+  labs(x = "Date", y = "Monthly count of visits") +
   facet_wrap(~clinic_type_clean, nrow = 3) +
@@
 
-Visual inspect of our data showed potential outliers.
-which may have arisen due to data entry mistakes, synchronization errors, and other sources.
+Visual inspect of our data showed potential outliers, which may have arisen due to data entry mistakes, synchronization errors, and other sources.
 To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series.
 The nonparametric Friedman’s super smoother regression estimator [@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation [@hyndmanAutomaticTimeSeries2008].
-By considering outliers on a facility-by-facility basis, the data cleaning approach preserves extreme values that may reflect true variances in incidence (for example, incidences reported by a large, regional reference hospital) while addressing potential errors in data entry.
+By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may habe reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry.
 Interpolated values were coerced to the nearest integer.

### 2023-03-11 appendix_2.2.Rmd
Revisions throughout and final version for External Reader

@@
 n_facilities_name <- data_mh %>% dplyr::select(clinic_name) %>% unique %>% nrow()
-n_facilities <- data_mh %>% unique %>% nrow()
+n_facilities_overall <- data_mh %>% unique %>% nrow()
 
@@
 
-In Madagascar, public health facilities can be broadly classified under four types:
+In Madagascar, public health facilities can broadly be classified under four types:
 
@@
 The sample of health facilities in our study was obtained from health facility data from Madagascar's *Gestion du Système d'Information Sanitaire* (GESIS).
-While the format of outputs from GESIS vary across years and facility type, there are four variables which uniquely identify facilities.
-
-* **Region**: The region of Madagascar that contains the facility's catchment area. All facilities have a value for this variable.
-* **District**: The district of Madagascar (2nd largest administrative unit) that contains the facility's catchment area.
-Only district- and commune-level facilities will have a value for this variable; regional-level hospitals  have an "*NA*" for this variable.
-* **Commune**: The commune of Madagascar (3rd largest unit) that contains the facility's catchment area. District- and regional-level hospitals have an "*NA*" for this variable.
+While the format of outputs from GESIS varied across years and facility type, there were four variables which uniquely identified facilities.
+
+* **Region**: The region of Madagascar that contained the facility's catchment area. All facilities had a value for this variable.
+* **District**: The district of Madagascar (2nd largest administrative unit) that contained the facility's catchment area. Only district- and commune-level facilities had a value for this variable.
+* **Commune**: The commune of Madagascar (3rd largest unit) that contained the facility's catchment area. Only basic health facility had a value for this variable.
 * **FS**: The facility type and name.
-The facility type will typically be identified with an acronym (e.g., CSB2, CHD1, etc.), with the facility name following thereafter.
-The facility name will occasionally be the same as the commune, district, or region that corresponds with the facility's catchment area (e.g., CHRR Alaotra Mangoro).
-Some facilities are named for the village (*fokontany*) that they are located in.
-Other facilities are named for the groups that operate them (e.g., facilities named "EKAR" are operated by the *Eglizy Katôlika Apôstôlika Rômanina*, or the Roman Catholic Church).
+The facility type would typically be identified with an acronym (e.g., CSB2, CHD1, etc.), with the facility name following thereafter.
+The facility name would occasionally be the same as the commune, district, or region that corresponded with the facility's catchment area (e.g., CHRR Alaotra Mangoro).
+Some facilities were named for the village (*fokontany*) that they were located in.
+Other facilities were named for the groups that operated them (e.g., facilities named "EKAR" are operated by the *Eglizy Katôlika Apôstôlika Rômanina*, or the Roman Catholic Church).
 
@@
 
-Using facility name, type, and catchment area to uniquely identify facilities in our sample, we identified `r  prettyNum(n_facilities, big.mark = ",", scientific = FALSE)` unique facilities.
+Using facility name, type, and catchment area to uniquely identify facilities in our sample, we identified `r  prettyNum(n_facilities_overall, big.mark = ",", scientific = FALSE)` unique facilities.
 In order to classify these facilities by type, we extracted the relevant data from the "FS' variable; in doing so, we observed slight orthographic variations in the classification of facilities types (e.g., "CSB 1" vs.
@@
 
-We further standardized region, district, and commune names in our sample against reference shapefiles to address variations in translation (e.g., "Atsimo" and "Sud" being the Malagasy and French words for "South"), abbreviation (e.g., "St." as an abbreviation for "Saint"), transposition (e.g., "Bevoay Beretra" transposed as "Beretra Bevoay"), accent marks (e.g., "Tovòna" vs.
+We standardized region, district, and commune names in our sample against reference shapefiles to address variations in translation (e.g., "Atsimo" and "Sud" being the Malagasy and French words for "South"), abbreviation (e.g., "St." as an abbreviation for "Saint"), transposition (e.g., "Bevoay Beretra" transposed as "Beretra Bevoay"), accent marks (e.g., "Tovòna" vs.
 "Tovona"), spacing (e.g., "AmbalapaisoII" vs.
@@
 This list of facilities was then manually inspected for any remaining duplicates.
-From reviewing this list, we observed that in the Diana region, the regional hospitals named "Hopitaly MANARA-PENITRA" and "Hopitaly Manara-Penitra Antsiranana" are duplicates, but appear separately because the later name contains the city the hospital is located in, Antsiranana.
-We standardized the names of those facilities, which resolved `r  prettyNum(n_dif, big.mark = ",", scientific = FALSE)` duplicate(s).
-
-The final sample of `r  prettyNum(n_facilities_new, big.mark = ",", scientific = FALSE)` unique facilities consisted of:
-
-*  `r  prettyNum(n_CSB +n_CSB1 +n_CSB2, big.mark = ",", scientific = FALSE)` CSB facilities, including `r  prettyNum(n_CSB1, big.mark = ",", scientific = FALSE)` CSB1s, `r  prettyNum(n_CSB2, big.mark = ",", scientific = FALSE)` CSB2s, and `r  prettyNum(n_CSB, big.mark = ",", scientific = FALSE)` of unknown level;
-*   `r  prettyNum(n_FSP, big.mark = ",", scientific = FALSE)`  FSP facilities;
-*  `r  prettyNum(n_CHD + n_CHD1 + n_CHD2, big.mark = ",", scientific = FALSE)`  district hospitals, including `r  prettyNum(n_CHD1, big.mark = ",", scientific = FALSE)` CHD1 facilities, `r  prettyNum(n_CHD2, big.mark = ",", scientific = FALSE)` CHD2 facilities, and `r  prettyNum(n_CHD, big.mark = ",", scientific = FALSE)` facilities of unknown level, and
-*  `r  prettyNum(n_CHRR +n_CHU +n_CHRRCHU, big.mark = ",", scientific = FALSE)` regional hospitals, including `r  prettyNum(n_CHRR, big.mark = ",", scientific = FALSE)` CHRRs, `r  prettyNum(n_CHU, big.mark = ",", scientific = FALSE)` CHUs, and `r  prettyNum(n_CHRRCHU, big.mark = ",", scientific = FALSE)` of unknown type.
+From reviewing this list, we observed that in the Diana region, the regional hospitals named "Hopitaly MANARA-PENITRA" and "Hopitaly Manara-Penitra Antsiranana" were duplicates, but appeared separately because the latter name contained the city the hospital is located in, Antsiranana.
+We standardized the names of those facilities, which resolved `r  prettyNum(n_dif, big.mark = ",", scientific = FALSE)` `r ifelse(n_dif > 1, "duplicates","duplicate")`).
+
+The final sample of `r  prettyNum(n_facilities_new, big.mark = ",", scientific = FALSE)` unique facilities consisted of:  `r  prettyNum(n_CSB +n_CSB1 +n_CSB2, big.mark = ",", scientific = FALSE)` CSB facilities, including `r  prettyNum(n_CSB1, big.mark = ",", scientific = FALSE)` CSB1s, `r  prettyNum(n_CSB2, big.mark = ",", scientific = FALSE)` CSB2s, and `r  prettyNum(n_CSB, big.mark = ",", scientific = FALSE)` of unknown level; `r  prettyNum(n_FSP, big.mark = ",", scientific = FALSE)`  FSP facilities; `r  prettyNum(n_CHD + n_CHD1 + n_CHD2, big.mark = ",", scientific = FALSE)`  district hospitals, including `r  prettyNum(n_CHD1, big.mark = ",", scientific = FALSE)` CHD1 facilities, `r  prettyNum(n_CHD2, big.mark = ",", scientific = FALSE)` CHD2 facilities, and `r  prettyNum(n_CHD, big.mark = ",", scientific = FALSE)` facilities of unknown level, and `r  prettyNum(n_CHRR +n_CHU +n_CHRRCHU, big.mark = ",", scientific = FALSE)` regional hospitals, including `r  prettyNum(n_CHRR, big.mark = ",", scientific = FALSE)` CHRRs, `r  prettyNum(n_CHU, big.mark = ",", scientific = FALSE)` CHUs, and `r  prettyNum(n_CHRRCHU, big.mark = ",", scientific = FALSE)` of unknown type.
 
@@
 
-**Step 1: Matching to validated spatial inventory of public facilities in Sub-Saharan Africa (Maina et al.)**
+**Step 1: Matching to validated spatial inventory of public facilities in Sub-Saharan Africa**
 ``` {r step_1-loading_data, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
@@
 
-To maximize pair accuracy, we separately conducting matching among primary health facilities (i.e., FSPs and CSBs) and among hospitals (i.e., CHDs, CHRRs, and CHUs).
+To maximize pair accuracy, we separately conducted matching among primary health facilities (i.e., FSPs and CSBs) and among hospitals (i.e., CHDs, CHRRs, and CHUs).
 For primary health facilities, the full, standardized facility names included the facility's region, district, and commune; for hospitals, the full name included the region and district only.
@@
 
+library(english)
+
 ```
@@
 Using this approach, `r format(as.numeric(n_matched_facilities_rhino), big.mark = ",")` facilities were matched to coordinates in the RHINoVision spatial inventory, of which `r format(as.numeric(n_adist_rhino_0), big.mark = ",")` facilities were matched based on identical string matches,  `r format(as.numeric(n_adist_rhino_1), big.mark = ",")` facilities were matched based on string matches with a Levenshtein distance of 1, `r format(as.numeric(n_adist_rhino_2), big.mark = ",")` facilities were matched based on string matches with a Levenshtein distance of 2, and `r format(as.numeric(n_adist_rhino_3), big.mark = ",")` facilities were matched based on string matches with a Levenshtein distance of 3.
-(`r format(as.numeric(n_adist_rhino_0+n_adist_rhino_1+n_adist_rhino_2+n_adist_rhino_3 - n_matched_facilities_rhino), big.mark = ",")` matches were duplicates and were removed.)
+(`r str_to_sentence(english(as.numeric(n_adist_rhino_0+n_adist_rhino_1+n_adist_rhino_2+n_adist_rhino_3 - n_matched_facilities_rhino)))` matches were duplicates and were removed.)
 
@@
 
+facilities_gps_any_test <- facilities_gps_any
+
 ```
@@
 
-Most of the coordinates in this expanded inventory were duplicates (i.e., the same facility will appear in different sources).
+Most of the coordinates in this expanded inventory were duplicates, as the same facility would appear in different sources.
 Importantly, coordinates for the same facility could be slightly different across sources, due to variation in precision and geolocation.
@@
 
-#
+sf_use_s2(TRUE)
 
@@
                              ifelse(length != 0 & area_km == 0, 
-                                    "line", "polygon"))) %>%
-
-                                    # 
-                                    # 
-                                    # ifelse(length == 0,
-                                    #        "polygon", "other")))) %>%
+                                    "line",
+                                    "polygon"))) %>%
 
   # Let's apply our thresholds from the PARENT file
-  mutate(retain = ifelse(length == 0 & area_km == 0, 
+  mutate(retain = 
+           ifelse(shape_type == "point" |
+                    (shape_type == "line" & length <= length_lim) |
+                    (shape_type == "polygon" & area_km <= area_lim),
                                        "Within threshold", 
-                         ifelse(length <= length_lim & area_km == 0, 
-                                "Within threshold",
-                                ifelse(length == 0 & area_km <= area_lim,
-                                       "Within threshold", 
-                                       "Above threshold")))) %>%
+                                       "Above threshold")) %>%
   ungroup()
@@
 We applied an arbitrary restriction to line and polygon groups, such that the length or area, respectively, would not exceed a particular threshold.
-The threshold for length (`r format(as.numeric(length_lim), big.mark = ",")` km.) was selected to be approximately half the distance of one side of a spatial climate resolution tile (~31 km for ERA-5 data).
-The threshold for area (`r format(as.numeric(area_lim), big.mark = ",")` square km.) was assigned to be the length threshold, squared.
+The threshold for length (`r format(as.numeric(length_lim), big.mark = ",")` km.) was selected to be approximately half the distance of one side of a spatial climate resolution tile (~30 km for ERA-5 data).
+The threshold for area (`r format(as.numeric(area_lim), big.mark = ",")` km²) was assigned to be the length threshold, squared.
 Groups that exceeded their respective thresholds were discarded.
@@
 Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km², with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km².
-At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` square km., all polygon groups fell within the cut-off.
+At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` km², all polygon groups fell within the cut-off.
 Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km, with a maximum distance of `r format(round(n_max_length), big.mark = ",")` km.
@@
 While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used.
-The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 30 km² will have the same time series for a given variable.
+The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 900 km² will have the same time series for a given variable.
 Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.
@@
 For commune-level facilities, knowing the catchment area may therefore be just as informative as knowing the facility's precise location if the catchment area was sufficiently small.
-Determining a cut-off was, again, arbitrary; to adopt a conservative threshold, we considered a catchment area small if its area was  no greater than `r format(as.numeric(area_lim), big.mark = ",")` square km, which corresponded to approximately `r round(as.numeric(area_lim)/(30*30) * 100,0)`% of the area of a climate data spatial resolution tile (Figure \ref{figure_communes_fokontany}).
+Determining a cut-off was, again, arbitrary; to adopt a conservative threshold, we considered a catchment area small if its area was  no greater than `r format(as.numeric(area_lim), big.mark = ",")` km², which corresponded to approximately `r round(as.numeric(area_lim)/(30*30) * 100,0)`% of the area of a climate data spatial resolution tile (Figure \ref{figure_communes_fokontany}).
 
@@
 
-To exploit all available information for geolocation, we first attempted to match commune-level facilities to known *fokontany* based on the facility name and catchment area.
-We used approximate string matching to link facilities named for their locations in our sample to known villages; if the village area was smaller than our threshold, the centroid of the village was used as a proxy for the facility location.
+To exploit all available information for geolocation, we first used approximate string matching to link facilities named for their locations in our sample to known *fokontany*, based on the facility name and catchment area; if the village area was smaller than our threshold, the centroid of the village was used as a proxy for the facility location.
 We then applied the same approach to unmatched commune-level facilities to known communes.
@@
 Altogether, matching to centroids of communes and *fokontany* in Step 5 led to `r format(as.numeric(n_matched_facilities_step_5), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_5)/n_facilities_new * 100,0)`% of our sample) being geolocated.
-
-\newpage
 
@@
 We then calculated the physical distance between the independently identified coordinates and the coordinates identified from our geolocating process for each facility.
-
 Table S2.10 provides the list of facilities in the validation sample.
@@
 * *Avaratra*: north (Malagasy)
-* *Est*: west (French)
+* *Est*: east (French)
 * *Haute*: high (French)

### 2023-03-11 conclusion.Rmd
Revisions throughout and final version for External Reader

@@
 
-Overview of Paper 1
+In this dissertation, I investigated different quantitative facets of the global burden of mental disorders, a burden that is widespread,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] growing,[@patelLancetCommissionGlobal2018] and largely unmet.[@bassUnitedNationsGeneral2012a; @demyttenaerePrevalenceSeverityUnmet2004]
 
-Overview of Paper 2
+In Chapter 1, we examined how the global burden is defined, and we proposed an estimation approach to more comprehensively reflect morbidity and loss of life due to suicide and premature mortality attributable to mental disorders.
+After applying this composite estimation approach to the most recently available estimates from the Global Burden of Disease study, we found that approximately one in 6 disability-adjusted life years (approximately 16%) were due to mental disorders in 2019.
+We then applied a value of a statistical life year approach to estimate the associated global economic burden.
+Our findings suggest staggering loses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion USD in 2019.
+The magnitude of these findings underscores the global scale of impact that mental disorders have and highlights the urgency for research and action to support mental health worldwide.
 
-Overview of Paper 3
+In Chapter 2, we examined how this global burden might be shifting with changes in climate by analyzing health system data in Madagascar, a country with little to no mental health surveillance data and high vulnerability to climate change.
+We obtained data on monthly counts of mental health related visits reported by 3,413 facilities in Madagascar from 2010 to 2020.
+We then geolocated these facilities and obtained meteorologic data on climate conditions to examine the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms.
+We found that monthly mental health related visits declined as temperature increased, particularly in the central highlands, where cooler temperatures were more prevalent; conversely, higher grades of soil moisture were associated with greater mental health visits with a lag of approximately three months, an increase found primarily in regions associated with higher flood risk in Madagascar.
+Our findings illustrate potential heterogeneity in how changing climate conditions may impact mental health needs, and our work demonstrates how routine health system data may be leveraged to address data gaps in health surveillance, particularly in resource-constrained settings.
 
-Policy implications and future research
+In Chapter 3, I examined how search data for health symptoms could, in the absence of high frequency surveillance data, provide insight into changes in population mental health during the COVID-19 pandemic.
+I obtained Google search data from U.S.
+counties, states, and international trends for over 400 symptoms and used these data to study the immediate and sustained impacts of announcements of the development of safe and effective COVID-19 vaccines in November 2020.
+I found that searches for anxiety, depression, and major depressive disorder significantly fell after these announcements, and that this decline continued throughout the subsequent weeks.
+Furthermore, despite the subsequent (and ongoing) politicization of COVID-19 vaccines in the United States, I observed consistency in search density declines for mental health symptoms across red and blue states/counties.
+The findings speak to the importance of timely and transparent communication in public health, as well as to the potential use of internet search data to investigate changes in population mental health that may be difficult to detect without high frequency data.
 
+These papers add to a growing understanding of the tremendous scale of mental health needs worldwide.
 The magnitude of this burden has galvanized a global movement and a call to action for greater investment and prioritization for mental health.[@patelRenewedAgendaGlobal2011] This movement has emphasized the importance of investing in mental health as a means of promoting sustainable development, human rights, and social inclusion.[@patelLancetCommissionGlobal2018]
 
-Burden may be larger than traditionally conceptualized
+To respond to this burden, health systems will need to be mindful of factors beyond the traditional extent of mental health services and consider mental health within a background of broader contextual challenges.
+As seen in Chapters 2 and 3, changes in climate and the course of the COVID-19 pandemic highlight the importance of considering the connections between mental health and other issues in public health.
+Insofar as these challenges may exacerbate one another and strengthen vulnerabilities and inequities in health, responding to them in concert—and addressing the mental health needs of populations facing new and evolving stressors—may be key in overcoming them and fostering resiliency.
+This will require global, multisectoral action across countries at all economic levels, coupled with a substantive increase in financial resources dedicated to mental health.
 
-Papers also show that mental health is linked to broader contextual challenges (climate change, COVID-19) – resilience/vulnerability, exacerbating existing disparities, but also could be critical to overcoming them…
+Moreover, health systems and global health research will need to develop new means of dealing with the current limitations in the measurement of population mental health.
+As discussed in Chapter 1, traditional approaches to estimating the global burden of mental disorders may not capture its true scale, contributing to a lack of perceived importance of mental health to human well-being.
+This perception remains unchallenged, in part, due to the lack of detailed epidemiological data on the prevalence and distribution of mental disorders, a challenge that further constrains mental health research.
+As demonstrated by Chapters 2 and 3, innovative uses of health system and internet search data may help in overcoming this constraint but come with limitations of their own.
 
-In the absence of population mental health metrics, innovative uses of health data may be helpful in conducting research, but come with limitations
+While this dissertation has underscored that the burden of mental disorders is complex in nature and vast in scope, the challenges this burden poses are not insurmountable.
+By measuring and understanding the mental health needs of populations, and by addressing these needs within a broader context of societal challenges, health systems may more effectively respond to this challenge, bringing the world closer to parity between mental health and physical health.
+Through a global effort to address this essential facet of human wellbeing, millions of individuals may be helped to achieve their full potential, strengthen resilience, and obtain access to the care they need to flourish.

### 2023-03-11 frontmatter.Rmd
Revisions throughout and final version for External Reader

@@
 First and foremost, I would like to thank the members of my dissertation committee, Stéphane Verguet, Jessica Cohen, Karestan Koenen, and Margaret McConnell.
-I thank the committee chair, Stéphane Verguet, for his service, and for his exceptional mentorship as my academic advisor.
+I thank the committee chair, Stéphane Verguet, for his service, and for his extraordinary mentorship as my academic advisor.
 Throughout the last four years, he has consistently offered unwavering support and insightful guidance throughout my academic journey, and in the moments where I faltered or doubted myself most, his confidence and cheer always helped see me through.
 
-Jessica Cohen has been a constant source of joy and inspiration throughout my studies, and her exceptional teaching and scholarship have set a standard to aspire to.
+Jessica Cohen has been a constant source of joy and inspiration throughout my studies, and her teaching and scholarship have set a standard to aspire to.
 In addition to being a brilliant scholar, she is an incredible mentor and instructor, bringing genuine joy to the rigorous study of challenging questions.
-Her enthusiasm for econometrics and public health is infectious, and I feel extremely grateful to have learned so much by her example.
+I feel extremely grateful to have learned so much from her example and from her enthusiasm for econometrics and public health.
 
@@
 
-I am also deeply grateful to my coauthors, without whom the research in these pages would be immeasurably lessened, and to the reviewers whose thoughtful reflections strengthened every page.
+I am also deeply grateful to my coauthors and reviewers, whose thoughtful reflections strengthened every page.
 I thank Shekhar Saxena for his guiding leadership in global mental health and for welcoming me into the field when I first arrived at Harvard, and I thank Christopher Golden for welcoming me into his lab and providing every opportunity, guidance, and support a student could wish for throughout the development of the second paper of this thesis.
@@
 My deep appreciation goes to David Bloom, David Canning, Margaret Kruk, and Vikram Patel, whose classes and coffee chats all have shaped my interests and the course of my career.
+I also owe a debt of gratitude to Barbara Heil and Allison Conary for all the mountains they have moved and the uphill struggles they have seen me soundly through.
 
-Among the acknowledgements of our department's dissertations past, two people who have tirelessly worked to support students on their journeys are highlighted, without fail.
-This dissertation is no exception: to Barbara Heil and Allison Conary, I owe a debt of gratitude for all the mountains they have moved and the uphill struggles they have seen me soundly through.
-
-I also would like to thank the many other individuals at the School of Public Health who have made the last four years so memorable and full of warm memories.
+I also would like to thank the many other individuals at the School of Public Health who have made the last four years so full of warm memories.
 I am thankful to Claudette Agustin, Matthew Boccuzzi, Jarvis Chen, and Bruce Villineau for all the care and welcome they have shared with me and with each cohort of students in the Population Health Sciences program.
@@
 
-Across the Charles River are many dear colleagues who have dedicated themselves to ensuring that Harvard feel like home to all its students.
+Across the Charles River are many dear colleagues who have dedicated themselves to ensuring that Harvard feels like home to all its students.
 To Jackie Yun and Janet Daniels at the GSAS Student Center, and to Sheila Thomas, Katie Saibara, and Karina Gonzalez Herrera of the GSAS Office of Equity, Diversity, Inclusion & Belonging, I wish to express my deepest admiration and appreciation.
@@
 
-To my parents, your \emph{hijito} hopes that this work honors your lifelong commitment to the pursuit of knowledge and a better world—a devotion only exceeded by the love and support you have shared with me every day of my life.
+To my parents, your \emph{hijito} hopes that this work honors your lifelong commitment to the pursuit of knowledge and of a better world—a devotion only exceeded by the love and support you have shared with me every day of my life.
 
@@
 
-To John, my partner, words cannot express how much it has meant to me to call you that. Every step on this journey, love, has been easier with you at my side, with your hand in mine.
+To John, my partner, words cannot express how much it has meant to me to call you that. Every step on this journey has been easier with you at my side, with your hand in mine.
 
@@
 
-\emph{To the steps we have taken already, and to the many we have ahead.}
+\emph{To the steps we have taken already, love, and to the many we have ahead.}
 

### 2023-03-11 intro.Rmd
Revisions throughout and final version for External Reader

@@
 
-For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are a leading cause of disability,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] with the Global Burden of Disease (GBD) 2019 study estimating that 4.9% of disability-adjusted life years (DALYs) and 14.6% of years lived with disability (YLDs) are attributable to mental disorders.[@vosGlobalBurden3692020a] Mental disorders are closely linked to physical health, and can be a significant risk factor for premature mortality.[@walkerMortalityMentalDisorders2015] Among patients living with the most severe mental illnesses, premature mortality may reduce life expectancy by as much as 10 to 20 years.[@demooijDyingTooSoon2019]
+For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are a leading cause of disability,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] with the Global Burden of Disease (GBD) study estimating that 4.9% of disability-adjusted life years (DALYs) and 14.6% of years lived with disability (YLDs) were attributable to mental disorders in 2019.[@vosGlobalBurden3692020a] Mental disorders are also closely linked to physical health and can be a significant risk factor for premature mortality.[@walkerMortalityMentalDisorders2015] Among patients living with the most severe mental illnesses, premature mortality may reduce life expectancy by as much as 10 to 20 years.[@demooijDyingTooSoon2019]
 
-At all levels of sociodemographic development, this burden of morbidity and mortality is rising.[@patelLancetCommissionGlobal2018] Yet despite this global scale and despite a growing evidence base for impactful, cost-effective interventions that may help,[@patelMentalNeurologicalSubstance2016] the profound impact of mental disorders has been met by a profound treatment gap.[@demyttenaerePrevalenceSeverityUnmet2004] The majority of people living with a mental disorder do not have access to adequate care (Figure \ref{figure_service_gap}),[@bassUnitedNationsGeneral2012a; @demyttenaerePrevalenceSeverityUnmet2004] and many face stigma,[@alonsoPerceivedStigmaIndividuals2009; @angermeyerStigmaMentalIllness2003] discrimination,[@stuartMentalIllnessEmployment2006; @thornicroftDiscriminationHealthCare2007] and abuse.[@humanrightswatchDeathSentenceAbuses2012; @mfoafo-mcarthyHumanRightsViolations2014; @rahmanMentalDistressHuman2021]
+At all levels of sociodemographic development, this burden is rising.[@patelLancetCommissionGlobal2018] Yet despite this global scale and despite a growing evidence base for impactful, cost-effective interventions that may help,[@patelMentalNeurologicalSubstance2016] the profound impact of mental disorders has been met by a profound treatment gap.[@demyttenaerePrevalenceSeverityUnmet2004] A majority of the world's population lives in countries with fewer than 10 psychiatrists for every 100,000 people (Figure \ref{figure_service_gap}).
+Most of those living with a mental disorder do not have access to adequate care,[@bassUnitedNationsGeneral2012a; @demyttenaerePrevalenceSeverityUnmet2004] and many face stigma,[@alonsoPerceivedStigmaIndividuals2009; @angermeyerStigmaMentalIllness2003] discrimination,[@stuartMentalIllnessEmployment2006; @thornicroftDiscriminationHealthCare2007] and abuse.[@humanrightswatchDeathSentenceAbuses2012; @mfoafo-mcarthyHumanRightsViolations2014; @rahmanMentalDistressHuman2021]
 
@@
 
-```{r figure_service_gap, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 11, fig.height = 6.5, fig.align='center', out.width = '97%',  fig.scap="Countries where fewer than 10 psychiastrists per 100,000 capita were working in the health sector, 2013-2017.", out.extra='',  fig.cap="\\label{figure_all_diseases}Countries where fewer than 10 psychiastrists per 100,000 capita were working in the health sector between 2013-2017, average.
-Data from the Globa Health Observator (GHO) of the World Health Organization (WHO)."}
+```{r figure_service_gap, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 11, fig.height = 6.5, fig.align='center', out.width = '97%', fig.scap="Countries where fewer than 10 psychiatrists per 100,000 capita were working in the health sector, 2013-2017.", out.extra='', fig.cap="\\label{figure_service_gap}Countries where fewer than 10 psychiatrists per 100,000 capita were working in the health sector between 2013-2017, average.
+Data from the Global Health Observatory (GHO) of the World Health Organization (WHO)."}
 
@@
 In addition to the long-standing challenges of these unmet needs, new and emerging dangers such as climate change and COVID-19 reveal additional stressors that threaten to exacerbate this burden.
-Global climate change—an accelerating existential threat to planetary health that the United Nations considers the “defining crisis of our time”—is already manifesting profound impacts on mental health.[@worldhealthorganizationMentalHealthClimate2022] The impacts are shaped both by the disastrous upheaval caused by worsening extreme weather events and by the incremental change rising temperatures and sea levels have wrought on livelihoods and means of living—altering the availability and access to natural resources, land use, infrastructure, and community.[@atwoliMentalHealthClimate2022; @hayesClimateChangeMental2018] This essential connections between mental health and human wellbeing have been further underscored by the devastating impacts of the COVID-19 pandemic, which continues to deal psychological and psychiatric harm to patients, health care workers, and the public overall.[@vindegaardCOVID19PandemicMental2020]
+Global climate change—an accelerating existential threat to planetary health that the United Nations considers the “defining crisis of our time”—is already manifesting profound impacts on mental health.[@worldhealthorganizationMentalHealthClimate2022] These impacts are shaped both by the disastrous upheaval caused by worsening extreme weather events and by the incremental change rising temperatures and sea levels have wrought on livelihoods and means of living—altering the availability and access to natural resources, land use, infrastructure, and community.[@atwoliMentalHealthClimate2022; @hayesClimateChangeMental2018] The essential connections between mental health and human well-being have been further underscored by the devastating impacts of the COVID-19 pandemic, which continues to deal psychological and psychiatric harm to patients, health care workers, and the public overall.[@vindegaardCOVID19PandemicMental2020]
 
-The extant and evolving challenges of global mental health, in turn, entail jeopardy to health systems and to the three intrinsic goals of improving health, responsiveness, and financial protection.
-According to the WHO’s Mental Health Atlas report from 2020, mental health system governance, capacity, and integration into routine service delivery is fundamentally lacking across nations of all levels of economic development, with only 15% of countries having functional integration of mental health into primary health care.[@worldhealthorganizationMentalHealthAtlas2021] This lack of service delivery echoes a lack of basic epidemiological data,[@steinCrossnationalEpidemiologySocial2017] constraining researching and frustrating efforts to respond to mental health needs.
+The extant and evolving challenges of global mental health, in turn, entail jeopardy to health systems and to the three intrinsic goals of improving health, responsiveness, and financial protection.[@robertsGettingHealthReform2008] According to the WHO’s Mental Health Atlas report from 2020, mental health system governance, capacity, and integration into routine service delivery is fundamentally lacking across nations of all levels of economic development, with only 15% of countries having functional integration of mental health into primary health care.[@worldhealthorganizationMentalHealthAtlas2021] This lack of service delivery echoes a lack of basic epidemiological data,[@steinCrossnationalEpidemiologySocial2017] constraining research and frustrating efforts to respond to mental health needs.
 Among nations, the Atlas report highlights widening disparities in health system indicators, with worsened gaps in service availability and public health expenditure for mental health between low- and middle-income countries and high-income peers.
-With respect to health spending in many countries, mental health care services have relied primarily or exclusively on out-of-pocket payments,[@dixonFinancingMentalHealth2006] resulting in a greater risk of catastrophic health expenditure among households with patients living with a mental disorder.
-These direct costs, when coupled with the indirect costs of diminished due to disability, may exacerbate conditions of poverty, [@patelPovertyCommonMental2003] which, in turn, may lead to worsening mental health[@lundPovertyCommonMental2010]—exacerbating a vicious cycle that harms households and nations alike.
+With respect to health spending, mental health care services in many countries have traditionally relied primarily or exclusively on out-of-pocket payments,[@dixonFinancingMentalHealth2006] resulting in a greater risk of catastrophic health expenditure among households with patients living with a mental disorder.
+These direct costs, when coupled with the indirect costs of diminished earnings due to disability, may exacerbate conditions of poverty, [@patelPovertyCommonMental2003] which, in turn, may lead to worsening mental health[@lundPovertyCommonMental2010]—feeding a vicious cycle that harms households and nations alike.
 
-A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequence to strengthening of health system responses to mental disorders and improving health outcomes for millions of individuals worldwide.
+A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequences to strengthening health system responses to mental disorders and improving health outcomes for millions of individuals worldwide.
 Contributing to such an understanding has motivated this dissertation, which takes as its focus different quantitative aspects of the global burden of mental illness—how we measure and evaluate it, how it may be changing, and how novel data sources may help in characterizing it, particularly in the absence of robust, high-frequency epidemiological surveillance.
@@
 In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value.
-We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available GBD data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in the year 2019.
-Using value of statistical life approaches, we estimated that the economic value of this mental health burden would exceed 4.7 trillion USD.
+We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available GBD data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019.
+Using value of statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion USD.
 
@@
 Madagascar has little to no mental health surveillance data and is among the nations most vulnerable to climate change.
-To address these gaps, we studied the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms—by leveraging meteorologic, geospatial, and health system data reported by 3,413 facilities in Madagascar from 2010 to 2020.
-We found a statistically significant reduction in monthly cases reported associated with temperature, primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
-We further found that higher soil moisture may be associated with higher case counts in the future, after a three month lag; this increase was primarily found in the eastern lowlands and the northern dry deciduous forests, consistent with the geographic concentration of flood risk in Madagascar.
-Our findings point to suggest potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.
+To address these gaps, we studied the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms—by leveraging meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020.
+We found a statistically significant reduction in monthly mental health related visits associated with each degree Celcius increase in temperature, primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
+We further found that higher soil moisture may be associated with more mental health visits in the future, after a three month lag; this increase was primarily found in the eastern lowlands and the northern dry deciduous forests, consistent with the geographic concentration of flood risk in Madagascar.
+Our findings point to potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.
 
-In Chapter 3, we investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic.
+In Chapter 3, I investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic.
 Using search data from U.S.
-counties, states, and international trends, we explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms.
-We found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
+counties, states, and international trends, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms.
+I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
 The findings underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

### 2023-03-11 paper1.Rmd
Revisions throughout and final version for External Reader

@@
 ```{r paper1code_libraries_data}
-
-# Loading libraries
-library(readxl)
-library(dplyr)
-library(tidyr)
-library(ggplot2)
-library(RColorBrewer)
-library(sp)
-library(broom)
-library(sf)
-library(scales)
-library(viridis)
-library(data.table)
-library(ggpubr)
-library(lemon)
-library(rnaturalearth)
-library(rnaturalearthdata)
-library(sysfonts)
-library(showtext)
-font_add_google("Source Sans Pro")
-library(gridExtra)
-showtext_auto() 
-showtext_opts(dpi = 300)  
-library(rnaturalearthhires) # install.packages("rnaturalearthhires", repos = "http://packages.ropensci.org", type = "source")
 
@@
  abstract2,
-  "\\% of global DALYs (Figure 1). Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising ",
+ "\\% of global DALYs (Figure 2). Under all three methods, the burden of mental disorders (in DALYs) exhibited a country-income gradient, with mental disorders comprising ",
  ifelse(results5/results6 > 2.4, "over twice", ifelse(results5/results6> 2, "roughly twice", "approximately twice")),
@@
 
-\emph{Daniel Arias, Shekhar Saxena, Stéphane Verguet}
+\emph{Daniel Arias, Shekhar Saxena, and Stéphane Verguet}
 
@@
 
-A version of this paper was accepted for publication by \emph{eClinicalMedicine} on September 9, 2022 and was published in Volume 54, Issue 101675 in December 2022.
+An earlier version of this paper was published by \emph{eClinicalMedicine} in Volume 54, Issue 101675 in December 2022.
 
@@
 The most recent estimates of morbidity and mortality due to mental disorders come from the Global Burden of Disease (GBD) 2019 study.[@vosGlobalBurden3692020a] The GBD study provides disease burden estimates using DALYs, years of life lost (YLLs), and years lived with disability (YLDs), which are then aggregated within a hierarchical grouping scheme that classifies causes of disability and death at different levels of mutually exclusive and completely exhaustive categories.
-(Mental disorders are a Level 2 condition, nested under NCDs; see Table S1.3.)
+(Mental disorders are a Level 2 condition, nested under noncommunicable diseases (NCDs); see Table S1.3.)
 
 While GBD remains the gold standard for global epidemiologic estimation, the nature of the GBD scheme—in particular, the rationale for grouping certain conditions under mental disorders or not—has been the subject of debate in the literature.[@atunChallengesEstimatingTrue2016; @vigoEstimatingTrueGlobal2016; @whitefordChallengesEstimatingTrue2016] In particular, work by Vigo et al.
-(2016) published in The Lancet Psychiatry argues for an expanded classification of mental disorders under the GBD classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders.
+(2016) published in \emph{The Lancet Psychiatry} argues for an expanded classification of mental disorders under the GBD classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders.
 Using data from the 2013 GBD study, Vigo and colleagues re-allocated the entire burden of dementias, epilepsy, migraine, tension-type headache, and self-harm to mental disorders.
@@
 Using this approach on GBD 2019 estimates, we then apply monetary values to DALYs to reach estimates of the global economic value of the mental burden of disease using a value of a statistical life (VSL) approach similar to that of Bloom and colleagues,[@bloomGlobalEconomicBurden2011] which attempts to capture a population’s willingness to pay to reduce morbidity and mortality associated with illness.
-The VSL approach—in contrast alternatives such as cost of illness and value of lost output approaches—includes an economic valuation of mortality risk reductions in monetary terms, and thus enables comparison across sectors (beyond the sole health sector) which can motivate decision-making toward ameliorating welfare and societal mental health.
+The VSL approach—in contrast to alternatives such as cost of illness and value of lost output approaches—includes an economic valuation of mortality risk reductions in monetary terms, and thus enables comparison across sectors (beyond the sole health sector) which can motivate decision-making toward ameliorating welfare and societal mental health.
 Our findings suggest that both the epidemiological and economic burden of mental disorders could be larger than previously estimated, and that underestimation would be larger among regions where premature mortality due to mental disorders is greater.
@@
 In addition to our base-case economic valuation, we further report our VSL estimates using three times GDP per capita as the value of a DALY.
-(Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S1.5 and S1.6 of Appendix 1)
+(Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S1.5 and S1.6 of Appendix 1.)
 
@@
 
-The research draws exclusively on secondary country-level data reported at the national or subnational level.
-As such, it does not involve data collection, experimentation, or investigation concerning human subjects.
 The Institutional Review Board (IRB) of the Harvard T.H.
-Chan School of Public Health determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).
-
-### Role of funding source
-
-This study received no funding. All authors (DA, SV, and SS) had access to the data and shared in the decision to submit this article for publication.
+Chan School of Public Health determined that this study was not human subjects research and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).
 
@@
 
-```{r figure_dalys_nation, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="DALYs attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.", out.extra='', fig.cap=paste0("\\label{figure_dalys_nation}DALYs attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.
-ATG: Antigua and Barbuda; DALYs: disability-adjusted life years; FSM: Federated States of Micronesia; LCA: Saint Lucia; TLS: East Timor; TTO: Trinidad and Tobago; VCT: Saint Vincent and the Grenadines."), fig.width = 13.7, fig.height = 7.5, fig.align='center', out.width = '98%'}
+```{r figure_dalys_nation, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="Disability-adjusted life years (DALYs) attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.", out.extra='', fig.cap=paste0("\\label{figure_dalys_nation}Disability-adjusted life years (DALYs) attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.
+ATG: Antigua and Barbuda.
+FSM: Federated States of Micronesia.
+LCA: Saint Lucia.
+TLS: East Timor.
+TTO: Trinidad and Tobago.
+VCT: Saint Vincent and the Grenadines."), fig.width = 13.7, fig.height = 7.5, fig.align='center', out.width = '98%'}
 
@@
 Values are aggregated by GBD region.
-DALYs: Disability-adjusted life years; YLDs: years lived with disability; YLLs: years of life lost; GBD: Global Burden of Disease."), fig.width = 11, fig.height = 11, fig.align='center', out.width = '97%'}
+DALYs: Disability-adjusted life years.
+YLDs: years lived with disability.
+YLLs: years of life lost.
+GBD: Global Burden of Disease."), fig.width = 11, fig.height = 11, fig.align='center', out.width = '97%'}
 
@@
 Values are aggregated by GBD region.
-GDP: gross domestic product; USD: United States dollar; DALY: disability-adjusted life year; GBD: Global Burden of Disease.", echo = FALSE, include = TRUE}
+GDP: gross domestic product.
+USD: United States dollar.
+DALY: disability-adjusted life year.
+GBD: Global Burden of Disease.", echo = FALSE, include = TRUE}
 
@@
 All authors contributed to study conception, methodology, and interpretation.
-DA oversaw data acquisition, programming, formal analysis, visualization, the first draft of the manuscript.
+DA oversaw data acquisition, programming, formal analysis, visualization, and the first draft of the manuscript.
 All authors contributed to critical revision of the manuscript, with responses to reviewers and subsequent revisions led by DA.
-All authors had access to and verified all the data and accept responsibility for the decision to submit for publication.
+
+### Funding statement
+
+This study received no funding.
 
@@
 All codes used for the analysis in this article are available on GitHub (https://github.com/darias5/gmh_econ).
-
-\newpage

### 2023-03-11 paper2.Rmd
Revisions throughout and final version for External Reader

@@
      p_val <- round(output_df$p_value, 3)
-        low <- round(exp(output_df$lower_99), 3)
-        high <- round(exp(output_df$upper_99), 3)
+     low <- format(round(exp(output_df$lower_99), 3), nsmall = 3)
+     high <- format(round(exp(output_df$upper_99), 3), nsmall = 3)
 
@@
       "(IRR: ",
-            val,
+       format(val, nsmall = 3),
       ", p ",
@@
           paste0("= ",
-                          p_val,
+             format(p_val, nsmall = 3),
              ", ")),
@@
       val < 1,
-            paste0(round(1 - val, 3) * 100, "\\% fewer"),
+      paste0(round(val, 3) * 100, "\\% fewer"),
       paste0(round(val - 1, 3) * 100, "\\%")
@@
    if (value == "ame"){
+
     val <- round(output_df$ame, 3)
     p_val <- round(output_df$ame_p_value, 3)
-        low <- round(output_df$ame_lower_99, 3)
-        high <- round(output_df$ame_upper_99, 3)
+    low <- format(round(output_df$ame_lower_99, 3), nsmall = 3)
+    high <- format(round(output_df$ame_upper_99, 3), nsmall = 3)
 
@@
       "(AME: ",
-            val,
+      format(val, nsmall = 3),
       ", p ",
@@
 
-          return(round(val, 2))
+     return(format(round(val, 3), nsmall = 3))
 
@@
 
-\emph{Daniel Arias, Karestan Koenen, Christopher Golden}
-
-\vspace{24pt}
+\emph{Daniel Arias, Karestan Koenen, and Christopher Golden}
+
+\vspace{12pt}
 
@@
 
-{\bf Methods:} To better understand climate conditions and population mental health in these settings, we leverage meteorologic, geospatial, and monthly cases of mental and neurological disorders reported by `r num_facilities_pretty` facilities in Madagascar from 2010 to 2020 to explore the mental health impacts of three CCEs using negative binomial regression: temperature, soil moisture, and duration of cyclones and tropical storms.
-
-{\bf Findings and interpretation:} We found a statistically significant reduction in monthly cases reported associated with temperature—approximately `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = "only")` cases reported per each degree Celsius increase `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = TRUE)`.
+{\bf Methods:} To better understand climate conditions and population mental health in these settings, we leverage meteorologic and geospatial data to explore the mental health impacts of three CCEs on monthly counts of patient visits for mental and neurological disorders reported by `r num_facilities_pretty` facilities in Madagascar from 2010 to 2020.
+We used negative binomial regression to examine the impacts of three CCEs: temperature, soil moisture, and duration of cyclones and tropical storms.
+
+{\bf Findings and interpretation:} We found a statistically significant reduction in monthly visits reported associated with temperature—approximately `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = "only")` visits reported per each degree Celsius increase `r function_dynamic_text_results(section = "main", coefficient_option = "exposure_temperature", model_option = 4, value = "irr", value_include = TRUE)`.
 A multiverse analysis of `r num_models_multiverse` models found this estimate to be robust to alternative specifications; ecoregion analysis indicated that this association was primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
-We further found that higher soil moisture may be associated with higher case counts in the future, with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")`  elevation in incident cases reported `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`  after a three month lag.
-Ecoloregion analysis suggest higher cases are reported in the eastern lowlands and the northern dry deciduous forests when soil moisture rises, which is consistent with the geographic concentration of flood risk in Madagascar.
+We further found that higher soil moisture may be associated with higher mental health related visits in the future, with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in visits reported `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)` after a three month lag.
+Ecoregion analysis suggests more visits are reported in the eastern lowlands and the northern dry deciduous forests when soil moisture rises, which is consistent with the geographic concentration of flood risk in Madagascar.
 Our findings highlight the complex interactions between CCEs and population mental health and suggest potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.
@@
 
-Understanding how both incremental and extreme changes in climate impact population mental health is critical to gauging the full extent to which CCEs impact human health and wellbeing under a multidisciplinary approach to population health.[@berryCaseSystemsThinking2018] This understanding is particularly important in contexts such as Madagascar, where climate conditions are already demonstrating pronounced pressures on economic, social, and physical wellbeing.
+Understanding how both incremental and extreme changes in climate impact population mental health is critical to gauging the full extent to which CCEs impact human health and well-being under a multidisciplinary approach to population health.[@berryCaseSystemsThinking2018] This understanding is particularly important in contexts such as Madagascar, where climate conditions are already demonstrating pronounced pressures on economic, social, and physical well-being.
 
@@
 Despite the poor availability of mental health services in many settings, routine health system data can still provide valuable insights into trends and patterns of service use and the need and distribution of care for mental health issues.
-Although these data may only capture a share of the true burden of disease, reported cases and visits related can be a valuable starting point for preliminary research into the impact of climate change on population mental health in resource-constrained settings.
+Although these data may only capture a share of the true burden of disease, reported visits related to mental health complaints can be a valuable starting point for preliminary research into the impact of climate change on population mental health in resource-constrained settings.
 
@@
 
-As a measure of population mental health, we considered facility-level monthly reports cases of mental disorders; in terms of exposure, we explored the predictive association of three CCEs with incident mental health visits: mean monthly ambient air temperature, mean monthly soil moisture, and monthly cyclone activity.
-As exposure to these stressors could involve a delay in onset of mental health symptoms and subsequent care seeking, we further explored whether exposures in prior months were associated with monthly reported cases in sequent ones.
+As a measure of population mental health, we considered facility-level monthly reported visits related to mental disorders; in terms of exposure, we explored the predictive association of three CCEs with incident mental health visits: mean monthly ambient air temperature, mean monthly soil moisture, and monthly cyclone activity.
+As exposure to these stressors could involve a delay in onset of mental health symptoms and subsequent care seeking, we further explored whether exposures in prior months were associated with monthly reported visits in subsequent ones.
 We further considered interactive and additive models to account for complexity in the interaction of climate variables in Madagascar, as well as ecological variation to capture differences in regional climate systems.
@@
 
-To analyze the impact of climate on population mental health in Madagascar, we first obtained health management information system (HMIS) data from the Madagascar Ministère de la Santé Publique.
+To analyze the impact of climate on population mental health in Madagascar, we first obtained health management information system (HMIS) data through a collaboration with the Madagascar Ministère de la Santé Publique.
 We then obtained gridded temperature and soil moisture data from the European ReAnalysis (ERA5)[@copernicusclimatechangeservicec3sFifthGenerationECMWF2017] and the European Space Agency’s Climate Change Initiative (ESA CCI),[@europeanspaceagencyEuropeanSpaceAgency2022] respectively.
-Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@wikipediaSouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the National Oceanic and Atmospheric Administration (NOAA)[@InternationalBestTrack2021] for accuracy.
+Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@wikipediaSouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the National Oceanic and Atmospheric Administration (NOAA)[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021] for accuracy.
 
@@
 A summary of classification by facility type and year is provided in Appendix 2.1, Table S2.1, with English translations of the French disease names provided in Table S2.2.
-and yearly cumulative reported case totals by disorder reported by facility level and year in Tables S2.3-5.
-
-To address heterogeneity in reporting, our analysis aggregated any monthly incidence of mental or neurological disorders reported by a facility, irrespective of age and sex, into a summary outcome measure.
+and yearly cumulative reported visit totals by disorder reported by facility level and year in Tables S2.3-5.
+
+To address heterogeneity in reporting, our analysis aggregated any monthly visits concerning mental or neurological disorders reported by a facility, irrespective of age and sex, into a summary outcome measure.
 To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series.
@@
 
-ERA 5 is a global atmospheric reanalysis from the European Centre for Medium-Range Weather Forecasts (ECMWF) and is freely available through its Copernicus Climate Change Service (C3S)[@europeanspaceagencyEuropeanSpaceAgency2022].
-The spatial resolution of ERA 5 is approximately 30 km, with quality-assured hourly estimates available from 1959 to the present.[@europeanspaceagencyEuropeanSpaceAgency2022] Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation  [@googleearthengineERA5MonthlyAggregates2022] Temperature data was then converted to degrees Celsius.
+ERA5 is a global atmospheric reanalysis from the European Centre for Medium-Range Weather Forecasts (ECMWF) and is freely available through its Copernicus Climate Change Service (C3S)[@europeanspaceagencyEuropeanSpaceAgency2022].
+The spatial resolution of ERA5 is approximately 30 km, with quality-assured hourly estimates available from 1959 to the present.[@europeanspaceagencyEuropeanSpaceAgency2022] Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation.[@googleearthengineERA5MonthlyAggregates2022] Temperature data was then converted to degrees Celsius.
 
@@
 Duration of cyclone activity was included in all models using our count indicator of exposure.
-In all models, we included fixed effects for Madagascar’s twenty-two regions to account for geographic differences in climate patterns and case reporting.
+In all models, we included fixed effects for Madagascar’s twenty-two regions to account for geographic differences in climate patterns and case/visit reporting.
 We further included month and year fixed effects to account for seasonality and time-varying omitted variables.
@@
 The Institutional Review Board (IRB) of the Harvard T.H.
-Chan School of Public Health determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB21-1303, determined on October 19, 2021).
+Chan School of Public Health determined that this study was not human subjects research and that additional review was not required (protocol number: IRB21-1303, determined on October 19, 2021).
 
@@
 
-```{r figure_gps, include = TRUE, echo=FALSE, warnings = FALSE,  fig.scap="Map of facilities in Madagascar, by GPS coordinate source and facility type.", out.extra='', fig.cap="\\label{figure_gps}Map of facilities in Madagascar, by GPS coordinate source (left panel) and facility type (right panel).", fig.width = 16, fig.height = 10, fig.align='center', out.height= '90%'}
+```{r figure_gps, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="Map of facilities in Madagascar, by coordinate source and facility type.", out.extra='', fig.cap="\\label{figure_gps}Map of facilities in Madagascar, by coordinate source (left panel) and facility type (right panel).", fig.width = 16, fig.height = 10, fig.align='center', out.height= '90%'}
 
@@
                 col_search),
-                     name = "GPS type")
+           name = "Source")
 
@@
  gt(rowname_col = "coefficient", groupname_col = "model") %>%
-  tab_header(title = md("Table 2.2: incidence rate ratios (IRRs) and average marginal effects (AME) of climate exposures on monthly reported cases of mental and neurological disorders, Models 1 through 4.")) %>%
+ tab_header(title = md("Table 2.2: incidence rate ratios (IRRs) and average marginal effects (AME) of climate exposures on monthly reported visits related to mental and neurological disorders, Models 1 through 4.")) %>%
 
@@
 The regression models predicting monthly counts of any mental or neurological disorder (Table 2.2) showed significant associations with temperature across all models.
-A one-degree Celsius increase in temperature was associated with approximately `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` cases reported `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)` by primary clinics and hospitals in Model 1.
+A one-degree Celsius increase in temperature was associated with approximately `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` visits reported `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)` by primary clinics and hospitals in Model 1.
 Inclusion of both climate predictors resulted in little change to the measure of association for temperature.
-In an additive model with soil moisture included (Model 3), the effect estimate associated with temperature grew to `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` cases reported `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)`.
+In an additive model with soil moisture included (Model 3), the effect estimate associated with temperature grew to `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` visits reported `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)`.
 Adopting an interactive model (Model 4) attenuated the association `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)`, but remained significant at a 95% level of confidence.
-Across all models with temperature, the average marginal effect associated with temperature (across a sample with all clinics) ranged between 2 and 3 fewer monthly cases reported and was statistically significant at an alpha of 0.01, with the average marginal effect in Model 4 being `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "ame", value_include ="only")` cases `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "ame", value_include =FALSE)`.
+Across all models with temperature, the average marginal effect associated with temperature (across a sample with all clinics) ranged between 2 and 3 fewer monthly mental health visits reported and was statistically significant at an alpha of 0.01, with the average marginal effect in Model 4 being `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "ame", value_include ="only")` visits `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "exposure_temperature", value = "ame", value_include =FALSE)`.
 
 Effect estimates associated with soil moisture were not statistically significant across all four models.
-In all models, we observed a modest reduction in cases reported per each additional day duration of cyclone activity, with the incidence ratio ratios of Models 3 `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "days_with_cyclone", value = "irr", value_include =TRUE)` and Models 4 `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "days_with_cyclone", value = "irr", value_include = TRUE)` being significant at a level of 0.05.
-In all models, however, the average marginal effect was close to 0, with the average marginal effect in Model 4 being only `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "days_with_cyclone", value = "ame", value_include ="only")` cases `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "days_with_cyclone", value = "ame", value_include ="FALSE")`.
-
-```{r figure_marginal, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 13, fig.height = 13, fig.align='center', out.width = '95%', fig.scap="Predicted values of monthly case counts and marginal effect estimates by coefficient and their 95\\% and 99\\% confidence intervals.", out.extra='', fig.cap="\\label{figure_marginal}Predicted values of monthly case counts and marginal effect estimates by coefficient and their 95\\% and 99\\% confidence intervals.
-The left panels show predicted values of monthly case counts of mental and neurological disorders in Madagascar, given different units of climate exposure.
+In all models, we observed a modest reduction in visits reported per each additional day duration of cyclone activity, with the incidence ratio ratios of Models 3 `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "days_with_cyclone", value = "irr", value_include =TRUE)` and Models 4 `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "days_with_cyclone", value = "irr", value_include = TRUE)` being significant at a level of 0.05.
+In all models, however, the average marginal effect was close to 0, with the average marginal effect in Model 4 being only `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "days_with_cyclone", value = "ame", value_include ="only")` visits `r function_dynamic_text_results(section = "main", model_option = 4, coefficient_option = "days_with_cyclone", value = "ame", value_include ="FALSE")`.
+
+```{r figure_marginal, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 13, fig.height = 13, fig.align='center', out.width = '95%', fig.scap="Predicted values of monthly mental health visits and marginal effect estimates by coefficient and their 95\\% and 99\\% confidence intervals.", out.extra='', fig.cap="\\label{figure_marginal} Predicted values of monthly mental health visits and marginal effect estimates by coefficient and their 95\\% and 99\\% confidence intervals.
+The left panels show predicted values of monthly counts of visits related to mental and neurological disorders in Madagascar, given different units of climate exposure.
 The right panels show marginal effect estimates over different units of climate exposure in the data.
-The dotted horizontal lines in the right panel depict no marginal effect on case counts.
+The dotted horizontal lines in the right panel depict no marginal effect on visit counts.
 In all panels, the model used to generate predictions and marginal effects corresponds to Model 4.
@@
  geom_point() +
-  labs(y = "Predicted monthly case counts, given climate exposure",
+ labs(y = "Predicted monthly mental health visit counts, given climate exposure",
     x = "Units of climate exposure") +
@@
 
-```{r figure_lag, include = TRUE, echo=FALSE, warnings = FALSE,  fig.scap="Effect estimates by coefficient with lagged exposures and their 99\\% and 95\\% confidence intervals, Model 4.", out.extra='',  fig.cap="\\label{figure_lag}Effect estimates by coefficient with lagged exposures and their 99\\% and 95\\% confidence intervals, Model 4.
-The x-axis correspond to the length of the lag (e.g., a value of 2 reflects a lag of two months, such that case counts are predicted by climate conditions two months prior), with the value of 0 reflecting a model without any lag in exposure.
+```{r figure_lag, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap="Effect estimates by coefficient with lagged exposures and their 95\\% and 99\\% confidence intervals, Model 4.", out.extra='', fig.cap="\\label{figure_lag}Effect estimates by coefficient with lagged exposures and their 95\\% and 99\\% confidence intervals, Model 4.
+The x-axis correspond to the length of the lag (e.g., a value of 2 reflects a lag of two months, such that visit counts are predicted by climate conditions two months prior), with the value of 0 reflecting a model without any lag in exposure.
 The dotted horizontal lines depict a null effect.
@@
 ```
-Predicted values of monthly case counts under Model 4 echoed the effect estimates from Table 2, with fewer cases reported in warmer months (Figure \ref{figure_marginal}).
-Marginal effect estimates across the distribution of temperatures in our data showed that the greatest level of reduction occurred between 10 and 15 degrees Celsius, with each degree increase associated with 4 to 5 fewer cases of mental or neurological disorders reported, controlling for other covariates.
-Months with greater levels of soil moisture and days with cyclone activity also showed fewer reported cases; however, the marginal effects associated with soil moisture were not significant across any unit of exposure, while those associated with days with cyclone activity were close to zero for all lengths of activity.
-
-Examining lagged effects showed potential temporal associations between soil moisture levels in preceding months and case counts in those following (Figure \ref{figure_lag}), with higher saturation leading to a statistically significant elevation in cases reported 1 to 5 months later.
-At a lag of 3 months, the elevation in cases was approximately `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`.
+Predicted values of monthly mental health related visits counts under Model 4 echoed the effect estimates from Table 2, with fewer visits reported in warmer months (Figure \ref{figure_marginal}).
+Marginal effect estimates across the distribution of temperatures in our data showed that the greatest level of reduction occurred between 10 and 15 degrees Celsius, with each degree increase associated with 4 to 5 fewer visits related to mental or neurological disorders reported, controlling for other covariates.
+Months with greater levels of soil moisture and days with cyclone activity also showed fewer reported visits; however, the marginal effects associated with soil moisture were not significant across any unit of exposure, while those associated with days with cyclone activity were close to zero for all lengths of activity.
+
+Examining lagged effects showed potential temporal associations between soil moisture levels in preceding months and visit counts in those following (Figure \ref{figure_lag}), with higher saturation leading to a statistically significant elevation in visits reported 1 to 5 months later.
+At a lag of 3 months, the elevation in visits was approximately `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`.
 There appeared to be a significant elevation of similar magnitude 13 to 17 months prior, suggesting potential annularity in lagged association.
 Effects for temperature were not significant across any lag; cyclone activity similarly showed no significance in lags under a year, but did show modest, statistically significant associations at lags of 12 months `r function_dynamic_text_results(section = "lags", lag_option = 12, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)` and 15 months `r function_dynamic_text_results(section = "lags", lag_option = 15, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)`.
-A slight increase in cases was associated with cyclone activity in a prior month, but this increase was not statistically significant `r function_dynamic_text_results(section = "lags", lag_option = 1, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)`.
+A slight increase in visits was associated with cyclone activity in a prior month, but this increase was not statistically significant `r function_dynamic_text_results(section = "lags", lag_option = 1, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)`.
 
@@
 Results from our subgroup analysis showed evidence of potential effect heterogeneity by ecoregion (Table 2.3).
-For temperature, estimates of association were only statistically significant in the highland subhumid forests, where each one-degree Celsius increase in temperature was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = "only")` cases reported `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = TRUE)`.
-Temperature was associated with a slight increase in temperature in the eastern lowland forests `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)` and the desert and xeric shrublands `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)`, but in neither case was the estimate significant at a level of 0.05.
+For temperature, estimates of association were only statistically significant in the highland subhumid forests, where each one-degree Celsius increase in temperature was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = "only")` visits reported `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "2", value = "irr", value_include = TRUE)`.
+Temperature was associated with a slight increase in visits in the eastern lowland forests `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)` and the desert and xeric shrublands `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_temperature", region_option = "1", value = "irr", value_include = TRUE)`, but in neither case was the estimate significant at a level of 0.05.
 
@@
 
-With respect to soil moisture, while our primary analysis found no evidence of a statistically significant association with reported cases in the full sample, we found evidence of heterogeneity in our subgroup analysis.
-Among facilities in the highland subhumid forests, we found that each percentage point increase in soil moisture was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = TRUE)`, with an average marginal effect of `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = FALSE)`.
-Conversely, each percentage point increase in soil moisture in the dry deciduous forests was associated with a `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = "only")` increase in reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = TRUE)`, with an average marginal effect of `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "ame", value_include = "only")` reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "ame", value_include = FALSE)`.
+With respect to soil moisture, while our primary analysis found no evidence of a statistically significant association with reported visits in the full sample, we found evidence of heterogeneity in our subgroup analysis.
+Among facilities in the highland subhumid forests, we found that each percentage point increase in soil moisture was associated with `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = "only")` reported visits `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "irr", value_include = TRUE)`, with an average marginal effect of `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = "only")` reported visits `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "2", value = "ame", value_include = FALSE)`.
+Conversely, each percentage point increase in soil moisture in the dry deciduous forests was associated with a `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = "only")` increase in reported visits `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "irr", value_include = TRUE)`, with an average marginal effect of `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "ame", value_include = "only")` reported visits `r function_dynamic_text_results(section = "regional", coefficient_option = "exposure_sm", region_option = "4", value = "ame", value_include = FALSE)`.
 
 Finally, our estimates of the incidence rate ratio associated with each additional day of cyclone duration in a given month were consistent between each ecoregion and our full sample.
-Among facilities in the dry deciduous forests, each additional day of cyclone activity was associated with the greatest reduction in reported cases `r function_dynamic_text_results(section = "regional", coefficient_option = "days_with_cyclone", region_option = "4", value = "irr", value_include = TRUE)`.
+Among facilities in the dry deciduous forests, each additional day of cyclone activity was associated with the greatest reduction in reported visits `r function_dynamic_text_results(section = "regional", coefficient_option = "days_with_cyclone", region_option = "4", value = "irr", value_include = TRUE)`.
 
@@
 
-In our multiverse analysis, `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = FALSE)` of `r num_models_multiverse` models (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = FALSE)/as.numeric(num_models_multiverse)*100,0)`%) returned effect estimates for temperature associating a one-degree increase with fewer reported cases of mental or neurological disorders, with `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = 0.01)` (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = 0.01)/as.numeric(num_models_multiverse)*100,0)`%) of those estimates having p-values below 0.01 (Figure \ref{figure_sensitivity_analysis_temp}).
+In our multiverse analysis, `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = FALSE)` of `r num_models_multiverse` models (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = FALSE)/as.numeric(num_models_multiverse)*100,0)`%) returned effect estimates for temperature associating a one-degree increase with fewer reported visits related to mental or neurological disorders, with `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = 0.01)` (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "negative", multiverse_p = 0.01)/as.numeric(num_models_multiverse)*100,0)`%) of those estimates having p-values below 0.01 (Figure \ref{figure_sensitivity_analysis_temp}).
 Only `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "positive", multiverse_p = 0.01)` (`r round(function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_temperature", multiverse_sign = "positive", multiverse_p = 0.01)/as.numeric(num_models_multiverse)*100,0)`%) models returned statistically significant IRR estimates greater than 1; all six models were negative binomial interactive models that excluded month and year fixed effects and were run on data that restricted to the CSB/FSP sample only.
@@
 With respect to soil moisture, only `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "negative", multiverse_p = 0.01) + function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "positive", multiverse_p = 0.01)` of `r num_models_multiverse` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "negative", multiverse_p = 0.01) + function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "positive", multiverse_p = 0.01))/as.numeric(num_models_multiverse)*100,0)`%) returned effect estimates with p-values below 0.01, with `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "positive", multiverse_p = 0.01)` of such models reporting IRRs greater than 1 and `r function_dynamic_text_results(section = "multiverse", coefficient_option = "exposure_sm", multiverse_sign = "negative", multiverse_p = 0.01)` models reporting IRRs smaller than 1 (Figure \ref{figure_sensitivity_analysis_sm}).
-The overwhelming majority of models showed no significant association between soil moisture and monthly case counts, in either direction.
+The overwhelming majority of models showed no significant association between soil moisture and monthly visit counts, in either direction.
 Of models showing statistically significant IRRs of a magnitude greater than 1, all excluded both region and time fixed effects.
 
-Among the `r as.numeric(num_models_multiverse)/3` models that included cyclone activity measured in days per month, `r function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "negative", multiverse_p = FALSE)` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "negative", multiverse_p = FALSE)*100/(as.numeric(num_models_multiverse)/3)),0)`%) reported reduced case counts associated with cyclone duration, compared to `r function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "positive", multiverse_p = FALSE)` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "positive", multiverse_p = FALSE)*100/(as.numeric(num_models_multiverse)/3)),0)`%) showing IRRs below 1 (Figure \ref{figure_sensitivity_analysis_cyclone}).
+Among the `r as.numeric(num_models_multiverse)/3` models that included cyclone activity measured in days per month, `r function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "negative", multiverse_p = FALSE)` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "negative", multiverse_p = FALSE)*100/(as.numeric(num_models_multiverse)/3)),0)`%) reported reduced visit counts associated with cyclone duration, compared to `r function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "positive", multiverse_p = FALSE)` models (`r round((function_dynamic_text_results(section = "multiverse", coefficient_option = "days_with_cyclone", multiverse_sign = "positive", multiverse_p = FALSE)*100/(as.numeric(num_models_multiverse)/3)),0)`%) showing IRRs below 1 (Figure \ref{figure_sensitivity_analysis_cyclone}).
 None of the `r as.numeric(num_models_multiverse)/3` models, however, had a p-value below 0.01.
@@
 
-In our study of health facilities in Madagascar, we investigated how temperature, soil moisture, and exposure to cyclone activity impacted monthly incident cases of mental and neurological disorders reported by `r num_facilities_pretty`  facilities between 2010 and 2020.
+In our study of health facilities in Madagascar, we investigated how temperature, soil moisture, and exposure to cyclone activity impacted monthly counts of patient visits for mental and neurological disorders reported by `r num_facilities_pretty` facilities between 2010 and 2020.
 This study had three major findings.
-First, we found evidence of a statistically significant reduction in reported cases of approximately 4.5% associated with mean monthly temperature, with warmer temperature being, on average, associated with 2 to 3 fewer cases per month.
+First, we found evidence of a statistically significant reduction in reported mental health visits of approximately 4.5% associated with mean monthly temperature, with warmer temperature being, on average, associated with 2 to 3 fewer visits per month.
 According to our multiverse analysis, the statistically significant inverse association we observed was robust to numerous specifications, while our subgroup analysis indicated that this association was primarily localized in the highland subhumid forest ecoregion.
-Second, we found evidence to suggest potential lagged impacts, with higher soil saturation being associated with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in reported case counts in the subsequent quarter.
-We also found evidence of possible effect heterogeneity, with each percentage point increase in soil moisture leading to an *elevation* of cases in the dry deciduous forest ecoregion and a *decrease* in cases in the highland subhumid forests.
-Third, while our lagged models and multiverse analysis suggested the possibility of a negative relationship between cyclone activity and incident case counts reported in Madagascar, the marginal effects associated with cyclone duration were negligible, and we did not observe sufficient statistically significant evidence to reject the null assumption of no association at a level of 0.01.
-
-It is important to note in our interpretation of these findings that the true relationship between reported mental health cases and actual cases of mental disorders is not well understood, particularly in Madagascar, where there is no epidemiological data on the prevalence or distribution of mental disorders in the general population.
-The changes in reported cases could reflect changes in the actual cases of mental disorders, but could also result from the influence of CCEs on help-seeking behavior, diagnostic capacity, or other factors.
+Second, we found evidence to suggest potential lagged impacts, with higher soil saturation being associated with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in reported visit counts in the subsequent quarter.
+We also found evidence of possible effect heterogeneity, with each percentage point increase in soil moisture leading to an *elevation* of visits in the dry deciduous forest ecoregion and a *decrease* in visits in the highland subhumid forests.
+Third, while our lagged models and multiverse analysis suggested the possibility of a negative relationship between cyclone activity and mental health visits reported in Madagascar, the marginal effects associated with cyclone duration were negligible, and we did not observe sufficient statistically significant evidence to reject the null assumption of no association at a level of 0.01.
+
+It is important to note in our interpretation of these findings that the true relationship between reported mental health visits and actual cases of mental disorders is not well understood, particularly in Madagascar, where there is no epidemiological data on the prevalence or distribution of mental disorders in the general population.
+The changes in mental health visits could reflect changes in the actual cases of mental disorders but could also result from the influence of CCEs on help-seeking behavior, diagnostic capacity, or other factors.
 Additionally, it has been widely recognized that the majority individuals with mental disorders often do not receive any mental health treatment, particularly in low-income settings.
@@
 
-With these caveats in mind, our results concerning an inverse relationship between temperature and recorded cases of mental and neurological disorders are nonetheless surprising and run counter to our expectation, given that a robust body of literature has documented that heat and heat waves have a harmful effect on mental health outcomes[@thompsonAssociationsHighAmbient2018] and general aspects such as mood,[@connollyItMildNot2013] life satisfaction,[@maddisonImpactClimateLife2011] and happiness.[@rehdanzClimateHappiness2005]
+With these caveats in mind, our results concerning an inverse relationship between temperature and visits related to mental and neurological disorders are nonetheless surprising and run counter to our expectation, given that a robust body of literature has documented that heat and heat waves have a harmful effect on mental health outcomes[@thompsonAssociationsHighAmbient2018] and general aspects such as mood,[@connollyItMildNot2013] life satisfaction,[@maddisonImpactClimateLife2011] and happiness.[@rehdanzClimateHappiness2005]
 
 Research in subtropical regions, however, has found that the association between temperature and mental disorders is likely non-linear, with both extreme cold and extreme heat being associated with harmful effects on mental morbidity.[@zhangEffectTemperatureCausespecific2020] Degree increases in temperature, therefore, could show a protective effect in colder months, resulting in an overall inverse association between temperature and reported cases in a sample with few extremely warm months.
-This is consistent with our marginal effect estimates, which show the greatest reduction in case counts being associated with degree increases at the coldest temperatures.
+This is consistent with our marginal effect estimates, which show the greatest reduction in visit counts being associated with degree increases at the coldest temperatures.
 In addition, this explanation would be consistent with our subgroup analysis, which found that the protective effect of warmer temperatures was observed only among facilities in the central high plateau—where temperatures are generally cooler than those in the surrounding lowlands.
@@
 
-Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we observed a significant association of higher soil moisture and cases of mental health complaints in the following quarter, echoing similar findings from U.S.
+Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we observed a significant association of higher soil moisture and visits for mental health complaints in the following quarter, echoing similar findings from U.S.
 meteorological data linking higher precipitation with worsened mental health.[@obradovichEmpiricalEvidenceMental2018] In addition, our subgroup analysis also indicated significant and diverging effects among different ecoregions.
-In particular, we found that greater soil moisture was associated with higher cases reported in the eastern lowlands and the northern dry deciduous forests, which echoes the geographic concentration of flood risk in Madagascar.[@rakotoarisonSpatialAnalysisRisks2021] Conversely, the observed (though statistically modest) reduction in cases associated with higher soil moisture in the desert and xeric shrublands overlaps with the concentration of drought risk, where increased soil moisture could be taken as an indicator of reduced drought vulnerability.
+In particular, we found that greater soil moisture was associated with more visits reported in the eastern lowlands and the northern dry deciduous forests, which echoes the geographic concentration of flood risk in Madagascar.[@rakotoarisonSpatialAnalysisRisks2021] Conversely, the observed (though statistically modest) reduction in visits associated with higher soil moisture in the desert and xeric shrublands overlaps with the concentration of drought risk, where increased soil moisture could be taken as an indicator of reduced drought vulnerability.
 It is important to note, however, that the time frame of available GESIS data excludes the most severe period of the ongoing drought in Madagascar, limiting our ability to directly study the impact of the current crisis on population mental health in this analysis.
@@
 
-Madagascar’s wet season is marked by frequent tropical storms and cyclones—the intensification of which has been linked to rising temperatures in the Indian Ocean.[@ottoClimateChangeIncreased2022] In the majority of our models in the multiverse analysis, we found that months with greater duration of cyclone activity were associated with *fewer* monthly report cases of mental disorders, though none of these models were significant at the threshold of 0.01.
+Madagascar’s wet season is marked by frequent tropical storms and cyclones—the intensification of which has been linked to rising temperatures in the Indian Ocean.[@ottoClimateChangeIncreased2022] In the majority of our models in the multiverse analysis, we found that months with greater duration of cyclone activity were associated with *fewer* monthly report visits for mental disorders, though none of these models were significant at the threshold of 0.01.
 In numerous studies, cyclones and similar disasters have been found to worsen mental health;[@obradovichEmpiricalEvidenceMental2018] however, these storms may also result in numerous conditions that make access to mental health resources more challenging.
-Disruptions to regular health care services and an intensification of acute health needs [@wangDisruptionExistingMental2008] in the post-disaster period could result in barriers to receiving care for incident mental disorders,[@shultzEpidemiologyTropicalCyclones2005] which would be consistent with a reduction in reported cases despite a rise in mental distress.
-
-Failure to observe effect heterogeneity in our subgroup analysis of the association of cyclone activity with reported case counts likely is due, in part, to our specification choice to define exposure to cyclone activity without geographic variation in intensity.
+Disruptions to regular health care services and an intensification of acute health needs [@wangDisruptionExistingMental2008] in the post-disaster period could result in barriers to receiving care for incident mental disorders,[@shultzEpidemiologyTropicalCyclones2005] which would be consistent with a reduction in reported visits despite a rise in mental distress.
+
+Failure to observe effect heterogeneity in our subgroup analysis of the association of cyclone activity with reported monthly visits likely is due, in part, to our specification choice to define exposure to cyclone activity without geographic variation in intensity.
 While we felt justified in opting for a simplified indicator, given that storms in Madagascar typically impact the whole of the island, a more nuanced (but data-hungry) approach could define exposure with greater geographic precision based on additional climate metrics, including peak wind, rainfall, and distance from the storm’s track.[@andersonExposureAssessmentTropical2022]
@@
 Despite these limitations, our study has important implications for future research on the relationship between climate change exposures and population mental health.
-By leveraging, reported cases from over three thousand health facilities over ten years, utilizing the most comprehensive sources of climate data available, and linking the two via a rigorous, multistep geolocating process, our analysis demonstrates how routine health system data may offer valuable insights, particularly when other epidemiological data are not available.
+By leveraging reported visits from over three thousand health facilities over ten years, utilizing the most comprehensive sources of climate data available, and linking the two via a rigorous, multistep geolocating process, our analysis demonstrates how routine health system data may offer valuable insights, particularly when other epidemiological data are not available.
 As one of the only studies to investigate mental health and climate in Africa using national HMIS data, our findings also underscore the need for further research to understand the relationships and pathways between changing climate and population mental health, particularly countries most vulnerable to climate change.

### 2023-03-11 paper3.Rmd
Revisions throughout and final version for External Reader

--- 2023-03-02 paper3.Rmd
@@
 
-paper3_abstract <- paste0("For searches related to depression, we observe a sustained decline in search density of ",
+paper3_abstract <- paste0("For searches related to depression, I observed a sustained decline in search density of ",
              function_dynamic_text_results("main","depression", "slope" , TRUE, TRUE), " and an immediate downward level shift of ",
              function_dynamic_text_results("main","depression", "intercept", TRUE),
-                          " relative to comparable symptom searches. For anxiety, we estimated a similar slope change of",
+             " relative to comparable symptom searches. For anxiety, I estimated a similar slope change of ",
              function_dynamic_text_results("main","anxiety", "slope", TRUE), 
@@
  ".
-We did not observe significant variations across predominately Democrat or Republican voting states and counties, and our findings were robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
+I did not observe significant variations across predominately Democrat or Republican voting states and counties, and the findings were robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
 
@@
 
-\emph{Daniel Arias, Jessica Cohen, Karestan Koenen, Margaret McConnell, Stéphane Verguet}
-
-\vspace{24pt}
+\emph{Daniel Arias}
+
+\vspace{12pt}
 
@@
 
-{\bf Methods:} We utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety in the U.S..
-We examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptoms compared with physical health symptoms, and estimated associations between vaccine announcement and changes in mental health symptom search density.
-We adjusted for state, month, and weekday effects, and applied numerous sensitivity analyses to assess the robustness of our findings.
-To explore heterogeneity by predominate political affiliation, we also tested whether our estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
-
-{\bf Findings and interpretation:} Under our main model specification, we observed reduced search density for depression and anxiety associated with the announcement of vaccine safety data.
-`r paper3_abstract` If symptom search density echoes population health, our results would indicate that announcements regarding the development of safe and effective COVID-19 vaccines led to a robust and sustained improvement in mental health.
-Our findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
+{\bf Methods:} I utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety in U.S.
+states and counties.
+I examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptoms compared with physical health symptoms, and estimated associations between vaccine announcement and changes in mental health symptom search density.
+I adjusted for state, month, and weekday effects, and applied numerous sensitivity analyses to assess the robustness of the findings.
+To explore heterogeneity by predominate political affiliation, I also tested whether the estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
+
+{\bf Findings and interpretation:} Under the main model specification, I observed reduced search density for depression and anxiety associated with the announcement of vaccine safety data.
+`r paper3_abstract` If symptom search density echoes population health, the results would indicate that announcements regarding the development of safe and effective COVID-19 vaccines led to a robust and sustained improvement in mental health.
+These findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
 
@@
 ## Introduction
-The COVID-19 pandemic has had a profound effect on the mental health and wellbeing of individuals worldwide.
-Studies from Australia,[@batterhamTrajectoriesDepressionAnxiety2021] China,[@ahmedEpidemicCOVID19China2020; @gaoMentalHealthProblems2020; @hwangLonelinessSocialIsolation; @leiComparisonPrevalenceAssociated2020; @liuPrevalencePredictorsPTSS2020; @qiuNationwideSurveyPsychological2020; @wangImmediatePsychologicalResponses2020; @wangStudyPublicPsychological2021; @wangPsychologicalDistressCoping2020; @zhangImpactCOVID19Pandemic2020] Denmark,[@sonderskovDepressiveStateDenmark] Europe,[@hajekPrevalenceDeterminantsProbable2022] Iran,[@moghanibashi-mansouriehAssessingAnxietyLevel2020] Ireland,[@hylandAnxietyDepressionRepublic2020]  Italy,[@mazzaNationwideSurveyPsychological2020; @mocciaAffectiveTemperamentAttachment2020] Nepal,[@samadarshiOnlineSurveyFactors2020] New Zealand,[@gasteigerDepressionAnxietyStress2021; @lawRiskFactorsChanges2022] Spain,[@gonzalez-sanguinoMentalHealthConsequences2020; @ozamiz-etxebarriaStressAnxietyDepression2020] Turkey[@ozdinLevelsPredictorsAnxiety2020],  the United States,[@jiaNationalStateTrends2021, p.
-2020–2021; @kujawaExposureCOVID19Pandemic2020] and the United Kingdom[@dettmannInvestigatingPrevalenceAnxiety2022] have reported high levels of anxiety (6-51%), depression (15-48%), and post-traumatic stress disorder (7-54%) associated with the onset of the pandemic.
+The COVID-19 pandemic has had a profound effect on the mental health and well-being of individuals worldwide.
+Studies from Australia,[@batterhamTrajectoriesDepressionAnxiety2021] China,[@ahmedEpidemicCOVID19China2020; @gaoMentalHealthProblems2020; @hwangLonelinessSocialIsolation; @leiComparisonPrevalenceAssociated2020; @liuPrevalencePredictorsPTSS2020; @qiuNationwideSurveyPsychological2020; @wangImmediatePsychologicalResponses2020; @wangStudyPublicPsychological2021; @wangPsychologicalDistressCoping2020; @zhangImpactCOVID19Pandemic2020] Denmark,[@sonderskovDepressiveStateDenmark] Europe,[@hajekPrevalenceDeterminantsProbable2022] Iran,[@moghanibashi-mansouriehAssessingAnxietyLevel2020] Ireland,[@hylandAnxietyDepressionRepublic2020] Italy,[@mazzaNationwideSurveyPsychological2020; @mocciaAffectiveTemperamentAttachment2020] Nepal,[@samadarshiOnlineSurveyFactors2020] New Zealand,[@gasteigerDepressionAnxietyStress2021; @lawRiskFactorsChanges2022] Spain,[@gonzalez-sanguinoMentalHealthConsequences2020; @ozamiz-etxebarriaStressAnxietyDepression2020] Turkey[@ozdinLevelsPredictorsAnxiety2020], the United Kingdom[@dettmannInvestigatingPrevalenceAnxiety2022], and the United States[@jiaNationalStateTrends2021, p.
+2020–2021; @kujawaExposureCOVID19Pandemic2020] have reported high levels of anxiety (6-51%), depression (15-48%), and post-traumatic stress disorder (7-54%) associated with the onset of the pandemic.
 In the United States, approximately four in ten adults reported experiencing symptoms of anxiety or depression in December 2020—a four-fold increase from January-June 2019.[@panchalImplicationsCOVID19Mental2021, p.
@@
 While this literature suggests that receiving a COVID-19 vaccine can improve mental health, the potential mental health benefits of announcements regarding the development of vaccines have received comparatively less attention.[@cotfasLongestMonthAnalyzing2021; @kesselEffectCOVID19Pandemic2023] In the context of a deadly pandemic, the announcement of a safe and effective vaccine could be a powerful signal, providing a psychological boost that the worst might soon be mitigated.
-Studying how population mental health may have been impacted by the release of vaccine efficacy and safety trial data may provide insights into how emotional well-being changed throughout the pandemic in response to these signals, which, in turn, could inform public health communication and contribute to our understanding of how the public responds to information about vaccines—a necessary understanding for increasing vaccine uptake and trust in public health responses.
+Studying how population mental health may have been impacted by the release of vaccine efficacy and safety trial data may provide insights into how emotional well-being changed throughout the pandemic in response to these signals, which, in turn, could inform public health communication and contribute to the understanding of how the public responds to information about vaccines—a necessary understanding for increasing vaccine uptake and trust in public health responses.
 
@@
 
-Our study analyzes whether news announcements (in November 2020) regarding the imminent availability of safe and effective COVID-19 vaccines impacted population mental health—even before these vaccines were made available to the public.
-Using Google search density data, we applied interrupted time series approaches to investigate how these announcements might have affected search trends for mental health symptoms in the U.S.
-and five other countries where data were available: Australia, the United Kingdom, Ireland, New Zealand, Singapore.
-Owing to emerging evidence that political ideology may be a predictor of confidence in public health and vaccine hesitancy,[@debusPoliticalIdeologyVaccination2021; @baumgaertnerInfluencePoliticalIdeology2018; @stolerSociopoliticalPsychologicalCorrelates2022] we further explored whether changes in search trends for mental health symptoms varied across U.S.
-states and counties that predominantly voted Democrat vs.
-Republican in the 2020 presidential election.
-Our findings suggest declines in density for searches related to anxiety and depression in all of the countries examined; in the U.S., these declines were found to be consistent irrespective of political ideology.
+This study analyzes whether news announcements (in November 2020) regarding the imminent availability of safe and effective COVID-19 vaccines impacted population mental health—even before these vaccines were made available to the public.
+Using Google search density data, I applied interrupted time series approaches to investigate how these announcements might have affected search trends for mental health symptoms in the U.S.
+and five other countries where data were available: Australia, Ireland, New Zealand, Singapore, and the United Kingdom.
+Owing to emerging evidence that political ideology may be a predictor of confidence in public health and vaccine hesitancy,[@debusPoliticalIdeologyVaccination2021; @baumgaertnerInfluencePoliticalIdeology2018; @stolerSociopoliticalPsychologicalCorrelates2022] I further explored whether changes in search trends for mental health symptoms varied across U.S.
+states and counties that predominantly voted Democrat versus Republican in the 2020 presidential election.
+These findings suggest declines in density for searches related to anxiety and depression in all of the countries examined; in the U.S., these declines were found to be consistent irrespective of political ideology.
 
@@
 
-We take as our first credible signal of the imminent availability of safe and effective COVID-19 vaccines to be November 16, 2020.
+I took November 16, 2020 as the date of the first credible signal of the imminent availability of safe and effective COVID-19 vaccines.
 On November 9^th^, Pzifer announced that early vaccine trial data showed 90% efficacy[@thomasPfizerEarlyData2020] and on the 16^th^, Moderna announced preliminary results showing 95% efficacy.[@gradyEarlyDataShow2020] While U.S.
@@
 
-We accessed aggregated national and subnational data from Google’s COVID-19 Search Trends Symptoms Dataset [@Wahltinez2020] (hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021.
+I accessed aggregated national and subnational data from Google’s COVID-19 Search Trends Symptoms Dataset [@Wahltinez2020] (hereafter referred to as the symptoms dataset) between January 1, 2020 and April 1, 2021.
 The symptoms dataset provides time series data of search term density, standardized to pairs of health symptoms and regions (e.g., searches for depression in Australia or fever in Cook County, Illinois) and normalized within each pair based on the symptom’s relative popularity.
@@
 
-Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominately English-speaking countries: Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the U.S.
+Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominately English-speaking countries: Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States.
 In the U.S., subnational regions include states and counties.
-Because the aggregated search density data were constructed based on relative search population within each region, we could not compare search density for specific symptoms across different regions; however, comparing search density within regions (or a group of regions) was feasible both over time and across different symptoms.
+Because the aggregated search density data were constructed based on relative search population within each region, I could not compare search density for specific symptoms across different regions; however, comparing search density within regions (or a group of regions) was feasible both over time and across different symptoms.
 
@@
 
-We utilized three levels of region: 1) national level for the six countries; 2) U.S.
-state level data across `r n_states` states and the District of Colombia; and 3) U.S.
-county level across `r n_counties` counties (though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset).
-Following the convention of the symptoms dataset, we will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."
+I utilized three levels of region: 1) national level for the six countries; 2) U.S.
+state level data across `r n_states` states and the District of Columbia; and 3) U.S.
+county level data across `r n_counties` counties (though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset).
+Following the convention of the symptoms dataset, I will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."
 
@@
 
-We obtained county-level presidential election results for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which we used to calculate aggregate county and state votes (including absentee, early, and election day ballots) for each candidate.
+I obtained county-level presidential election results for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which I used to calculate aggregate county and state votes (including absentee, early, and election day ballots) for each candidate.
 The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the winning candidate and the runner up).
-Applying a similar approach as other research into COVID-19 and political party inclination,[@grossmannAllStatesClose2021] we used these margins to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth quintile.
-
-\newpage
+Applying a similar approach as other research into COVID-19 and political party inclination,[@grossmannAllStatesClose2021] I used these margins to sort counties and states into quintiles, such that the 20% most Republican-voting localities appearing in the symptoms dataset were sorted into the first quintile and the 20% most Democratic-voting localities sorted into the fifth quintile.
 
@@
 
-We used an interrupted time series (ITS) approach to model the Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days before the vaccine announcement ($time_0$), $Post_i$ is an indicator variable equal to 1 in the period after the announcement (0 otherwise), $\theta_r$ indicates a series of fixed effects for each region $(r)$, $T^{'}_t\chi$ is a matrix of time fixed effects (i.e., month and day of week), and $\epsilon_{it}$ is an error term.
+I used an interrupted time series (ITS) approach to model the Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days before the vaccine announcement ($time_0$), $Post_i$ is an indicator variable equal to 1 in the period after the announcement (0 otherwise), $\theta_r$ indicates a series of fixed effects for each region $(r)$, $T^{'}_t\chi$ is a matrix of time fixed effects (i.e., month and day of week), and $\epsilon_{it}$ is an error term.
 $\alpha_d$ can be interpreted as a level change associated with the announcement date—that is, the immediate difference in search density for a disease $d$ following November 19, 2020; $\beta_d$—the slope change—can be interpreted as the sustained change in search density in the days following November 16th.
@@
 ```
-We apply this model for all available `r diseases_n` diseases with county-level data.
-As search density may rapidly change in response to new announcements, we trimmed the bandwidth of dates to fit our model to 40 days before and after November 16, 2020.
-
-To control for time-varying confounders which may affect symptom search trends, we applied a controlled interrupted time series (CITS) approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
-
-After reviewing the list of symptoms for which search density data were available, we identified the following `r mh_diseases_n` mental health symptoms: `r paste0(gsub("asperger", "Asperger", gsub("_", " ", printList(toPrint = sort(list_mental_health_symptoms), finalSepWord = "and", midSep = ","))),".")`
-
-For each of these symptoms, $d$, we ran the following model:
+I applied this model for all available `r diseases_n` diseases with county-level data.
+As search density may rapidly change in response to new announcements, I trimmed the bandwidth of dates to fit the model to 40 days before and after November 16, 2020.
+
+To control for time-varying confounders which may affect symptom search trends, I applied a controlled interrupted time series (CITS) approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
+
+After reviewing the list of symptoms for which search density data were available, I identified the following `r mh_diseases_n` mental health symptoms: `r paste0(gsub("asperger", "Asperger", gsub("_", " ", printList(toPrint = sort(list_mental_health_symptoms), finalSepWord = "and", midSep = ","))),".")`
+
+For each of these symptoms, $d$, I ran the following model:
 
@@
 
-Given the high number of observations in our sample, we evaluated significance against an alpha of 0.01, and we constructed 99% confidence intervals (CIs) using heteroskedasticity-robust standard errors.
+Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals (CIs) using heteroskedasticity-robust standard errors.
 
@@
 As with other quasi-experimental methods, it is recommended that the modeling specifications be evaluated using a sensitivity analysis.
-To do so, we defined a list of seven methodological choices concerning data processing and modeling assumptions and interacted these choices to generate all plausible combinations.
+To do so, I defined a list of seven methodological choices concerning data processing and modeling assumptions and interacted these choices to generate all plausible combinations.
 These combinations were then conducted to allow for a multiverse analysis to identify how sensitive effect estimates and CIs were to different methodological choices.
@@
 
-First, we considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, we compared the level of region of aggregated data, using U.S.
+First, I considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, I compared the level of region of aggregated data, using U.S.
 counties, U.S.
 states, and, finally, national trends from the six counties in the sample.
-Third, we evaluated sensitivity to our specification of the bandwidth cut-off around the announcement date, extending it from ±40 days to ±50 and ±60 days.
-Fourth, we toggled whether to account for day of week fixed effects; fifth, we toggled month fixed effects; and sixth, we toggled regional fixed effects (i.e., fixed effects for states in the U.S.
+Third, I evaluated sensitivity to the specification of the bandwidth cut-off around the announcement date, extending it from ±40 days to ±50 and ±60 days.
+Fourth, I toggled whether to account for day of week fixed effects; fifth, I toggled month fixed effects; and sixth, I toggled regional fixed effects (i.e., fixed effects for states in the U.S.
 state level data, fixed effects for counties in the U.S.
@@
 
-The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using our nationally aggregated data.
+The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using the nationally aggregated data.
 This analysis aimed to investigate the extent to which effects observed in U.S.
@@
 The second subgroup analysis applied the CITS approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share.
-Our subgroup analysis comparing CITS effect estimates in blue vs.
-red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
+The subgroup analysis comparing CITS effect estimates in blue versus red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
 
@@
 The Institutional Review Board (IRB) of the Harvard T.H.
-Chan School of Public Health determined that the study was not human subjects research, and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).
+Chan School of Public Health determined that this study was not human subjects research and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).
 
@@
 For most symptoms, search density exhibited negligible differences following the announcement, with small positive level shifts offset by modest negative slope changes.
-For four mental health symptoms, however, we observed relatively large, negative slope changes for searches for anxiety `r function_dynamic_text_results("its","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("its","depression", "slope", value_include = "allnumber")`, major depressive disorder (MDD)`r function_dynamic_text_results("its","major_depressive_disorder", "slope", value_include = "allnumber")`, and attention deficit hyperactivity disorder (ADHD)`r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "slope", value_include = "allnumber")`.
+For four mental health symptoms, however, I observed relatively large, negative slope changes for searches for anxiety `r function_dynamic_text_results("its","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("its","depression", "slope", value_include = "allnumber")`, major depressive disorder (MDD)`r function_dynamic_text_results("its","major_depressive_disorder", "slope", value_include = "allnumber")`, and attention deficit hyperactivity disorder (ADHD)`r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "slope", value_include = "allnumber")`.
 With respect to level shifts, changes for anxiety `r function_dynamic_text_results("its","anxiety", "intercept", value_include = "allnumber")` and depression `r function_dynamic_text_results("its","depression", "intercept", value_include = "allnumber")` were close to zero, while those for MDD `r function_dynamic_text_results("its","major_depressive_disorder", "intercept", value_include = "allnumber")` and ADHD `r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "intercept", value_include = "allnumber")` were approximately 0.3 percentage points.
@@
 
-While our ITS analysis provided suggestive evidence that search density for mental health symptoms might have changed in the post-announcement period, it also highlighted that searches may have generally changed across other diseases at the same time.
-Our CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed our ITS analysis, with most conditions showing level and slope changes close to 0.
-For three conditions, our CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")`, all showing sustained declines.
-All three symptoms had relatively large slope changes in our ITS analysis.
-In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "intercept")`, a decrease double in magnitude compared to the majority of estimates for other symptoms.
-
-```{r figure_cits_outputs, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7, fig.height = 8, fig.align='center', out.width = '95%', fig.scap="Controlled interrupted time series effect estimates on Google Search density by symptom.", out.extra='',  fig.cap="\\label{figure_cits_outputs}Controlled interrupted time series effect estimates (A: slope change per 10 days and B: level shift)  on Google Search density by symptom.
+While the ITS analysis provided suggestive evidence that search density for mental health symptoms might have changed in the post-announcement period, it also highlighted that searches may have generally changed across other diseases at the same time.
+The CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed the ITS analysis, with most conditions showing level and slope changes close to 0.
+For three conditions, the CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")`, all showing sustained declines.
+All three symptoms had relatively large slope changes in the ITS analysis.
+In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "intercept")`, a decrease double in magnitude compared to most estimates for other symptoms.
+
+```{r figure_cits_outputs, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7, fig.height = 8, fig.align='center', out.width = '95%', fig.scap="Controlled interrupted time series effect estimates for Google Search density by symptom.", out.extra='', fig.cap="\\label{figure_cits_outputs}Controlled interrupted time series effect estimates (A: slope change per 10 days and B: level shift) for Google Search density by symptom.
 Effect estimates are represented as thick, horizontal lines in between colored bands, which represent the 99\\% confidence intervals for the estimates.
@@
 
-In both our analyses, search trends for anxiety, depression, and MDD showed potential immediate and sustained declines in density following November 16th.
+In both the analyses, search trends for anxiety, depression, and MDD showed potential immediate and sustained declines in density following November 16th.
 Search density for these three symptoms and the comparison search data for headaches is plotted in Figures \ref{figures_cits_data_anxiety} through \ref{figures_cits_data_mdd} at the level of U.S.
@@
 counties, and international data.
-We observed relatively strong concordance between our CITS estimates and the observed trends in the data, with strong fit to both mental health symptoms and headaches.
-We further observed strong within-week patterns in searches, supporting our inclusion of fixed effects to account for this weekly periodicity.
-
-```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='', fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
+I observed relatively strong concordance between the CITS estimates and the observed trends in the data, with strong fit to both mental health symptoms and headaches.
+I further observed strong within-week patterns in searches, supporting the inclusion of fixed effects to account for this weekly periodicity.
+
+```{r figures_cits_data_anxiety, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 6.8, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for anxiety, by region, as a function of time.", out.extra='', fig.cap="\\label{figures_cits_data_anxiety}Density of Google Search trends for anxiety, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: anxiety in blue and headaches in grey.
-In the first column, data from U.S.
+In the first row, data from U.S.
 states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second column, data from U.S.
-counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
-In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
+In the second row, data from U.S.
+counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
+In the third row, national data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States are shown.
 Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
@@
 
-```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
+```{r figures_cits_data_depression, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 6.8, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for depression, by region, as a function of time.", out.extra='', fig.cap="\\label{figures_cits_data_depression}Density of Google Search trends for depression, by region and as a function of time.
 In each row, search density data for two symptoms are displayed: depression in blue and headaches in grey.
-In the first column, data from U.S.
+In the first row, data from U.S.
 states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second column, data from U.S.
-counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
-In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
+In the second row, data from U.S.
+counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
+In the third row, national data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States are shown.
 Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
@@
 
-```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 7, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='',  fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for MDD, by region and as a function of time.
+```{r figures_cits_data_mdd, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 4.5, fig.height = 6.8, fig.align='center', out.width = '99%', fig.scap="Density of Google Search trends for major depressive disorder (MDD), by region, as a function of time.", out.extra='', fig.cap="\\label{figures_cits_data_mdd}Density of Google Search trends for major depressive disorder (MDD), by region and as a function of time.
 In each row, search density data for two symptoms are displayed: MDD in blue and headaches in grey.
-In the first column, data from U.S.
+In the first row, data from U.S.
 states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second column, data from U.S.
-counties are shown; because of the large number of counties reporting data, county-level search data are shown as daily boxplots.
-In the third column, national data from Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States are shown.
+In the second row, data from U.S.
+counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
+In the third row, national data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States are shown.
 Each graph shows the density of symptom searches on the y-axis, while time is centered and displayed as days prior to and following November 16, 2020 on the x-axis.
@@
 
-Our multiverse analysis further underscored the robustness of our findings concerning the relatively large negative immediate and sustained effects on searches for anxiety and depression, in particular (Figure \ref{fig_multiverse_analysis_all}).
+The multiverse analysis further underscored the robustness of the findings concerning the relatively large negative immediate and sustained effects on searches for anxiety and depression, in particular (Figure \ref{fig_multiverse_analysis_all}).
 For anxiety, all 144 models had negative level shifts and slope changes.
 For depression, all `r function_dynamic_text_results("multiverse","depression", "slope", multiverse_sign = "negative")` models had negative slope changes, of which only `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "positive")` models had any positive level shift.
-For MDD, we similarly observed a universally negative slope change in all `r function_dynamic_text_results("multiverse","major_depressive_disorder", "slope", multiverse_sign = "negative", multiverse_p = FALSE)` models; however, the majority of models showed a positive level shift (`r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "positive", multiverse_p = FALSE)` models), whereas only `r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "negative", multiverse_p = FALSE)` showed a downward level shift.
+For MDD, I similarly observed a universally negative slope change in all `r function_dynamic_text_results("multiverse","major_depressive_disorder", "slope", multiverse_sign = "negative", multiverse_p = FALSE)` models; however, the majority of models showed a positive level shift (`r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "positive", multiverse_p = FALSE)` models), whereas only `r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "negative", multiverse_p = FALSE)` showed a downward level shift.
 
@@
 
-Turning to our subgroup analysis, we found modest evidence of effect estimates of similar magnitude comparing across countries (Figure \ref{fig_international}).
-Across the most populous countries (Australia, the United Kingdom, and the United States), effect estimates were broadly consistent, with wider CIs than our ITS or CITS main analysis results due to the smaller number of observations.
-Negative level shifts and slope changes were more pronounced in New Zealand compared to other countries, while the level shift estimated for searches for depression in Ireland was positive; we caution, however, that owing to the construction of the Google search density data being relative to regions, this may be due to differences in search volume intensity for depression in Ireland and New Zealand compared to other countries, and not due to a strong effect itself.
+Turning to the subgroup analysis, I found modest evidence of effect estimates of similar magnitude comparing across countries (Figure \ref{fig_international}).
+Across the most populous countries (Australia, the United Kingdom, and the United States), effect estimates were broadly consistent, with wider CIs than the ITS or CITS main analysis results due to the smaller number of observations.
+Negative level shifts and slope changes were more pronounced in New Zealand compared to other countries, while the level shift estimated for searches for depression in Ireland was positive; owing to the construction of the Google search density data being relative to regions, this may be due to differences in search volume intensity for depression in Ireland and New Zealand compared to other countries, and not due to a strong effect itself.
 
@@
 
-```{r fig_international, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 6.5, fig.align='center', out.width = '95%',  fig.scap="International CITS effect estimates and confidence intervals by mental health symptom.", out.extra='',  fig.cap="\\label{fig_international}Controlled interrupted time series estimates of changes in search density by mental health related symptom, reported across six countries (Australia, the United Kingdom, Ireland, New Zealand, Singapore, and the United States).
+```{r fig_international, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 7.5, fig.height = 6.5, fig.align='center', out.width = '95%', fig.scap="International CITS effect estimates and confidence intervals by mental health symptom.", out.extra='', fig.cap="\\label{fig_international}Controlled interrupted time series estimates of changes in search density by mental health related symptom, reported across six countries (Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States).
 The top panel reports estimates of associated level shift and the lower panel estimates of the associated slope change.
@@
 
-Results from our analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and MDD as found in our main analysis (Figure \ref{fig_political}).
-This was particularly observed in our analysis of U.S.
+Results from the analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and MDD as found in the main analysis (Figure \ref{fig_political}).
+This was particularly observed in the analysis of U.S.
 state-level data, where confidence intervals for the CITS effect estimates were statistically equivalent across red and blue states.
-In our county-level analysis, however, we observed larger immediate and sustained declines in searches for depression among red counties than blue ones, with minor overlap in confidence intervals.
+In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties than blue ones, with minor overlap in confidence intervals.
 The observed slope change for searches related to depression among red counties was `r function_dynamic_text_results("political", "depression", "slope", region_option = 1)`, compared to `r function_dynamic_text_results("political", "depression", "slope", region_option = 5)` for blue counties.
-Similarly, a more pronounced level shift was observed in red counties than blue ones, `r function_dynamic_text_results("political", "depression", "intercept", region_option = 1)` vs.
-`r function_dynamic_text_results("political", "depression", "intercept", region_option = 5)`, respectively.
+Similarly, a more pronounced level shift was observed in red counties than blue ones, `r function_dynamic_text_results("political", "depression", "intercept", region_option = 1)` versus `r function_dynamic_text_results("political", "depression", "intercept", region_option = 5)`, respectively.
 
@@
  scale_fill_manual(values = c(col_all, col_dem, col_red),
-                    name = "Political ideology")  +
+          name = "Location") +
 
  scale_color_manual(values = c(col_all, col_dem, col_red),
-                     name = "Political ideology")
+           name = "Location")
 
@@
 Using search data from U.S.
-counties, states, and international trends, we applied ITS and CITS modeling approaches to investigate possible associations between these announcements and search density changes.
-We found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
-The declines were relatively large compared to changes in other symptoms, both physical and mental, and a multiverse analysis indicated that our findings were robust to alternative specifications.
+counties, states, and international trends, I applied ITS and CITS modeling approaches to investigate possible associations between these announcements and search density changes.
+I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
+The declines were relatively large compared to changes in other symptoms, both physical and mental, and a multiverse analysis indicated that the findings were robust to alternative specifications.
 
 To interpret these observed changes as reactions to the vaccine safety and efficacy announcements, it is important to evaluate whether they may be responses to other contemporary events.
-We highlight two potential alternatives that coincided with the period under study: the 2020 U.S.
-general election on November 3^rd^ and the observance of the Thanksgiving holiday in the United States on November 26^th^.
-While it is possible that our estimates encompass impacts from these events, data from our subgroup analysis lends support for our interpretation that these alternatives are insufficient to explain the observed declines in search trends for anxiety, depression, and MDD.
+I highlight two potential alternatives that coincided with the period under study: the 2020 U.S.
+presidential election on November 3^rd^ and the observance of the Thanksgiving holiday in the United States on November 26^th^.
+While it is possible that the estimates encompass impacts from these events, data from the subgroup analysis lends support for the interpretation that these alternatives are insufficient to explain the observed declines in search trends for anxiety, depression, and MDD.
 
 With respect to the U.S.
-general election, we would anticipate any post-election decline in mental health related symptoms to be concentrated in the United States, given its domestic importance and the political fervor that surrounded it.
-Similarly, we would expect that impacts of the Thanksgiving holiday would be unique to the U.S., as it is not celebrated by the other nations in the sample and there were no other national holidays observed by those nations at the same time (with the exception of Singapore’s observance of Deepavali on November 14^th^).
-
-In our subgroup analysis comparing Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, we did not observe evidence of U.S.-specific effects, with our analysis showing consistent declines in searches related to anxiety and depression (though these differed in degree).
+presidential election, I would anticipate any post-election decline in mental health related symptoms to be concentrated in the United States, given its domestic importance and the political fervor that surrounded it.
+Similarly, I would expect that impacts of the Thanksgiving holiday would be unique to the U.S., as it is not celebrated by the other nations in the sample and there were no other national holidays observed by those nations at the same time (with the exception of Singapore’s observance of Deepavali on November 14^th^).
+
+In the subgroup analysis comparing Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I did not observe evidence of U.S.-specific effects, with the analysis showing consistent declines in searches related to anxiety and depression across all countries (though these differed in degree).
 Furthermore, the estimated declines in search density in Australia and the United Kingdom—which, along with the U.S., are the most populous nations in the sample—were greater than that of the U.S.
@@
 Further countering the explanation that observed declines in search trends for mental health symptoms were due to the U.S.
-general election are the results from our subgroup analysis comparing blue and red states/counties.
+presidential election are the results from the subgroup analysis comparing blue and red states/counties.
 If voters expressed relief following the election if their candidate was the winner, a greater decline in searches related to anxiety and depression in states and counties would be expected in those that more heavily voted for Joe Biden, the Democratic candidate and subsequent President-elect, than for former President Donald Trump, the Republican candidate.
-This gradient would also echo our hypothesis that, given findings that political ideology may affect receptiveness to vaccination, the announcement of vaccine safety and efficacy would have had a less pronounced effect among Republican vs.
-Democratic voters compared to liberal ones.
-Instead, we observed the opposite: among the counties that most heavily voted for the Republican candidate, the estimated declines in search density for anxiety and depression were larger than in those that most heavily voted Democrat.
-We did, however, observe broad similarities in the confidence intervals of these estimates, such that we did not rule out the possibility that the effects were the same across red and blue counties.
-However, even this finding would be striking, giving the enduring political controversy over vaccination in the U.S.; while subsequent attitudes towards vaccination may show an ideological split by political affiliation, our findings—if taken as a reasonable reflection of individual attitudes—suggest that whatever relief the vaccine announcements brought was shared across the aisle.
-
-Our findings should be interpreted with some limitation in mind.
-First, the aggregated and anonymized nature of our data imposes a constraint to our interpretations, as we are unable to identify whether individual political ideologies were correlated with changes in search trends.
-Instead, we relied on population aggregates that reflect political orientation (i.e., vote share by county and state) as a proxy, focusing on the 20% most Democrat and Republican-voting areas to strengthen the plausibility of this proxy.
-In addition, we highlighted that the use of Google search density as a proxy for population mental health could not be directly validated in our study, as the search data was anonymized and aggregated.
+This gradient would also echo the hypothesis that, given findings that political ideology may affect receptiveness to vaccination, the announcement of vaccine safety and efficacy would have had a less pronounced effect among conservative voters compared to liberal ones.
+Instead, I observed the opposite: among the counties that most heavily voted for the Republican candidate, the estimated declines in search density for anxiety and depression were larger than in those that most heavily voted Democrat.
+I did, however, observe broad similarities in the confidence intervals of these estimates, such that I did not rule out the possibility that the effects were the same across red and blue counties.
+However, even this finding would be striking, giving the enduring political controversy over vaccination in the U.S.; while subsequent attitudes towards vaccination may show an ideological split by political affiliation, the findings—if taken as a reasonable reflection of individual attitudes—suggest that whatever relief the vaccine announcements brought was shared across the aisle.
+
+These findings should be interpreted with some limitations in mind.
+First, the aggregated and anonymized nature of the data imposes a constraint to the interpretations, as it was not possible to identify whether individual political ideologies were correlated with changes in search trends.
+Instead, I relied on population aggregates that reflect political orientation (i.e., vote share by county and state) as a proxy, focusing on the 20% most Democrat and Republican-voting areas to strengthen the plausibility of this proxy.
+In addition, the use of Google search density as a proxy for population mental health could not be directly validated in the study, as the search data was anonymized and aggregated.
 While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and U.S.
-population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective wellbeing and care seeking.
-
-Despite these limitations, our findings suggest that the announcement of COVID-19 vaccine safety and efficacy led to a robust and sustained reduction in Google search density for anxiety and depression, relative to search density prior to the announcements and to searches for other symptoms.
-If symptom search density echoes population health, our results would indicate that these announcements led to an improvement in mental health, an improvement observed across countries and predominant political party inclination.
-Our findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
+population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.
+
+Despite these limitations, the findings suggest that the announcement of COVID-19 vaccine safety and efficacy led to a robust and sustained reduction in Google search density for anxiety and depression, relative to search density prior to the announcements and to searches for other symptoms.
+If symptom search density echoes population health, the results would indicate that these announcements led to an improvement in mental health, an improvement observed across countries and predominant political party inclination.
+These findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
+
+## Acknowledgements
+<!-- Update with names of internal reviewers -->
+
+I thank Jessica Cohen, Karestan Koenen, Margaret McConnell and Stéphane Verguet for their comments on earlier versions of this paper.
+
+### Funding statement
+<!-- Confirm with team -->
+
+This study received no funding.
+
+### Declaration of interests
+<!-- Confirm with team -->
+
+I declare no competing interests.
+
+### Data sharing statement
+<!-- Would be good to provide information on whether the Madagascar mental health data is available -->
+All codes used for the analysis in this article are available on GitHub (https://github.com/darias5/mh_google_search_trends).
 

### 2023-03-11 thesis_final_version.Rmd
Revisions throughout and final version for External Reader

--- 2023-03-11 Arias,-Daniel---Thesis---2023.03.10.Rmd
@@
 In Chapter 2, we focused on Madagascar—a low income country that is among the most vulnerable to the health consequences of climate change—and examine how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones.
-Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities in Madagascar from 2010 to 2020, we conducted an ecological analysis using negative binomial regression.
+Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020, we conducted an ecological analysis using negative binomial regression.
 Our results indicated that warmer temperatures in the cooler central highlands were associated with a decrease in monthly reported visits for mental disorders, while higher soil moisture could lead to an increase in visits, particular in high flood-risk regions and after a three-month lag, indicating potential variation in the impact of climate change on mental health needs and system responses.
 
-In Chapter 3, we investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic.
+In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic.
 Using an interrupted time series approach with search data from U.S.
-counties, states, and international trends, we found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for searches related to anxiety and depression.
+counties, states, and international trends, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression.
 These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.

### 2023-04-24 appendix_2.1.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
 
-The health facility data used in our study were obtained from Madagascar's *Gestion du Système d'Information Sanitaire* (GESIS), a Microsoft Access electronic health management information systems database.
-
-While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in GESIS, case definitions varied across facilities of different levels.
+The health facility data used in our study were obtained from Madagascar's *Gestion du Système d'Information Sanitaire* (\acr{GESIS}), a Microsoft Access electronic health management information systems database.
+
+While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in \acr{GESIS}, case definitions varied across facilities of different levels.
 Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visit by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).
@@
 
-A summary of GESIS data availability is provided in Table S2.1.
+A summary of \acr{GESIS} data availability is provided in Table S2.1.
 
@@
 
-After compiling the GESIS data, we translated the case definitions from French to English. The translations are provided in Table S2.2.
+After compiling the \acr{GESIS} data, we translated the case definitions from French to English. The translations are provided in Table S2.2.
 
@@
 
-Among primary health facilities, we observed that the case definition for mental disorders changed during 2015, alongside the changes in GESIS that enabled disaggregated reporting by sex and greater disaggregation for data by age.
+Among primary health facilities, we observed that the case definition for mental disorders changed during 2015, alongside the changes in \acr{GESIS} that enabled disaggregated reporting by sex and greater disaggregation for data by age.
 
@@
 To address heterogeneity in reporting across primary, district, and regional facilities, our analysis constructed a single, summary outcome measure: any mental or neurological disorders reported in a given month by a given facility, irrespective of age and sex.
-This outcome measure was constructed by grouping our count data by facility and month-year, and then summing the incidence of mental and neurological disorders reported in GESIS within groups, preventing double counting and the inclusion of referrals in the summary measure.
+This outcome measure was constructed by grouping our count data by facility and month-year, and then summing the incidence of mental and neurological disorders reported in \acr{GESIS} within groups, preventing double counting and the inclusion of referrals in the summary measure.
 

### 2023-04-24 appendix_2.2.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
 combination of names (e.g., "Tanambaovatrakaka" vs.
-"Tanambao Vahatrakaka"), hyphenation (e.g, "Ankiabe Salohy" and "Ankiabe-Salohy"), and spelling (e.g., "Mizilo Gare" vs.	"Mizilo Gara").
+"Tanambao Vahatrakaka"), hyphenation (e.g., "Ankiabe Salohy" and "Ankiabe-Salohy"), and spelling (e.g., "Mizilo Gare" vs.	"Mizilo Gara").
 
@@
 We applied an arbitrary restriction to line and polygon groups, such that the length or area, respectively, would not exceed a particular threshold.
-The threshold for length (`r format(as.numeric(length_lim), big.mark = ",")` km.) was selected to be approximately half the distance of one side of a spatial climate resolution tile (~30 km for ERA-5 data).
-The threshold for area (`r format(as.numeric(area_lim), big.mark = ",")` km²) was assigned to be the length threshold, squared.
+The threshold for length (`r format(as.numeric(length_lim), big.mark = ",")` \acr{km}) was selected to be approximately half the distance of one side of a spatial climate resolution tile (~30 \acr{km} for \acr{ERA5} data).
+The threshold for area (`r format(as.numeric(area_lim), big.mark = ",")` \acr{km}²) was assigned to be the length threshold, squared.
 Groups that exceeded their respective thresholds were discarded.
@@
 
-Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` km², with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` km².
-At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` km², all polygon groups fell within the cut-off.
-Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` km, with a maximum distance of `r format(round(n_max_length), big.mark = ",")` km.
-At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` km,  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).
+Among polygon groups, the mean area was `r format(round(n_mean_area_polygons,2), big.mark = ",")` \acr{km}², with a maximum area of `r format(round(n_max_area_polygons), big.mark = ",")` \acr{km}².
+At the threshold of `r format(as.numeric(area_lim), big.mark = ",")` \acr{km}², all polygon groups fell within the cut-off.
+Among line groups, the mean distance between coordinates was `r format(round(n_mean_length,2), big.mark = ",")` \acr{km}, with a maximum distance of `r format(round(n_max_length), big.mark = ",")` \acr{km}.
+At the threshold of `r format(as.numeric(length_lim), big.mark = ",")` \acr{km},  `r format(round(n_length_retained), big.mark = ",")` line groups fell within the cut-off (`r round(as.numeric(n_length_retained)/n_line * 100,0)`% of line groups).
 
@@
 While it would be ideal to obtain precise locations for each facility in our sample, for the purposes of our analysis, an approximate location would be sufficient, given the spatial resolution of the climate data we used.
-The spatial resolution of ERA-5 and ESA-CCI data is approximately 30 km., meaning that all coordinates within a spatial tile of 900 km² will have the same time series for a given variable.
+The spatial resolution of \acr{ERA5} and \acr{ESA CCI} data is approximately 30 \acr{km}, meaning that all coordinates within a spatial tile of 900 \acr{km}² will have the same time series for a given variable.
 Furthermore, neighboring tiles are unlikely to have extraordinarily different time series, underscoring that close approximate locations would likely result in minimal impact to the analysis versus exact coordinates.
@@
 For commune-level facilities, knowing the catchment area may therefore be just as informative as knowing the facility's precise location if the catchment area was sufficiently small.
-Determining a cut-off was, again, arbitrary; to adopt a conservative threshold, we considered a catchment area small if its area was  no greater than `r format(as.numeric(area_lim), big.mark = ",")` km², which corresponded to approximately `r round(as.numeric(area_lim)/(30*30) * 100,0)`% of the area of a climate data spatial resolution tile (Figure \ref{figure_communes_fokontany}).
+Determining a cut-off was, again, arbitrary; to adopt a conservative threshold, we considered a catchment area small if its area was  no greater than `r format(as.numeric(area_lim), big.mark = ",")` \acr{km}², which corresponded to approximately `r round(as.numeric(area_lim)/(30*30) * 100,0)`% of the area of a climate data spatial resolution tile (Figure \ref{figure_communes_fokontany}).
 
@@
        height = 7,
+       bg = "white")
+
+ ggsave(filename = paste0("Figure_24.jpg"),
+    plot = last_plot(),
+    width = 7,
+    height = 6,
     bg = "white")

### 2023-04-24 conclusion.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
 We then applied a value of a statistical life year approach to estimate the associated global economic burden.
-Our findings suggest staggering loses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion USD in 2019.
+Our findings suggest staggering loses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion \acr{USD} in 2019.
 The magnitude of these findings underscores the global scale of impact that mental disorders have and highlights the urgency for research and action to support mental health worldwide.
@@
 In Chapter 3, I examined how search data for health symptoms could, in the absence of high frequency surveillance data, provide insight into changes in population mental health during the COVID-19 pandemic.
-I obtained Google search data from U.S.
-counties, states, and international trends for over 400 symptoms and used these data to study the immediate and sustained impacts of announcements of the development of safe and effective COVID-19 vaccines in November 2020.
+I obtained Google search data from \acr{US} counties, states, and international trends for over 400 symptoms and used these data to study the immediate and sustained impacts of announcements of the development of safe and effective COVID-19 vaccines in November 2020.
 I found that searches for anxiety, depression, and major depressive disorder significantly fell after these announcements, and that this decline continued throughout the subsequent weeks.

### 2023-04-24 frontmatter.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
 
-I am grateful to the many individuals who have supported and encouraged me throughout my doctoral studies
+I am grateful to the many individuals who have supported and encouraged me throughout my doctoral studies.
 
@@
 Across the Charles River are many dear colleagues who have dedicated themselves to ensuring that Harvard feels like home to all its students.
-To Jackie Yun and Janet Daniels at the GSAS Student Center, and to Sheila Thomas, Katie Saibara, and Karina Gonzalez Herrera of the GSAS Office of Equity, Diversity, Inclusion & Belonging, I wish to express my deepest admiration and appreciation.
+To Jackie Yun and Janet Daniels at the Graduate School of Arts and Sciences Student Center, and to Sheila Thomas, Katie Saibara, and Karina Gonzalez Herrera of the Office of Equity, Diversity, Inclusion & Belonging, I wish to express my deepest admiration and appreciation.
 
@@
 *     *     *
+
 \vspace{12pt}
@@
 
-\vspace{12pt}
+\vspace{14pt}
 

### 2023-04-24 intro.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
 Mental health is an essential part of human flourishing.
-As defined by the World Health Organization (WHO), it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community”.[@worldhealthorganizationComprehensiveMentalHealth2013]
+As defined by the \acr{WHO}, it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community”.[@worldhealthorganizationComprehensiveMentalHealth2013]
 
-For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are a leading cause of disability,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] with the Global Burden of Disease (GBD) study estimating that 4.9% of disability-adjusted life years (DALYs) and 14.6% of years lived with disability (YLDs) were attributable to mental disorders in 2019.[@vosGlobalBurden3692020a] Mental disorders are also closely linked to physical health and can be a significant risk factor for premature mortality.[@walkerMortalityMentalDisorders2015] Among patients living with the most severe mental illnesses, premature mortality may reduce life expectancy by as much as 10 to 20 years.[@demooijDyingTooSoon2019]
+For much of the global population, however, attaining this state of mental health is an enduring challenge, with over one billion people worldwide living with a mental or addictive disorder.[@rehmGlobalBurdenDisease2019] Mental disorders are a leading cause of disability,[@charlsonExcessMortalityMental2015; @rehmGlobalBurdenDisease2019] with the \acr{GBD} study estimating that 4.9% of \acr{DALYs} and 14.6% of \acr{YLDs} were attributable to mental disorders in 2019.[@vosGlobalBurden3692020a] Mental disorders are also closely linked to physical health and can be a significant risk factor for premature mortality.[@walkerMortalityMentalDisorders2015] Among patients living with the most severe mental illnesses, premature mortality may reduce life expectancy by as much as 10 to 20 years.[@demooijDyingTooSoon2019]
 
@@
 
-col_light_blue = "deeppink3"
+col_highlight = "#E4007C"
 col_grey = "#CCCCCC"
@@
   scale_fill_manual(name = "",
-                    values = c(col_light_blue, col_grey, col_light_grey)) +
+                    values = c(col_highlight, col_grey, col_light_grey)) +
   theme(legend.position = "bottom",
@@
   theme(legend.position = "none") +
-  scale_fill_manual(values = c(col_light_blue, col_grey))
+  scale_fill_manual(values = c(col_highlight, col_grey))
 
@@
 
+ggsave(filename = paste0("Figure_1.png"), 
+    plot = final_figure, 
+    width = 13.33,
+    height = 6.3,
+    bg = "white")
+
 print(final_figure)
@@
 
-The extant and evolving challenges of global mental health, in turn, entail jeopardy to health systems and to the three intrinsic goals of improving health, responsiveness, and financial protection.[@robertsGettingHealthReform2008] According to the WHO’s Mental Health Atlas report from 2020, mental health system governance, capacity, and integration into routine service delivery is fundamentally lacking across nations of all levels of economic development, with only 15% of countries having functional integration of mental health into primary health care.[@worldhealthorganizationMentalHealthAtlas2021] This lack of service delivery echoes a lack of basic epidemiological data,[@steinCrossnationalEpidemiologySocial2017] constraining research and frustrating efforts to respond to mental health needs.
+The extant and evolving challenges of global mental health, in turn, entail jeopardy to health systems and to the three intrinsic goals of improving health, responsiveness, and financial protection.[@robertsGettingHealthReform2008] According to the \acr{WHO}'s Mental Health Atlas report from 2020, mental health system governance, capacity, and integration into routine service delivery is fundamentally lacking across nations of all levels of economic development, with only 15% of countries having functional integration of mental health into primary health care.[@worldhealthorganizationMentalHealthAtlas2021] This lack of service delivery echoes a lack of basic epidemiological data,[@steinCrossnationalEpidemiologySocial2017] constraining research and frustrating efforts to respond to mental health needs.
 Among nations, the Atlas report highlights widening disparities in health system indicators, with worsened gaps in service availability and public health expenditure for mental health between low- and middle-income countries and high-income peers.
@@
 The papers presented in the subsequent three chapters echo the interdisciplinary nature of global mental health, drawing on a broad range of quantitative methods and applying analytic tools and insights from epidemiology, health economics, and econometrics.
+They further address different dimensions and determinants of population mental health, as illustrated in the conceptual framework shown in Figure \ref{figure_conceptual_framework}, which is based on a model identified by Dykxhoorn et al.[@dykxhoornConceptualisingPublicMental2022]
+
+```{r figure_conceptual_framework, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 8.5, fig.height = 9.5, fig.align='center', out.width = '95%', fig.scap="Conceptual framework for population mental health.", out.extra='', fig.cap="\\label{figure_conceptual_framework}Conceptual framework for population mental health.
+Original design, based on framework from Dykxhoorn, J., Fischer, L., Bayliss, B.
+et al.
+Conceptualising public mental health: development of a conceptual framework for public mental health.BMC Public Health 22, 1407 (2022).
+https://doi.org/10.1186/s12889-022-13775-9.
+Creative Commons Attribution 4.0 International License"}
+
+knitr::include_graphics("conceptual_framework_figure.png")
+
+```
 
 In Chapter 1, we investigated the share of the global burden of disease attributable to mental disorders and its associated economic value.
-We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available GBD data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019.
-Using value of statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion USD.
+We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available \acr{GBD} data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019.
+Using value of statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion \acr{USD}.
 
@@
 In Chapter 3, I investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic.
-Using search data from U.S.
-counties, states, and international trends, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms.
+Using search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms.
 I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.

### 2023-04-24 paper1.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
 
-abstract_sentence2 <- paste0("The economic value associated with this burden is estimated at about USD ",
+abstract_sentence2 <- paste0("The economic value associated with this burden is estimated at about ",
                abstract4,
-               " trillion. ")
+               " trillion United States dollars. ")
 
@@
 
-Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This landmark paper by Bloom and colleagues estimated that the value of losses due to mental disorders was roughly 1.3 trillion USD in 2010 (1.6 trillion USD in 2019) when DALYs were valued at one times GDP per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion USD 2010 (or approximately 3.0 trillion USD in 2019) by 2030.
+Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This landmark paper by Bloom and colleagues estimated that the value of losses due to mental disorders was roughly 1.3 trillion United States dollars (\acr{USD}) in 2010 (1.6 trillion \acr{USD} in 2019) when disability-adjusted life years (\acr{DALYs}) were valued at one times \acr{GDP} per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion \acr{USD} 2010 (or approximately 3.0 trillion \acr{USD} in 2019) by 2030.
 (See Tables S1.1 and S1.2 in Appendix 1 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]
@@
 
-The most recent estimates of morbidity and mortality due to mental disorders come from the Global Burden of Disease (GBD) 2019 study.[@vosGlobalBurden3692020a] The GBD study provides disease burden estimates using DALYs, years of life lost (YLLs), and years lived with disability (YLDs), which are then aggregated within a hierarchical grouping scheme that classifies causes of disability and death at different levels of mutually exclusive and completely exhaustive categories.
-(Mental disorders are a Level 2 condition, nested under noncommunicable diseases (NCDs); see Table S1.3.)
-
-While GBD remains the gold standard for global epidemiologic estimation, the nature of the GBD scheme—in particular, the rationale for grouping certain conditions under mental disorders or not—has been the subject of debate in the literature.[@atunChallengesEstimatingTrue2016; @vigoEstimatingTrueGlobal2016; @whitefordChallengesEstimatingTrue2016] In particular, work by Vigo et al.
-(2016) published in \emph{The Lancet Psychiatry} argues for an expanded classification of mental disorders under the GBD classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders.
-Using data from the 2013 GBD study, Vigo and colleagues re-allocated the entire burden of dementias, epilepsy, migraine, tension-type headache, and self-harm to mental disorders.
-In addition, a third of the burden of musculoskeletal disorders without anatomical correlate (i.e., somatoform disorders with prominent pain) was attributed to mental disorders.[@vigoEstimatingTrueGlobal2016] This reallocation attributed 13% of DALYs to mental disorders, a 6 percentage point increase from the GBD estimate of 7%.
+The most recent estimates of morbidity and mortality due to mental disorders come from the Global Burden of Disease (\acr{GBD}) 2019 study.[@vosGlobalBurden3692020a] The \acr{GBD} study provides disease burden estimates using \acr{DALYs}, years of healthy life lost due to disability (\acr{YLDs}), and \acr{YLLs}, which are then aggregated within a hierarchical grouping scheme that classifies causes of disability and death at different levels of mutually exclusive and completely exhaustive categories.
+(Mental disorders are a Level 2 condition, nested under \acr{NCDs}; see Table S1.3.)
+
+While \acr{GBD} remains the gold standard for global epidemiologic estimation, the nature of the \acr{GBD} scheme—in particular, the rationale for grouping certain conditions under mental disorders or not—has been the subject of debate in the literature.[@atunChallengesEstimatingTrue2016; @vigoEstimatingTrueGlobal2016; @whitefordChallengesEstimatingTrue2016] In particular, work by Vigo et al.
+(2016) published in \emph{The Lancet Psychiatry} argues for an expanded classification of mental disorders under the \acr{GBD} classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders.
+Using data from the 2013 \acr{GBD} study, Vigo and colleagues re-allocated the entire burden of dementias, epilepsy, migraine, tension-type headache, and self-harm to mental disorders.
+In addition, a third of the burden of musculoskeletal disorders without anatomical correlate (i.e., somatoform disorders with prominent pain) was attributed to mental disorders.[@vigoEstimatingTrueGlobal2016] This reallocation attributed 13% of \acr{DALYs} to mental disorders, a 6 percentage point increase from the \acr{GBD} estimate of 7%.
 
@@
 Our aim is to characterize potential underestimation of the burden of mental disorders and to quantify the economic value of this burden under different estimation approaches.
-Specifically, we expand on Vigo et al.[@vigoEstimatingTrueGlobal2016] by capturing premature mortality due to mental disorders using pooled risk ratios of mortality from a systematic review of mental disorders[@walkerMortalityMentalDisorders2015] to determine the population attributable fraction (PAF) of premature mortality.
-Inclusion of premature mortality through the PAF presents a novel composite approach that can more broadly capture attributable morbidity and mortality.
-Using this approach on GBD 2019 estimates, we then apply monetary values to DALYs to reach estimates of the global economic value of the mental burden of disease using a value of a statistical life (VSL) approach similar to that of Bloom and colleagues,[@bloomGlobalEconomicBurden2011] which attempts to capture a population’s willingness to pay to reduce morbidity and mortality associated with illness.
-The VSL approach—in contrast to alternatives such as cost of illness and value of lost output approaches—includes an economic valuation of mortality risk reductions in monetary terms, and thus enables comparison across sectors (beyond the sole health sector) which can motivate decision-making toward ameliorating welfare and societal mental health.
+Specifically, we expand on Vigo et al.[@vigoEstimatingTrueGlobal2016] by capturing premature mortality due to mental disorders using pooled risk ratios of mortality from a systematic review of mental disorders[@walkerMortalityMentalDisorders2015] to determine the \acr{PAF} of premature mortality.
+Inclusion of premature mortality through the \acr{PAF} presents a novel composite approach that can more broadly capture attributable morbidity and mortality.
+Using this approach on \acr{GBD} 2019 estimates, we then apply monetary values to \acr{DALYs} to reach estimates of the global economic value of the mental burden of disease using a \acr{VSL} approach similar to that of Bloom and colleagues,[@bloomGlobalEconomicBurden2011] which attempts to capture a population’s willingness to pay to reduce morbidity and mortality associated with illness.
+The \acr{VSL} approach—in contrast to alternatives such as cost of illness and value of lost output approaches—includes an economic valuation of mortality risk reductions in monetary terms, and thus enables comparison across sectors (beyond the sole health sector) which can motivate decision-making toward ameliorating welfare and societal mental health.
 Our findings suggest that both the epidemiological and economic burden of mental disorders could be larger than previously estimated, and that underestimation would be larger among regions where premature mortality due to mental disorders is greater.
@@
 
-To estimate the economic burden of mental disorders, we first estimate the attributable mental burden of DALYs under various estimation approaches using data from the 2019 GBD study (available from the Global Health Data Exchange at https://ghdx.healthdata.org/gbd-2019).
+To estimate the economic burden of mental disorders, we first estimate the attributable mental burden of \acr{DALYs} under various estimation approaches using data from the 2019 \acr{GBD} study (available from the Global Health Data Exchange at https://ghdx.healthdata.org/gbd-2019).
 Second, we apply a monetary value to a DALY to yield an economic assessment associated with these burden estimates.
@@
 In our analysis, we replicate the approach of Vigo et al.
-(2016) using GBD 2019 estimates, applying a similar re-allocation formula to YLLs, YLDs, DALYs, and deaths.
+(2016) using \acr{GBD} 2019 estimates, applying a similar re-allocation formula to YLLs, YLDs, \acr{DALYs}, and deaths.
 Our approach, however, differs in some key respects.
 
-First, we agree with Whiteford and colleagues in viewing the assigning of the entire burden of suicide and self-harm to mental disorders as an overestimate, and consequently do not reallocate all DALYs due to suicide towards the mental health burden.[@whitefordChallengesEstimatingTrue2016] While it is empirically clear that mental disorders elevate the risk of death by suicide and that the majority of suicides appear to be due to mental disorders,[@bertoloteSuicidePsychiatricDiagnosis2002] we view assigning the entirety of this burden to mental disorders as overinclusive, which we avoid to favor a conservative estimation strategy.
+First, we agree with Whiteford and colleagues in viewing the assigning of the entire burden of suicide and self-harm to mental disorders as an overestimate, and consequently do not reallocate all \acr{DALYs} due to suicide towards the mental health burden.[@whitefordChallengesEstimatingTrue2016] While it is empirically clear that mental disorders elevate the risk of death by suicide and that the majority of suicides appear to be due to mental disorders,[@bertoloteSuicidePsychiatricDiagnosis2002] we view assigning the entirety of this burden to mental disorders as overinclusive, which we avoid to favor a conservative estimation strategy.
 
@@
 
-Following Vigo and colleagues, we replicate reallocations in neurological and musculoskeletal conditions, and further include alcohol and mental use disorders, as these were previously classified under mental disorders within the GBD classification.
+Following Vigo and colleagues, we replicate reallocations in neurological and musculoskeletal conditions, and further include alcohol and mental use disorders, as these were previously classified under mental disorders within the \acr{GBD} classification.
 
 This provides estimates of YLDs due to mental disorders.
-We then estimate the PAF of mortality due to mental disorders, using GBD prevalence estimates and relative risk estimates for natural-cause and unnatural-cause mortality generated from a systematic review and meta-analysis by Walker et al.[@walkerMortalityMentalDisorders2015] A comparison of our allocation approach with those of Vigo et al.
-and the original GBD hierarchical allocation is shown in Table 1.1.
+We then estimate the \acr{PAF} of mortality due to mental disorders, using \acr{GBD} prevalence estimates and relative risk estimates for natural-cause and unnatural-cause mortality generated from a systematic review and meta-analysis by Walker et al.[@walkerMortalityMentalDisorders2015] A comparison of our allocation approach with those of Vigo et al.
+and the original \acr{GBD} hierarchical allocation is shown in Table 1.1.
 
@@
 Overall, the pooled risk of all-cause mortality was 2.2 times higher (95% confidence interval (CI): 2.1-2.3) among people with mental disorders compared to those without.
-Using this relative risk estimate, Walker and colleagues calculated a PAF to estimate that 8 million deaths were due to mental disorders in 2012.
-
-While Walker and colleagues used a global estimate of the worldwide prevalence of mental disorders in their study to calculate the PAF, we use GBD estimates of prevalence to derive both global- and country-level results.
-The PAF for a given disorder d and country c is given by:
+Using this relative risk estimate, Walker and colleagues calculated a \acr{PAF} to estimate that 8 million deaths were due to mental disorders in 2012.
+
+While Walker and colleagues used a global estimate of the worldwide prevalence of mental disorders in their study to calculate the PAF, we use \acr{GBD} estimates of prevalence to derive both global- and country-level results.
+The \acr{PAF} for a given disorder d and country c is given by:
 \[ PAF_{(d,c)}= \frac{p_{(d,c)}\ (RR_d-1)}{1+p_{(d,c)}\ (RR_d-1)}\ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (1.1)\]
@@
 
-We separately estimate the PAF for natural and unnatural causes of mortality.
-Using the calculated PAF estimates, we estimate YLLs attributable to mental disorders by multiplying the PAF by the national burden of mortality.
-For natural causes of death, we conservatively apply the PAF against YLLs attributable to NCDs.
-For unnatural causes of death, we apply the PAF against YLLs due to self-harm and injuries.
-These YLLs are then combined with the YLDs calculated previously to provide DALYs.
+We separately estimate the \acr{PAF} for natural and unnatural causes of mortality.
+Using the calculated \acr{PAF} estimates, we estimate YLLs attributable to mental disorders by multiplying the \acr{PAF} by the national burden of mortality.
+For natural causes of death, we conservatively apply the \acr{PAF} against YLLs attributable to \acr{NCDs}.
+For unnatural causes of death, we apply the \acr{PAF} against YLLs due to self-harm and injuries.
+These YLLs are then combined with the YLDs calculated previously to provide \acr{DALYs}.
 
@@
 
-To estimate the economic cost associated with premature mortality and morbidity tied to mental illnesses, we assigned a monetary value to attributable DALYs.
-VSL approaches assign a monetary value to small reductions in mortality risks.[@robinsonValuingMortalityRisk2019] Drawing from these approaches, Jamison and colleagues have estimated monetary values of statistical life years,[@jamisonGlobalHealth20352013] which Khadka and colleagues recently adapted to quantify the economic value of changing mortality risk by cause of death in low- and middle-income countries (LMICs).[@khadkaEconomicValueChanging2021] While VSL approaches are not meant to assign monetary values to full life years or years lived with illness or disability,[@robinsonValuingMortalityRisk2019] the Copenhagen Consensus has previously implemented the use of GDP per capita as a proxy for the monetary value of a DALY as a standard estimate.[@copenhagenconsensuscenterMethodology] Values of one and three times GDP per capita have been suggested as proxies for the value of a DALY.[@bertramCostEffectivenessThresholds2016; @commissiononmacroeconomicsandhealthMacroeconomicsHealthInvesting2001] Estimates of $1,000 and $5,000 per DALY have been used, with the justification that these would be reasonable and convenient lower and upper values, particularly for low-income and lower-middle income countries.[@jamisonInfectiousDiseaseInjury2013; @jhaBenefitsCostsHealth2018]
-
-Consistent with previous approaches, we use GDP per capita (USD 2019) for our base-case value of a DALY.
-GDP inputs are reported in 2019 USD and obtained from the World Bank’s World Development Indicators; for consistency with our epidemiological inputs, we convert to per capita values using GBD population estimates.
+To estimate the economic cost associated with premature mortality and morbidity tied to mental illnesses, we assigned a monetary value to attributable \acr{DALYs}.
+\acr{VSL} approaches assign a monetary value to small reductions in mortality risks.[@robinsonValuingMortalityRisk2019] Drawing from these approaches, Jamison and colleagues have estimated monetary values of statistical life years,[@jamisonGlobalHealth20352013] which Khadka and colleagues recently adapted to quantify the economic value of changing mortality risk by cause of death in \acr{LMICs}.[@khadkaEconomicValueChanging2021] While \acr{VSL} approaches are not meant to assign monetary values to full life years or years lived with illness or disability,[@robinsonValuingMortalityRisk2019] the Copenhagen Consensus has previously implemented the use of \acr{GDP} per capita as a proxy for the monetary value of a DALY as a standard estimate.[@copenhagenconsensuscenterMethodology] Values of one and three times \acr{GDP} per capita have been suggested as proxies for the value of a DALY.[@bertramCostEffectivenessThresholds2016; @commissiononmacroeconomicsandhealthMacroeconomicsHealthInvesting2001] Estimates of $1,000 and $5,000 per DALY have been used, with the justification that these would be reasonable and convenient lower and upper values, particularly for low-income and lower-middle income countries.[@jamisonInfectiousDiseaseInjury2013; @jhaBenefitsCostsHealth2018]
+
+Consistent with previous approaches, we use \acr{GDP} per capita (\acr{USD} 2019) for our base-case value of a DALY.
+\acr{GDP} inputs are reported in 2019 \acr{USD} and obtained from the World Bank’s World Development Indicators; for consistency with our epidemiological inputs, we convert to per capita values using \acr{GBD} population estimates.
 
@@
 To address parameter uncertainty within each approach, we apply a three-way sensitivity analysis.
-First, following a simple intuitive approach, we incorporate the upper and lower uncertainty intervals (UIs) provided by GBD 2019 for YLLs, YLDs, and DALYs to account for parameter uncertainty.
-Second, we use the upper and lower values of prevalence estimates and of the 95% confidence intervals (CIs) of the pooled relative risk of all-cause mortality from Walker and colleagues in our composite approach.[@walkerMortalityMentalDisorders2015] Third, our lower bound estimates are set to reallocate one sixth of the burden of musculoskeletal disorders proposed by Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] while our upper bound estimates are set to reallocate one half of this burden.
-
-In addition to our base-case economic valuation, we further report our VSL estimates using three times GDP per capita as the value of a DALY.
-(Alternative valuations using values of $1,000 and $5,000, as well as purchasing power parity (PPP)-adjusted GDP per capita, are reported in Tables S1.5 and S1.6 of Appendix 1.)
+First, following a simple intuitive approach, we incorporate the upper and lower \acr{UIs} provided by \acr{GBD} 2019 for \acr{YLLs}, \acr{YLDs}, and \acr{DALYs} to account for parameter uncertainty.
+Second, we use the upper and lower values of prevalence estimates and of the 95% \acr{CIs} of the pooled relative risk of all-cause mortality from Walker and colleagues in our composite approach.[@walkerMortalityMentalDisorders2015] Third, our lower bound estimates are set to reallocate one sixth of the burden of musculoskeletal disorders proposed by Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] while our upper bound estimates are set to reallocate one half of this burden.
+
+In addition to our base-case economic valuation, we further report our \acr{VSL} estimates using three times \acr{GDP} per capita as the value of a DALY.
+(Alternative valuations using values of $1,000 and $5,000, as well as \acr{PPP}-adjusted \acr{GDP} per capita, are reported in Tables S1.5 and S1.6 of Appendix 1.)
 
@@
 
-The Institutional Review Board (IRB) of the Harvard T.H.
+The \acr{IRB} of the Harvard T.H.
 Chan School of Public Health determined that this study was not human subjects research and that additional review was not required (protocol number: IRB20-1946, determined on November 13, 2020).
@@
 
-Rates of DALYs and deaths attributable to mental disorders under the different estimation approaches are presented by GBD region (Figure \ref{figure_gbd_adjusted}).
-Geographically, the composite approach allocated a large portion of DALYs (to mental disorders) in Eastern Europe, North and Latin America, and sub-Saharan Africa.
+Rates of \acr{DALYs} and deaths attributable to mental disorders under the different estimation approaches are presented by \acr{GBD} region (Figure \ref{figure_gbd_adjusted}).
+Geographically, the composite approach allocated a large portion of \acr{DALYs} (to mental disorders) in Eastern Europe, North and Latin America, and sub-Saharan Africa.
 This is largely driven by the inclusion of premature mortality in the composite approach.
-Estimates of DALYs by country income group and GBD region are reported in Table 1.2.
+Estimates of DALYs by country income group and \acr{GBD} region are reported in Table 1.2.
 (Estimates of deaths are reported in Table S1.4-1.6.)
@@
 
-```{r figure_dalys_nation, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="Disability-adjusted life years (DALYs) attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.", out.extra='', fig.cap=paste0("\\label{figure_dalys_nation}Disability-adjusted life years (DALYs) attributable to mental disorders in 2019, by estimation approach, as a share of all DALYs.
+```{r figure_dalys_nation, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="Disability-adjusted life years (DALYs) attributable to mental disorders in 2019, under the composite estimation approach, as a share of all DALYs.", out.extra='', fig.cap=paste0("\\label{figure_dalys_nation}Disability-adjusted life years (DALYs) attributable to mental disorders in 2019, under the composite estimation approach, as a share of all DALYs.
 ATG: Antigua and Barbuda.
@@
 
+estimates_values <- c(1,2,4)
+
+for (z in estimates_values) {
+
 data_temporary <- data_rev_map %>% 
  filter(measure_id == 2) %>% 
- filter(estimate_id == 4) %>%
+ filter(estimate_id == z) %>%
  st_drop_geometry() %>%
@@
                     axis='l')
+
+ggsave(filename = paste0("Figure_2_estimate_",z,".jpg"), 
+    plot = final_figure, 
+    width = 13.33,
+    height = 6.3,
+    bg = "white")
+
+}
+
+if (z == 4) {
+
   main_map_combined
+
+}
 
@@
 
-ggsave(filename = paste0("Figure_1.png"), 
-    plot = last_plot(), 
-    path = resultspath)
-
-    # ,
-    # width = 1689,
-    # height = 1153,
-    # units = "px",
-    # dpi = 320)
+ggsave(filename = paste0("Figure_3_DALY.png"), 
+    plot = dalys, 
+    width = 12,
+    height = 6.3,
+    bg = "white")
+
+ggsave(filename = paste0("Figure_3_YLD.png"), 
+    plot = ylds, 
+    width = 12,
+    height = 6.3,
+    bg = "white")
+
+ggsave(filename = paste0("Figure_3_YLL.png"), 
+    plot = ylls, 
+    width = 12,
+    height = 6.3,
+    bg = "white")
+
+ggsave(filename = paste0("Figure_3_deaths.png"), 
+    plot = deaths, 
+    width = 12,
+    height = 6.3,
+    bg = "white")
 
@@
 GDP: gross domestic product.
-USD: United States dollar.
+USD: United States dollars.
 DALY: disability-adjusted life year.
@@
 
-ggsave(filename = paste0("Figure_2.png"),
-    path = resultspath,
+ggsave(filename = paste0("Figure_4.png"), 
+    plot = last_plot(), 
     width = 8,
-    height = 6)
+    height = 6,
+    bg = "white")
 
@@
 
-Although economic losses do not represent an actual loss to GDP, a sense of the scale can be gained by expressing the economic consequences with respect to GDP.
-Figure \ref{figure_cost_by_region} displays the economic burden of disease due to mental disorders under the three estimation approaches by GBD region, as a percent of regional GDP.
+Although economic losses do not represent an actual loss to \acr{GDP}, a sense of the scale can be gained by expressing the economic consequences with respect to \acr{GDP}.
+Figure \ref{figure_cost_by_region} displays the economic burden of disease due to mental disorders under the three estimation approaches by \acr{GBD} region, as a percent of regional \acr{GDP}.
 (Estimates by absolute values per DALY are provided in Appendix 1, along with mapped data visualizing estimates across all values per DALY.) Across approaches, the greatest change in estimated burden occurs in Eastern Europe, Latin America, North America, and Southern sub-Saharan Africa.
@@
 Put in context of the existing literature, our epidemiological and economic estimates provide two important contributions.
-First, our findings echo in magnitude those of Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] which have highlighted that suicide and premature mortality due to mental disorders are potentially large sources of underestimation in the current GBD classification.
+First, our findings echo in magnitude those of Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] which have highlighted that suicide and premature mortality due to mental disorders are potentially large sources of underestimation in the current \acr{GBD} classification.
 Second, when including these sources of attributable mortality, the economic findings suggest staggering loses.
@@
 
-Our findings add to a growing literature concerning the classification of mental disorders, in particular related to underscoring the importance of including premature mortality attributable to mental disorders in burden conceptualizations.[@vigoBurdenMentalNeurological2020; @vigoEstimatingTrueGlobal2016; @vigoTrueGlobalDisease2022; @whitefordChallengesEstimatingTrue2016] These calls have most recently been emphasized by GBD collaborators who have urged that “the differential mortality gap for individuals with mental disorders needs to be reflected within the GBD framework.”[@gbd2019mentaldisorderscollaboratorsGlobalRegionalNational2022] Our composite approach to assigning attributable mortality presents one potential attempt for acknowledging this differential mortality gap.
+Our findings add to a growing literature concerning the classification of mental disorders, in particular related to underscoring the importance of including premature mortality attributable to mental disorders in burden conceptualizations.[@vigoBurdenMentalNeurological2020; @vigoEstimatingTrueGlobal2016; @vigoTrueGlobalDisease2022; @whitefordChallengesEstimatingTrue2016] These calls have most recently been emphasized by \acr{GBD} collaborators who have urged that “the differential mortality gap for individuals with mental disorders needs to be reflected within the \acr{GBD} framework.”[@gbd2019mentaldisorderscollaboratorsGlobalRegionalNational2022] Our composite approach to assigning attributable mortality presents one potential attempt for acknowledging this differential mortality gap.
 Our economic analysis further provides updated monetary estimates of the burden of mental illness; to our knowledge, this is the first such analysis of the global economic burden of mental disorders in over a decade.
@@
 Our results should, however, be interpreted with several limitations in mind.
-First, our estimation approaches themselves all draw upon modeled data (i.e., GBD estimates).
-While GBD generates descriptions of morbidity and mortality at fine demographic and geographic levels, it is important to emphasize that the sophisticated modeling approaches implemented often draw on (potentially little) available underlying empirical data.[@tichenorMetricPartnershipsGlobal2019] These inputs can be extremely limited for particular diseases and geographical locations, especially so for mental disorders.
-By way of example, the GBD 2019 Data Input Sources Tool retrieves 3,084 separate data sources for mental disorders.
+First, our estimation approaches themselves all draw upon modeled data (i.e., \acr{GBD} estimates).
+While \acr{GBD} generates descriptions of morbidity and mortality at fine demographic and geographic levels, it is important to emphasize that the sophisticated modeling approaches implemented often draw on (potentially little) available underlying empirical data.[@tichenorMetricPartnershipsGlobal2019] These inputs can be extremely limited for particular diseases and geographical locations, especially so for mental disorders.
+By way of example, the \acr{GBD} 2019 Data Input Sources Tool retrieves 3,084 separate data sources for mental disorders.
 Of these, only 60 pertain to sub-Saharan Africa (1.9%) and 58 to South Asia (1.8%).[@instituteforhealthmetricsandevaluationihmeGlobalBurdenDisease] By comparison, of the 6,064 records pertaining to maternal and neonatal disorders, 631 are for sub-Saharan Africa (10.4%) and 270 for South Asia (4.5%).
@@
 While the authors found that the estimates of mortality risk did not vary by region, the limited representation of studies from the world’s most populous and epidemiologically diverse continents is a considerable shortcoming.
-It is possible, for instance, that the relative risk of all-cause mortality associated with mental disorders is lower where the burden of mortality is more heavily concentrated among child, maternal, and infectious diseases, and is higher where the burden is dominated by NCDs.
-Therefore, to reach a conservative estimate of attributable mortality, we separately estimated population attributable fractions for natural and unnatural causes of death and restricted our allocation of YLLs from natural causes to NCDs—meaning no deaths from maternal or infectious diseases were attributed to mental disorders under the composite approach.
-
-Furthermore, our composite approach allocates mortality due to mental disorders by calculating population attributable fractions using the conventional formula, which may be biased in the presence of confounding or effect heterogeneity.[@darrowConfoundingBiasAttributable2011] In particular, the use of adjusted risk ratios (as in the current analysis) may result in anticonservative bias if the crude risk ratios are lower than the adjusted ones.
+It is possible, for instance, that the relative risk of all-cause mortality associated with mental disorders is lower where the burden of mortality is more heavily concentrated among child, maternal, and infectious diseases, and is higher where the burden is dominated by \acr{NCDs}.
+Therefore, to reach a conservative estimate of attributable mortality, we separately estimated \acr{PAF}s for natural and unnatural causes of death and restricted our allocation of YLLs from natural causes to \acr{NCDs}—meaning no deaths from maternal or infectious diseases were attributed to mental disorders under the composite approach.
+
+Furthermore, our composite approach allocates mortality due to mental disorders by calculating \acr{PAF}s using the conventional formula, which may be biased in the presence of confounding or effect heterogeneity.[@darrowConfoundingBiasAttributable2011] In particular, the use of adjusted risk ratios (as in the current analysis) may result in anticonservative bias if the crude risk ratios are lower than the adjusted ones.
 To mitigate the potential for bias, our sensitivity analysis presents results under conservative assumptions for risk ratios and estimates of prevalence and mortality.
@@
 We note that our findings may themselves be an underestimate, as our composite approach excludes deaths due to neonatal, maternal, and infectious diseases attributable to mental disorders.
-However, we observe that conventional estimation approaches may fail to capture large shares of premature mortality attributable to mental health causes, both from self-inflicted and unnatural causes of death and mortality from NCDs.
+However, we observe that conventional estimation approaches may fail to capture large shares of premature mortality attributable to mental health causes, both from self-inflicted and unnatural causes of death and mortality from \acr{NCDs}.
 Capturing this share of the burden emphasizes that mental health is a critical risk factor for premature mortality, as well as a direct source of morbidity.
@@
 
-GBD estimates are available for download from the Global Health Data Exchange and are available freely for non-commercial users under the Open Data Commons Attribution License (https://ghdx.healthdata.org/gbd-2019).
+\acr{GBD} estimates are available for download from the Global Health Data Exchange and are available freely for non-commercial users under the Open Data Commons Attribution License (https://ghdx.healthdata.org/gbd-2019).
 All codes used for the analysis in this article are available on GitHub (https://github.com/darias5/gmh_econ).

### 2023-04-24 paper2.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
       val < 1,
-      paste0(round(val, 3) * 100, "\\% fewer"),
+      paste0(round(1 - val, 3) * 100, "\\% fewer"),
       paste0(round(val - 1, 3) * 100, "\\%")
@@
 
-As empirical evidence increasingly highlights the wide-scale impact of human activities on climate, there is a growing, parallel body of evidence documenting the impacts our changing climate has on human health.[@watts2020ReportLancet2021] Rising temperatures and extreme weather events (including floods, hurricanes, droughts, and fires) have been associated with worsened health outcomes in multiple settings.[@cianconiImpactClimateChange2020a; @rocqueHealthEffectsClimate2021] In particular, these and other climate change-related exposures (CCEs) have been increasingly linked to worsened mental health[@padhyMentalHealthEffects2015 @batterhamSystematicReviewQuantitative2022], with systematic reviews suggesting, among other climate condition impacts, positive associations between high ambient temperatures and mental disorders,[@liuThereAssociationHot2021] drought conditions and suicide,[@stankeHealthEffectsDrought2013] and cyclones and negative mental health outcomes.[@tasdikhasanExploringMentalHealth2020]
-
-Despite the weight of this evidence, few quantitative studies evaluating the effects of climate on population mental health have, to date, taken place in low- and middle-income countries (LMICs),[@sharpeClimateChangeClimaterelated2021] populations that—despite contributing the least to human-driven climate change—are among the most likely to be vulnerable to its impacts.[@bakerProjectingGlobalEmissions2020]
+As empirical evidence increasingly highlights the wide-scale impact of human activities on climate, there is a growing, parallel body of evidence documenting the impacts our changing climate has on human health.[@watts2020ReportLancet2021] Rising temperatures and extreme weather events (including floods, hurricanes, droughts, and fires) have been associated with worsened health outcomes in multiple settings.[@cianconiImpactClimateChange2020a; @rocqueHealthEffectsClimate2021] In particular, these and other \acr{CCEs} have been increasingly linked to worsened mental health[@padhyMentalHealthEffects2015 @batterhamSystematicReviewQuantitative2022], with systematic reviews suggesting, among other climate condition impacts, positive associations between high ambient temperatures and mental disorders,[@liuThereAssociationHot2021] drought conditions and suicide,[@stankeHealthEffectsDrought2013] and cyclones and negative mental health outcomes.[@tasdikhasanExploringMentalHealth2020]
+
+Despite the weight of this evidence, few quantitative studies evaluating the effects of climate on population mental health have, to date, taken place in low- and middle-income countries (\acr{LMICs}),[@sharpeClimateChangeClimaterelated2021] populations that—despite contributing the least to human-driven climate change—are among the most likely to be vulnerable to its impacts.[@bakerProjectingGlobalEmissions2020]
 
 Among low-income countries most vulnerable to the health consequences of climate change is Madagascar, a nation that generates one percent *of* one percent of global carbon dioxide emissions.
-Worsening CCEs in Madagascar (primarily in the form of droughts, floods, and cyclones) are likely to exacerbate endemic, climate-sensitive threats to health, including malnutrition and malaria.[@rakotoarisonAssessmentRiskVulnerability2018] In particular, persistent drought conditions in recent years have led to extensive food insecurity.[@adamtaylorMadagascarHeadedClimate] Though there is debate concerning the extent to which human activity is directly responsible for Madagascar's current drought,[@harringtonAttributionSevereLow; @zhongManyDimensionsDrought2021] the extremity of the situation has led some observers to classify conditions in Madagascar as the first climate change famine in history.[@worldfoodprogrammeMadagascarSevereDrought2021]
-
-Understanding how both incremental and extreme changes in climate impact population mental health is critical to gauging the full extent to which CCEs impact human health and well-being under a multidisciplinary approach to population health.[@berryCaseSystemsThinking2018] This understanding is particularly important in contexts such as Madagascar, where climate conditions are already demonstrating pronounced pressures on economic, social, and physical well-being.
+Worsening \acr{CCEs} in Madagascar (primarily in the form of droughts, floods, and cyclones) are likely to exacerbate endemic, climate-sensitive threats to health, including malnutrition and malaria.[@rakotoarisonAssessmentRiskVulnerability2018] In particular, persistent drought conditions in recent years have led to extensive food insecurity.[@adamtaylorMadagascarHeadedClimate] Though there is debate concerning the extent to which human activity is directly responsible for Madagascar's current drought,[@harringtonAttributionSevereLow; @zhongManyDimensionsDrought2021] the extremity of the situation has led some observers to classify conditions in Madagascar as the first climate change famine in history.[@worldfoodprogrammeMadagascarSevereDrought2021]
+
+Understanding how both incremental and extreme changes in climate impact population mental health is critical to gauging the full extent to which \acr{CCEs} impact human health and well-being under a multidisciplinary approach to population health.[@berryCaseSystemsThinking2018] This understanding is particularly important in contexts such as Madagascar, where climate conditions are already demonstrating pronounced pressures on economic, social, and physical well-being.
 
@@
 In this ecological study, we investigated the association of climate conditions and population mental health in Madagascar between 2010 and 2020 using routine health system data from Madagascar’s Ministry of Public Health.
-The use of health system data enabled us to indirectly evaluate the extent to which existing public health data may already be showing signals of CCEs, which may aid efforts to prevent and mitigate mental health stressors and better design systemic responses to mental health needs.
-
-As a measure of population mental health, we considered facility-level monthly reported visits related to mental disorders; in terms of exposure, we explored the predictive association of three CCEs with incident mental health visits: mean monthly ambient air temperature, mean monthly soil moisture, and monthly cyclone activity.
+The use of health system data enabled us to indirectly evaluate the extent to which existing public health data may already be showing signals of \acr{CCEs}, which may aid efforts to prevent and mitigate mental health stressors and better design systemic responses to mental health needs.
+
+As a measure of population mental health, we considered facility-level monthly reported visits related to mental disorders; in terms of exposure, we explored the predictive association of three \acr{CCEs} with incident mental health visits: mean monthly ambient air temperature, mean monthly soil moisture, and monthly cyclone activity.
 As exposure to these stressors could involve a delay in onset of mental health symptoms and subsequent care seeking, we further explored whether exposures in prior months were associated with monthly reported visits in subsequent ones.
@@
 
-To analyze the impact of climate on population mental health in Madagascar, we first obtained health management information system (HMIS) data through a collaboration with the Madagascar Ministère de la Santé Publique.
-We then obtained gridded temperature and soil moisture data from the European ReAnalysis (ERA5)[@copernicusclimatechangeservicec3sFifthGenerationECMWF2017] and the European Space Agency’s Climate Change Initiative (ESA CCI),[@europeanspaceagencyEuropeanSpaceAgency2022] respectively.
-Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@wikipediaSouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the National Oceanic and Atmospheric Administration (NOAA)[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021] for accuracy.
+To analyze the impact of climate on population mental health in Madagascar, we first obtained \acr{HMIS} data through a collaboration with the Madagascar Ministère de la Santé Publique.
+We then obtained gridded temperature and soil moisture data from the \acr{ERA5}[@copernicusclimatechangeservicec3sFifthGenerationECMWF2017] and the \acr{ESA CCI},[@europeanspaceagencyEuropeanSpaceAgency2022] respectively.
+Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@wikipediaSouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the \acr{NOAA}[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021] for accuracy.
 
@@
 Madagascar’s health information system provided facility-level data on counts of disease incidence summarized and reported monthly.
-Prior to 2019, this system was the Gestion du Système d'Information Sanitaire (GESIS); in early 2019, the system transitioned to using District Health Information Software 2 (DHIS2).[@measureevaluationStrengtheningHealthInformation2019]
-
-Among facilities reporting any mental health data between 2010 and 2020, data were obtained from `r num_facilities_CSB` public and private primary health centers (known as Centres Santé de Base or CSBs and Formations Sanitaires Privées de Base or FSBs, respectively), `r num_facilities_CHD` district referral hospitals (CHDs), `r num_facilities_CHRR_CHU` regional referral hospitals (CHRRs) and university hospitals (CHUs), for a total of `r num_facilities_pretty` uniquely-identified facilities in our sample.
-
-Exploratory data analysis indicated that the classification and reporting of counts of mental disorders in GESIS varied across types of facilities in their level of detail.
+Prior to 2019, this system was the \acr{GESIS}; in early 2019, the system transitioned to using \acr{DHIS2}.[@measureevaluationStrengtheningHealthInformation2019]
+
+Among facilities reporting any mental health data between 2010 and 2020, data were obtained from `r num_facilities_CSB` public and private primary health centers, known as Centres Santé de Base or CSBs and Formations Sanitaires Privées de Base or FSBs, respectively), `r num_facilities_CHD` district referral hospitals (CHDs), `r num_facilities_CHRR_CHU` regional referral hospitals (CHRRs) and university hospitals (CHUs), for a total of `r num_facilities_pretty` uniquely-identified facilities in our sample.
+
+Exploratory data analysis indicated that the classification and reporting of counts of mental disorders in \acr{GESIS} varied across types of facilities in their level of detail.
 Among CHD facilities, incidence of mental disorders was aggregated with neurological disorders (coded as “neuro psychiatric disorders”), while CHRR and CHU facilities reported more detailed counts of specific mental disorders, such as depression, personality disorders, and schizophrenia.
@@
 To retrieve spatial climate data for the facilities in our sample, it was first necessary to geocode facilities to obtain their latitude and longitude.
-Facility data from GESIS included limited geospatial information.
+Facility data from \acr{GESIS} included limited geospatial information.
 While exact facility coordinates were not available, information on the relevant administrative unit served by a facility was included in the data (e.g., regions for CHRRs, districts for CHDs, and communes for CSBs).
@@
 
-Among the remaining facilities, an additional `r format(as.numeric(n_matched_facilities_RHINO), big.mark = ",")` primary facilities were matched to coordinates from a spatial inventory of `r format(as.numeric(n_facilities_rhino), big.mark = ",")` coordinates obtained from the Routine Health Information Network (RHINO),[@rhinovisiondecisionsupportsystemMadagascarDecisionSupport] which supports an open source database of health facility data in conjunction with the United States Agency for International Development, the government of Madagascar, and other stakeholders.
+Among the remaining facilities, an additional `r format(as.numeric(n_matched_facilities_RHINO), big.mark = ",")` primary facilities were matched to coordinates from a spatial inventory of `r format(as.numeric(n_facilities_rhino), big.mark = ",")` coordinates obtained from the \acr{RHINO},[@rhinovisiondecisionsupportsystemMadagascarDecisionSupport] which supports an open source database of health facility data in conjunction with the \acr{USAID}, the government of Madagascar, and other stakeholders.
 
@@
 
-An additional `r format(as.numeric(n_centroid), big.mark = ",")` facilities were matched to the centroid of their relevant administrative unit in cases where the unit was less than or equal to `r min(commune_lim, fokontany_lim)` square kilometers, as these administrative units are quite small relative to the spatial resolution of gridded climate data (approximately 900 km²).
+An additional `r format(as.numeric(n_centroid), big.mark = ",")` facilities were matched to the centroid of their relevant administrative unit in cases where the unit was less than or equal to `r min(commune_lim, fokontany_lim)` square \acr{km}, as these administrative units are quite small relative to the spatial resolution of gridded climate data (approximately 900 \acr{km}²).
 Among the remaining facilities, geolocations were manually identified for `r format(n_gps_facilities_searches, big.mark = ",")` facilities using targeted searches, resulting in `r format(as.numeric(n_matched_facilities) + as.numeric(n_matched_facilities_RHINO) + as.numeric(n_centroid) + as.numeric(n_gps_facilities_fuzzy) + as.numeric(n_gps_facilities_searches), big.mark = ",")` of the `r format(num_facilities, big.mark = ",")` facilities (`r round((as.numeric(n_matched_facilities) + as.numeric(n_matched_facilities_RHINO) + as.numeric(n_centroid) + as.numeric(n_gps_facilities_fuzzy) + as.numeric(n_gps_facilities_searches))/as.numeric(num_facilities) * 100,0)`%) in the sample being geolocated.
@@
 To gauge the accuracy of the geolocating process, a subset of 1% of geolocated facilities was selected for validation against manually identified coordinates.
-Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` km, with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` km, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data.
+Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` \acr{km}, with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` \acr{km}, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data.
 Additional detail on the geolocating and validation process is available in Appendix 2.2.
@@
 
-Facility geolocations were then used to retrieve spatially referenced monthly averages of temperature and soil moisture data from ERA5 and ESA CCI, respectively.
-To allow for modelling of lagged associations, data were obtained for both ERA5 and ESA CCI SM from `r earliest_climate_date` to `r latest_climate_date`.
-
-ERA5 is a global atmospheric reanalysis from the European Centre for Medium-Range Weather Forecasts (ECMWF) and is freely available through its Copernicus Climate Change Service (C3S)[@europeanspaceagencyEuropeanSpaceAgency2022].
-The spatial resolution of ERA5 is approximately 30 km, with quality-assured hourly estimates available from 1959 to the present.[@europeanspaceagencyEuropeanSpaceAgency2022] Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation.[@googleearthengineERA5MonthlyAggregates2022] Temperature data was then converted to degrees Celsius.
-
-We obtained soil moisture data from the European Space Agency’s soil moisture dataset (ESA CCI SM), the world’s first and most comprehensive, multi-decade, satellite-observed dataset of global soil moisture.
-The spatial resolution of ESA CCI SM is approximately 26 km, with daily estimates available from 1978 to 2021.
-Using ESA CCI SM active and passive radiometer data, a time series of monthly aggregate values for mean soil moisture—measured as saturation percentage—was constructed from daily observations at each land grid point within Madagascar.
+Facility geolocations were then used to retrieve spatially referenced monthly averages of temperature and soil moisture data from \acr{ERA5} and \acr{ESA CCI}, respectively.
+To allow for modelling of lagged associations, data were obtained for both \acr{ERA5} and \acr{ESA CCI SM} from `r earliest_climate_date` to `r latest_climate_date`.
+
+\acr{ERA5} is a global atmospheric reanalysis from the \acr{ECMWF} and is freely available through its \acr{C3S}[@europeanspaceagencyEuropeanSpaceAgency2022].
+The spatial resolution of \acr{ERA5} is approximately 30 \acr{km}, with quality-assured hourly estimates available from 1959 to the present.[@europeanspaceagencyEuropeanSpaceAgency2022] Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation.[@googleearthengineERA5MonthlyAggregates2022] Temperature data was then converted to degrees Celsius.
+
+We obtained soil moisture data from \acr{ESA CCI SM}, the world’s first and most comprehensive, multi-decade, satellite-observed dataset of global soil moisture.
+The spatial resolution of \acr{ESA CCI SM} is approximately 26 \acr{km}, with daily estimates available from 1978 to 2021.
+Using \acr{ESA CCI SM} active and passive radiometer data, a time series of monthly aggregate values for mean soil moisture—measured as saturation percentage—was constructed from daily observations at each land grid point within Madagascar.
 We then applied nearest neighbor matching to link these time series to our geolocated facilities.
 
-For a location to have soil moisture data available in ESA CCI SM, it must fall within one of 244,243 land grid points.
-For some facilities on Madagascar’s coastline, their location placed them outside of ESA CCI’s spatial coverage, resulting in missing values.
-To address facilities without any soil moisture data, nearest neighbor searching was conducted to identify the nearest land grid point for which ESA CCI SM data would be available; this nearest neighbor’s soil moisture time series data would then be applied to the facility with missing data.
-Within a time series of ESA CCI data for a given location, however, monthly data could still be missing if adequate satellite observation was not recorded anytime during a given month; for these values, we used linear interpolation to address missing data within a time series.
+For a location to have soil moisture data available in \acr{ESA CCI SM}, it must fall within one of 244,243 land grid points.
+For some facilities on Madagascar’s coastline, their location placed them outside of \acr{ESA CCI}’s spatial coverage, resulting in missing values.
+To address facilities without any soil moisture data, nearest neighbor searching was conducted to identify the nearest land grid point for which \acr{ESA CCI SM} data would be available; this nearest neighbor’s soil moisture time series data would then be applied to the facility with missing data.
+Within a time series of \acr{ESA CCI} data for a given location, however, monthly data could still be missing if adequate satellite observation was not recorded anytime during a given month; for these values, we used linear interpolation to address missing data within a time series.
 
 In addition, we obtained data on tropical storms and cyclones in the South-West Indian Ocean for the 2009-2010 to 2020-2021 seasons, inclusive.
-Open source data on tropical cyclones in the south-west Indian Ocean was obtained by scraping information from Wikipedia summaries of each cyclone season, which were originally sourced from alerts issued by Météo-France La Réunion (MFR La Réunion), the World Meteorological Organisation designated Regional Specialized Meteorological Centre (RSMC) for the provision of forecasts and warnings of tropical cyclones in the South-West Indian Ocean.
-To ensure that the compiled data accurately reflected storms in Madagascar during the study period, we cross-referenced these data against storm trajectory data for the South Indian Basin from NOAA.[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021]
+Open source data on tropical cyclones in the south-west Indian Ocean was obtained by scraping information from Wikipedia summaries of each cyclone season, which were originally sourced from alerts issued by \acr{MFR La Réunion}, the \acr{WMO}-designated \acr{RSMC} for the provision of forecasts and warnings of tropical cyclones in the South-West Indian Ocean.
+To ensure that the compiled data accurately reflected storms in Madagascar during the study period, we cross-referenced these data against storm trajectory data for the South Indian Basin from \acr{NOAA}.[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021]
 
@@
 
-Exploratory data analysis highlighted that the variance of monthly facility-level counts of incident mental disorders highly exceeded the mean; consequently, our statistical analysis utilized negative binomial (NB) regression, which is recommended in the case of over-dispersed count data.
+Exploratory data analysis highlighted that the variance of monthly facility-level counts of incident mental disorders highly exceeded the mean; consequently, our statistical analysis utilized \acr{NB} regression, which is recommended in the case of over-dispersed count data.
 
@@
 
-Though CCEs could acutely impact mental health in our sample, we could anticipate that these impacts might not immediately result in changes to monthly case and visit counts, owing to delays in symptom onset, care seeking, and care delivery.
+Though \acr{CCEs} could acutely impact mental health in our sample, we could anticipate that these impacts might not immediately result in changes to monthly case and visit counts, owing to delays in symptom onset, care seeking, and care delivery.
 To test for lagged associations—that is, whether in a given month, climate conditions in prior months were associated with counts of mental disorders—versions of Model 4 were conducted using lagged predictors.
@@
 Owing to the large number of observations in our sample, significance was evaluated against an alpha of 0.01, with 99% confidence intervals reported.
-Coefficients and confidence intervals for our indicators of climate exposure were exponentiated to generated incidence rate ratios (IRRs).
-Confidence intervals were constructed using heteroskedasticity-robust standard errors.
+Coefficients and confidence intervals for our indicators of climate exposure were exponentiated to generated \acr{IRRs}.
+Confidence intervals (\acr{CIs}) were constructed using heteroskedasticity-robust standard errors.
 
@@
 
-To explore potential heterogeneity of our effect estimates, we evaluated Models 1 through 4 among facilities in each of Madagascar's four predominant ecoregions: the lowland, humid forests of the east, the subhumid forests of the Central High Plateau, the desert and xeric shrublands of the south, and the northeastern Dry deciduous forests.
+To explore potential heterogeneity of our effect estimates, we evaluated Models 1 through 4 among facilities in each of Madagascar's four predominant ecoregions: the lowland, humid forests of the east, the subhumid forests of the Central High Plateau, the desert and xeric shrublands of the south, and the northeastern dry deciduous forests.
 (Ecoregions are presented in Figure \ref{figure_ecological_zone}.)
@@
 
-ggsave(filename = paste0("figure_4b.jpg"),
-    plot = last_plot(),
-    path = analysis_figures,
+ggsave(filename = paste0("Figure_5.jpg"),
+    plot = last_plot(),
     width = 8,
@@
 Model 4), with both alternatives included in our multiverse analysis.
-Fourth, we evaluated our decision to account for overdispersion with a NB model by using a Poisson regression framework as an alternative.
+Fourth, we evaluated our decision to account for overdispersion with a \acr{NB} model by using a Poisson regression framework as an alternative.
 Fifth, we evaluated alternative specifications of exposure to cyclone activity, using three options: our binary indicator, our count indicator, and no term for cyclone activity included.
@@
 #### Ethics statement
-The Institutional Review Board (IRB) of the Harvard T.H.
+The \acr{IRB} of the Harvard T.H.
 Chan School of Public Health determined that this study was not human subjects research and that additional review was not required (protocol number: IRB21-1303, determined on October 19, 2021).
@@
 
-ggsave(filename = paste0("figure_1.jpg"),
-    plot = last_plot(),
-    path = analysis_figures,
-    width = 16,
+ggsave(filename = paste0("Figure_6a.jpg"),
+    plot = map_a,
+    width = 8,
+    height = 10,
+    bg = "white")
+
+ggsave(filename = paste0("Figure_6b.jpg"),
+    plot = map_b,
+    width = 8,
     height = 10,
@@
 
+ggsave(filename = paste0("Figure_7.jpg"),
+    plot = last_plot(),
+    width = 6,
+    height = 6,
+    bg = "white")
+
 ```
@@
 
+ggsave(filename = paste0("Figure_8.jpg"),
+    plot = last_plot(),
+    width = 10,
+    height = 6,
+    bg = "white")
+
 ```
@@
     height = 5,
+    bg = "white")
+
+ggsave(filename = paste0("Figure_9.jpg"),
+    plot = last_plot(),
+    width = 10,
+    height = 6,
     bg = "white")
@@
 
+ggsave(filename = paste0("Figure_10.jpg"),
+    plot = last_plot(),
+    width = 10,
+    height = 6,
+    bg = "white")
+
 ```
@@
     height = 7)
+
+ggsave(filename = paste0("Figure_11.jpg"),
+    plot = last_plot(),
+    width = 10,
+    height = 6,
+    bg = "white")
 
@@
 
+ ggsave(filename = paste0("Figure_12.jpg"),
+    plot = last_plot(),
+    width = 13.33,
+    height = 6.3,
+    bg = "white")
+
 }
@@
 
+ ggsave(filename = paste0("Figure_13.jpg"),
+    plot = last_plot(),
+    width = 13.33,
+    height = 6.3,
+    bg = "white")
+
 }
@@
 
+ ggsave(filename = paste0("Figure_14.jpg"),
+    plot = last_plot(),
+    width = 13.33,
+    height = 6.3,
+    bg = "white")
+
 }
@@
 It is important to note in our interpretation of these findings that the true relationship between reported mental health visits and actual cases of mental disorders is not well understood, particularly in Madagascar, where there is no epidemiological data on the prevalence or distribution of mental disorders in the general population.
-The changes in mental health visits could reflect changes in the actual cases of mental disorders but could also result from the influence of CCEs on help-seeking behavior, diagnostic capacity, or other factors.
+The changes in mental health visits could reflect changes in the actual cases of mental disorders but could also result from the influence of \acr{CCEs} on help-seeking behavior, diagnostic capacity, or other factors.
 Additionally, it has been widely recognized that the majority individuals with mental disorders often do not receive any mental health treatment, particularly in low-income settings.
@@
 
-Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we observed a significant association of higher soil moisture and visits for mental health complaints in the following quarter, echoing similar findings from U.S.
-meteorological data linking higher precipitation with worsened mental health.[@obradovichEmpiricalEvidenceMental2018] In addition, our subgroup analysis also indicated significant and diverging effects among different ecoregions.
+Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we observed a significant association of higher soil moisture and visits for mental health complaints in the following quarter, echoing similar findings from United States meteorological data linking higher precipitation with worsened mental health.[@obradovichEmpiricalEvidenceMental2018] In addition, our subgroup analysis also indicated significant and diverging effects among different ecoregions.
 In particular, we found that greater soil moisture was associated with more visits reported in the eastern lowlands and the northern dry deciduous forests, which echoes the geographic concentration of flood risk in Madagascar.[@rakotoarisonSpatialAnalysisRisks2021] Conversely, the observed (though statistically modest) reduction in visits associated with higher soil moisture in the desert and xeric shrublands overlaps with the concentration of drought risk, where increased soil moisture could be taken as an indicator of reduced drought vulnerability.
@@
 While these are important caveats in interpreting our results, we assert that there is considerable value in leveraging existing data from national health management information systems to generate epidemiologic evidence.
-The opportunity to employ health information system data is particularly important in countries like Madagascar, where, as in many LMICs, HMIS information is routinely generated but systematically underutilized.[@mbondjiHealthInformationSystems2014]
+The opportunity to employ health information system data is particularly important in countries like Madagascar, where, as in many \acr{LMICs}, \acr{HMIS} information is routinely generated but systematically underutilized.[@mbondjiHealthInformationSystems2014]
 
@@
 By leveraging reported visits from over three thousand health facilities over ten years, utilizing the most comprehensive sources of climate data available, and linking the two via a rigorous, multistep geolocating process, our analysis demonstrates how routine health system data may offer valuable insights, particularly when other epidemiological data are not available.
-As one of the only studies to investigate mental health and climate in Africa using national HMIS data, our findings also underscore the need for further research to understand the relationships and pathways between changing climate and population mental health, particularly countries most vulnerable to climate change.
+As one of the only studies to investigate mental health and climate in Africa using national \acr{HMIS} data, our findings also underscore the need for further research to understand the relationships and pathways between changing climate and population mental health, particularly countries most vulnerable to climate change.
 Finally, our findings and interpretations highlight the importance of local knowledge and collaboration with local ministries in global health research, to make best use of existing data and to foster research to support health system strengthening.
@@
 
-We thank Jessica Cohen, Karestan Koenen, Margaret McConnell, and Stéphane Verguet for their feedback on an earlier version of this paper, as well Marissa Lynn Childs, Angela Jean Rigden, Oladimeji Mudele, and Wenchang Yang for their assistance in initially accessing and processing climate data.
+We thank Jessica Cohen, Margaret McConnell, and Stéphane Verguet for their feedback on an earlier version of this paper, as well Marissa Lynn Childs, Angela Jean Rigden, Oladimeji Mudele, and Wenchang Yang for their assistance in initially accessing and processing climate data.
 

### 2023-04-24 paper3.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
        color = "",
-       title = ifelse(g == "state", "U.S. states", 
-              ifelse(g == "county", "U.S. counties",
+       title = ifelse(g == "state", "US states", 
+              ifelse(g == "county", "US counties",
                   "International data"))) +
@@
 
-{\bf Background:} A key obstacle to studying the impact of policies on population mental health in the U.S.
-is a lack of appropriate high frequency surveillance data.
+{\bf Background:} A key obstacle to studying the impact of policies on population mental health in the United States (US) is a lack of appropriate high frequency surveillance data.
 A potential marker of population mental health is the use of Internet search data, which enables real-time, large-scale analysis of evolving mental health issues.
 
-{\bf Methods:} I utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety in U.S.
-states and counties.
+{\bf Methods:} I utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety in US states and counties.
 I examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptoms compared with physical health symptoms, and estimated associations between vaccine announcement and changes in mental health symptom search density.
@@
 2020–2021; @kujawaExposureCOVID19Pandemic2020] have reported high levels of anxiety (6-51%), depression (15-48%), and post-traumatic stress disorder (7-54%) associated with the onset of the pandemic.
-In the United States, approximately four in ten adults reported experiencing symptoms of anxiety or depression in December 2020—a four-fold increase from January-June 2019.[@panchalImplicationsCOVID19Mental2021, p.
-19] Globally, it has been estimated that the prevalence of depression and anxiety during the COVID-19 pandemic may be as high as 24% and 21%, respectively.[@banko-ferranImpactCOVID19Mental2020; @castaldelli-maiaInvestigatingEffectNational2021] This striking burden has been described as a mental health crisis[@melimopoulosHowCOVID19Pandemic2021] and as a pandemic in its own right.[@kwaiWhatPointYoung2021]
+In the \acr{US}, approximately four in ten adults reported experiencing symptoms of anxiety or depression in December 2020—a four-fold increase from January-June 2019.[@panchalImplicationsCOVID19Mental2021, p.
+19] Globally, it has been estimated that the prevalence of depression and anxiety during the COVID-19 pandemic may be as high as 24% and 21%, respectively[@banko-ferranImpactCOVID19Mental2020; @castaldelli-maiaInvestigatingEffectNational2021], with regions  hit hardest by COVID-19 showing the greatest increases in prevalence.[@santomauroGlobalPrevalenceBurden2021] This striking burden has been described as a mental health crisis[@melimopoulosHowCOVID19Pandemic2021] and as a pandemic in its own right.[@kwaiWhatPointYoung2021]
 
@@
 Beyond the physical benefits vaccines provide in reducing the risk of infection and associated morbidity and mortality, a growing body of evidence suggests that vaccination has also
-contributed to improved mental health.[@agrawalImpactCOVID19Vaccine2021; @chourpiliadisShorttermImprovementMental2023; @nguyenPsychologicalBenefitsCOVID192021; @rubinsteinEffectCOVID19Vaccinations2023] While there is limited international data on the secondary mental health impact of COVID-19 vaccination, research drawing from the U.S.
-Census Bureau’s Household Pulse Survey has found that benefits of vaccination may include up to a 30% reduction in symptoms of anxiety and depression among vaccinated adults,[@agrawalImpactCOVID19Vaccine2021] while research using the University of Southern California Understanding America Survey suggests a reduction in loneliness associated with greater social interactions following vaccination.[@leeEffectVaccinationSocial2022]
+contributed to improved mental health.[@agrawalImpactCOVID19Vaccine2021; @chourpiliadisShorttermImprovementMental2023; @nguyenPsychologicalBenefitsCOVID192021; @rubinsteinEffectCOVID19Vaccinations2023] While there is limited international data on the secondary mental health impact of COVID-19 vaccination, research drawing from the \acr{US} Census Bureau’s Household Pulse Survey has found that benefits of vaccination may include up to a 30% reduction in symptoms of anxiety and depression among vaccinated adults,[@agrawalImpactCOVID19Vaccine2021] while research using the University of Southern California Understanding America Survey suggests a reduction in loneliness associated with greater social interactions following vaccination.[@leeEffectVaccinationSocial2022]
 
@@
 A potential marker of population mental health is the use of internet search data, which enables real-time, large-scale analysis of evolving mental health issues.
-A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020] found a strong correlation between search trends for depression and anxiety with indicators of mental health services utilization (reported in the U.S.
-Census Household Pulse Survey) and rates of emergency department visits for mental health conditions (from the U.S.
-Centers for Disease Control and Prevention’s (CDC) National Syndromic Surveillance Program).[@vaidyanathanEvaluationInternetSearches2022] If taken as a reasonable proxy for mental health disorders, search data can provide valuable information on how population mental health reacts to real-time events, enabling policymakers to better respond to mental health needs in a timely manner.
+A recently published evaluation of Google’s COVID-19 Search Trends Symptoms Dataset[@Wahltinez2020] found a strong correlation between search trends for depression and anxiety with indicators of mental health services utilization (reported in the \acr{US} Census Household Pulse Survey) and rates of emergency department visits for mental health conditions (from the National Syndromic Surveillance Program of the \acr{US} \acr{CDC}).[@vaidyanathanEvaluationInternetSearches2022] If taken as a reasonable proxy for mental health disorders, search data can provide valuable information on how population mental health reacts to real-time events, enabling policymakers to better respond to mental health needs in a timely manner.
 
 This study analyzes whether news announcements (in November 2020) regarding the imminent availability of safe and effective COVID-19 vaccines impacted population mental health—even before these vaccines were made available to the public.
-Using Google search density data, I applied interrupted time series approaches to investigate how these announcements might have affected search trends for mental health symptoms in the U.S.
-and five other countries where data were available: Australia, Ireland, New Zealand, Singapore, and the United Kingdom.
-Owing to emerging evidence that political ideology may be a predictor of confidence in public health and vaccine hesitancy,[@debusPoliticalIdeologyVaccination2021; @baumgaertnerInfluencePoliticalIdeology2018; @stolerSociopoliticalPsychologicalCorrelates2022] I further explored whether changes in search trends for mental health symptoms varied across U.S.
-states and counties that predominantly voted Democrat versus Republican in the 2020 presidential election.
-These findings suggest declines in density for searches related to anxiety and depression in all of the countries examined; in the U.S., these declines were found to be consistent irrespective of political ideology.
+Using Google search density data, I applied interrupted time series approaches to investigate how these announcements might have affected search trends for mental health symptoms in the \acr{US} and five other countries where data were available: Australia, Ireland, New Zealand, Singapore, and the United Kingdom.
+Owing to emerging evidence that political ideology may be a predictor of confidence in public health and vaccine hesitancy,[@debusPoliticalIdeologyVaccination2021; @baumgaertnerInfluencePoliticalIdeology2018; @stolerSociopoliticalPsychologicalCorrelates2022] I further explored whether changes in search trends for mental health symptoms varied across \acr{US} states and counties that predominantly voted Democrat versus Republican in the 2020 presidential election.
+These findings suggest declines in density for searches related to anxiety and depression in all of the countries examined; in the \acr{US}, these declines were found to be consistent irrespective of political ideology.
 
@@
 I took November 16, 2020 as the date of the first credible signal of the imminent availability of safe and effective COVID-19 vaccines.
-On November 9^th^, Pzifer announced that early vaccine trial data showed 90% efficacy[@thomasPfizerEarlyData2020] and on the 16^th^, Moderna announced preliminary results showing 95% efficacy.[@gradyEarlyDataShow2020] While U.S.
-Food and Drug Administration (FDA) Emergency Use Authorization (EUA) was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
+On November 9^th^, Pzifer announced that early vaccine trial data showed 90% efficacy[@thomasPfizerEarlyData2020] and on the 16^th^, Moderna announced preliminary results showing 95% efficacy.[@gradyEarlyDataShow2020] While \acr{US} \acr{FDA} \acr{EUA} was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
 
@@
 Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominately English-speaking countries: Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States.
-In the U.S., subnational regions include states and counties.
+In the \acr{US}, subnational regions include states and counties.
 Because the aggregated search density data were constructed based on relative search population within each region, I could not compare search density for specific symptoms across different regions; however, comparing search density within regions (or a group of regions) was feasible both over time and across different symptoms.
@@
 
-I utilized three levels of region: 1) national level for the six countries; 2) U.S.
-state level data across `r n_states` states and the District of Columbia; and 3) U.S.
-county level data across `r n_counties` counties (though there are over 3,000 counties in the U.S., due to data privacy concerns, smaller county results were not included in the symptoms dataset).
+I utilized three levels of region: 1) national level for the six countries; 2) \acr{US} state level data across `r n_states` states and the District of Columbia; and 3) \acr{US} county level data across `r n_counties` counties (though there are over 3,000 counties in the \acr{US}, due to data privacy concerns, smaller county results were not included in the symptoms dataset).
 Following the convention of the symptoms dataset, I will refer to the geographic units (e.g., states, counties, and nations) within the data as "regions."
@@
 
-I obtained county-level presidential election results for 2020 from the MIT Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which I used to calculate aggregate county and state votes (including absentee, early, and election day ballots) for each candidate.
+I obtained county-level presidential election results for 2020 from the \acr{MIT} Election Data and Science Lab,[@mitelectiondataandsciencelabCountyPresidentialElection2022] which I used to calculate aggregate county and state votes (including absentee, early, and election day ballots) for each candidate.
 The aggregate votes were then used to determine vote share and margins (e.g., the percentage points difference in vote share between the winning candidate and the runner up).
@@
 
-Population estimates for 2020 by Federal Information Processing Standards (FIPS) code were obtained from the U.S. Department of Agriculture (USDA) Economic Research Service.
+Population estimates for 2020 by \acr{FIPS} code were obtained from the\acr{USDA} Economic Research Service.
 
@@
 
-I used an interrupted time series (ITS) approach to model the Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days before the vaccine announcement ($time_0$), $Post_i$ is an indicator variable equal to 1 in the period after the announcement (0 otherwise), $\theta_r$ indicates a series of fixed effects for each region $(r)$, $T^{'}_t\chi$ is a matrix of time fixed effects (i.e., month and day of week), and $\epsilon_{it}$ is an error term.
+I used an \acr{ITS} approach to model the Google search density for a given symptom $d$ using the following baseline equation: $$Y_{d,g, i} = \lambda_0 + \lambda_1 time_t + \alpha_d Post_{d,i} + \beta_d time_t*post_{d,i} + \theta_r + T^{'}_t\chi + \epsilon_{it} \ \ \ ,\ \ \ \ \ \ \ \ \ \ \ \ (3.1)$$ where $time_t$ is a continuous variable that captures the days before the vaccine announcement ($time_0$), $Post_i$ is an indicator variable equal to 1 in the period after the announcement (0 otherwise), $\theta_r$ indicates a series of fixed effects for each region $(r)$, $T^{'}_t\chi$ is a matrix of time fixed effects (i.e., month and day of week), and $\epsilon_{it}$ is an error term.
 $\alpha_d$ can be interpreted as a level change associated with the announcement date—that is, the immediate difference in search density for a disease $d$ following November 19, 2020; $\beta_d$—the slope change—can be interpreted as the sustained change in search density in the days following November 16th.
@@
 
-To control for time-varying confounders which may affect symptom search trends, I applied a controlled interrupted time series (CITS) approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
+To control for time-varying confounders which may affect symptom search trends, I applied a \acr{CITS} approach to contrast how searches for mental health symptoms varied above and beyond changes in search density for a comparable physical complaint (i.e., headaches).
 
@@
 
-Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals (CIs) using heteroskedasticity-robust standard errors.
+Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals (\acr{CIs}) using heteroskedasticity-robust standard errors.
 
@@
 
-First, I considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, I compared the level of region of aggregated data, using U.S.
-counties, U.S.
-states, and, finally, national trends from the six counties in the sample.
+First, I considered the role of data cleaning in the outcome data, which involved outlier smoothing using Friedman’s nonparametric super smoother regression estimator.[@friedmanVariableSpanScatterplot1984] Second, I compared the level of region of aggregated data, using \acr{US} counties, \acr{US} states, and, finally, national trends from the six counties in the sample.
 Third, I evaluated sensitivity to the specification of the bandwidth cut-off around the announcement date, extending it from ±40 days to ±50 and ±60 days.
-Fourth, I toggled whether to account for day of week fixed effects; fifth, I toggled month fixed effects; and sixth, I toggled regional fixed effects (i.e., fixed effects for states in the U.S.
-state level data, fixed effects for counties in the U.S.
-county level data, etc.).
+Fourth, I toggled whether to account for day of week fixed effects; fifth, I toggled month fixed effects; and sixth, I toggled regional fixed effects (i.e., fixed effects for states in the \acr{US} state level data, fixed effects for counties in the \acr{US} county level data, etc.).
 
@@
 
-The first subgroup analysis applied the CITS approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using the nationally aggregated data.
-This analysis aimed to investigate the extent to which effects observed in U.S.
-states and counties were also seen in other countries.
-
-The second subgroup analysis applied the CITS approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share.
-The subgroup analysis comparing CITS effect estimates in blue versus red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
+The first subgroup analysis applied the \acr{CITS} approach against all `r mh_diseases_n` mental health related symptoms against search data from each of the six countries in the sample, using the nationally aggregated data.
+This analysis aimed to investigate the extent to which effects observed in \acr{US} states and counties were also seen in other countries.
+
+The second subgroup analysis applied the \acr{CITS} approach to the 20% most Republican-voting localities (hereafter referred to as red states/counties) and to the 20% most Democratic-voting localities (hereafter referred to as blue states/counties) based on 2020 presidential election vote share.
+The subgroup analysis comparing \acr{CITS} effect estimates in blue versus red states aimed to investigate whether the initial response to imminent safe and effective COVID-19 vaccines showed evidence of heterogeneity by predominant political ideology, under the hypothesis that if conservative voters were more likely to be averse to vaccination, any impact on mental health related symptom search density from the announcement of upcoming vaccines would be lesser in red states and counties compared to blue ones.
 
@@
 
-The Institutional Review Board (IRB) of the Harvard T.H.
+The \acr{IRB} of the Harvard T.H.
 Chan School of Public Health determined that this study was not human subjects research and that additional review was not required (protocol number: IRB23-0095, determined on January 25, 2023).
@@
 
-The estimates for the immediate (level shift) and sustained (slope change) effects associated with the announcement of vaccine safety and efficacy data on search density for all `r diseases_n` are presented in Figure \ref{figure_all_diseases}.
+The estimates for the immediate (level shift) and sustained (slope change) effects associated with the announcement of vaccine safety and efficacy data on search density for all `r diseases_n` symptoms are presented in Figure \ref{figure_all_diseases}.
 
 For most symptoms, search density exhibited negligible differences following the announcement, with small positive level shifts offset by modest negative slope changes.
-For four mental health symptoms, however, I observed relatively large, negative slope changes for searches for anxiety `r function_dynamic_text_results("its","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("its","depression", "slope", value_include = "allnumber")`, major depressive disorder (MDD)`r function_dynamic_text_results("its","major_depressive_disorder", "slope", value_include = "allnumber")`, and attention deficit hyperactivity disorder (ADHD)`r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "slope", value_include = "allnumber")`.
-With respect to level shifts, changes for anxiety `r function_dynamic_text_results("its","anxiety", "intercept", value_include = "allnumber")` and depression `r function_dynamic_text_results("its","depression", "intercept", value_include = "allnumber")` were close to zero, while those for MDD `r function_dynamic_text_results("its","major_depressive_disorder", "intercept", value_include = "allnumber")` and ADHD `r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "intercept", value_include = "allnumber")` were approximately 0.3 percentage points.
+For four mental health symptoms, however, I observed relatively large, negative slope changes for searches for anxiety `r function_dynamic_text_results("its","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("its","depression", "slope", value_include = "allnumber")`, \acr{MDD}`r function_dynamic_text_results("its","major_depressive_disorder", "slope", value_include = "allnumber")`, and \acr{ADHD}`r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "slope", value_include = "allnumber")`.
+With respect to level shifts, changes for anxiety `r function_dynamic_text_results("its","anxiety", "intercept", value_include = "allnumber")` and depression `r function_dynamic_text_results("its","depression", "intercept", value_include = "allnumber")` were close to zero, while those for \acr{MDD} `r function_dynamic_text_results("its","major_depressive_disorder", "intercept", value_include = "allnumber")` and \acr{ADHD} `r function_dynamic_text_results("its","attention_deficit_hyperactivity_disorder", "intercept", value_include = "allnumber")` were approximately 0.3 percentage points.
 
@@
 
-```
-
-While the ITS analysis provided suggestive evidence that search density for mental health symptoms might have changed in the post-announcement period, it also highlighted that searches may have generally changed across other diseases at the same time.
-The CITS estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed the ITS analysis, with most conditions showing level and slope changes close to 0.
-For three conditions, the CITS analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and MDD `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")`, all showing sustained declines.
-All three symptoms had relatively large slope changes in the ITS analysis.
-In addition, the CITS level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "intercept")`, a decrease double in magnitude compared to most estimates for other symptoms.
+ ggsave(filename = paste0("Figure_15.jpg"),
+    plot = last_plot(),
+    width = 7,
+    height = 6.3,
+    bg = "white")
+
+```
+
+While the \acr{ITS} analysis provided suggestive evidence that search density for mental health symptoms might have changed in the post-announcement period, it also highlighted that searches may have generally changed across other diseases at the same time.
+The \acr{CITS} estimates of each mental health symptom (Figure \ref{figure_cits_outputs}) using searches for headaches as a comparison broadly echoed the \acr{ITS} analysis, with most conditions showing level and slope changes close to 0.
+For three conditions, the \acr{CITS} analysis showed relatively large slope changes with searches for anxiety `r function_dynamic_text_results("main","anxiety", "slope", value_include = "allnumber")`, depression `r function_dynamic_text_results("main","depression", "slope", value_include = "allnumber")`, and \acr{MDD} `r function_dynamic_text_results("main","major_depressive_disorder", "slope", value_include = "allnumber")`, all showing sustained declines.
+All three symptoms had relatively large slope changes in the \acr{ITS} analysis.
+In addition, the \acr{CITS} level shift (i.e., the relative immediate effect) for anxiety was `r function_dynamic_text_results("main","anxiety", "intercept")`, a decrease double in magnitude compared to most estimates for other symptoms.
 
@@
 
-```
-
-In both the analyses, search trends for anxiety, depression, and MDD showed potential immediate and sustained declines in density following November 16th.
-Search density for these three symptoms and the comparison search data for headaches is plotted in Figures \ref{figures_cits_data_anxiety} through \ref{figures_cits_data_mdd} at the level of U.S.
-states, U.S.
-counties, and international data.
-I observed relatively strong concordance between the CITS estimates and the observed trends in the data, with strong fit to both mental health symptoms and headaches.
+ ggsave(filename = paste0("Figure_16.jpg"),
+    plot = last_plot(),
+    width = 7,
+    height = 6.3,
+    bg = "white")
+
+```
+
+In both the analyses, search trends for anxiety, depression, and \acr{MDD} showed potential immediate and sustained declines in density following November 16th.
+Search density for these three symptoms and the comparison search data for headaches is plotted in Figures \ref{figures_cits_data_anxiety} through \ref{figures_cits_data_mdd} at the level of \acr{US} states, \acr{US} counties, and international data.
+I observed relatively strong concordance between the \acr{CITS} estimates and the observed trends in the data, with strong fit to both mental health symptoms and headaches.
 I further observed strong within-week patterns in searches, supporting the inclusion of fixed effects to account for this weekly periodicity.
@@
 In each row, search density data for two symptoms are displayed: anxiety in blue and headaches in grey.
-In the first row, data from U.S.
-states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second row, data from U.S.
-counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
+In the first row, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second row, data from US counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
 In the third row, national data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States are shown.
@@
 The solid lines show predicted lines of best fit under a basic controlled interrupted time series model (i.e., no fixed effects).
-U.S.: United States."}
+US: United States."}
 
 function_figures_cits_data(geography = geography, "anxiety")
+
+ ggsave(filename = paste0("Figure_17.jpg"),
+    plot = last_plot(),
+    width = 4.4,
+    height = 6.3,
+    bg = "white")
 
@@
 In each row, search density data for two symptoms are displayed: depression in blue and headaches in grey.
-In the first row, data from U.S.
-states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second row, data from U.S.
-counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
+In the first row, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second row, data from US counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
 In the third row, national data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States are shown.
@@
 The solid lines show predicted lines of best fit under a basic controlled interrupted time series model (i.e., no fixed effects).
-U.S.: United States."}
+US: United States."}
 
 function_figures_cits_data(geography = geography, "depression")
+
+ ggsave(filename = paste0("Figure_18.jpg"),
+    plot = last_plot(),
+    width = 4.4,
+    height = 6.3,
+    bg = "white")
 
@@
 In each row, search density data for two symptoms are displayed: MDD in blue and headaches in grey.
-In the first row, data from U.S.
-states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
-In the second row, data from U.S.
-counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
+In the first row, data from US states are shown, where each point represents the search density of a specific symptom on a specific date in a specific state.
+In the second row, data from US counties are shown; because of the large number of counties reporting data, county-level search data are summarized as daily boxplots.
 In the third row, national data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States are shown.
@@
 The solid lines show predicted lines of best fit under a basic controlled interrupted time series model (i.e., no fixed effects).
-U.S.: United States."}
+US: United States."}
 
 function_figures_cits_data(geography = geography, "major_depressive_disorder")
+
+ ggsave(filename = paste0("Figure_19.jpg"),
+    plot = last_plot(),
+    width = 4.4,
+    height = 6.3,
+    bg = "white")
 
@@
 For depression, all `r function_dynamic_text_results("multiverse","depression", "slope", multiverse_sign = "negative")` models had negative slope changes, of which only `r function_dynamic_text_results("multiverse","depression", "intercept", multiverse_sign = "positive")` models had any positive level shift.
-For MDD, I similarly observed a universally negative slope change in all `r function_dynamic_text_results("multiverse","major_depressive_disorder", "slope", multiverse_sign = "negative", multiverse_p = FALSE)` models; however, the majority of models showed a positive level shift (`r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "positive", multiverse_p = FALSE)` models), whereas only `r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "negative", multiverse_p = FALSE)` showed a downward level shift.
+For \acr{MDD}, I similarly observed a universally negative slope change in all `r function_dynamic_text_results("multiverse","major_depressive_disorder", "slope", multiverse_sign = "negative", multiverse_p = FALSE)` models; however, the majority of models showed a positive level shift (`r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "positive", multiverse_p = FALSE)` models), whereas only `r function_dynamic_text_results("multiverse","major_depressive_disorder", "intercept", multiverse_sign = "negative", multiverse_p = FALSE)` showed a downward level shift.
 
@@
  facet_wrap(~disease)
-```
-
-Slope changes and level shifts for anxiety, depression, and MDD are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}.
-Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates compared to state level estimates, but with much tighter CIs, even when geographic fixed effects and narrower bandwidths were included.
+
+ ggsave(filename = paste0("Figure_20.jpg"),
+    plot = last_plot(),
+    width = 7,
+    height = 8,
+    bg = "white")
+
+```
+
+Slope changes and level shifts for anxiety, depression, and \acr{MDD} are reported for each combination (144 models) in Figure \ref{fig_multiverse_analysis}.
+Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates compared to state level estimates, but with much tighter \acr{CIs}, even when geographic fixed effects and narrower bandwidths were included.
 Across all models, the sustained change in search density for anxiety and depression was negative and significant with an alpha of 0.01.
@@
 Turning to the subgroup analysis, I found modest evidence of effect estimates of similar magnitude comparing across countries (Figure \ref{fig_international}).
-Across the most populous countries (Australia, the United Kingdom, and the United States), effect estimates were broadly consistent, with wider CIs than the ITS or CITS main analysis results due to the smaller number of observations.
+Across the most populous countries (Australia, the United Kingdom, and the United States), effect estimates were broadly consistent, with wider \acr{CIs} than the \acr{ITS} or \acr{CITS} main analysis results due to the smaller number of observations.
 Negative level shifts and slope changes were more pronounced in New Zealand compared to other countries, while the level shift estimated for searches for depression in Ireland was positive; owing to the construction of the Google search density data being relative to regions, this may be due to differences in search volume intensity for depression in Ireland and New Zealand compared to other countries, and not due to a strong effect itself.
@@
 
+ ggsave(filename = paste0("Figure_21.jpg"),
+    plot = last_plot(),
+    width = 18,
+    height = 14,
+    bg = "white")
+
 print(combo_plot)
@@
 
-```
-
-Results from the analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and MDD as found in the main analysis (Figure \ref{fig_political}).
-This was particularly observed in the analysis of U.S.
-state-level data, where confidence intervals for the CITS effect estimates were statistically equivalent across red and blue states.
+ ggsave(filename = paste0("Figure_22.jpg"),
+    plot = last_plot(),
+    width = 13,
+    height = 6,
+    bg = "white")
+
+```
+
+Results from the analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and \acr{MDD} as found in the main analysis (Figure \ref{fig_political}).
+This was particularly observed in the analysis of \acr{US} state-level data, where confidence intervals for the \acr{CITS} effect estimates were statistically equivalent across red and blue states.
 In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties than blue ones, with minor overlap in confidence intervals.
@@
 CITS: controlled interrupted time series.
-U.S.: United States."}
+US: United States."}
 
@@
  function_clean_diseases() %>%
- mutate(geography = ifelse(geography == "state", "U.S. states", "U.S. counties")) %>%
+ mutate(geography = ifelse(geography == "state", "US states", "US counties")) %>%
  mutate(polity = ifelse(polity == 1, "Red states/counties (top 20% most Republican", 
@@
 
+ ggsave(filename = paste0("Figure_23.jpg"),
+    plot = last_plot(),
+    width = 13,
+    height = 6,
+    bg = "white")
+
 rm(packages_and_paremeters_on)
@@
 This study evaluated whether two contemporary announcements of COVID-19 vaccine safety and efficacy data on November 9th and November 16^th^, 2020 were associated with changes in health-related Google search density related to mental health symptoms.
-Using search data from U.S.
-counties, states, and international trends, I applied ITS and CITS modeling approaches to investigate possible associations between these announcements and search density changes.
+Using search data from \acr{US} counties, states, and international trends, I applied \acr{ITS} and \acr{CITS} modeling approaches to investigate possible associations between these announcements and search density changes.
 I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
@@
 To interpret these observed changes as reactions to the vaccine safety and efficacy announcements, it is important to evaluate whether they may be responses to other contemporary events.
-I highlight two potential alternatives that coincided with the period under study: the 2020 U.S.
-presidential election on November 3^rd^ and the observance of the Thanksgiving holiday in the United States on November 26^th^.
-While it is possible that the estimates encompass impacts from these events, data from the subgroup analysis lends support for the interpretation that these alternatives are insufficient to explain the observed declines in search trends for anxiety, depression, and MDD.
-
-With respect to the U.S.
-presidential election, I would anticipate any post-election decline in mental health related symptoms to be concentrated in the United States, given its domestic importance and the political fervor that surrounded it.
-Similarly, I would expect that impacts of the Thanksgiving holiday would be unique to the U.S., as it is not celebrated by the other nations in the sample and there were no other national holidays observed by those nations at the same time (with the exception of Singapore’s observance of Deepavali on November 14^th^).
-
-In the subgroup analysis comparing Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I did not observe evidence of U.S.-specific effects, with the analysis showing consistent declines in searches related to anxiety and depression across all countries (though these differed in degree).
-Furthermore, the estimated declines in search density in Australia and the United Kingdom—which, along with the U.S., are the most populous nations in the sample—were greater than that of the U.S.
-for these two symptom searches, providing additional counterevidence to these alternative explanations.
-
-Further countering the explanation that observed declines in search trends for mental health symptoms were due to the U.S.
-presidential election are the results from the subgroup analysis comparing blue and red states/counties.
+I highlight two potential alternatives that coincided with the period under study: the 2020 \acr{US} presidential election on November 3^rd^ and the observance of the Thanksgiving holiday in the United States on November 26^th^.
+While it is possible that the estimates encompass impacts from these events, data from the subgroup analysis lends support for the interpretation that these alternatives are insufficient to explain the observed declines in search trends for anxiety, depression, and \acr{MDD}.
+
+With respect to the \acr{US} presidential election, I would anticipate any post-election decline in mental health related symptoms to be concentrated in the United States, given its domestic importance and the political fervor that surrounded it.
+Similarly, I would expect that impacts of the Thanksgiving holiday would be unique to the \acr{US}, as it is not celebrated by the other nations in the sample and there were no other national holidays observed by those nations at the same time (with the exception of Singapore’s observance of Deepavali on November 14^th^).
+
+In the subgroup analysis comparing Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I did not observe evidence of \acr{US}-specific effects, with the analysis showing consistent declines in searches related to anxiety and depression across all countries (though these differed in degree).
+Furthermore, the estimated declines in search density in Australia and the United Kingdom—which, along with the \acr{US}, are the most populous nations in the sample—were greater than that of the \acr{US} for these two symptom searches, providing additional counterevidence to these alternative explanations.
+
+Further countering the explanation that observed declines in search trends for mental health symptoms were due to the \acr{US} presidential election are the results from the subgroup analysis comparing blue and red states/counties.
 If voters expressed relief following the election if their candidate was the winner, a greater decline in searches related to anxiety and depression in states and counties would be expected in those that more heavily voted for Joe Biden, the Democratic candidate and subsequent President-elect, than for former President Donald Trump, the Republican candidate.
@@
 I did, however, observe broad similarities in the confidence intervals of these estimates, such that I did not rule out the possibility that the effects were the same across red and blue counties.
-However, even this finding would be striking, giving the enduring political controversy over vaccination in the U.S.; while subsequent attitudes towards vaccination may show an ideological split by political affiliation, the findings—if taken as a reasonable reflection of individual attitudes—suggest that whatever relief the vaccine announcements brought was shared across the aisle.
+However, even this finding would be striking, giving the enduring political controversy over vaccination in the \acr{US}; while subsequent attitudes towards vaccination may show an ideological split by political affiliation, the findings—if taken as a reasonable reflection of individual attitudes—suggest that whatever relief the vaccine announcements brought was shared across the aisle.
 
@@
 In addition, the use of Google search density as a proxy for population mental health could not be directly validated in the study, as the search data was anonymized and aggregated.
-While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and U.S.
-population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.
+While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and \acr{US} population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.
 

### 2023-04-24 thesis_final_version.Rmd
Revisions in advance of PhD defense, corrections, addition of conceptual framework, additional references

@@
 bibliography: main.bib
-# natbiboptions: "numbers"
 csl: https://www.zotero.org/styles/the-lancet
-
-  # intro: intro.bib
-  # ch1: chapter1.bib
-  #
-
 acronyms:
   insert_loa: false
-  loa_title: ""
-
-  # loa_title: "List of Acronyms"
+  insert_links: false
+  loa_title: ''
   keys:
-    - shortname: LMIC
-      longname: low and middle income country
-
+    - shortname: DALYs
+      longname: disability-adjusted life years
+    - shortname: YLLs
+      longname: years of life lost 
+    - shortname: YLDs
+      longname: years of healthy life lost due to disability 
+    - shortname: LMICs
+      longname: low- and middle-incomee countries
+    - shortname: WHO
+      longname: World Health Organization
+    - shortname: USD
+      longname: United States dollars
+    - shortname: GBD
+      longname: Global Burden of Disease
+    - shortname: GBO
+      longname: Global Health Observatory
+    - shortname: GDP
+      longname: gross domestic product
+    - shortname: NCDs
+      longname: noncommunicable diseases
+    - shortname: PAF
+      longname: population attributable fraction
+    - shortname: VSL
+      longname: value of a statistical life
+    - shortname: IRB
+      longname: Institutional Review Board 
+    - shortname: UIs
+      longname: uncertainty intervals
+    - shortname: CIs
+      longname: confidence intervals
+    - shortname: PPP
+      longname: purchasing power parity
+    - shortname: CCEs
+      longname: climate change-related exposures
+    - shortname: HMIS
+      longname: health management information system
+    - shortname: ESA CCI
+      longname: European Space Agency’s Climate Change Initiative
+    - shortname: ESA CCI SM
+      longname: ESA CCI soil moisture dataset
+    - shortname: ERA5
+      longname: 'European ReAnalysis 5' 
+    - shortname: NOAA
+      longname: United States National Oceanic and Atmospheric Administration
+    - shortname: GESIS
+      longname: Gestion du Système d'Information Sanitaire
+    - shortname: DHIS2
+      longname: 'District Health Information Software 2'
+    - shortname: CSB
+      longname: centre santé de base
+    - shortname: FSB
+      longname: formation sanitaires privées de dase
+    - shortname: CHD/CHRD
+      longname: centre hospitalier de référence de district
+    - shortname: RHINO
+      longname: Routine Health Information Network
+    - shortname: USAID
+      longname: United States Agency for International Development
+    - shortname: US
+      longname: United States
+    - shortname: CHRR
+      longname: centre hospitalier de référence régionale
+    - shortname: CHU
+      longname: centre hospitalier universitaire
+    - shortname: C3S
+      longname: Copernicus Climate Change Service
+    - shortname: ECMWF
+      longname: European Centre for Medium-Range Weather Forecasts
+    - shortname: km
+      longname: kilometers
+    - shortname: MFR La Réunion
+      longname: Météo-France La Réunion
+    - shortname: WMO
+      longname: World Meteorological Organisation
+    - shortname: RSMC 
+      longname: Regional Specialized Meteorological Center
+    - shortname: NB
+      longname: negative binomial
+    - shortname: IRRs
+      longname: incidence rate ratios
+    - shortname: FE
+      longname: fixed effects
+    - shortname: CDC
+      longname: Centers for Disease Control and Prevention
+    - shortname: FDA
+      longname: Food and Drug Administration
+    - shortname: EUA
+      longname: Emergency Use Authorization
+    - shortname: MIT
+      longname: Massachusetts Institute of Technology
+    - shortname: FIPS
+      longname: Federal Information Processing Standards
+    - shortname: USDA
+      longname: United States Department of Agriculture
+    - shortname: ITS
+      longname: interrupted time series
+    - shortname: CITS
+      longname: controlled interrupted time series
+    - shortname: MDD
+      longname: major depressive disorder
+    - shortname: ADHD
+      longname: attention deficit hyperactivity disorder
+    - shortname: CoC
+      longname: clouding of consciousness
+    - shortname: GAD
+      longname: generalized anxiety disorder
 ---
@@
 Using the most recently available estimates from the Global Burden of Disease study, we found that the burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019.
-The economic value of this mental health burden was estimated to exceed 4.7 trillion USD using a value of statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.
+The economic value of this mental health burden was estimated to exceed 4.7 trillion United States dollars using a value of statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.
 
@@
 In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic.
-Using an interrupted time series approach with search data from U.S.
-counties, states, and international trends, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression.
+Using an interrupted time series approach with search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression.
 These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.
@@
 
+\newpage
+
 \end{spacing}
+
+\section*{List of Acronyms}
+
+\addcontentsline{toc}{section}{List of Acronyms}
+
+\printacronyms
+
+\newpage
 
@@
 
-# Acronyms with acronym down
-# Separate bibliography for each section
+# Check that sequential articles are represented by a dash
+# Institutional authors need to be fixed in bibliography
 # Numbered figures and tables by section
 
-# Check that sequential articles are represented by a dash
-# Table of figures and tables
-# Institutional authors need to be fixed in bibliography
-
 ```

### 2023-05-11 appendix_2.1.Rmd
Final revisions to manuscript

@@
 
+```{r table_s_2_1, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table_s_2_1.png")
+
+```
+
 \addcontentsline{lot}{table}{Table S2.1: Availability of disaggregated health system data by year and level of care.}
 
-```{r table_s_2_1, echo = FALSE, include = TRUE, out.width = '100%'}
-
-knitr::include_graphics("table_s_2_1.png")
-
-```
 \end{raggedright}
@@
 The nonparametric Friedman’s super smoother regression estimator [@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation [@hyndmanAutomaticTimeSeries2008].
-By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may habe reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry.
+By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may have reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry.
 Interpolated values were coerced to the nearest integer.

### 2023-05-11 appendix_2.2.Rmd
Final revisions to manuscript

@@
 * **District**: The district of Madagascar (2nd largest administrative unit) that contained the facility's catchment area. Only district- and commune-level facilities had a value for this variable.
-* **Commune**: The commune of Madagascar (3rd largest unit) that contained the facility's catchment area. Only basic health facility had a value for this variable.
+* **Commune**: The commune of Madagascar (3rd largest unit) that contained the facility's catchment area. Only basic health facilities had a value for this variable.
 * **FS**: The facility type and name.
@@
 
-``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
+``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
 
@@
 From reviewing this list, we observed that in the Diana region, the regional hospitals named "Hopitaly MANARA-PENITRA" and "Hopitaly Manara-Penitra Antsiranana" were duplicates, but appeared separately because the latter name contained the city the hospital is located in, Antsiranana.
-We standardized the names of those facilities, which resolved `r  prettyNum(n_dif, big.mark = ",", scientific = FALSE)` `r ifelse(n_dif > 1, "duplicates","duplicate")`).
+We standardized the names of those facilities, which resolved `r  prettyNum(n_dif, big.mark = ",", scientific = FALSE)` `r ifelse(n_dif > 1, "duplicates","duplicate")`.
 
@@
 In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented an approximate string matching technique.
-This technique—also known as "fuzzy string searching"—is a common approach to record linkage, where information from one source (e.g., our sample) needs to be linked to data from another (e.g., the spatial inventory).
+This technique—also known as "fuzzy string searching"—is a common approach to record linkage, where information from one source (i.e., our sample) needs to be linked to data from another (i.e., the spatial inventory).
 As its name suggests, this techniques allows for "strings" of text to be matched approximately, rather than exactly, to corresponding patterns.
@@
 
-In order to evaluate whether groups of two coordinates (which we referred to as "line groups") and groups of three or more coordinate ("polygon groups") were internally consistent (i.e., the points within a group were not geographically far apart, suggesting uncertainty in the location of a facility), we calculated the length (for line groups) and area (for polygon groups) of groups with more than one coordinate.
+In order to evaluate whether groups of two coordinates (which we referred to as "line groups") and groups of three or more coordinates ("polygon groups") were internally consistent (i.e., the points within a group were not geographically far apart, suggesting uncertainty in the location of a facility), we calculated the length (for line groups) and area (for polygon groups) of groups with more than one coordinate.
 
@@
 
-\addcontentsline{lot}{table}{Table S2.11: Distance between geolocated and validated coordinates.}
-
 ```{r validation_table, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, results=TRUE}
@@
 ```
+
+\addcontentsline{lot}{table}{Table S2.11: Distance between geolocated and validated coordinates.}
+
 \end{spacing}

### 2023-05-11 conclusion.Rmd
Final revisions to manuscript

@@
 We then applied a value of a statistical life year approach to estimate the associated global economic burden.
-Our findings suggest staggering loses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion \acr{USD} in 2019.
+Our findings suggest staggering losses: after accounting for premature mortality and other sources of morbidity associated with mental disorders, global losses were estimated to approximate 4.7 trillion \acr{USD} in 2019.
 The magnitude of these findings underscores the global scale of impact that mental disorders have and highlights the urgency for research and action to support mental health worldwide.
@@
 We then geolocated these facilities and obtained meteorologic data on climate conditions to examine the impact of three climate change exposures—temperature, soil moisture, and duration of cyclones and tropical storms.
-We found that monthly mental health related visits declined as temperature increased, particularly in the central highlands, where cooler temperatures were more prevalent; conversely, higher grades of soil moisture were associated with greater mental health visits with a lag of approximately three months, an increase found primarily in regions associated with higher flood risk in Madagascar.
+We found that monthly mental health related visits declined as temperature increased, particularly in the central highlands, where cooler temperatures were more prevalent; conversely, higher grades of soil moisture were associated with greater mental health visits with a lag of approximately three months, an increase found primarily in Madagascar's flood-prone regions.
 Our findings illustrate potential heterogeneity in how changing climate conditions may impact mental health needs, and our work demonstrates how routine health system data may be leveraged to address data gaps in health surveillance, particularly in resource-constrained settings.

### 2023-05-11 frontmatter.Rmd
Final revisions to manuscript

@@
 
-Jessica Cohen has been a constant source of joy and inspiration throughout my studies, and her teaching and scholarship have set a standard to aspire to.
+Jessica Cohen has been a constant source of inspiration throughout my studies, and her teaching and scholarship have set a standard to aspire to.
 In addition to being a brilliant scholar, she is an incredible mentor and instructor, bringing genuine joy to the rigorous study of challenging questions.
@@
 I thank Shekhar Saxena for his guiding leadership in global mental health and for welcoming me into the field when I first arrived at Harvard, and I thank Christopher Golden for welcoming me into his lab and providing every opportunity, guidance, and support a student could wish for throughout the development of the second paper of this thesis.
-
-<!-- I also wish to express my gratitude to Judith Bass, who graciously offered to serve as the External Reader for this dissertation, and who fostered my interest in mental health while undertaking my Masters of Public Health degree at Johns Hopkins.
--->
+I also wish to express my gratitude to Judith Bass, who graciously offered to serve as the External Reader for this dissertation.
 

### 2023-05-11 intro.Rmd
Final revisions to manuscript

@@
 Mental health is an essential part of human flourishing.
-As defined by the \acr{WHO}, it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community”.[@worldhealthorganizationComprehensiveMentalHealth2013]
+As defined by the \acr{WHO}, it encompasses “a state of well-being in which every individual realizes [their] own potential, can cope with the normal stresses of life, can work productively and fruitfully, and is able to make a contribution to [their] community.”[@worldhealthorganizationComprehensiveMentalHealth2013]
 
@@
 A better understanding of the evolving burden and dynamics of global mental health may thus have broad consequences to strengthening health system responses to mental disorders and improving health outcomes for millions of individuals worldwide.
+
 Contributing to such an understanding has motivated this dissertation, which takes as its focus different quantitative aspects of the global burden of mental illness—how we measure and evaluate it, how it may be changing, and how novel data sources may help in characterizing it, particularly in the absence of robust, high-frequency epidemiological surveillance.
-The papers presented in the subsequent three chapters echo the interdisciplinary nature of global mental health, drawing on a broad range of quantitative methods and applying analytic tools and insights from epidemiology, health economics, and econometrics.
-They further address different dimensions and determinants of population mental health, as illustrated in the conceptual framework shown in Figure \ref{figure_conceptual_framework}, which is based on a model identified by Dykxhoorn et al.[@dykxhoornConceptualisingPublicMental2022]
+
+The three chapters presented in this dissertation reflect the interdisciplinary nature of global mental health, utilizing a diverse range of quantitative methods and drawing on insights from epidemiology, health economics, and econometrics.
+Furthermore, these papers align with the broader conceptual framework of population mental health (Figure \ref{figure_conceptual_framework}), which recognizes the complex interplay of environmental, social, and structural determinants in shaping mental health outcomes.
+This framework, based on determinants identified by Dykxhoorn et al.,[@dykxhoornConceptualisingPublicMental2022] illustrates the comprehensive contributions of these determinants to individual and public mental health and guides the approaches in Chapters 1, 2, and 3.
 
@@
 We reviewed recent efforts to estimate both the epidemiologic and economic burden of mental disorders, and we propose a composite approach to estimation to capture a broader share of attributable morbidity and mortality.[@bloomGlobalEconomicBurden2011; @charlsonExcessMortalityMental2015; @vigoEstimatingTrueGlobal2016; @vosGlobalBurden3692020a; @walkerMortalityMentalDisorders2015; @whitefordGlobalBurdenDisease2013] Applying this approach using the most recently available \acr{GBD} data, we estimated that the global burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019.
-Using value of statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion \acr{USD}.
+Using value of a statistical life approaches, we estimated that the economic value of this burden would exceed 4.7 trillion \acr{USD}.
 
@@
 We found a statistically significant reduction in monthly mental health related visits associated with each degree Celcius increase in temperature, primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
-We further found that higher soil moisture may be associated with more mental health visits in the future, after a three month lag; this increase was primarily found in the eastern lowlands and the northern dry deciduous forests, consistent with the geographic concentration of flood risk in Madagascar.
+We further found that higher soil moisture may be associated with more mental health visits in the future, after a three-month lag; this increase was primarily found in the eastern lowlands and the northern dry deciduous forests, consistent with the geographic concentration of flood risk in Madagascar.
 Our findings point to potential heterogeneity in how changing climate conditions will impact mental health needs and system responses.
 
-In Chapter 3, I investigated how internet search data for health symptoms might provide high frequency insight into the state of population mental health during the COVID-19 pandemic.
+In Chapter 3, I investigated how internet search data for health symptoms might provide high-frequency insight into the state of population mental health during the COVID-19 pandemic.
 Using search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I explored how announcements of COVID-19 vaccine safety and efficacy data in November 2020 impacted Google search trends for mental health symptoms.
 I found evidence of statistically significant immediate and sustained declines in searches for anxiety, depression, and major depressive disorder throughout the 40 days following these announcements.
-The findings underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.
+The findings underscore the importance of timely and transparent public health communication and illustrate the potential application of high-frequency internet search data for population mental health surveillance.
 

### 2023-05-11 paper1.Rmd
Final revisions to manuscript

@@
 
-\vspace{6pt}
+\vspace{5pt}
 
 \noindent\rule{8cm}{0.4pt}
+
+\vspace{1pt}
 
@@
 
-Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This landmark paper by Bloom and colleagues estimated that the value of losses due to mental disorders was roughly 1.3 trillion United States dollars (\acr{USD}) in 2010 (1.6 trillion \acr{USD} in 2019) when disability-adjusted life years (\acr{DALYs}) were valued at one times \acr{GDP} per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion \acr{USD} 2010 (or approximately 3.0 trillion \acr{USD} in 2019) by 2030.
+Evaluating the economic burden of mental illness is a critical part in making the investment case for global mental health, informing public health decision-making, and guiding priority-setting and the scale-up of much-needed interventions.[@chisholmScalingupTreatmentDepression2016] At the global level, however, the most recent estimate of the economic impact of mental disorders was published in 2011, using burden of disease estimates from 2004.[@bloomGlobalEconomicBurden2011] This landmark paper by Bloom and colleagues estimated that the value of losses due to mental disorders was roughly 1.3 trillion United States dollars (\acr{USD}) in 2010 (1.6 trillion \acr{USD} in 2019) when disability-adjusted life years (\acr{DALYs}) were valued at one times \acr{GDP} per capita.[@bloomGlobalEconomicBurden2011] The authors further projected that these losses would grow to nearly 2.5 trillion \acr{USD} 2010 (or approximately 3.0 trillion \acr{USD} in 2019) by 2030.
 (See Tables S1.1 and S1.2 in Appendix 1 for estimates from the other two approaches.) These estimates have been widely cited in calls to action concerning global mental health.[@patelLancetCommissionGlobal2018; @thelancetglobalhealthMentalHealthMatters2020]
@@
 (2016) published in \emph{The Lancet Psychiatry} argues for an expanded classification of mental disorders under the \acr{GBD} classification scheme to account for underestimation of the burden of mental disorders.[@vigoEstimatingTrueGlobal2016] The authors attribute this underestimation to five main causes: 1) the distinction drawn between mental and neurological diseases; 2) the categorization of self-harm and suicide under injuries; 3) the classification of all chronic pain and somatoform disorders under musculoskeletal disorders; 4) the exclusion of personality disorders; and 5) the exclusion of premature mortality due to mental disorders.
-Using data from the 2013 \acr{GBD} study, Vigo and colleagues re-allocated the entire burden of dementias, epilepsy, migraine, tension-type headache, and self-harm to mental disorders.
+Using data from the 2013 \acr{GBD} study, Vigo and colleagues re-allocated the entire burden of dementia, epilepsy, migraine, tension-type headache, and self-harm to mental disorders.
 In addition, a third of the burden of musculoskeletal disorders without anatomical correlate (i.e., somatoform disorders with prominent pain) was attributed to mental disorders.[@vigoEstimatingTrueGlobal2016] This reallocation attributed 13% of \acr{DALYs} to mental disorders, a 6 percentage point increase from the \acr{GBD} estimate of 7%.
@@
 
+```{r table1_1, echo = FALSE, include = TRUE, out.width = '100%'}
+
+knitr::include_graphics("table1_1.png")
+
+```
 \addcontentsline{lot}{table}{Table 1.1: Comparison of the composition of the global burden of mental disorders, by estimation approach.}
 
-```{r table1_1, echo = FALSE, include = TRUE, out.width = '100%'}
-
-knitr::include_graphics("table1_1.png")
-
-```
 \end{raggedright}
@@
 First, our findings echo in magnitude those of Vigo and colleagues,[@vigoEstimatingTrueGlobal2016] which have highlighted that suicide and premature mortality due to mental disorders are potentially large sources of underestimation in the current \acr{GBD} classification.
-Second, when including these sources of attributable mortality, the economic findings suggest staggering loses.
+Second, when including these sources of attributable mortality, the economic findings suggest staggering losses.
 `r discussion_sentence3`[@bloomGlobalEconomicBurden2011]

### 2023-05-11 paper2.Rmd
Final revisions to manuscript

@@
 A multiverse analysis of `r num_models_multiverse` models found this estimate to be robust to alternative specifications; ecoregion analysis indicated that this association was primarily localized to facilities in the central highlands, where cooler temperatures are more prevalent.
-We further found that higher soil moisture may be associated with higher mental health related visits in the future, with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in visits reported `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)` after a three month lag.
+We further found that higher soil moisture may be associated with higher mental health related visits in the future, with an `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` elevation in visits reported `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)` after a three-month lag.
 Ecoregion analysis suggests more visits are reported in the eastern lowlands and the northern dry deciduous forests when soil moisture rises, which is consistent with the geographic concentration of flood risk in Madagascar.
@@
 Among low-income countries most vulnerable to the health consequences of climate change is Madagascar, a nation that generates one percent *of* one percent of global carbon dioxide emissions.
-Worsening \acr{CCEs} in Madagascar (primarily in the form of droughts, floods, and cyclones) are likely to exacerbate endemic, climate-sensitive threats to health, including malnutrition and malaria.[@rakotoarisonAssessmentRiskVulnerability2018] In particular, persistent drought conditions in recent years have led to extensive food insecurity.[@adamtaylorMadagascarHeadedClimate] Though there is debate concerning the extent to which human activity is directly responsible for Madagascar's current drought,[@harringtonAttributionSevereLow; @zhongManyDimensionsDrought2021] the extremity of the situation has led some observers to classify conditions in Madagascar as the first climate change famine in history.[@worldfoodprogrammeMadagascarSevereDrought2021]
+Worsening \acr{CCEs} in Madagascar (primarily in the form of droughts, floods, and cyclones) are likely to exacerbate endemic, climate-sensitive threats to health, including malnutrition and malaria.[@rakotoarisonAssessmentRiskVulnerability2018] In particular, persistent drought conditions in recent years have led to extensive food insecurity.[@adamtaylorMadagascarHeadedClimate2021] Though there is debate concerning the extent to which human activity is directly responsible for Madagascar's current drought,[@harringtonAttributionSevereLow; @zhongManyDimensionsDrought2021] the extremity of the situation has led some observers to classify conditions in Madagascar as the first climate change famine in history.[@worldfoodprogrammeMadagascarSevereDrought2021]
 
@@
 
-Among facilities reporting any mental health data between 2010 and 2020, data were obtained from `r num_facilities_CSB` public and private primary health centers, known as Centres Santé de Base or CSBs and Formations Sanitaires Privées de Base or FSBs, respectively), `r num_facilities_CHD` district referral hospitals (CHDs), `r num_facilities_CHRR_CHU` regional referral hospitals (CHRRs) and university hospitals (CHUs), for a total of `r num_facilities_pretty` uniquely-identified facilities in our sample.
+Among facilities reporting any mental health data between 2010 and 2020, data were obtained from `r num_facilities_CSB` public and private primary health centers, known as Centres Santé de Base or CSBs, and Formations Sanitaires Privées de Base or FSBs, respectively, `r num_facilities_CHD` district referral hospitals (CHDs), `r num_facilities_CHRR_CHU` regional referral hospitals (CHRRs) and university hospitals (CHUs), for a total of `r num_facilities_pretty` uniquely-identified facilities in our sample.
 
@@
 Among CHD facilities, incidence of mental disorders was aggregated with neurological disorders (coded as “neuro psychiatric disorders”), while CHRR and CHU facilities reported more detailed counts of specific mental disorders, such as depression, personality disorders, and schizophrenia.
-Across all facilities, disaggregated data was reported by age group but not by sex.
-Among CSB facilities, incidences of mental disorders were reported by age group under “mental illnesses and psychic disorders” until June 2015, when reporting was reclassified to “mental disorders,” and disaggregated data was reported by both age and sex.
-A summary of classification by facility type and year is provided in Appendix 2.1, Table S2.1, with English translations of the French disease names provided in Table S2.2.
-and yearly cumulative reported visit totals by disorder reported by facility level and year in Tables S2.3-5.
-
-To address heterogeneity in reporting, our analysis aggregated any monthly visits concerning mental or neurological disorders reported by a facility, irrespective of age and sex, into a summary outcome measure.
+Across all facilities, disaggregated data were reported by age group but not by sex.
+Among CSB facilities, incidences of mental disorders were reported by age group under “mental illnesses and psychic disorders” until June 2015, when reporting was reclassified to “mental disorders”; disaggregated data were reported by both age and sex.
+A summary of classification by facility type and year is provided in Appendix 2.1, Table S2.1, with English translations of the French disease names provided in Table S2.2 and yearly cumulative reported visit totals by disorder reported by facility level and year in Tables S2.3-5.
+
+To address heterogeneity in reporting, our analysis aggregated any monthly visits concerning mental or neurological disorders reported by a facility into a summary outcome measure, irrespective of age and sex.
 To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series.
@@
 To retrieve spatial climate data for the facilities in our sample, it was first necessary to geocode facilities to obtain their latitude and longitude.
-Facility data from \acr{GESIS} included limited geospatial information.
+Facility data from \acr{GESIS} included limited information on the location of facilities.
 While exact facility coordinates were not available, information on the relevant administrative unit served by a facility was included in the data (e.g., regions for CHRRs, districts for CHDs, and communes for CSBs).
@@
 
-First, we considered the role of data cleaning in the outcome data and chose to compare our analysis using the cleaned outcome data against the raw, unadjusted values.
-Second, we chose to compare our findings using data from all facilities (the full sample) against a sample without district and regional hospital (CSB/FSP facilities only).
-Primary care facilities have smaller catchment areas than hospitals; consequently, it is more plausible that climate data for primary care facilities will closely reflect climate exposure to patients compared to referral hospitals.
+First, we considered the role of data cleaning of the outcome data and chose to compare our analysis using the cleaned outcome data against the raw unadjusted values.
+Second, we chose to compare our findings using data from all facilities (the full sample) against a sample without district and regional hospitals (CSB/FSP facilities only).
+Primary care facilities have smaller catchment areas than hospitals; consequently, it is more likely that climate data for primary care facilities will closely reflect patients' climate exposure compared to referral hospitals.
 Third, we considered the decision to model temperature and soil moisture as an additive or interactive relationship (Model 3 vs.
@@
 
-We then interacted the methodological choices to generate `r num_models_multiverse` plausible models.
-Using the effect estimates and confidence intervals for these models, we constructed specification curves for monthly temperature, soil moisture, and—for the `r as.numeric(num_models_multiverse)/3` models that included the cyclone count indicator— cyclone activity to visually compare the distribution of plausible estimates under different combinations.
+We then interacted the methodological choices to generate `r num_models_multiverse` plausible model specifications.
+Using the effect estimates and confidence intervals for these models, we constructed specification curves for monthly temperature, soil moisture, and—for the `r as.numeric(num_models_multiverse)/3` models that included the cyclone count indicator— cyclone activity to visually compare the distribution of plausible estimates for different combinations.
 
@@
 
-Figure \ref{figure_gps_climate} shows the spatial distribution of temperature and soil moisture across the facilities in our sample during January and June 2015, corresponding to the warmer, wet season and the dryer, cool season, respectively.
-When evaluated over time, annual climate trends in Madagascar showed relatively stable distribution of average temperatures, while soil moisture had a slight upward shift through 2020 (Figure \ref{figure_climate_distribution}).
+Figure \ref{figure_gps_climate} shows the spatial distribution of temperature and soil moisture across the facilities in our sample during January and June 2015, corresponding to the warmer, wet season and the drier, cool season, respectively.
+When evaluated over time, annual climate trends in Madagascar showed a relatively stable distribution of average temperatures, while soil moisture had a slight upward shift through 2020 (Figure \ref{figure_climate_distribution}).
 Data of tropical storm and cyclone activity throughout the study period also exhibited seasonal patterns, with most major storms occurring in the hot season, with a peak between February and May (Figure \ref{figure_cyclone}).
@@
 ```{r figure_gps_climate, include = TRUE, echo = FALSE, warnings = FALSE, fig.scap="Spatial distribution of climate conditions across clinics and seasons in Madagascar.", out.extra='', fig.cap="\\label{figure_gps_climate}Spatial distribution of climate conditions across clinics and seasons in Madagascar.
-Mean monthly temperature (top) is measured in degrees Celcius and mean soil moisture is measured in percent saturation (below).", fig.width = 6, fig.height = 7.5, fig.align='center', out.width = '90%'}
+Mean monthly temperature (top) is measured in degrees Celsius  and mean soil moisture is measured in percent saturation (below).", fig.width = 6, fig.height = 7.5, fig.align='center', out.width = '90%'}
 
@@
 A one-degree Celsius increase in temperature was associated with approximately `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` visits reported `r function_dynamic_text_results(section = "main", model_option = 1, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)` by primary clinics and hospitals in Model 1.
-Inclusion of both climate predictors resulted in little change to the measure of association for temperature.
+Inclusion of both climate predictors resulted in little change in the measure of association for temperature.
 In an additive model with soil moisture included (Model 3), the effect estimate associated with temperature grew to `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include ="only")` visits reported `r function_dynamic_text_results(section = "main", model_option = 3, coefficient_option = "exposure_temperature", value = "irr", value_include =TRUE)`.
@@
 ```
-Predicted values of monthly mental health related visits counts under Model 4 echoed the effect estimates from Table 2, with fewer visits reported in warmer months (Figure \ref{figure_marginal}).
+Predicted values of monthly mental health related visit counts under Model 4 echoed the effect estimates from Table 2, with fewer visits reported in warmer months (Figure \ref{figure_marginal}).
 Marginal effect estimates across the distribution of temperatures in our data showed that the greatest level of reduction occurred between 10 and 15 degrees Celsius, with each degree increase associated with 4 to 5 fewer visits related to mental or neurological disorders reported, controlling for other covariates.
@@
 At a lag of 3 months, the elevation in visits was approximately `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include = "only")` `r function_dynamic_text_results(section = "lags", lag_option = 3, coefficient_option = "exposure_sm", value = "irr", value_include =TRUE)`.
-There appeared to be a significant elevation of similar magnitude 13 to 17 months prior, suggesting potential annularity in lagged association.
+There appeared to be a significant elevation of similar magnitude 13 to 17 months prior, suggesting a potential annual pattern in the lagged association.
 Effects for temperature were not significant across any lag; cyclone activity similarly showed no significance in lags under a year, but did show modest, statistically significant associations at lags of 12 months `r function_dynamic_text_results(section = "lags", lag_option = 12, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)` and 15 months `r function_dynamic_text_results(section = "lags", lag_option = 15, coefficient_option = "exposure_cyclone", value = "irr", value_include = TRUE)`.
@@
 \begin{spacing}{1.5}
+
+\addcontentsline{lot}{table}{Table 2.3: Subgroup analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
 
@@
 
-\addcontentsline{lot}{table}{Table 2.3: Subgroup analysis results, summarized by incidence rate ratios (IRRs) and average marginal effects (AME) from Models 1 through 4.}
-
 With respect to soil moisture, while our primary analysis found no evidence of a statistically significant association with reported visits in the full sample, we found evidence of heterogeneity in our subgroup analysis.
@@
 ```{r figure_sensitivity_analysis_temp, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap=paste("Specification curve depicting the effect estimates and confidence intervals for mean monthly temperature (degrees Celsius) across", num_models_multiverse, "models."), out.extra='', fig.cap=paste("\\label{figure_sensitivity_analysis_temp}Specification curve depicting the effect estimates and confidence intervals for mean monthly temperature (degrees Celsius) across", num_models_multiverse, "models.
-In the top panel, estimated incidence rate ratios (IRRs) across different models are depicted as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+In the top panel, estimated incidence rate ratios (IRRs) across different models are shown as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
 The dotted horizontal line depicts a null effect.
@@
 ```{r figure_sensitivity_analysis_sm, include = TRUE, echo=FALSE, warnings = FALSE, fig.scap=paste("Specification curve depicting the effect estimates and confidence intervals for mean monthly soil moisture (percent saturation) across", num_models_multiverse, "models."), out.extra='', fig.cap=paste("\\label{figure_sensitivity_analysis_sm}Specification curve depicting the effect estimates and confidence intervals for mean monthly soil moisture (percent saturation) across", num_models_multiverse, "models.
-In the top panel, estimated incidence rate ratios (IRRs) across different models are depicted as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+In the top panel, estimated incidence rate ratios (IRRs) across different models are shown as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
 The dotted horizontal line depicts a null effect.
@@
 ```{r figure_sensitivity_analysis_cyclone, include = TRUE, echo=FALSE, warnings = FALSE, fig.width = 15, fig.height = 9, fig.align='center', out.width = '95%', fig.scap=paste("Specification curve depicting the effect estimates and confidence intervals for duration of cyclone activity across", num_models_multiverse, "models."), out.extra='', fig.cap=paste("\\label{figure_sensitivity_analysis_cyclone}Specification curve depicting the effect estimates and confidence intervals for cyclone activity (measured as days with a tropical storm or cyclone impacting Madagascar in a month) across", as.numeric(num_models_multiverse)/3, "models.
-In the top panel, estimated incidence rate ratios (IRRs) across different models are depicted as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
+In the top panel, estimated incidence rate ratios (IRRs) across different models are shown as circles; the darkly and lightly shaded regions above and below these circles correspond to 95\\% and 99\\% confidence intervals of these estimates, respectively.
 The dotted horizontal line depicts a null effect.
@@
 
-It is important to note in our interpretation of these findings that the true relationship between reported mental health visits and actual cases of mental disorders is not well understood, particularly in Madagascar, where there is no epidemiological data on the prevalence or distribution of mental disorders in the general population.
+It is important to note that the true relationship between reported mental health visits and actual cases of mental disorders is not well understood in Madagascar due to the lack of epidemiological data on the prevalence or distribution of mental disorders in the general population.
 The changes in mental health visits could reflect changes in the actual cases of mental disorders but could also result from the influence of \acr{CCEs} on help-seeking behavior, diagnostic capacity, or other factors.
@@
 
-An alternative explanation could be that access to mental health services is limited in warmer months due to factors such as increased demand for medical services related to heat-related illnesses.
+An alternative explanation could be that access to mental health services is limited in warmer months due to factors such as the increased demand for medical services related to heat-related illnesses.
 A crowding out of provider availability due to physical complaints in warmer months (for example, malaria-related fever) could lead to decreased availability of provider access for mental disorders, especially at primary health facilities with already limited diagnostic capacity.
@@
 
-Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we observed a significant association of higher soil moisture and visits for mental health complaints in the following quarter, echoing similar findings from United States meteorological data linking higher precipitation with worsened mental health.[@obradovichEmpiricalEvidenceMental2018] In addition, our subgroup analysis also indicated significant and diverging effects among different ecoregions.
-In particular, we found that greater soil moisture was associated with more visits reported in the eastern lowlands and the northern dry deciduous forests, which echoes the geographic concentration of flood risk in Madagascar.[@rakotoarisonSpatialAnalysisRisks2021] Conversely, the observed (though statistically modest) reduction in visits associated with higher soil moisture in the desert and xeric shrublands overlaps with the concentration of drought risk, where increased soil moisture could be taken as an indicator of reduced drought vulnerability.
+Though incidence rate ratios and marginal effect estimates associated with soil moisture were not statistically significant in our main analysis, we observed a significant association of higher soil moisture and visits for mental health complaints in the following quarter, echoing similar findings from United States meteorological data linking higher precipitation with worsened mental health.[@obradovichEmpiricalEvidenceMental2018] In addition, our subgroup analysis also indicated significant and divergent effects among different ecoregions.
+In particular, we found that greater soil moisture was associated with more visits reported in the eastern lowlands and the northern dry deciduous forests, which echoes the geographic concentration of flood risk in Madagascar.[@rakotoarisonSpatialAnalysisRisks2021] Conversely, the observed (though statistically modest) reduction in visits associated with higher soil moisture in the desert and xeric shrublands overlaps with the concentration of drought risk, where higher soil moisture could indicate reduced drought vulnerability.
 It is important to note, however, that the time frame of available GESIS data excludes the most severe period of the ongoing drought in Madagascar, limiting our ability to directly study the impact of the current crisis on population mental health in this analysis.

### 2023-05-11 paper3.Rmd
Adding section on population weighting in Paper 3.
Final revisions to manuscript

@@
  ".
-I did not observe significant variations across predominately Democrat or Republican voting states and counties, and the findings were robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
+I did not observe significant variations across predominantly Democrat or Republican voting states and counties, and the findings were robust to alternative specifications of bandwidth, fixed effects, and data cleaning decisions.")
 
@@
 
-{\bf Background:} A key obstacle to studying the impact of policies on population mental health in the United States (US) is a lack of appropriate high frequency surveillance data.
-A potential marker of population mental health is the use of Internet search data, which enables real-time, large-scale analysis of evolving mental health issues.
-
-{\bf Methods:} I utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to symptoms of depression and anxiety in US states and counties.
-I examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptoms compared with physical health symptoms, and estimated associations between vaccine announcement and changes in mental health symptom search density.
+{\bf Background:} A key obstacle to studying the impact of policies on population mental health in the United States (US) is a lack of appropriate high-frequency surveillance data.
+A potential marker of population mental health is the use of Internet search data, which enables real-time, large-scale analysis of evolving mental health conditions
+
+{\bf Methods:} I utilized controlled interrupted time series approaches to evaluate whether the development of COVID-19 vaccines reduced Google searches related to depression and anxiety in US states and counties.
+I examined how search trends changed following the announcement of vaccine safety and efficacy data for mental health symptom searches compared with physical health symptom searches, and estimated associations between vaccine announcement and changes in mental health symptom search density.
 I adjusted for state, month, and weekday effects, and applied numerous sensitivity analyses to assess the robustness of the findings.
-To explore heterogeneity by predominate political affiliation, I also tested whether the estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
+To explore heterogeneity by predominant political affiliation, I also tested whether the estimates varied among states and counties that predominantly voted for the Democratic Party candidate in the 2020 presidential election compared to the Republican candidate.
 
@@
 `r paper3_abstract` If symptom search density echoes population health, the results would indicate that announcements regarding the development of safe and effective COVID-19 vaccines led to a robust and sustained improvement in mental health.
-These findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
+These findings underscore the importance of timely and transparent communication and highlight the potential application of high-frequency internet search data for population mental health surveillance.
 
@@
 
-While COVID-19 continues to bring unprecedented challenges to societies around the world, the development and distribution of safe and effective vaccines has fundamentally changed the trajectory of the pandemic.
+While COVID-19 continues to bring unprecedented challenges to societies around the world, the development of safe and effective vaccines has fundamentally changed the trajectory of the pandemic.
 Beyond the physical benefits vaccines provide in reducing the risk of infection and associated morbidity and mortality, a growing body of evidence suggests that vaccination has also
@@
 
-A key obstacle to studying the impact of public health policies on population mental health, however, is a lack of appropriate high frequency surveillance data.
+A key obstacle to studying the impact of public health policies on population mental health, however, is a lack of appropriate high-frequency surveillance data.
 A potential marker of population mental health is the use of internet search data, which enables real-time, large-scale analysis of evolving mental health issues.
@@
 
-Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominately English-speaking countries: Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States.
+Search density data for over 400 symptoms were reported by Google across national and subnational regions of six predominantly English-speaking countries: Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States.
 In the \acr{US}, subnational regions include states and counties.
@@
 
-Population estimates for 2020 by \acr{FIPS} code were obtained from the\acr{USDA} Economic Research Service.
+Population estimates for 2020 by \acr{FIPS} code were obtained from the \acr{USDA} Economic Research Service.
 
@@
 ```
-I applied this model for all available `r diseases_n` diseases with county-level data.
+I applied this model for all available `r diseases_n` diseases with county-level data, weighted by population size.
 As search density may rapidly change in response to new announcements, I trimmed the bandwidth of dates to fit the model to 40 days before and after November 16, 2020.
@@
 
-Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals (\acr{CIs}) using heteroskedasticity-robust standard errors.
+Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals ( \acr{CIs}) using heteroskedasticity-robust standard errors.
 
@@
 Examining the plausible model combinations of the multiverse analysis for these three symptoms underscored the importance of regional level to inference, as the use of county-level data (with a greater number of observations) consistently showed similar effect estimates compared to state level estimates, but with much tighter \acr{CIs}, even when geographic fixed effects and narrower bandwidths were included.
-Across all models, the sustained change in search density for anxiety and depression was negative and significant with an alpha of 0.01.
+Across all models, the sustained changes in search density for anxiety and depression were negative and significant with an alpha of 0.01.
 In terms of the estimated level shifts, `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)` models for anxiety (`r round(function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "negative", multiverse_p = 0.01)*100/144,0)`%) had a statistically significant negative change, compared to `r function_dynamic_text_results("multiverse","anxiety", "intercept", multiverse_sign = "positive", multiverse_p = 0.01)` models with a positive one.
@@
 This was particularly observed in the analysis of \acr{US} state-level data, where confidence intervals for the \acr{CITS} effect estimates were statistically equivalent across red and blue states.
-In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties than blue ones, with minor overlap in confidence intervals.
+In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties compared to blue ones, with minor overlap in confidence intervals.
 The observed slope change for searches related to depression among red counties was `r function_dynamic_text_results("political", "depression", "slope", region_option = 1)`, compared to `r function_dynamic_text_results("political", "depression", "slope", region_option = 5)` for blue counties.
@@
 In addition, the use of Google search density as a proxy for population mental health could not be directly validated in the study, as the search data was anonymized and aggregated.
-While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and \acr{US} population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.
+While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and \acr{US} population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high-frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.
 
@@
 If symptom search density echoes population health, the results would indicate that these announcements led to an improvement in mental health, an improvement observed across countries and predominant political party inclination.
-These findings underscore the importance of timely and transparent communication and highlight the potential application of high frequency internet search data for population mental health surveillance.
+These findings underscore the importance of timely and transparent communication and highlight the potential application of high-frequency internet search data for population mental health surveillance.
 

### 2023-05-11 thesis_final_version.Rmd
Final revisions to manuscript

--- 2023-03-11 thesis_final_version.Rmd
@@
 bibliography: main.bib
-# natbiboptions: "numbers"
 csl: https://www.zotero.org/styles/the-lancet
-
-  # intro: intro.bib
-  # ch1: chapter1.bib
-  #
-
 acronyms:
   insert_loa: false
-  loa_title: ""
-
-  # loa_title: "List of Acronyms"
+  insert_links: false
+  loa_title: ''
   keys:
-    - shortname: LMIC
-      longname: low and middle income country
-
+    - shortname: DALYs
+      longname: disability-adjusted life years
+    - shortname: YLLs
+      longname: years of life lost 
+    - shortname: YLDs
+      longname: years of healthy life lost due to disability 
+    - shortname: LMICs
+      longname: low- and middle-income countries
+    - shortname: WHO
+      longname: World Health Organization
+    - shortname: USD
+      longname: United States dollars
+    - shortname: GBD
+      longname: Global Burden of Disease
+    - shortname: GBO
+      longname: Global Health Observatory
+    - shortname: GDP
+      longname: gross domestic product
+    - shortname: NCDs
+      longname: noncommunicable diseases
+    - shortname: PAF
+      longname: population attributable fraction
+    - shortname: VSL
+      longname: value of a statistical life
+    - shortname: IRB
+      longname: Institutional Review Board 
+    - shortname: UIs
+      longname: uncertainty intervals
+    - shortname: CIs
+      longname: confidence intervals
+    - shortname: PPP
+      longname: purchasing power parity
+    - shortname: CCEs
+      longname: climate change-related exposures
+    - shortname: HMIS
+      longname: health management information system
+    - shortname: ESA CCI
+      longname: European Space Agency’s Climate Change Initiative
+    - shortname: ESA CCI SM
+      longname: ESA CCI soil moisture dataset
+    - shortname: ERA5
+      longname: 'European ReAnalysis 5' 
+    - shortname: NOAA
+      longname: United States National Oceanic and Atmospheric Administration
+    - shortname: GESIS
+      longname: Gestion du Système d'Information Sanitaire
+    - shortname: DHIS2
+      longname: 'District Health Information Software 2'
+    - shortname: CSB
+      longname: centre santé de base
+    - shortname: FSB
+      longname: formation sanitaires privées de dase
+    - shortname: CHD/CHRD
+      longname: centre hospitalier de référence de district
+    - shortname: RHINO
+      longname: Routine Health Information Network
+    - shortname: USAID
+      longname: United States Agency for International Development
+    - shortname: US
+      longname: United States
+    - shortname: CHRR
+      longname: centre hospitalier de référence régionale
+    - shortname: CHU
+      longname: centre hospitalier universitaire
+    - shortname: C3S
+      longname: Copernicus Climate Change Service
+    - shortname: ECMWF
+      longname: European Centre for Medium-Range Weather Forecasts
+    - shortname: km
+      longname: kilometers
+    - shortname: MFR La Réunion
+      longname: Météo-France La Réunion
+    - shortname: WMO
+      longname: World Meteorological Organization
+    - shortname: RSMC 
+      longname: Regional Specialized Meteorological Center
+    - shortname: NB
+      longname: negative binomial
+    - shortname: IRRs
+      longname: incidence rate ratios
+    - shortname: FE
+      longname: fixed effects
+    - shortname: CDC
+      longname: Centers for Disease Control and Prevention
+    - shortname: FDA
+      longname: Food and Drug Administration
+    - shortname: EUA
+      longname: Emergency Use Authorization
+    - shortname: MIT
+      longname: Massachusetts Institute of Technology
+    - shortname: FIPS
+      longname: Federal Information Processing Standards
+    - shortname: USDA
+      longname: United States Department of Agriculture
+    - shortname: ITS
+      longname: interrupted time series
+    - shortname: CITS
+      longname: controlled interrupted time series
+    - shortname: MDD
+      longname: major depressive disorder
+    - shortname: ADHD
+      longname: attention deficit hyperactivity disorder
+    - shortname: CoC
+      longname: clouding of consciousness
+    - shortname: GAD
+      longname: generalized anxiety disorder
 ---
@@
 Using the most recently available estimates from the Global Burden of Disease study, we found that the burden of mental disorders is likely much higher than previously estimated, encompassing 16% of disability-adjusted life years in 2019.
-The economic value of this mental health burden was estimated to exceed 4.7 trillion USD using a value of statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.
+The economic value of this mental health burden was estimated to exceed 4.7 trillion United States dollars using a value of a statistical life year approach, accounting for regional losses that range from 3.9% of gross domestic product in Eastern Sub-Saharan Africa to 7.9% in High-income North America.
 
-In Chapter 2, we focused on Madagascar—a low income country that is among the most vulnerable to the health consequences of climate change—and examine how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones.
+In Chapter 2, we focused on Madagascar—a low-income country that is among the most vulnerable to the health consequences of climate change—and examined how health system visits for mental disorders may be shifting in response to climate change exposures such as changes in temperature, soil moisture, and the duration of tropical storms and cyclones.
 Drawing on meteorologic, geospatial, and health system data reported by 3,413 facilities from 2010 to 2020, we conducted an ecological analysis using negative binomial regression.
@@
 In Chapter 3, I investigated how Google search data for mental health symptoms might provide insight into the state of mental health during the COVID-19 pandemic.
-Using an interrupted time series approach with search data from U.S.
-counties, states, and international trends, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression.
-These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent communication and illustrate the potential application of high frequency internet search data for population mental health surveillance.
+Using an interrupted time series approach with search data from Australia, Ireland, New Zealand, Singapore, the United Kingdom, and the United States, I found that announcements of COVID-19 vaccine safety and efficacy data in November 2020 were associated with immediate and sustained declines in search density for anxiety and depression.
+These declines in searches, if taken as a reasonable proxy for population mental health, underscore the importance of timely and transparent public health communication and illustrate the potential application of high-frequency internet search data for population mental health surveillance.
 
@@
 
-```{r todo}
+<!-- ```{r todo} -->
 
-### TO DO / KNOWN ISSUES
+<!-- ### TO DO / KNOWN ISSUES -->
 
-# Acronyms with acronym down
-# Separate bibliography for each section
-# Numbered figures and tables by section
+<!-- # Check that sequential articles are represented by a dash -->
+<!-- # Institutional authors need to be fixed in bibliography -->
+<!-- # Numbered figures and tables by section -->
 
-# Check that sequential articles are represented by a dash
-# Table of figures and tables
-# Institutional authors need to be fixed in bibliography
-
-```
+<!-- ``` -->

### 2023-05-12 paper1.Rmd
Formatting corrections

@@
 
-\vspace{1pt}
+\vspace{6pt}
 
@@
 
-\vspace{24pt}
+\vspace{18pt}
 
@@
 In addition to our base-case economic valuation, we further report our \acr{VSL} estimates using three times \acr{GDP} per capita as the value of a DALY.
-(Alternative valuations using values of $1,000 and $5,000, as well as \acr{PPP}-adjusted \acr{GDP} per capita, are reported in Tables S1.5 and S1.6 of Appendix 1.)
 
@@
 Further adjusting for purchasing power parity, the global value of mental illness losses would exceed 7.2 trillion international dollars in 2019 (Table S1.7).
+(Alternative valuations using values of $1,000 and $5,000, as well as \acr{PPP}-adjusted \acr{GDP} per capita, are reported in Table S1.8 of Appendix 1.)
 

### 2023-05-12 thesis_final_version.Rmd
Formatting corrections

@@
     number_sections: TRUE
-
-  # pdf_document:
-  #   pandoc_args: !expr acronymsdown::add_filter()
-  #   number_sections: TRUE
 
@@
   - \usepackage[nottoc]{tocbibind}
-  # - \usepackage{acro}
-  # - \usepackage{float}
-  # - \usepackage{chapterbib}
-  # - \usepackage{lastpage}
-  # - \usepackage{dcolumn}
-  # - \usepackage[backend=biber,style=authoryear-icomp]{biblatex}
-  # - \addbibresource{bibliography.bib}
 
@@
 
+\addcontentsline{toc}{section}{Title page}
+
 {\bf `r toupper("Quantitative Approaches Towards Evaluating the Global Burden of Mental Illness")`}
@@
 
-`r format(Sys.time(), '%B %Y')`
+`r format(as.Date('04-26-2023', '%m-%d-%Y'), '%B %Y')`
 
@@
 
+\addcontentsline{toc}{section}{Copyright}
+
 \vspace*{\fill}
-© `r format(Sys.time(), '%Y')` Daniel Arias. All rights reserved.
+© `r format(Sys.time(), '%Y')` Daniel Alejandro Arias. All rights reserved.
 
@@
 
-Dissertation Advisor: Stéphane Verguet \hfill Daniel Arias
+Dissertation Advisor: Stéphane Verguet \hfill Daniel Alejandro Arias
 
@@
 ```
-
-\newpage
-
-<!-- ```{r todo} -->
-
-<!-- ### TO DO / KNOWN ISSUES -->
-
-<!-- # Check that sequential articles are represented by a dash -->
-<!-- # Institutional authors need to be fixed in bibliography -->
-<!-- # Numbered figures and tables by section -->
-
-<!-- ``` -->

### 2023-05-15 appendix_2.1.Rmd
Additional typesettting changes

@@
 While primary, district, and regional referral facilities in Madagascar all reported monthly visits related to mental disorders in \acr{GESIS}, case definitions varied across facilities of different levels.
-Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visit by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).
-
-Disaggregated data was available by age; among adults, however, disaggregated data for adults ages 25 to 59 and adults 60 years and older was only reported by primary health facilities after 2015.
+Disaggregated data by specific condition (e.g., depression, schizophrenia, etc.) were only reported among regional referral hospitals and university hospitals; for all other facilities, visits by type of mental heath complaint were reported in aggregate (e.g., "Neuro-psychic diseases" for district hospitals).
+
+Disaggregated data were available by age; among adults, however, disaggregated data for adults ages 25 to 59 and adults 60 years and older were only reported by primary health facilities after 2015.
 For all other years and all other facilities, these age categories were not separately reported.
-Similarly, data by sex was only reported for primary health facilities after 2015.
+Similarly, data by sex were only reported for primary health facilities after 2015.
 Referrals were reported by primary health facilities and district hospitals.
@@
 
-Visual inspect of our data showed potential outliers, which may have arisen due to data entry mistakes, synchronization errors, and other sources.
+Visual inspection of our data showed potential outliers, which may have arisen due to data entry mistakes, synchronization errors, and other sources.
 To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series.
@@
 By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may have reflected true variances in visit counts (for example, visits reported by a large, regional reference hospital) while addressing potential errors in data entry.
-Interpolated values were coerced to the nearest integer.
+Interpolated values were rounded to the nearest integer.
 

### 2023-05-15 appendix_2.2.Rmd
Additional typesettting changes

@@
 #     title = md("**Examples of duplicate facility names in different regions**")) %>%
-#   tab_options(table.font.names = "Source Sans Pro") %>%
+#   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
 #   tab_style(
@@
 
-``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique()
-column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique()
-
-r_old <- column1 %>% dplyr::select(region_name) %>% unique()
-r_new <- column2 %>% dplyr::select(region) %>% unique()
-
-cbind(r_old, r_new) %>% mutate(test = region_name == region) %>%
-  filter(test == FALSE) %>%
-  relocate(region, .before = region_name) %>%
-  rename("Name in data" = region,
-         "Standardized name" = region_name) %>%
-  dplyr::select(!test) %>%
-  gt() %>%
-  tab_header(
-    title = md("**Table S2.6: Standardization of region names**"))
-
-```
+```{r table_s_2_6, echo = FALSE, include = TRUE, out.height = '97%'}
+
+knitr::include_graphics("table_s_2_6.png")
+
+```
+
+<!-- ``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
+
+<!-- column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique() -->
+<!-- column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique() -->
+
+<!-- r_old <- column1 %>% dplyr::select(region_name) %>% unique() -->
+<!-- r_new <- column2 %>% dplyr::select(region) %>% unique() -->
+
+<!-- cbind(r_old, r_new) %>% mutate(test = region_name == region) %>% -->
+<!--   filter(test == FALSE) %>% -->
+<!--   relocate(region, .before = region_name) %>% -->
+<!--   rename("Name in data" = region, -->
+<!--          "Standardized name" = region_name) %>% -->
+<!--   dplyr::select(!test) %>% -->
+<!--   gt() %>% -->
+<!--   tab_header( -->
+<!--     title = md("**Table S2.6: Standardization of region names**")) %>% -->
+<!--   gtsave("table_s_2_6.docx") -->
+
+<!-- ``` -->
 
@@
 
-``` {r table_standardization_district_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-district_old <- c("Anosibe An'Ala", "Antananarivo Atsimon", "Antananarivo Avaradr", "Antananarivo Renivoh", "Fenoarivo Atsinanana", "Mananara Avaratra", "Nosy Boraha", "Ambovombe Androy", "Tsiombe", "Amboasary Atsimo", "Ankazoabo Atsimo", "Toliara I", "Toliara II", "Toliara-I", "Toliara-II", "Midongy Atsimo", "Antanambao Manampont", "Antanambao Manampotsy", "Vohibinany", "Ambatoboeny", "FenoarivoBe", "Nosy Be", "Fianarantsoa II", "lalangina", "Belo Tsiribihina", "Vohimarina", "Befandriana Avaratra", "Boriziny", "Nosy Varika")
-
-district_new <- c("Anosibe-An'ala", "Antananarivo Atsimondrano", "Antananarivo Avaradrano", "Antananarivo Renivohitra", "Fenerive Est", "Mananara-Avaratra", "Sainte Marie", "Ambovombe-Androy", "Tsihombe", "Amboasary-Atsimo", "Ankazoabo", "Toliary-I", "Toliary-II", "Toliary-I", "Toliary-II", "Midongy-Atsimo", "Antanambao Manampontsy", "Antanambao Manampontsy", "Brickaville", "Ambato Boeni", "Fenoarivobe", "Nosy-Be", "Fianarantsoa I", "Lalangina", "Belo Sur Tsiribihina", "Vohemar", "Befandriana Nord", "Port-Berge (Boriziny-Vaovao)", "Nosy-Varika")
-
-as.data.frame(cbind(district_old, district_new)) %>%
-  arrange(district_old) %>%
-  rename("Name in data" = district_old,
-         "Standardized name" = district_new) %>%
-  gt() %>%
-  tab_header(
-    title = md("**Table S2.7: Standardization of district names**")) %>%
-  tab_options(table.font.names = "Source Sans Pro") %>%
-  tab_style(
-    locations = cells_column_labels(),
-    style     = list(
-      cell_text(weight = "bold"))
-  )
-```
+```{r table_s_2_7, echo = FALSE, include = TRUE, out.height = '97%'}
+
+knitr::include_graphics("table_s_2_7.png")
+
+```
+
+<!-- ``` {r table_standardization_district_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
+
+<!-- district_old <- c("Anosibe An'Ala", "Antananarivo Atsimon", "Antananarivo Avaradr", "Antananarivo Renivoh", "Fenoarivo Atsinanana", "Mananara Avaratra", "Nosy Boraha", "Ambovombe Androy", "Tsiombe", "Amboasary Atsimo", "Ankazoabo Atsimo", "Toliara I", "Toliara II", "Toliara-I", "Toliara-II", "Midongy Atsimo", "Antanambao Manampont", "Antanambao Manampotsy", "Vohibinany", "Ambatoboeny", "FenoarivoBe", "Nosy Be", "Fianarantsoa II", "lalangina", "Belo Tsiribihina", "Vohimarina", "Befandriana Avaratra", "Boriziny", "Nosy Varika") -->
+
+<!-- district_new <- c("Anosibe-An'ala", "Antananarivo Atsimondrano", "Antananarivo Avaradrano", "Antananarivo Renivohitra", "Fenerive Est", "Mananara-Avaratra", "Sainte Marie", "Ambovombe-Androy", "Tsihombe", "Amboasary-Atsimo", "Ankazoabo", "Toliary-I", "Toliary-II", "Toliary-I", "Toliary-II", "Midongy-Atsimo", "Antanambao Manampontsy", "Antanambao Manampontsy", "Brickaville", "Ambato Boeni", "Fenoarivobe", "Nosy-Be", "Fianarantsoa I", "Lalangina", "Belo Sur Tsiribihina", "Vohemar", "Befandriana Nord", "Port-Berge (Boriziny-Vaovao)", "Nosy-Varika") -->
+
+<!-- as.data.frame(cbind(district_old, district_new)) %>% -->
+<!--   arrange(district_old) %>% -->
+<!--   rename("Name in data" = district_old, -->
+<!--          "Standardized name" = district_new) %>% -->
+<!--   gt() %>% -->
+<!--   tab_header( -->
+<!--     title = md("**Table S2.7: Standardization of district names**")) %>% -->
+<!--   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>% -->
+<!--   tab_style( -->
+<!--     locations = cells_column_labels(), -->
+<!--     style     = list( -->
+<!--       cell_text(weight = "bold")) -->
+<!--   ) %>% -->
+<!--   gtsave("table_s_2_7.docx") -->
+<!-- ``` -->
 
@@
 
-``` {r table_standardization_district_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-district_tobechanged <- c("Antsirabe II", "Port-Berge (Boriziny-Vaovao)", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Betafo", "Vohemar", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I")
-
-district_communes_affected <- c("Antanamalaza", "Andribavontsona", "Ambalamidera", "Andoharanomaintso", "Anjoma-tsara", "Ankarinarivo", "Fanjakana", "Iavinomby", "Isorana", "Nasandratrony", "Soatanana", "Alakamisy Ambohimahy", "Ambalakely", "Ambalamahasoa", "Andianjanto Est", "Andrainjanto Centre", "Androy", "Fandravandava", "Ialananidro", "Ivoamba", "Mahatsinjo", "Mahatsinjony", "Sahambavy", "Taindambo", "Antanambao Ambary", "Antsahavaribe", "Ambohimahavelona", "Ambolofoty", "Anakao", "Analamisampy", "Andranohinaly", "Andranovory", "Ankililoaka", "Ankilimalinika", "Beheloka", "Behompy", "Belalanda", "Betsinjaka", "Manombo", "Manorofify", "MarofotyMarofoty", "Maromiandra", "Miary", "Milenaka", "Mitsinjo", "Soalara", "St Augustin", "Tsianisiha", "Alakamisy Itenina", "Andranomiditra", "Andranovorivato", "Ankaromalaza Mifanas", "Ihazoara", "Mahaditra", "Mahasoabe", "Maneva", "Soaindrana", "Talata Ampano", "Vohibato Ouest", "Vohimarina", "Vohitrafeno")
-
-district_changed <- c("Ambatolampy", "Analalava", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Mandoto", "Sambava", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato")
-
-as.data.frame(cbind(district_tobechanged, district_changed, district_communes_affected)) %>%
-  arrange(district_tobechanged) %>%
-  relocate(district_communes_affected, .before = district_tobechanged) %>%
-  rename("District name in data" = district_tobechanged,
-         "Communes" = district_communes_affected,
-         "District name, updated" = district_changed) %>%
-  gt() %>% 
-  tab_header(
-    title = md("**Table S2.8: Standardization of district names, based on commune name**")) %>%
-  tab_options(table.font.names = "Source Sans Pro") %>%
-  tab_style(
-    locations = cells_column_labels(),
-    style     = list(
-      cell_text(weight = "bold"))
-  )
-
-```
+```{r table_s_2_8, echo = FALSE, include = TRUE, out.height = '97%'}
+
+knitr::include_graphics("table_s_2_8.png")
+
+```
+
+<!-- ``` {r table_standardization_district_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
+
+<!-- district_tobechanged <- c("Antsirabe II", "Port-Berge (Boriziny-Vaovao)", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Betafo", "Vohemar", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I") -->
+
+<!-- district_communes_affected <- c("Antanamalaza", "Andribavontsona", "Ambalamidera", "Andoharanomaintso", "Anjoma-tsara", "Ankarinarivo", "Fanjakana", "Iavinomby", "Isorana", "Nasandratrony", "Soatanana", "Alakamisy Ambohimahy", "Ambalakely", "Ambalamahasoa", "Andianjanto Est", "Andrainjanto Centre", "Androy", "Fandravandava", "Ialananidro", "Ivoamba", "Mahatsinjo", "Mahatsinjony", "Sahambavy", "Taindambo", "Antanambao Ambary", "Antsahavaribe", "Ambohimahavelona", "Ambolofoty", "Anakao", "Analamisampy", "Andranohinaly", "Andranovory", "Ankililoaka", "Ankilimalinika", "Beheloka", "Behompy", "Belalanda", "Betsinjaka", "Manombo", "Manorofify", "MarofotyMarofoty", "Maromiandra", "Miary", "Milenaka", "Mitsinjo", "Soalara", "St Augustin", "Tsianisiha", "Alakamisy Itenina", "Andranomiditra", "Andranovorivato", "Ankaromalaza Mifanas", "Ihazoara", "Mahaditra", "Mahasoabe", "Maneva", "Soaindrana", "Talata Ampano", "Vohibato Ouest", "Vohimarina", "Vohitrafeno") -->
+
+<!-- district_changed <- c("Ambatolampy", "Analalava", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Mandoto", "Sambava", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato") -->
+
+<!-- as.data.frame(cbind(district_tobechanged, district_changed, district_communes_affected)) %>% -->
+<!--   arrange(district_tobechanged) %>% -->
+<!--   relocate(district_communes_affected, .before = district_tobechanged) %>% -->
+<!--   rename("District name in data" = district_tobechanged, -->
+<!--          "Communes" = district_communes_affected, -->
+<!--          "District name, updated" = district_changed) %>% -->
+<!--   gt() %>%  -->
+<!--   tab_header( -->
+<!--     title = md("**Table S2.8: Standardization of district names, based on commune name**")) %>% -->
+<!--   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>% -->
+<!--   tab_style( -->
+<!--     locations = cells_column_labels(), -->
+<!--     style     = list( -->
+<!--       cell_text(weight = "bold")) -->
+<!--   )%>% -->
+<!--   gtsave("table_s_2_8.docx") -->
+
+<!-- ``` -->
+
 \addcontentsline{lot}{table}{Table S2.9: Standardization of commune names.}
 
-``` {r table_standardization_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-commune_old <- c("Alakamisy Ambohimahy", "Alakamisy Itenina", "Ambadrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy   II", "Ambalamidera", "AmbalapaisoII", "Ambararatabe /Nord",
-                 "Ambarijeby Atsimo", "Ambatoben'anja", "AmbatofisakaII", "AmbatoharananaI", "Ambatolampy Tsimahaf", "Ambatolampy Tsimahafotsy", "Ambatoriha/Est", "Ambatotsipihana", 
-                 "Ambatovala", "Ambatry", "Ambinanin'Andravory", "Ambinaninandro", "Ambinaniroa-Andonaka", "Ambodiadabo Maitsokely", "Ambodiadabo", "Ambodiampana Lokoho",
-                 "Ambodiampanana", "Ambodifarihy", "Ambodihazambo", "Ambodimanga  I", "Ambodimanga II-B", "Ambodimotso Atsimo", "AmbodinonokaAntaratr", "Ambodirian'Isahafary",
-                 "Amboditandroho", "Ambohibao Atsimo", "Ambohibary", "Ambohijato Mandritsara", "Ambohimahavelona", "Ambohimalaza", "Ambohimàna", "Ambohimanga Sud",
-                 "Ambohimanjaka", "AmbohimiarinaII", "Ambohitralalana", "Ambohitrandriamanitr", "AmbohitsaraEst", "Ambolidibe Atsinanana", "Ambolofoty", "Amboropotsy",
-                 "Ampasimadinika", "Ampasimborajka", "Ampasimpotsy", "Ampasipotsy Gare", "Ampasipotsy Madialaz", "Ampataka Manampaneva", "Ampataka Maroreny", "Anakao",
-                 "Analalaiva", "Analamisampy", "Analamitsivala", "Anbatomainty", "Andanandava", "Andianjanto Est", "Andimaka", "Andoharanomaintso", "Andoharanomaintso",
-                 "Andrainjanto Centre", "Andranohinaly", "Andranomiditra", "Andranomiely", "Andranovorivato", "Andranovory", "Andravola", "Andrebakely", "Andribavontsona",
-                 "Androndrona", "Androy", "Anjapaly", "Anjeke Ankilira", "Anjeva Gare", "Anjiabe", "Anjiaija", "Anjoman'Ankona", "Anjoma-tsara", "Ankadinondry", "Ankafina",
-                 "Ankarinarivo", "Ankaromalaza Mifanas", "Ankasakasa", "Ankazoabo", "Ankazotokana I", "Ankiabe Salohy", "Ankiakabe-Nord", "Ankililoaka", "Ankilimalinika",
-                 "Ankirondro", "Anontsibe", "Anosiarivo", "Anosy Tsararafara", "Antalaha", "Antanamalaza", "Antanambao Ambary", "Antanambao I", "Antanambao Manampotsy",
-                 "Antanambaon'Amberina", "Antananarivo I", "Antananarivo II", "Antananarivo III", "Antananarivo IV", "Antananarivo V", "Antananarivo VI", "Antanandava Nord",
-                 "Antananivo /Haut", "Antanetibe Mahazaza", "Antanimora- Sud", "Antenina I", "Antoby", "Antohaboto", "Antongo", "Antokoboritelo", "Antranonkarany", "Antsahavaribe",
-                 "Antsakomanondro", "Antsapanimahazo", "Antsirabe I", "Antsiranana I", "Antsoantany", "Bealampoana", "Bealanana I", "Beampombo  I", "Beandrarezona I",
-                 "Befandriana Avaratra", "Befandriana-Sud", "Befetra", "Befotaka Avaratra", "Befotaka", "Beheloka", "Behera", "Behompy", "Belafika Haut", "Belalanda",
-                 "Belambo", "Belaoko Marovato", "Belo sur Mer", "Belo Tsiribihina", "Belotsiribihina", "Bemaneviky H", "BenatoToby", "Beraketa", "Berevo Ranobe",
-                 "Beroy Sud", "Betioky Sud", "Betsakotsako Andrano", "Betsimiositra", "Betsinjaka", "Bevoay Beretra", "Bevonotro", "Efatsy Anandroza", "Enakara Haut",
-                 "Enaniiliha", "Ereda", "Etrotroka", "Fandravandava", "Fanjakana", "Faux-Cap", "Fenoevo", "Fieferana", "Foulpointe", "Ialananidro", "Iavinomby", "Ibity",
-                 "Ihaborano Namohora", "Ihazoara", "Iloto", "Imady", "Imeritsiatosika", "Isaka Ivondro", "Isaraha", "Isorana", "Ivatana", "Ivato Aéroport", "Ivoamba",
-                 "Ivony", "Kalalao", "Kianjandrandrakefina", "labohazo", "Lavaraty Ivondro", "Mahaditra", "Mahafasa", "Mahajanga I", "Mahasoabe", "Mahatsara Lefaka",
-                 "Mahatsinjo Atsinanana", "Mahatsinjo", "Mahatsinjony", "Mahazina", "Manajary Urbain", "Manakambahiny Est", "Manakambahiny Ouest", "Manakara(com)",
-                 "Manambotra Sud", "Manapatrana", "Mandromodromotra", "Maneva", "Mangarivot", "Manombo", "Manorofify", "Marintampona", "Marivorahona", "Maroarivo", 
-                 "MarofotyMarofoty", "Maromiandra", "Maromokotra-Loky", "Marosavoa Bas", "Marovitsika", "Merimandroso", "Miary", "Milenaka", "Mitsinjo", "Mizilo Gare", 
-                 "Moramanga Urbain", "Morarano Gare", "Morombe", "Nagnarena", "Nasandratrony", "Niarovana", "Nosibe Masianaka", "Onilhy", "Port Bergé I", "Port Bergé II",
-                 "Rantabe Est", "Rantabe Sud", "Razanaka", "Sahamadio", "Sahambavy", "Sahambo", "Sahanivotry Atsimo", "Sakamahily-Ouest", "Sakay", "Sakona", "Sambava Urbain",
-                 "Sarobaratra", "Soaindrana", "Soalara", "Soatanana", "St Augustin", "Taindambo", "Talata Ampano", "Talatan'Angavo", "Taolognaro", "Tanakamba", "Tanambao  Daoud",
-                 "Tanambaovatrakaka", "Tanandava-Sud", "Tanandrano", "Toamasina Suburbain", "Tovòna", "Tsarahonenana", "Tsarajomoko", "Tsaratanana", "Tsiafajavona Ankarat",
-                 "Tsianisiha", "Tsianofàna", "Tsinjoarivo", "Tsiombe", "Tsiroanomadidy Ville", "Tsiroanomandidy Ville", "Vatolatsaky", "Vilihazo", "Vinaninony Avaratra",
-                 "Vineta Andamasiny", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zomabealoka")
-
-commune_new <- c("Alakamisy Ambohimaha", "Alakamisy Itenina", "Ambandrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy II", "Ambalamidera II", "Ambalapaiso II", "Ambararatabe Nord",
-                 "Ambarijeby Sud", "Ambatoben'anjavy", "Ambatofisaka II", "Ambatoharanana", "Ambatolampy", "Ambatolampy", "Ambatoriha Est", "Ambatotsipihina", "Ambatolava", 
-                 "Ambatry Mitsinjo", "Ambinanin'andravory", "Ambinanindrano", "Ambinaniroa", "Ambodiadabo", "Ambodiadabo M", "Ambodiampana", "Ambodiampana", "Ambodifarihy Fenomanana",
-                 "Ambodihazoambo", "Ambodimanga I","Ambodimanga II", "Ambodimotso Sud", "Ambodinonoka", "Ambodirian'i Sahafary", "Amboditandroroho", "Ambohibao Sud",
-                 "Ambohibary Vohilena", "Mandritsara", " Ambohimahavelona", "Ambohimalaza Miray", "Ambohimana", "Ambohimanga Du Sud", "Sahatsiho Ambohimanjaka",
-                 "Ambohimiarina II", "Ambohitralanana", "Ambohitrandriamanitra", "Ambohitsara Est", "Ambolidibe Est", "Ambolofoty", "Amborompotsy", "Ampasimadinika Manambolo",
-                 "Ampasimboraka", "Ampasimpotsy Sud", "Ampasimpotsy Gara", "Ampasipotsy Mandialaza", "Manampaneva", "Ampatakamaroreny", "Anakao", "Analaiva", "Analamisampy",
-                 "Analamitsivalana", "Ambatomainty", "Antanandava", "Andrainjato Est", "Andimaky Manambolo", "Andoharanomaitso", "Andoharanomaitso", "Andrainjato Centre",
-                 "Andranohinaly", "Andranomiditra", "Rambolamasoandro Andranomiely", "Andranovorivato", "Andranovory", "Andravola Vohipeno", "Andrebakely Nord", "Andribavontsona",
-                 "Androndrono", "Androy", "Anjampaly", "Anjeky Ankilikira", "Anjeva Gara", "Anjiabe Ambony", "Anjiajia", "Anjoman'ankona", "Anjoma Itsara", "Ankadinondry Sakay",
-                 "Ankafina Tsarafidy", "Ankarinarivo Manirisoa", "Ankaromalaza Mifanasoa", "Ankasakasa Tsibiray", "Ankazoabo Sud", "Ankazotokana", "Ankiabe-Salohy", " Ankiakabe Nord",
-                 "Ankililoaka", "Ankilimalinike", "Bemarivo Ankirondro", "Anontsibe Centre", "Anosiarivo I", "Anosy Tsararafa", " Antalaha Ambonivohitra", "Antanamalaza", "Antanambao Ambary",
-                 "Antanambao", "Antanambao Manampontsy", "Antanambaon'amberina", "1er Arrondissement", "2e Arrondissement", "3e Arrondissement", "4e Arrondissement", "5e Arrondissement",
-                 "6e Arrondissement", "Antanandava", "Antananivo Haut", "Antanetibe", "Antanimora Atsimo", "Antenina", "Antoby Est", "Antohabato", "Antongo Vaovao", "Marovitsika Sud", "Antranokarany",
-                 "Antsahavaribe", "Antsakoamanondro", "Antsampanimahazo", "Antsirabe Afovoany Atsinanana", "Diego Suarez", "Antsoatany", "Bealampona", "Bealanana", "Beampombo I",
-                 "Beandrarezona", "Befandriana Nord", "Befandriana Sud", "Befeta", "Befotaka Nord", "Befotaka Sud", "Beheloka", "Behara", "Behompy", "Belafike Haut", "Belalanda",
-                 "Belambo Firaisana", "Belaoka Marovato", "Belo Sur Mer", "Belo Sur Tsiribihina", "Belo Sur Tsiribihina", "Bemaneviky Haut Sambirano", "Benato Toby", "Bereketa", 
-                 "Berevo/ranobe", "Beroy Atsimo", "Betioky Atsimo", "Betsakotsako Andranotsara", "Betsimisotra", "Betsinjaka", " Beretra Bevoay", "Bevonotra", "Efatsy", "Enakara-Haut",
-                 "Enaniliha", "Erada", "Etrotroka Atsimo", "Fandrandava", "Fanjakana", "Betanty (Faux Cap)", "Fenoevo-Efita", "Fiaferana", "Mahavelona (Foulpointe)", "Ialananindro", 
-                 "Iavonomby Vohibola", "Alatsinainy Ibity", "Namohora Iaborano", "Ihazoara", "Menamaty Iloto", "Imerina Imady", "Imerintsiatosika", "Isaka-Ivondro", "Isahara",
-                 "Isorana", "Vatana", "Ivato Aeroport", "Ivoamba", "Ivony Miaramiasa", "Ikalalao", "Kianjandrakefina", "Iabohazo", "Ivondro", "Mahaditra", "Mahafasa Centre", 
-                 "Mahajanga", "Mahasoabe", "Mahatsara Iefaka", "Mahatsinjo Est", "Mahatsinjony", "Mahatsinjony", "Mahazina Ambohipierenana", "Mananjary", "Manakambahiny Antsinanana",
-                 "Manakambahiny Andrefana", "Manakara", "Manambotra Atsimo", "Manampatrana", "Mandromondromotra", "Maneva", "Mangarivotra", "Manombo Sud", "Manorofify", "Maritampona", 
-                 "Tanambao Marivorahona", "Maroarivo Ankazomanga", "Marofoty", "Maromiandra", "Maromokotra Loky", "Marosavoa", "Marovitsika Sud", "Imerimandroso", "Miary Ambohibola", 
-                 "Milenaka", "Mitsinjo Betanimena", "Mizilo Gara", "Moramanga", "Morarano Gara", "Cu Morombe", "Nanarena Besakoa", "Nasandratrony", "Niarovana Marosampanana", 
-                 "Masianaka", "Onilahy", "Port Berge", "Port Berge II", "Rantabe", "Rantabe", "Vohipeno Razanaka", "Sahamadio Fisakana", "Sahambavy", "Sahambano", "Sahanivotry Manandona",
-                 "Sakamahily", "Tanamarina Sakay", "Sakoana", "Sambava Cu", "Sarobaratra Ifanja", "Soaindrana", "Soalara Sud", "Soatanana", "Saint Augustin", "Taindambo", "Tatala Ampano", 
-                 "Talata Angavo", "Fort-Dauphin", "Tanakambana", "Tanambao Daoud", "Tanambao Vahatrakaka", "Tanandava Sud", "Tandrano", "Toamasina Suburbaine", "Tovona", "Tsarahonenana Sahanivotry",
-                 "Tsarajomoka", "Tsaratanana I", "Tsiafajavona Ankaratra", "Tsianisiha", "Tsianofana", "Tsinjoarivo Imanga", "Tsihombe", "Tsiroanomandidy Fihaonana", 
-                 "Tsiroanomandidy Fihaonana", "Vatolatsaka", "Viliahazo", "Vinaninony Atsimo", "Andamasiny Vineta", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zoma Bealoka")
-
-as.data.frame(cbind(commune_old, commune_new)) %>%
-  arrange(commune_old) %>%
-  mutate(test = commune_new == commune_old) %>%
-  filter(test == FALSE) %>%
-  dplyr::select(!test) %>%
-  rename("Name in data" = commune_old,
-         "Standardized name" = commune_new) %>%
-  gt() %>%
-  tab_header(
-    title = md("**Table S2.9: Standardization of commune names**")) %>%
-  tab_options(table.font.names = "Source Sans Pro") %>%
-  tab_style(
-    locations = cells_column_labels(),
-    style     = list(
-      cell_text(weight = "bold"))
-  )
+```{r table_s_2_9, echo = FALSE, include = TRUE, out.height = '97%'}
+
+knitr::include_graphics("table_s_2_9a.png")
+knitr::include_graphics("table_s_2_9b.png")
+
+```
+
+<!-- ``` {r table_standardization_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
+
+<!-- commune_old <- c("Alakamisy Ambohimahy", "Alakamisy Itenina", "Ambadrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy   II", "Ambalamidera", "AmbalapaisoII", "Ambararatabe /Nord", -->
+<!--                  "Ambarijeby Atsimo", "Ambatoben'anja", "AmbatofisakaII", "AmbatoharananaI", "Ambatolampy Tsimahaf", "Ambatolampy Tsimahafotsy", "Ambatoriha/Est", "Ambatotsipihana",  -->
+<!--                  "Ambatovala", "Ambatry", "Ambinanin'Andravory", "Ambinaninandro", "Ambinaniroa-Andonaka", "Ambodiadabo Maitsokely", "Ambodiadabo", "Ambodiampana Lokoho", -->
+<!--                  "Ambodiampanana", "Ambodifarihy", "Ambodihazambo", "Ambodimanga  I", "Ambodimanga II-B", "Ambodimotso Atsimo", "AmbodinonokaAntaratr", "Ambodirian'Isahafary", -->
+<!--                  "Amboditandroho", "Ambohibao Atsimo", "Ambohibary", "Ambohijato Mandritsara", "Ambohimahavelona", "Ambohimalaza", "Ambohimàna", "Ambohimanga Sud", -->
+<!--                  "Ambohimanjaka", "AmbohimiarinaII", "Ambohitralalana", "Ambohitrandriamanitr", "AmbohitsaraEst", "Ambolidibe Atsinanana", "Ambolofoty", "Amboropotsy", -->
+<!--                  "Ampasimadinika", "Ampasimborajka", "Ampasimpotsy", "Ampasipotsy Gare", "Ampasipotsy Madialaz", "Ampataka Manampaneva", "Ampataka Maroreny", "Anakao", -->
+<!--                  "Analalaiva", "Analamisampy", "Analamitsivala", "Anbatomainty", "Andanandava", "Andianjanto Est", "Andimaka", "Andoharanomaintso", "Andoharanomaintso", -->
+<!--                  "Andrainjanto Centre", "Andranohinaly", "Andranomiditra", "Andranomiely", "Andranovorivato", "Andranovory", "Andravola", "Andrebakely", "Andribavontsona", -->
+<!--                  "Androndrona", "Androy", "Anjapaly", "Anjeke Ankilira", "Anjeva Gare", "Anjiabe", "Anjiaija", "Anjoman'Ankona", "Anjoma-tsara", "Ankadinondry", "Ankafina", -->
+<!--                  "Ankarinarivo", "Ankaromalaza Mifanas", "Ankasakasa", "Ankazoabo", "Ankazotokana I", "Ankiabe Salohy", "Ankiakabe-Nord", "Ankililoaka", "Ankilimalinika", -->
+<!--                  "Ankirondro", "Anontsibe", "Anosiarivo", "Anosy Tsararafara", "Antalaha", "Antanamalaza", "Antanambao Ambary", "Antanambao I", "Antanambao Manampotsy", -->
+<!--                  "Antanambaon'Amberina", "Antananarivo I", "Antananarivo II", "Antananarivo III", "Antananarivo IV", "Antananarivo V", "Antananarivo VI", "Antanandava Nord", -->
+<!--                  "Antananivo /Haut", "Antanetibe Mahazaza", "Antanimora- Sud", "Antenina I", "Antoby", "Antohaboto", "Antongo", "Antokoboritelo", "Antranonkarany", "Antsahavaribe", -->
+<!--                  "Antsakomanondro", "Antsapanimahazo", "Antsirabe I", "Antsiranana I", "Antsoantany", "Bealampoana", "Bealanana I", "Beampombo  I", "Beandrarezona I", -->
+<!--                  "Befandriana Avaratra", "Befandriana-Sud", "Befetra", "Befotaka Avaratra", "Befotaka", "Beheloka", "Behera", "Behompy", "Belafika Haut", "Belalanda", -->
+<!--                  "Belambo", "Belaoko Marovato", "Belo sur Mer", "Belo Tsiribihina", "Belotsiribihina", "Bemaneviky H", "BenatoToby", "Beraketa", "Berevo Ranobe", -->
+<!--                  "Beroy Sud", "Betioky Sud", "Betsakotsako Andrano", "Betsimiositra", "Betsinjaka", "Bevoay Beretra", "Bevonotro", "Efatsy Anandroza", "Enakara Haut", -->
+<!--                  "Enaniiliha", "Ereda", "Etrotroka", "Fandravandava", "Fanjakana", "Faux-Cap", "Fenoevo", "Fieferana", "Foulpointe", "Ialananidro", "Iavinomby", "Ibity", -->
+<!--                  "Ihaborano Namohora", "Ihazoara", "Iloto", "Imady", "Imeritsiatosika", "Isaka Ivondro", "Isaraha", "Isorana", "Ivatana", "Ivato Aéroport", "Ivoamba", -->
+<!--                  "Ivony", "Kalalao", "Kianjandrandrakefina", "labohazo", "Lavaraty Ivondro", "Mahaditra", "Mahafasa", "Mahajanga I", "Mahasoabe", "Mahatsara Lefaka", -->
+<!--                  "Mahatsinjo Atsinanana", "Mahatsinjo", "Mahatsinjony", "Mahazina", "Manajary Urbain", "Manakambahiny Est", "Manakambahiny Ouest", "Manakara(com)", -->
+<!--                  "Manambotra Sud", "Manapatrana", "Mandromodromotra", "Maneva", "Mangarivot", "Manombo", "Manorofify", "Marintampona", "Marivorahona", "Maroarivo",  -->
+<!--                  "MarofotyMarofoty", "Maromiandra", "Maromokotra-Loky", "Marosavoa Bas", "Marovitsika", "Merimandroso", "Miary", "Milenaka", "Mitsinjo", "Mizilo Gare",  -->
+<!--                  "Moramanga Urbain", "Morarano Gare", "Morombe", "Nagnarena", "Nasandratrony", "Niarovana", "Nosibe Masianaka", "Onilhy", "Port Bergé I", "Port Bergé II", -->
+<!--                  "Rantabe Est", "Rantabe Sud", "Razanaka", "Sahamadio", "Sahambavy", "Sahambo", "Sahanivotry Atsimo", "Sakamahily-Ouest", "Sakay", "Sakona", "Sambava Urbain", -->
+<!--                  "Sarobaratra", "Soaindrana", "Soalara", "Soatanana", "St Augustin", "Taindambo", "Talata Ampano", "Talatan'Angavo", "Taolognaro", "Tanakamba", "Tanambao  Daoud", -->
+<!--                  "Tanambaovatrakaka", "Tanandava-Sud", "Tanandrano", "Toamasina Suburbain", "Tovòna", "Tsarahonenana", "Tsarajomoko", "Tsaratanana", "Tsiafajavona Ankarat", -->
+<!--                  "Tsianisiha", "Tsianofàna", "Tsinjoarivo", "Tsiombe", "Tsiroanomadidy Ville", "Tsiroanomandidy Ville", "Vatolatsaky", "Vilihazo", "Vinaninony Avaratra", -->
+<!--                  "Vineta Andamasiny", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zomabealoka") -->
+
+<!-- commune_new <- c("Alakamisy Ambohimaha", "Alakamisy Itenina", "Ambandrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy II", "Ambalamidera II", "Ambalapaiso II", "Ambararatabe Nord", -->
+<!--                  "Ambarijeby Sud", "Ambatoben'anjavy", "Ambatofisaka II", "Ambatoharanana", "Ambatolampy", "Ambatolampy", "Ambatoriha Est", "Ambatotsipihina", "Ambatolava",  -->
+<!--                  "Ambatry Mitsinjo", "Ambinanin'andravory", "Ambinanindrano", "Ambinaniroa", "Ambodiadabo", "Ambodiadabo M", "Ambodiampana", "Ambodiampana", "Ambodifarihy Fenomanana", -->
+<!--                  "Ambodihazoambo", "Ambodimanga I","Ambodimanga II", "Ambodimotso Sud", "Ambodinonoka", "Ambodirian'i Sahafary", "Amboditandroroho", "Ambohibao Sud", -->
+<!--                  "Ambohibary Vohilena", "Mandritsara", " Ambohimahavelona", "Ambohimalaza Miray", "Ambohimana", "Ambohimanga Du Sud", "Sahatsiho Ambohimanjaka", -->
+<!--                  "Ambohimiarina II", "Ambohitralanana", "Ambohitrandriamanitra", "Ambohitsara Est", "Ambolidibe Est", "Ambolofoty", "Amborompotsy", "Ampasimadinika Manambolo", -->
+<!--                  "Ampasimboraka", "Ampasimpotsy Sud", "Ampasimpotsy Gara", "Ampasipotsy Mandialaza", "Manampaneva", "Ampatakamaroreny", "Anakao", "Analaiva", "Analamisampy", -->
+<!--                  "Analamitsivalana", "Ambatomainty", "Antanandava", "Andrainjato Est", "Andimaky Manambolo", "Andoharanomaitso", "Andoharanomaitso", "Andrainjato Centre", -->
+<!--                  "Andranohinaly", "Andranomiditra", "Rambolamasoandro Andranomiely", "Andranovorivato", "Andranovory", "Andravola Vohipeno", "Andrebakely Nord", "Andribavontsona", -->
+<!--                  "Androndrono", "Androy", "Anjampaly", "Anjeky Ankilikira", "Anjeva Gara", "Anjiabe Ambony", "Anjiajia", "Anjoman'ankona", "Anjoma Itsara", "Ankadinondry Sakay", -->
+<!--                  "Ankafina Tsarafidy", "Ankarinarivo Manirisoa", "Ankaromalaza Mifanasoa", "Ankasakasa Tsibiray", "Ankazoabo Sud", "Ankazotokana", "Ankiabe-Salohy", " Ankiakabe Nord", -->
+<!--                  "Ankililoaka", "Ankilimalinike", "Bemarivo Ankirondro", "Anontsibe Centre", "Anosiarivo I", "Anosy Tsararafa", " Antalaha Ambonivohitra", "Antanamalaza", "Antanambao Ambary", -->
+<!--                  "Antanambao", "Antanambao Manampontsy", "Antanambaon'amberina", "1er Arrondissement", "2e Arrondissement", "3e Arrondissement", "4e Arrondissement", "5e Arrondissement", -->
+<!--                  "6e Arrondissement", "Antanandava", "Antananivo Haut", "Antanetibe", "Antanimora Atsimo", "Antenina", "Antoby Est", "Antohabato", "Antongo Vaovao", "Marovitsika Sud", "Antranokarany", -->
+<!--                  "Antsahavaribe", "Antsakoamanondro", "Antsampanimahazo", "Antsirabe Afovoany Atsinanana", "Diego Suarez", "Antsoatany", "Bealampona", "Bealanana", "Beampombo I", -->
+<!--                  "Beandrarezona", "Befandriana Nord", "Befandriana Sud", "Befeta", "Befotaka Nord", "Befotaka Sud", "Beheloka", "Behara", "Behompy", "Belafike Haut", "Belalanda", -->
+<!--                  "Belambo Firaisana", "Belaoka Marovato", "Belo Sur Mer", "Belo Sur Tsiribihina", "Belo Sur Tsiribihina", "Bemaneviky Haut Sambirano", "Benato Toby", "Bereketa",  -->
+<!--                  "Berevo/ranobe", "Beroy Atsimo", "Betioky Atsimo", "Betsakotsako Andranotsara", "Betsimisotra", "Betsinjaka", " Beretra Bevoay", "Bevonotra", "Efatsy", "Enakara-Haut", -->
+<!--                  "Enaniliha", "Erada", "Etrotroka Atsimo", "Fandrandava", "Fanjakana", "Betanty (Faux Cap)", "Fenoevo-Efita", "Fiaferana", "Mahavelona (Foulpointe)", "Ialananindro",  -->
+<!--                  "Iavonomby Vohibola", "Alatsinainy Ibity", "Namohora Iaborano", "Ihazoara", "Menamaty Iloto", "Imerina Imady", "Imerintsiatosika", "Isaka-Ivondro", "Isahara", -->
+<!--                  "Isorana", "Vatana", "Ivato Aeroport", "Ivoamba", "Ivony Miaramiasa", "Ikalalao", "Kianjandrakefina", "Iabohazo", "Ivondro", "Mahaditra", "Mahafasa Centre",  -->
+<!--                  "Mahajanga", "Mahasoabe", "Mahatsara Iefaka", "Mahatsinjo Est", "Mahatsinjony", "Mahatsinjony", "Mahazina Ambohipierenana", "Mananjary", "Manakambahiny Antsinanana", -->
+<!--                  "Manakambahiny Andrefana", "Manakara", "Manambotra Atsimo", "Manampatrana", "Mandromondromotra", "Maneva", "Mangarivotra", "Manombo Sud", "Manorofify", "Maritampona",  -->
+<!--                  "Tanambao Marivorahona", "Maroarivo Ankazomanga", "Marofoty", "Maromiandra", "Maromokotra Loky", "Marosavoa", "Marovitsika Sud", "Imerimandroso", "Miary Ambohibola",  -->
+<!--                  "Milenaka", "Mitsinjo Betanimena", "Mizilo Gara", "Moramanga", "Morarano Gara", "Cu Morombe", "Nanarena Besakoa", "Nasandratrony", "Niarovana Marosampanana",  -->
+<!--                  "Masianaka", "Onilahy", "Port Berge", "Port Berge II", "Rantabe", "Rantabe", "Vohipeno Razanaka", "Sahamadio Fisakana", "Sahambavy", "Sahambano", "Sahanivotry Manandona", -->
+<!--                  "Sakamahily", "Tanamarina Sakay", "Sakoana", "Sambava Cu", "Sarobaratra Ifanja", "Soaindrana", "Soalara Sud", "Soatanana", "Saint Augustin", "Taindambo", "Tatala Ampano",  -->
+<!--                  "Talata Angavo", "Fort-Dauphin", "Tanakambana", "Tanambao Daoud", "Tanambao Vahatrakaka", "Tanandava Sud", "Tandrano", "Toamasina Suburbaine", "Tovona", "Tsarahonenana Sahanivotry", -->
+<!--                  "Tsarajomoka", "Tsaratanana I", "Tsiafajavona Ankaratra", "Tsianisiha", "Tsianofana", "Tsinjoarivo Imanga", "Tsihombe", "Tsiroanomandidy Fihaonana",  -->
+<!--                  "Tsiroanomandidy Fihaonana", "Vatolatsaka", "Viliahazo", "Vinaninony Atsimo", "Andamasiny Vineta", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zoma Bealoka") -->
+
+<!-- as.data.frame(cbind(commune_old, commune_new)) %>% -->
+<!--   arrange(commune_old) %>% -->
+<!--   mutate(test = commune_new == commune_old) %>% -->
+<!--   filter(test == FALSE) %>% -->
+<!--   dplyr::select(!test) %>% -->
+<!--   rename("Name in data" = commune_old, -->
+<!--          "Standardized name" = commune_new) %>% -->
+<!--   gt() %>% -->
+<!--   tab_header( -->
+<!--     title = md("**Table S2.9: Standardization of commune names**")) %>% -->
+<!--   tab_options(table.font.names = "Source Sans Pro", -->
+<!--               page.header.use_tbl_headings	= TRUE) %>% -->
+<!--   tab_style( -->
+<!--     locations = cells_column_labels(), -->
+<!--     style     = list( -->
+<!--       cell_text(weight = "bold")) -->
+<!--   ) %>% -->
+<!--   gtsave("table_s_2_9.docx") -->
+
+<!-- ``` -->
+
+```{r housekeeping_1a, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
 
@@
 
-```
-
-```{r housekeeping_1a, warning = FALSE, message = FALSE, echo = FALSE, include = FALSE}
-
-rm(column1, column2, data_mh_dup_names, r_new, r_old, chu_files, commune_new, commune_old, district_new, district_communes_affected, district_old, district_tobechanged, duplicates)
+# rm(column1, column2, data_mh_dup_names, r_new, r_old, chu_files, commune_new, commune_old, district_new, district_communes_affected, district_old, district_tobechanged, duplicates)
 
@@
                             ": Approximate string matches"))) %>%
-  tab_options(table.font.names = "Source Sans Pro") %>%
+  tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
   tab_style(
@@
 
-In total, matching to our expanded inventory in Step 2 led to `r format(as.numeric(n_matched_facilities_step_2), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_2)/n_facilities_new * 100,0)`% of our sample) being geolocated.
+In total, matching to our expanded inventory in Step 2 resulted in `r format(as.numeric(n_matched_facilities_step_2), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_2)/n_facilities_new * 100,0)`% of our sample) being geolocated.
 
@@
 Using this approach, `r format(as.numeric(n_matched_facilities_any_region + n_matched_facilities_any_district + n_matched_facilities_any_commune), big.mark = ",")` facilities were matched to coordinate groups in our expanded spatial inventory, including `r format(as.numeric(n_matched_facilities_any_region), big.mark = ",")` regional facilities, `r format(as.numeric(n_matched_facilities_any_district), big.mark = ",")` district-level facilities, and `r format(as.numeric(n_matched_facilities_any_commune), big.mark = ",")` commune-level facilities.
-In total, matching to our expanded inventory in Step 3 led to `r format(as.numeric(n_matched_facilities_step_3), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_3)/n_facilities_new * 100,0)`% of our sample) being geolocated.
+In total, matching to our expanded inventory in Step 3 resulted in `r format(as.numeric(n_matched_facilities_step_3), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_3)/n_facilities_new * 100,0)`% of our sample) being geolocated.
 
@@
       title = md("**Manual matches across data and expanded spatial inventory: facility names**")) %>%
-         tab_options(table.font.names = "Source Sans Pro") %>%
+         tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
             tab_style(
@@
       title = md("**Manual matches across data and expanded spatial inventory: facility types**")) %>%
-         tab_options(table.font.names = "Source Sans Pro") %>%
+         tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
             tab_style(
@@
       title = md("**Manual matches across data and expanded spatial inventory: facility districts**")) %>%
-         tab_options(table.font.names = "Source Sans Pro") %>%
+         tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
             tab_style(
@@
       title = md("**Manual matches across data and expanded spatial inventory: facility communes**")) %>%
-         tab_options(table.font.names = "Source Sans Pro") %>%
+         tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
             tab_style(
@@
 Manual matching allowed for an additional `r format(as.numeric(n_manual_matches), big.mark = ",")` facilities in our sample being linked to coordinates in our expanded spatial inventory.
-In total, matching to our expanded inventory in Step 4 led to `r format(as.numeric(n_matched_facilities_step_3), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_3)/n_facilities_new * 100,0)`% of our sample) being geolocated.
+In total, matching to our expanded inventory in Step 4 resulted in `r format(as.numeric(n_matched_facilities_step_3), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_3)/n_facilities_new * 100,0)`% of our sample) being geolocated.
 
@@
 
-Altogether, matching to centroids of communes and *fokontany* in Step 5 led to `r format(as.numeric(n_matched_facilities_step_5), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_5)/n_facilities_new * 100,0)`% of our sample) being geolocated.
+Altogether, matching to centroids of communes and *fokontany* in Step 5 resulted in `r format(as.numeric(n_matched_facilities_step_5), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_5)/n_facilities_new * 100,0)`% of our sample) being geolocated.
 
@@
 
-Combined with the previous steps, targeted searches led to `r format(as.numeric(n_matched_facilities_step_6), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_6)/n_facilities_new * 100,1)`% of our sample) being geolocated.
+Combined with the previous steps, targeted searches resulted in `r format(as.numeric(n_matched_facilities_step_6), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities_step_6)/n_facilities_new * 100,1)`% of our sample) being geolocated.
 

### 2023-05-15 intro.Rmd
Additional typesettting changes

@@
 Most of those living with a mental disorder do not have access to adequate care,[@bassUnitedNationsGeneral2012a; @demyttenaerePrevalenceSeverityUnmet2004] and many face stigma,[@alonsoPerceivedStigmaIndividuals2009; @angermeyerStigmaMentalIllness2003] discrimination,[@stuartMentalIllnessEmployment2006; @thornicroftDiscriminationHealthCare2007] and abuse.[@humanrightswatchDeathSentenceAbuses2012; @mfoafo-mcarthyHumanRightsViolations2014; @rahmanMentalDistressHuman2021]
+
+In addition to the long-standing challenges of these unmet needs, new and emerging dangers such as climate change and COVID-19 reveal additional stressors that threaten to exacerbate this burden.
+Global climate change—an accelerating existential threat to planetary health that the United Nations considers the “defining crisis of our time”—is already manifesting profound impacts on mental health.[@worldhealthorganizationMentalHealthClimate2022]
 
@@
 
-In addition to the long-standing challenges of these unmet needs, new and emerging dangers such as climate change and COVID-19 reveal additional stressors that threaten to exacerbate this burden.
-Global climate change—an accelerating existential threat to planetary health that the United Nations considers the “defining crisis of our time”—is already manifesting profound impacts on mental health.[@worldhealthorganizationMentalHealthClimate2022] These impacts are shaped both by the disastrous upheaval caused by worsening extreme weather events and by the incremental change rising temperatures and sea levels have wrought on livelihoods and means of living—altering the availability and access to natural resources, land use, infrastructure, and community.[@atwoliMentalHealthClimate2022; @hayesClimateChangeMental2018] The essential connections between mental health and human well-being have been further underscored by the devastating impacts of the COVID-19 pandemic, which continues to deal psychological and psychiatric harm to patients, health care workers, and the public overall.[@vindegaardCOVID19PandemicMental2020]
+These impacts are shaped both by the disastrous upheaval caused by worsening extreme weather events and by the incremental change rising temperatures and sea levels have wrought on livelihoods and means of living—altering the availability and access to natural resources, land use, infrastructure, and community.[@atwoliMentalHealthClimate2022; @hayesClimateChangeMental2018] The essential connections between mental health and human well-being have been further underscored by the devastating impacts of the COVID-19 pandemic, which continues to deal psychological and psychiatric harm to patients, health care workers, and the public overall.[@vindegaardCOVID19PandemicMental2020]
 

### 2023-05-15 paper2.Rmd
Formatting corrections
Additional typesettting changes

@@
 
-As empirical evidence increasingly highlights the wide-scale impact of human activities on climate, there is a growing, parallel body of evidence documenting the impacts our changing climate has on human health.[@watts2020ReportLancet2021] Rising temperatures and extreme weather events (including floods, hurricanes, droughts, and fires) have been associated with worsened health outcomes in multiple settings.[@cianconiImpactClimateChange2020a; @rocqueHealthEffectsClimate2021] In particular, these and other \acr{CCEs} have been increasingly linked to worsened mental health[@padhyMentalHealthEffects2015 @batterhamSystematicReviewQuantitative2022], with systematic reviews suggesting, among other climate condition impacts, positive associations between high ambient temperatures and mental disorders,[@liuThereAssociationHot2021] drought conditions and suicide,[@stankeHealthEffectsDrought2013] and cyclones and negative mental health outcomes.[@tasdikhasanExploringMentalHealth2020]
+As empirical evidence increasingly highlights the widespread impact of human activities on climate, there is a growing, parallel body of evidence documenting the impacts the changing climate has on human health.[@watts2020ReportLancet2021] Rising temperatures and extreme weather events (including floods, hurricanes, droughts, and fires) have been associated with worsened health outcomes in multiple settings.[@cianconiImpactClimateChange2020a; @rocqueHealthEffectsClimate2021] In particular, these and other \acr{CCEs} have been increasingly linked to worsened mental health,[@padhyMentalHealthEffects2015 @batterhamSystematicReviewQuantitative2022] with systematic reviews suggesting, among other climate condition impacts, positive associations between high ambient temperatures and mental disorders,[@liuThereAssociationHot2021] drought conditions and suicide,[@stankeHealthEffectsDrought2013] and cyclones and negative mental health outcomes.[@tasdikhasanExploringMentalHealth2020]
 
@@
 
-To analyze the impact of climate on population mental health in Madagascar, we first obtained \acr{HMIS} data through a collaboration with the Madagascar Ministère de la Santé Publique.
+To analyze the impact of climate on population mental health in Madagascar, we first obtained \acr{HMIS} data through a collaboration with Madagascar's Ministère de la Santé Publique.
 We then obtained gridded temperature and soil moisture data from the \acr{ERA5}[@copernicusclimatechangeservicec3sFifthGenerationECMWF2017] and the \acr{ESA CCI},[@europeanspaceagencyEuropeanSpaceAgency2022] respectively.
-Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean[@wikipediaSouthWestIndianOcean2023], which were in turn cross-referenced against storm trajectory data from the \acr{NOAA}[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021] for accuracy.
+Data on tropical storms and cyclones were obtained from open-source compilations of storms in the South-West Indian Ocean,[@wikipediaSouthWestIndianOcean2023] which were in turn cross-referenced against storm trajectory data from the \acr{NOAA}[@internationalbesttrackarchiveforclimatestewardshipibtracsInternationalBestTrack2021] for accuracy.
 
@@
 
-\acr{ERA5} is a global atmospheric reanalysis from the \acr{ECMWF} and is freely available through its \acr{C3S}[@europeanspaceagencyEuropeanSpaceAgency2022].
-The spatial resolution of \acr{ERA5} is approximately 30 \acr{km}, with quality-assured hourly estimates available from 1959 to the present.[@europeanspaceagencyEuropeanSpaceAgency2022] Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation.[@googleearthengineERA5MonthlyAggregates2022] Temperature data was then converted to degrees Celsius.
+\acr{ERA5} is a global atmospheric reanalysis from the \acr{ECMWF} and is freely available through its \acr{C3S}.[@europeanspaceagencyEuropeanSpaceAgency2022] The spatial resolution of \acr{ERA5} is approximately 30 \acr{km}, with quality-assured hourly estimates available from 1959 to the present.[@europeanspaceagencyEuropeanSpaceAgency2022] Using Google Earth Engine, a time series of monthly aggregate values for mean air temperature in degrees Kelvin at a height of 2 meters was obtained for each facility geolocation.[@googleearthengineERA5MonthlyAggregates2022] Temperature data was then converted to degrees Celsius.
 
@@
 
+\newpage
+
 \begin{spacing}{1.5}
@@
 
-With respect to soil moisture, to the best of our knowledge, there have been no studies that directly explore the association between soil saturation and mental health in non-emergency conditions.
+With respect to soil moisture, to the best of our knowledge there have been no studies that directly explore the association between soil saturation and mental health in non-emergency conditions.
 In terms of extremely low soil moisture, evidence from droughts suggest potential indirect pathways to worsened mental health outcomes,[@obrienDroughtMentalHealth2014] but these impacts are not well characterized and may not manifest over a short time horizon.[@vinsMentalHealthOutcomes2015]
@@
 In particular, we found that greater soil moisture was associated with more visits reported in the eastern lowlands and the northern dry deciduous forests, which echoes the geographic concentration of flood risk in Madagascar.[@rakotoarisonSpatialAnalysisRisks2021] Conversely, the observed (though statistically modest) reduction in visits associated with higher soil moisture in the desert and xeric shrublands overlaps with the concentration of drought risk, where higher soil moisture could indicate reduced drought vulnerability.
-It is important to note, however, that the time frame of available GESIS data excludes the most severe period of the ongoing drought in Madagascar, limiting our ability to directly study the impact of the current crisis on population mental health in this analysis.
+It is important to note that the time frame of available GESIS data excludes the most severe period of the ongoing drought in Madagascar, limiting our ability to directly study the impact of the current crisis on population mental health in this analysis.
 Further research could leverage spatial reanalysis data on precipitation to further characterize these associations.
 
-Madagascar’s wet season is marked by frequent tropical storms and cyclones—the intensification of which has been linked to rising temperatures in the Indian Ocean.[@ottoClimateChangeIncreased2022] In the majority of our models in the multiverse analysis, we found that months with greater duration of cyclone activity were associated with *fewer* monthly report visits for mental disorders, though none of these models were significant at the threshold of 0.01.
+Madagascar’s wet season is marked by frequent tropical storms and cyclones—the intensification of which has been linked to rising temperatures in the Indian Ocean.[@ottoClimateChangeIncreased2022] In the majority of our models in the multiverse analysis, we found that months with a greater duration of cyclone activity were associated with *fewer* monthly report visits for mental disorders, though none of these models were significant at the threshold of 0.01.
 In numerous studies, cyclones and similar disasters have been found to worsen mental health;[@obradovichEmpiricalEvidenceMental2018] however, these storms may also result in numerous conditions that make access to mental health resources more challenging.
@@
 
-Failure to observe effect heterogeneity in our subgroup analysis of the association of cyclone activity with reported monthly visits likely is due, in part, to our specification choice to define exposure to cyclone activity without geographic variation in intensity.
-While we felt justified in opting for a simplified indicator, given that storms in Madagascar typically impact the whole of the island, a more nuanced (but data-hungry) approach could define exposure with greater geographic precision based on additional climate metrics, including peak wind, rainfall, and distance from the storm’s track.[@andersonExposureAssessmentTropical2022]
+Failure to observe effect heterogeneity in our subgroup analysis of the association of cyclone activity with reported monthly visits likely is due, in part, to our decision to define exposure to cyclone activity without geographic variation in intensity.
+While we justify our simplified indicator based on observation that storms in Madagascar typically impact the whole of the island, a more nuanced (but data-hungry) approach could define exposure with greater geographic precision based on additional climate metrics, including peak wind, rainfall, and distance from the storm’s track.[@andersonExposureAssessmentTropical2022]
 
@@
 By leveraging reported visits from over three thousand health facilities over ten years, utilizing the most comprehensive sources of climate data available, and linking the two via a rigorous, multistep geolocating process, our analysis demonstrates how routine health system data may offer valuable insights, particularly when other epidemiological data are not available.
-As one of the only studies to investigate mental health and climate in Africa using national \acr{HMIS} data, our findings also underscore the need for further research to understand the relationships and pathways between changing climate and population mental health, particularly countries most vulnerable to climate change.
-Finally, our findings and interpretations highlight the importance of local knowledge and collaboration with local ministries in global health research, to make best use of existing data and to foster research to support health system strengthening.
+As one of the only studies to investigate mental health and climate in Africa using national \acr{HMIS} data, our findings also underscore the need for further research to understand the relationships and pathways between changing climate and population mental health, particularly in countries most vulnerable to climate change.
+Finally, our findings and interpretations highlight the importance of collaboration with local ministries in global health research, to make best use of existing data and to foster research to support health system strengthening.
 We believe that this approach to research is essential for understanding the complex relationships and mechanisms linking climate change exposures to mental health, as well as identifying strategies to mitigate these impacts amid the unfolding global climate crisis.
@@
 The funders had no role in the design and conduct of the study, nor in the collection, management, analysis, and interpretation of the data.
-The authors alone are responsible for the content and writing of the article.
 

### 2023-05-15 paper3.Rmd
Additional typesettting changes

@@
 The COVID-19 pandemic has had a profound effect on the mental health and well-being of individuals worldwide.
-Studies from Australia,[@batterhamTrajectoriesDepressionAnxiety2021] China,[@ahmedEpidemicCOVID19China2020; @gaoMentalHealthProblems2020; @hwangLonelinessSocialIsolation; @leiComparisonPrevalenceAssociated2020; @liuPrevalencePredictorsPTSS2020; @qiuNationwideSurveyPsychological2020; @wangImmediatePsychologicalResponses2020; @wangStudyPublicPsychological2021; @wangPsychologicalDistressCoping2020; @zhangImpactCOVID19Pandemic2020] Denmark,[@sonderskovDepressiveStateDenmark] Europe,[@hajekPrevalenceDeterminantsProbable2022] Iran,[@moghanibashi-mansouriehAssessingAnxietyLevel2020] Ireland,[@hylandAnxietyDepressionRepublic2020] Italy,[@mazzaNationwideSurveyPsychological2020; @mocciaAffectiveTemperamentAttachment2020] Nepal,[@samadarshiOnlineSurveyFactors2020] New Zealand,[@gasteigerDepressionAnxietyStress2021; @lawRiskFactorsChanges2022] Spain,[@gonzalez-sanguinoMentalHealthConsequences2020; @ozamiz-etxebarriaStressAnxietyDepression2020] Turkey[@ozdinLevelsPredictorsAnxiety2020], the United Kingdom[@dettmannInvestigatingPrevalenceAnxiety2022], and the United States[@jiaNationalStateTrends2021, p.
+Studies from Australia,[@batterhamTrajectoriesDepressionAnxiety2021] China,[@ahmedEpidemicCOVID19China2020; @gaoMentalHealthProblems2020; @hwangLonelinessSocialIsolation; @leiComparisonPrevalenceAssociated2020; @liuPrevalencePredictorsPTSS2020; @qiuNationwideSurveyPsychological2020; @wangImmediatePsychologicalResponses2020; @wangStudyPublicPsychological2021; @wangPsychologicalDistressCoping2020; @zhangImpactCOVID19Pandemic2020] Denmark,[@sonderskovDepressiveStateDenmark] Europe,[@hajekPrevalenceDeterminantsProbable2022] Iran,[@moghanibashi-mansouriehAssessingAnxietyLevel2020] Ireland,[@hylandAnxietyDepressionRepublic2020] Italy,[@mazzaNationwideSurveyPsychological2020; @mocciaAffectiveTemperamentAttachment2020] Nepal,[@samadarshiOnlineSurveyFactors2020] New Zealand,[@gasteigerDepressionAnxietyStress2021; @lawRiskFactorsChanges2022] Spain,[@gonzalez-sanguinoMentalHealthConsequences2020; @ozamiz-etxebarriaStressAnxietyDepression2020] Turkey,[@ozdinLevelsPredictorsAnxiety2020] the United Kingdom,[@dettmannInvestigatingPrevalenceAnxiety2022] and the United States[@jiaNationalStateTrends2021, p.
 2020–2021; @kujawaExposureCOVID19Pandemic2020] have reported high levels of anxiety (6-51%), depression (15-48%), and post-traumatic stress disorder (7-54%) associated with the onset of the pandemic.
 In the \acr{US}, approximately four in ten adults reported experiencing symptoms of anxiety or depression in December 2020—a four-fold increase from January-June 2019.[@panchalImplicationsCOVID19Mental2021, p.
-19] Globally, it has been estimated that the prevalence of depression and anxiety during the COVID-19 pandemic may be as high as 24% and 21%, respectively[@banko-ferranImpactCOVID19Mental2020; @castaldelli-maiaInvestigatingEffectNational2021], with regions  hit hardest by COVID-19 showing the greatest increases in prevalence.[@santomauroGlobalPrevalenceBurden2021] This striking burden has been described as a mental health crisis[@melimopoulosHowCOVID19Pandemic2021] and as a pandemic in its own right.[@kwaiWhatPointYoung2021]
+19] Globally, it has been estimated that the prevalence of depression and anxiety during the COVID-19 pandemic may be as high as 24% and 21%, respectively,[@banko-ferranImpactCOVID19Mental2020; @castaldelli-maiaInvestigatingEffectNational2021] with regions  hit hardest by COVID-19 showing the greatest increases in prevalence.[@santomauroGlobalPrevalenceBurden2021] This striking burden has been described as a mental health crisis[@melimopoulosHowCOVID19Pandemic2021] and as a pandemic in its own right.[@kwaiWhatPointYoung2021]
 
@@
 I took November 16, 2020 as the date of the first credible signal of the imminent availability of safe and effective COVID-19 vaccines.
-On November 9^th^, Pzifer announced that early vaccine trial data showed 90% efficacy[@thomasPfizerEarlyData2020] and on the 16^th^, Moderna announced preliminary results showing 95% efficacy.[@gradyEarlyDataShow2020] While \acr{US} \acr{FDA} \acr{EUA} was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
+On November 9^th^, Pfizer announced that early vaccine trial data showed 90% efficacy[@thomasPfizerEarlyData2020] and on the 16^th^, Moderna announced preliminary results showing 95% efficacy.[@gradyEarlyDataShow2020] While \acr{US} \acr{FDA} \acr{EUA} was not granted until December, the concurrent announcements of vaccine efficacy were widely reported and interpreted by many public health practitioners, policymakers, and the general public as a substantial signal of a new phase of the pandemic, with Moderna’s chief executive officer calling the news “a game changer” in the fight against COVID-19.
 
@@
 Negative level shifts and slope changes were more pronounced in New Zealand compared to other countries, while the level shift estimated for searches for depression in Ireland was positive; owing to the construction of the Google search density data being relative to regions, this may be due to differences in search volume intensity for depression in Ireland and New Zealand compared to other countries, and not due to a strong effect itself.
+
+Results from the analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and \acr{MDD} as found in the main analysis (Figure \ref{fig_political}).
+This was particularly observed in the analysis of \acr{US} state-level data, where confidence intervals for the \acr{CITS} effect estimates were statistically equivalent across red and blue states.
+In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties compared to blue ones, with minor overlap in confidence intervals.
+The observed slope change for searches related to depression among red counties was `r function_dynamic_text_results("political", "depression", "slope", region_option = 1)`, compared to `r function_dynamic_text_results("political", "depression", "slope", region_option = 5)` for blue counties.
+Similarly, a more pronounced level shift was observed in red counties than blue ones, `r function_dynamic_text_results("political", "depression", "intercept", region_option = 1)` versus `r function_dynamic_text_results("political", "depression", "intercept", region_option = 5)`, respectively.
 
@@
 ```
-
-Results from the analysis comparing red and blue states and counties showed broad consistency in both slope changes and level shifts for searches for anxiety, depression, and \acr{MDD} as found in the main analysis (Figure \ref{fig_political}).
-This was particularly observed in the analysis of \acr{US} state-level data, where confidence intervals for the \acr{CITS} effect estimates were statistically equivalent across red and blue states.
-In the county-level analysis, however, I observed larger immediate and sustained declines in searches for depression among red counties compared to blue ones, with minor overlap in confidence intervals.
-The observed slope change for searches related to depression among red counties was `r function_dynamic_text_results("political", "depression", "slope", region_option = 1)`, compared to `r function_dynamic_text_results("political", "depression", "slope", region_option = 5)` for blue counties.
-Similarly, a more pronounced level shift was observed in red counties than blue ones, `r function_dynamic_text_results("political", "depression", "intercept", region_option = 1)` versus `r function_dynamic_text_results("political", "depression", "intercept", region_option = 5)`, respectively.
 
@@
 This gradient would also echo the hypothesis that, given findings that political ideology may affect receptiveness to vaccination, the announcement of vaccine safety and efficacy would have had a less pronounced effect among conservative voters compared to liberal ones.
+
 Instead, I observed the opposite: among the counties that most heavily voted for the Republican candidate, the estimated declines in search density for anxiety and depression were larger than in those that most heavily voted Democrat.
@@
 In addition, the use of Google search density as a proxy for population mental health could not be directly validated in the study, as the search data was anonymized and aggregated.
+
 While this is an important limitation, prior work has found a strong correlation between searches for anxiety and depression and \acr{US} population survey responses for receiving therapy, receiving medication for mental health disorders, and having unmet mental health needs.[@agrawalImpactCOVID19Vaccine2021] Given the paucity of high-frequency population mental health data, Google search density data offered a unique opportunity to investigate the immediate and sustained impacts of vaccine safety and efficacy announcements with an aggregated measures that may be linked with subjective well-being and care seeking.
+
+\newpage
 
@@
 If symptom search density echoes population health, the results would indicate that these announcements led to an improvement in mental health, an improvement observed across countries and predominant political party inclination.
-These findings underscore the importance of timely and transparent communication and highlight the potential application of high-frequency internet search data for population mental health surveillance.
+These findings underscore the importance of timely and transparent public health communication and highlight the potential application of high-frequency internet search data for population mental health surveillance.
 

### 2023-05-16 appendix_2.1.Rmd
Revisions to tables, revised submission to ProQuest

@@
 
-\vspace{24 pt}
-
-\begin{spacing}{1}
+\newpage
 
@@
 
-```{r  table_s_2_2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-mh_english_disease %>% unique() %>%
-  arrange(disease) %>%
-  relocate(disease, .before=disease_english) %>%
-    mutate(disease = gsub(" and ", " & ", disease),
-           disease =  StrTrunc(disease, maxlen = 40, ellipsis = "...", wbound = TRUE),
-           disease_english = gsub(" and ", " & ", disease_english),
-   disease_english = case_when(
-       str_detect(disease_english, "Bouffées délirantes aiguës") ~
-                   "Short-lived psychosis",
-   TRUE ~ disease_english),
-      disease_english = gsub("of diseases classified elsewhere", "(d.c.e.)", disease_english),
-      disease_english = gsub("in diseases classified elsewhere", "(d.c.e.)", disease_english),
-   disease_english = gsub(" nervous system", " N.S.", disease_english)) %>%
-  rename(English = disease_english, French = disease) %>%
-  gt() %>%
-  tab_footnote(
-    footnote = "d.c.e.: in or among diseases classified elsewhere. N.S.: nervous system",
-    locations = cells_column_labels(
-      columns = English
-    )
-  ) %>%
-  tab_style(locations = cells_column_labels(),
-            style     = list(cell_text(weight = "bold", size = 9))) %>%
-    tab_header(
-    title ="Table S2.2: Mental health disorders reported in GESIS, in French and English")
+```{r table_s_2_2, echo = FALSE, include = TRUE, out.width = '97%'}
+
+knitr::include_graphics("table_s_2_2.png")
+
+# 
+# mh_english_disease %>% unique() %>%
+#   arrange(disease) %>%
+#   relocate(disease, .before=disease_english) %>%
+#     mutate(disease = gsub(" and ", " & ", disease),
+#            disease =  StrTrunc(disease, maxlen = 40, ellipsis = "...", wbound = TRUE),
+#            disease_english = gsub(" and ", " & ", disease_english),
+#    disease_english = case_when(
+#        str_detect(disease_english, "Bouffées délirantes aiguës") ~
+#                    "Short-lived psychosis",
+#    TRUE ~ disease_english),
+#       disease_english = gsub("of diseases classified elsewhere", "(d.c.e.)", disease_english),
+#       disease_english = gsub("in diseases classified elsewhere", "(d.c.e.)", disease_english),
+#    disease_english = gsub(" nervous system", " N.S.", disease_english)) %>%
+#   rename(English = disease_english, French = disease) %>%
+#   gt() %>%
+#   tab_footnote(
+#     footnote = "d.c.e.: in or among diseases classified elsewhere. N.S.: nervous system",
+#     locations = cells_column_labels(
+#       columns = English
+#     )
+#   ) %>%
+#   tab_style(locations = cells_column_labels(),
+#             style     = list(cell_text(weight = "bold", size = 9))) %>%
+#     tab_header(
+#     title ="Table S2.2: Mental health disorders reported in GESIS, in French and English")  %>%
+#    gtsave("table_s_2_2.docx")
 
 ```
+
+\newpage
 
@@
 
-\end{spacing}
-
 \vspace{24 pt}
@@
 
+\begin{spacing}{1}
+
+\addcontentsline{lot}{table}{Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities.}
+
+```{r  reporting_tables1a, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, out.width = '97%'}
+
+knitr::include_graphics("table_s_2_3.png")
+
+# 
+# reporting_table(csb_data, "Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities")  %>%
+#    gtsave("table_s_2_3.docx")
+
+```
+
+\addcontentsline{lot}{table}{Table S2.4:  Yearly cumulative visits for mental and neurological disorders reported at district hospitals.}
+
+```{r  reporting_tables1b, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, out.width = '97%'}
+
+knitr::include_graphics("table_s_2_4.png")
+
+# reporting_table(chd_data, "Table S2.4: Yearly cumulative visits for mental and neurological disorders reported at district hospitals") %>%
+#    gtsave("table_s_2_4.docx")
+
+```
+
 \newpage
 
-\begin{spacing}{1}
-
-\addcontentsline{lot}{table}{Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities.}
-
-```{r  reporting_tables1a, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-reporting_table(csb_data, "Table S2.3: Yearly cumulative visits for mental and neurological disorders reported at primary facilities")
-
-```
-
-\addcontentsline{lot}{table}{Table S2.4:  Yearly cumulative visits for mental and neurological disorders reported at district hospitals.}
-
-```{r  reporting_tables1b, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-reporting_table(chd_data, "Table S2.4: Yearly cumulative visits for mental and neurological disorders reported at district hospitals")
-
-```
-
-\newpage
-
 \addcontentsline{lot}{table}{Table S2.5: Yearly cumulative visits for mental and neurological disorders reported at regional hospitals.}
 
-```{r  reporting_tables2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE}
-
-reporting_table(chu_data, "Table S2.5: Yearly cumulative visits for mental and neurological disorders reported at regional hospitals")
+```{r  reporting_tables2, warning = FALSE, message = FALSE, echo = FALSE, include = TRUE, out.width = '97%'}
+
+knitr::include_graphics("table_s_2_5a.png")
+knitr::include_graphics("table_s_2_5b.png")
+
+# reporting_table(chu_data, "Table S2.5: Yearly cumulative visits for mental and neurological disorders reported at regional hospitals") %>%
+#    gtsave("table_s_2_5.docx")
 

### 2023-05-16 appendix_2.2.Rmd
Revisions to tables, revised submission to ProQuest

@@
 
-```{r table_s_2_6, echo = FALSE, include = TRUE, out.height = '97%'}
+```{r table_s_2_6, echo = FALSE, include = TRUE, out.width = '97%'}
 
@@
 
-```
-
-<!-- ``` {r table_standardization_region_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
-
-<!-- column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique() -->
-<!-- column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique() -->
-
-<!-- r_old <- column1 %>% dplyr::select(region_name) %>% unique() -->
-<!-- r_new <- column2 %>% dplyr::select(region) %>% unique() -->
-
-<!-- cbind(r_old, r_new) %>% mutate(test = region_name == region) %>% -->
-<!--   filter(test == FALSE) %>% -->
-<!--   relocate(region, .before = region_name) %>% -->
-<!--   rename("Name in data" = region, -->
-<!--          "Standardized name" = region_name) %>% -->
-<!--   dplyr::select(!test) %>% -->
-<!--   gt() %>% -->
-<!--   tab_header( -->
-<!--     title = md("**Table S2.6: Standardization of region names**")) %>% -->
-<!--   gtsave("table_s_2_6.docx") -->
-
-<!-- ``` -->
+# column2 <- data_mh %>% dplyr::select(commune, district, region) %>% unique()
+# column1 <- facilities_all %>% dplyr::select(region_name, district_name, commune_name) %>% unique()
+# 
+# r_old <- column1 %>% dplyr::select(region_name) %>% unique()
+# r_new <- column2 %>% dplyr::select(region) %>% unique()
+# 
+# cbind(r_old, r_new) %>% mutate(test = region_name == region) %>%
+#   filter(test == FALSE) %>%
+#   relocate(region, .before = region_name) %>%
+#   rename("Name in data" = region,
+#          "Standardized name" = region_name) %>%
+#   dplyr::select(!test) %>%
+#   gt() %>%
+#   tab_header(
+#     title = md("**Table S2.6: Standardization of region names**")) %>%
+#   gtsave("table_s_2_6.docx")
+
+```
 
@@
 
-```{r table_s_2_7, echo = FALSE, include = TRUE, out.height = '97%'}
+```{r table_s_2_7, echo = FALSE, include = TRUE, out.width = '97%'}
 
@@
 
-```
-
-<!-- ``` {r table_standardization_district_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
-
-<!-- district_old <- c("Anosibe An'Ala", "Antananarivo Atsimon", "Antananarivo Avaradr", "Antananarivo Renivoh", "Fenoarivo Atsinanana", "Mananara Avaratra", "Nosy Boraha", "Ambovombe Androy", "Tsiombe", "Amboasary Atsimo", "Ankazoabo Atsimo", "Toliara I", "Toliara II", "Toliara-I", "Toliara-II", "Midongy Atsimo", "Antanambao Manampont", "Antanambao Manampotsy", "Vohibinany", "Ambatoboeny", "FenoarivoBe", "Nosy Be", "Fianarantsoa II", "lalangina", "Belo Tsiribihina", "Vohimarina", "Befandriana Avaratra", "Boriziny", "Nosy Varika") -->
-
-<!-- district_new <- c("Anosibe-An'ala", "Antananarivo Atsimondrano", "Antananarivo Avaradrano", "Antananarivo Renivohitra", "Fenerive Est", "Mananara-Avaratra", "Sainte Marie", "Ambovombe-Androy", "Tsihombe", "Amboasary-Atsimo", "Ankazoabo", "Toliary-I", "Toliary-II", "Toliary-I", "Toliary-II", "Midongy-Atsimo", "Antanambao Manampontsy", "Antanambao Manampontsy", "Brickaville", "Ambato Boeni", "Fenoarivobe", "Nosy-Be", "Fianarantsoa I", "Lalangina", "Belo Sur Tsiribihina", "Vohemar", "Befandriana Nord", "Port-Berge (Boriziny-Vaovao)", "Nosy-Varika") -->
-
-<!-- as.data.frame(cbind(district_old, district_new)) %>% -->
-<!--   arrange(district_old) %>% -->
-<!--   rename("Name in data" = district_old, -->
-<!--          "Standardized name" = district_new) %>% -->
-<!--   gt() %>% -->
-<!--   tab_header( -->
-<!--     title = md("**Table S2.7: Standardization of district names**")) %>% -->
-<!--   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>% -->
-<!--   tab_style( -->
-<!--     locations = cells_column_labels(), -->
-<!--     style     = list( -->
-<!--       cell_text(weight = "bold")) -->
-<!--   ) %>% -->
-<!--   gtsave("table_s_2_7.docx") -->
-<!-- ``` -->
+# district_old <- c("Anosibe An'Ala", "Antananarivo Atsimon", "Antananarivo Avaradr", "Antananarivo Renivoh", "Fenoarivo Atsinanana", "Mananara Avaratra", "Nosy Boraha", "Ambovombe Androy", "Tsiombe", "Amboasary Atsimo", "Ankazoabo Atsimo", "Toliara I", "Toliara II", "Toliara-I", "Toliara-II", "Midongy Atsimo", "Antanambao Manampont", "Antanambao Manampotsy", "Vohibinany", "Ambatoboeny", "FenoarivoBe", "Nosy Be", "Fianarantsoa II", "lalangina", "Belo Tsiribihina", "Vohimarina", "Befandriana Avaratra", "Boriziny", "Nosy Varika")
+# 
+# district_new <- c("Anosibe-An'ala", "Antananarivo Atsimondrano", "Antananarivo Avaradrano", "Antananarivo Renivohitra", "Fenerive Est", "Mananara-Avaratra", "Sainte Marie", "Ambovombe-Androy", "Tsihombe", "Amboasary-Atsimo", "Ankazoabo", "Toliary-I", "Toliary-II", "Toliary-I", "Toliary-II", "Midongy-Atsimo", "Antanambao Manampontsy", "Antanambao Manampontsy", "Brickaville", "Ambato Boeni", "Fenoarivobe", "Nosy-Be", "Fianarantsoa I", "Lalangina", "Belo Sur Tsiribihina", "Vohemar", "Befandriana Nord", "Port-Berge (Boriziny-Vaovao)", "Nosy-Varika")
+# 
+# as.data.frame(cbind(district_old, district_new)) %>%
+#   arrange(district_old) %>%
+#   rename("Name in data" = district_old,
+#          "Standardized name" = district_new) %>%
+#   gt() %>%
+#   tab_header(
+#     title = md("**Table S2.7: Standardization of district names**")) %>%
+#   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
+#   tab_style(
+#     locations = cells_column_labels(),
+#     style     = list(
+#       cell_text(weight = "bold"))
+#   ) %>%
+#   gtsave("table_s_2_7.docx")
+
+```
 
@@
 
-```
-
-<!-- ``` {r table_standardization_district_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
-
-<!-- district_tobechanged <- c("Antsirabe II", "Port-Berge (Boriziny-Vaovao)", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Betafo", "Vohemar", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I") -->
-
-<!-- district_communes_affected <- c("Antanamalaza", "Andribavontsona", "Ambalamidera", "Andoharanomaintso", "Anjoma-tsara", "Ankarinarivo", "Fanjakana", "Iavinomby", "Isorana", "Nasandratrony", "Soatanana", "Alakamisy Ambohimahy", "Ambalakely", "Ambalamahasoa", "Andianjanto Est", "Andrainjanto Centre", "Androy", "Fandravandava", "Ialananidro", "Ivoamba", "Mahatsinjo", "Mahatsinjony", "Sahambavy", "Taindambo", "Antanambao Ambary", "Antsahavaribe", "Ambohimahavelona", "Ambolofoty", "Anakao", "Analamisampy", "Andranohinaly", "Andranovory", "Ankililoaka", "Ankilimalinika", "Beheloka", "Behompy", "Belalanda", "Betsinjaka", "Manombo", "Manorofify", "MarofotyMarofoty", "Maromiandra", "Miary", "Milenaka", "Mitsinjo", "Soalara", "St Augustin", "Tsianisiha", "Alakamisy Itenina", "Andranomiditra", "Andranovorivato", "Ankaromalaza Mifanas", "Ihazoara", "Mahaditra", "Mahasoabe", "Maneva", "Soaindrana", "Talata Ampano", "Vohibato Ouest", "Vohimarina", "Vohitrafeno") -->
-
-<!-- district_changed <- c("Ambatolampy", "Analalava", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Mandoto", "Sambava", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato") -->
-
-<!-- as.data.frame(cbind(district_tobechanged, district_changed, district_communes_affected)) %>% -->
-<!--   arrange(district_tobechanged) %>% -->
-<!--   relocate(district_communes_affected, .before = district_tobechanged) %>% -->
-<!--   rename("District name in data" = district_tobechanged, -->
-<!--          "Communes" = district_communes_affected, -->
-<!--          "District name, updated" = district_changed) %>% -->
-<!--   gt() %>%  -->
-<!--   tab_header( -->
-<!--     title = md("**Table S2.8: Standardization of district names, based on commune name**")) %>% -->
-<!--   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>% -->
-<!--   tab_style( -->
-<!--     locations = cells_column_labels(), -->
-<!--     style     = list( -->
-<!--       cell_text(weight = "bold")) -->
-<!--   )%>% -->
-<!--   gtsave("table_s_2_8.docx") -->
-
-<!-- ``` -->
+# 
+# 
+# district_tobechanged <- c("Antsirabe II", "Port-Berge (Boriziny-Vaovao)", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Betafo", "Vohemar", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Toliara-I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I", "Fianarantsoa I")
+# 
+# 
+# district_communes_affected <- c("Antanamalaza", "Andribavontsona", "Ambalamidera", "Andoharanomaintso", "Anjoma-tsara", "Ankarinarivo", "Fanjakana", "Iavinomby", "Isorana", "Nasandratrony", "Soatanana", "Alakamisy Ambohimahy", "Ambalakely", "Ambalamahasoa", "Andianjanto Est", "Andrainjanto Centre", "Androy", "Fandravandava", "Ialananidro", "Ivoamba", "Mahatsinjo", "Mahatsinjony", "Sahambavy", "Taindambo", "Antanambao Ambary", "Antsahavaribe", "Ambohimahavelona", "Ambolofoty", "Anakao", "Analamisampy", "Andranohinaly", "Andranovory", "Ankililoaka", "Ankilimalinika", "Beheloka", "Behompy", "Belalanda", "Betsinjaka", "Manombo", "Manorofify", "MarofotyMarofoty", "Maromiandra", "Miary", "Milenaka", "Mitsinjo", "Soalara", "St Augustin", "Tsianisiha", "Alakamisy Itenina", "Andranomiditra", "Andranovorivato", "Ankaromalaza Mifanas", "Ihazoara", "Mahaditra", "Mahasoabe", "Maneva", "Soaindrana", "Talata Ampano", "Vohibato Ouest", "Vohimarina", "Vohitrafeno")
+# 
+# 
+# district_changed <- c("Ambatolampy", "Analalava", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Isandra", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Lalangina", "Mandoto", "Sambava", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Toliary-II", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato", "Vohibato")
+# 
+# 
+# as.data.frame(cbind(district_tobechanged, district_changed, district_communes_affected)) %>%
+#   arrange(district_tobechanged) %>%
+#   relocate(district_communes_affected, .before = district_tobechanged) %>%
+#   rename("District name in data" = district_tobechanged,
+#          "Communes" = district_communes_affected,
+#          "District name, updated" = district_changed) %>%
+#   gt() %>%
+#   tab_header(
+#     title = md("**Table S2.8: Standardization of district names, based on commune name**")) %>%
+#   tab_options(table.font.names = "Source Sans Pro",  page.header.use_tbl_headings	= TRUE) %>%
+#   tab_style(
+#     locations = cells_column_labels(),
+#     style     = list(
+#       cell_text(weight = "bold"))
+#   )%>%
+#   gtsave("table_s_2_8.docx")
+
+```
 
@@
 
-```{r table_s_2_9, echo = FALSE, include = TRUE, out.height = '97%'}
+```{r table_s_2_9a, echo = FALSE, include = TRUE, out.width = '97%'}
 
 knitr::include_graphics("table_s_2_9a.png")
+
+```
+
+```{r table_s_2_9b, echo = FALSE, include = TRUE, out.width = '97%'}
+
 knitr::include_graphics("table_s_2_9b.png")
 
-```
-
-<!-- ``` {r table_standardization_commune_1, results = TRUE, , warning = FALSE, message = FALSE, echo = FALSE, include = TRUE} -->
-
-<!-- commune_old <- c("Alakamisy Ambohimahy", "Alakamisy Itenina", "Ambadrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy   II", "Ambalamidera", "AmbalapaisoII", "Ambararatabe /Nord", -->
-<!--                  "Ambarijeby Atsimo", "Ambatoben'anja", "AmbatofisakaII", "AmbatoharananaI", "Ambatolampy Tsimahaf", "Ambatolampy Tsimahafotsy", "Ambatoriha/Est", "Ambatotsipihana",  -->
-<!--                  "Ambatovala", "Ambatry", "Ambinanin'Andravory", "Ambinaninandro", "Ambinaniroa-Andonaka", "Ambodiadabo Maitsokely", "Ambodiadabo", "Ambodiampana Lokoho", -->
-<!--                  "Ambodiampanana", "Ambodifarihy", "Ambodihazambo", "Ambodimanga  I", "Ambodimanga II-B", "Ambodimotso Atsimo", "AmbodinonokaAntaratr", "Ambodirian'Isahafary", -->
-<!--                  "Amboditandroho", "Ambohibao Atsimo", "Ambohibary", "Ambohijato Mandritsara", "Ambohimahavelona", "Ambohimalaza", "Ambohimàna", "Ambohimanga Sud", -->
-<!--                  "Ambohimanjaka", "AmbohimiarinaII", "Ambohitralalana", "Ambohitrandriamanitr", "AmbohitsaraEst", "Ambolidibe Atsinanana", "Ambolofoty", "Amboropotsy", -->
-<!--                  "Ampasimadinika", "Ampasimborajka", "Ampasimpotsy", "Ampasipotsy Gare", "Ampasipotsy Madialaz", "Ampataka Manampaneva", "Ampataka Maroreny", "Anakao", -->
-<!--                  "Analalaiva", "Analamisampy", "Analamitsivala", "Anbatomainty", "Andanandava", "Andianjanto Est", "Andimaka", "Andoharanomaintso", "Andoharanomaintso", -->
-<!--                  "Andrainjanto Centre", "Andranohinaly", "Andranomiditra", "Andranomiely", "Andranovorivato", "Andranovory", "Andravola", "Andrebakely", "Andribavontsona", -->
-<!--                  "Androndrona", "Androy", "Anjapaly", "Anjeke Ankilira", "Anjeva Gare", "Anjiabe", "Anjiaija", "Anjoman'Ankona", "Anjoma-tsara", "Ankadinondry", "Ankafina", -->
-<!--                  "Ankarinarivo", "Ankaromalaza Mifanas", "Ankasakasa", "Ankazoabo", "Ankazotokana I", "Ankiabe Salohy", "Ankiakabe-Nord", "Ankililoaka", "Ankilimalinika", -->
-<!--                  "Ankirondro", "Anontsibe", "Anosiarivo", "Anosy Tsararafara", "Antalaha", "Antanamalaza", "Antanambao Ambary", "Antanambao I", "Antanambao Manampotsy", -->
-<!--                  "Antanambaon'Amberina", "Antananarivo I", "Antananarivo II", "Antananarivo III", "Antananarivo IV", "Antananarivo V", "Antananarivo VI", "Antanandava Nord", -->
-<!--                  "Antananivo /Haut", "Antanetibe Mahazaza", "Antanimora- Sud", "Antenina I", "Antoby", "Antohaboto", "Antongo", "Antokoboritelo", "Antranonkarany", "Antsahavaribe", -->
-<!--                  "Antsakomanondro", "Antsapanimahazo", "Antsirabe I", "Antsiranana I", "Antsoantany", "Bealampoana", "Bealanana I", "Beampombo  I", "Beandrarezona I", -->
-<!--                  "Befandriana Avaratra", "Befandriana-Sud", "Befetra", "Befotaka Avaratra", "Befotaka", "Beheloka", "Behera", "Behompy", "Belafika Haut", "Belalanda", -->
-<!--                  "Belambo", "Belaoko Marovato", "Belo sur Mer", "Belo Tsiribihina", "Belotsiribihina", "Bemaneviky H", "BenatoToby", "Beraketa", "Berevo Ranobe", -->
-<!--                  "Beroy Sud", "Betioky Sud", "Betsakotsako Andrano", "Betsimiositra", "Betsinjaka", "Bevoay Beretra", "Bevonotro", "Efatsy Anandroza", "Enakara Haut", -->
-<!--                  "Enaniiliha", "Ereda", "Etrotroka", "Fandravandava", "Fanjakana", "Faux-Cap", "Fenoevo", "Fieferana", "Foulpointe", "Ialananidro", "Iavinomby", "Ibity", -->
-<!--                  "Ihaborano Namohora", "Ihazoara", "Iloto", "Imady", "Imeritsiatosika", "Isaka Ivondro", "Isaraha", "Isorana", "Ivatana", "Ivato Aéroport", "Ivoamba", -->
-<!--                  "Ivony", "Kalalao", "Kianjandrandrakefina", "labohazo", "Lavaraty Ivondro", "Mahaditra", "Mahafasa", "Mahajanga I", "Mahasoabe", "Mahatsara Lefaka", -->
-<!--                  "Mahatsinjo Atsinanana", "Mahatsinjo", "Mahatsinjony", "Mahazina", "Manajary Urbain", "Manakambahiny Est", "Manakambahiny Ouest", "Manakara(com)", -->
-<!--                  "Manambotra Sud", "Manapatrana", "Mandromodromotra", "Maneva", "Mangarivot", "Manombo", "Manorofify", "Marintampona", "Marivorahona", "Maroarivo",  -->
-<!--                  "MarofotyMarofoty", "Maromiandra", "Maromokotra-Loky", "Marosavoa Bas", "Marovitsika", "Merimandroso", "Miary", "Milenaka", "Mitsinjo", "Mizilo Gare",  -->
-<!--                  "Moramanga Urbain", "Morarano Gare", "Morombe", "Nagnarena", "Nasandratrony", "Niarovana", "Nosibe Masianaka", "Onilhy", "Port Bergé I", "Port Bergé II", -->
-<!--                  "Rantabe Est", "Rantabe Sud", "Razanaka", "Sahamadio", "Sahambavy", "Sahambo", "Sahanivotry Atsimo", "Sakamahily-Ouest", "Sakay", "Sakona", "Sambava Urbain", -->
-<!--                  "Sarobaratra", "Soaindrana", "Soalara", "Soatanana", "St Augustin", "Taindambo", "Talata Ampano", "Talatan'Angavo", "Taolognaro", "Tanakamba", "Tanambao  Daoud", -->
-<!--                  "Tanambaovatrakaka", "Tanandava-Sud", "Tanandrano", "Toamasina Suburbain", "Tovòna", "Tsarahonenana", "Tsarajomoko", "Tsaratanana", "Tsiafajavona Ankarat", -->
-<!--                  "Tsianisiha", "Tsianofàna", "Tsinjoarivo", "Tsiombe", "Tsiroanomadidy Ville", "Tsiroanomandidy Ville", "Vatolatsaky", "Vilihazo", "Vinaninony Avaratra", -->
-<!--                  "Vineta Andamasiny", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zomabealoka") -->
-
-<!-- commune_new <- c("Alakamisy Ambohimaha", "Alakamisy Itenina", "Ambandrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy II", "Ambalamidera II", "Ambalapaiso II", "Ambararatabe Nord", -->
-<!--                  "Ambarijeby Sud", "Ambatoben'anjavy", "Ambatofisaka II", "Ambatoharanana", "Ambatolampy", "Ambatolampy", "Ambatoriha Est", "Ambatotsipihina", "Ambatolava",  -->
-<!--                  "Ambatry Mitsinjo", "Ambinanin'andravory", "Ambinanindrano", "Ambinaniroa", "Ambodiadabo", "Ambodiadabo M", "Ambodiampana", "Ambodiampana", "Ambodifarihy Fenomanana", -->
-<!--                  "Ambodihazoambo", "Ambodimanga I","Ambodimanga II", "Ambodimotso Sud", "Ambodinonoka", "Ambodirian'i Sahafary", "Amboditandroroho", "Ambohibao Sud", -->
-<!--                  "Ambohibary Vohilena", "Mandritsara", " Ambohimahavelona", "Ambohimalaza Miray", "Ambohimana", "Ambohimanga Du Sud", "Sahatsiho Ambohimanjaka", -->
-<!--                  "Ambohimiarina II", "Ambohitralanana", "Ambohitrandriamanitra", "Ambohitsara Est", "Ambolidibe Est", "Ambolofoty", "Amborompotsy", "Ampasimadinika Manambolo", -->
-<!--                  "Ampasimboraka", "Ampasimpotsy Sud", "Ampasimpotsy Gara", "Ampasipotsy Mandialaza", "Manampaneva", "Ampatakamaroreny", "Anakao", "Analaiva", "Analamisampy", -->
-<!--                  "Analamitsivalana", "Ambatomainty", "Antanandava", "Andrainjato Est", "Andimaky Manambolo", "Andoharanomaitso", "Andoharanomaitso", "Andrainjato Centre", -->
-<!--                  "Andranohinaly", "Andranomiditra", "Rambolamasoandro Andranomiely", "Andranovorivato", "Andranovory", "Andravola Vohipeno", "Andrebakely Nord", "Andribavontsona", -->
-<!--                  "Androndrono", "Androy", "Anjampaly", "Anjeky Ankilikira", "Anjeva Gara", "Anjiabe Ambony", "Anjiajia", "Anjoman'ankona", "Anjoma Itsara", "Ankadinondry Sakay", -->
-<!--                  "Ankafina Tsarafidy", "Ankarinarivo Manirisoa", "Ankaromalaza Mifanasoa", "Ankasakasa Tsibiray", "Ankazoabo Sud", "Ankazotokana", "Ankiabe-Salohy", " Ankiakabe Nord", -->
-<!--                  "Ankililoaka", "Ankilimalinike", "Bemarivo Ankirondro", "Anontsibe Centre", "Anosiarivo I", "Anosy Tsararafa", " Antalaha Ambonivohitra", "Antanamalaza", "Antanambao Ambary", -->
-<!--                  "Antanambao", "Antanambao Manampontsy", "Antanambaon'amberina", "1er Arrondissement", "2e Arrondissement", "3e Arrondissement", "4e Arrondissement", "5e Arrondissement", -->
-<!--                  "6e Arrondissement", "Antanandava", "Antananivo Haut", "Antanetibe", "Antanimora Atsimo", "Antenina", "Antoby Est", "Antohabato", "Antongo Vaovao", "Marovitsika Sud", "Antranokarany", -->
-<!--                  "Antsahavaribe", "Antsakoamanondro", "Antsampanimahazo", "Antsirabe Afovoany Atsinanana", "Diego Suarez", "Antsoatany", "Bealampona", "Bealanana", "Beampombo I", -->
-<!--                  "Beandrarezona", "Befandriana Nord", "Befandriana Sud", "Befeta", "Befotaka Nord", "Befotaka Sud", "Beheloka", "Behara", "Behompy", "Belafike Haut", "Belalanda", -->
-<!--                  "Belambo Firaisana", "Belaoka Marovato", "Belo Sur Mer", "Belo Sur Tsiribihina", "Belo Sur Tsiribihina", "Bemaneviky Haut Sambirano", "Benato Toby", "Bereketa",  -->
-<!--                  "Berevo/ranobe", "Beroy Atsimo", "Betioky Atsimo", "Betsakotsako Andranotsara", "Betsimisotra", "Betsinjaka", " Beretra Bevoay", "Bevonotra", "Efatsy", "Enakara-Haut", -->
-<!--                  "Enaniliha", "Erada", "Etrotroka Atsimo", "Fandrandava", "Fanjakana", "Betanty (Faux Cap)", "Fenoevo-Efita", "Fiaferana", "Mahavelona (Foulpointe)", "Ialananindro",  -->
-<!--                  "Iavonomby Vohibola", "Alatsinainy Ibity", "Namohora Iaborano", "Ihazoara", "Menamaty Iloto", "Imerina Imady", "Imerintsiatosika", "Isaka-Ivondro", "Isahara", -->
-<!--                  "Isorana", "Vatana", "Ivato Aeroport", "Ivoamba", "Ivony Miaramiasa", "Ikalalao", "Kianjandrakefina", "Iabohazo", "Ivondro", "Mahaditra", "Mahafasa Centre",  -->
-<!--                  "Mahajanga", "Mahasoabe", "Mahatsara Iefaka", "Mahatsinjo Est", "Mahatsinjony", "Mahatsinjony", "Mahazina Ambohipierenana", "Mananjary", "Manakambahiny Antsinanana", -->
-<!--                  "Manakambahiny Andrefana", "Manakara", "Manambotra Atsimo", "Manampatrana", "Mandromondromotra", "Maneva", "Mangarivotra", "Manombo Sud", "Manorofify", "Maritampona",  -->
-<!--                  "Tanambao Marivorahona", "Maroarivo Ankazomanga", "Marofoty", "Maromiandra", "Maromokotra Loky", "Marosavoa", "Marovitsika Sud", "Imerimandroso", "Miary Ambohibola",  -->
-<!--                  "Milenaka", "Mitsinjo Betanimena", "Mizilo Gara", "Moramanga", "Morarano Gara", "Cu Morombe", "Nanarena Besakoa", "Nasandratrony", "Niarovana Marosampanana",  -->
-<!--                  "Masianaka", "Onilahy", "Port Berge", "Port Berge II", "Rantabe", "Rantabe", "Vohipeno Razanaka", "Sahamadio Fisakana", "Sahambavy", "Sahambano", "Sahanivotry Manandona", -->
-<!--                  "Sakamahily", "Tanamarina Sakay", "Sakoana", "Sambava Cu", "Sarobaratra Ifanja", "Soaindrana", "Soalara Sud", "Soatanana", "Saint Augustin", "Taindambo", "Tatala Ampano",  -->
-<!--                  "Talata Angavo", "Fort-Dauphin", "Tanakambana", "Tanambao Daoud", "Tanambao Vahatrakaka", "Tanandava Sud", "Tandrano", "Toamasina Suburbaine", "Tovona", "Tsarahonenana Sahanivotry", -->
-<!--                  "Tsarajomoka", "Tsaratanana I", "Tsiafajavona Ankaratra", "Tsianisiha", "Tsianofana", "Tsinjoarivo Imanga", "Tsihombe", "Tsiroanomandidy Fihaonana",  -->
-<!--                  "Tsiroanomandidy Fihaonana", "Vatolatsaka", "Viliahazo", "Vinaninony Atsimo", "Andamasiny Vineta", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zoma Bealoka") -->
-
-<!-- as.data.frame(cbind(commune_old, commune_new)) %>% -->
-<!--   arrange(commune_old) %>% -->
-<!--   mutate(test = commune_new == commune_old) %>% -->
-<!--   filter(test == FALSE) %>% -->
-<!--   dplyr::select(!test) %>% -->
-<!--   rename("Name in data" = commune_old, -->
-<!--          "Standardized name" = commune_new) %>% -->
-<!--   gt() %>% -->
-<!--   tab_header( -->
-<!--     title = md("**Table S2.9: Standardization of commune names**")) %>% -->
-<!--   tab_options(table.font.names = "Source Sans Pro", -->
-<!--               page.header.use_tbl_headings	= TRUE) %>% -->
-<!--   tab_style( -->
-<!--     locations = cells_column_labels(), -->
-<!--     style     = list( -->
-<!--       cell_text(weight = "bold")) -->
-<!--   ) %>% -->
-<!--   gtsave("table_s_2_9.docx") -->
-
-<!-- ``` -->
+# commune_old <- c("Alakamisy Ambohimahy", "Alakamisy Itenina", "Ambadrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy   II", "Ambalamidera", "AmbalapaisoII", "Ambararatabe /Nord",
+#                  "Ambarijeby Atsimo", "Ambatoben'anja", "AmbatofisakaII", "AmbatoharananaI", "Ambatolampy Tsimahaf", "Ambatolampy Tsimahafotsy", "Ambatoriha/Est", "Ambatotsipihana",
+#                  "Ambatovala", "Ambatry", "Ambinanin'Andravory", "Ambinaninandro", "Ambinaniroa-Andonaka", "Ambodiadabo Maitsokely", "Ambodiadabo", "Ambodiampana Lokoho",
+#                  "Ambodiampanana", "Ambodifarihy", "Ambodihazambo", "Ambodimanga  I", "Ambodimanga II-B", "Ambodimotso Atsimo", "AmbodinonokaAntaratr", "Ambodirian'Isahafary",
+#                  "Amboditandroho", "Ambohibao Atsimo", "Ambohibary", "Ambohijato Mandritsara", "Ambohimahavelona", "Ambohimalaza", "Ambohimàna", "Ambohimanga Sud",
+#                  "Ambohimanjaka", "AmbohimiarinaII", "Ambohitralalana", "Ambohitrandriamanitr", "AmbohitsaraEst", "Ambolidibe Atsinanana", "Ambolofoty", "Amboropotsy",
+#                  "Ampasimadinika", "Ampasimborajka", "Ampasimpotsy", "Ampasipotsy Gare", "Ampasipotsy Madialaz", "Ampataka Manampaneva", "Ampataka Maroreny", "Anakao",
+#                  "Analalaiva", "Analamisampy", "Analamitsivala", "Anbatomainty", "Andanandava", "Andianjanto Est", "Andimaka", "Andoharanomaintso", "Andoharanomaintso",
+#                  "Andrainjanto Centre", "Andranohinaly", "Andranomiditra", "Andranomiely", "Andranovorivato", "Andranovory", "Andravola", "Andrebakely", "Andribavontsona",
+#                  "Androndrona", "Androy", "Anjapaly", "Anjeke Ankilira", "Anjeva Gare", "Anjiabe", "Anjiaija", "Anjoman'Ankona", "Anjoma-tsara", "Ankadinondry", "Ankafina",
+#                  "Ankarinarivo", "Ankaromalaza Mifanas", "Ankasakasa", "Ankazoabo", "Ankazotokana I", "Ankiabe Salohy", "Ankiakabe-Nord", "Ankililoaka", "Ankilimalinika",
+#                  "Ankirondro", "Anontsibe", "Anosiarivo", "Anosy Tsararafara", "Antalaha", "Antanamalaza", "Antanambao Ambary", "Antanambao I", "Antanambao Manampotsy",
+#                  "Antanambaon'Amberina", "Antananarivo I", "Antananarivo II", "Antananarivo III", "Antananarivo IV", "Antananarivo V", "Antananarivo VI", "Antanandava Nord",
+#                  "Antananivo /Haut", "Antanetibe Mahazaza", "Antanimora- Sud", "Antenina I", "Antoby", "Antohaboto", "Antongo", "Antokoboritelo", "Antranonkarany", "Antsahavaribe",
+#                  "Antsakomanondro", "Antsapanimahazo", "Antsirabe I", "Antsiranana I", "Antsoantany", "Bealampoana", "Bealanana I", "Beampombo  I", "Beandrarezona I",
+#                  "Befandriana Avaratra", "Befandriana-Sud", "Befetra", "Befotaka Avaratra", "Befotaka", "Beheloka", "Behera", "Behompy", "Belafika Haut", "Belalanda",
+#                  "Belambo", "Belaoko Marovato", "Belo sur Mer", "Belo Tsiribihina", "Belotsiribihina", "Bemaneviky H", "BenatoToby", "Beraketa", "Berevo Ranobe",
+#                  "Beroy Sud", "Betioky Sud", "Betsakotsako Andrano", "Betsimiositra", "Betsinjaka", "Bevoay Beretra", "Bevonotro", "Efatsy Anandroza", "Enakara Haut",
+#                  "Enaniiliha", "Ereda", "Etrotroka", "Fandravandava", "Fanjakana", "Faux-Cap", "Fenoevo", "Fieferana", "Foulpointe", "Ialananidro", "Iavinomby", "Ibity",
+#                  "Ihaborano Namohora", "Ihazoara", "Iloto", "Imady", "Imeritsiatosika", "Isaka Ivondro", "Isaraha", "Isorana", "Ivatana", "Ivato Aéroport", "Ivoamba",
+#                  "Ivony", "Kalalao", "Kianjandrandrakefina", "labohazo", "Lavaraty Ivondro", "Mahaditra", "Mahafasa", "Mahajanga I", "Mahasoabe", "Mahatsara Lefaka",
+#                  "Mahatsinjo Atsinanana", "Mahatsinjo", "Mahatsinjony", "Mahazina", "Manajary Urbain", "Manakambahiny Est", "Manakambahiny Ouest", "Manakara(com)",
+#                  "Manambotra Sud", "Manapatrana", "Mandromodromotra", "Maneva", "Mangarivot", "Manombo", "Manorofify", "Marintampona", "Marivorahona", "Maroarivo",
+#                  "MarofotyMarofoty", "Maromiandra", "Maromokotra-Loky", "Marosavoa Bas", "Marovitsika", "Merimandroso", "Miary", "Milenaka", "Mitsinjo", "Mizilo Gare",
+#                  "Moramanga Urbain", "Morarano Gare", "Morombe", "Nagnarena", "Nasandratrony", "Niarovana", "Nosibe Masianaka", "Onilhy", "Port Bergé I", "Port Bergé II",
+#                  "Rantabe Est", "Rantabe Sud", "Razanaka", "Sahamadio", "Sahambavy", "Sahambo", "Sahanivotry Atsimo", "Sakamahily-Ouest", "Sakay", "Sakona", "Sambava Urbain",
+#                  "Sarobaratra", "Soaindrana", "Soalara", "Soatanana", "St Augustin", "Taindambo", "Talata Ampano", "Talatan'Angavo", "Taolognaro", "Tanakamba", "Tanambao  Daoud",
+#                  "Tanambaovatrakaka", "Tanandava-Sud", "Tanandrano", "Toamasina Suburbain", "Tovòna", "Tsarahonenana", "Tsarajomoko", "Tsaratanana", "Tsiafajavona Ankarat",
+#                  "Tsianisiha", "Tsianofàna", "Tsinjoarivo", "Tsiombe", "Tsiroanomadidy Ville", "Tsiroanomandidy Ville", "Vatolatsaky", "Vilihazo", "Vinaninony Avaratra",
+#                  "Vineta Andamasiny", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zomabealoka")
+# 
+# commune_new <- c("Alakamisy Ambohimaha", "Alakamisy Itenina", "Ambandrika", "Ambalakely", "Ambalamahasoa", "Ambalamanasy II", "Ambalamidera II", "Ambalapaiso II", "Ambararatabe Nord",
+#                  "Ambarijeby Sud", "Ambatoben'anjavy", "Ambatofisaka II", "Ambatoharanana", "Ambatolampy", "Ambatolampy", "Ambatoriha Est", "Ambatotsipihina", "Ambatolava",
+#                  "Ambatry Mitsinjo", "Ambinanin'andravory", "Ambinanindrano", "Ambinaniroa", "Ambodiadabo", "Ambodiadabo M", "Ambodiampana", "Ambodiampana", "Ambodifarihy Fenomanana",
+#                  "Ambodihazoambo", "Ambodimanga I","Ambodimanga II", "Ambodimotso Sud", "Ambodinonoka", "Ambodirian'i Sahafary", "Amboditandroroho", "Ambohibao Sud",
+#                  "Ambohibary Vohilena", "Mandritsara", " Ambohimahavelona", "Ambohimalaza Miray", "Ambohimana", "Ambohimanga Du Sud", "Sahatsiho Ambohimanjaka",
+#                  "Ambohimiarina II", "Ambohitralanana", "Ambohitrandriamanitra", "Ambohitsara Est", "Ambolidibe Est", "Ambolofoty", "Amborompotsy", "Ampasimadinika Manambolo",
+#                  "Ampasimboraka", "Ampasimpotsy Sud", "Ampasimpotsy Gara", "Ampasipotsy Mandialaza", "Manampaneva", "Ampatakamaroreny", "Anakao", "Analaiva", "Analamisampy",
+#                  "Analamitsivalana", "Ambatomainty", "Antanandava", "Andrainjato Est", "Andimaky Manambolo", "Andoharanomaitso", "Andoharanomaitso", "Andrainjato Centre",
+#                  "Andranohinaly", "Andranomiditra", "Rambolamasoandro Andranomiely", "Andranovorivato", "Andranovory", "Andravola Vohipeno", "Andrebakely Nord", "Andribavontsona",
+#                  "Androndrono", "Androy", "Anjampaly", "Anjeky Ankilikira", "Anjeva Gara", "Anjiabe Ambony", "Anjiajia", "Anjoman'ankona", "Anjoma Itsara", "Ankadinondry Sakay",
+#                  "Ankafina Tsarafidy", "Ankarinarivo Manirisoa", "Ankaromalaza Mifanasoa", "Ankasakasa Tsibiray", "Ankazoabo Sud", "Ankazotokana", "Ankiabe-Salohy", " Ankiakabe Nord",
+#                  "Ankililoaka", "Ankilimalinike", "Bemarivo Ankirondro", "Anontsibe Centre", "Anosiarivo I", "Anosy Tsararafa", " Antalaha Ambonivohitra", "Antanamalaza", "Antanambao Ambary",
+#                  "Antanambao", "Antanambao Manampontsy", "Antanambaon'amberina", "1er Arrondissement", "2e Arrondissement", "3e Arrondissement", "4e Arrondissement", "5e Arrondissement",
+#                  "6e Arrondissement", "Antanandava", "Antananivo Haut", "Antanetibe", "Antanimora Atsimo", "Antenina", "Antoby Est", "Antohabato", "Antongo Vaovao", "Marovitsika Sud", "Antranokarany",
+#                  "Antsahavaribe", "Antsakoamanondro", "Antsampanimahazo", "Antsirabe Afovoany Atsinanana", "Diego Suarez", "Antsoatany", "Bealampona", "Bealanana", "Beampombo I",
+#                  "Beandrarezona", "Befandriana Nord", "Befandriana Sud", "Befeta", "Befotaka Nord", "Befotaka Sud", "Beheloka", "Behara", "Behompy", "Belafike Haut", "Belalanda",
+#                  "Belambo Firaisana", "Belaoka Marovato", "Belo Sur Mer", "Belo Sur Tsiribihina", "Belo Sur Tsiribihina", "Bemaneviky Haut Sambirano", "Benato Toby", "Bereketa",
+#                  "Berevo/ranobe", "Beroy Atsimo", "Betioky Atsimo", "Betsakotsako Andranotsara", "Betsimisotra", "Betsinjaka", " Beretra Bevoay", "Bevonotra", "Efatsy", "Enakara-Haut",
+#                  "Enaniliha", "Erada", "Etrotroka Atsimo", "Fandrandava", "Fanjakana", "Betanty (Faux Cap)", "Fenoevo-Efita", "Fiaferana", "Mahavelona (Foulpointe)", "Ialananindro",
+#                  "Iavonomby Vohibola", "Alatsinainy Ibity", "Namohora Iaborano", "Ihazoara", "Menamaty Iloto", "Imerina Imady", "Imerintsiatosika", "Isaka-Ivondro", "Isahara",
+#                  "Isorana", "Vatana", "Ivato Aeroport", "Ivoamba", "Ivony Miaramiasa", "Ikalalao", "Kianjandrakefina", "Iabohazo", "Ivondro", "Mahaditra", "Mahafasa Centre",
+#                  "Mahajanga", "Mahasoabe", "Mahatsara Iefaka", "Mahatsinjo Est", "Mahatsinjony", "Mahatsinjony", "Mahazina Ambohipierenana", "Mananjary", "Manakambahiny Antsinanana",
+#                  "Manakambahiny Andrefana", "Manakara", "Manambotra Atsimo", "Manampatrana", "Mandromondromotra", "Maneva", "Mangarivotra", "Manombo Sud", "Manorofify", "Maritampona",
+#                  "Tanambao Marivorahona", "Maroarivo Ankazomanga", "Marofoty", "Maromiandra", "Maromokotra Loky", "Marosavoa", "Marovitsika Sud", "Imerimandroso", "Miary Ambohibola",
+#                  "Milenaka", "Mitsinjo Betanimena", "Mizilo Gara", "Moramanga", "Morarano Gara", "Cu Morombe", "Nanarena Besakoa", "Nasandratrony", "Niarovana Marosampanana",
+#                  "Masianaka", "Onilahy", "Port Berge", "Port Berge II", "Rantabe", "Rantabe", "Vohipeno Razanaka", "Sahamadio Fisakana", "Sahambavy", "Sahambano", "Sahanivotry Manandona",
+#                  "Sakamahily", "Tanamarina Sakay", "Sakoana", "Sambava Cu", "Sarobaratra Ifanja", "Soaindrana", "Soalara Sud", "Soatanana", "Saint Augustin", "Taindambo", "Tatala Ampano",
+#                  "Talata Angavo", "Fort-Dauphin", "Tanakambana", "Tanambao Daoud", "Tanambao Vahatrakaka", "Tanandava Sud", "Tandrano", "Toamasina Suburbaine", "Tovona", "Tsarahonenana Sahanivotry",
+#                  "Tsarajomoka", "Tsaratanana I", "Tsiafajavona Ankaratra", "Tsianisiha", "Tsianofana", "Tsinjoarivo Imanga", "Tsihombe", "Tsiroanomandidy Fihaonana",
+#                  "Tsiroanomandidy Fihaonana", "Vatolatsaka", "Viliahazo", "Vinaninony Atsimo", "Andamasiny Vineta", "Vohibato Ouest", "Vohimarina", "Vohitrafeno", "Zoma Bealoka")
+# 
+# as.data.frame(cbind(commune_old, commune_new)) %>%
+#   arrange(commune_old) %>%
+#   mutate(test = commune_new == commune_old) %>%
+#   filter(test == FALSE) %>%
+#   dplyr::select(!test) %>%
+#   rename("Name in data" = commune_old,
+#          "Standardized name" = commune_new) %>%
+#   gt() %>%
+#   tab_header(
+#     title = md("**Table S2.9: Standardization of commune names**")) %>%
+#   tab_options(table.font.names = "Source Sans Pro",
+#               page.header.use_tbl_headings	= TRUE) %>%
+#   tab_style(
+#     locations = cells_column_labels(),
+#     style     = list(
+#       cell_text(weight = "bold"))
+#   ) %>%
+#   gtsave("table_s_2_9.docx")
+
+```
 
@@
 The similarity between two strings of text can be measured numerically using the Levenshtein (or edit) distance.
-@konstantinidisComputingEditDistance2007 The Levenshtein distance between two identical strings will be zero, while strings involving a single character edit (insertions, deletions or substitutions) will involve a distance of 1.
+@konstantinidisComputingEditDistance2007 The Levenshtein distance between two identical strings will be zero, while strings involving a single character edit (insertions, deletions, or substitutions) will involve a distance of 1.
 

### 2023-05-16 paper3.Rmd
Revisions to tables, revised submission to ProQuest

@@
 \begin{spacing}{1}
-
 $$Y_{d,it} = \lambda_0 + \lambda_1 time_t + \lambda_2 Post_t + \lambda_3 time_t*Post_t + \alpha_d mhealth_{di} + 
@@
 
-Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals ( \acr{CIs}) using heteroskedasticity-robust standard errors.
+Given the high number of observations in the sample, I evaluated significance against an alpha of 0.01, and I constructed 99% confidence intervals (\acr{CIs}) using heteroskedasticity-robust standard errors.
 
@@
 
-\newpage
-
 Despite these limitations, the findings suggest that the announcement of COVID-19 vaccine safety and efficacy led to a robust and sustained reduction in Google search density for anxiety and depression, relative to search density prior to the announcements and to searches for other symptoms.
